### 2016-11-25 Limber_Comment.tex
Skeleton draft commit

\documentclass[preprint]{aastex}
\usepackage{graphicx}   % Including figure files
\usepackage{amsmath}    % Advanced maths comm
\usepackage{color,verbatim,url}
\usepackage{tabularx}
\usepackage[table,usenames,dvipsnames]{xcolor}\usepackage{pdflscape}
\usepackage{lastpage}

\definecolor{pink}{rgb}{0.858, 0.188, 0.478}
\definecolor{purple}{RGB}{76, 0,153}

\newcommand{\red}[1]{{\color{red}{#1}}}
\newcommand{\green}[1]{{\color{green}{#1}}}
\newcommand{\blue}[1]{{\color{blue}{#1}}}
\newcommand{\x}{\vec{x}}
\renewcommand{\d}[0]{{\rm d}}

\newcommand{\be}{\begin{equation}}  \newcommand{\ee}{\end{equation}}
\newcommand{\mb}[1]{\mbox{ #1 }}  
\newcommand{\ba}{\begin{eqnarray}}\newcommand{\ea}{\end{eqnarray}}
\newcommand{\bm}[1]{\mbox{\boldmath{$#1$}}}   %this is bold italic for MNRAS
\newcommand{\mat}[1]{\mathbfss{#1}}

\begin{document}

\title{\huge{Comment on `The Limits of Cosmic Shear'}}

\author{Members of the KiDS, DES, HSC, CFHTLenS and RCSLenS collaborations\altaffilmark{1} ....}
%\email{tbd@tbd}

\altaffiltext{1}{Aim is for representatives from each survey to sign}

\begin{abstract}
Kitching et al. (2016) examine the impact of four approximations that can be used when constraining cosmological parameters from the measurement of weak gravitational lensing by large-scale structures, also known as cosmic shear.  We support the core important message of this paper that such approximations should not be used for the future analysis of high precision surveys such as Euclid, LSST and WFIRST.  In this comment, we argue that these approximations are not able to explain away the tension between the constraints from some current weak lensing surveys and Planck.  Reducing uncertainty and characterising bias and in photometric redshift estimation is certainly a crucial task for the success of current and future surveys.  We highlight that sophisticated treatments of these uncertainties have already been explored in the literature and have been shown not to resolve the tension with Planck, in contrast to the message that Kitching et al. (2016) convey.

\end{abstract}
\section{Introduction}

The measurement of weak gravitational lensing by large scale structures provides a powerful cosmological probe of dark matter, dark energy and modifications to gravity.  As such it is the primary science goal of several current (KiDS, HSC, DES) and future (Euclid, LSST, WFIRST) large-scale surveys.   Interest in the results from these surveys is high as statistically significant tensions have been found between the cosmological parameter constraints from the CMB Planck experiment \citep{planck/cosmo:2015} in comparison to weak lensing constraints from both the Kilo-Degree Survey (KiDS) and the Canada-France-Hawaii Telescope Lensing Survey (CFHTLenS).  If the source of this tension is not a result of so-far unconsidered sources of systematic errors in one or all experiments, extensions to the standard flat $\Lambda$CDM cosmological need to be considered.  \citet{joudaki/etal:2017} have shown, for example, that the tension can be resolved with an evolving dark energy model.

In this comment paper we discuss four approximations that can be used when deriving theoretical predictions for the principally used cosmic shear statistic, $\xi_\pm$, the two-point shear correlation function.   These approximations have been explored in (ADD REF) and most recently highlighted by \citet{kitching/etal:2016} as a way to reduce tensions between weak lensing and CMB experiments, focusing on a re-analysis of the non-tomographic weak lensing data from the CFHTLenS survey \citet{kilbinger/etal:2013}.    In section~\ref{sec:cfhtlens} we compare the `one-parameter' cosmological re-analysis of \citet{kitching/etal:2016} with the full six-parameter analysis by \citet{kilbinger/etal:2013}, arguing that this particular non-tomographic data set is not in significant tension with Planck.  We also briefly review the literature that has advanced our understanding since the original CFHTLenS analyses were published.  In section~\ref{sec:theory} we clarify that only one/two? of the approximations highlighted by \citet{kitching/etal:2016} have actually been used in recent weak lensing analyses \citet{joudaki/etal:2016, hildebrandt/etal:2016, joudaki/etal:2017} and discuss why we do not expect these approximations to impact on the cosmological analysis of these surveys.    Finally in section~\ref{sec:photoz} we review our current knowledge of photometric redshift uncertainties and the sophisticated mitigation strategies that have already been applied to data from CFHTLenS, DES and KiDS.  We suggest that a possible misinterpretation in the direction of the redshift biases reported in \citet{choi/etal:2016} has lead to the incorrect conclusion of \citet{kitching/etal:2016} that these redshift biases can resolve the tension with Planck.

%-the analysis in the Kitching et al paper is fine, but the approximations used are not able to explain away the tension with Planck results, in contrast to the message the paper conveys.
%- we have verified that current (KiDS450) analyses are barely affected because they are restricted to larger scales
%- the CFHTLenS analysis used as an example has larger errors than the marginal error quoted in Kitching et al, and deviates less from Planck than most other results
%- the Limber and flat-sky approximations barely move this data point, so do not resolve even this tension
%- the discussion on photo-z uncertainties, where the uncertainty is characterized by a simple shift in the mean, is oversimplified and does not apply to more sophisticated treatment as used in latest results

\section{CFHTLenS:The Canada-France-Hawaii Telescope Lensing Survey}
\label{sec:cfhtlens}
\input{cfhtlens.tex}

\section{Theory}
\label{sec:theory}
\input{theory.tex}

\section{Photometric redshift bias and uncertainty}
\label{sec:photoz}
\input{photoz.tex}

\section{Conclusion}

\bibliographystyle{apj}
\bibliography{Limber_Comment}
\end{document}

### 2016-11-25 compile.sh

@@ -1,0 +1,5 @@
+pdflatex Limber_Comment.tex
+bibtex Limber_Comment
+pdflatex Limber_Comment.tex
+pdflatex Limber_Comment.tex
+

### 2016-11-25 Limber_Comment.tex
First draft at intro and cfhtlens section

@@
 (2016) examine the impact of four approximations that can be used when constraining cosmological parameters from the measurement of weak gravitational lensing by large-scale structures, also known as cosmic shear.
-We support the core important message of this paper that such approximations should not be used for the future analysis of high precision surveys such as Euclid, LSST and WFIRST.
+We support the core important message of this paper that the use of such approximations should be carefully considered in the future analysis of high precision surveys such as Euclid, LSST and WFIRST.
 In this comment, we argue that these approximations are not able to explain away the tension between the constraints from some current weak lensing surveys and Planck.
-Reducing uncertainty and characterising bias and in photometric redshift estimation is certainly a crucial task for the success of current and future surveys.
+Reducing uncertainty and characterising bias in photometric redshift estimation is certainly a crucial task for the success of current and future surveys.
 We highlight that sophisticated treatments of these uncertainties have already been explored in the literature and have been shown not to resolve the tension with Planck, in contrast to the message that Kitching et al.
@@
 In this comment paper we discuss four approximations that can be used when deriving theoretical predictions for the principally used cosmic shear statistic, $\xi_\pm$, the two-point shear correlation function.
-These approximations have been explored in (ADD REF) and most recently highlighted by \citet{kitching/etal:2016} as a way to reduce tensions between weak lensing and CMB experiments, focusing on a re-analysis of the non-tomographic weak lensing data from the CFHTLenS survey \citet{kilbinger/etal:2013}.
+These approximations have been explored in (ADD REF) and most recently highlighted by \citet{kitching/etal:2016} as a way to reduce tensions between weak lensing and CMB experiments, focusing on a re-analysis of the non-tomographic weak lensing data from the CFHTLenS survey \citep{kilbinger/etal:2013}.
 In section~\ref{sec:cfhtlens} we compare the `one-parameter' cosmological re-analysis of \citet{kitching/etal:2016} with the full six-parameter analysis by \citet{kilbinger/etal:2013}, arguing that this particular non-tomographic data set is not in significant tension with Planck.
@@
 In section~\ref{sec:theory} we clarify that only one/two?
-of the approximations highlighted by \citet{kitching/etal:2016} have actually been used in recent weak lensing analyses \citet{joudaki/etal:2016, hildebrandt/etal:2016, joudaki/etal:2017} and discuss why we do not expect these approximations to impact on the cosmological analysis of these surveys.
+of the approximations highlighted by \citet{kitching/etal:2016} have actually been used in recent weak lensing analyses \citep{joudaki/etal:2016, hildebrandt/etal:2016, joudaki/etal:2017} and discuss why we do not expect these approximations to impact on the cosmological analysis of these surveys.
 Finally in section~\ref{sec:photoz} we review our current knowledge of photometric redshift uncertainties and the sophisticated mitigation strategies that have already been applied to data from CFHTLenS, DES and KiDS.
@@
 
-\section{CFHTLenS:The Canada-France-Hawaii Telescope Lensing Survey}
+\section{Advances in understanding since CFHTLenS}
 \label{sec:cfhtlens}

### 2016-11-25 cfhtlens.tex
First draft at intro and cfhtlens section

The Canada-France-Hawaii Telescope Lensing Survey (CFHTLenS) represented a major step forward for the field of weak gravitational lensing, in terms of improved accuracy in data reduction \citep{erben/etal:2013}, the implementation of gaussianised matched multi-band photometry \citep{hildebrandt/etal:2012}, cross-correlation clustering analysis between photometric redshift slices to verify tomographic redshift distributions \citep{benjamin/etal:2013}, accurate shape measurements \citep{miller/etal:2013} and a full suite of informative systematic tests to select a clean data set \citep{heymans/etal:2012}.    Since the public release of this survey in 2013, the community has continued to scrutinise and advance our understanding of CFHTLenS by identifying a number of areas where the analysis could improve;
\begin{itemize}
\item{\citet{choi/etal:2016} identified biases in the tomographic photometric redshift distributions using a more effective clustering analysis, in comparison to \citet{benjamin/etal:2013}, by incorporating newly overlapping spectroscopy from the Sloan Digital Sky Survey.}
\item{\citet{asgari/etal:2016} used the stringent `COSEBI' statistic to identify significant non-lensing `B-mode' distortions when the CFHTLenS data was split into tomographic slices.}
\item{\citet{kuijken/etal:2015} showed that the CFHTLenS shear calibration corrections derived in \citet{miller/etal:2013} were underestimated as a result an imperfect match between the galaxy populations in the data and image simulations.}
\item{\citet{fenechconti/etal:2016} demonstrated that the CFHTLenS data would have been subject to a weight bias that favours galaxies that are more closely oriented with the point-spread function.}
\item{\citet{joudaki/etal:2016} updated the CFHTLenS covariance matrices using larger-box numerical simulations that were less subject to the lack power on large scales.}
\end{itemize}
Given this well publicised list of shortcomings with the original CFHTLenS results, it was surprising that \citet{kitching/etal:2016} chose to focus their study on the now outdated cosmic shear analysis of \citet{kilbinger/etal:2013}.  Furthermore, out of all the CFHTLenS cosmic shear results, the non-tomographic analysis of \citet{kilbinger/etal:2013} is the least in tension with Planck \citep[see for example][]{fu/etal:2014,abbott/etal:2016}, with $\sigma_8 (\Omega_m/0.3)^{0.5} = 0.738^{+0.055}_{-0.032}$, an agreement with Planck at $1.6 \sigma$.

\citet{kitching/etal:2016} choose to only vary $\sigma_8$ in their analysis, fixing all other parameters to Planck constraints.  They find a conditional value of $\sigma_8 = 0.789 \pm 0.015$ for their `standard analysis' which we review in Section~\ref{sec:theory}.    We argue that this artificial reduction in the error could easily mislead as it makes it appear that the impact of removing all approximations from the theoretical analysis is more significant for current surveys than it is in reality.

We conclude this section by noting that all the advances in understanding listed above were incorporated and accounted for in the recent KiDS cosmic shear analysis \citep{hildebrandt/etal:2016}.  The CFHTLenS tomographic cosmological analysis was also revisited by \citet{joudaki/etal:2016} in order to include a full redshift error analysis, as discussed in more detail in Section~\ref{sec:photoz}.  Efforts are now underway to fully re-analyse CFHTLenS using the advanced KiDS analysis pipeline with revised measurements and calibrations for the shear and photometric redshifts.

### 2016-11-25 conclusion.tex
First draft of photo-z section and conclusion

In this comment we have highlighted a number of shortcomings in the analysis presented in \cite{kitching/etal:2016}.  We argue that the flat sky and Limber approximations that can be used in cosmic shear analyses are not able to explain away the tension between weak lensing and Planck results, in contrast to the message that \cite{kitching/etal:2016} convey.  Our critique should not, however, detract from the extremely important core message of their paper, that future surveys will need to carefully consider these approximations and optimise their statistical analyses accordingly.  For example moving from the standard two-point shear correlation function statistic to the more stringent `COSEBI' statistic renders the cosmic shear measurement completely insensitive to the low-$\ell$ scales where these approximations become important \citep{schneider/etal:2010}.

### 2016-11-25 photoz.tex
First draft of photo-z section and conclusion

In \citet{choi/etal:2016} a cross-correlation clustering analysis, between photometric redshift slices and overlapping spectroscopic redshifts, is used to determine linear biases in the CFHTLenS photometric redshift distributions.   The maximum redshift $z_B<0.9$ in this analysis was limited by the redshift overlap with the spectroscopic sample  \citet{choi/etal:2016} found significant biases and concluded that any re-analysis of CFHTLenS should include systematic error terms to account for bias and scatter.    This re-analysis was presented in \citet{joudaki/etal:2016} where the impact of correcting for the biases determined by \citet{choi/etal:2016}, including their associated errors, served to reduce the overall constraining power of the survey and hence also the tension between constraints.  The best-fit model, however moved further from the Planck-preferred model, in agreement with the `toy-model' analysis of \citet{choi/etal:2016} which concluded that the effect of these biases would be to {\it reduce} the recovered amplitude of $\sigma_8$ by $\sim 4$\%.

\citet{choi/etal:2016} additionally showed that applying a simple linear shift to the photometric redshift distributions was insufficient when modelling the true underlying redshift distribution.  In \citet{hildebrandt/etal:2016}, a direct calibration method was used to determine the redshift distribution of four tomographic bins.  Multiple bootstrap samples of the resulting calibrated distribution allowed for the characterisation of both the uncertainty in the mean and shape of the redshift distribution.  The inclusion of this more sophisticated treatment of photometric redshift errors did not alleviate the tension between Planck and KiDS parameter constraints.

\cite{kitching/etal:2016} use a linear relation fit to the biases determined by \citet{choi/etal:2016} in order to extrapolate the results beyond the photometric redshift limit of $z_B<0.9$ and determine a bias at each redshift.  They then correct the non-tomographic \citet{kilbinger/etal:2013} redshift distribution with this bias relation.  They report that this correction results in an {\it increase} to the recovered amplitude of $\sigma_8$ by $\sim 4$\%, which resolves the tension with Planck.   We are unable to recover this conclusion using two different methods.   Based on the \cite{kitching/etal:2016} relation, the predicted shift at the mean CFHTLenS redshift $z=0.747$ is $\Delta_z = 0.056$, where we use the convention from \citet{choi/etal:2016} that a positive $\Delta_z$ serves to increase the overall mean redshift.  Using the same relation to individually shift each component of the full \citet{kilbinger/etal:2013} redshift histogram also results in a change to the mean redshift of $\Delta_z = 0.056$.  Increasing the mean redshift implies a reduction in the recovered amplitude of $\sigma_8$.  Using the same toy-model' analysis of \citet{choi/etal:2016} we would expect this change in the mean redshift to {\it reduce} the recovered amplitude of $\sigma_8$ by $\sim 5$\%.    From this we can only conclude that \cite{kitching/etal:2016} have misinterpreted the direction of the redshift biases reported in \citet{choi/etal:2016}.

### 2016-11-25 Limber_Comment.tex
First draft of photo-z section and conclusion
Full draft; TBD the theory section!

@@
 As such it is the primary science goal of several current (KiDS, HSC, DES) and future (Euclid, LSST, WFIRST) large-scale surveys.
-Interest in the results from these surveys is high as statistically significant tensions have been found between the cosmological parameter constraints from the CMB Planck experiment \citep{planck/cosmo:2015} in comparison to weak lensing constraints from both the Kilo-Degree Survey (KiDS) and the Canada-France-Hawaii Telescope Lensing Survey (CFHTLenS).
+Interest in the results from these surveys is high as statistically significant deviations have been found between the cosmological parameter constraints from the CMB Planck experiment \citep{planck/cosmo:2015} in comparison to weak lensing constraints from both the Kilo-Degree Survey \citep[KiDS;][]{hildebrandt/etal:2016} and the Canada-France-Hawaii Telescope Lensing Survey \citep[CFHTLenS;][] {joudaki/etal:2016}.
 If the source of this tension is not a result of so-far unconsidered sources of systematic errors in one or all experiments, extensions to the standard flat $\Lambda$CDM cosmological need to be considered.
@@
 of the approximations highlighted by \citet{kitching/etal:2016} have actually been used in recent weak lensing analyses \citep{joudaki/etal:2016, hildebrandt/etal:2016, joudaki/etal:2017} and discuss why we do not expect these approximations to impact on the cosmological analysis of these surveys.
-Finally in section~\ref{sec:photoz} we review our current knowledge of photometric redshift uncertainties and the sophisticated mitigation strategies that have already been applied to data from CFHTLenS, DES and KiDS.
+Finally in section~\ref{sec:photoz} we review our current knowledge of photometric redshift uncertainties and the sophisticated mitigation strategies that have already been applied to data.
 We suggest that a possible misinterpretation in the direction of the redshift biases reported in \citet{choi/etal:2016} has lead to the incorrect conclusion of \citet{kitching/etal:2016} that these redshift biases can resolve the tension with Planck.
@@
 \section{Conclusion}
+\label{sec:conclusion}
+\input{conclusion.tex}
 

### 2016-11-25 cfhtlens.tex
Full draft; TBD the theory section!

@@
 They find a conditional value of $\sigma_8 = 0.789 \pm 0.015$ for their `standard analysis' which we review in Section~\ref{sec:theory}.
-We argue that this artificial reduction in the error could easily mislead as it makes it appear that the impact of removing all approximations from the theoretical analysis is more significant for current surveys than it is in reality.
+We argue that this artificial reduction in the error could easily mislead, making it appear that the impact of removing all approximations from the theoretical analysis is more significant for current surveys than it is in reality.
 
-We conclude this section by noting that all the advances in understanding listed above were incorporated and accounted for in the recent KiDS cosmic shear analysis \citep{hildebrandt/etal:2016}.
+All the advances in understanding listed above were incorporated and accounted for in the recent KiDS cosmic shear analysis \citep{hildebrandt/etal:2016} which reports at $2.3 \sigma$ tension with Planck.
 The CFHTLenS tomographic cosmological analysis was also revisited by \citet{joudaki/etal:2016} in order to include a full redshift error analysis, as discussed in more detail in Section~\ref{sec:photoz}.

### 2016-11-25 conclusion.tex
Full draft; TBD the theory section!

@@
 In this comment we have highlighted a number of shortcomings in the analysis presented in \cite{kitching/etal:2016}.
-We argue that the flat sky and Limber approximations that can be used in cosmic shear analyses are not able to explain away the tension between weak lensing and Planck results, in contrast to the message that \cite{kitching/etal:2016} convey.
+We argue that the flat sky and Limber approximations that can be used in cosmic shear analyses are not able to explain away the tension between current weak lensing and Planck results, in contrast to the message that \cite{kitching/etal:2016} convey.
 Our critique should not, however, detract from the extremely important core message of their paper, that future surveys will need to carefully consider these approximations and optimise their statistical analyses accordingly.

### 2016-11-25 photoz.tex
Full draft; TBD the theory section!

@@
 In \citet{choi/etal:2016} a cross-correlation clustering analysis, between photometric redshift slices and overlapping spectroscopic redshifts, is used to determine linear biases in the CFHTLenS photometric redshift distributions.
-The maximum redshift $z_B<0.9$ in this analysis was limited by the redshift overlap with the spectroscopic sample  \citet{choi/etal:2016} found significant biases and concluded that any re-analysis of CFHTLenS should include systematic error terms to account for bias and scatter.
+The maximum redshift $z_B<0.9$ in this analysis was limited by the redshift overlap with the spectroscopic sample.
+\citet{choi/etal:2016} found significant biases and concluded that any re-analysis of CFHTLenS should include systematic error terms to account for bias and scatter.
 This re-analysis was presented in \citet{joudaki/etal:2016} where the impact of correcting for the biases determined by \citet{choi/etal:2016}, including their associated errors, served to reduce the overall constraining power of the survey and hence also the tension between constraints.
@@
 We are unable to recover this conclusion using two different methods.
-Based on the \cite{kitching/etal:2016} relation, the predicted shift at the mean CFHTLenS redshift $z=0.747$ is $\Delta_z = 0.056$, where we use the convention from \citet{choi/etal:2016} that a positive $\Delta_z$ serves to increase the overall mean redshift.
+Based on the \cite{kitching/etal:2016} relation, the predicted shift at the mean CFHTLenS redshift $z=0.747$ is $\Delta_z = 0.056$, where we use the convention from \citet{choi/etal:2016} that a positive $\Delta_z$ serves to increase the true mean redshift.
 Using the same relation to individually shift each component of the full \citet{kilbinger/etal:2013} redshift histogram also results in a change to the mean redshift of $\Delta_z = 0.056$.
@@
 Using the same toy-model' analysis of \citet{choi/etal:2016} we would expect this change in the mean redshift to {\it reduce} the recovered amplitude of $\sigma_8$ by $\sim 5$\%.
-From this we can only conclude that \cite{kitching/etal:2016} have misinterpreted the direction of the redshift biases reported in \citet{choi/etal:2016}.
+From this we suggest that \cite{kitching/etal:2016} could have misinterpreted the direction of the redshift biases reported in \citet{choi/etal:2016}.

### 2016-12-02 theory.tex
First draft theory section

\subsection{The Flat-Sky approximation and Extended Limber Approximation}
The baseline measurement for many cosmic shear studies has focused on the two-point shear correlation function between two tomographic bins $ij$ \citep[for more details see][and references therein]{bartelmann/schneider:2001}, given by
\be
\xi_\pm^{ij}(\theta) = \frac{1}{2\pi}\int \d\ell \,\ell \,P^{ij}_\kappa(\ell) \, J_{0,4}(\ell \theta) \, , 
\label{eqn:xiGG}
\ee
where $J_{0,4} (\ell \theta)$ is the zeroth (for $\xi_+$) or fourth (for $\xi_- $) order Bessel function of the first kind and $P_\kappa(\ell)$ is the convergence power spectrum at angular wave number $\ell$ which can be related to the underlying matter power spectrum $P_\delta$, using a Limber approximation, 
\be 
P^{ij}_\kappa(\ell) = T_l \int_0^{\chi_{\rm H}} \d \chi \, \frac{q_i(\chi)q_j(\chi)}{[f_K(\chi)]^2} \, P_\delta \left( \frac{\nu}{f_K(\chi)},\chi \right).
\label{eqn:Pkappa} 
\ee
Here $f_K(\chi)$ is the comoving angular diameter distance out to comoving radial distance $\chi$ and $\chi_{\rm H}$ is the horizon distance.  The lensing efficiency function $q(\chi)$ is given in equation (5) of \citet{hildebrandt/etal:2016}.   \citet{kitching/etal:2016} show that the pre-factor $T_\ell$ is given by
\be
T_\ell = \frac{(\ell+2)(\ell+1)\ell(\ell-1)}{(\ell + 0.5)^4} \, .
\label{eqn:Tl}
\ee
When a survey is sufficiently small, a flat-sky approximation can be made reducing $T_\ell \approx 1$.  $\nu$ depends on whether a baseline Limber approximation, or the more accurate extended Limber approximation of \citet{loverde/afshordi:2008} is used.  In the analysis of \citet{kitching/etal:2016} it is not fully clear which combinations of  $T_\ell$ and $\nu$ are considered, so we review them all as summarised in Table~\ref{tab:Tl_nu}, also highlighting which combinations were used in recent cosmic shear analyses.

\begin{table}
\label{tab:Tl_nu}
\begin{center}
\begin{tabular}{ | l | c | c  | c |}
\hline
Case & $T_\ell$ & $\nu$ & Used in \\ \hline
\citet{kitching/etal:2016} `Standard' & $1$ & $\ell$ & pre-2014 CFHTLenS papers \\
Baseline Limber Flat Sky &  $\ell^4 / (\ell + 0.5)^4$ & $\ell$ & \\
Baseline Limber Spherical & equation~\ref{eqn:Tl} & $\ell$ & \\
Extended Limber Flat Sky & $\ell^4 / (\ell + 0.5)^4$ & $\ell + 0.5$ & \\
Extended Limber Spherical & equation~\ref{eqn:Tl}& $\ell + 0.5$  & \\
Extended `Standard' & $1$ & $\ell + 0.5$ & \citet{joudaki/etal:2016} \&  \\
  & & & \citet{hildebrandt/etal:2016}  \\\hline
 \end{tabular}
 \end{center}
 \caption{Variations on the different approximations that can be made when calculating the convergence power spectrum $P_\kappa(\ell)$ (equation~\ref{eqn:Pkappa}), using a Limber approximation.}
 \end{table}

{\bf TBD: add figures of $P_\kappa$ and $\xi_/pm$ for all these combinations showing that they make no difference.}

 \subsection{Cosmic shear without the Limber Approximation}
In collecting our comments on \citet{kitching/etal:2016} we contacted colleagues who had previously tested the impact of the Limber approximation on cosmic shear studies by comparing a Limber approximated cosmic shear power spectrum with an exact calculation.  The majority of these analyses, carried out many years ago, remained unpublished as no significant deviation was found.  One notable exception, however, is \citet{giannantonio/etal:2012} who find that for a cosmic shear power spectrum, the extended Limber approximation is consistent with the exact calculation for $\ell>5$, with any differences well within cosmic-variance errors for a Euclid-like survey\footnote{\citet{kitching/etal:2016} comment on this result, but indicate that it is in error owing to the application of a fixed low-$\ell$ limit.  \citet{giannantonio/etal:2012} however state that this limit is only applied in a positive curvature case.}.  We therefore argue that the assertion by \citet{kitching/etal:2016} that the majority of data analyses to date have made an `axiomatic assumption (i.e. an unquestioned and untested assumption at the beginning of the analysis)'  is unwarranted.  Not only is there published work that has questioned and tested the Limber approximation for cosmic shear studies, individual teams have also verified this result internally.

Given the insignificant effect of using the Limber approximation found by various groups, this ability to calculate an exact non-Limber solution has not been maintained in theoretical code over the years.  Instead these codes have evolved to account for important approximations such as the impact of baryon feedback on the matter power spectrum and non-zero neutrino masses \citep[see for example][]{joudaki/etal:2016, mead/etal:2016}.    We are therefore unable to readily determine non-Limber theoretical calculations for the shear-correlation function to directly compare with the results of \citet{kitching/etal:2016}.   Instead we refer the reader to Figure 3 of \citet{giannantonio/etal:2012} to draw their own conclusions.

### 2016-12-02 Limber_Comment.tex
Re-arranging sections so theory comes first

@@
 
-\author{Members of the KiDS, DES, HSC, CFHTLenS and RCSLenS collaborations\altaffilmark{1} ....}
+\author{Members of the KiDS, CFHTLenS and RCSLenS collaborations\altaffilmark{1} ....}
 %\email{tbd@tbd}
 
-\altaffiltext{1}{Aim is for representatives from each survey to sign}
+%\altaffiltext{1}{}
 
@@
 Kitching et al.
-(2016) examine the impact of four approximations that can be used when constraining cosmological parameters from the measurement of weak gravitational lensing by large-scale structures, also known as cosmic shear.
-We support the core important message of this paper that the use of such approximations should be carefully considered in the future analysis of high precision surveys such as Euclid, LSST and WFIRST.
-In this comment, we argue that these approximations are not able to explain away the tension between the constraints from some current weak lensing surveys and Planck.
-Reducing uncertainty and characterising bias in photometric redshift estimation is certainly a crucial task for the success of current and future surveys.
+(2016) examine the impact of the flat-sky and Limber approximations that can be used when constraining cosmological parameters from the measurement of weak gravitational lensing by large-scale structures, also known as cosmic shear.
+We support the core message of this paper that the use of such approximations should be considered in the future analysis of high precision surveys such as Euclid, LSST and WFIRST.
+In this comment, we argue that these approximations have negligible impact for current surveys and are not able to explain away the tension between the constraints from some current weak lensing surveys and Planck.
+Reducing uncertainty and characterising bias in photometric redshift estimation a critical task for the success of current and future surveys.
 We highlight that sophisticated treatments of these uncertainties have already been explored in the literature and have been shown not to resolve the tension with Planck, in contrast to the message that Kitching et al.
@@
 
-In this comment paper we discuss four approximations that can be used when deriving theoretical predictions for the principally used cosmic shear statistic, $\xi_\pm$, the two-point shear correlation function.
-These approximations have been explored in (ADD REF) and most recently highlighted by \citet{kitching/etal:2016} as a way to reduce tensions between weak lensing and CMB experiments, focusing on a re-analysis of the non-tomographic weak lensing data from the CFHTLenS survey \citep{kilbinger/etal:2013}.
-In section~\ref{sec:cfhtlens} we compare the `one-parameter' cosmological re-analysis of \citet{kitching/etal:2016} with the full six-parameter analysis by \citet{kilbinger/etal:2013}, arguing that this particular non-tomographic data set is not in significant tension with Planck.
+In this comment paper we discuss the flat sky and Limber approximations that can be used when deriving theoretical predictions for the principally used cosmic shear statistic, $\xi_\pm$, the two-point shear correlation function.
+The Limber approximation for cosmic shear has been previously explored by \citet{giannantonio/etal:2012} finding that it provided sufficient accuracy for future cosmic shear studies.
+Recently \citet{kitching/etal:2016} highlighted that considering the flat sky and Limber approximations in concert can reduce tensions between weak lensing and CMB experiments, focusing on a re-analysis of the non-tomographic weak lensing data from the CFHTLenS survey \citep{kilbinger/etal:2013}.
+
+In section~\ref{sec:theory} we clarify that which brand of approximations highlighted by \citet{kitching/etal:2016} have been used in recent weak lensing analyses \citep{joudaki/etal:2016, hildebrandt/etal:2016, joudaki/etal:2017} and show that we are unable to re-produce their conclusions.
+We therefore do not expect these approximations to impact on the cosmological analysis of current surveys.
+In section~\ref{sec:cfhtlens} we compare the `one-parameter' cosmological re-analysis of \citet{kitching/etal:2016} with the full six-parameter analysis by \citet{kilbinger/etal:2013}, arguing that this particular non-tomographic data set was never in significant tension with Planck.
 We also briefly review the literature that has advanced our understanding since the original CFHTLenS analyses were published.
-In section~\ref{sec:theory} we clarify that only one/two?
-of the approximations highlighted by \citet{kitching/etal:2016} have actually been used in recent weak lensing analyses \citep{joudaki/etal:2016, hildebrandt/etal:2016, joudaki/etal:2017} and discuss why we do not expect these approximations to impact on the cosmological analysis of these surveys.
+
 Finally in section~\ref{sec:photoz} we review our current knowledge of photometric redshift uncertainties and the sophisticated mitigation strategies that have already been applied to data.
@@
 
-%-the analysis in the Kitching et al paper is fine, but the approximations used are not able to explain away the tension with Planck results, in contrast to the message the paper conveys.
-%- we have verified that current (KiDS450) analyses are barely affected because they are restricted to larger scales
-%- the CFHTLenS analysis used as an example has larger errors than the marginal error quoted in Kitching et al, and deviates less from Planck than most other results
-%- the Limber and flat-sky approximations barely move this data point, so do not resolve even this tension
-%- the discussion on photo-z uncertainties, where the uncertainty is characterized by a simple shift in the mean, is oversimplified and does not apply to more sophisticated treatment as used in latest results
+\section{Theory}
+\label{sec:theory}
+\input{theory.tex}
 
@@
 \input{cfhtlens.tex}
-
-\section{Theory}
-\label{sec:theory}
-\input{theory.tex}
 

### 2016-12-02 theory.tex
Re-arranging sections so theory comes first

@@
 
-\begin{table}
+ \begin{table}[htb]
 \label{tab:Tl_nu}
@@
 Extended `Standard' & $1$ & $\ell + 0.5$ & \citet{joudaki/etal:2016} \&  \\
-  & & & \citet{hildebrandt/etal:2016}  \\\hline
+  & & & \citet{hildebrandt/etal:2016}$^*$\\\hline
  \end{tabular}
  \end{center}
- \caption{Variations on the different approximations that can be made when calculating the convergence power spectrum $P_\kappa(\ell)$ (equation~\ref{eqn:Pkappa}), using a Limber approximation.}
+ \caption{Variations on the different approximations that can be made when calculating the convergence power spectrum $P_\kappa(\ell)$ (equation~\ref{eqn:Pkappa}), using a Limber approximation.
+$^*$We confirm that there is a typographical error in equation 4 of \citet{hildebrandt/etal:2016} which does not include the extra factor of 0.5 in $\nu$ that was incorporated in the cosmological analysis.}
  \end{table}

### 2016-12-02 cfhtlens.tex
updated with XXX for SJ to fill in :)

--- 2016-11-25 cfhtlens.tex
@@
 \begin{itemize}
-\item{\citet{choi/etal:2016} identified biases in the tomographic photometric redshift distributions using a more effective clustering analysis, in comparison to \citet{benjamin/etal:2013}, by incorporating newly overlapping spectroscopy from the Sloan Digital Sky Survey.}
+\item{\citet{choi/etal:2016} identified biases in the tomographic photometric redshift distributions using a more effective clustering analysis, in comparison to \citet{benjamin/etal:2013}, by incorporating newly overlapping spectroscopy from the Sloan Digital Sky Survey.
+The CFHTLenS tomographic cosmological analysis was then revisited by \citet{joudaki/etal:2016} in order to include a full redshift error analysis based on the results from \citet{choi/etal:2016}, as discussed in more detail in Section~\ref{sec:photoz}}
 \item{\citet{asgari/etal:2016} used the stringent `COSEBI' statistic to identify significant non-lensing `B-mode' distortions when the CFHTLenS data was split into tomographic slices.}
@@
 \end{itemize}
-Given this well publicised list of shortcomings with the original CFHTLenS results, it was surprising that \citet{kitching/etal:2016} chose to focus their study on the now outdated cosmic shear analysis of \citet{kilbinger/etal:2013}.
-Furthermore, out of all the CFHTLenS cosmic shear results, the non-tomographic analysis of \citet{kilbinger/etal:2013} is the least in tension with Planck \citep[see for example][]{fu/etal:2014,abbott/etal:2016}, with $\sigma_8 (\Omega_m/0.3)^{0.5} = 0.738^{+0.055}_{-0.032}$, an agreement with Planck at $1.6 \sigma$.
+All these advances in our understanding were incorporated and accounted for in the recent KiDS cosmic shear analysis \citep{hildebrandt/etal:2016} which reports at $2.3 \sigma$ tension with Planck.
+Efforts are now underway to fully re-analyse CFHTLenS using the advanced KiDS analysis pipeline with revised shape measurements and calibrations for the shear and photometric redshifts.
+
+Given the known shortcomings with the original CFHTLenS results, which will impact in different ways on the cosmological conclusions one can draw from the survey, it is surprising that \citet{kitching/etal:2016} chose to focus their study on the cosmic shear analysis of \citet{kilbinger/etal:2013}.
+This is also unexpected as, out of all the CFHTLenS cosmic shear results, the non-tomographic analysis of \citet{kilbinger/etal:2013} is the least in tension with Planck \citep[see for example][who show that with $\sigma_8 (\Omega_m/0.3)^{0.5} = 0.738^{+0.055}_{-0.032}$, \citet{kilbinger/etal:2013} is in agreement with Planck at $1.6 \sigma$]{abbott/etal:2016}.
 
 \citet{kitching/etal:2016} choose to only vary $\sigma_8$ in their analysis, fixing all other parameters to Planck constraints.
-They find a conditional value of $\sigma_8 = 0.789 \pm 0.015$ for their `standard analysis' which we review in Section~\ref{sec:theory}.
-We argue that this artificial reduction in the error could easily mislead as it makes it appear that the impact of removing all approximations from the theoretical analysis is more significant for current surveys than it is in reality.
+They find a conditional value of $\sigma_8 = 0.789 \pm 0.015$ for their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}).
+We argue that this artificial reduction in the error by a factor of $\sim 3$ could easily mislead, making it appear that the impact of removing all approximations from the theoretical analysis is more significant for current surveys than it is in reality.
 
-We conclude this section by noting that all the advances in understanding listed above were incorporated and accounted for in the recent KiDS cosmic shear analysis \citep{hildebrandt/etal:2016}.
-The CFHTLenS tomographic cosmological analysis was also revisited by \citet{joudaki/etal:2016} in order to include a full redshift error analysis, as discussed in more detail in Section~\ref{sec:photoz}.
-Efforts are now underway to fully re-analyse CFHTLenS using the advanced KiDS analysis pipeline with revised measurements and calibrations for the shear and photometric redshifts.
+We repeated the `one-parameter' analysis for the full range of Limber cases listed in Table~\ref{tab:Tl_nu} finding the lowest conditional value of $\sigma_8 = XXX \pm XXX$ for the XXX case and the highest conditional value of $\sigma_8 = XXX \pm XXX$ for the XXX case.
+As expected from the comparison in Figure~\ref{fig:Cl_xi} the different combinations of assuming flat or spherical sky, or baseline of extended Limber make very little difference to the cosmological parameter constraints, even in this exaggerated `one-parameter' analysis.
+
+Our findings are in disagreement with \citet{kitching/etal:2016} who find a shift of $\Delta \sigma_8 = 0.007$ between their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) and their `Limber' analysis (which we believe corresponds to
+the Extended Limber spherical case in Table~\ref{tab:Tl_nu}).
+
+\subsection{Comparison of two-point shear statistics; the two-point correlation function, mass aperture statistic and COSEBIS}
+\citet{kilbinger/etal:2013} present the most detailed comparison to date of constraints from a range different two-point shear statistics.

### 2016-12-02 cfhtlens.tex
Now with section 3.1 on the comparison of xi, map and COSEBIS

@@
 
-Our findings are in disagreement with \citet{kitching/etal:2016} who find a shift of $\Delta \sigma_8 = 0.007$ between their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) and their `Limber' analysis (which we believe corresponds to
-the Extended Limber spherical case in Table~\ref{tab:Tl_nu}).
+Our Limber-case findings are therefore in disagreement with \citet{kitching/etal:2016} who find a shift of $\Delta \sigma_8 = 0.007$ between their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) and their `Limber' analysis (which we believe corresponds to the Extended Limber spherical case in Table~\ref{tab:Tl_nu}).
 
 \subsection{Comparison of two-point shear statistics; the two-point correlation function, mass aperture statistic and COSEBIS}
-\citet{kilbinger/etal:2013} present the most detailed comparison to date of constraints from a range different two-point shear statistics.
+\citet{kilbinger/etal:2013} present a detailed comparison of cosmological constraints obtained from a range different two-point shear statistics including the shear correlation function, $\xi_\pm$, the mass aperture statistic, $M_ {\rm ap}^2$ \citep{schneider/etal:1998}, and the COSEBIs statistics \citep{schneider/etal:2010}.
+As shown by each statistic's weight function in figure~\ref{fig:filters}, these two-point cosmic shear statistics exhibit different dependences between the angular scales sampled and the $\ell$-range probed.
+If a significant bias had been introduced at low-$\ell$ by using flat-sky and Limber approximations, we would then expect to see a systematic shift between the different two-point statistics with the COSEBI statistic being completely unaffected as it only includes modes with $\ell \gtrsim 80$.
+This is found not to be the case with all three statistics finding $\sigma_8 (\Omega_m/0.27)^\alpha = 0.79$ with errors than range from $0.03$ to $0.06$ \citep[see Table 5 of][]{kilbinger/etal:2013}.
+This comparison further supports our argument that the approximations highlighted by \citet{kitching/etal:2016} have negligible impact for current surveys.
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=0.5\textwidth]{figures/ellWnPell1-100.pdf}
+\caption{ \label{fig:filters}.  Currently just COSEBIS, will also have $\xi_\pm$ and $M_{\rm ap}^2$.}
+\end{center}
+\end{figure}

### 2016-12-02 conclusion.tex
Now with section 3.1 on the comparison of xi, map and COSEBIS

@@
 We argue that the flat sky and Limber approximations that can be used in cosmic shear analyses are not able to explain away the tension between current weak lensing and Planck results, in contrast to the message that \cite{kitching/etal:2016} convey.
-Our critique should not, however, detract from the extremely important core message of their paper, that future surveys will need to carefully consider these approximations and optimise their statistical analyses accordingly.
-For example moving from the standard two-point shear correlation function statistic to the more stringent `COSEBI' statistic renders the cosmic shear measurement completely insensitive to the low-$\ell$ scales where these approximations become important \citep{schneider/etal:2010}.
+Our critique should not, however, detract from the important core message of their paper, that future surveys will need to consider these approximations and optimise their statistical analyses accordingly.
+For example moving from the standard two-point shear correlation function statistic to the more stringent `COSEBI' statistic \citep{schneider/etal:2010} renders the cosmic shear measurement completely insensitive to the low-$\ell$ scales where these approximations become important.

### 2016-12-02 Limber_Comment.tex
small text changes after full read through

@@
 The Limber approximation for cosmic shear has been previously explored by \citet{giannantonio/etal:2012} finding that it provided sufficient accuracy for future cosmic shear studies.
-Recently \citet{kitching/etal:2016} highlighted that considering the flat sky and Limber approximations in concert can reduce tensions between weak lensing and CMB experiments, focusing on a re-analysis of the non-tomographic weak lensing data from the CFHTLenS survey \citep{kilbinger/etal:2013}.
+Recently, however, \citet{kitching/etal:2016} reported that when considering the flat sky and Limber approximations in concert, tensions between weak lensing and CMB experiments can be reduced.
+This was demonstrated with a re-analysis of the non-tomographic weak lensing data from the CFHTLenS survey \citep{kilbinger/etal:2013}.
 
-In section~\ref{sec:theory} we clarify that which brand of approximations highlighted by \citet{kitching/etal:2016} have been used in recent weak lensing analyses \citep{joudaki/etal:2016, hildebrandt/etal:2016, joudaki/etal:2017} and show that we are unable to re-produce their conclusions.
-We therefore do not expect these approximations to impact on the cosmological analysis of current surveys.
-In section~\ref{sec:cfhtlens} we compare the `one-parameter' cosmological re-analysis of \citet{kitching/etal:2016} with the full six-parameter analysis by \citet{kilbinger/etal:2013}, arguing that this particular non-tomographic data set was never in significant tension with Planck.
+This comment is structured as follows.
+In section~\ref{sec:theory} we clarify which brand of approximations, highlighted by \citet{kitching/etal:2016}, have been used in recent weak lensing analyses \citep{joudaki/etal:2016, hildebrandt/etal:2016, joudaki/etal:2017}.
+We show that we are unable to replicate key results from \citet{kitching/etal:2016} and therefore do not expect these approximations to impact on the cosmological analysis of current surveys.
+In section~\ref{sec:cfhtlens} we compare the `one-parameter' cosmological re-analysis of \citet{kitching/etal:2016} with the full six-parameter analysis by \citet{kilbinger/etal:2013}, arguing that this particular non-tomographic data set is not in significant tension with Planck.
 We also briefly review the literature that has advanced our understanding since the original CFHTLenS analyses were published.
 
-Finally in section~\ref{sec:photoz} we review our current knowledge of photometric redshift uncertainties and the sophisticated mitigation strategies that have already been applied to data.
+In section~\ref{sec:photoz} we review our current knowledge of photometric redshift uncertainties and the sophisticated mitigation strategies that have already been applied to data.
 We suggest that a possible misinterpretation in the direction of the redshift biases reported in \citet{choi/etal:2016} has lead to the incorrect conclusion of \citet{kitching/etal:2016} that these redshift biases can resolve the tension with Planck.

### 2016-12-02 cfhtlens.tex
small text changes after full read through

@@
-The Canada-France-Hawaii Telescope Lensing Survey (CFHTLenS) represented a major step forward for the field of weak gravitational lensing, in terms of improved accuracy in data reduction \citep{erben/etal:2013}, the implementation of gaussianised matched multi-band photometry \citep{hildebrandt/etal:2012}, cross-correlation clustering analysis between photometric redshift slices to verify tomographic redshift distributions \citep{benjamin/etal:2013}, accurate shape measurements \citep{miller/etal:2013} and a full suite of informative systematic tests to select a clean data set \citep{heymans/etal:2012}.
+The Canada-France-Hawaii Telescope Lensing Survey (CFHTLenS) represented a major step forward for the field of weak gravitational lensing, in terms of improved accuracy in data reduction \citep{erben/etal:2013}, the implementation of gaussianised matched multi-band photometry \citep{hildebrandt/etal:2012}, cross-correlation clustering analysis between photometric redshift slices to verify tomographic redshift distributions \citep{benjamin/etal:2013}, accurate calibrated shape measurements \citep{miller/etal:2013} and a full suite of informative systematic tests to select a clean data set \citep{heymans/etal:2012}.
 Since the public release of this survey in 2013, the community has continued to scrutinise and advance our understanding of CFHTLenS by identifying a number of areas where the analysis could improve;
@@
 \item{\citet{choi/etal:2016} identified biases in the tomographic photometric redshift distributions using a more effective clustering analysis, in comparison to \citet{benjamin/etal:2013}, by incorporating newly overlapping spectroscopy from the Sloan Digital Sky Survey.
-The CFHTLenS tomographic cosmological analysis was then revisited by \citet{joudaki/etal:2016} in order to include a full redshift error analysis based on the results from \citet{choi/etal:2016}, as discussed in more detail in Section~\ref{sec:photoz}}
+The CFHTLenS tomographic cosmological analysis was then revisited by \citet{joudaki/etal:2016} in order to include a full redshift error analysis based on the results from \citet{choi/etal:2016}, discussed further in section~\ref{sec:photoz}.}
 \item{\citet{asgari/etal:2016} used the stringent `COSEBI' statistic to identify significant non-lensing `B-mode' distortions when the CFHTLenS data was split into tomographic slices.}
 \item{\citet{kuijken/etal:2015} showed that the CFHTLenS shear calibration corrections derived in \citet{miller/etal:2013} were underestimated as a result an imperfect match between the galaxy populations in the data and image simulations.}
-\item{\citet{fenechconti/etal:2016} demonstrated that the CFHTLenS data would have been subject to a weight bias that favours galaxies that are more closely oriented with the point-spread function.}
+\item{\citet{fenechconti/etal:2016} demonstrated that the CFHTLenS data would have been subject to a weight bias that favours galaxies that are more intrinsically oriented with the point-spread function.}
 \item{\citet{joudaki/etal:2016} updated the CFHTLenS covariance matrices using larger-box numerical simulations that were less subject to the lack power on large scales.}
@@
 
-Given the known shortcomings with the original CFHTLenS results, which will impact in different ways on the cosmological conclusions one can draw from the survey, it is surprising that \citet{kitching/etal:2016} chose to focus their study on the cosmic shear analysis of \citet{kilbinger/etal:2013}.
-This is also unexpected as, out of all the CFHTLenS cosmic shear results, the non-tomographic analysis of \citet{kilbinger/etal:2013} is the least in tension with Planck \citep[see for example][who show that with $\sigma_8 (\Omega_m/0.3)^{0.5} = 0.738^{+0.055}_{-0.032}$, \citet{kilbinger/etal:2013} is in agreement with Planck at $1.6 \sigma$]{abbott/etal:2016}.
+Given the known shortcomings with the original CFHTLenS results, which will impact in different ways on the cosmological conclusions that one can draw from the survey, it is surprising that \citet{kitching/etal:2016} chose to focus their study on the cosmic shear analysis of \citet{kilbinger/etal:2013}.
+This is even more unexpected as, out of all the CFHTLenS cosmic shear results, the non-tomographic analysis of \citet{kilbinger/etal:2013} is the least in tension with Planck \citep[see for example][who show that with $\sigma_8 (\Omega_m/0.3)^{0.5} = 0.738^{+0.055}_{-0.032}$, \citet{kilbinger/etal:2013} is in agreement with Planck at $1.6 \sigma$]{abbott/etal:2016}.
 
 \citet{kitching/etal:2016} choose to only vary $\sigma_8$ in their analysis, fixing all other parameters to Planck constraints.
-They find a conditional value of $\sigma_8 = 0.789 \pm 0.015$ for their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}).
+They find a conditional value of $\sigma_8 = 0.789 \pm 0.015$ for their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) of the data from \citet{kilbinger/etal:2013}.
 We argue that this artificial reduction in the error by a factor of $\sim 3$ could easily mislead, making it appear that the impact of removing all approximations from the theoretical analysis is more significant for current surveys than it is in reality.
@@
 We repeated the `one-parameter' analysis for the full range of Limber cases listed in Table~\ref{tab:Tl_nu} finding the lowest conditional value of $\sigma_8 = XXX \pm XXX$ for the XXX case and the highest conditional value of $\sigma_8 = XXX \pm XXX$ for the XXX case.
-As expected from the comparison in Figure~\ref{fig:Cl_xi} the different combinations of assuming flat or spherical sky, or baseline of extended Limber make very little difference to the cosmological parameter constraints, even in this exaggerated `one-parameter' analysis.
+As expected from the comparison in Figure~\ref{fig:Cl_xi} the different combinations of assuming flat or spherical sky, or baseline of extended Limber make little difference to the cosmological parameter constraints, even in this exaggerated `one-parameter' analysis.
 
@@
 As shown by each statistic's weight function in figure~\ref{fig:filters}, these two-point cosmic shear statistics exhibit different dependences between the angular scales sampled and the $\ell$-range probed.
-If a significant bias had been introduced at low-$\ell$ by using flat-sky and Limber approximations, we would then expect to see a systematic shift between the different two-point statistics with the COSEBI statistic being completely unaffected as it only includes modes with $\ell \gtrsim 80$.
-This is found not to be the case with all three statistics finding $\sigma_8 (\Omega_m/0.27)^\alpha = 0.79$ with errors than range from $0.03$ to $0.06$ \citep[see Table 5 of][]{kilbinger/etal:2013}.
+If a significant bias had been introduced at low-$\ell$ by using flat-sky and Limber approximations, we would then expect to see a systematic shift between the different two-point statistics with the COSEBI statistic being essentially unaffected as it only includes modes with $\ell \gtrsim 80$.
+This is found not to be the case with all three statistics finding $\sigma_8 (\Omega_m/0.27)^\alpha = 0.79$ with errors that range from $0.03$ to $0.06$ \citep[see Table 5 of][]{kilbinger/etal:2013}.
 This comparison further supports our argument that the approximations highlighted by \citet{kitching/etal:2016} have negligible impact for current surveys.

### 2016-12-02 photoz.tex
small text changes after full read through

@@
 The maximum redshift $z_B<0.9$ in this analysis was limited by the redshift overlap with the spectroscopic sample.
-\citet{choi/etal:2016} found significant biases and concluded that any re-analysis of CFHTLenS should include systematic error terms to account for bias and scatter.
+\citet{choi/etal:2016} found significant biases in the redshift distributions used in the original CFHTLenS analyses,
+concluding that any re-analysis of CFHTLenS should include systematic error terms to account for bias and scatter.
 This re-analysis was presented in \citet{joudaki/etal:2016} where the impact of correcting for the biases determined by \citet{choi/etal:2016}, including their associated errors, served to reduce the overall constraining power of the survey and hence also the tension between constraints.

### 2016-12-02 theory.tex
theory.tex update
updated with XXX for SJ to fill in :)
small text changes after full read through

@@
 \ee
-where $J_{0,4} (\ell \theta)$ is the zeroth (for $\xi_+$) or fourth (for $\xi_- $) order Bessel function of the first kind and $P_\kappa(\ell)$ is the convergence power spectrum at angular wave number $\ell$ which can be related to the underlying matter power spectrum $P_\delta$, using a Limber approximation,
+where $J_{0,4} (\ell \theta)$ is the zeroth (for $\xi_+$) or fourth (for $\xi_- $) order Bessel function of the first kind and $P_\kappa(\ell)$ is the convergence power spectrum at angular wave number $\ell$ which can be related to the underlying matter power spectrum $P_\delta$, using a Limber approximation as,
 \be 
@@
 When a survey is sufficiently small, a flat-sky approximation can be made reducing $T_\ell \approx 1$.
-$\nu$ depends on whether a baseline Limber approximation, or the more accurate extended Limber approximation of \citet{loverde/afshordi:2008} is used.
+The value of $\nu$ depends on whether a baseline Limber approximation, or the more accurate extended Limber approximation of \citet{loverde/afshordi:2008} is used.
 In the analysis of \citet{kitching/etal:2016} it is not fully clear which combinations of  $T_\ell$ and $\nu$ are considered, so we review them all as summarised in Table~\ref{tab:Tl_nu}, also highlighting which combinations were used in recent cosmic shear analyses.
@@
 
-{\bf TBD: add figures of $P_\kappa$ and $\xi_/pm$ for all these combinations showing that they make no difference.}
+{\bf TBD: add figures of $P_\kappa$ and $\xi_\pm$ for all these combinations showing that they make absolutely no difference.}
+
+ \begin{figure}
+ \label{fig:Cl_xi}
+ \caption{Will show $P_\kappa$ and $\xi_\pm$, TBD}
+ \end{figure}
 
@@
 \citet{giannantonio/etal:2012} however state that this limit is only applied in a positive curvature case.}.
-We therefore argue that the assertion by \citet{kitching/etal:2016} that the majority of data analyses to date have made an `axiomatic assumption (i.e.
+We therefore argue that the assertion by \citet{kitching/etal:2016} that the majority of cosmic shear data analyses to date have made an `axiomatic assumption (i.e.
 an unquestioned and untested assumption at the beginning of the analysis)'  is unwarranted.
@@
 
-Given the insignificant effect of using the Limber approximation found by various groups, this ability to calculate an exact non-Limber solution has not been maintained in theoretical code over the years.
+Given the insignificant effect of using the Limber approximation found by various groups, the ability to calculate an exact non-Limber solution has unfortunately not been maintained in theoretical code over the years.
 Instead these codes have evolved to account for important approximations such as the impact of baryon feedback on the matter power spectrum and non-zero neutrino masses \citep[see for example][]{joudaki/etal:2016, mead/etal:2016}.

### 2016-12-02 Limber_Comment.tex
Fixed typos.

@@
 (2016) examine the impact of the flat-sky and Limber approximations that can be used when constraining cosmological parameters from the measurement of weak gravitational lensing by large-scale structures, also known as cosmic shear.
-We support the core message of this paper that the use of such approximations should be considered in the future analysis of high precision surveys such as Euclid, LSST and WFIRST.
+We support the core message of this paper that the use of such approximations should be considered in the future analyses of high precision surveys such as Euclid, LSST and WFIRST.
 In this comment, we argue that these approximations have negligible impact for current surveys and are not able to explain away the tension between the constraints from some current weak lensing surveys and Planck.
-Reducing uncertainty and characterising bias in photometric redshift estimation a critical task for the success of current and future surveys.
+Reducing uncertainty and characterising bias in photometric redshift estimation is a critical task for the success of current and future surveys.
 We highlight that sophisticated treatments of these uncertainties have already been explored in the literature and have been shown not to resolve the tension with Planck, in contrast to the message that Kitching et al.

### 2016-12-02 theory.tex
Minor edit.

@@
 \ee
-Here $f_K(\chi)$ is the comoving angular diameter distance out to comoving radial distance $\chi$ and $\chi_{\rm H}$ is the horizon distance.
+Here $f_K(\chi)$ is the comoving angular diameter distance out to comoving radial distance $\chi$ and $\chi_{\rm H}$ is the comoving horizon distance.
 The lensing efficiency function $q(\chi)$ is given in equation (5) of \citet{hildebrandt/etal:2016}.
@@
  \caption{Variations on the different approximations that can be made when calculating the convergence power spectrum $P_\kappa(\ell)$ (equation~\ref{eqn:Pkappa}), using a Limber approximation.
-$^*$We confirm that there is a typographical error in equation 4 of \citet{hildebrandt/etal:2016} which does not include the extra factor of 0.5 in $\nu$ that was incorporated in the cosmological analysis.}
+$^*$We confirm that there is a typographical error in equation 4 of \citet{hildebrandt/etal:2016} which does not include the extra term of `$+0.5$' in $\nu$ that was incorporated in the cosmological analysis.}
  \end{table}

### 2016-12-02 cfhtlens.tex
Minor edit.

@@
 The Canada-France-Hawaii Telescope Lensing Survey (CFHTLenS) represented a major step forward for the field of weak gravitational lensing, in terms of improved accuracy in data reduction \citep{erben/etal:2013}, the implementation of gaussianised matched multi-band photometry \citep{hildebrandt/etal:2012}, cross-correlation clustering analysis between photometric redshift slices to verify tomographic redshift distributions \citep{benjamin/etal:2013}, accurate calibrated shape measurements \citep{miller/etal:2013} and a full suite of informative systematic tests to select a clean data set \citep{heymans/etal:2012}.
-Since the public release of this survey in 2013, the community has continued to scrutinise and advance our understanding of CFHTLenS by identifying a number of areas where the analysis could improve;
+Since the public release of this survey in 2013, the community has continued to scrutinise and advance our understanding of CFHTLenS by identifying a number of areas where the analysis could improve:
 \begin{itemize}
@@
 \item{\citet{asgari/etal:2016} used the stringent `COSEBI' statistic to identify significant non-lensing `B-mode' distortions when the CFHTLenS data was split into tomographic slices.}
-\item{\citet{kuijken/etal:2015} showed that the CFHTLenS shear calibration corrections derived in \citet{miller/etal:2013} were underestimated as a result an imperfect match between the galaxy populations in the data and image simulations.}
+\item{\citet{kuijken/etal:2015} showed that the CFHTLenS shear calibration corrections derived in \citet{miller/etal:2013} were underestimated as a result of an imperfect match between the galaxy populations in the data and image simulations.}
 \item{\citet{fenechconti/etal:2016} demonstrated that the CFHTLenS data would have been subject to a weight bias that favours galaxies that are more intrinsically oriented with the point-spread function.}

### 2016-12-04 conclusion.tex
Added a comment.
Added a conclusion paragraph about photo-z.

@@
 For example moving from the standard two-point shear correlation function statistic to the more stringent `COSEBI' statistic \citep{schneider/etal:2010} renders the cosmic shear measurement completely insensitive to the low-$\ell$ scales where these approximations become important.
+
+\blue{The treatment of photo-$z$ uncertainties in \cite{kitching/etal:2016} is based on a simple linear shift of redshift distributions.
+This has been shown to be insufficient to capture the full complexity of the problem.
+More importantly though, it seems like \cite{kitching/etal:2016} apply the photo-$z$ calibrations from \cite{choi/etal:2016} in the wrong direction.
+Instead of alleviating the tension between CFHTLenS and Planck a correct application of the offsets would increase the discrepancy, in agreement with a recent re-analysis of the CFHTLenS data \citep{joudaki/etal:2016} as well as results from the KiDS project \citep{hildebrandt/etal:2016}.}

### 2016-12-04 theory.tex
Added Catherine's figure with the Cl and xi+.

@@
  \begin{figure}
+ \begin{center}
+ \includegraphics[width=0.5\textwidth]{figures/Cl_xi_comp.pdf}
  \label{fig:Cl_xi}
- \caption{Will show $P_\kappa$ and $\xi_\pm$, TBD}
+ \caption{\emph{Top:} Theoretical models of the $\kappa$ power spectrum (\emph{left}) and shear correlation function $\xi_+$ (\emph{right})for the different approximations discussed in \citet{kitching/etal:2016}.
+\emph{Bottom:} Deviations with respect to the full treatment (LSH).}
+ \end{center}
  \end{figure}

### 2016-12-04 cfhtlens.tex
plots added to tex

@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{figures/ellWnPell1-100.pdf}
-\caption{ \label{fig:filters}.  Currently just COSEBIS, will also have $\xi_\pm$ and $M_{\rm ap}^2$.}
+\includegraphics[width=0.5\textwidth]{figures/IntegKsip.pdf}\\
+\includegraphics[width=0.5\textwidth]{figures/IntegCOSEBIs.pdf}\\
+\includegraphics[width=0.5\textwidth]{figures/IntegMap.pdf}
+\caption{ \label{fig:filters}. Integrand of $\xi_+$, $E_1$ and $M_{\rm ap}$.
+All the values are normalized with respect to their maximum value. Two cases are shown for each statistic. 
+For COSEBIs this is an angular range indicated in the caption. For aperture mass statistic $\theta_{\rm max}=2\theta$ is shown.
+}
 \end{center}

### 2016-12-04 Limber_Comment.tex
minor correction to intro

@@
 Interest in the results from these surveys is high as statistically significant deviations have been found between the cosmological parameter constraints from the CMB Planck experiment \citep{planck/cosmo:2015} in comparison to weak lensing constraints from both the Kilo-Degree Survey \citep[KiDS;][]{hildebrandt/etal:2016} and the Canada-France-Hawaii Telescope Lensing Survey \citep[CFHTLenS;][] {joudaki/etal:2016}.
-If the source of this tension is not a result of so-far unconsidered sources of systematic errors in one or all experiments, extensions to the standard flat $\Lambda$CDM cosmological need to be considered.
+If the source of this tension is not a result of so-far unconsidered sources of systematic errors in one or all experiments, extensions to the standard flat $\Lambda$CDM cosmological models need to be considered.
 \citet{joudaki/etal:2017} have shown, for example, that the tension can be resolved with an evolving dark energy model.

### 2016-12-05 Limber_Comment.tex
few changes and comments

@@
 \renewcommand{\d}[0]{{\rm d}}
+\newcommand{\shahab}[1]{\textcolor{pink}{\bf #1}}
 
@@
 We support the core message of this paper that the use of such approximations should be considered in the future analyses of high precision surveys such as Euclid, LSST and WFIRST.
-In this comment, we argue that these approximations have negligible impact for current surveys and are not able to explain away the tension between the constraints from some current weak lensing surveys and Planck.
+\shahab{(not sure it is clear that they are important even for future surveys, when considered together vs not considered at all)} In this comment, we argue that these approximations have negligible impact for current surveys and are not able to explain away the tension between the constraints from some current weak lensing surveys and Planck.
 Reducing uncertainty and characterising bias in photometric redshift estimation is a critical task for the success of current and future surveys.
 We highlight that sophisticated treatments of these uncertainties have already been explored in the literature and have been shown not to resolve the tension with Planck, in contrast to the message that Kitching et al.
-(2016) convey.
+(2016) convey \shahab{(do we perhaps want to remove the last clause "in contrast to the message..." to make the draft somewhat less Kitching-centric given the weakness of that analysis?)}.
 
@@
 
-The measurement of weak gravitational lensing by large scale structures provides a powerful cosmological probe of dark matter, dark energy and modifications to gravity.
+The measurement of weak gravitational lensing by large scale structures provides a powerful cosmological probe of dark matter, dark energy, and modifications to gravity.
 As such it is the primary science goal of several current (KiDS, HSC, DES) and future (Euclid, LSST, WFIRST) large-scale surveys.
@@
 We show that we are unable to replicate key results from \citet{kitching/etal:2016} and therefore do not expect these approximations to impact on the cosmological analysis of current surveys.
-In section~\ref{sec:cfhtlens} we compare the `one-parameter' cosmological re-analysis of \citet{kitching/etal:2016} with the full six-parameter analysis by \citet{kilbinger/etal:2013}, arguing that this particular non-tomographic data set is not in significant tension with Planck.
+In section~\ref{sec:cfhtlens} we compare the `one-parameter' cosmological re-analysis of \citet{kitching/etal:2016} with the full six-parameter analysis by \citet{kilbinger/etal:2013}, arguing that this particular non-tomographic data set is not in significant tension with Planck (\shahab{not sure I agree with this clause, please see my email}).
 We also briefly review the literature that has advanced our understanding since the original CFHTLenS analyses were published.

### 2016-12-05 cfhtlens.tex
few changes and comments

@@
-The Canada-France-Hawaii Telescope Lensing Survey (CFHTLenS) represented a major step forward for the field of weak gravitational lensing, in terms of improved accuracy in data reduction \citep{erben/etal:2013}, the implementation of gaussianised matched multi-band photometry \citep{hildebrandt/etal:2012}, cross-correlation clustering analysis between photometric redshift slices to verify tomographic redshift distributions \citep{benjamin/etal:2013}, accurate calibrated shape measurements \citep{miller/etal:2013} and a full suite of informative systematic tests to select a clean data set \citep{heymans/etal:2012}.
+The Canada-France-Hawaii Telescope Lensing Survey (CFHTLenS) represented a major step forward for the field of weak gravitational lensing, in terms of improved accuracy in data reduction \citep{erben/etal:2013}, the implementation of Gaussianised matched multi-band photometry \citep{hildebrandt/etal:2012}, cross-correlation clustering analysis between photometric redshift slices to verify tomographic redshift distributions \citep{benjamin/etal:2013}, accurate calibrated shape measurements \citep{miller/etal:2013} and a full suite of informative systematic tests to select a clean data set \citep{heymans/etal:2012}.
 Since the public release of this survey in 2013, the community has continued to scrutinise and advance our understanding of CFHTLenS by identifying a number of areas where the analysis could improve:

### 2016-12-05 theory.tex
added a red comment to fig 1
few changes and comments

@@
 \ee
-where $J_{0,4} (\ell \theta)$ is the zeroth (for $\xi_+$) or fourth (for $\xi_- $) order Bessel function of the first kind and $P_\kappa(\ell)$ is the convergence power spectrum at angular wave number $\ell$ which can be related to the underlying matter power spectrum $P_\delta$, using a Limber approximation as,
+where $J_{0,4} (\ell \theta)$ is the zeroth (for $\xi_+$) or fourth (for $\xi_- $) order Bessel function of the first kind and $P_\kappa(\ell)$ is the convergence power spectrum (\shahab{should we perhaps rename this as the shear power spectrum as only equal to convergence power spectrum in the flat-sky limit, which we will not always use?}) at angular wave number $\ell$ which can be related to the underlying matter power spectrum $P_\delta$, using a Limber approximation as,
 \be 
@@
 The lensing efficiency function $q(\chi)$ is given in equation (5) of \citet{hildebrandt/etal:2016}.
-\citet{kitching/etal:2016} show that the pre-factor $T_\ell$ is given by
+\citet{kitching/etal:2016} show that the pre-factor $T_\ell$ \shahab{for the shear power spectrum} is given by
 \be
@@
 \ee
+\shahab{The corresponding pre-factor for the convergence power spectrum (along with the pre-factors for a range of other statistics such as the CMB lensing power spectrum and galaxy-galaxy lensing power spectrum) is given in \citet{jk12}.}
 When a survey is sufficiently small, a flat-sky approximation can be made reducing $T_\ell \approx 1$.
@@
 
+%perhaps include Joudaki & Kaplinghat (2012) reference here instead:
+%\shahab{We further note that \citet{kitching/etal:2016} were not the first to consider the pre-factor from the extended Limber approximation and all-sky formulation of the power spectrum.
+For example, the corresponding pre-factor for the convergence power spectrum, along with the pre-factors for a range of other statistics such as the CMB lensing power spectrum and galaxy-galaxy lensing power spectrum, were given in \citet{jk12}.}
+
 {\bf TBD: add figures of $P_\kappa$ and $\xi_\pm$ for all these combinations showing that they make absolutely no difference.}
@@
  \caption{\emph{Top:} Theoretical models of the $\kappa$ power spectrum (\emph{left}) and shear correlation function $\xi_+$ (\emph{right})for the different approximations discussed in \citet{kitching/etal:2016}.
-\emph{Bottom:} Deviations with respect to the full treatment (LSH).}
+\emph{Bottom:} Deviations with respect to the full treatment (LSH).\red{ Fig 3 in Kitching et al.
+is showing $C_\ell$ not $\ell(\ell+1)/2\pi C_\ell$.
+Would be better to show the same thing here ($C_\ell$ instead of $\ell C_\ell$ with the same axes range).} }
  \end{center}

### 2016-12-05 cfhtlens.tex
minor update

@@
 \item{\citet{fenechconti/etal:2016} demonstrated that the CFHTLenS data would have been subject to a weight bias that favours galaxies that are more intrinsically oriented with the point-spread function.}
-\item{\citet{joudaki/etal:2016} updated the CFHTLenS covariance matrices using larger-box numerical simulations that were less subject to the lack power on large scales.}
+\item{\citet{joudaki/etal:2016} updated the CFHTLenS covariance matrices using larger-box numerical simulations that were less subject to the lack of power on large scales.}
 \end{itemize}
-All these advances in our understanding were incorporated and accounted for in the recent KiDS cosmic shear analysis \citep{hildebrandt/etal:2016} which reports at $2.3 \sigma$ tension with Planck.
+All these advances in our understanding were incorporated and accounted for in the recent KiDS cosmic shear analysis \citep{hildebrandt/etal:2016} which reports a $2.3 \sigma$ tension with Planck.
 Efforts are now underway to fully re-analyse CFHTLenS using the advanced KiDS analysis pipeline with revised shape measurements and calibrations for the shear and photometric redshifts.
@@
 This is even more unexpected as, out of all the CFHTLenS cosmic shear results, the non-tomographic analysis of \citet{kilbinger/etal:2013} is the least in tension with Planck \citep[see for example][who show that with $\sigma_8 (\Omega_m/0.3)^{0.5} = 0.738^{+0.055}_{-0.032}$, \citet{kilbinger/etal:2013} is in agreement with Planck at $1.6 \sigma$]{abbott/etal:2016}.
+\shahab{(not sure I entirely agree with this last sentence, please see email)}
 
-\citet{kitching/etal:2016} choose to only vary $\sigma_8$ in their analysis, fixing all other parameters to Planck constraints.
+\citet{kitching/etal:2016} choose to only vary $\sigma_8$ in their analysis, fixing all other parameters to their Planck values.
 They find a conditional value of $\sigma_8 = 0.789 \pm 0.015$ for their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) of the data from \citet{kilbinger/etal:2013}.

### 2016-12-05 conclusion.tex
minor update

@@
 We argue that the flat sky and Limber approximations that can be used in cosmic shear analyses are not able to explain away the tension between current weak lensing and Planck results, in contrast to the message that \cite{kitching/etal:2016} convey.
-Our critique should not, however, detract from the important core message of their paper, that future surveys will need to consider these approximations and optimise their statistical analyses accordingly.
+Our critique should not, however, detract from the important core message of their paper, that future surveys will need to consider these approximations and optimise their statistical analyses accordingly (\shahab{I think we are being too nice, it's unclear the Limber and flat-sky approximations are important even for future surveys when considered together --- moreover Tommaso's paper seems to suggest Limber approximation fine even for future surveys}).
 For example moving from the standard two-point shear correlation function statistic to the more stringent `COSEBI' statistic \citep{schneider/etal:2010} renders the cosmic shear measurement completely insensitive to the low-$\ell$ scales where these approximations become important.

### 2016-12-05 cfhtlens.tex
text for Fig 2

@@
 
-\subsection{Comparison of two-point shear statistics; the two-point correlation function, mass aperture statistic and COSEBIS}
+\subsection{Comparison of two-point shear statistics; the two-point correlation function, mass aperture statistic and COSEBIs}
 \citet{kilbinger/etal:2013} present a detailed comparison of cosmological constraints obtained from a range different two-point shear statistics including the shear correlation function, $\xi_\pm$, the mass aperture statistic, $M_ {\rm ap}^2$ \citep{schneider/etal:1998}, and the COSEBIs statistics \citep{schneider/etal:2010}.
+Figure~\ref{fig:filters} shows the integrands of these statistics for two cases,
+normalised to their maximum value.
+The top plot shows the integrand of $\xi_+$ for $\theta=100'$ and $\theta=350'$. 
+Note that the bottom left panel of Fig. 1 in \citet{kitching/etal:2016} shows an integrated form of this function for a maximum
+angular separation of $100'$. However, in \citet{kilbinger/etal:2013} which is the same data used in \citet{kitching/etal:2016} 
+the maximum $\theta$ is $350'$. The middle panel in Figure~\ref{fig:filters} shows COSEBIs integrands for two angular ranges,
+$[1',100']$ and $[0.8',350']$ which corresponds to the largest angular range used in \citet{kilbinger/etal:2013}.
+Here we only show the integrands for the lowest COSEBIs mode, as the higher modes generally probe larger $\ell$-modes.
+Finally, the bottom panel shows the integrands of aperture mass dispersion statistics, for two maximum angular ranges, discussed above. 
 As shown by each statistic's weight function in figure~\ref{fig:filters}, these two-point cosmic shear statistics exhibit different dependences between the angular scales sampled and the $\ell$-range probed.
-If a significant bias had been introduced at low-$\ell$ by using flat-sky and Limber approximations, we would then expect to see a systematic shift between the different two-point statistics with the COSEBI statistic being essentially unaffected as it only includes modes with $\ell \gtrsim 80$.
+If a significant bias had been introduced at low-$\ell$ by using flat-sky and Limber approximations, we would then expect to see a systematic shift between the different two-point statistics with the COSEBIs statistic being essentially unaffected as it only includes modes with $\ell \gtrsim 80$.
 This is found not to be the case with all three statistics finding $\sigma_8 (\Omega_m/0.27)^\alpha = 0.79$ with errors that range from $0.03$ to $0.06$ \citep[see Table 5 of][]{kilbinger/etal:2013}.
@@
 \includegraphics[width=0.5\textwidth]{figures/IntegMap.pdf}
-\caption{ \label{fig:filters}. Integrand of $\xi_+$, $E_1$ and $M_{\rm ap}$.
+\caption{ \label{fig:filters}. Integrand of $\xi_+$, $E_1$ (E-COSEBIs) and $M^2_{\rm ap}$, respectively.
 All the values are normalized with respect to their maximum value. Two cases are shown for each statistic. 
 For COSEBIs this is an angular range indicated in the caption. For aperture mass statistic $\theta_{\rm max}=2\theta$ is shown.
+Note that higher order COSEBIs modes generally probe larger $\ell$-modes, hence here we only show the lowest mode $E_1$. 
 }

### 2016-12-05 cfhtlens.tex
added JHD's comments and sections on CMB Lensing and Nbody sims

@@
 The Canada-France-Hawaii Telescope Lensing Survey (CFHTLenS) represented a major step forward for the field of weak gravitational lensing, in terms of improved accuracy in data reduction \citep{erben/etal:2013}, the implementation of Gaussianised matched multi-band photometry \citep{hildebrandt/etal:2012}, cross-correlation clustering analysis between photometric redshift slices to verify tomographic redshift distributions \citep{benjamin/etal:2013}, accurate calibrated shape measurements \citep{miller/etal:2013} and a full suite of informative systematic tests to select a clean data set \citep{heymans/etal:2012}.
-Since the public release of this survey in 2013, the community has continued to scrutinise and advance our understanding of CFHTLenS by identifying a number of areas where the analysis could improve:
+Since the public release of this survey in 2013, the community has continued to scrutinise and advance our understanding of CFHTLenS by identifying a number of areas where analyses could improve:
 \begin{itemize}
@@
 We repeated the `one-parameter' analysis for the full range of Limber cases listed in Table~\ref{tab:Tl_nu} finding the lowest conditional value of $\sigma_8 = XXX \pm XXX$ for the XXX case and the highest conditional value of $\sigma_8 = XXX \pm XXX$ for the XXX case.
-As expected from the comparison in Figure~\ref{fig:Cl_xi} the different combinations of assuming flat or spherical sky, or baseline of extended Limber make little difference to the cosmological parameter constraints, even in this exaggerated `one-parameter' analysis.
+As expected from the comparison in Figure~\ref{fig:Cl_xi} the different combinations of assuming flat or spherical sky, or baseline of extended Limber make little difference to the cosmological parameter constraints, even in this `one-parameter' analysis.
 
@@
 \end{figure}
+
+\subsection{On the Validation of Methods on Simulations}
+It is discussed in \citet{kitching/etal:2016} that the validation of cosmic shear estimators on mock catalogues could also be affected by the approximations they investigate.
+We agree that a full sky mock should be compared to a full curved sky non-Limber prediction.
+It is then suggested, however, that the discrepancies already reported between existing mocks and the predictions could be attributed to these approximations, as opposed to a finite box effect \citep{kiessling/etal:2011, harnois-deraps/etal:2012, harnois-deraps/vanwaerbeke:2015}.
+Going beyond flat sky and Limber could improve the agreement, however this cannot explain the results of \citet{harnois-deraps/vanwaerbeke:2015} who demonstrate that the large scale under-estimation of power varies with the simulation box size.
+This volume effect was verified by comparing explicitly the $\xi_+$ statistic at large angular scales between simulation volumes with box sides = 147Mpc/h and 515Mpc/h \citep[see Fig.
+5 in][]{harnois-deraps/vanwaerbeke:2015}.
+The increase of power loss with decreasing box size was shown to be fully-modelled by excluding the super-box $k$-modes in the Limber predictions, something that the approximations discussed in \citet{kitching/etal:2016} would be unable to explain.
+
+We note that any future comparison of mock data with full curved sky non-Limber predictions will place requirements on the input weak lensing simulations.
+Many currently work with parallel plane mass-sheets as opposed to curved sky mass-sheets and at large angles, these two approaches differ regardless of the box size.
+
+\subsection{On the application to CMB lensing}
+\citet{kitching/etal:2016} argue that their correction to the Limber and flat sky approximations would also affect predictions involving the shear and convergence cross-spectrum, such that CMB lensing - galaxy lensing cross-correlation should include a pre-term $[\ell/(\ell+0.5)]^4$.
+We have verified that this term would have negligible impact on the current measurements, given the relatively low signal to noise ratio.
+For example, most measurements \citep{hand/etal:2015, liu/hill:2015, kirk/etal:2016,harnois-deraps/etal:2016} are carried over angular multipoles in the range $\ell \in [20-2000]$, and are organized in $\sim$ five bins.
+The size of the pre-term $[\ell/(\ell+0.5)]^4$, averaged over the first bin, is of the order of 2\%, and then becomes sub-percent for all other bins.
+In comparison, the size of the statistical error bars are of the order 25-35\% with additional uncertainty due to photometric redshifts (10-15\%) and intrinsic galaxy alignments (10-15\%).

### 2016-12-05 Limber_Comment.tex
Limber_Comment.tex: Addressed SJ's comments

--- 2016-12-04 Limber_Comment.tex
@@
 We highlight that sophisticated treatments of these uncertainties have already been explored in the literature and have been shown not to resolve the tension with Planck, in contrast to the message that Kitching et al.
-(2016) convey.
+(2016) convey}.
 
@@
 We show that we are unable to replicate key results from \citet{kitching/etal:2016} and therefore do not expect these approximations to impact on the cosmological analysis of current surveys.
-In section~\ref{sec:cfhtlens} we compare the `one-parameter' cosmological re-analysis of \citet{kitching/etal:2016} with the full six-parameter analysis by \citet{kilbinger/etal:2013}, arguing that this particular non-tomographic data set is not in significant tension with Planck.
-We also briefly review the literature that has advanced our understanding since the original CFHTLenS analyses were published.
+In section~\ref{sec:cfhtlens} we compare with \citet{kitching/etal:2016} our conclusions of a `one-parameter' cosmological re-analysis of 2D cosmic shear data from \citet{kilbinger/etal:2013}.
+We also briefly review the literature that has advanced our understanding since the original CFHTLenS analyses were published and discuss the impact in our analysis of numerical simulations and CMB lensing.
 

### 2016-12-05 cfhtlens.tex
cfhtlens.tex:
Added Sj comment that Kilbinger et al is in tension - jsut Abbott et al is wrong

conclusion.tex
accepted HH's paragraph

theory.tex:
Accepted SJ's changes

@@
 Given the known shortcomings with the original CFHTLenS results, which will impact in different ways on the cosmological conclusions that one can draw from the survey, it is surprising that \citet{kitching/etal:2016} chose to focus their study on the cosmic shear analysis of \citet{kilbinger/etal:2013}.
-This is even more unexpected as, out of all the CFHTLenS cosmic shear results, the non-tomographic analysis of \citet{kilbinger/etal:2013} is the least in tension with Planck \citep[see for example][who show that with $\sigma_8 (\Omega_m/0.3)^{0.5} = 0.738^{+0.055}_{-0.032}$, \citet{kilbinger/etal:2013} is in agreement with Planck at $1.6 \sigma$]{abbott/etal:2016}.
-\shahab{(not sure I entirely agree with this last sentence, please see email)}
 
@@
 They find a conditional value of $\sigma_8 = 0.789 \pm 0.015$ for their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) of the data from \citet{kilbinger/etal:2013}.
-We argue that this artificial reduction in the error by a factor of $\sim 3$ could easily mislead, making it appear that the impact of removing all approximations from the theoretical analysis is more significant for current surveys than it is in reality.
+We argue that this artificial reduction in the error by a factor of $\sim 2$, in comparison to a full six-parameter fit, could easily mislead, making it appear that the impact of removing all approximations from the theoretical analysis is more significant for current surveys than it is in reality.
 

### 2016-12-05 conclusion.tex
cfhtlens.tex:
Added Sj comment that Kilbinger et al is in tension - jsut Abbott et al is wrong

conclusion.tex
accepted HH's paragraph

theory.tex:
Accepted SJ's changes

--- 2016-12-02 conclusion.tex
@@
 For example moving from the standard two-point shear correlation function statistic to the more stringent `COSEBI' statistic \citep{schneider/etal:2010} renders the cosmic shear measurement completely insensitive to the low-$\ell$ scales where these approximations become important.
+
+The treatment of photo-$z$ uncertainties in \cite{kitching/etal:2016} is based on a simple linear shift of redshift distributions.
+This has been shown to be insufficient to capture the full complexity of the problem.
+More importantly though, it seems like \cite{kitching/etal:2016} apply the photo-$z$ calibrations from \cite{choi/etal:2016} in the wrong direction.
+Instead of alleviating the tension between CFHTLenS and Planck a correct application of the offsets would increase the discrepancy, in agreement with a recent re-analysis of the CFHTLenS data \citep{joudaki/etal:2016} as well as results from the KiDS project \citep{hildebrandt/etal:2016}.

### 2016-12-05 theory.tex
cfhtlens.tex:
Added Sj comment that Kilbinger et al is in tension - jsut Abbott et al is wrong

conclusion.tex
accepted HH's paragraph

theory.tex:
Accepted SJ's changes

--- 2016-12-04 theory.tex
@@
 \be
-\xi_\pm^{ij}(\theta) = \frac{1}{2\pi}\int \d\ell \,\ell \,P^{ij}_\kappa(\ell) \, J_{0,4}(\ell \theta) \, , 
+\xi_\pm^{ij}(\theta) = \frac{1}{2\pi}\int \d\ell \,\ell \,P^{ij}_\gamma(\ell) \, J_{0,4}(\ell \theta) \, , 
 \label{eqn:xiGG}
 \ee
-where $J_{0,4} (\ell \theta)$ is the zeroth (for $\xi_+$) or fourth (for $\xi_- $) order Bessel function of the first kind and $P_\kappa(\ell)$ is the convergence power spectrum at angular wave number $\ell$ which can be related to the underlying matter power spectrum $P_\delta$, using a Limber approximation as,
+where $J_{0,4} (\ell \theta)$ is the zeroth (for $\xi_+$) or fourth (for $\xi_- $) order Bessel function of the first kind and $P_\gamma(\ell)$ is the shear power spectrum at angular wave number $\ell$ which can be related to the underlying matter power spectrum $P_\delta$, using a Limber approximation as,
 \be 
-P^{ij}_\kappa(\ell) = T_l \int_0^{\chi_{\rm H}} \d \chi \, \frac{q_i(\chi)q_j(\chi)}{[f_K(\chi)]^2} \, P_\delta \left( \frac{\nu}{f_K(\chi)},\chi \right).
+P^{ij}_\gamma(\ell) = T_l \int_0^{\chi_{\rm H}} \d \chi \, \frac{q_i(\chi)q_j(\chi)}{[f_K(\chi)]^2} \, P_\delta \left( \frac{\nu}{f_K(\chi)},\chi \right).
 \label{eqn:Pkappa} 
@@
 The lensing efficiency function $q(\chi)$ is given in equation (5) of \citet{hildebrandt/etal:2016}.
-\citet{kitching/etal:2016} show that the pre-factor $T_\ell$ is given by
+\citet{kitching/etal:2016} show that the pre-factor $T_\ell$ for the shear power spectrum is given by
 \be
@@
 \ee
+The corresponding pre-factor for the convergence power spectrum, along with the pre-factors for a range of other statistics such as the CMB lensing power spectrum and galaxy-galaxy lensing power spectrum, is given in \citet{jk12}.
+
 When a survey is sufficiently small, a flat-sky approximation can be made reducing $T_\ell \approx 1$.

### 2016-12-05 photoz.tex
Added two sentences about the limitation of the Choi et al. analysis.
photoz.tex
Accepted HH's comment (but as a footnote)

@@
 In \citet{choi/etal:2016} a cross-correlation clustering analysis, between photometric redshift slices and overlapping spectroscopic redshifts, is used to determine linear biases in the CFHTLenS photometric redshift distributions.
-The maximum redshift $z_B<0.9$ in this analysis was limited by the redshift overlap with the spectroscopic sample.
+The maximum redshift $z_B<0.9$ in this analysis was limited by the redshift overlap with the spectroscopic sample\footnote{The implication of a $z_B < 0.9$ high-redshift limit is that the analysis is unable to constrain the high-redshift tails of the redshift distributions due to the lack of high-$z$ spec-$z$ samples.
+As such the results from \citet{choi/etal:2016} are only the first important step towards a detailed understanding of the CFHTLenS tomographic redshift distributions and as such may be revised in the future.}.
 \citet{choi/etal:2016} found significant biases in the redshift distributions used in the original CFHTLenS analyses,

### 2016-12-05 theory.tex
Updated labels on Fig 1

@@
 \begin{center}
-\begin{tabular}{ | l | c | c  | c |}
+\begin{tabular}{ | l | l | c | c  | c |}
 \hline
-Case & $T_\ell$ & $\nu$ & Used in \\ \hline
-\citet{kitching/etal:2016} `Standard' & $1$ & $\ell$ & pre-2014 CFHTLenS papers \\
-Baseline Limber Flat Sky &  $\ell^4 / (\ell + 0.5)^4$ & $\ell$ & \\
-Baseline Limber Spherical & equation~\ref{eqn:Tl} & $\ell$ & \\
-Extended Limber Flat Sky & $\ell^4 / (\ell + 0.5)^4$ & $\ell + 0.5$ & \\
-Extended Limber Spherical & equation~\ref{eqn:Tl}& $\ell + 0.5$  & \\
-Extended `Standard' & $1$ & $\ell + 0.5$ & \citet{joudaki/etal:2016} \&  \\
-  & & & \citet{hildebrandt/etal:2016}$^*$\\\hline
+Case & ID & $T_\ell$ & $\nu$ & Used in \\ \hline
+\citet{kitching/etal:2016} `Standard' & KSt & $1$ & $\ell$ & pre-2014 CFHTLenS papers \\
+Baseline Limber `Flat' Sky &  LF & $\ell^4 / (\ell + 0.5)^4$ & $\ell$ & \\
+Baseline Limber Spherical & LS & equation~\ref{eqn:Tl} & $\ell$ & \\
+Extended Limber `Flat' Sky & ELF & $\ell^4 / (\ell + 0.5)^4$ & $\ell + 0.5$ & \\
+Extended Limber Spherical & ELS & equation~\ref{eqn:Tl}& $\ell + 0.5$  & \\
+Extended Standard Flat Sky & ESt & $1$ & $\ell + 0.5$ & \citet{joudaki/etal:2016} \&  \\
+  &  & & & \citet{hildebrandt/etal:2016}$^*$\\\hline
  \end{tabular}
  \end{center}
- \caption{Variations on the different approximations that can be made when calculating the convergence power spectrum $P_\kappa(\ell)$ (equation~\ref{eqn:Pkappa}), using a Limber approximation.
-$^*$We confirm that there is a typographical error in equation 4 of \citet{hildebrandt/etal:2016} which does not include the extra term of `$+0.5$' in $\nu$ that was incorporated in the cosmological analysis.}
+ \caption{Variations on the different approximations that can be made when calculating the shear power spectrum $P_\gamma(\ell)$ (equation~\ref{eqn:Pkappa}), using a Limber approximation.
+$^*$We apologise for the typographical error in equation 4 of \citet{hildebrandt/etal:2016} which should include the extra term of `$+0.5$' in $\nu$ that was incorporated in the cosmological analysis.}
  \end{table}
@@
  \begin{center}
- \includegraphics[width=0.5\textwidth]{figures/Cl_xi_comp.pdf}
+ \includegraphics[width=0.75\textwidth]{figures/Cl_xi_comp.pdf}
  \label{fig:Cl_xi}
- \caption{\emph{Top:} Theoretical models of the $\kappa$ power spectrum (\emph{left}) and shear correlation function $\xi_+$ (\emph{right})for the different approximations discussed in \citet{kitching/etal:2016}.
-\emph{Bottom:} Deviations with respect to the full treatment (LSH).\red{ Fig 3 in Kitching et al.
-is showing $C_\ell$ not $\ell(\ell+1)/2\pi C_\ell$.
-Would be better to show the same thing here ($C_\ell$ instead of $\ell C_\ell$ with the same axes range).} }
+ \caption{\emph{Upper Panels:} Theoretical models for the shear power spectrum (\emph{left}) and shear correlation function $\xi_+$ (\emph{right}) for the different approximations listed in Table~\ref{tab:Tl_nu}.
+\emph{Lower Panels:} Deviations with respect to the full treatment (ELS).}
  \end{center}

### 2016-12-05 theory.tex
theory.tex: Discussion on Fig 1

@@
 The value of $\nu$ depends on whether a baseline Limber approximation, or the more accurate extended Limber approximation of \citet{loverde/afshordi:2008} is used.
-In the analysis of \citet{kitching/etal:2016} it is not fully clear which combinations of  $T_\ell$ and $\nu$ are considered, so we review them all as summarised in Table~\ref{tab:Tl_nu}, also highlighting which combinations were used in recent cosmic shear analyses.
+In the text of \citet{kitching/etal:2016} it is not fully clear which combinations of  $T_\ell$ and $\nu$ are considered, so we review them all as summarised in Table~\ref{tab:Tl_nu}, also highlighting which combinations were used in recent cosmic shear analyses.
 
@@
 
-{\bf TBD: add figures of $P_\kappa$ and $\xi_\pm$ for all these combinations showing that they make absolutely no difference.}
+Figure~\ref{fig:Cl_xi} shows theoretical models for the shear power spectrum $P_\gamma(\ell)$ (equation~\ref{eqn:Pkappa}), and the shear correlation function (equation~\ref{eqn:xiGG}) for the different variations on the approximations listed in Table~\ref{tab:Tl_nu}.
+The majority of the models agree.
+The two outliers found, are the `Baseline' and `Extended' Limber cases where the \citet{kitching/etal:2016} `Flat' Sky approximation has been made with $T_\ell = \ell^4 / (\ell + 0.5)^4$.
+We argue that applying the approximation, that $\ell \pm x \approx \ell$, where $x$ is small, only to the numerator of equation~\ref{eqn:Tl} is inconsistent.
+To our knowledge, this form of the flat-sky approximation has not been used in cosmic shear studies to date.
+
+As shown in the lower panels of Figure~\ref{fig:Cl_xi}, the `standard flat' sky approximation used by recent cosmic shear surveys, where $T_\ell = 1$, recovers a very similar result to the spherical sky case.
+Over angular scales used in the recent KiDS analysis (shown dashed), these curves differ by less than 1\% and such the standard flat-sky approximations that have been used will not impact the cosmological analyses of current surveys.
 
@@
  \begin{center}
- \includegraphics[width=0.75\textwidth]{figures/Cl_xi_comp.pdf}
+ \includegraphics[width=0.85\textwidth]{figures/Cl_xi_comp.pdf}
  \label{fig:Cl_xi}
- \caption{\emph{Upper Panels:} Theoretical models for the shear power spectrum (\emph{left}) and shear correlation function $\xi_+$ (\emph{right}) for the different approximations listed in Table~\ref{tab:Tl_nu}.
-\emph{Lower Panels:} Deviations with respect to the full treatment (ELS).}
+ \caption{\emph{Upper Panels:} Theoretical models for the shear power spectrum (\emph{left}) and shear correlation function $\xi_+$ (\emph{right}) for the different approximations listed in Table~\ref{tab:Tl_nu}, assuming a \citet{planck/cosmo:2015} cosmology and the 2D CFHTLenS redshift distribution.
+\emph{Lower Panels:} Deviations with respect to the extended Limber spherical sky model (ELS).
+The dashed lines in the left panels show the largest angular scale used in the recent KIDS cosmic shear analysis where an Extended Standard (ESt) analysis was used.}
  \end{center}

### 2016-12-05 cfhtlens.tex
cfhtlens.tex Added numbers from Shahab's recent runs

@@
 We argue that this artificial reduction in the error by a factor of $\sim 2$, in comparison to a full six-parameter fit, could easily mislead, making it appear that the impact of removing all approximations from the theoretical analysis is more significant for current surveys than it is in reality.
-
-We repeated the `one-parameter' analysis for the full range of Limber cases listed in Table~\ref{tab:Tl_nu} finding the lowest conditional value of $\sigma_8 = XXX \pm XXX$ for the XXX case and the highest conditional value of $\sigma_8 = XXX \pm XXX$ for the XXX case.
+Nevertheless, we repeated the `one-parameter' analysis for the full range of Limber cases listed in Table~\ref{tab:Tl_nu} finding the lowest conditional value of $\sigma_8 = 0.743 \pm 0.023$ for the `Standard' (KSt) case and the highest conditional value of $\sigma_8 = 0.744 \pm 0.023$ for the `Baseline Limber Flat` (LF) case.
 As expected from the comparison in Figure~\ref{fig:Cl_xi} the different combinations of assuming flat or spherical sky, or baseline of extended Limber make little difference to the cosmological parameter constraints, even in this `one-parameter' analysis.
 
-Our Limber-case findings are therefore in disagreement with \citet{kitching/etal:2016} who find a shift of $\Delta \sigma_8 = 0.007$ between their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) and their `Limber' analysis (which we believe corresponds to the Extended Limber spherical case in Table~\ref{tab:Tl_nu}).
+We find our Limber-case findings to be in disagreement with \citet{kitching/etal:2016} who find a shift of $\Delta \sigma_8 = 0.007$ between their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) and their `Limber' analysis (which we believe corresponds to the Extended Limber spherical (ELS) case in Table~\ref{tab:Tl_nu}).
 

### 2016-12-05 Limber_Comment.tex
photoz.tex
Accepted HH's comment (but as a footnote)
ready to send to the wider group...

@@
 We highlight that sophisticated treatments of these uncertainties have already been explored in the literature and have been shown not to resolve the tension with Planck, in contrast to the message that Kitching et al.
-(2016) convey}.
+(2016) convey.
 
@@
 In section~\ref{sec:theory} we clarify which brand of approximations, highlighted by \citet{kitching/etal:2016}, have been used in recent weak lensing analyses \citep{joudaki/etal:2016, hildebrandt/etal:2016, joudaki/etal:2017}.
-We show that we are unable to replicate key results from \citet{kitching/etal:2016} and therefore do not expect these approximations to impact on the cosmological analysis of current surveys.
+We find that we are unable to replicate key results from \citet{kitching/etal:2016} and show that do not expect these approximations to impact on the cosmological analysis of current surveys.
 In section~\ref{sec:cfhtlens} we compare with \citet{kitching/etal:2016} our conclusions of a `one-parameter' cosmological re-analysis of 2D cosmic shear data from \citet{kilbinger/etal:2013}.
-We also briefly review the literature that has advanced our understanding since the original CFHTLenS analyses were published and discuss the impact in our analysis of numerical simulations and CMB lensing.
+We also briefly review the literature that has advanced our understanding since the original CFHTLenS analyses were published and discuss the impact of flat-sky and Limber approximations in our analysis of numerical simulations and CMB lensing.
 

### 2016-12-05 cfhtlens.tex
ready to send to the wider group...

@@
 Nevertheless, we repeated the `one-parameter' analysis for the full range of Limber cases listed in Table~\ref{tab:Tl_nu} finding the lowest conditional value of $\sigma_8 = 0.743 \pm 0.023$ for the `Standard' (KSt) case and the highest conditional value of $\sigma_8 = 0.744 \pm 0.023$ for the `Baseline Limber Flat` (LF) case.
-As expected from the comparison in Figure~\ref{fig:Cl_xi} the different combinations of assuming flat or spherical sky, or baseline of extended Limber make little difference to the cosmological parameter constraints, even in this `one-parameter' analysis.
+As expected from the comparison in Figure~\ref{fig:Cl_xi} the different combinations of assuming flat or spherical sky, baseline or extended Limber, make little difference to the cosmological parameter constraints, even in this `one-parameter' analysis.
 
@@
 
+We note that it appears \citet{kitching/etal:2016} have chosen to use their `Flat' approximation in their `Full' non-Limber analysis rather than a full spherical-sky solution.
+The rationale is based on the Hankel transform in equation~\ref{eqn:xiGG} which is derived assuming a flat-sky approximation.
+As shown in Figure~\ref{fig:Cl_xi}, however their chosen version of a flat-sky approximation serves to exacerbates the tension in theoretical models when a flat-sky solution is compared with the spherical-sky solution.
+We do not find this to be the case when considering the Standard $T_\ell = 1$ flat-sky approximation that has been used in the majority of cosmic shear studies to date.
+
 \subsection{Comparison of two-point shear statistics; the two-point correlation function, mass aperture statistic and COSEBIs}
 \citet{kilbinger/etal:2013} present a detailed comparison of cosmological constraints obtained from a range different two-point shear statistics including the shear correlation function, $\xi_\pm$, the mass aperture statistic, $M_ {\rm ap}^2$ \citep{schneider/etal:1998}, and the COSEBIs statistics \citep{schneider/etal:2010}.
-Figure~\ref{fig:filters} shows the integrands of these statistics for two cases,
-normalised to their maximum value.
-The top plot shows the integrand of $\xi_+$ for $\theta=100'$ and $\theta=350'$. 
-Note that the bottom left panel of Fig. 1 in \citet{kitching/etal:2016} shows an integrated form of this function for a maximum
-angular separation of $100'$. However, in \citet{kilbinger/etal:2013} which is the same data used in \citet{kitching/etal:2016} 
-the maximum $\theta$ is $350'$. The middle panel in Figure~\ref{fig:filters} shows COSEBIs integrands for two angular ranges,
-$[1',100']$ and $[0.8',350']$ which corresponds to the largest angular range used in \citet{kilbinger/etal:2013}.
-Here we only show the integrands for the lowest COSEBIs mode, as the higher modes generally probe larger $\ell$-modes.
-Finally, the bottom panel shows the integrands of aperture mass dispersion statistics, for two maximum angular ranges, discussed above. 
-As shown by each statistic's weight function in figure~\ref{fig:filters}, these two-point cosmic shear statistics exhibit different dependences between the angular scales sampled and the $\ell$-range probed.
+Figure~\ref{fig:filters} shows the integrands of these statistics (i.e.
+the weights placed on each $\ell$ scale),  for two cases, normalised to their maximum value.
+The upper panel shows the integrand\footnote{Note that the lower left panel of Fig.
+1 in \citet{kitching/etal:2016} shows an integrated form of this function for a maximum
+angular separation of $100'$. However, in \citet{kilbinger/etal:2013}, the data used in \citet{kitching/etal:2016}, 
+the maximum $\theta$ is $350'$.} of $\xi_+$ for $\theta=100'$ and $\theta=350'$.
+The middle panel in Figure~\ref{fig:filters} shows COSEBIs integrands for two angular ranges,$[1',100']$ and $[0.8',350']$, where we only show the integrands for the lowest COSEBIs mode, as the higher modes generally probe larger $\ell$-modes.
+Finally, the lower panel shows the integrands of aperture mass dispersion statistics, for the same two maximum angular ranges.
+From Figure~\ref{fig:filters} we can see that the two-point cosmic shear statistics tested by \citet{kilbinger/etal:2013} exhibit different dependences between the angular scales sampled and the $\ell$-range probed.
 If a significant bias had been introduced at low-$\ell$ by using flat-sky and Limber approximations, we would then expect to see a systematic shift between the different two-point statistics with the COSEBIs statistic being essentially unaffected as it only includes modes with $\ell \gtrsim 80$.
@@
 \subsection{On the application to CMB lensing}
-\citet{kitching/etal:2016} argue that their correction to the Limber and flat sky approximations would also affect predictions involving the shear and convergence cross-spectrum, such that CMB lensing - galaxy lensing cross-correlation should include a pre-term $[\ell/(\ell+0.5)]^4$.
+\citet{kitching/etal:2016} argue that their correction to the Limber and flat sky approximations would also affect predictions involving the shear and convergence cross-spectrum, such that CMB lensing - galaxy lensing cross-correlation should include a pre-term $ [(\ell*(\ell+1))^2]/(\ell+1/2)^4.$.
 We have verified that this term would have negligible impact on the current measurements, given the relatively low signal to noise ratio.

### 2016-12-05 theory.tex
ready to send to the wider group...

@@
 As shown in the lower panels of Figure~\ref{fig:Cl_xi}, the `standard flat' sky approximation used by recent cosmic shear surveys, where $T_\ell = 1$, recovers a very similar result to the spherical sky case.
-Over angular scales used in the recent KiDS analysis (shown dashed), these curves differ by less than 1\% and such the standard flat-sky approximations that have been used will not impact the cosmological analyses of current surveys.
+Over angular scales used in the recent KiDS analysis (shown dashed), these curves differ by less than 1\% as such the standard flat-sky approximations that have been used will not impact the cosmological analyses of current surveys.
 

### 2016-12-06 Limber_Comment.tex
Included JHD 2nd round of comments

@@
 We support the core message of this paper that the use of such approximations should be considered in the future analyses of high precision surveys such as Euclid, LSST and WFIRST.
-In this comment, we argue that these approximations have negligible impact for current surveys and are not able to explain away the tension between the constraints from some current weak lensing surveys and Planck.
+In this comment, we argue that these approximations have negligible impact for current surveys and are thus unable to explain away the tension between the constraints from some current weak lensing surveys and Planck.
 Reducing uncertainty and characterising bias in photometric redshift estimation is a critical task for the success of current and future surveys.
@@
 In section~\ref{sec:theory} we clarify which brand of approximations, highlighted by \citet{kitching/etal:2016}, have been used in recent weak lensing analyses \citep{joudaki/etal:2016, hildebrandt/etal:2016, joudaki/etal:2017}.
-We find that we are unable to replicate key results from \citet{kitching/etal:2016} and show that do not expect these approximations to impact on the cosmological analysis of current surveys.
+We find that we are unable to replicate key results from \citet{kitching/etal:2016} and show that we do not expect these approximations to impact on the cosmological analysis of current surveys.
 In section~\ref{sec:cfhtlens} we compare with \citet{kitching/etal:2016} our conclusions of a `one-parameter' cosmological re-analysis of 2D cosmic shear data from \citet{kilbinger/etal:2013}.

### 2016-12-06 cfhtlens.tex
cfhtlens.tex: Moved Fig 2 further into text
cfhtlens.tex: more faffing
Included JHD 2nd round of comments

@@
 the maximum $\theta$ is $350'$.} of $\xi_+$ for $\theta=100'$ and $\theta=350'$.
-The middle panel in Figure~\ref{fig:filters} shows COSEBIs integrands for two angular ranges,$[1',100']$ and $[0.8',350']$, where we only show the integrands for the lowest COSEBIs mode, as the higher modes generally probe larger $\ell$-modes.
+The middle panel in Figure~\ref{fig:filters} shows COSEBIs integrands for two angular ranges, $[1',100']$ and $[0.8',350']$, where we only show the integrands for the lowest COSEBIs mode, as the higher modes generally probe larger $\ell$-modes.
 Finally, the lower panel shows the integrands of aperture mass dispersion statistics, for the same two maximum angular ranges.
@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{figures/IntegKsip.pdf}\\
-\includegraphics[width=0.5\textwidth]{figures/IntegCOSEBIs.pdf}\\
-\includegraphics[width=0.5\textwidth]{figures/IntegMap.pdf}
+\begin{tabular}{ccc}
+\includegraphics[width=0.31\textwidth]{figures/IntegKsip.pdf} &
+\includegraphics[width=0.31\textwidth]{figures/IntegCOSEBIs.pdf} &
+\includegraphics[width=0.31\textwidth]{figures/IntegMap.pdf}
+\end{tabular}
 \caption{ \label{fig:filters}. Integrand of $\xi_+$, $E_1$ (E-COSEBIs) and $M^2_{\rm ap}$, respectively.
-All the values are normalized with respect to their maximum value. Two cases are shown for each statistic. 
-For COSEBIs this is an angular range indicated in the caption. For aperture mass statistic $\theta_{\rm max}=2\theta$ is shown.
-Note that higher order COSEBIs modes generally probe larger $\ell$-modes, hence here we only show the lowest mode $E_1$. 
+Two cases are shown for each statistic as listed in each caption.
+For the aperture mass statistic $\theta_{\rm max}=2\theta$ is shown. 
+Note that higher order COSEBIs modes generally probe larger $\ell$-modes, hence here we only show the lowest mode $E_1$. All values are normalized with respect to their maximum value. 
 }
@@
 \subsection{On the application to CMB lensing}
-\citet{kitching/etal:2016} argue that their correction to the Limber and flat sky approximations would also affect predictions involving the shear and convergence cross-spectrum, such that CMB lensing - galaxy lensing cross-correlation should include a pre-term $ [(\ell*(\ell+1))^2]/(\ell+1/2)^4.$.
+\citet{kitching/etal:2016} argue that their correction to the Limber and flat sky approximations would also affect predictions involving the shear and convergence cross-spectrum, such that CMB lensing - galaxy lensing cross-correlation should include a pre-term $ [\ell(\ell+1)]^2/(\ell+ 0.5)^4.$.
 We have verified that this term would have negligible impact on the current measurements, given the relatively low signal to noise ratio.
 For example, most measurements \citep{hand/etal:2015, liu/hill:2015, kirk/etal:2016,harnois-deraps/etal:2016} are carried over angular multipoles in the range $\ell \in [20-2000]$, and are organized in $\sim$ five bins.
-The size of the pre-term $[\ell/(\ell+0.5)]^4$, averaged over the first bin, is of the order of 2\%, and then becomes sub-percent for all other bins.
+The size of the pre-term $ [(\ell(\ell+1))^2]/(\ell+ 0.5)^4.$, averaged over the first bin, is of the order of 2\%, and then becomes sub-percent for all other bins.
 In comparison, the size of the statistical error bars are of the order 25-35\% with additional uncertainty due to photometric redshifts (10-15\%) and intrinsic galaxy alignments (10-15\%).

### 2016-12-06 photoz.tex
Included JHD 2nd round of comments

@@
 In \citet{choi/etal:2016} a cross-correlation clustering analysis, between photometric redshift slices and overlapping spectroscopic redshifts, is used to determine linear biases in the CFHTLenS photometric redshift distributions.
-The maximum redshift $z_B<0.9$ in this analysis was limited by the redshift overlap with the spectroscopic sample\footnote{The implication of a $z_B < 0.9$ high-redshift limit is that the analysis is unable to constrain the high-redshift tails of the redshift distributions due to the lack of high-$z$ spec-$z$ samples.
+The maximum redshift $z_B<0.9$ in this analysis was limited by the redshift overlap with the spectroscopic sample\footnote{The implication of a $z_B < 0.9$ high-redshift limit is that the analysis is unable to constrain the high-redshift tails of the redshift distributions due to the lack of overlapping high-redshift spectroscopic samples.
 As such the results from \citet{choi/etal:2016} are only the first important step towards a detailed understanding of the CFHTLenS tomographic redshift distributions and as such may be revised in the future.}.
@@
 Increasing the mean redshift implies a reduction in the recovered amplitude of $\sigma_8$.
-Using the same toy-model' analysis of \citet{choi/etal:2016} we would expect this change in the mean redshift to {\it reduce} the recovered amplitude of $\sigma_8$ by $\sim 5$\%.
+Using the same `toy-model' analysis of \citet{choi/etal:2016} we would expect this change in the mean redshift to {\it reduce} the recovered amplitude of $\sigma_8$ by $\sim 5$\%.
 From this we suggest that \cite{kitching/etal:2016} could have misinterpreted the direction of the redshift biases reported in \citet{choi/etal:2016}.

### 2016-12-06 theory.tex
Included JHD 2nd round of comments

@@
 \be 
-P^{ij}_\gamma(\ell) = T_l \int_0^{\chi_{\rm H}} \d \chi \, \frac{q_i(\chi)q_j(\chi)}{[f_K(\chi)]^2} \, P_\delta \left( \frac{\nu}{f_K(\chi)},\chi \right).
+P^{ij}_\gamma(\ell) = T_l \int_0^{\chi_{\rm H}} \d \chi \, \frac{q_i(\chi)q_j(\chi)}{[f_K(\chi)]^2} \, P_\delta \left( \frac{\nu(\ell)}{f_K(\chi)},\chi \right).
 \label{eqn:Pkappa} 
@@
 Here $f_K(\chi)$ is the comoving angular diameter distance out to comoving radial distance $\chi$ and $\chi_{\rm H}$ is the comoving horizon distance.
-The lensing efficiency function $q(\chi)$ is given in equation (5) of \citet{hildebrandt/etal:2016}.
+The lensing efficiency function $q(\chi)$ is given in equation (5) of \citet{hildebrandt/etal:2016}, and the value of $\nu(\ell)$ depends on whether a baseline Limber approximation ($\nu(\ell) = \ell$), or the more accurate extended Limber approximation ($\nu(\ell) = \ell + 0.5$) from \citet{loverde/afshordi:2008} is used.
 \citet{kitching/etal:2016} show that the pre-factor $T_\ell$ for the shear power spectrum is given by
@@
 When a survey is sufficiently small, a flat-sky approximation can be made reducing $T_\ell \approx 1$.
-The value of $\nu$ depends on whether a baseline Limber approximation, or the more accurate extended Limber approximation of \citet{loverde/afshordi:2008} is used.
-In the text of \citet{kitching/etal:2016} it is not fully clear which combinations of  $T_\ell$ and $\nu$ are considered, so we review them all as summarised in Table~\ref{tab:Tl_nu}, also highlighting which combinations were used in recent cosmic shear analyses.
+In \citet{kitching/etal:2016} it is not fully clear which combinations of  $T_\ell$ and $\nu(\ell)$ are considered, so we review them all as summarised in Table~\ref{tab:Tl_nu}, also highlighting which combinations were used in recent cosmic shear analyses.
 
@@
  \caption{Variations on the different approximations that can be made when calculating the shear power spectrum $P_\gamma(\ell)$ (equation~\ref{eqn:Pkappa}), using a Limber approximation.
-$^*$We apologise for the typographical error in equation 4 of \citet{hildebrandt/etal:2016} which should include the extra term of `$+0.5$' in $\nu$ that was incorporated in the cosmological analysis.}
+$^*$We confirm that there is a typographical error in equation 4 of \citet{hildebrandt/etal:2016} which should include the extra term of `$+0.5$' in $\nu$ that was incorporated in the cosmological analysis.}
  \end{table}
@@
 \emph{Lower Panels:} Deviations with respect to the extended Limber spherical sky model (ELS).
-The dashed lines in the left panels show the largest angular scale used in the recent KIDS cosmic shear analysis where an Extended Standard (ESt) analysis was used.}
+The dashed lines in the right panels show the largest angular scale used in the recent KIDS cosmic shear analysis where an Extended Standard (ESt) analysis was used.}
  \end{center}

### 2016-12-06 cfhtlens.tex
added LvW's comments

@@
 the weights placed on each $\ell$ scale),  for two cases, normalised to their maximum value.
-The upper panel shows the integrand\footnote{Note that the lower left panel of Fig.
+The right panel shows the integrand\footnote{Note that the lower left panel of Fig.
 1 in \citet{kitching/etal:2016} shows an integrated form of this function for a maximum
@@
 The middle panel in Figure~\ref{fig:filters} shows COSEBIs integrands for two angular ranges, $[1',100']$ and $[0.8',350']$, where we only show the integrands for the lowest COSEBIs mode, as the higher modes generally probe larger $\ell$-modes.
-Finally, the lower panel shows the integrands of aperture mass dispersion statistics, for the same two maximum angular ranges.
+Finally, the left panel shows the integrands of aperture mass dispersion statistics, for the same two maximum angular ranges.
 From Figure~\ref{fig:filters} we can see that the two-point cosmic shear statistics tested by \citet{kilbinger/etal:2013} exhibit different dependences between the angular scales sampled and the $\ell$-range probed.
@@
 We note that any future comparison of mock data with full curved sky non-Limber predictions will place requirements on the input weak lensing simulations.
-Many currently work with parallel plane mass-sheets as opposed to curved sky mass-sheets and at large angles, these two approaches differ regardless of the box size.
+Many work with parallel plane mass-sheets as opposed to curved sky mass-sheets and at large angles these two approaches differ, regardless of the box size.
 

### 2016-12-06 theory.tex
added LvW's comments

@@
  \begin{table}[htb]
-\label{tab:Tl_nu}
 \begin{center}
@@
  \end{center}
- \caption{Variations on the different approximations that can be made when calculating the shear power spectrum $P_\gamma(\ell)$ (equation~\ref{eqn:Pkappa}), using a Limber approximation.
+ \caption{\label{tab:Tl_nu}Variations on the different approximations that can be made when calculating the shear power spectrum $P_\gamma(\ell)$ (equation~\ref{eqn:Pkappa}), using a Limber approximation.
 $^*$We confirm that there is a typographical error in equation 4 of \citet{hildebrandt/etal:2016} which should include the extra term of `$+0.5$' in $\nu$ that was incorporated in the cosmological analysis.}
@@
  \includegraphics[width=0.85\textwidth]{figures/Cl_xi_comp.pdf}
- \label{fig:Cl_xi}
- \caption{\emph{Upper Panels:} Theoretical models for the shear power spectrum (\emph{left}) and shear correlation function $\xi_+$ (\emph{right}) for the different approximations listed in Table~\ref{tab:Tl_nu}, assuming a \citet{planck/cosmo:2015} cosmology and the 2D CFHTLenS redshift distribution.
+ \caption{ \label{fig:Cl_xi}\emph{Upper Panels:} Theoretical models for the shear power spectrum (\emph{left}) and shear correlation function $\xi_+$ (\emph{right}) for the different approximations listed in Table~\ref{tab:Tl_nu}, assuming a \citet{planck/cosmo:2015} cosmology and the 2D CFHTLenS redshift distribution.
 \emph{Lower Panels:} Deviations with respect to the extended Limber spherical sky model (ELS).

### 2016-12-06 theory.tex
added LvW extra refs

@@
 \subsection{The Flat-Sky approximation and Extended Limber Approximation}
-The baseline measurement for many cosmic shear studies has focused on the two-point shear correlation function between two tomographic bins $ij$ \citep[for more details see][and references therein]{bartelmann/schneider:2001}, given by
+The baseline measurement for many cosmic shear studies has focused on the two-point shear correlation function between two tomographic bins $ij$ \citep[for more details see][and references therein]{miraldaescude:1991, kaiser:1992, bartelmann/schneider:2001}, given by
 \be

### 2016-12-06 cfhtlens.tex
cfhtlens.tex
Added MV comment on FC paper

@@
 \item{\citet{kuijken/etal:2015} showed that the CFHTLenS shear calibration corrections derived in \citet{miller/etal:2013} were underestimated as a result of an imperfect match between the galaxy populations in the data and image simulations.}
-\item{\citet{fenechconti/etal:2016} demonstrated that the CFHTLenS data would have been subject to a weight bias that favours galaxies that are more intrinsically oriented with the point-spread function.}
+\item{\citet{fenechconti/etal:2016} demonstrated that the CFHTLenS data would have been subject to a weight bias that favours galaxies that are more intrinsically oriented with the point-spread function.
+They also showed that the impact of calibration selection biases, that were not considered in \citet{miller/etal:2013}, would have lead to the over-correction of multiplicative shear bias in the CFHTLenS analyses, by a few percent.}
 \item{\citet{joudaki/etal:2016} updated the CFHTLenS covariance matrices using larger-box numerical simulations that were less subject to the lack of power on large scales.}

### 2016-12-06 cfhtlens.tex
minor edits

@@
 Efforts are now underway to fully re-analyse CFHTLenS using the advanced KiDS analysis pipeline with revised shape measurements and calibrations for the shear and photometric redshifts.
-
 Given the known shortcomings with the original CFHTLenS results, which will impact in different ways on the cosmological conclusions that one can draw from the survey, it is surprising that \citet{kitching/etal:2016} chose to focus their study on the cosmic shear analysis of \citet{kilbinger/etal:2013}.
@@
 They find a conditional value of $\sigma_8 = 0.789 \pm 0.015$ for their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) of the data from \citet{kilbinger/etal:2013}.
-We argue that this artificial reduction in the error by a factor of $\sim 2$, in comparison to a full six-parameter fit, could easily mislead, making it appear that the impact of removing all approximations from the theoretical analysis is more significant for current surveys than it is in reality.
+We argue that this reduction in the error by a factor of $\sim 2$, in comparison to a full six-parameter fit, could easily mislead, making it appear that the impact of removing all approximations from the theoretical analysis is more significant for current surveys than it is in reality.
 Nevertheless, we repeated the `one-parameter' analysis for the full range of Limber cases listed in Table~\ref{tab:Tl_nu} finding the lowest conditional value of $\sigma_8 = 0.743 \pm 0.023$ for the `Standard' (KSt) case and the highest conditional value of $\sigma_8 = 0.744 \pm 0.023$ for the `Baseline Limber Flat` (LF) case.
@@
 The rationale is based on the Hankel transform in equation~\ref{eqn:xiGG} which is derived assuming a flat-sky approximation.
-As shown in Figure~\ref{fig:Cl_xi}, however their chosen version of a flat-sky approximation serves to exacerbates the tension in theoretical models when a flat-sky solution is compared with the spherical-sky solution.
-We do not find this to be the case when considering the Standard $T_\ell = 1$ flat-sky approximation that has been used in the majority of cosmic shear studies to date.
+As shown in Figure~\ref{fig:Cl_xi}, however their chosen version of a flat-sky approximation serves to exacerbate the tension in theoretical models when a flat-sky solution is compared with the spherical-sky solution.
+We do not find this to be the case when considering the standard $T_\ell = 1$ flat-sky approximation that has been used in the majority of cosmic shear studies to date.
 
@@
 Finally, the left panel shows the integrands of aperture mass dispersion statistics, for the same two maximum angular ranges.
+
 From Figure~\ref{fig:filters} we can see that the two-point cosmic shear statistics tested by \citet{kilbinger/etal:2013} exhibit different dependences between the angular scales sampled and the $\ell$-range probed.
 If a significant bias had been introduced at low-$\ell$ by using flat-sky and Limber approximations, we would then expect to see a systematic shift between the different two-point statistics with the COSEBIs statistic being essentially unaffected as it only includes modes with $\ell \gtrsim 80$.
-This is found not to be the case with all three statistics finding $\sigma_8 (\Omega_m/0.27)^\alpha = 0.79$ with errors that range from $0.03$ to $0.06$ \citep[see Table 5 of][]{kilbinger/etal:2013}.
+This is found not to be the case with all three statistics finding $\sigma_8 (\Omega_m/0.27)^\alpha = 0.79$ with errors that range from $0.03$ to $0.06$, and $\alpha$ ranging from $0.59$ to 0.7 \citep[see Table 5 of][]{kilbinger/etal:2013}.
 This comparison further supports our argument that the approximations highlighted by \citet{kitching/etal:2016} have negligible impact for current surveys.
@@
 
-We note that any future comparison of mock data with full curved sky non-Limber predictions will place requirements on the input weak lensing simulations.
+We note that any future comparison of mock data with full curved sky non-Limber predictions would place requirements on the input weak lensing simulations.
 Many work with parallel plane mass-sheets as opposed to curved sky mass-sheets and at large angles these two approaches differ, regardless of the box size.

### 2016-12-06 theory.tex
minor edits

@@
 Here $f_K(\chi)$ is the comoving angular diameter distance out to comoving radial distance $\chi$ and $\chi_{\rm H}$ is the comoving horizon distance.
-The lensing efficiency function $q(\chi)$ is given in equation (5) of \citet{hildebrandt/etal:2016}, and the value of $\nu(\ell)$ depends on whether a baseline Limber approximation ($\nu(\ell) = \ell$), or the more accurate extended Limber approximation ($\nu(\ell) = \ell + 0.5$) from \citet{loverde/afshordi:2008} is used.
+The lensing efficiency function $q(\chi)$ is given in equation (5) of \citet{hildebrandt/etal:2016}, and the value of $\nu(\ell)$ depends on whether a baseline Limber approximation, $\nu(\ell) = \ell$, or the more accurate extended Limber approximation, $\nu(\ell) = \ell + 0.5$, from \citet{loverde/afshordi:2008} is used.
 \citet{kitching/etal:2016} show that the pre-factor $T_\ell$ for the shear power spectrum is given by
@@
  \caption{\label{tab:Tl_nu}Variations on the different approximations that can be made when calculating the shear power spectrum $P_\gamma(\ell)$ (equation~\ref{eqn:Pkappa}), using a Limber approximation.
-$^*$We confirm that there is a typographical error in equation 4 of \citet{hildebrandt/etal:2016} which should include the extra term of `$+0.5$' in $\nu$ that was incorporated in the cosmological analysis.}
+$^*$We confirm that there is a typographical error in equation 4 of \citet{hildebrandt/etal:2016} which should include the extra term of `$+0.5$' in $\nu(\ell)$ that was incorporated in the cosmological analysis.}
  \end{table}
@@
 As shown in the lower panels of Figure~\ref{fig:Cl_xi}, the `standard flat' sky approximation used by recent cosmic shear surveys, where $T_\ell = 1$, recovers a very similar result to the spherical sky case.
-Over angular scales used in the recent KiDS analysis (shown dashed), these curves differ by less than 1\% as such the standard flat-sky approximations that have been used will not impact the cosmological analyses of current surveys.
+Over angular scales used in the recent KiDS cosmic shear analysis (where the maximum angular scale is shown dashed), these curves differ by less than 1\%.
+As such the standard flat-sky approximations that have been used will not impact the cosmological analyses of current surveys.
 

### 2016-12-06 Limber_Comment.tex
included comments from KK

@@
 Recently, however, \citet{kitching/etal:2016} reported that when considering the flat sky and Limber approximations in concert, tensions between weak lensing and CMB experiments can be reduced.
-This was demonstrated with a re-analysis of the non-tomographic weak lensing data from the CFHTLenS survey \citep{kilbinger/etal:2013}.
+They demonstrate the effect with a re-analysis of the non-tomographic weak lensing data from the CFHTLenS survey \citep{kilbinger/etal:2013}.
 
@@
 In section~\ref{sec:photoz} we review our current knowledge of photometric redshift uncertainties and the sophisticated mitigation strategies that have already been applied to data.
-We suggest that a possible misinterpretation in the direction of the redshift biases reported in \citet{choi/etal:2016} has lead to the incorrect conclusion of \citet{kitching/etal:2016} that these redshift biases can resolve the tension with Planck.
+We suggest that a possible misinterpretation in the sign of the redshift biases reported in \citet{choi/etal:2016} has led to the incorrect conclusion of \citet{kitching/etal:2016} that these redshift biases can resolve the tension with Planck.
 

### 2016-12-06 cfhtlens.tex
included comments from KK

@@
-The Canada-France-Hawaii Telescope Lensing Survey (CFHTLenS) represented a major step forward for the field of weak gravitational lensing, in terms of improved accuracy in data reduction \citep{erben/etal:2013}, the implementation of Gaussianised matched multi-band photometry \citep{hildebrandt/etal:2012}, cross-correlation clustering analysis between photometric redshift slices to verify tomographic redshift distributions \citep{benjamin/etal:2013}, accurate calibrated shape measurements \citep{miller/etal:2013} and a full suite of informative systematic tests to select a clean data set \citep{heymans/etal:2012}.
+The Canada-France-Hawaii Telescope Lensing Survey (CFHTLenS) represented a major step forward for the field of weak gravitational lensing, in terms of improved accuracy in data reduction \citep{erben/etal:2013}, the implementation of PSF-Gaussianised matched multi-band photometry \citep{hildebrandt/etal:2012}, cross-correlation clustering analysis between photometric redshift slices to verify tomographic redshift distributions \citep{benjamin/etal:2013}, accurate calibrated shape measurements \citep{miller/etal:2013} and a full suite of informative systematic tests to select a clean data set \citep{heymans/etal:2012}.
 Since the public release of this survey in 2013, the community has continued to scrutinise and advance our understanding of CFHTLenS by identifying a number of areas where analyses could improve:
@@
 We argue that this reduction in the error by a factor of $\sim 2$, in comparison to a full six-parameter fit, could easily mislead, making it appear that the impact of removing all approximations from the theoretical analysis is more significant for current surveys than it is in reality.
-Nevertheless, we repeated the `one-parameter' analysis for the full range of Limber cases listed in Table~\ref{tab:Tl_nu} finding the lowest conditional value of $\sigma_8 = 0.743 \pm 0.023$ for the `Standard' (KSt) case and the highest conditional value of $\sigma_8 = 0.744 \pm 0.023$ for the `Baseline Limber Flat` (LF) case.
+Nevertheless, we repeated the `one-parameter' analysis for the full range of Limber cases listed in Table~\ref{tab:Tl_nu} and are unable to confirm their results.
+We find the lowest conditional value of $\sigma_8 = 0.743 \pm 0.023$ for the `Standard' (KSt) case and the highest conditional value of $\sigma_8 = 0.744 \pm 0.023$ for the `Baseline Limber Flat` (LF) case.
 As expected from the comparison in Figure~\ref{fig:Cl_xi} the different combinations of assuming flat or spherical sky, baseline or extended Limber, make little difference to the cosmological parameter constraints, even in this `one-parameter' analysis.
@@
 \subsection{On the application to CMB lensing}
-\citet{kitching/etal:2016} argue that their correction to the Limber and flat sky approximations would also affect predictions involving the shear and convergence cross-spectrum, such that CMB lensing - galaxy lensing cross-correlation should include a pre-term $ [\ell(\ell+1)]^2/(\ell+ 0.5)^4.$.
-We have verified that this term would have negligible impact on the current measurements, given the relatively low signal to noise ratio.
+\citet{kitching/etal:2016} argue that their correction to the Limber and flat sky approximations would also affect predictions involving the shear and convergence cross-spectrum, such that CMB lensing - galaxy lensing cross-correlation should include a pre-term $ [\ell(\ell+1)]^2/(\ell+ 0.5)^4$.
+We have verified that this term would have negligible impact on current measurements, given the relatively low signal to noise ratio.
 For example, most measurements \citep{hand/etal:2015, liu/hill:2015, kirk/etal:2016,harnois-deraps/etal:2016} are carried over angular multipoles in the range $\ell \in [20-2000]$, and are organized in $\sim$ five bins.
-The size of the pre-term $ [(\ell(\ell+1))^2]/(\ell+ 0.5)^4.$, averaged over the first bin, is of the order of 2\%, and then becomes sub-percent for all other bins.
+The size of the pre-term $ [(\ell(\ell+1))^2]/(\ell+ 0.5)^4$, averaged over the first bin, is of the order of 2\%, and then becomes sub-percent for all other bins.
 In comparison, the size of the statistical error bars are of the order 25-35\% with additional uncertainty due to photometric redshifts (10-15\%) and intrinsic galaxy alignments (10-15\%).

### 2016-12-06 conclusion.tex
included comments from KK

@@
 This has been shown to be insufficient to capture the full complexity of the problem.
-More importantly though, it seems like \cite{kitching/etal:2016} apply the photo-$z$ calibrations from \cite{choi/etal:2016} in the wrong direction.
-Instead of alleviating the tension between CFHTLenS and Planck a correct application of the offsets would increase the discrepancy, in agreement with a recent re-analysis of the CFHTLenS data \citep{joudaki/etal:2016} as well as results from the KiDS project \citep{hildebrandt/etal:2016}.
+More importantly though, we suggest that \cite{kitching/etal:2016} have applied the photo-$z$ calibrations from \cite{choi/etal:2016} in the wrong sense.
+Instead of alleviating the tension between CFHTLenS and Planck a correct application of the offsets would increase the discrepancy, as shown with a recent re-analysis of the CFHTLenS data \citep{joudaki/etal:2016} as well as results from the KiDS project \citep{hildebrandt/etal:2016}.

### 2016-12-06 photoz.tex
included comments from KK

@@
 Multiple bootstrap samples of the resulting calibrated distribution allowed for the characterisation of both the uncertainty in the mean and shape of the redshift distribution.
-The inclusion of this more sophisticated treatment of photometric redshift errors did not alleviate the tension between Planck and KiDS parameter constraints.
+The inclusion of this more sophisticated treatment of photometric redshift errors was not found to alleviate the tension between Planck and KiDS parameter constraints.
 

### 2016-12-06 theory.tex
included comments from KK

@@
 In collecting our comments on \citet{kitching/etal:2016} we contacted colleagues who had previously tested the impact of the Limber approximation on cosmic shear studies by comparing a Limber approximated cosmic shear power spectrum with an exact calculation.
-The majority of these analyses, carried out many years ago, remained unpublished as no significant deviation was found.
+The majority of these analyses, carried out many years ago, remained unpublished in peer reviewed journals as no significant deviation was found\footnote{See for example appendix M of the 2010 PhD thesis from Donghui Jeong (\url{http://www.personal.psu.edu/duj13/dissertation/djeong_diss_appM.pdf}) and Chapter 7 of 2012 PhD thesis from Nicolas Van de Rijt (\url{http://ipht.cea.fr/Docspht/articles/t12/080/public/these_vanderijt2012.pdf}).}.
 One notable exception, however, is \citet{giannantonio/etal:2012} who find that for a cosmic shear power spectrum, the extended Limber approximation is consistent with the exact calculation for $\ell>5$, with any differences well within cosmic-variance errors for a Euclid-like survey\footnote{\citet{kitching/etal:2016} comment on this result, but indicate that it is in error owing to the application of a fixed low-$\ell$ limit.
@@
 Given the insignificant effect of using the Limber approximation found by various groups, the ability to calculate an exact non-Limber solution has unfortunately not been maintained in theoretical code over the years.
-Instead these codes have evolved to account for important approximations such as the impact of baryon feedback on the matter power spectrum and non-zero neutrino masses \citep[see for example][]{joudaki/etal:2016, mead/etal:2016}.
+Instead these codes have evolved to account for (much more) important approximations such as the impact of baryon feedback on the matter power spectrum and non-zero neutrino masses \citep[see for example][]{joudaki/etal:2016, mead/etal:2016}.
 We are therefore unable to readily determine non-Limber theoretical calculations for the shear-correlation function to directly compare with the results of \citet{kitching/etal:2016}.

### 2016-12-06 theory.tex
Added Limber 1953 reference

@@
 \ee
-where $J_{0,4} (\ell \theta)$ is the zeroth (for $\xi_+$) or fourth (for $\xi_- $) order Bessel function of the first kind and $P_\gamma(\ell)$ is the shear power spectrum at angular wave number $\ell$ which can be related to the underlying matter power spectrum $P_\delta$, using a Limber approximation as,
+where $J_{0,4} (\ell \theta)$ is the zeroth (for $\xi_+$) or fourth (for $\xi_- $) order Bessel function of the first kind and $P_\gamma(\ell)$ is the shear power spectrum at angular wave number $\ell$ which can be related to the underlying matter power spectrum $P_\delta$, using a Limber approximation \citep{limber:1953} as,
 \be 

### 2016-12-06 cfhtlens.tex
cfhtlens.tex: Added JHD update

@@
 \subsection{On the application to CMB lensing}
-\citet{kitching/etal:2016} argue that their correction to the Limber and flat sky approximations would also affect predictions involving the shear and convergence cross-spectrum, such that CMB lensing - galaxy lensing cross-correlation should include a pre-term $ [\ell(\ell+1)]^2/(\ell+ 0.5)^4$.
+\citet{kitching/etal:2016} discuss how corrections to the Limber and flat sky approximations would also affect predictions involving the shear and convergence cross-spectrum, such that the CMB lensing - galaxy lensing cross-correlation should include a pre-term $ [\ell(\ell+1)]^2/(\ell+ 0.5)^4$.
 We have verified that this term would have negligible impact on current measurements, given the relatively low signal to noise ratio.
-For example, most measurements \citep{hand/etal:2015, liu/hill:2015, kirk/etal:2016,harnois-deraps/etal:2016} are carried over angular multipoles in the range $\ell \in [20-2000]$, and are organized in $\sim$ five bins.
-The size of the pre-term $ [(\ell(\ell+1))^2]/(\ell+ 0.5)^4$, averaged over the first bin, is of the order of 2\%, and then becomes sub-percent for all other bins.
+For example, most measurements \citep{hand/etal:2015, liu/hill:2015, kirk/etal:2016,harnois-deraps/etal:2016} are carried over angular multipoles in the range $\ell \in [20-2000]$.
+The size of the pre-term, averaged over this range, is of the order of 0.01\%.
 In comparison, the size of the statistical error bars are of the order 25-35\% with additional uncertainty due to photometric redshifts (10-15\%) and intrinsic galaxy alignments (10-15\%).
+The pre-term reaches 1\% only for $\ell < 7$, which will become relevant for very large upcoming surveys but is negligible for current surveys.

### 2016-12-06 cfhtlens.tex
updates from shahab

@@
 They find a conditional value of $\sigma_8 = 0.789 \pm 0.015$ for their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) of the data from \citet{kilbinger/etal:2013}.
-We argue that this reduction in the error by a factor of $\sim 2$, in comparison to a full six-parameter fit, could easily mislead, making it appear that the impact of removing all approximations from the theoretical analysis is more significant for current surveys than it is in reality.
-Nevertheless, we repeated the `one-parameter' analysis for the full range of Limber cases listed in Table~\ref{tab:Tl_nu} and are unable to confirm their results.
-We find the lowest conditional value of $\sigma_8 = 0.743 \pm 0.023$ for the `Standard' (KSt) case and the highest conditional value of $\sigma_8 = 0.744 \pm 0.023$ for the `Baseline Limber Flat` (LF) case.
-As expected from the comparison in Figure~\ref{fig:Cl_xi} the different combinations of assuming flat or spherical sky, baseline or extended Limber, make little difference to the cosmological parameter constraints, even in this `one-parameter' analysis.
+This can be compared to the full five-parameter fit from \citet{kilbinger/etal:2013} who find $S_8=\sigma_8(\Omega_m/0.3)^{0.6} = 0.74 \pm 0.03$.
+We argue that this reduction in the relevant error by a factor of $\sim 2$, could easily mislead, making it appear that the impact of removing all approximations from the theoretical analysis is more significant for current surveys than it is in reality.
+Nevertheless, we repeated the `one-parameter' analysis for the full range of Limber cases listed in Table~\ref{tab:Tl_nu} and are unable to confirm the results quoted by \citet{kitching/etal:2016} {\bf TBD:  The results that follow use the exact Planck 2015 cosmology.
+We just noticed footnote 5 in Kitching et al that shows that they've actually used an approximate Planck 2015 cosmology - currently re-running with this alternative which is unlikely to change these results significantly}.
+We find the lowest conditional value of $\sigma_8 = 0.743 \pm 0.023$ for the `Standard' (KSt) case and the highest conditional value of $\sigma_8 = 0.744 \pm 0.023$ for the `Baseline Limber Flat` (LF) case, noting that fluctuations between different MCMC runs are of the order 0.001.
+Therefore, as expected from the comparison in Figure~\ref{fig:Cl_xi}, we find that the different combinations of assuming flat or spherical sky, baseline or extended Limber, make little difference to the cosmological parameter constraints, even in this `one-parameter' analysis.
 
-We find our Limber-case findings to be in disagreement with \citet{kitching/etal:2016} who find a shift of $\Delta \sigma_8 = 0.007$ between their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) and their `Limber' analysis (which we believe corresponds to the Extended Limber spherical (ELS) case in Table~\ref{tab:Tl_nu}).
+Our Limber-case findings are in disagreement with \citet{kitching/etal:2016} who find a shift of $\Delta \sigma_8 = 0.007$ between their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) and their `Limber' analysis (which we believe corresponds to the Extended Limber spherical (ELS) case in Table~\ref{tab:Tl_nu}).
 

### 2016-12-06 cfhtlens.tex
cfhtlens.tex:
Therefore, as expected from the comparison in Figure~\ref{fig:Cl_xi}, and given the low signal-to-noise CFHTLenS measurements on large scales, we find that the different combinations of assuming flat or spherical sky, baseline or extended Limber, make little difference to the cosmological parameter constraints, even in this `one-parameter' analysis.

@@
 We find the lowest conditional value of $\sigma_8 = 0.743 \pm 0.023$ for the `Standard' (KSt) case and the highest conditional value of $\sigma_8 = 0.744 \pm 0.023$ for the `Baseline Limber Flat` (LF) case, noting that fluctuations between different MCMC runs are of the order 0.001.
-Therefore, as expected from the comparison in Figure~\ref{fig:Cl_xi}, we find that the different combinations of assuming flat or spherical sky, baseline or extended Limber, make little difference to the cosmological parameter constraints, even in this `one-parameter' analysis.
+Therefore, as expected from the comparison in Figure~\ref{fig:Cl_xi}, and given the low signal-to-noise CFHTLenS measurements on large scales, we find that the different combinations of assuming flat or spherical sky, baseline or extended Limber, make little difference to the cosmological parameter constraints, even in this `one-parameter' analysis.
 

### 2016-12-06 cfhtlens.tex
Fig 2 caption and description changed

@@
 \subsection{Comparison of two-point shear statistics; the two-point correlation function, mass aperture statistic and COSEBIs}
-\citet{kilbinger/etal:2013} present a detailed comparison of cosmological constraints obtained from a range different two-point shear statistics including the shear correlation function, $\xi_\pm$, the mass aperture statistic, $M_ {\rm ap}^2$ \citep{schneider/etal:1998}, and the COSEBIs statistics \citep{schneider/etal:2010}.
-Figure~\ref{fig:filters} shows the integrands of these statistics (i.e.
-the weights placed on each $\ell$ scale),  for two cases, normalised to their maximum value.
+\citet{kilbinger/etal:2013} present a detailed comparison of cosmological constraints obtained from a range different two-point shear statistics including the shear correlation function, $\xi_\pm$, the aperture-mass dispersion, $M_ {\rm ap}^2$ \citep{schneider/etal:1998}, and the COSEBIs \citep{schneider/etal:2010}.
+Figure~\ref{fig:filters} shows the integrands of these statistics
+% (i.e. the weights placed on each $\ell$ scale),  
+for two cases, normalised to their maximum value.
+The integrands are of the form $\ell F(\ell) P(\ell)$, where $F(\ell)=J_0(\ell)$ for $\xi_+$, $F(\ell)= U^2_\theta(\ell)$ for  $M_ {\rm ap}^2$ \citep[see][]{schneider/etal:1998} and $F(\ell)=W_n(\ell)$ for COSEBIs \citep[see][]{schneider/etal:2010}.
+For $\xi_\pm$, $P(\ell)$ is equal to the sum of the E and B-mode convergence power spectra.
+This is one of the main motivators for the development of aperture-mass dispersion.
+However, $M_ {\rm ap}^2$ statistics is a lossy conversion and is biased by small angular separations,
+where blending of galaxies makes shear measurement challenging/impossible \citep{Kilbinger/etal:2006}. As a result, COSEBIs was developed which tackles both shortcomings of $M_ {\rm ap}^2$ statistics.
 The right panel shows the integrand\footnote{Note that the lower left panel of Fig.
-1 in \citet{kitching/etal:2016} shows an integrated form of this function for a maximum
-angular separation of $100'$. However, in \citet{kilbinger/etal:2013}, the data used in \citet{kitching/etal:2016}, 
-the maximum $\theta$ is $350'$.} of $\xi_+$ for $\theta=100'$ and $\theta=350'$.
+1 in \citet{kitching/etal:2016} shows an integrated form of this function for a maximum angular separation of $100'$.
+However, in \citet{kilbinger/etal:2013}, the data used in \citet{kitching/etal:2016}, $\theta$ is between $0.8'$ and $350'$.} of $\xi_+$ for $\theta=100'$ and $\theta=350'$.
 The middle panel in Figure~\ref{fig:filters} shows COSEBIs integrands for two angular ranges, $[1',100']$ and $[0.8',350']$, where we only show the integrands for the lowest COSEBIs mode, as the higher modes generally probe larger $\ell$-modes.
@@
 \caption{ \label{fig:filters}. Integrand of $\xi_+$, $E_1$ (E-COSEBIs) and $M^2_{\rm ap}$, respectively.
+All integrands are of the form $\ell F(\ell) P(\ell)$, where $F(\ell)$ is the corresponding weight-function
+for each statistic and $P(\ell)$ is the E-mode convergence power spectrum, with the exception of $\xi_+$, for which
+$P(\ell)$ is equal to the sum of E and B-mode power spectra. 
 Two cases are shown for each statistic as listed in each caption.
 For the aperture mass statistic $\theta_{\rm max}=2\theta$ is shown. 
-Note that higher order COSEBIs modes generally probe larger $\ell$-modes, hence here we only show the lowest mode $E_1$. All values are normalized with respect to their maximum value. 
+Note that higher order COSEBIs modes generally probe larger $\ell$-modes, 
+hence here we only show the lowest mode $E_1$. All values are normalized with respect to their maximum value. 
 }

### 2016-12-07 cfhtlens.tex
minor changes to cfhtlens.tex
minor update and comment

@@
 We argue that this reduction in the relevant error by a factor of $\sim 2$, could easily mislead, making it appear that the impact of removing all approximations from the theoretical analysis is more significant for current surveys than it is in reality.
-Nevertheless, we repeated the `one-parameter' analysis for the full range of Limber cases listed in Table~\ref{tab:Tl_nu} and are unable to confirm the results quoted by \citet{kitching/etal:2016} {\bf TBD:  The results that follow use the exact Planck 2015 cosmology.
+Nevertheless, we repeated the `one-parameter' analysis for the full range of Limber cases listed in Table~\ref{tab:Tl_nu} and are unable to confirm the results quoted by \citet{kitching/etal:2016}.
+%{\bf TBD:  The results that follow use the exact Planck 2015 cosmology.
 We just noticed footnote 5 in Kitching et al that shows that they've actually used an approximate Planck 2015 cosmology - currently re-running with this alternative which is unlikely to change these results significantly}.
-We find the lowest conditional value of $\sigma_8 = 0.743 \pm 0.023$ for the `Standard' (KSt) case and the highest conditional value of $\sigma_8 = 0.744 \pm 0.023$ for the `Baseline Limber Flat` (LF) case, noting that fluctuations between different MCMC runs are of the order 0.001.
+We find the lowest conditional value of $\sigma_8 = 0.7461 \pm 0.0231$ for the `Standard' (KSt) case and the highest conditional value of $\sigma_8 = 0.7487 \pm 0.0232$ for the `Baseline Limber Flat` (LF) case.
+Comparing the fiducially used `Extended Standard Flat` (ESt) case with the preferred `Extended Limber Spherical` (ELS) case, the constraints are identical at the $0.01\sigma$ level.
 Therefore, as expected from the comparison in Figure~\ref{fig:Cl_xi}, and given the low signal-to-noise CFHTLenS measurements on large scales, we find that the different combinations of assuming flat or spherical sky, baseline or extended Limber, make little difference to the cosmological parameter constraints, even in this `one-parameter' analysis.
@@
 Our Limber-case findings are in disagreement with \citet{kitching/etal:2016} who find a shift of $\Delta \sigma_8 = 0.007$ between their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) and their `Limber' analysis (which we believe corresponds to the Extended Limber spherical (ELS) case in Table~\ref{tab:Tl_nu}).
+\shahab{(I believe Tom in the latest email claimed the 0.007 number is between ESt and ELS)}
 
@@
 \begin{tabular}{ccc}
-\includegraphics[width=0.31\textwidth]{figures/IntegKsip.pdf} &
-\includegraphics[width=0.31\textwidth]{figures/IntegCOSEBIs.pdf} &
-\includegraphics[width=0.31\textwidth]{figures/IntegMap.pdf}
+\includegraphics[width=0.325\textwidth]{figures/IntegKsip.pdf} 
+\includegraphics[width=0.325\textwidth]{figures/IntegCOSEBIs.pdf} 
+\includegraphics[width=0.325\textwidth]{figures/IntegMap.pdf}
 \end{tabular}
-\caption{ \label{fig:filters}. Integrand of $\xi_+$, $E_1$ (E-COSEBIs) and $M^2_{\rm ap}$, respectively.
+\caption{ \small{\label{fig:filters}. Integrand of $\xi_+$, $E_1$ (E-COSEBIs) and $M^2_{\rm ap}$, respectively.
 All integrands are of the form $\ell F(\ell) P(\ell)$, where $F(\ell)$ is the corresponding weight-function
@@
 Note that higher order COSEBIs modes generally probe larger $\ell$-modes, 
-hence here we only show the lowest mode $E_1$. All values are normalized with respect to their maximum value. 
+hence here we only show the lowest mode $E_1$. All values are normalized with respect to their maximum value. }
 }

### 2016-12-08 cfhtlens.tex

@@
 We just noticed footnote 5 in Kitching et al that shows that they've actually used an approximate Planck 2015 cosmology - currently re-running with this alternative which is unlikely to change these results significantly}.
-We find the lowest conditional value of $\sigma_8 = 0.7461 \pm 0.0231$ for the `Standard' (KSt) case and the highest conditional value of $\sigma_8 = 0.7487 \pm 0.0232$ for the `Baseline Limber Flat` (LF) case.
-Comparing the fiducially used `Extended Standard Flat` (ESt) case with the preferred `Extended Limber Spherical` (ELS) case, the constraints are identical at the $0.01\sigma$ level.
+We find the lowest conditional value of $\sigma_8 = 0.7461 \pm 0.0231$ for the `Standard' (KSt) case and the highest conditional value of $\sigma_8 = 0.7487 \pm 0.0232$ for the `Baseline Limber Flat' (LF) case.
+Comparing the fiducially used `Extended Standard Flat' (ESt) case with the preferred `Extended Limber Spherical' (ELS) case, the constraints are identical at the $0.01\sigma$ level.
 Therefore, as expected from the comparison in Figure~\ref{fig:Cl_xi}, and given the low signal-to-noise CFHTLenS measurements on large scales, we find that the different combinations of assuming flat or spherical sky, baseline or extended Limber, make little difference to the cosmological parameter constraints, even in this `one-parameter' analysis.

### 2016-12-08 cfhtlens.tex
Added Fabian's text Accepted SJ's changes (thx SJ)

@@
 
-\citet{kitching/etal:2016} choose to only vary $\sigma_8$ in their analysis, fixing all other parameters to their Planck values.
+\citet{kitching/etal:2016} choose to only vary $\sigma_8$ in their analysis, fixing all other parameters to Planck values.
 They find a conditional value of $\sigma_8 = 0.789 \pm 0.015$ for their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) of the data from \citet{kilbinger/etal:2013}.
@@
 Nevertheless, we repeated the `one-parameter' analysis for the full range of Limber cases listed in Table~\ref{tab:Tl_nu} and are unable to confirm the results quoted by \citet{kitching/etal:2016}.
-%{\bf TBD:  The results that follow use the exact Planck 2015 cosmology.
-We just noticed footnote 5 in Kitching et al that shows that they've actually used an approximate Planck 2015 cosmology - currently re-running with this alternative which is unlikely to change these results significantly}.
-We find the lowest conditional value of $\sigma_8 = 0.7461 \pm 0.0231$ for the `Standard' (KSt) case and the highest conditional value of $\sigma_8 = 0.7487 \pm 0.0232$ for the `Baseline Limber Flat' (LF) case.
-Comparing the fiducially used `Extended Standard Flat' (ESt) case with the preferred `Extended Limber Spherical' (ELS) case, the constraints are identical at the $0.01\sigma$ level.
-Therefore, as expected from the comparison in Figure~\ref{fig:Cl_xi}, and given the low signal-to-noise CFHTLenS measurements on large scales, we find that the different combinations of assuming flat or spherical sky, baseline or extended Limber, make little difference to the cosmological parameter constraints, even in this `one-parameter' analysis.
+We find the lowest conditional value of $\sigma_8 = 0.746 \pm 0.023$ for the `Standard' (KSt) case and the highest conditional value of $\sigma_8 = 0.749 \pm 0.023$ for the `Baseline Limber Flat' (LF) case, a maximum change of $\Delta \sigma_8 = 0.0026 = 0.11 \sigma$.
+These findings are in disagreement with \citet{kitching/etal:2016} who find a shift of $\Delta \sigma_8 = 0.007 = 0.5\sigma$ between their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) and their `Limber' analysis (which we believe corresponds to the Extended Limber spherical (ELS) case in Table~\ref{tab:Tl_nu}).
 
-Our Limber-case findings are in disagreement with \citet{kitching/etal:2016} who find a shift of $\Delta \sigma_8 = 0.007$ between their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) and their `Limber' analysis (which we believe corresponds to the Extended Limber spherical (ELS) case in Table~\ref{tab:Tl_nu}).
-\shahab{(I believe Tom in the latest email claimed the 0.007 number is between ESt and ELS)}
+The most relevant case to consider is differences between the fiducially used `Extended Standard Flat' (ESt) case with the preferred `Extended Limber Spherical' (ELS) case.
+Here we find that the constraints are identical at the $0.01\sigma$ level.
+As expected from the comparison in Figure~\ref{fig:Cl_xi}, and given the low signal-to-noise CFHTLenS measurements on large scales, we conclude that the different combinations of assuming flat or spherical sky, baseline or extended Limber, make little difference to the cosmological parameter constraints, even in a `one-parameter' analysis.
 
-We note that it appears \citet{kitching/etal:2016} have chosen to use their `Flat' approximation in their `Full' non-Limber analysis rather than a full spherical-sky solution.
+We note that \citet{kitching/etal:2016} have chosen to use their `Flat' approximation in their `Full' non-Limber analysis rather than a full spherical-sky solution.
 The rationale is based on the Hankel transform in equation~\ref{eqn:xiGG} which is derived assuming a flat-sky approximation.
@@
 However, $M_ {\rm ap}^2$ statistics is a lossy conversion and is biased by small angular separations,
-where blending of galaxies makes shear measurement challenging/impossible \citep{Kilbinger/etal:2006}. As a result, COSEBIs was developed which tackles both shortcomings of $M_ {\rm ap}^2$ statistics.
+where blending of galaxies makes shear measurement challenging/impossible \citep{kilbinger/etal:2006}. As a result, COSEBIs was developed which tackles both shortcomings of $M_ {\rm ap}^2$ statistics.
 The right panel shows the integrand\footnote{Note that the lower left panel of Fig.
@@
 The pre-term reaches 1\% only for $\ell < 7$, which will become relevant for very large upcoming surveys but is negligible for current surveys.
+
+\subsection{On the quadratic estimator}
+
+\citet{kitching/etal:2016} state that `the derivative of a Limber-approximated power spectrum is not equal to the Limber-approximation of the derivative'.
+Based on this statement they conclude that `statistics that use Limber-approximated quadratic estimators to measure the cosmic shear power spectrum are not accurate' and refer explicitly to the quadratic estimator implementation used in \citet{Koehlinger2016} to measure the cosmic shear power spectrum from CFHTLenS.
+In this quadratic estimator implementation, however, the Limber approximation does not enter.
+The algorithm was originally presented by \citet{Hu2001} in the context of cosmic shear and has also been applied to other shear data sets (e.g.
+\citealt{Brown2003, Heymans2005, Lin2012}).
+Below we briefly summarize this quadratic estimator algorithm and emphasize that the Limber approximation does not enter in there.
+
+The aim of the method is to find the best-fitting power spectra assuming a Gaussian likelihood function $\mathcal{L}$.
+The likelihood depends on the shear data vector and its covariance $\mathbf{C}$ which consists of the sum of the shear correlation matrix $\mathbf{C}^\mathrm{sig}$ and the noise matrix $\mathbf{C}^\mathrm{noise}$.
+The shear correlation matrix can be written as a linear combination of piece-wise constant band powers $\mathcal{B}$ approximating the Fourier transforms of the shear correlations, i.e.
+their power spectra (cf.
+equations~3,~10 in \citealt{Koehlinger2016}).
+The best-fitting power spectra are found by iteratively stepping through a Newton--Raphson method in order to find the root of $\diff \mathcal{L}/ \diff \mathcal{B} = 0$ \citep{Bond1998, Seljak1998}.
+In the subsequent equations of the Newton--Raphson method only derivatives of the full covariance matrix enter, where the derivatives are taken with respect to band powers\footnote{i.e.
+$\partial \mathbf{C} / \partial \mathcal{B}_A$, where $A$ is a superindex over the type of the band, band-power bin and redshift correlation, see appendix\~A in \citealt{Koehlinger2016}.}.
+The only approximation entering in the algorithm is the flat-sky approximation when introducing the Fourier decomposition of the spin-2 shear field.
+This approximation is appropriate and accurate for current surveys as $\ell>80$  in all analyses published to date.

### 2016-12-08 Limber_Comment.tex
Limber_Comment.tex: minor edit
Added names (TBC; Patrick/Peter)
Added Fabian's text Accepted SJ's changes (thx SJ)
Added Patrick's comments

@@
-\documentclass[preprint]{aastex}
+%\documentclass[a4paper,preprint, fleqn]{aastex}
+\documentclass[a4paper, preprint, fleqn, usenatbib]{aastex}
 \usepackage{graphicx}   % Including figure files
-\usepackage{amsmath}    % Advanced maths comm
+\usepackage{amsmath}	% Advanced maths commands
+\usepackage{amssymb}	% Extra maths symbols
 \usepackage{color,verbatim,url}
 \usepackage{tabularx}
-\usepackage[table,usenames,dvipsnames]{xcolor}\usepackage{pdflscape}
+\usepackage[table,usenames,dvipsnames]{xcolor}
+\usepackage{pdflscape}
 \usepackage{lastpage}
+\usepackage{newtxtext, newtxmath}
+
+\usepackage[T1]{fontenc}
+\usepackage{ae, aecompl}
 
@@
 \newcommand{\bm}[1]{\mbox{\boldmath{$#1$}}}   %this is bold italic for MNRAS
-\newcommand{\mat}[1]{\mathbfss{#1}}
+%\newcommand{\mat}[1]{\mathbfss{#1}}
+\newcommand{\diff}{\mathrm{d}}
 
@@
 
-\author{Members of the KiDS, CFHTLenS and RCSLenS collaborations\altaffilmark{1} ....}
+\author{Members of the KiDS, CFHTLenS and RCSLenS collaborations; \\
+M. Asgari, J. Harnois-D\'eraps, C. Heymans, H. Hildebrandt, S. Joudaki,  M. Kilbinger, F. K\"ohlinger, K. Kuijken, P. Schneider, P. Simon, L. Van Waerbeke, M. Viola}%\altaffilmark{1} ....}
 %\email{tbd@tbd}
@@
 We support the core message of this paper that the use of such approximations should be considered in the future analyses of high precision surveys such as Euclid, LSST and WFIRST.
-In this comment, we argue that these approximations have negligible impact for current surveys and are thus unable to explain away the tension between the constraints from some current weak lensing surveys and Planck.
+In this comment, we argue that these approximations have negligible impact for current surveys and are thus unable to explain away the tension between the constraints from some current weak lensing surveys and the Planck CMB experiment.
 Reducing uncertainty and characterising bias in photometric redshift estimation is a critical task for the success of current and future surveys.
@@
 
-This comment is structured as follows.
+This comment discusses why we disagree with the findings of \citet{kitching/etal:2016} and is structured as follows.
 In section~\ref{sec:theory} we clarify which brand of approximations, highlighted by \citet{kitching/etal:2016}, have been used in recent weak lensing analyses \citep{joudaki/etal:2016, hildebrandt/etal:2016, joudaki/etal:2017}.
 We find that we are unable to replicate key results from \citet{kitching/etal:2016} and show that we do not expect these approximations to impact on the cosmological analysis of current surveys.
-In section~\ref{sec:cfhtlens} we compare with \citet{kitching/etal:2016} our conclusions of a `one-parameter' cosmological re-analysis of 2D cosmic shear data from \citet{kilbinger/etal:2013}.
-We also briefly review the literature that has advanced our understanding since the original CFHTLenS analyses were published and discuss the impact of flat-sky and Limber approximations in our analysis of numerical simulations and CMB lensing.
+In section~\ref{sec:cfhtlens} we present a `one-parameter' cosmological re-analysis of 2D cosmic shear data from \citet{kilbinger/etal:2013} which is inconsistent with the analysis presented in \citet{kitching/etal:2016}.
+We also briefly review the literature that has advanced our understanding since the original CFHTLenS analyses were published and discuss the impact of flat-sky and Limber approximations in our analysis of numerical simulations, CMB lensing and quadratic estimators for cosmic shear power spectrum.
 

### 2016-12-08 cfhtlens.tex
Added Patrick's comments

@@
 The rationale is based on the Hankel transform in equation~\ref{eqn:xiGG} which is derived assuming a flat-sky approximation.
-As shown in Figure~\ref{fig:Cl_xi}, however their chosen version of a flat-sky approximation serves to exacerbate the tension in theoretical models when a flat-sky solution is compared with the spherical-sky solution.
+As shown in Figure~\ref{fig:Cl_xi}, however, their chosen version of a flat-sky approximation serves to exacerbate the tension in theoretical models when a flat-sky solution is compared with the spherical-sky solution.
 We do not find this to be the case when considering the standard $T_\ell = 1$ flat-sky approximation that has been used in the majority of cosmic shear studies to date.
@@
 \subsection{Comparison of two-point shear statistics; the two-point correlation function, mass aperture statistic and COSEBIs}
-\citet{kilbinger/etal:2013} present a detailed comparison of cosmological constraints obtained from a range different two-point shear statistics including the shear correlation function, $\xi_\pm$, the aperture-mass dispersion, $M_ {\rm ap}^2$ \citep{schneider/etal:1998}, and the COSEBIs \citep{schneider/etal:2010}.
+\citet{kilbinger/etal:2013} present a detailed comparison of cosmological constraints obtained from a range different two-point shear statistics including the shear correlation function, $\xi_\pm$, the aperture-mass dispersion, $\langle M_ {\rm ap} \rangle ^2$ \citep{schneider/etal:1998}, and the COSEBIs \citep{schneider/etal:2010}.
 Figure~\ref{fig:filters} shows the integrands of these statistics
@@
 for two cases, normalised to their maximum value.
-The integrands are of the form $\ell F(\ell) P(\ell)$, where $F(\ell)=J_0(\ell)$ for $\xi_+$, $F(\ell)= U^2_\theta(\ell)$ for  $M_ {\rm ap}^2$ \citep[see][]{schneider/etal:1998} and $F(\ell)=W_n(\ell)$ for COSEBIs \citep[see][]{schneider/etal:2010}.
+The integrands are of the form $\ell F(\ell) P(\ell)$, where $F(\ell)=J_0(\ell)$ for $\xi_+$, $F(\ell)= U^2_\theta(\ell)$ for  $\langle M_ {\rm ap} \rangle^2$ \citep[see][]{schneider/etal:1998} and $F(\ell)=W_n(\ell)$ for COSEBIs \citep[see][]{schneider/etal:2010}.
 For $\xi_\pm$, $P(\ell)$ is equal to the sum of the E and B-mode convergence power spectra.
 This is one of the main motivators for the development of aperture-mass dispersion.
-However, $M_ {\rm ap}^2$ statistics is a lossy conversion and is biased by small angular separations,
-where blending of galaxies makes shear measurement challenging/impossible \citep{kilbinger/etal:2006}. As a result, COSEBIs was developed which tackles both shortcomings of $M_ {\rm ap}^2$ statistics.
-The right panel shows the integrand\footnote{Note that the lower left panel of Fig.
+However, $\langle M_ {\rm ap} \rangle ^2$ statistics is a lossy conversion and is biased by small angular separations,
+where blending of galaxies makes shear measurement challenging/impossible \citep{kilbinger/etal:2006}.
+As a result, COSEBIs was developed which tackles both shortcomings of $\langle M_ {\rm ap} \rangle ^2$ statistics.
+The upper panel shows the integrand\footnote{Note that the lower left panel of Fig.
 1 in \citet{kitching/etal:2016} shows an integrated form of this function for a maximum angular separation of $100'$.
@@
 The middle panel in Figure~\ref{fig:filters} shows COSEBIs integrands for two angular ranges, $[1',100']$ and $[0.8',350']$, where we only show the integrands for the lowest COSEBIs mode, as the higher modes generally probe larger $\ell$-modes.
-Finally, the left panel shows the integrands of aperture mass dispersion statistics, for the same two maximum angular ranges.
+Finally, the lower panel shows the integrands of aperture mass dispersion statistics, for the same two maximum angular ranges.
 
@@
 
-\begin{figure}[htb]
+\begin{figure}[!htp]
 \begin{center}
 \begin{tabular}{ccc}
-\includegraphics[width=0.325\textwidth]{figures/IntegKsip.pdf} 
-\includegraphics[width=0.325\textwidth]{figures/IntegCOSEBIs.pdf} 
-\includegraphics[width=0.325\textwidth]{figures/IntegMap.pdf}
+%\includegraphics[width=0.325\textwidth]{figures/IntegKsip.pdf} 
+%\includegraphics[width=0.325\textwidth]{figures/IntegCOSEBIs.pdf} 
+%\includegraphics[width=0.325\textwidth]{figures/IntegMap.pdf}
+\includegraphics[width=0.65\textwidth]{figures/IntegKsip.pdf} \\
+\includegraphics[width=0.65\textwidth]{figures/IntegCOSEBIs.pdf} \\
+\includegraphics[width=0.65\textwidth]{figures/IntegMap.pdf}\\
 \end{tabular}
-\caption{ \small{\label{fig:filters}. Integrand of $\xi_+$, $E_1$ (E-COSEBIs) and $M^2_{\rm ap}$, respectively.
+\caption{ \small{\label{fig:filters}. Integrand of $\xi_+$ (upper), $E_1$ (middle, E-COSEBIs) and $\langle M_{\rm ap} \rangle^2$ (lower panel).
 All integrands are of the form $\ell F(\ell) P(\ell)$, where $F(\ell)$ is the corresponding weight-function
@@
 Going beyond flat sky and Limber could improve the agreement, however this cannot explain the results of \citet{harnois-deraps/vanwaerbeke:2015} who demonstrate that the large scale under-estimation of power varies with the simulation box size.
-This volume effect was verified by comparing explicitly the $\xi_+$ statistic at large angular scales between simulation volumes with box sides = 147Mpc/h and 515Mpc/h \citep[see Fig.
+This volume effect was verified by comparing explicitly the $\xi_+$ statistic at large angular scales between simulation volumes with box sides  ranging from 147$\rm{Mpc/h}$ to 515$\rm{Mpc/h}$ \citep[see Fig.
 5 in][]{harnois-deraps/vanwaerbeke:2015}.
@@
 \subsection{On the application to CMB lensing}
-\citet{kitching/etal:2016} discuss how corrections to the Limber and flat sky approximations would also affect predictions involving the shear and convergence cross-spectrum, such that the CMB lensing - galaxy lensing cross-correlation should include a pre-term $ [\ell(\ell+1)]^2/(\ell+ 0.5)^4$.
+\citet{kitching/etal:2016} discuss how corrections to the Limber and flat sky approximations would also affect predictions involving the shear and convergence cross-spectrum, such that the cross-correlation of CMB lensing and galaxy lensing should include a pre-factor $ [\ell(\ell+1)]^2/(\ell+ 0.5)^4$.
 We have verified that this term would have negligible impact on current measurements, given the relatively low signal to noise ratio.
 For example, most measurements \citep{hand/etal:2015, liu/hill:2015, kirk/etal:2016,harnois-deraps/etal:2016} are carried over angular multipoles in the range $\ell \in [20-2000]$.
-The size of the pre-term, averaged over this range, is of the order of 0.01\%.
+The size of the pre-factor, averaged over this range, is of the order of 0.01\%.
 In comparison, the size of the statistical error bars are of the order 25-35\% with additional uncertainty due to photometric redshifts (10-15\%) and intrinsic galaxy alignments (10-15\%).
-The pre-term reaches 1\% only for $\ell < 7$, which will become relevant for very large upcoming surveys but is negligible for current surveys.
+The pre-factor reaches 1\% only for $\ell < 7$, which may become relevant for very large upcoming surveys but is negligible for current surveys.
 

### 2016-12-08 photoz.tex
Added Patrick's comments

@@
 
-\cite{kitching/etal:2016} use a linear relation fit to the biases determined by \citet{choi/etal:2016} in order to extrapolate the results beyond the photometric redshift limit of $z_B<0.9$ and determine a bias at each redshift.
+\cite{kitching/etal:2016} use a linear fit to the biases determined by \citet{choi/etal:2016} in order to extrapolate the results beyond the photometric redshift limit of $z_B<0.9$ and determine a bias at each redshift.
 They then correct the non-tomographic \citet{kilbinger/etal:2013} redshift distribution with this bias relation.

### 2016-12-08 theory.tex
Added Patrick's comments

@@
 
-When a survey is sufficiently small, a flat-sky approximation can be made reducing $T_\ell \approx 1$.
+When a survey is sufficiently small, a flat-sky approximation can be made reducing $T_\ell =1$ and $\nu(\ell) = \ell$.
 In \citet{kitching/etal:2016} it is not fully clear which combinations of  $T_\ell$ and $\nu(\ell)$ are considered, so we review them all as summarised in Table~\ref{tab:Tl_nu}, also highlighting which combinations were used in recent cosmic shear analyses.
@@
 \hline
-Case & ID & $T_\ell$ & $\nu$ & Used in \\ \hline
+Case & ID & $T_\ell$ & $\nu(\ell)$ & Used in \\ \hline
 \citet{kitching/etal:2016} `Standard' & KSt & $1$ & $\ell$ & pre-2014 CFHTLenS papers \\
@@
 Figure~\ref{fig:Cl_xi} shows theoretical models for the shear power spectrum $P_\gamma(\ell)$ (equation~\ref{eqn:Pkappa}), and the shear correlation function (equation~\ref{eqn:xiGG}) for the different variations on the approximations listed in Table~\ref{tab:Tl_nu}.
-The majority of the models agree.
-The two outliers found, are the `Baseline' and `Extended' Limber cases where the \citet{kitching/etal:2016} `Flat' Sky approximation has been made with $T_\ell = \ell^4 / (\ell + 0.5)^4$.
+The Standard and Spherical models agree at the few percent level above $\ell>10$ and below $\theta< 100$ arcmin.
+The two outliers are the Baseline and Extended `Flat' Sky Limber cases (LF and ELF) where the \citet{kitching/etal:2016} `Flat' Sky approximation has been made with $T_\ell = \ell^4 / (\ell + 0.5)^4$.
 We argue that applying the approximation, that $\ell \pm x \approx \ell$, where $x$ is small, only to the numerator of equation~\ref{eqn:Tl} is inconsistent.
@@
 
-As shown in the lower panels of Figure~\ref{fig:Cl_xi}, the `standard flat' sky approximation used by recent cosmic shear surveys, where $T_\ell = 1$, recovers a very similar result to the spherical sky case.
-Over angular scales used in the recent KiDS cosmic shear analysis (where the maximum angular scale is shown dashed), these curves differ by less than 1\%.
+As shown in the lower panels of Figure~\ref{fig:Cl_xi}, the `standard flat' sky approximation used by recent cosmic shear surveys\footnote{The KSt approximation was used for pre-2014 CFHTLenS analysis and the ESt approximation was used for recent CFHTLenS and KiDS analyses}, where $T_\ell = 1$, recovers a very similar result to the spherical sky case.
+Over angular scales used in the recent KiDS cosmic shear analysis (where the maximum angular scale $\theta<50.7$ arcmin is shown dashed), these curves differ by less than 1\%.
 As such the standard flat-sky approximations that have been used will not impact the cosmological analyses of current surveys.
@@
  \subsection{Cosmic shear without the Limber Approximation}
-In collecting our comments on \citet{kitching/etal:2016} we contacted colleagues who had previously tested the impact of the Limber approximation on cosmic shear studies by comparing a Limber approximated cosmic shear power spectrum with an exact calculation.
+In collecting our comments on \citet{kitching/etal:2016} we contacted colleagues who had previously tested the impact of the Limber approximation on cosmic shear studies by comparing a Limber-approximated cosmic shear power spectrum with an exact calculation.
 The majority of these analyses, carried out many years ago, remained unpublished in peer reviewed journals as no significant deviation was found\footnote{See for example appendix M of the 2010 PhD thesis from Donghui Jeong (\url{http://www.personal.psu.edu/duj13/dissertation/djeong_diss_appM.pdf}) and Chapter 7 of 2012 PhD thesis from Nicolas Van de Rijt (\url{http://ipht.cea.fr/Docspht/articles/t12/080/public/these_vanderijt2012.pdf}).}.
@@
 an unquestioned and untested assumption at the beginning of the analysis)'  is unwarranted.
-Not only is there published work that has questioned and tested the Limber approximation for cosmic shear studies, individual teams have also verified this result internally.
+Not only is there published work that has questioned and tested the Limber approximation for the cosmic shear power spectrum, individual teams have also verified this result internally for their own cosmic shear analyses.
 
-Given the insignificant effect of using the Limber approximation found by various groups, the ability to calculate an exact non-Limber solution has unfortunately not been maintained in theoretical code over the years.
+Given the insignificant effect of using the Limber approximation found by various groups, the ability to calculate an exact non-Limber solution has unfortunately not been maintained in many theoretical codes over the years.
 Instead these codes have evolved to account for (much more) important approximations such as the impact of baryon feedback on the matter power spectrum and non-zero neutrino masses \citep[see for example][]{joudaki/etal:2016, mead/etal:2016}.
+Two exceptions to this are recent updates to CLASS \citep{blas/lesgourgues/tram:2011,audren/etal:2013} and CosmicFish \citep{raveri/etal:2016}.
+On-going code comparisons have, however, revealed differences that are larger than the expected impact of Limber or non-Limber approximation.
 We are therefore unable to readily determine non-Limber theoretical calculations for the shear-correlation function to directly compare with the results of \citet{kitching/etal:2016}.
-Instead we refer the reader to Figure 3 of \citet{giannantonio/etal:2012} to draw their own conclusions.
+Instead we refer the reader to Figure 3 of \citet{giannantonio/etal:2012} to draw their own conclusions about the impact of this effect.

### 2016-12-08 Limber_Comment.tex
Started on Peters comments

@@
 We support the core message of this paper that the use of such approximations should be considered in the future analyses of high precision surveys such as Euclid, LSST and WFIRST.
-In this comment, we argue that these approximations have negligible impact for current surveys and are thus unable to explain away the tension between the constraints from some current weak lensing surveys and the Planck CMB experiment.
+In this comment, we argue that these approximations have negligible impact for current surveys and are thus unable to significantly reduce the tension between the constraints from some current weak lensing surveys and the Planck CMB experiment.
 Reducing uncertainty and characterising bias in photometric redshift estimation is a critical task for the success of current and future surveys.
@@
 
-The measurement of weak gravitational lensing by large scale structures provides a powerful cosmological probe of dark matter, dark energy, and modifications to gravity.
+The measurement of weak gravitational lensing by large-scale structures provides a powerful cosmological probe of dark matter, dark energy, and modifications to gravity.
 As such it is the primary science goal of several current (KiDS, HSC, DES) and future (Euclid, LSST, WFIRST) large-scale surveys.
@@
 
-In this comment paper we discuss the flat sky and Limber approximations that can be used when deriving theoretical predictions for the principally used cosmic shear statistic, $\xi_\pm$, the two-point shear correlation function.
-The Limber approximation for cosmic shear has been previously explored by \citet{giannantonio/etal:2012} finding that it provided sufficient accuracy for future cosmic shear studies.
-Recently, however, \citet{kitching/etal:2016} reported that when considering the flat sky and Limber approximations in concert, tensions between weak lensing and CMB experiments can be reduced.
-They demonstrate the effect with a re-analysis of the non-tomographic weak lensing data from the CFHTLenS survey \citep{kilbinger/etal:2013}.
+In this comment paper we discuss the flat-sky and Limber approximations that can be used when deriving theoretical predictions for the principally used cosmic shear statistic, $\xi_\pm$, the two-point shear correlation functions.
+The Limber approximation for cosmic shear was previously explored by \citet{giannantonio/etal:2012} finding that it provided sufficient accuracy for future cosmic shear studies.
+Recently, however, \citet{kitching/etal:2016} reported that when considering the flat-sky and Limber approximations in concert, tensions between weak lensing and CMB experiments can be reduced.
+They illustrate the effect with a re-analysis of the non-tomographic weak lensing data from the CFHTLenS survey \citep{kilbinger/etal:2013}.
+On initial inspection we found that these claims appeared implausible, for two reasons: First, in a naive estimate, the deviation of flat-sky approximation from a full treatment are expected to be of similar order as the fractional difference between $\theta_{\rm max}$ and $\sin\theta_{\rm max}$,
+where $\theta_{\rm max}$ is the maximum angular scale considered in the cosmic shear analysis.
+In the case of \citep{hildebrandt/etal:2016}, where $\theta_{\rm max}=50$ arcmin, $(\theta_{\rm max} - \sin\theta_{\rm max})/\theta_{\rm max} \approx 3.52 \times 10^{-5}$.
+Second, it was shown in \citet[][see their Fig.3]{giannantonio/etal:2012} that the difference between the Limber approximation and exact treatment is far smaller than cosmic variance, even for a full-sky cosmic shear survey.
 
-This comment discusses why we disagree with the findings of \citet{kitching/etal:2016} and is structured as follows.
+This comment seeks to explore the content of \citet{kitching/etal:2016} in detail, discussing why we disagree with their findings.
+It is structured as follows.
 In section~\ref{sec:theory} we clarify which brand of approximations, highlighted by \citet{kitching/etal:2016}, have been used in recent weak lensing analyses \citep{joudaki/etal:2016, hildebrandt/etal:2016, joudaki/etal:2017}.
-We find that we are unable to replicate key results from \citet{kitching/etal:2016} and show that we do not expect these approximations to impact on the cosmological analysis of current surveys.
+We are unable to replicate key results from \citet{kitching/etal:2016} and show that we do not expect these approximations to impact on the cosmological analysis of current surveys.
 In section~\ref{sec:cfhtlens} we present a `one-parameter' cosmological re-analysis of 2D cosmic shear data from \citet{kilbinger/etal:2013} which is inconsistent with the analysis presented in \citet{kitching/etal:2016}.

### 2016-12-08 cfhtlens.tex
Started on Peters comments

@@
 Efforts are now underway to fully re-analyse CFHTLenS using the advanced KiDS analysis pipeline with revised shape measurements and calibrations for the shear and photometric redshifts.
-Given the known shortcomings with the original CFHTLenS results, which will impact in different ways on the cosmological conclusions that one can draw from the survey, it is surprising that \citet{kitching/etal:2016} chose to focus their study on the cosmic shear analysis of \citet{kilbinger/etal:2013}.
+Until this analysis is complete we note that these known shortcomings with the original CFHTLenS results impact in different ways on the cosmological conclusions that one can draw from the survey.
 
-\citet{kitching/etal:2016} choose to only vary $\sigma_8$ in their analysis, fixing all other parameters to Planck values.
+\citet{kitching/etal:2016} chose to only vary $\sigma_8$ in their analysis, fixing all other parameters to Planck values.
 They find a conditional value of $\sigma_8 = 0.789 \pm 0.015$ for their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) of the data from \citet{kilbinger/etal:2013}.
@@
 
-We note that \citet{kitching/etal:2016} have chosen to use their `Flat' approximation in their `Full' non-Limber analysis rather than a full spherical-sky solution.
-The rationale is based on the Hankel transform in equation~\ref{eqn:xiGG} which is derived assuming a flat-sky approximation.
-As shown in Figure~\ref{fig:Cl_xi}, however, their chosen version of a flat-sky approximation serves to exacerbate the tension in theoretical models when a flat-sky solution is compared with the spherical-sky solution.
-We do not find this to be the case when considering the standard $T_\ell = 1$ flat-sky approximation that has been used in the majority of cosmic shear studies to date.
+We note that \citet{kitching/etal:2016} use their `Flat' approximation for the `Full' non-Limber analysis of the CFHTLenS data.
+This is because on a sphere, correlation functions cannot be related to the power spectrum by a Hankel transform (e.g.
+equation~\ref{eqn:xiGG}) as the power spectrum is not defined for non-integer $\ell$.
+In Figure~\ref{fig:Cl_xi}, however, we show that this chosen version of a flat-sky approximation serves to exacerbate the tension in theoretical models when a flat-sky solution is compared with the spherical-sky solution in the Limber approximated case.
+This is not the case when considering the standard $T_\ell = 1$ flat-sky approximation that has been used in the majority of cosmic shear studies to date.
+We would therefore argue that it is more appropriate to use a $T_\ell = 1$ flat-sky approximation when carrying out a `Full' non-Limber analysis of the shear correlation function.
 
@@
 From Figure~\ref{fig:filters} we can see that the two-point cosmic shear statistics tested by \citet{kilbinger/etal:2013} exhibit different dependences between the angular scales sampled and the $\ell$-range probed.
-If a significant bias had been introduced at low-$\ell$ by using flat-sky and Limber approximations, we would then expect to see a systematic shift between the different two-point statistics with the COSEBIs statistic being essentially unaffected as it only includes modes with $\ell \gtrsim 80$.
-This is found not to be the case with all three statistics finding $\sigma_8 (\Omega_m/0.27)^\alpha = 0.79$ with errors that range from $0.03$ to $0.06$, and $\alpha$ ranging from $0.59$ to 0.7 \citep[see Table 5 of][]{kilbinger/etal:2013}.
+If a significant bias had been introduced at low-$\ell$ by using flat-sky and Limber approximations, we would then expect to see a systematic shift between the different two-point statistics with the COSEBIs statistic being essentially unaffected as it only includes modes with $\ell \gtrsim 20$.
+This is found not to be the case with all three statistics finding $\sigma_8 (\Omega_m/0.27)^\alpha = 0.79$ with errors that range from $0.03$ to $0.06$ for the full five-parameter fit, and $\alpha$ ranging from $0.59$ to 0.7 \citep[see Table 5 of][]{kilbinger/etal:2013}.
 This comparison further supports our argument that the approximations highlighted by \citet{kitching/etal:2016} have negligible impact for current surveys.
@@
 It is then suggested, however, that the discrepancies already reported between existing mocks and the predictions could be attributed to these approximations, as opposed to a finite box effect \citep{kiessling/etal:2011, harnois-deraps/etal:2012, harnois-deraps/vanwaerbeke:2015}.
-Going beyond flat sky and Limber could improve the agreement, however this cannot explain the results of \citet{harnois-deraps/vanwaerbeke:2015} who demonstrate that the large scale under-estimation of power varies with the simulation box size.
+Going beyond flat-sky and Limber could improve the agreement, however this cannot explain the results of \citet{harnois-deraps/vanwaerbeke:2015} who demonstrate that the large-scale under-estimation of power varies with the simulation box size.
 This volume effect was verified by comparing explicitly the $\xi_+$ statistic at large angular scales between simulation volumes with box sides  ranging from 147$\rm{Mpc/h}$ to 515$\rm{Mpc/h}$ \citep[see Fig.
@@
 \subsection{On the application to CMB lensing}
-\citet{kitching/etal:2016} discuss how corrections to the Limber and flat sky approximations would also affect predictions involving the shear and convergence cross-spectrum, such that the cross-correlation of CMB lensing and galaxy lensing should include a pre-factor $ [\ell(\ell+1)]^2/(\ell+ 0.5)^4$.
+\citet{kitching/etal:2016} discuss how corrections to the Limber and flat-sky approximations would also affect predictions involving the shear and convergence cross-spectrum, such that the cross-correlation of CMB lensing and galaxy lensing should include a pre-factor $ [\ell(\ell+1)]^2/(\ell+ 0.5)^4$.
 We have verified that this term would have negligible impact on current measurements, given the relatively low signal to noise ratio.

### 2016-12-08 theory.tex
Started on Peters comments

@@
 \be
-\xi_\pm^{ij}(\theta) = \frac{1}{2\pi}\int \d\ell \,\ell \,P^{ij}_\gamma(\ell) \, J_{0,4}(\ell \theta) \, , 
+\xi_\pm^{ij}(\theta) = \frac{1}{2\pi}\int_0^\infty \d\ell \,\ell \,P^{ij}_\gamma(\ell) \, J_{0,4}(\ell \theta) \, , 
 \label{eqn:xiGG}
@@
 \be
-T_\ell = \frac{(\ell+2)(\ell+1)\ell(\ell-1)}{(\ell + 0.5)^4} \, .
+T_\ell = \frac{(\ell+2)(\ell+1)\ell(\ell-1)}{(\ell + 0.5)^4} = 1-{5\over 2\ell^2} +{\cal O}(\ell^{-3}) \, .
 \label{eqn:Tl}
@@
 The Standard and Spherical models agree at the few percent level above $\ell>10$ and below $\theta< 100$ arcmin.
-The two outliers are the Baseline and Extended `Flat' Sky Limber cases (LF and ELF) where the \citet{kitching/etal:2016} `Flat' Sky approximation has been made with $T_\ell = \ell^4 / (\ell + 0.5)^4$.
+The two outliers are the Baseline and Extended `Flat' Sky Limber cases (LF and ELF) where the \citet{kitching/etal:2016} `Flat' Sky approximation has been made with
+\be
+T_\ell^{\rm `Flat'} = \ell^4 / (\ell + 0.5)^4 \approx 1-{2\over \ell}+{5\over 2\ell^2} +{\cal O}(\ell^{-3}) \, . 
+\ee    
 We argue that applying the approximation, that $\ell \pm x \approx \ell$, where $x$ is small, only to the numerator of equation~\ref{eqn:Tl} is inconsistent.
+By comparing the expansions of equations~\ref{eqn:Tl} and~\ref{eqn:Tlflat}, we see that the \citet{kitching/etal:2016} `Flat' Sky approximation effectively introduces a new term $2/\ell$ making it more deviant from the full spherical solution in comparison to the standard $T_\ell = 1$ case.
 To our knowledge, this form of the flat-sky approximation has not been used in cosmic shear studies to date.
@@
 Given the insignificant effect of using the Limber approximation found by various groups, the ability to calculate an exact non-Limber solution has unfortunately not been maintained in many theoretical codes over the years.
-Instead these codes have evolved to account for (much more) important approximations such as the impact of baryon feedback on the matter power spectrum and non-zero neutrino masses \citep[see for example][]{joudaki/etal:2016, mead/etal:2016}.
+Instead these codes have evolved to account for critical approximations such as the impact of baryon feedback on the matter power spectrum and non-zero neutrino masses \citep[see for example][]{joudaki/etal:2016, mead/etal:2016}.
 Two exceptions to this are recent updates to CLASS \citep{blas/lesgourgues/tram:2011,audren/etal:2013} and CosmicFish \citep{raveri/etal:2016}.

### 2016-12-08 cfhtlens.tex
rest of PS's comments

@@
 \subsection{On the application to CMB lensing}
-\citet{kitching/etal:2016} discuss how corrections to the Limber and flat-sky approximations would also affect predictions involving the shear and convergence cross-spectrum, such that the cross-correlation of CMB lensing and galaxy lensing should include a pre-factor $ [\ell(\ell+1)]^2/(\ell+ 0.5)^4$.
+\citet{kitching/etal:2016} discuss how corrections to the Limber and flat-sky approximations would also affect predictions involving the shear and convergence cross-spectrum, such that the cross-correlation of CMB lensing and galaxy lensing should include a pre-factor $ [\ell(\ell+1)]^2/(\ell+ 0.5)^4 = 1-{1\over 2\ell^2}+{\cal O}(\ell^{-3})$.
 We have verified that this term would have negligible impact on current measurements, given the relatively low signal to noise ratio.

### 2016-12-08 conclusion.tex
Added names (TBC; Patrick/Peter)
Added Lance to the thnx
rest of PS's comments

@@
 In this comment we have highlighted a number of shortcomings in the analysis presented in \cite{kitching/etal:2016}.
-We argue that the flat sky and Limber approximations that can be used in cosmic shear analyses are not able to explain away the tension between current weak lensing and Planck results, in contrast to the message that \cite{kitching/etal:2016} convey.
+We argue that the flat-sky and Limber approximations that can be used in cosmic shear analyses are not able to explain away the tension between current weak lensing and Planck results, in contrast to the message that \cite{kitching/etal:2016} convey.
 Our critique should not, however, detract from the important core message of their paper, that future surveys will need to consider these approximations and optimise their statistical analyses accordingly.
@@
 Instead of alleviating the tension between CFHTLenS and Planck a correct application of the offsets would increase the discrepancy, as shown with a recent re-analysis of the CFHTLenS data \citep{joudaki/etal:2016} as well as results from the KiDS project \citep{hildebrandt/etal:2016}.
+
+\section{Acknowledgements}
+We thank Sarah Bridle, Ami Choi, Tommaso Giannantonio, Donnacha Kirk, Lance Miller, Benjamin Joachimi and Adam Amara for useful discussions during the collection of these comments.

### 2016-12-08 theory.tex
rest of PS's comments
Added BJ comments

@@
 \be
-T_\ell^{\rm `Flat'} = \ell^4 / (\ell + 0.5)^4 \approx 1-{2\over \ell}+{5\over 2\ell^2} +{\cal O}(\ell^{-3}) \, . 
+T_\ell^{\rm `Flat'} = \ell^4 / (\ell + 0.5)^4 = 1-{2\over \ell}+{5\over 2\ell^2} +{\cal O}(\ell^{-3}) \, . 
 \ee    
@@
 \citet{giannantonio/etal:2012} however state that this limit is only applied in a positive curvature case.}.
-We therefore argue that the assertion by \citet{kitching/etal:2016} that the majority of cosmic shear data analyses to date have made an `axiomatic assumption (i.e.
+They conclude that the Limber approximation works so well for cosmic shear owing to the wide redshift distribution of the lensed sources.
+This is in comparison to the case of galaxy power spectra,  where narrower redshift bins result in a significant difference between the Limber and non-Limber cases \citep[see also][]{simon/2007}.
+Given this body of work, we argue that the assertion by \citet{kitching/etal:2016} that the majority of cosmic shear data analyses to date have made an `axiomatic assumption (i.e.
 an unquestioned and untested assumption at the beginning of the analysis)'  is unwarranted.

### 2016-12-08 cfhtlens.tex

@@
 \subsection{Comparison of two-point shear statistics; the two-point correlation function, mass aperture statistic and COSEBIs}
-\citet{kilbinger/etal:2013} present a detailed comparison of cosmological constraints obtained from a range different two-point shear statistics including the shear correlation function, $\xi_\pm$, the aperture-mass dispersion, $\langle M_ {\rm ap} \rangle ^2$ \citep{schneider/etal:1998}, and the COSEBIs \citep{schneider/etal:2010}.
+\citet{kilbinger/etal:2013} present a detailed comparison of cosmological constraints obtained from a range of different two-point shear statistics including the shear correlation function, $\xi_\pm$, the aperture-mass dispersion, $\langle M_ {\rm ap} \rangle ^2$ \citep{schneider/etal:1998}, and the COSEBIs, $E_n$ \citep{schneider/etal:2010}.
+These statatistics are linearly related to the power spectrum via integrals of the form,
+%
+\begin{align}
+\label{eqn:integ}
+& E_n =\int_0^{\infty}\frac{\d \ell \ell}{2\pi} W_n(\ell) P(\ell)\;,\\ \nonumber
+& \langle M_ {\rm ap} \rangle ^2(\theta)=\int_0^{\infty}\frac{\d \ell \ell}{2\pi} U^2_\theta(\ell) P(\ell)\;,
+\end{align}
+%
+where $W_n(\ell)$ and $U^2_\theta(\ell)$ are defined in \cite{schneider/etal:2010} and \cite{schneider/etal:1998}. The corresponding equations for $\xi_\pm$ is given in \eqref{eqn:xiGG}.
 Figure~\ref{fig:filters} shows the integrands of these statistics 
-% (i.e. the weights placed on each $\ell$ scale),  
 for two cases, normalised to their maximum value. 
-The integrands are of the form $\ell F(\ell) P(\ell)$, where $F(\ell)=J_0(\ell)$ for $\xi_+$, $F(\ell)= U^2_\theta(\ell)$ for  $\langle M_ {\rm ap} \rangle^2$ \citep[see][]{schneider/etal:1998} and $F(\ell)=W_n(\ell)$ for COSEBIs \citep[see][]{schneider/etal:2010}.
-For $\xi_\pm$, $P(\ell)$ is equal to the sum of the E and B-mode convergence power spectra.
+The integrands are of the form $\ell F(\ell) P(\ell)$ (see equations~\ref{eqn:xiGG} and \ref{eqn:integ}).
+For $\xi_\pm$, $P(\ell)$ is equal to the sum of the E and B-mode power spectra.
 This is one of the main motivators for the development of aperture-mass dispersion.
-However, $\langle M_ {\rm ap} \rangle ^2$ statistics is a lossy conversion and is biased by small angular separations,
-where blending of galaxies makes shear measurement challenging/impossible \citep{kilbinger/etal:2006}.
+However, $\langle M_ {\rm ap} \rangle ^2$ statistics is a lossy conversion and is biased by small angular separations, where blending of galaxies makes shear measurement challenging/impossible \citep{kilbinger/etal:2006}.
 As a result, COSEBIs was developed which tackles both shortcomings of $\langle M_ {\rm ap} \rangle ^2$ statistics.
-The upper panel shows the integrand\footnote{Note that the lower left panel of Fig.
+The upper two panels show the integrands\footnote{Note that the lower left panel of Fig.
 1 in \citet{kitching/etal:2016} shows an integrated form of this function for a maximum angular separation of $100'$.
-However, in \citet{kilbinger/etal:2013}, the data used in \citet{kitching/etal:2016}, $\theta$ is between $0.8'$ and $350'$.} of $\xi_+$ for $\theta=100'$ and $\theta=350'$.
-The middle panel in Figure~\ref{fig:filters} shows COSEBIs integrands for two angular ranges, $[1',100']$ and $[0.8',350']$, where we only show the integrands for the lowest COSEBIs mode, as the higher modes generally probe larger $\ell$-modes.
-Finally, the lower panel shows the integrands of aperture mass dispersion statistics, for the same two maximum angular ranges.
+However, in \citet{kilbinger/etal:2013}, the data used in \citet{kitching/etal:2016}, $\theta$ is between $0.8'$ and $350'$.} of $\xi_\pm$ for $\theta=100'$ and $\theta=350'$.
+The lower middle panel in Figure~\ref{fig:filters} shows the COSEBIs integrands for two angular ranges, $[1',100']$ and $[0.8',350']$, where we only show the integrands for the lowest COSEBIs mode, $E_1$, as the higher modes generally probe larger $\ell$-modes.
+Finally, the lowest panel shows the integrands of aperture mass dispersion statistics, for the same two maximum angular ranges.
 
@@
 \begin{tabular}{ccc}
-%\includegraphics[width=0.325\textwidth]{figures/IntegKsip.pdf} 
-%\includegraphics[width=0.325\textwidth]{figures/IntegCOSEBIs.pdf} 
-%\includegraphics[width=0.325\textwidth]{figures/IntegMap.pdf}
-\includegraphics[width=0.65\textwidth]{figures/IntegKsip.pdf} \\
-\includegraphics[width=0.65\textwidth]{figures/IntegCOSEBIs.pdf} \\
-\includegraphics[width=0.65\textwidth]{figures/IntegMap.pdf}\\
+\includegraphics[width=\textwidth]{figures/IntegAll.pdf} \\
 \end{tabular}
-\caption{ \small{\label{fig:filters}. Integrand of $\xi_+$ (upper), $E_1$ (middle, E-COSEBIs) and $\langle M_{\rm ap} \rangle^2$ (lower panel).
+\caption{ \small{\label{fig:filters}. Integrand of $\xi_+$ (upper), $\xi_-$ (upper middle), $E_1$ ( lower middle, E-COSEBIs) and $\langle M_{\rm ap} \rangle^2$ (lower panel).
 All integrands are of the form $\ell F(\ell) P(\ell)$, where $F(\ell)$ is the corresponding weight-function
-for each statistic and $P(\ell)$ is the E-mode convergence power spectrum, with the exception of $\xi_+$, for which
+for each statistic and $P(\ell)$ is the E-mode convergence power spectrum, with the exception of $\xi_\pm$, for which
 $P(\ell)$ is equal to the sum of E and B-mode power spectra. 
@@
 Going beyond flat-sky and Limber could improve the agreement, however this cannot explain the results of \citet{harnois-deraps/vanwaerbeke:2015} who demonstrate that the large-scale under-estimation of power varies with the simulation box size.
-This volume effect was verified by comparing explicitly the $\xi_+$ statistic at large angular scales between simulation volumes with box sides  ranging from 147$\rm{Mpc/h}$ to 515$\rm{Mpc/h}$ \citep[see Fig.
+This volume effect was verified by comparing explicitly the $\xi_+$ statistic at large angular scales between simulation volumes with box sides  ranging from 147$\;\rm{Mpc/h}$ to 515$\;\rm{Mpc/h}$ \citep[see Fig.
 5 in][]{harnois-deraps/vanwaerbeke:2015}.

### 2016-12-09 cfhtlens.tex
minor fix

@@
 Nevertheless, we repeated the `one-parameter' analysis for the full range of Limber cases listed in Table~\ref{tab:Tl_nu} and are unable to confirm the results quoted by \citet{kitching/etal:2016}.
-We find the lowest conditional value of $\sigma_8 = 0.746 \pm 0.023$ for the `Standard' (KSt) case and the highest conditional value of $\sigma_8 = 0.749 \pm 0.023$ for the `Baseline Limber Flat' (LF) case, a maximum change of $\Delta \sigma_8 = 0.0026 = 0.11 \sigma$.
+We find the lowest conditional value of $\sigma_8 = 0.746 \pm 0.023$ for the `Standard' (KSt) case and the highest conditional value of $\sigma_8 = 0.749 \pm 0.023$ for the `Extended Limber Flat' (ELF) case, a maximum change of $\Delta \sigma_8 = 0.0026 = 0.11 \sigma$.
 These findings are in disagreement with \citet{kitching/etal:2016} who find a shift of $\Delta \sigma_8 = 0.007 = 0.5\sigma$ between their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) and their `Limber' analysis (which we believe corresponds to the Extended Limber spherical (ELS) case in Table~\ref{tab:Tl_nu}).

### 2016-12-09 Limber_Comment.tex
edited out Marika (temporarily on her request)
CH typo check read through I think this is ready to send...

@@
 \author{Members of the KiDS, CFHTLenS and RCSLenS collaborations; \\
-M. Asgari, J. Harnois-D\'eraps, C. Heymans, H. Hildebrandt, S. Joudaki,  M. Kilbinger, F. K\"ohlinger, K. Kuijken, P. Schneider, P. Simon, L. Van Waerbeke, M. Viola}%\altaffilmark{1} ....}
+J. Harnois-D\'eraps, C. Heymans, H. Hildebrandt, S. Joudaki,  M. Kilbinger, F. K\"ohlinger, K. Kuijken, P. Schneider, P. Simon, L. Van Waerbeke, M. Viola}%\altaffilmark{1} ....}
 %\email{tbd@tbd}
+%M. Asgari,
 
@@
 In this comment paper we discuss the flat-sky and Limber approximations that can be used when deriving theoretical predictions for the principally used cosmic shear statistic, $\xi_\pm$, the two-point shear correlation functions.
-The Limber approximation for cosmic shear was previously explored by \citet{giannantonio/etal:2012} finding that it provided sufficient accuracy for future cosmic shear studies.
-Recently, however, \citet{kitching/etal:2016} reported that when considering the flat-sky and Limber approximations in concert, tensions between weak lensing and CMB experiments can be reduced.
+\citet{kitching/etal:2016} report that when considering the flat-sky and Limber approximations in concert, tensions between weak lensing and CMB experiments can be reduced.
 They illustrate the effect with a re-analysis of the non-tomographic weak lensing data from the CFHTLenS survey \citep{kilbinger/etal:2013}.
-On initial inspection we found that these claims appeared implausible, for two reasons: First, in a naive estimate, the deviation of flat-sky approximation from a full treatment are expected to be of similar order as the fractional difference between $\theta_{\rm max}$ and $\sin\theta_{\rm max}$,
+On initial inspection we found that these claims appeared implausible, for two reasons: First, in a naive estimate, the deviation of a flat-sky approximation from a full treatment is expected to be of a similar order to the fractional difference between $\theta_{\rm max}$ and $\sin\theta_{\rm max}$,
 where $\theta_{\rm max}$ is the maximum angular scale considered in the cosmic shear analysis.
-In the case of \citep{hildebrandt/etal:2016}, where $\theta_{\rm max}=50$ arcmin, $(\theta_{\rm max} - \sin\theta_{\rm max})/\theta_{\rm max} \approx 3.52 \times 10^{-5}$.
-Second, it was shown in \citet[][see their Fig.3]{giannantonio/etal:2012} that the difference between the Limber approximation and exact treatment is far smaller than cosmic variance, even for a full-sky cosmic shear survey.
+In the case of \citet{hildebrandt/etal:2016}, where $\theta_{\rm max}=50$ arcmin, $(\theta_{\rm max} - \sin\theta_{\rm max})/\theta_{\rm max} \approx 3.5 \times 10^{-5}$.
+Second, it was shown in \citet[][see their Fig.3]{giannantonio/etal:2012} that the difference between the Limber approximated shear power spectrum and one calculated using an exact treatment is far smaller than cosmic variance, even for a full-sky cosmic shear survey.
 
@@
 In section~\ref{sec:cfhtlens} we present a `one-parameter' cosmological re-analysis of 2D cosmic shear data from \citet{kilbinger/etal:2013} which is inconsistent with the analysis presented in \citet{kitching/etal:2016}.
-We also briefly review the literature that has advanced our understanding since the original CFHTLenS analyses were published and discuss the impact of flat-sky and Limber approximations in our analysis of numerical simulations, CMB lensing and quadratic estimators for cosmic shear power spectrum.
+We also briefly review the literature that has advanced our understanding since the original CFHTLenS analyses were published and discuss the impact of flat-sky and Limber approximations in our analysis of numerical simulations, CMB lensing and quadratic estimators for the cosmic shear power spectrum.
 

### 2016-12-09 cfhtlens.tex
CH typo check read through I think this is ready to send...

--- 2016-12-08 cfhtlens.tex
@@
 
-\citet{kitching/etal:2016} chose to only vary $\sigma_8$ in their analysis, fixing all other parameters to Planck values.
-They find a conditional value of $\sigma_8 = 0.789 \pm 0.015$ for their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) of the data from \citet{kilbinger/etal:2013}.
-This can be compared to the full five-parameter fit from \citet{kilbinger/etal:2013} who find $S_8=\sigma_8(\Omega_m/0.3)^{0.6} = 0.74 \pm 0.03$.
+The \citet{kitching/etal:2016} re-analysis of the 2D CFHTLenS data from \citet{kilbinger/etal:2013} chose to only vary $\sigma_8$ in their analysis, fixing all other parameters to Planck values.
+They find a conditional value of $\sigma_8 = 0.789 \pm 0.015$ for their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}).
+This result can be compared to the full five-parameter fit from \citet{kilbinger/etal:2013} who find $S_8=\sigma_8(\Omega_m/0.3)^{0.6} = 0.74 \pm 0.03$.
 We argue that this reduction in the relevant error by a factor of $\sim 2$, could easily mislead, making it appear that the impact of removing all approximations from the theoretical analysis is more significant for current surveys than it is in reality.
@@
 
-We note that \citet{kitching/etal:2016} use their `Flat' approximation for the `Full' non-Limber analysis of the CFHTLenS data.
+We note that \citet{kitching/etal:2016} use their `Flat' approximation for their `Full' non-Limber analysis of the CFHTLenS data.
 This is because on a sphere, correlation functions cannot be related to the power spectrum by a Hankel transform (e.g.
@@
 \citet{kilbinger/etal:2013} present a detailed comparison of cosmological constraints obtained from a range of different two-point shear statistics including the shear correlation function, $\xi_\pm$, the aperture-mass dispersion, $\langle M_ {\rm ap} \rangle ^2$ \citep{schneider/etal:1998}, and the COSEBIs, $E_n$ \citep{schneider/etal:2010}.
-These statatistics are linearly related to the power spectrum via integrals of the form,
+These statistics are linearly related to the power spectrum via integrals of the form,
 %
@@
 %
-where $W_n(\ell)$ and $U^2_\theta(\ell)$ are defined in \cite{schneider/etal:2010} and \cite{schneider/etal:1998}. The corresponding equations for $\xi_\pm$ is given in \eqref{eqn:xiGG}.
+where $W_n(\ell)$ and $U^2_\theta(\ell)$ are defined in \cite{schneider/etal:2010} and \cite{schneider/etal:1998}. The corresponding equation for $\xi_\pm$ is given in equation~\ref{eqn:xiGG}.
 Figure~\ref{fig:filters} shows the integrands of these statistics 
-for two cases, normalised to their maximum value. 
-The integrands are of the form $\ell F(\ell) P(\ell)$ (see equations~\ref{eqn:xiGG} and \ref{eqn:integ}).
-For $\xi_\pm$, $P(\ell)$ is equal to the sum of the E and B-mode power spectra.
-This is one of the main motivators for the development of aperture-mass dispersion.
-However, $\langle M_ {\rm ap} \rangle ^2$ statistics is a lossy conversion and is biased by small angular separations, where blending of galaxies makes shear measurement challenging/impossible \citep{kilbinger/etal:2006}.
-As a result, COSEBIs was developed which tackles both shortcomings of $\langle M_ {\rm ap} \rangle ^2$ statistics.
-The upper two panels show the integrands\footnote{Note that the lower left panel of Fig.
+for two cases, normalised to their maximum value, where the integrands are of the form $\ell F(\ell) P(\ell)$.
+For $\xi_\pm$, $P(\ell)$ is equal to the sum of the E and B-mode power spectra, motivating the development of the aperture-mass dispersion statistic, $\langle M_ {\rm ap} \rangle ^2$.
+This statistic is, however, a lossy conversion and is biased by small angular separations, where blending of galaxies makes shear measurement challenging \citep{kilbinger/etal:2006}.
+The COSEBIs statistic tackles both these shortcomings.
+The upper two panels of figure~\ref{fig:filters} show the integrands\footnote{Note that the lower left panel of Fig.
 1 in \citet{kitching/etal:2016} shows an integrated form of this function for a maximum angular separation of $100'$.
@@
 Finally, the lowest panel shows the integrands of aperture mass dispersion statistics, for the same two maximum angular ranges.
-
-From Figure~\ref{fig:filters} we can see that the two-point cosmic shear statistics tested by \citet{kilbinger/etal:2013} exhibit different dependences between the angular scales sampled and the $\ell$-range probed.
-If a significant bias had been introduced at low-$\ell$ by using flat-sky and Limber approximations, we would then expect to see a systematic shift between the different two-point statistics with the COSEBIs statistic being essentially unaffected as it only includes modes with $\ell \gtrsim 20$.
-This is found not to be the case with all three statistics finding $\sigma_8 (\Omega_m/0.27)^\alpha = 0.79$ with errors that range from $0.03$ to $0.06$ for the full five-parameter fit, and $\alpha$ ranging from $0.59$ to 0.7 \citep[see Table 5 of][]{kilbinger/etal:2013}.
-This comparison further supports our argument that the approximations highlighted by \citet{kitching/etal:2016} have negligible impact for current surveys.
 
@@
 \end{tabular}
-\caption{ \small{\label{fig:filters}. Integrand of $\xi_+$ (upper), $\xi_-$ (upper middle), $E_1$ ( lower middle, E-COSEBIs) and $\langle M_{\rm ap} \rangle^2$ (lower panel).
+\caption{ \small{\label{fig:filters}. Integrand of $\xi_+$ (upper), $\xi_-$ (upper middle), $E_1$ (lower middle, E-COSEBIs) and $\langle M_{\rm ap} \rangle^2$ (lower panel).
 All integrands are of the form $\ell F(\ell) P(\ell)$, where $F(\ell)$ is the corresponding weight-function
 for each statistic and $P(\ell)$ is the E-mode convergence power spectrum, with the exception of $\xi_\pm$, for which
-$P(\ell)$ is equal to the sum of E and B-mode power spectra. 
+$P(\ell)$ is equal to the sum of the E and B-mode power spectra. 
 Two cases are shown for each statistic as listed in each caption.
@@
 
+From Figure~\ref{fig:filters} we can see that the two-point cosmic shear statistics tested by \citet{kilbinger/etal:2013} exhibit different dependences between the angular scales sampled and the $\ell$-range probed.
+If a significant bias had been introduced at low-$\ell$ by using flat-sky and Limber approximations, we would then expect to see a systematic shift between the different two-point statistics with the COSEBIs statistic being essentially unaffected as it only includes modes with $\ell \gtrsim 20$.
+This is found not to be the case with all three statistics finding $\sigma_8 (\Omega_m/0.27)^\alpha = 0.79$ with errors that range from $0.03$ to $0.06$ for the full five-parameter fit, and $\alpha$ ranging from $0.59$ to 0.7 \citep[see Table 5 of][]{kilbinger/etal:2013}.
+This comparison further supports our argument that the approximations highlighted by \citet{kitching/etal:2016} have negligible impact for current surveys.
+
 \subsection{On the Validation of Methods on Simulations}
@@
 Going beyond flat-sky and Limber could improve the agreement, however this cannot explain the results of \citet{harnois-deraps/vanwaerbeke:2015} who demonstrate that the large-scale under-estimation of power varies with the simulation box size.
-This volume effect was verified by comparing explicitly the $\xi_+$ statistic at large angular scales between simulation volumes with box sides  ranging from 147$\;\rm{Mpc/h}$ to 515$\;\rm{Mpc/h}$ \citep[see Fig.
+This volume effect was verified by comparing the $\xi_+$ statistic at large angular scales between simulation volumes with box sides  ranging from $147\;\rm{Mpc/h}$ to $515\;\rm{Mpc/h}$ \citep[see Fig.
 5 in][]{harnois-deraps/vanwaerbeke:2015}.
@@
 
-\subsection{On the quadratic estimator}
+\subsection{On the quadratic estimator of the cosmic shear power spectrum}
 
@@
 In this quadratic estimator implementation, however, the Limber approximation does not enter.
-The algorithm was originally presented by \citet{Hu2001} in the context of cosmic shear and has also been applied to other shear data sets (e.g.
+
+The quadratic estimator algorithm was originally presented by \citet{Hu2001} in the context of cosmic shear and has also been applied to other shear data sets (e.g.
 \citealt{Brown2003, Heymans2005, Lin2012}).
-Below we briefly summarize this quadratic estimator algorithm and emphasize that the Limber approximation does not enter in there.
-
 The aim of the method is to find the best-fitting power spectra assuming a Gaussian likelihood function $\mathcal{L}$.
@@
 $\partial \mathbf{C} / \partial \mathcal{B}_A$, where $A$ is a superindex over the type of the band, band-power bin and redshift correlation, see appendix\~A in \citealt{Koehlinger2016}.}.
-The only approximation entering in the algorithm is the flat-sky approximation when introducing the Fourier decomposition of the spin-2 shear field.
+We emphasize that the only approximation entering this algorithm is the flat-sky approximation when introducing the Fourier decomposition of the spin-2 shear field.
 This approximation is appropriate and accurate for current surveys as $\ell>80$  in all analyses published to date.

### 2016-12-09 conclusion.tex
CH typo check read through I think this is ready to send...

@@
 Our critique should not, however, detract from the important core message of their paper, that future surveys will need to consider these approximations and optimise their statistical analyses accordingly.
-For example moving from the standard two-point shear correlation function statistic to the more stringent `COSEBI' statistic \citep{schneider/etal:2010} renders the cosmic shear measurement completely insensitive to the low-$\ell$ scales where these approximations become important.
+For example moving from the standard two-point shear correlation function statistic to the more stringent `COSEBI' statistic \citep{schneider/etal:2010} renders the cosmic shear measurement insensitive to the low-$\ell$ scales where these approximations become important.
 
@@
 More importantly though, we suggest that \cite{kitching/etal:2016} have applied the photo-$z$ calibrations from \cite{choi/etal:2016} in the wrong sense.
-Instead of alleviating the tension between CFHTLenS and Planck a correct application of the offsets would increase the discrepancy, as shown with a recent re-analysis of the CFHTLenS data \citep{joudaki/etal:2016} as well as results from the KiDS project \citep{hildebrandt/etal:2016}.
+Instead of alleviating the tension between CFHTLenS and Planck, a correct application of the offsets would increase the discrepancy, as shown with a recent re-analysis of the CFHTLenS data \citep{joudaki/etal:2016} as well as results from the KiDS project \citep{hildebrandt/etal:2016}.
 

### 2016-12-09 theory.tex
minor
edited out Marika (temporarily on her request)
CH typo check read through I think this is ready to send...

@@
 Figure~\ref{fig:Cl_xi} shows theoretical models for the shear power spectrum $P_\gamma(\ell)$ (equation~\ref{eqn:Pkappa}), and the shear correlation function (equation~\ref{eqn:xiGG}) for the different variations on the approximations listed in Table~\ref{tab:Tl_nu}.
-The Standard and Spherical models agree at the few percent level above $\ell>10$ and below $\theta< 100$ arcmin.
+The Standard and Spherical models agree at the few percent level above $\ell>20$ and below $\theta< 100$ arcmin.
 The two outliers are the Baseline and Extended `Flat' Sky Limber cases (LF and ELF) where the \citet{kitching/etal:2016} `Flat' Sky approximation has been made with
@@
 T_\ell^{\rm `Flat'} = \ell^4 / (\ell + 0.5)^4 = 1-{2\over \ell}+{5\over 2\ell^2} +{\cal O}(\ell^{-3}) \, . 
+\label{eqn:Tlflat}
 \ee    
@@
 
-As shown in the lower panels of Figure~\ref{fig:Cl_xi}, the `standard flat' sky approximation used by recent cosmic shear surveys\footnote{The KSt approximation was used for pre-2014 CFHTLenS analysis and the ESt approximation was used for recent CFHTLenS and KiDS analyses}, where $T_\ell = 1$, recovers a very similar result to the spherical sky case.
+As shown in the lower panels of Figure~\ref{fig:Cl_xi}, the `standard flat' sky approximation used by recent cosmic shear surveys\footnote{The KSt approximation was used for pre-2014 CFHTLenS analysis and the ESt approximation was used for recent CFHTLenS and KiDS analyses.}, where $T_\ell = 1$, recovers a very similar result to the spherical sky case.
 Over angular scales used in the recent KiDS cosmic shear analysis (where the maximum angular scale $\theta<50.7$ arcmin is shown dashed), these curves differ by less than 1\%.
@@
 In collecting our comments on \citet{kitching/etal:2016} we contacted colleagues who had previously tested the impact of the Limber approximation on cosmic shear studies by comparing a Limber-approximated cosmic shear power spectrum with an exact calculation.
-The majority of these analyses, carried out many years ago, remained unpublished in peer reviewed journals as no significant deviation was found\footnote{See for example appendix M of the 2010 PhD thesis from Donghui Jeong (\url{http://www.personal.psu.edu/duj13/dissertation/djeong_diss_appM.pdf}) and Chapter 7 of 2012 PhD thesis from Nicolas Van de Rijt (\url{http://ipht.cea.fr/Docspht/articles/t12/080/public/these_vanderijt2012.pdf}).}.
+The majority of these analyses remained unpublished in peer reviewed journals as no significant deviation was found\footnote{See for example appendix M of the 2010 PhD thesis from Donghui Jeong (\url{http://www.personal.psu.edu/duj13/dissertation/djeong_diss_appM.pdf}) and Chapter 7 of 2012 PhD thesis from Nicolas Van de Rijt (\url{http://ipht.cea.fr/Docspht/articles/t12/080/public/these_vanderijt2012.pdf}).}.
 One notable exception, however, is \citet{giannantonio/etal:2012} who find that for a cosmic shear power spectrum, the extended Limber approximation is consistent with the exact calculation for $\ell>5$, with any differences well within cosmic-variance errors for a Euclid-like survey\footnote{\citet{kitching/etal:2016} comment on this result, but indicate that it is in error owing to the application of a fixed low-$\ell$ limit.
 \citet{giannantonio/etal:2012} however state that this limit is only applied in a positive curvature case.}.
-They conclude that the Limber approximation works so well for cosmic shear owing to the wide redshift distribution of the lensed sources.
-This is in comparison to the case of galaxy power spectra,  where narrower redshift bins result in a significant difference between the Limber and non-Limber cases \citep[see also][]{simon/2007}.
+They conclude that the Limber approximation works well for cosmic shear owing to the wide redshift distribution of the lensed sources.
+This is in contrast to the case of galaxy power spectra,  where narrower redshift bins result in a significant difference between the Limber and non-Limber cases \citep[see also][]{simon/2007}.
 Given this body of work, we argue that the assertion by \citet{kitching/etal:2016} that the majority of cosmic shear data analyses to date have made an `axiomatic assumption (i.e.
@@
 Two exceptions to this are recent updates to CLASS \citep{blas/lesgourgues/tram:2011,audren/etal:2013} and CosmicFish \citep{raveri/etal:2016}.
-On-going code comparisons have, however, revealed differences that are larger than the expected impact of Limber or non-Limber approximation.
+On-going code comparisons have, however, revealed differences between the calculated theoretical models that are larger than the expected impact of Limber or non-Limber approximation.
 We are therefore unable to readily determine non-Limber theoretical calculations for the shear-correlation function to directly compare with the results of \citet{kitching/etal:2016}.

### 2016-12-09 theory.tex
moved note about typo in eqn 4 into the main body of the text

@@
 In \citet{kitching/etal:2016} it is not fully clear which combinations of  $T_\ell$ and $\nu(\ell)$ are considered, so we review them all as summarised in Table~\ref{tab:Tl_nu}, also highlighting which combinations were used in recent cosmic shear analyses.
+We note and confirm that there is a typographical error in equation 4 of \citet{hildebrandt/etal:2016} which should have included the extra term of `$+0.5$' in $\nu(\ell)$ that was incorporated in the cosmological analysis.
 
@@
 Extended Standard Flat Sky & ESt & $1$ & $\ell + 0.5$ & \citet{joudaki/etal:2016} \&  \\
-  &  & & & \citet{hildebrandt/etal:2016}$^*$\\\hline
+  &  & & & \citet{hildebrandt/etal:2016}\\\hline
  \end{tabular}
  \end{center}
- \caption{\label{tab:Tl_nu}Variations on the different approximations that can be made when calculating the shear power spectrum $P_\gamma(\ell)$ (equation~\ref{eqn:Pkappa}), using a Limber approximation.
-$^*$We confirm that there is a typographical error in equation 4 of \citet{hildebrandt/etal:2016} which should include the extra term of `$+0.5$' in $\nu(\ell)$ that was incorporated in the cosmological analysis.}
+ \caption{\label{tab:Tl_nu}Variations on the different approximations that can be made when calculating the shear power spectrum $P_\gamma(\ell)$ (equation~\ref{eqn:Pkappa}), using a Limber approximation.}
  \end{table}

### 2016-12-09 cfhtlens.tex
Added MK's final comments

@@
 This is not the case when considering the standard $T_\ell = 1$ flat-sky approximation that has been used in the majority of cosmic shear studies to date.
-We would therefore argue that it is more appropriate to use a $T_\ell = 1$ flat-sky approximation when carrying out a `Full' non-Limber analysis of the shear correlation function.
+We would therefore argue that it is more appropriate to use a $T_\ell = 1$ flat-sky approximation when carrying out a `Full' non-Limber analysis of the shear correlation function obtained from the Hankel transformation (equation~\ref{eqn:xiGG}).
 

### 2016-12-09 theory.tex
Added MK's final comments

@@
 In collecting our comments on \citet{kitching/etal:2016} we contacted colleagues who had previously tested the impact of the Limber approximation on cosmic shear studies by comparing a Limber-approximated cosmic shear power spectrum with an exact calculation.
-The majority of these analyses remained unpublished in peer reviewed journals as no significant deviation was found\footnote{See for example appendix M of the 2010 PhD thesis from Donghui Jeong (\url{http://www.personal.psu.edu/duj13/dissertation/djeong_diss_appM.pdf}) and Chapter 7 of 2012 PhD thesis from Nicolas Van de Rijt (\url{http://ipht.cea.fr/Docspht/articles/t12/080/public/these_vanderijt2012.pdf}).}.
-One notable exception, however, is \citet{giannantonio/etal:2012} who find that for a cosmic shear power spectrum, the extended Limber approximation is consistent with the exact calculation for $\ell>5$, with any differences well within cosmic-variance errors for a Euclid-like survey\footnote{\citet{kitching/etal:2016} comment on this result, but indicate that it is in error owing to the application of a fixed low-$\ell$ limit.
+The majority of these analyses were not published in peer reviewed journals as no significant deviation was found\footnote{See for example appendix M of the 2010 PhD thesis from Donghui Jeong (\url{http://www.personal.psu.edu/duj13/dissertation/djeong_diss_appM.pdf}).}.
+Two notable exceptions, however, are \citet{giannantonio/etal:2012} and \citet{bernardeau/etal:2012}.
+Figure 1 of \citet{bernardeau/etal:2012} shows that the Baseline Limber approximated cosmic shear power spectrum is accurate to better than 1\% at $\ell > 8$.
+\citet{giannantonio/etal:2012} also find that the extended Limber approximation is consistent with the exact calculation for their minimum tested $\ell>5$, with any differences well within cosmic-variance errors for a Euclid-like survey\footnote{\citet{kitching/etal:2016} comment on this result, but indicate that it is in error owing to the application of a fixed low-$\ell$ limit.
 \citet{giannantonio/etal:2012} however state that this limit is only applied in a positive curvature case.}.
@@
 This is in contrast to the case of galaxy power spectra,  where narrower redshift bins result in a significant difference between the Limber and non-Limber cases \citep[see also][]{simon/2007}.
+
 Given this body of work, we argue that the assertion by \citet{kitching/etal:2016} that the majority of cosmic shear data analyses to date have made an `axiomatic assumption (i.e.
@@
 We are therefore unable to readily determine non-Limber theoretical calculations for the shear-correlation function to directly compare with the results of \citet{kitching/etal:2016}.
-Instead we refer the reader to Figure 3 of \citet{giannantonio/etal:2012} to draw their own conclusions about the impact of this effect.
+Instead we refer the reader to Figure 3 of \citet{giannantonio/etal:2012} and Figure 1 of  \citet{bernardeau/etal:2012} to draw their own conclusions about the impact of this effect.

### 2016-12-09 cfhtlens.tex
added comments from Lance

@@
 We argue that this reduction in the relevant error by a factor of $\sim 2$, could easily mislead, making it appear that the impact of removing all approximations from the theoretical analysis is more significant for current surveys than it is in reality.
-Nevertheless, we repeated the `one-parameter' analysis for the full range of Limber cases listed in Table~\ref{tab:Tl_nu} and are unable to confirm the results quoted by \citet{kitching/etal:2016}.
+Nevertheless, we repeated the `one-parameter' analysis for the range of Limber-approximated cases listed in Table~\ref{tab:Tl_nu} and are unable to confirm the results quoted by \citet{kitching/etal:2016}.
 We find the lowest conditional value of $\sigma_8 = 0.746 \pm 0.023$ for the `Standard' (KSt) case and the highest conditional value of $\sigma_8 = 0.749 \pm 0.023$ for the `Extended Limber Flat' (ELF) case, a maximum change of $\Delta \sigma_8 = 0.0026 = 0.11 \sigma$.

### 2016-12-09 theory.tex
removed l+x = l sentance in preference for the expansion argument

@@
 \ee    
-We argue that applying the approximation, that $\ell \pm x \approx \ell$, where $x$ is small, only to the numerator of equation~\ref{eqn:Tl} is inconsistent.
-By comparing the expansions of equations~\ref{eqn:Tl} and~\ref{eqn:Tlflat}, we see that the \citet{kitching/etal:2016} `Flat' Sky approximation effectively introduces a new term $2/\ell$ making it more deviant from the full spherical solution in comparison to the standard $T_\ell = 1$ case.
+By comparing the Taylor expansions of equations~\ref{eqn:Tl} and~\ref{eqn:Tlflat}, we find that the \citet{kitching/etal:2016} `Flat' Sky approximation includes an extra term, $2/\ell$, making it more deviant from the full spherical solution, than the standard $T_\ell = 1$ case.
 To our knowledge, this form of the flat-sky approximation has not been used in cosmic shear studies to date.

### 2016-12-14 Limber_Comment.tex
Updating to mnras style

@@
 %\documentclass[a4paper,preprint, fleqn]{aastex}
-\documentclass[a4paper, preprint, fleqn, usenatbib]{aastex}
+%\documentclass[a4paper, preprint, fleqn, usenatbib]{aastex}
+\documentclass[fleqn, usenatbib]{mnras}
 \usepackage{graphicx}   % Including figure files
@@
 
+\title[Comment on `The Limits of Cosmic Shear']{Comment on `The Limits of Cosmic Shear'}
+
+\input{authors}
+
+\date{Released 16/12/2016}
+
+\pagerange{\pageref{firstpage}--\pageref{LastPage}} \pubyear{2016}
+
 \begin{document}
+\setlength{\voffset}{-12mm}
 
-\title{\huge{Comment on `The Limits of Cosmic Shear'}}
+\label{firstpage}
 
-\author{Members of the KiDS, CFHTLenS and RCSLenS collaborations; \\
-J. Harnois-D\'eraps, C. Heymans, H. Hildebrandt, S. Joudaki,  M. Kilbinger, F. K\"ohlinger, K. Kuijken, P. Schneider, P. Simon, L. Van Waerbeke, M. Viola}%\altaffilmark{1} ....}
-%\email{tbd@tbd}
-%M. Asgari,
-
-%\altaffiltext{1}{}
+\maketitle
 
 \begin{abstract}
+
+%\author{Members of the KiDS, CFHTLenS and RCSLenS collaborations; \\
+%J. Harnois-D\'eraps, C. Heymans, H. Hildebrandt, S. Joudaki,  M. Kilbinger, F. K\"ohlinger, K. Kuijken, P. Schneider, P. Simon, L. Van Waerbeke, M. Viola}%
+
 Kitching et al.
@@
 \end{abstract}
+
+\begin{keywords}
+cosmology: observations -- gravitational lensing: weak -- galaxies: photometry -- surveys
+\end{keywords}
+
 \section{Introduction}

### 2016-12-14 authors.tex
Added mnras style files

\author[Heymans, Asgari, Joudaki et al.]
{C. Heymans$^1$\thanks{Email: heymans@roe.ac.uk}, 
M. Asgari$^1$, 
S. Joudaki$^2$, 
J. Harnois-D\'eraps$^1$,
H. Hildebrandt$^3$,
\newauthor
M. Kilbinger$^4$,
F. K\"ohlinger$^5$,
K. Kuijken$^5$,
P. Schneider$^3$,
P. Simon$^3$,
\newauthor
L. Van Waerbeke$^6$,
M. Viola$^5$
\\
$^1$Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK\\
$^2$Centre for Astrophysics \& Supercomputing, Swinburne University of Technology, PO Box 218, Hawthorn, VIC 3122, Australia\\
$^3$Argelander-Institut f\"ur Astronomie, Auf dem H\"ugel 71, 53121 Bonn, Germany\\
$^4$Laboratoire AIM, CEA Saclay - CNRS - Paris 6, Irfu/SAp, F-91191 Gif-sur-Yvette, France\\
$^5$Leiden Observatory, Leiden University, Niels Bohrweg 2, 2333 CA Leiden, the Netherlands\\
$^6$Department of Physics and Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC V6T 1Z1, Canada\\
}

### 2017-02-02 limber2.tex
MK: first commit of limber2 paper

\documentclass[useAMS,usenatbib]{mn2e} %
\pdfoutput=1

%% Packages
\usepackage{amsmath,amssymb,graphicx}
\usepackage{bm,color}% bold math
%\usepackage{ulem}
\usepackage{mathtools}
\usepackage{url}
\usepackage{footnote}
%\makesavenoteenv{tabular}
\makesavenoteenv{table}

\bibpunct{(}{)}{;}{a}{}{,}

\onecolumn

\pagestyle{empty}
\usepackage{psfrag, epsfig}

\newcommand{\ellbar}{\hbox{\it \l}\,}
\newcommand{\pref}{{\cal A}}
\newcommand{\edth}{\,\eth\,}
\renewcommand{\vec}{\bm}

\newcommand{\mk}[1]{{\bf\textcolor{blue}{#1}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title[]
{Precision calculations of the cosmic shear power spectrum projection}

\author[M.~Kilbinger et~al.]
 {
  \parbox[h]{\textwidth}
  {
      Martin Kilbinger$^{1,2}$\thanks{E-mail: martin.kilbinger@cea.fr},
      Catherine Heymans,
      Peter Schneider,
      Shahab Joudaki,
      Marika Asgari,
      and other members of CFHTLenS and KiDS
      $\ldots$,
  }
  % 
  \vspace*{10pt} \\
  \hspace{-.1cm}$^1$ CEA/Irfu/SAp Saclay, Laboratoire AIM, 91191 Gif-sur-Yvette, France\\
  \hspace{-.1cm}$^2$ Institut d'Astrophysique de Paris, UMR7095 CNRS,
           Universit\'e Pierre \& Marie Curie, 98 bis boulevard Arago, 75014 Paris,
           France \\
 }

\voffset-0.50in

\date{\today}

\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2017}

\maketitle

\label{firstpage}

\begin{abstract}

We compute the spherical-sky weak-lensing power spectrum of the shear and
convergence. We discuss various approximations, such as flat-sky, first- and
second-order Limber equations for the projection. We show that the spherical
second-order Limber approximation agrees with the full projection at the
percent level for $\ell > 3$. for current surveys. The real-space shear
correlation functions show excellent agreement between all cases. The
consequence for parameter constraints are negligible for current surveys, which
we demonstrate using CFHTLenS data. In particular, the reported tension with
Planck CMB temperature anisotropy results cannot be alleviated. This is in
contrast to the recent claim made by \citet{2016arXiv161104954K}. In the spirit
of reproducible research, our numerical implementation of all approximations
and the full projection are publically available within the package
\texttt{nicaea} at \texttt{http://www.cosmostat.org/software/nicaea}.

\end{abstract}

\begin{keywords}
cosmological parameters -- methods: statistical
\end{keywords}

\input abbr-journals

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The measurement of weak gravitational lensing by large-scale structures
provides a powerful cosmological probe of dark matter, dark energy, and
modifications to gravity.  As such it is the primary science goal of several
current (KiDS, HSC, DES) and future (Euclid, LSST, WFIRST) large surveys.
Interest in the results from these surveys is high as statistically significant
deviations have been found between the cosmological parameter constraints from
the CMB Planck experiment \citep{2015arXiv150201589P} in comparison to weak
lensing constraints from both the Kilo-Degree Survey \citep[KiDS;][]{KiDS-450}
and the Canada-France-Hawaii Telescope Lensing Survey
\citep[CFHTLenS;][]{2016arXiv160105786J}.  If the source of this tension is not
a result of so-far unconsidered sources of systematic errors in one or all
experiments, extensions to the standard flat $\Lambda$CDM cosmological models
need to be considered. \citet{joudaki/etal:2017} have shown, for example, that
the tension can be resolved with an evolving dark energy model.

In the era of the upcoming large surveys that will provide measurements of
cosmic shear with unprecedented precision, one needs to revisit the theoretical
model predictions of the observables to make sure that the accuracy of the
models meet the upcoming data. In this paper, we examine the widely used Limber
approximation for the projected weak-lensing power spectrum. We consider
spherical coordinates and the flat-sky approximation, and compute the full
projection as well as first- and second-order Limber approximation. We show
that the latter is an excellent approximation of the full projection. Since it
involves only 1D integrals over the matter power specrum, it is very fast to
calculate numerically and can readily employed in Monte-Carlo sampling methods
to obtain precision constraints on cosmological parameters.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Weak-lensing projections and power spectra}
\label{sec:wl}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In this section we review the basic weak-lensing projection expressions, and
compute lensing power spectra for a spherical case, and in the flat-sky
approximation. Derivations for those expressions can be found in the appendix.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The lensing potential}
\label{sec:psi}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The lensing potential $\psi$ in the Born approximation is defined as the
projected 3D metric potential $\Phi$ along the line of sight
\citep{1998ApJ...498...26K,BS01},
%
% Hu00 (21,22) with minus sign
%
\begin{equation}
  \psi(\theta, \varphi) = \frac 2 {{\rm c}^2} \int_0^{\chi_{\rm lim}} \frac{{\rm d}\chi}{\chi}
    \Phi[\chi, f_K(\chi) \theta, f_K(\chi) \varphi; \chi] \, q(\chi),
  \label{eq:psi}
\end{equation}
%
where the lensing efficiency $q$ is given by
%
\begin{equation}
  q(\chi) = \int\limits_\chi^{\chi_{\rm lim}} {\rm d} \chi^\prime \, n(\chi^\prime)
    \frac{f_K(\chi^\prime - \chi)}{f_K(\chi^\prime)},
  %
  \label{eq:lens_efficiency}
\end{equation}
%
corresponding to a population of lensed galaxies with source redshift
distribution $n(z) {\rm d}z = n(\chi) {\rm d} \chi$. Here, ${\rm c}$ is the
speed of light, the projection is carried out over comoving distances $\chi$ up
to a limiting distance $\chi_{\rm lim}$, and $f_K$ is the the comoving angular
distance, which depend on the spatial curvature of the Universe $K$.
%
This assumes a homogeneous galaxy distribution without clustering, so that the
redshift distribution in this approximation does not depend on the position
$(\theta, \varphi)$. Accounting for this position dependence leads to
correction of weak-lensing quantities due to clustering of source galaxies with
other sources \citep{2002A&A...389..729S}, and with galaxies associated with
lens structures \citep{1998A&A...338..375B,H02}.

The 3D potential is related to the density contrast $\delta$ via the Poisson
equation. Assuming General Relativity, this relation is written in Fourier space as
%
\begin{align}
  \hat \Phi(\vec k; \chi) = & - \frac 3 2 \Omega_{\rm m} H_0^2 k^{-2} a^{-1}(\chi) \hat \delta(\vec k; \chi),
      \label{eq:poisson}
\end{align}
%
where $\Omega_{\rm m}$ is the matter density parameter, $H_0$ the Hubble constant, $\vec k$ a 3D Fourier wave
vector, and $a$ the scale factor with $a=1$ today.
The Fourier transform of the potential and its inverse are defined as
%
\begin{align}
  \hat \Phi(\vec k; \chi) = &  \int {\rm d}^3 r \, \Phi(\vec r; \chi) {\rm e}^{{\rm i} \vec k \vec r} .
  \label{eq:hatPhi}
  \\
  \Phi(\vec r; \chi) = &  \int \frac{{\rm d}^3 k}{(2\pi)^3}
      \hat \Phi(\vec k; \chi) {\rm e}^{-{\rm i} \vec r \vec k},
  \label{eq:hatPhi_inv}
\end{align}
%
where the integration range for both integrals is $\mathbb{R}^3$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Lensing power spectra in the spherical case}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Lensing potential power spectrum}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Following \cite{2000PhRvD..62d3007H} we decompose the lensing potential
(\ref{eq:psi}) into a spherical harmonics expansion, in analogy of CMB
temperature, both of which are scalar functions on the sphere. This
decomposition and its inverse are
%
% Hu00 (23)
%
\begin{align}
  \psi(\theta, \varphi) = \sum_{\ell=0}^\infty \sum_{m=-\ell}^\ell \psi_{\ell m} {\rm Y}_{\ell m}(\theta, \varphi);
    \label{eq:psi_harm_exp}
    \\
    %
  \psi_{\ell m} = \int_{\mathbb{S}^2} {\rm d} \Omega \, \psi(\theta, \varphi) {\rm Y}^\ast_{\ell m}(\theta, \varphi).
  \label{eq:psi_harm_exp_inv}
\end{align}

To specify tomographic redshift bins $i=0\ldots N_z-1$, we introduce a family
of lensing efficiency functions $q_i$ defined by a corresponding family of
redshift distributions $n_i$ via eq.~(\ref{eq:lens_efficiency}). The resulting
lensing potential is denoted by $\psi_{\ell m, i}$. The tomographic power
spectrum of the lensing potential between two redshift bins $i$ and $j$,
$C_{ij}^\psi$ is then defined by
%
\begin{equation}
  \left\langle \psi^{}_{\ell m, i} \, \psi^\ast_{\ell^\prime m^\prime, j} \right\rangle
    = \delta_{\ell \ell^\prime} \delta_{m m^\prime} C^\psi_{ij}(\ell) .
  \label{eq:C_ell_psi}
\end{equation}
%
Using the properties of the spherical harmonics (see
App.~\ref{sec:derivations_C} for details) the power spectrum can be written as
%
\begin{align}
  C_{ij}^\psi(\ell) = & \frac 8 {c^4 \pi} 
  \int_0^{\chi_{\rm lim}} \frac{{\rm d}\chi}{\chi} q_i(\chi)
  \int_0^{\chi^\prime_{\rm lim}} \frac{{\rm d}\chi^\prime}{\chi^\prime} q_j(\chi^\prime)
  \int {\rm d} k k^2 \, {\rm j}_\ell(k \chi) {\rm j}_\ell(k \chi^\prime) P_\Phi(k; \chi, \chi^\prime)
  \label{eq:C_ell_phi_Pphi} \\
  = & \frac 8 \pi \pref^2
  \int_0^{\chi_{\rm lim}} \frac{{\rm d}\chi}{\chi} \frac{q_i(\chi)}{a(\chi)}
  \int_0^{\chi^\prime_{\rm lim}} \frac{{\rm d}\chi^\prime}{\chi^\prime} \frac{q_j(\chi^\prime)}{a(\chi^\prime)}
  \int \frac{{\rm d} k}{k^2} \, {\rm j}_\ell(k \chi) {\rm j}_\ell(k \chi^\prime) P_{\rm m}(k; \chi, \chi^\prime) ;
  \label{eq:C_ell_phi_Pm}
\end{align}
%
where for convenience we defined the normalisation constant $\pref$ as
%
\begin{equation}
  \pref = \frac 3 2 \Omega_{\rm m} \left(\frac{H_0} c\right)^2.
  \label{eq:pref}
\end{equation}

In the following section we will discuss the relations between of shear and
convergence to the lensing potential on the sphere, and derive the power
spectrum of the former two fields.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Shear power spectrum}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The shear $\gamma = \gamma_1 + {\rm i} \gamma_2$ is related to the potential at
linear order by the trace-free part of the Jacobi matrix. The involved
differential operator on the sphere is called \emph{edth} derivative, $\edth$,
see \cite{2005PhRvD..72b3516C} for a in-depth mathematical discussion of this
concept. The edth operator $\edth$ ($\edth^\ast$) raises (lowers) the spin $s$
of an object. Twice applying this operator to the scalar (spin-0) potential
creates the spin-2 shear:
%
\begin{align}
  \gamma(\theta, \varphi) = & \frac 1 2 \edth \edth \psi(\theta, \varphi).
    \nonumber \\
  \gamma^\ast(\theta, \varphi) = & \frac 1 2 \edth^\ast \edth^\ast \psi(\theta, \varphi).
  \label{gamma_psi_spher}
\end{align}
%
To write the shear on the sphere in terms of the lensing potential $\psi$, we
insert the harmonics expansion of the potential (\ref{eq:psi_harm_exp}). This
requires to compute second derivatives of the spherical harmonic functions.
This opereration defines a new object, the \emph{spin-weighted spherical
harmonic} $_s{\rm Y}_{\ell m}$. The shear can be written on the sphere in terms
of these functions as a spherical harmonics multipole expansion with
coefficients $_{\pm 2} \gamma_{\ell m}$. This expansion together with its inverse
is
%
% Hu04 (A10), van de Rijt PhD (6.32)
%
\begin{align}
  (\gamma_1 \pm {\rm i} \gamma_2)(\theta, \varphi) = & \sum_{\ell m} \,\, _{\pm 2}\gamma_{\ell m} \; _{\pm 2}\!{\rm Y}_{\ell m}(\theta, \varphi);
  \label{eq:gamma_harm_exp}
    \\
  \, _2 \gamma_{\ell m} = & \int_{\mathbb{S}^2} {\rm d} \Omega \, \gamma(\theta, \varphi) \;  _2\!{\rm Y}^\ast_{\ell m}(\theta, \varphi);
    \nonumber \\
  \, _{-2} \gamma_{\ell m} = & \int_{\mathbb{S}^2} {\rm d} \Omega \, \gamma^\ast(\theta, \varphi) \,  _{-2}\!{\rm Y}^\ast_{\ell m}(\theta, \varphi).
  \label{eq:gamma_harm_exp_inv}
\end{align}
%
The spin-weighted spherical harmonics $_s\!{\rm Y}_{\ell m}$ that are the basis function
in the expansion of the shear (\ref{eq:gamma_harm_exp}) can be calculated via the relations
%
% Rijt (6.16); BBRV12 (9)
%
\begin{align}
  \ellbar(\ell, s) \; _s\!{\rm Y}_{\ell m}(\theta, \varphi) = & \edth^s {\rm Y}_{\ell m}(\theta, \varphi);
    \nonumber \\
  \ellbar(\ell, s) \; _{-s}\!{\rm Y}_{\ell m}(\theta, \varphi) = & (-1)^s \left(\edth^\ast\right)^s {\rm Y}_{\ell m}(\theta, \varphi),
  \label{eq:sYlm_def} 
\end{align}
%
with the spin prefactor \citep{2012PhRvD..86b3001B}
%
\begin{equation}
  \ellbar(\ell, s) = \sqrt{\frac{(\ell + s)!}{(\ell - s)!}}.
\end{equation} 
%
Inserting the lensing potential expansion (\ref{eq:psi_harm_exp}) into the
expression for the shear (\ref{gamma_psi_spher}), and using (\ref{eq:sYlm_def})
to compute the derivatives, we find for the shear expansion coefficients
\citep{2000PhRvD..62d3007H,2001astro.ph.11605T}
%
% Rijt after (7.5); Taylor01 (18); Hu00 (A10)
%
\begin{equation}
  _{\pm 2} \gamma_{\ell m} = \frac 1 2 \ellbar(\ell, 2) \psi_{\ell m}.
  \label{eq:gamma_ellm_phi_ellm}
\end{equation}
%
The two coefficients $_{+2} \gamma_{\ell m}$ and $_{-2} \gamma_{\ell m}$ are
identical since the potential $\phi$ is a real function.

The tomographic shear power spectrum, in analogy to (\ref{eq:C_ell_phi_Pm}), is defined by
%
\begin{equation}
  \left\langle _2\gamma^{}_{\ell m, i} \; {}_2\gamma^\ast_{\ell^\prime m^\prime, j} \right\rangle
    = \delta_{\ell \ell^\prime} \delta_{m m^\prime} C^\gamma_{ij}(\ell).
  \label{eq:C_ell_gamma}
\end{equation}
%
For a flat Universe, this is given by
%
\begin{align}
  C^\gamma_{ij}(\ell) = \frac 1 4 \ellbar^2(\ell, 2) \, C^\psi_{ij}(\ell)
                 = & \frac 2 \pi \, \ellbar^2(\ell, 2) \, \pref^2
                 \int_{0}^{\chi_{\rm lim}} \frac{\rm d \chi}{\chi} \frac{q_i(\chi)}{a(\chi)}
                \int_{0}^{\chi_{\rm lim}} \frac{\rm d \chi^\prime}{\chi^\prime}
                \frac{q_j(\chi^\prime)}{a(\chi^\prime)}
                %\nonumber \\
                %& \times
                \int_0^\infty \frac{{\rm d} k}{k^2} \, P_{\rm m}(k, \chi, \chi^\prime) \,
                {\rm j}_\ell(k \chi) \, {\rm j}_\ell(k \chi^\prime) .
  \label{eq:C_ell_full}
\end{align}
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Convergence power spectrum}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The convergence is related to the lensing potential on the sphere via the
product of spin-raising and spin-lowering edth operators, which are identical
to the spherical Laplacian differential operator.

%
\begin{equation}
  \kappa(\theta, \varphi) = \frac 1 2 \edth \edth^\ast \psi(\theta, \varphi) = \frac 1 2 \nabla^2 \psi(\theta, \varphi).
  \label{eq:kappa_psi_spher}
\end{equation}
%
The spherical harmonics are eigenfunctions of the Laplacian,
%
\begin{equation}
  \nabla^2 {\rm Y}_{\ell m}(\theta, \varphi) = - \ell (\ell + 1) {\rm Y}_{\ell m}(\theta, \varphi)
    = - \ellbar^2(\ell, 1) {\rm Y}_{\ell m}(\theta, \varphi),
  \label{eq:nabla_Ylm}
\end{equation}
%
The potential power spectrum is then similar to the shear power spectrum
(\ref{eq:C_ell_gamma}) with a different spherical prefactor,
%
\begin{equation}
  C^\kappa_{ij}(\ell) = \frac 1 4 \ellbar^4(\ell, 1) \, C^\psi_{ij}(\ell)
    = \frac{\ell (\ell+1)}{(\ell-1)(\ell+2)} C^\gamma_{ij}(\ell) .
  \label{eq:C_ell_kappa_full}
\end{equation}
%
The convergence power spectrum is thus larger than the shear power spectrum, by
10\% for $\ell=4$, 1\% for $\ell = 14$, and less than 0.1\% for $\ell>45$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Flat-sky approximation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Most previous work has used lensing quantities approximated on a flat sky,
neglecting the sky curvature. This is a valid approach for past and current
survey areas that have extents up to 10 degrees or less. The correlation
functions from the observed shear have been calculated using spherical
coordinates, and the effect on large scales is not negligible \cite{FSHK08}.
Here we examine the effect of sky curvature on the theoretical models.

For a flat sky, the spherical harmonics expansions are approximated by Fourier
transforms. The flat-sky equivalent of eqs.~(\ref{eq:psi_harm_exp}) and
(\ref{eq:psi_harm_exp_inv}) are
%
\begin{align}
  \psi(\vec \vartheta) = & \int \frac{{\rm d}^2 \ell}{(2\pi)^2} \, {\rm e}^{-{\rm i} \vec \ell \vec \vartheta} \hat \psi(\vec \ell);
  \label{eq:psi_fourier}
  \\
  %
  \hat \psi(\vec \ell) = & \int {\rm d}^2 \vartheta \, {\rm e}^{{\rm i} \vec \ell \vec \vartheta} \psi(\vec \vartheta);
  \label{eq:psi_fourier_inv}
\end{align}
%
where $\vec \vartheta = (\theta, \varphi)$ is the vector describing a 2D angle on the sky.
Instead of a harmonics coefficients $\psi_{\ell m}$, the Fourier representation of the potential
$\hat \psi$ now depends on the vector $\vec \ell \in R^2$.

The power spectrum, the flat-sky version of
(\ref{eq:C_ell_psi}) is defined by
%
\begin{equation}
  \left\langle \hat \psi_i^{}(\vec \ell) \hat \psi_j^\ast(\vec \ell^\prime) \right\rangle
    = (2\pi)^2 \delta_{\rm D}(\vec \ell - \vec \ell^\prime) P^\psi_{ij}(\ell).
  \label{eq:P_ell_psi}
\end{equation}

\mk{I can derive a flat-sky shear power spectrum by replacing $\ellbar^2(\ell, 2)$ with $\ell^4$
in (\ref{eq:C_ell_full}), equivalent to replacing the edth operators with Euclidian derivatives.
However, this results in a different expression compared to other references, e.g.~\cite{2008PhRvD..78d3002S},
which is the following equation.}

The flat-sky power spectrum is
%
\begin{align}
  P_{ij}^\gamma(\ell) = & \frac 2 \pi \, \pref^2
                 \int_{0}^{\chi_{\rm lim}} {\rm d} \chi \chi \, \frac{q_i(\chi)}{a(\chi)}
                \int_{0}^{\chi_{\rm lim}} {\rm d} \chi^\prime\, \chi^\prime
                \frac{q_j(\chi^\prime)}{a(\chi^\prime)}
                \nonumber \\
                & \times \int_0^\infty {\rm d} k \, k^2 \, P_{\rm m}(k, \chi, \chi^\prime) \,
                {\rm j}_\ell(k \chi) \, {\rm j}_\ell(k \chi^\prime) .
  \label{eq:P_ell_gamma}
\end{align}
%

\mk{I can get this by placing the prefactor under the integral and
setting $\ell^4 = k^4 \chi^2 {\chi^\prime}^2$. This does not seem to be the proper way.
Other derivations of the shear power spectrum (e.g.\cite{BS01} also assume other approximations
such as small-angle and Limber, but I do not know how to derive this without Limber.}

\section{Second-order Limber approximation for weak lensing}
\label{sec:L2}

\subsection{Spherical case}

We follow \cite{2008PhRvD..78l3506L} who derive the second-order Limber
expansion for general projections from 3D to 2D scalar fields in the spherical,
all-sky case. First, we use the identity of Bessel functions
%
\begin{equation}
  {\rm j}_\ell(x) = \sqrt{\frac{\pi}{2x}} {\rm J}_{\ell + 1/2}(x)
\end{equation}
%
in eq.~(\ref{eq:C_ell_full}). Next, \cite{2008PhRvD..78l3506L} solve
integrals of the form
%
\begin{equation}
  \int_0^\infty {\rm d} \chi f(\chi) {\rm J}_{\ell + 1/2}(k \chi)
  = \int_0^\infty {\rm d} x k^{-1} f(x/k) {\rm J}_{\ell + 1/2}(x)
  \label{eq:int_dchi}
\end{equation}
%
by performing a Taylor expansion of the function $f$ around $x = k \chi = \nu$, where
the Bessel function has its approximate maximum. To separate the $k$- and
$\chi, \chi^\prime$-terms in (\ref{eq:C_ell_full}), we first approximate the
matter power cross-spectrum between two distances as geometric mean of the two
involved distances \cite{2016arXiv161200770K}, and divide out the growth factor
to define a redshift-independent power spectrum $P_{\rm m}(k)$,
%
\begin{equation}
 P_{\rm m}(k, \chi, \chi^\prime) = \sqrt{ P_{\rm m}(k, \chi) P_{\rm m}(k, \chi^\prime) },
    = D_+(\chi) D_+(\chi^\prime) P_{\rm m}(k).
  \label{eq:P_geom_mean}
\end{equation}
%
This is not exact, since some non-linear prescriptions of the power spectrum
depend on redshift other than the growth factor, for example when computing the
non-linear scale $k_{\rm NL}(z)$ for \texttt{halofit}.

With this, eq.~(\ref{eq:C_ell_full}) is written as
%
\begin{align}
  C^\gamma_{ij}(\ell) \approx & \, \ellbar^2(\ell, 2) \, \pref^2
                \int_0^\infty \frac{{\rm d} k}{k^3} \, P_{\rm m}(k) \,
                \int_{0}^\infty \frac{{\rm d} \chi}{\chi^{3/2}} \frac{D_+(\chi)}{a(\chi)} q_i(\chi) {\rm J}_{\ell+1/2}(k \chi)
                \nonumber \\
                 & \times
                \int_{0}^\infty \frac{{\rm d} \chi^\prime}{{\chi^\prime}^{3/2}}
                \frac{D_+(\chi^\prime)}{a(\chi^\prime)} q_j(\chi^\prime) {\rm J}_{\ell+1/2}(k \chi^\prime)
  \label{eq:C_ell_full_Pk}
\end{align}
%
We replaced the upper limits of the distance integral with infinity. \mk{Comment on this.}
Note that this equation has a preactor $\ellbar^2(\ell, 2)$ corresponding to a spin-2 field, in contrast
to \cite{2008PhRvD..78l3506L} who show calculations for a scalar field.

Following \cite{2008PhRvD..78l3506L} we expand to third order
%
\begin{equation}
  \lim_{\varepsilon \rightarrow 0} \int_0^\infty {\rm d} x \, {\rm e}^{-\epsilon (x - \nu)} g(x) {\rm J}_\nu(x) \approx g(\nu) - \frac 1 2 g^{\prime\prime}(\nu)
      - \frac \nu 6 g^{\prime\prime\prime}(\nu) 
\end{equation}
%
with $g(x) = k^{-1} f(\chi)$, $\chi=x/k$, and its derivatives $g^{(n)}(x) =
k^{-1-n} f^{(n)}(\chi)$. In our case the projection kernel is
%
\begin{equation}
  f(\chi) = D_+(\chi) a^{-1}(\chi) \chi^{-3/2} q(\chi).
  \label{eq:f_LA08}
\end{equation}
%
(Add indices $i, j$ to $f$ and $q$ for the tomographic case.)
%
Replacing both distance integrals in (\ref{eq:C_ell_full_Pk}) by their Taylor-expansions around $\nu = k \chi$ and $\nu = k \chi^\prime$,
respectively, yields
%
\begin{align}
  C^\gamma_{ij}(\ell) \approx & \, \ellbar^2(\ell, 2) \, \pref^2
    \int_0^\infty \frac{{\rm d} k}{k^3} \, P_{\rm m}(k) k^{-2}
    \left[ f_i(\chi) - \frac{1}{2 k^2} f_i^{\prime\prime}(\chi)
      - \frac{\nu}{6 k^3} f_i^{\prime\prime\prime}(\nu) + \ldots \right]
    %\nonumber \\
    %& \times
    \left[ f_j(\chi) - \frac{1}{2 k^2} f_j^{\prime\prime}(\chi)
    - \frac{\nu}{6 k^3} f_j^{\prime\prime\prime}(\nu) + \ldots \right]
  \label{eq:C_ell_limber2_dk}
\end{align}
%
Changing the integration to $\chi = \nu/k$ and collecting terms according to their $\nu$-dependence:
%
\begin{align}
  C^\gamma_{ij}(\ell) \approx & \, C^\gamma_{{\rm L1}, ij}(\ell) + C^\gamma_{{\rm L2}, ij}(\ell)
      \nonumber \\
    = & \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2
    \int_0^\infty {\rm d} \chi \, \chi^3 \, P_{\rm m}\left( k \right)
    %\Bigg\{
    \left\{
    f_i(\chi) f_j(\chi)
    %\right.
      %\nonumber \\
    %&
    %\left.
     - \frac 1 {\nu^2} \left[ \frac{\chi^2}{2} \left( f^{}_i f^{\prime\prime}_j + f_i^{\prime\prime} f^{}_j \right)(\chi)
    + \frac{\chi^3}{6} \left( f^{}_i f^{\prime\prime\prime}_j + f^{\prime\prime\prime}_i f^{}_j \right)(\chi)
    \right]
    \right\}
    %\Bigg\}
  \label{eq:C_ell_limber12_dr}
\end{align}
%
The first term corresponds to the well-known first-order Limber approximation
\cite{1953ApJ...117..134L,1992ApJ...388..272K}, which is very widely used in
weak gravitational lensing. We retrieve the (spherical) standard expression by
inserting back the projection kernel (\ref{eq:f_LA08}) and the time-dependent
power spectrum,
%
\begin{align}
  C^\gamma_{{\rm L1}, ij}(\ell) = & \, \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2 \int {\rm d} \chi \frac{ q_i(\chi) q_j(\chi) }{a^2(\chi)}
  P\left(k = \frac{\nu}{\chi}; \chi\right).
  \label{eq:C_ell_limber1}
\end{align}
%
In the Limber approximation, modes between structures at different epochs do
not contribute to the single line-of-sight integration.

The second-order Limber term in (\ref{eq:C_ell_limber12_dr}) has an additional
$\nu^{-2}$-dependence, and is therefore strongly suppressed for large $\ell$.
%
\begin{align}
  C^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2} \, \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2
    \int {\rm d} \chi \, \chi^{2} a^{-2} P_{\rm m}\left(k = \frac\nu\chi; \chi\right)
    %\nonumber \\
    %& \times
    \frac 1 2 D^{-1}_+(\chi) a(\chi) \chi^{3/2} \left[ q^{}_i f^{\prime\prime}_j + f^{\prime\prime}_i q^{}_j
      + \frac{\chi}{3} \left( q^{}_i f^{\prime\prime\prime}_j + f^{\prime\prime\prime}_i q^{}_j
      \right)
    \right](\chi)
  \label{eq:C_ell_limber2_dr} 
\end{align}
%
The derivatives of the filter functions have to be computed numerically in the general case.

\subsection{Flat sky}

The extended flat-sky Limber approximation is readily derived from the
spherical case, by replacing the prefactor $\ellbar^2(\ell, 2)$ with $\ell^4$,
%
\begin{align}
  P^\gamma_{{\rm L1}, ij}(\ell) = & \, \frac{\ell^4}{\nu^4} \, \pref^2 \int {\rm d} \chi \frac{ q_i(\chi) q_j(\chi) }{a^2(\chi)}
  P_{\rm m}\left(k = \frac{\nu}{\chi}; \chi\right);
  \label{eq:P_ell_limber1}
  \\
    P^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2} \, \frac{\ell^4}{\nu^4} \, \pref^2
    \int {\rm d} \chi \, \chi^{2} a^{-2} P_{\rm m}\left(k = \frac\nu\chi; \chi\right)
    %\nonumber \\
    %& \times
    \frac 1 2 D^{-1}_+(\chi) a(\chi) \chi^{3/2} \left[ q^{}_i f^{\prime\prime}_j + f^{\prime\prime}_i q^{}_j  
      + \frac{\chi}{3} \left( q^{}_i f^{\prime\prime\prime}_j + f^{\prime\prime\prime}_i q^{}_j
      \right)
    \right](\chi)
  \label{eq:P_ell_limber2}
\end{align}
%
Different further approximations are commonly made for the prefactor $p(\ell) = \ell^4/\nu^4$ and $\nu(\ell)$.
%
\begin{enumerate}
  \item $p(\ell) = 1$, this corresponds to setting $\nu(\ell) = \ell$, and is the standard Limber approximation.
    Until recently, i.e.~for all pre-2014 CFHTlenS results, this was the approximation of choice.
  \item $p(\ell) = \ell^4/\nu^4(\ell)$ with $\nu(\ell) = \ell + 1/2$. This corresponds to the extended Limber
    approximation; however the following case is typically employed:
  \item $p(\ell) = 1$, but as the argument of the 3D power spectrum $\nu = \ell + 1/2$. This is a hybrid between
    standard and extended Limber approximation, and was used in \cite{KiDS-450,joudaki/etal:2016}. As is shown
    later, this is a much better approximation than case 2.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Comparison of the approximations}
\label{sec:comp}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In Fig.~\ref{fig:Cl_cases} we plot the full shear power spectrum and some of
the approximations. For $\ell > 100$ all power spectra coincide to better than one percent.
The extended first-order Limber approximation shows a better convergence to the true
power spectrum, the error decreases with $\ell^{-2}$. Including the spherical prefactor
decreases the difference by a factor of a few for $\ell < 5$.
Going to second-order yields percent accuracy down to $\ell = 4$.

\begin{figure}

  \begin{center}
    \resizebox{1.0\hsize}{!}{
      \includegraphics{P_kappa_limber_comp}
      \includegraphics{P_kappa_limber_delta}
    }
  \end{center}

  \caption{Shear power spectrum for different approximation. Limber to first order: for flat-sky (L1Fl),
        extended ($\ell + 1/2$) for flat sky (ExtL1Fl), and extended in the spherical expansion (ExtL1Sph);
        Second-order extended Limber spherical expansion (ExtL2Sph); full (exact) spherical projection (FullSph).
        The left (right) panels show the total (relative difference) power spectrum.
        See Table \ref{tab:cases} for more details on the different approximations. \mk{Right panel needs to be updated!
        ExtL1Fl curve is actually ExtL1FlHyb.}
      }

  \label{fig:Cl_cases}

\end{figure}

% nicaea            Kil+17      'Comment paper' Plot color    Kit+16                Plot color    my comment
% limber            L1Fl        Kst             black         Limber+Tl=1+Flat-sky  blue
% limber_la08       ExtL1Fl     ELF             blue
% limber_la08_hyb   ExtL1FlHyb  ESt             magenta                                           prefactor~1 despite nu=ell+1/2
% limber_la08_sph   ExtL1Sph    ELS             cyan
% limber2_la08      ExtL2Fl
% limber2_la08_hyb  ExtL2Fl
% limber2_la08_sph  ExtL2Sph
% full              Full

\renewcommand{\baselinestretch}{1.3}
\begin{table}[ht!]

  \label{tab:cases}

  \caption{Shear power spectrum approximations compared in this paper. \mk{The last column will be removed in the
        final version.}}

  \begin{tabular}{|l|l|c|c|c|c}
  \hline
  Case & ID & eq.~ & $p(\ell)$ & $\nu(\ell)$ & Label [Comment paper] \\ \hline
  % 
  $1^{\rm st}$-order standard Limber, flat sky & L1Fl & (\ref{eq:P_ell_limber1}) + (i)
    & $1$ & $\ell$ & Kst \\ \hline
  %
  $1^{\rm st}$-order extended Limber, flat sky & ExtL1Fl & (\ref{eq:P_ell_limber1}) + (ii)
    & $\ell^4/(\ell+1/2)^4$ & $\ell + 1/2$ & ELF \\ \hline
  %
  $1^{\rm st}$-order extended Limber, hybrid, flat sky & ExtL1FlHyb & (\ref{eq:P_ell_limber1}) + (iii)
    & $1$ & $\ell + 1/2$ & ESt \\ \hline
  %
  $1^{\rm st}$-order extended Limber, spherical & ExtL1Sph & (\ref{eq:C_ell_limber1})
    & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ & ELS \\ \hline
  %
  $2^{\rm st}$-order extended Limber, flat sky & Ext2FlHyb & (\ref{eq:P_ell_limber2}) + (iii)
    & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ & - \\ \hline
  %
  $2^{\rm st}$-order extended Limber, spherical & Ext2Sph & (\ref{eq:C_ell_limber1})+(\ref{eq:C_ell_limber2_dr})
    & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ & - \\ \hline
  %
  Full spherical & FullSph & (\ref{eq:C_ell_full}) &
      $\ellbar^2(\ell, 2)$ & - & - \\ \hline
  %
  \end{tabular}

\end{table}
\renewcommand{\baselinestretch}{1}

In Fig.~\ref{fig:xi_pm_K16} we show the correlation functions using the different cases
for the shear power spectrum. \mk{Replace this figure, don't show CFHTLenS data?}

\begin{figure}

  \begin{center}
    \resizebox{1.0\hsize}{!}{
      \includegraphics{xi_p_comp}
      \includegraphics{xi_m_comp}
    }
  \end{center}

  %\caption{Shear correlation funtions $\xi_+$ (\emph{left panel}) and $\xi_-$ (\emph{right}) in the
    %%represenation as in \cite{2016arXiv161104954K}. See Table \ref{tab:cases} for the cases of different
    %approximations and their symbols. The  points with error bars are the data from
    %\cite{CFHTLenS-2pt-notomo}; the theotical predictions correspond to the best-fit parameters with
    %$\Omega_{\rm m} = 0.279$ and $\sigma_8 = 0.79$, except the red dashed curve with adapts a Planck-best fit
    %normalisation $\sigma_8 = 0.83$.}

  \label{fig:xi_pm_K16}

\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Application to CFHTLenS data}
\label{sec:cfhtlens}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table}

  \begin{tabular}{lc} \hline
  ID       & $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$ \\ \hline
  L1Fl     & $0.769 \pm 0.031$ \\
  ExtL2Sph & $0.769 \pm 0.030$ \\ \hline
  \end{tabular}

\end{table}

\section*{Acknowledgments}

The authors thank Tommaso Giannantonio for very helpful discussions.

\bibliographystyle{mn2e}
\bibliography{astro}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{appendix}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Derivation of the weak-lensing power spectra}
\label{sec:derivations_C}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The following derivations are detailed e.g.~in \cite{2000PhRvD..62d3007H} and
\cite{2005PhRvD..72b3516C}.

\subsection{Spherical case}

\subsubsection{Lensing potential power spectrum}

To obtain the power spectrum of the lensing potential for a flat Universe, 
we insert the lensing projection (\ref{eq:psi}) for $K=0$ into the
inverse harmonics expansion (\ref{eq:psi_harm_exp_inv}) and write the 3D potential
as its Fourier transform (\ref{eq:hatPhi_inv}) to get
%
\begin{equation}
  \psi_{\ell m} = \frac 2 {c^2} \int {\rm d} \Omega {\rm Y}^\ast_{\ell m}(\theta, \varphi)
    \int_0^{\chi_{\rm lim}} \frac{{\rm d}\chi}{\chi} q(\chi) \int \frac{{\rm d}^3 k}{(2\pi)^3} \hat \Phi(\vec k; \chi) {\rm e}^{-{\rm i} \vec k \vec r}.
\end{equation}
%
The 3D position vector $\vec r$ is a 3D position vector with polar coordinate
$r = \chi$ and polar angles $(\theta, \varphi)$. Similarly we denote with
$\theta_k, \varphi_k$ the polar angles of the 3D Fourier vector $\vec k$. We
insert the expansion of a plane wave into spherical harmonics,
%
% BBRV12 (41)
%
\begin{equation}
  {\rm e}^{{\rm i} \vec k \vec r} = 4 \pi \sum_{\ell m} {\rm i}^\ell {\rm j}_\ell(k \chi)
    {\rm Y}_{\ell m}(\theta, \varphi) {\rm Y}_{\ell m}(\theta_k, \varphi_k),
  \label{eq:wave_exp}
\end{equation}
%
\mk{Comment on minus sign in exponential.}

Making use of the orthogonality of the spherical harmonics
%
% Rijt (6.15), Castro (B2).
%
\begin{equation}
  \int {\rm d} \Omega {\rm Y}^{}_{\ell m}(\theta, \varphi) {\rm Y}^\ast_{\ell^\prime m^\prime}(\theta, \varphi) = \delta_{\ell \ell^\prime} \delta_{m m^\prime},
  \label{eq:Yellm_ortho}
\end{equation}
%
the expression for $\psi_{\ell m}$ simplifies to
%
\begin{equation}
  \psi_{\ell m} = \frac {{\rm i}^\ell}{c^2 \pi^2} \int_0^{\chi_{\rm lim}} \frac{{\rm d}\chi}{\chi} q(\chi) \int {\rm d}^3 k \,
    \hat \Phi(\vec k; \chi) {\rm j}_\ell(k \chi) {\rm Y}_{\ell m}(\theta_k, \varphi_k).
  \label{eq:psi_ellm}
\end{equation}
%
We take the absolute square and use the definition of the 3D potential power spectrum,
%
\begin{align}
  \left\langle \Phi(\vec k; \chi) \Phi^\ast(\vec k^\prime; \chi^\prime) \right\rangle
    = & (2\pi)^3 \delta_{\rm D}(\vec k - \vec k^\prime) P_\Phi(k; \chi, \chi^\prime).
    %\nonumber \\
    %= & (2\pi)^3 \delta_{\rm D}(\vec k - \vec k^\prime) \pref^2 k^{-4} a^{-1}(\chi) a^{-1}(\chi^\prime)
      %P_{\rm m}(k; \chi, \chi^\prime).
  \label{eq:p_phi}
\end{align}
%
$P_{\rm m}$ is the 3D matter power cross-spectrum at line-of-sight comoving
Fourier mode $k$ and comoving distances $\chi$ and $\chi^\prime$. We denote
complex conjugation with superscript $^\ast$.
\mk{Peter's comment: What does the correlation between two epochs actually mean if they
are not on the backward light cone?}

The delta-function resolves one 3D Fourier
integral. We split the second integration into radial and spherical
coordinates, ${\rm d}^3 k = {\rm d} k k^2 {\rm d} \Omega_k$ and use once again
the orthogonality of the spherical harmonics to resolve the spherical integral. 
This leads to the potential power spectrum (\ref{eq:C_ell_phi_Pm}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion and comparison to previously published work}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Kitching et al.~2016}

Eq.~\ref{eq:C_ell_full} is analogous to (7) and (8) from
\cite{2016arXiv161104954K} for a flat Universe and in the case of perfect
photometric redshifts, $p(z | z_{\rm p}) = \delta_{\rm D}(z - z_{\rm p})$, and
for a bin function that selects the redshift bin $i$, $W^{\rm SR}(z, z_{\rm p})
= 1_{z \in i-\mbox{th bin}}$. In \cite{2016arXiv161104954K} eq.~(7) is however the
factor $2/\pi$ missing.

In App.~A they derive the Limber approximation starting from the full spherical
projection. Note that their filter function $q$ defined in (31) has an
errornous factor of comoving distance $r$, and an additional factor $\pi/2$
appears.

Eq.~19 of \cite{2016arXiv161104954K} corresponds to our
(\ref{eq:P_ell_gamma}). \mk{Has to be checked.}

We can not reproduce the amplitude of the differences between the cases, neither for
the power spectrum nor for the shear correlation function (see Fig.~\ref{fig:xi_pm_K16}).

\paragraph{Bernardeau, Bonvin, Van de Rijt, Vernizzi (2012); van de Rijt (2012)}

Eq.~(44) of \cite{2012PhRvD..86b3001B} is the non-tomographic $C(\ell)$ in
terms of the time-independent potential power spectrum $T^2(k) P(k)$, where $T$
is the transfer function; the growth factor $D$ is contained in their window
function $W$ (43) as growth-suppression factor $g(\chi) = D(\chi)/a(\chi)$
(defined after eq.~{24}). For a single source redshift, we find the identity
$W(\chi)$ = $q(\chi)\chi^{-1} D(\chi) a^{-1}(\chi)$.
\cite{2012PhRvD..86b3001B} is consistent with our
(\ref{eq:C_ell_full}), if we interpret the
scale factors at distances $\chi$ and $\chi^\prime$, respectively.

The PhD thesis of Van de Rijt \cite{vande2012} presents an explicit calculation
of the second-order Limber approximation for a fixed source redshift. They
carry out the derivatives of the kernels $f$ under the assumption of a constant
growth-suppression factor $D_+(a)/a$. We show the consistency between their
result (eq.~7.19) and our (\ref{eq:C_ell_limber2_dr}), as follows.

We write (\ref{eq:C_ell_limber2_dr}) without tomography, and insert again the
time-independent power spectrum (\ref{eq:P_geom_mean}),
%
\begin{align}
  C^\gamma_{{\rm L2}}(\ell) = & - \frac 1 {\nu^2} \, \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2
    \int {\rm d} \chi \, \chi^{2} P_{\rm m}\left(k = \frac\nu\chi\right)
    \nonumber \\
    & \times D_+(\chi) a^{-1}(\chi) \chi^{3/2} q(\chi) \left[ f^{\prime\prime} 
      + \frac{\chi}{3} f^{\prime\prime\prime} 
    \right](\chi)
  \label{eq:C_ell_limber2_dr_notomo}
\end{align}
%
For a fixed source comoving distance $\chi_{\rm S}$ the lensing efficiency is
$q(\chi) = (\chi_{\rm S} - \chi) \chi_{\rm S}^{-1}$. Assuming that
$D_+(\chi)/a(\chi) \approx g = \mbox{const}$, we get for the derivative terms,
with $f(\chi) = g \chi_{\rm S}^{-1} (\chi_{\rm S} - \chi) \chi^{-3/2}$,
%
\begin{equation}
  f^{\prime\prime}(\chi) + \frac{\chi}{3} f^{\prime\prime\prime}(\chi)
    = - \frac 1 8 \chi^{-5/2} \left( \frac 5 \chi
          + \frac 1 {\chi_{\rm S}} \right) \frac{D_+(\chi)}{a(\chi)}.
\end{equation}
%
Therefore,
%
\begin{align}
  C^\gamma_{{\rm L2}}(\ell) = \frac 1 {\nu^2} \, \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2
    \int {\rm d} \chi \, \chi \, P_{\rm m}\left(k = \frac\nu\chi\right)
    \frac{q(\chi)}{8} \left( \frac 5 \chi + \frac 1 {\chi_{\rm S}} \right)
      \left(\frac{D_+(\chi)}{a(\chi)}\right)^2 
\end{align}
%
We now replace the matter with the potential power spectrum, ${\cal A}^2 P_{\rm m}(k) = k^{4} a^2 P_\Phi(k)$, and pull into the integral $\nu^{-4} = \chi^{-4} k^{-4}$. This yields
%
\begin{align}
  C^\gamma_{{\rm L2}}(\ell) = \frac 1 {\nu^2} \, \ellbar^2(\ell, 2)
    \int \frac{{\rm d} \chi}{\chi^2} \, P_\Phi\left(k = \frac\nu\chi\right)
    a^2(\chi) \frac{1}{8} \frac{\chi_{\rm S} - \chi}{\chi \chi_{\rm S}}
    \left( \frac 5 \chi + \frac 1 {\chi_{\rm S}} \right)
      \left(\frac{D_+(\chi)}{a(\chi)}\right)^2 .
\end{align}
%
Note the additional factor $a^2(\chi)$. This difference is accounted for by the
factor $a^{-1}$ in the propagation of primordial potential perturbations to
late times, see eq.~(6.22) in \cite{vande2012}, where the transition is done
using $g(a)$ instead of $D(a)$. \mk{Check this further.}

In Fig.~\ref{fig:L1L2E_Rijt} we reproduce Fig.~7.3 from \cite{vande2012} using
a similar set up (flat $\Lambda$ Universe with $\Omega_{\rm m} = 0.3, h=0.65,
\Omega_{\rm b} = 0.0461, \sigma_8 = 0.8, n_{\rm s} = 0.96$. All source galaxies
are at redshift $z_{\rm S} = 1$. The non-linear 3D matter power spectrum from
\cite{2012ApJ...761..152T} is used. The ratio of the first-and second- Limber approximated
power spectra to the full
projection shows excellent agreement at the sub-percent level.

\begin{figure}

  \begin{center}
    \resizebox{0.9\hsize}{!}{
      \includegraphics{P_kappa_limber_delta_Rijt}
    }
  \end{center}

    \caption{Differences in percentage of spherical shear power spectra terms
    as function of wave mode $\ell$, see Table \ref{tab:cases}.
    The blue and red curves corresponds to the ones shown in Fig.~7.3 of \citet{vande2012}.
    }

    \label{fig:L1L2E_Rijt}

\end{figure}

\paragraph{LoVerde \& Afshordi (2009)}

This paper introduces the extended Limber approximation to second order that we
apply in this work. Although they present the specific case of 2D galaxy
clustering, their calculations are general enough to apply to weak lensing.

Their eq.~(5) is a general spherical power spectrum of a scalar field,
projected from 3D to 2D via (4). Comparing their expressions with the
weak-lensing potential (\ref{eq:psi}), we can set $F_A(\chi) = F_B(\chi) = 2
c^{-2} D_+(\chi) q(\chi) \chi^{-1}$. With that, their eq.~(5) is identical to
our (\ref{eq:C_ell_phi_Pphi}).

The second-order Limber approximation in \cite{2008PhRvD..78l3506L} is presented in
eq.~(12). This is consistent with our first-order (\ref{eq:C_ell_limber1}) and
second-order (\ref{eq:C_ell_limber2_dr}) Limber approximation, when accounting for the difference between
lensing potential and shear 2D power spectrum, and 3D potential and matter power spectrum.

\paragraph{Schmidt (2009)}

In eq.~(9) \cite{2008PhRvD..78d3002S} write the lensing power spectrum in the
flat-sky limit. The Poisson factor $D_\phi$ is defined in their eq.~(5), see
also our eq.~\ref{eq:poisson}, and $D_{\rm m}$ is the growth factor. The filter
function $W_\kappa$ (eq.~10) can be written as
%
\begin{align}
  W_\kappa(z) = & \frac 1 {H(z)} \int_z^\infty {\rm d} z_{\rm s} W_{\rm L}(z_{\rm s}, z) W_{\rm g}(z)
              =  \frac 1 {H(z)} \chi \int_\chi^\infty {\rm d} \chi^\prime \frac{\chi^\prime - \chi}{\chi^\prime}
                n(\chi)
              \nonumber \\
              & \equiv \frac 1 {H(z)} \chi q(\chi),
\end{align}
%
using ${\rm d} z W_{\rm g}(z) = {\rm d} \chi n(\chi)$.
To write the redshift integrals (9) in \cite{2008PhRvD..78d3002S} over 
comoving distance, we make the variable transformation
%
\begin{equation}
  {\rm d} \chi = \frac{c {\rm d} z}{H(z)} .
\end{equation}
%
We recover our (\ref{eq:P_ell_gamma}).

\paragraph{Giannantonio et al. (2012)}

In eqs.~(25) and (26) \cite{2012MNRAS.422.2854G} write the flat-sky lensing
power spectrum. Their window function $W^{\varepsilon_i}$ defined in (25) for a
flat Universe equals $\pref \times q(\chi) / a(\chi)$, since ${\rm d} z {\rm d}
N(z)/{\rm d} z = {\rm d} \chi n(\chi)$; however there is a factor $r_K[r(z)]$
missing in the window function, which translates into a missing $r_K[r]
r_K[r^\prime]$ in the integral\footnote{Confirmed by T.~G., priv.~comm.}. This
also leads to an errorous $r_K^{-2}(r)$ in the Limber equation (27). With these
factors accounted for, we reproduce the expressions of \cite{2012MNRAS.422.2854G}.

\label{lastpage}

\end{appendix}

\end{document}

### 2017-02-02 limber2.tex
Reshuffle - moved old files from the comment paper to a new directory

@@
       Martin Kilbinger$^{1,2}$\thanks{E-mail: martin.kilbinger@cea.fr},
-      Catherine Heymans,
-      Peter Schneider,
-      Shahab Joudaki,
-      Marika Asgari,
+      %Catherine Heymans,
+      %Peter Schneider,
+      %Shahab Joudaki,
+      %Marika Asgari,   % note that we'll worry about order at the end - Marika and Shahab put a lot of work into the comment paper, so we might just want to go alpha
       and other members of CFHTLenS and KiDS
@@
 
-\input abbr-journals
+%\input abbr-journals
 
@@
     \resizebox{1.0\hsize}{!}{
-      \includegraphics{P_kappa_limber_comp}
-      \includegraphics{P_kappa_limber_delta}
+      \includegraphics{figures/P_kappa_limber_comp}
+      \includegraphics{figures/P_kappa_limber_delta}
     }
@@
     \resizebox{1.0\hsize}{!}{
-      \includegraphics{xi_p_comp}
-      \includegraphics{xi_m_comp}
+      \includegraphics{figures/xi_p_comp}
+      \includegraphics{figures/xi_m_comp}
     }
@@
     \resizebox{0.9\hsize}{!}{
-      \includegraphics{P_kappa_limber_delta_Rijt}
+      \includegraphics{figures/P_kappa_limber_delta_Rijt}
     }

### 2017-02-02 original_comment_paper/conclusion.tex
Reshuffle - moved old files from the comment paper to a new directory

--- 2016-12-09 conclusion.tex
@@
 \section{Acknowledgements}
-We thank Sarah Bridle, Ami Choi, Tommaso Giannantonio, Donnacha Kirk, Lance Miller, Benjamin Joachimi and Adam Amara for useful discussions during the collection of these comments.
+We thank Sarah Bridle, Ami Choi, Tommaso Giannantonio, Donnacha Kirk, Lance Miller, Benjamin Joachimi, Chris Blake and Adam Amara for useful discussions during the collection of these comments.

### 2017-02-03 limber2.tex
updated figure 2
MK: Update figure

@@
 
-%\input abbr-journals
+\input abbr-journals
 
@@
 In Fig.~\ref{fig:Cl_cases} we plot the full shear power spectrum and some of
-the approximations. For $\ell > 100$ all power spectra coincide to better than one percent.
-The extended first-order Limber approximation shows a better convergence to the true
-power spectrum, the error decreases with $\ell^{-2}$. Including the spherical prefactor
-decreases the difference by a factor of a few for $\ell < 5$.
-Going to second-order yields percent accuracy down to $\ell = 4$.
+the approximations. For $\ell > 100$ all power spectra coincide to better than
+one percent. The standard first-order Limber approximation is better than 10\%
+but for the lowest $\ell$, but converges slowly to the true projection to
+higher $\ell$. For the extended Limber approximations, despite slightly worse
+for $\ell < 10$ in the hybrid cases, the errors with respect to the true power spectrum
+decrease much faster, with $\ell^{-2}$.
+Including the spherical prefactor decreases the difference by a
+factor of a few for $\ell < 5$. Going to second-order yields percent accuracy
+down to $\ell = 4$.
+
+The flat extended Limber approximations (ExtL1Fl and ExtL2Fl) perform relatively poorly, and
+reach 10\% precision only at $\ell > 100$.
 
@@
 
-  \caption{Shear power spectrum for different approximation. Limber to first order: for flat-sky (L1Fl),
-        extended ($\ell + 1/2$) for flat sky (ExtL1Fl), and extended in the spherical expansion (ExtL1Sph);
-        Second-order extended Limber spherical expansion (ExtL2Sph); full (exact) spherical projection (FullSph).
-        The left (right) panels show the total (relative difference) power spectrum.
-        See Table \ref{tab:cases} for more details on the different approximations. \mk{Right panel needs to be updated!
-        ExtL1Fl curve is actually ExtL1FlHyb.}
+  \caption{Shear power spectrum for different approximation. Limber to first order: standard with flat-sky (L1Fl),
+        extended for flat sky (ExtL1Fl), extended hybrid for flat sky (ExtL1FlHyb),
+        and extended in the spherical expansion (ExtL1Sph);
+        second-order Limber approximations: extended flat sky (ExtL2Fl), extended hybrid flat sky (ExtL2FlHyb),
+        and extended spherical expansion (ExtL2Sph); full (exact) spherical projection (FullSph).
+        The left panels show the total power spectrum.
+        See Table \ref{tab:cases} for more details on the different approximations.
         }
@@
     }
+
+    \resizebox{1.0\hsize}{!}{
+      \includegraphics{figures/xi_p_delta}
+      \includegraphics{figures/xi_m_delta}
+    }
   \end{center}
 
-  %\caption{Shear correlation funtions $\xi_+$ (\emph{left panel}) and $\xi_-$ (\emph{right}) in the
-    %%represenation as in \cite{2016arXiv161104954K}. See Table \ref{tab:cases} for the cases of different
-    %approximations and their symbols. The  points with error bars are the data from
+  \caption{Shear correlation funtions $\xi_+$ (\emph{left panels}) and $\xi_-$ (\emph{right}).
+    The lower row shows the relative differences to the case Ext2Sph,  see Table \ref{tab:cases} for the different
+    approximations and their symbols.
     %\cite{CFHTLenS-2pt-notomo}; the theotical predictions correspond to the best-fit parameters with
     %$\Omega_{\rm m} = 0.279$ and $\sigma_8 = 0.79$, except the red dashed curve with adapts a Planck-best fit
-    %normalisation $\sigma_8 = 0.83$.}
+    %normalisation $\sigma_8 = 0.83$.
+  }
 

### 2017-02-03 limber2.tex
MK: Included Patrick's comments

@@
 %
-corresponding to a population of lensed galaxies with source redshift
+corresponding to a population of lensed galaxies with normalised source redshift
 distribution $n(z) {\rm d}z = n(\chi) {\rm d} \chi$. Here, ${\rm c}$ is the
@@
 spectrum of the lensing potential between two redshift bins $i$ and $j$,
-$C_{ij}^\psi$ is then defined by
+$C_{ij}^\psi$ is then defined by \cite{pee80}
 %
@@
 \end{equation}
+%
+The first line expresses $C_{ij}^\psi$ in terms of the 3D potential power spectrum $P_\Phi$, defined as
+%
+\begin{align}
+  \left\langle \hat \Phi(\vec k; \chi) \hat \Phi^\ast(\vec k^\prime; \chi^\prime) \right\rangle
+    = & (2\pi)^3 \delta_{\rm D}(\vec k - \vec k^\prime) P_\Phi(k; \chi, \chi^\prime).
+    %\nonumber \\
+    %= & (2\pi)^3 \delta_{\rm D}(\vec k - \vec k^\prime) \pref^2 k^{-4} a^{-1}(\chi) a^{-1}(\chi^\prime)
+      %P_{\rm m}(k; \chi, \chi^\prime).
+  \label{eq:p_phi}
+\end{align}
+%
+The second line uses the 3D matter density power spectrum $P_{\rm m}$, which is defined analogously as
+%
+\begin{align}
+  \left\langle \hat \delta(\vec k; \chi) \hat \delta^\ast(\vec k^\prime; \chi^\prime) \right\rangle
+    = & (2\pi)^3 \delta_{\rm D}(\vec k - \vec k^\prime) P_{\rm m}(k; \chi, \chi^\prime),
+  \label{eq:p_m}
+\end{align}
+%
+and is
+related to $P_\Phi$ via the absolute square of the Poisson equation (\ref{eq:poisson}).
 
@@
 %
+The spherical prefactor for the full projection power spectrum is $p(\ell) =
+\ellbar^2(\ell, 2)$, which will be modified under flat-sky and Limber
+approximations below.
 
@@
 %
-The potential power spectrum is then similar to the shear power spectrum
+The convergence power spectrum is then similar to the shear power spectrum
 (\ref{eq:C_ell_gamma}) with a different spherical prefactor,
@@
 \begin{equation}
- P_{\rm m}(k, \chi, \chi^\prime) = \sqrt{ P_{\rm m}(k, \chi) P_{\rm m}(k, \chi^\prime) },
-    = D_+(\chi) D_+(\chi^\prime) P_{\rm m}(k).
+ P_{\rm m}(k, \chi, \chi^\prime) = \sqrt{ P_{\rm m}(k, \chi) P_{\rm m}(k, \chi^\prime) }
+    =: D_+(\chi) D_+(\chi^\prime) P_{\rm m}(k).
   \label{eq:P_geom_mean}
@@
 \begin{equation}
-  \lim_{\varepsilon \rightarrow 0} \int_0^\infty {\rm d} x \, {\rm e}^{-\epsilon (x - \nu)} g(x) {\rm J}_\nu(x) \approx g(\nu) - \frac 1 2 g^{\prime\prime}(\nu)
-      - \frac \nu 6 g^{\prime\prime\prime}(\nu) 
+  \lim_{\varepsilon \rightarrow 0} \int_0^\infty {\rm d} x \, {\rm e}^{-\epsilon (x - \nu)} g(x) {\rm J}_\nu(x)
+  %\approx g(\nu) - \frac 1 2 g^{\prime\prime}(\nu) - \frac \nu 6 g^{\prime\prime\prime}(\nu) 
+  \approx g(\nu) - \frac 1 2 \left.\frac{{\rm d}^2 g}{{\rm d} x^2}\right|_{x=\nu}
+                 - \frac \nu 6 \left.\frac{{\rm d}^3 g}{{\rm d} x^3}\right|_(x=\nu) ,
 \end{equation}
@@
     \left[ f_i(\chi) - \frac{1}{2 k^2} f_i^{\prime\prime}(\chi)
-      - \frac{\nu}{6 k^3} f_i^{\prime\prime\prime}(\nu) + \ldots \right]
+      - \frac{\nu}{6 k^3} f_i^{\prime\prime\prime}(\chi) + \ldots \right]
     %\nonumber \\
@@
     \left[ f_j(\chi) - \frac{1}{2 k^2} f_j^{\prime\prime}(\chi)
-    - \frac{\nu}{6 k^3} f_j^{\prime\prime\prime}(\nu) + \ldots \right]
+    - \frac{\nu}{6 k^3} f_j^{\prime\prime\prime}(\chi) + \ldots \right]
   \label{eq:C_ell_limber2_dk}
@@
   C^\gamma_{{\rm L1}, ij}(\ell) = & \, \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2 \int {\rm d} \chi \frac{ q_i(\chi) q_j(\chi) }{a^2(\chi)}
-  P\left(k = \frac{\nu}{\chi}; \chi\right).
+  P_{\rm m}\left(k = \frac{\nu}{\chi}; \chi\right).
   \label{eq:C_ell_limber1}
@@
 In Fig.~\ref{fig:Cl_cases} we plot the full shear power spectrum and some of
-the approximations. For $\ell > 100$ all power spectra coincide to better than
-one percent. The standard first-order Limber approximation is better than 10\%
-but for the lowest $\ell$, but converges slowly to the true projection to
-higher $\ell$. For the extended Limber approximations, despite slightly worse
-for $\ell < 10$ in the hybrid cases, the errors with respect to the true power spectrum
-decrease much faster, with $\ell^{-2}$.
-Including the spherical prefactor decreases the difference by a
-factor of a few for $\ell < 5$. Going to second-order yields percent accuracy
-down to $\ell = 4$.
+the approximations. The redshift distribution corresponds to CFHTLenS
+\cite{CFHTLenS-2pt-notomo}. \mk{NL power spectrum parameters.}
+For $\ell > 100$ all power spectra coincide to
+better than one percent. The standard first-order Limber approximation is
+better than 10\% but for the lowest $\ell$, but converges slowly to the true
+projection to higher $\ell$. For the extended Limber approximations, despite
+slightly worse for $\ell < 10$ in the hybrid cases, the errors with respect to
+the true power spectrum decrease much faster, with $\ell^{-2}$. Including the
+spherical prefactor decreases the difference by a factor of a few for $\ell <
+5$. Going to second-order yields percent accuracy down to $\ell = 4$.
 
@@
 
-  \caption{Shear power spectrum approximations compared in this paper. \mk{The last column will be removed in the
+  \caption{Shear power spectrum approximations compared in this paper. 'ID' is the abbrevation used in the plots.
+    The third column shows the power-spectrum prefactor $p(\ell)$.  \mk{The last column will be removed in the
         final version.}}
@@
   \hline
-  Case & ID & eq.~ & $p(\ell)$ & $\nu(\ell)$ & Label [Comment paper] \\ \hline
+  Case & ID & eq.~ & prefactor & $\nu(\ell)$ & Label [Comment paper] \\ \hline
   % 
@@
 In Fig.~\ref{fig:xi_pm_K16} we show the correlation functions using the different cases
-for the shear power spectrum. \mk{Replace this figure, don't show CFHTLenS data?}
+for the shear power spectrum. The redshift distribution and cosmological model are the same 
+as in Fig.~\ref{fig:Cl_cases}.
 
@@
     approximations and their symbols.
-    %\cite{CFHTLenS-2pt-notomo}; the theotical predictions correspond to the best-fit parameters with
+    \mk{Probably remove ExtL1Fl, ExtL2Fl, we already showed for $P_\kappa$ that they are worse than standard
+    Limber.}
+    %\cite{CFHTLenS-2pt-notomo}; the theoretical predictions correspond to the best-fit parameters with
     %$\Omega_{\rm m} = 0.279$ and $\sigma_8 = 0.79$, except the red dashed curve with adapts a Planck-best fit
@@
 \begin{equation}
-  {\rm e}^{{\rm i} \vec k \vec r} = 4 \pi \sum_{\ell m} {\rm i}^\ell {\rm j}_\ell(k \chi)
-    {\rm Y}_{\ell m}(\theta, \varphi) {\rm Y}_{\ell m}(\theta_k, \varphi_k),
+  {\rm e}^{{\rm i} \vec k \vec r} = 4 \pi \sum_{\ell=0}^{\infty} \sum_{m=-\ell}^{\ell}
+    {\rm i}^\ell \, {\rm j}_\ell(k \chi)
+    {\rm Y}_{\ell m}(\theta, \varphi) {\rm Y}_{\ell m}(\theta_k, \varphi_k) .
   \label{eq:wave_exp}
@@
 %
-\mk{Comment on minus sign in exponential.}
 
@@
 %
-We take the absolute square and use the definition of the 3D potential power spectrum,
-%
-\begin{align}
-  \left\langle \Phi(\vec k; \chi) \Phi^\ast(\vec k^\prime; \chi^\prime) \right\rangle
-    = & (2\pi)^3 \delta_{\rm D}(\vec k - \vec k^\prime) P_\Phi(k; \chi, \chi^\prime).
-    %\nonumber \\
-    %= & (2\pi)^3 \delta_{\rm D}(\vec k - \vec k^\prime) \pref^2 k^{-4} a^{-1}(\chi) a^{-1}(\chi^\prime)
-      %P_{\rm m}(k; \chi, \chi^\prime).
-  \label{eq:p_phi}
-\end{align}
-%
+We take the absolute square and use the definition of the 3D potential power spectrum (\ref{eq:p_phi}),
+to arrive at expression (\ref{eq:C_ell_phi_Pphi}).
+
 $P_{\rm m}$ is the 3D matter power cross-spectrum at line-of-sight comoving

### 2017-02-05 limber2.tex
added some CFHTLenS results

@@
 
+We run various projection modes on CFHTLenS single-redshift bin data
+\cite{CFHTLenS-2pt-notomo}. The setting is exactly the same as for the 2013
+results. Note that since then many improvements have been obtained, those
+results do not reflect the most up-to-date cosmological constraints. This is
+sufficient however for our purpose to show the effect of projection
+approximations for weak-lensing surveys. Thos improvement have been made on the
+theoretical modelling side (revised non-linear power spectrum
+\cite{2012ApJ...761..152T}, baryonic modifications of the total power spectrum
+\cite{2015MNRAS.454.1958M}), and the data processing (photometric redshifts
+\cite{2016MNRAS.463.3737C,joudaki/etal:2016}, shear calibration
+\cite{KiDS-450}, Fenech Compti). The state-of-the-art cosmological constraints
+for CFHTLenS including most of those updates are presented in
+\cite{joudaki/etal:2016}.
+
+The mean and 68\% credible interval for $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$
+published in \cite{CFHTLenS-2pt-notomo} were $0.787 \pm 0.032$. We make sure
+that changes introduced to \texttt{CosmoPMC} over the last four years do not
+change this result, we re-run the same setting using the newest version of
+\texttt{CosmoPMC} and obtain $0.787^{+0.031}_{-0.033}$.
+
+Table \ref{tab:CFHTLenS_Sigma8} lists the mean and 68\% credible interval for
+$\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$ for various approximations to the lensing
+power spectrum projections.
+
+As an example of significant effects that need to be accounted for, using the
+revised non-linear power spectrum of \cite{2012ApJ...761..152T} instead of
+\cite{2003MNRAS.341.1311S} yields $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6} =
+0.768^{+0.029}_{-0.031}$ for L1Fl, which is a lower corresponding to 60\% of
+the error bar.
+
 \begin{table}
+
+  \label{tab:CFHTLenS_Sigma8}
+
+  \caption{Mean and 68\% credible interval for 
+  $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$ for various approximations to the lensing
+  power spectrum projections.}
 
@@
   ID       & $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$ \\ \hline
-  L1Fl     & $0.769 \pm 0.031$ \\
-  ExtL2Sph & $0.769 \pm 0.030$ \\ \hline
+  L1Fl     & $0.787^{+0.031}_{-0.033}$ \\
+  ExtL2Sph & $0.788 \pm 0.032$ \\ \hline
   \end{tabular}

### 2017-02-06 limber2.tex
CH: Small changes to make it compile for me Hopefully it also compiles still for you!
limber2.tex:
CH added to the abstract and introduction

@@
-\documentclass[useAMS,usenatbib]{mn2e} %
+\documentclass[fleqn,usenatbib]{mnras} %
 \pdfoutput=1
@@
 
-\title[]
-{Precision calculations of the cosmic shear power spectrum projection}
+\title[Precision calculations for cosmic shear]{Precision calculations for cosmic shear}  %??
+%{Precision calculations of the cosmic shear power spectrum projection}
 
@@
 convergence. We discuss various approximations, such as flat-sky, first- and
-second-order Limber equations for the projection. We show that the spherical
-second-order Limber approximation agrees with the full projection at the
-percent level for $\ell > 3$. for current surveys. The real-space shear
-correlation functions show excellent agreement between all cases. The
-consequence for parameter constraints are negligible for current surveys, which
-we demonstrate using CFHTLenS data. In particular, the reported tension with
-Planck CMB temperature anisotropy results cannot be alleviated. This is in
-contrast to the recent claim made by \citet{2016arXiv161104954K}. In the spirit
-of reproducible research, our numerical implementation of all approximations
-and the full projection are publically available within the package
+second-order Limber equations for the projection. We find that the impact of adopting 
+these approximations are negligible when constraining cosmological parameters from 
+current weak lensing surveys.
+This is demonstrated using data from the Canada-France-Hawaii Lensing Survey (CFHTLenS). 
+We find that the reported tension with Planck CMB temperature anisotropy results cannot be alleviated, in
+contrast to the recent claim made by \citet{2016arXiv161104954K}. 
+For future large-scale surveys with unprecedented precision, we show that the spherical
+second-order Limber approximation will provide sufficient accuracy, as it is in 
+agreement with the full projection at the percent level for $\ell > 3$.  
+In the spirit of reproducible research, our numerical implementation of all approximations
+and the full projection are publicly available within the package
 \texttt{nicaea} at \texttt{http://www.cosmostat.org/software/nicaea}.
@@
 modifications to gravity.  As such it is the primary science goal of several
-current (KiDS, HSC, DES) and future (Euclid, LSST, WFIRST) large surveys.
+current (KiDS, HSC, DES) and future (Euclid, LSST, WFIRST) large-scale surveys.
 Interest in the results from these surveys is high as statistically significant
@@
 cosmic shear with unprecedented precision, one needs to revisit the theoretical
-model predictions of the observables to make sure that the accuracy of the
+model predictions of the observables to ensure that the accuracy of the
 models meet the upcoming data. In this paper, we examine the widely used Limber
@@
 that the latter is an excellent approximation of the full projection. Since it
-involves only 1D integrals over the matter power specrum, it is very fast to
+involves only 1D integrals over the matter power spectrum, it is very fast to
 calculate numerically and can readily employed in Monte-Carlo sampling methods
 to obtain precision constraints on cosmological parameters.
+
+This paper is organised as follows.
+In section~\ref{sec:wl} we provide a pedagogical introduction to weak gravitational lensing theory, projections and power spectra for the flat-sky and spherical cases.
+In section~\ref{sec:L2} we derive weak lensing observables using a second-order limber approximation first introduced by \citet{2008PhRvD..78l3506L}.
+We compare the shear power spectrum and commonly-used two-point shear correlation function for a range of different approximations in section~\ref{sec:comp}, providing cosmological constraints for each case using CFHTLenS data from \citet{CFHTLenS-2pt-notomo} in section~\ref{sec:cfhtlens}.
+This paper draws from several sources of literature which have previously reviewed the accuracy of the Limber approximation for weak lensing studies, namely \citet{2008PhRvD..78d3002S,2012PhRvD..86b3001B, 2012MNRAS.422.2854G}.
 
@@
 
-\bibliographystyle{mn2e}
+\bibliographystyle{mnras}
 \bibliography{astro}

### 2017-02-06 limber2.tex
limber2: added text according to Peter's question about separating k and chi

--- 2017-02-05 limber2.tex
@@
                 \nonumber \\
-                & \times \int_0^\infty {\rm d} k \, k^2 \, P_{\rm m}(k, \chi, \chi^\prime) \,
+                & \times \int_0^\infty {\rm d} k \, k^2 \, P_{\rm m}(k; \chi, \chi^\prime) \,
                 {\rm j}_\ell(k \chi) \, {\rm j}_\ell(k \chi^\prime) .
@@
 by performing a Taylor expansion of the function $f$ around $x = k \chi = \nu$, where
-the Bessel function has its approximate maximum. To separate the $k$- and
-$\chi, \chi^\prime$-terms in (\ref{eq:C_ell_full}), we first approximate the
-matter power cross-spectrum between two distances as geometric mean of the two
-involved distances \cite{2016arXiv161200770K}, and divide out the growth factor
-to define a redshift-independent power spectrum $P_{\rm m}(k)$,
-%
-\begin{equation}
- P_{\rm m}(k, \chi, \chi^\prime) = \sqrt{ P_{\rm m}(k, \chi) P_{\rm m}(k, \chi^\prime) }
-    =: D_+(\chi) D_+(\chi^\prime) P_{\rm m}(k).
+the Bessel function has its approximate maximum.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Geometric mean cross-correlation power spectrum}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+To separate the $k$- and $\chi, \chi^\prime$-terms in (\ref{eq:C_ell_full}), we
+first approximate the matter power cross-spectrum between two distances as
+geometric mean of the two involved distances \cite{2005PhRvD..72b3516C,2016arXiv161200770K},
+%
+\begin{equation}
+ P_{\rm m}(k; \chi, \chi^\prime) = \sqrt{ P_{\rm m}(k; \chi) P_{\rm m}(k; \chi^\prime) }
   \label{eq:P_geom_mean}
@@
 %
-This is not exact, since some non-linear prescriptions of the power spectrum
-depend on redshift other than the growth factor, for example when computing the
-non-linear scale $k_{\rm NL}(z)$ for \texttt{halofit}.
-
 With this, eq.~(\ref{eq:C_ell_full}) is written as
@@
   C^\gamma_{ij}(\ell) \approx & \, \ellbar^2(\ell, 2) \, \pref^2
-                \int_0^\infty \frac{{\rm d} k}{k^3} \, P_{\rm m}(k) \,
-                \int_{0}^\infty \frac{{\rm d} \chi}{\chi^{3/2}} \frac{D_+(\chi)}{a(\chi)} q_i(\chi) {\rm J}_{\ell+1/2}(k \chi)
+                \int_0^\infty \frac{{\rm d} k}{k^3} \,
+                % P_{\rm m}(k) \,
+                \int_{0}^\infty \frac{{\rm d} \chi}{\chi^{3/2}} \sqrt{P_{\rm m}(k; \chi)}
+                \frac{q_i(\chi)}{a(\chi)} {\rm J}_{\ell+1/2}(k \chi)
                 \nonumber \\
@@
                 \int_{0}^\infty \frac{{\rm d} \chi^\prime}{{\chi^\prime}^{3/2}}
-                \frac{D_+(\chi^\prime)}{a(\chi^\prime)} q_j(\chi^\prime) {\rm J}_{\ell+1/2}(k \chi^\prime)
+                \sqrt{P_{\rm m}(k; \chi^\prime)} \frac{q_j(\chi^\prime)}{a(\chi^\prime)} {\rm J}_{\ell+1/2}(k \chi^\prime)
   \label{eq:C_ell_full_Pk}
@@
   \approx g(\nu) - \frac 1 2 \left.\frac{{\rm d}^2 g}{{\rm d} x^2}\right|_{x=\nu}
-                 - \frac \nu 6 \left.\frac{{\rm d}^3 g}{{\rm d} x^3}\right|_(x=\nu) ,
-\end{equation}
-%
-with $g(x) = k^{-1} f(\chi)$, $\chi=x/k$, and its derivatives $g^{(n)}(x) =
-k^{-1-n} f^{(n)}(\chi)$. In our case the projection kernel is
-%
-\begin{equation}
-  f(\chi) = D_+(\chi) a^{-1}(\chi) \chi^{-3/2} q(\chi).
+                 - \frac \nu 6 \left.\frac{{\rm d}^3 g}{{\rm d} x^3}\right|_{x=\nu} ,
+\end{equation}
+%
+with $g(x) = k^{-1} f(k, \chi)$, $\chi=x/k$, and its derivatives $g^{(n)}(x) =
+k^{-1-n} f^{(n)}(k, \chi)$ for a given $k$. In our case the projection kernel is
+%
+\begin{equation}
+  f(k, \chi) = \sqrt{P_{\rm m}(k; \chi)} \, a^{-1}(\chi) \chi^{-3/2} q(\chi).
   \label{eq:f_LA08}
@@
   C^\gamma_{ij}(\ell) \approx & \, \ellbar^2(\ell, 2) \, \pref^2
-    \int_0^\infty \frac{{\rm d} k}{k^3} \, P_{\rm m}(k) k^{-2}
-    \left[ f_i(\chi) - \frac{1}{2 k^2} f_i^{\prime\prime}(\chi)
-      - \frac{\nu}{6 k^3} f_i^{\prime\prime\prime}(\chi) + \ldots \right]
+    \int_0^\infty \frac{{\rm d} k}{k^3} \, k^{-2}
+    \left[ f_i(k, \chi) - \frac{1}{2 k^2} f_i^{\prime\prime}(k, \chi)
+      - \frac{\nu}{6 k^3} f_i^{\prime\prime\prime}(k, \chi) + \ldots \right]
     %\nonumber \\
     %& \times
-    \left[ f_j(\chi) - \frac{1}{2 k^2} f_j^{\prime\prime}(\chi)
-    - \frac{\nu}{6 k^3} f_j^{\prime\prime\prime}(\chi) + \ldots \right]
+    \left[ f_j(k, \chi) - \frac{1}{2 k^2} f_j^{\prime\prime}(k, \chi)
+    - \frac{\nu}{6 k^3} f_j^{\prime\prime\prime}(k, \chi) + \ldots \right]
   \label{eq:C_ell_limber2_dk}
@@
     = & \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2
-    \int_0^\infty {\rm d} \chi \, \chi^3 \, P_{\rm m}\left( k \right)
+    \int_0^\infty {\rm d} \chi \, \chi^3 \, % P_{\rm m}\left( k \right)
     %\Bigg\{
     \left\{
-    f_i(\chi) f_j(\chi)
+    (f_i f_j)(\nu/\chi, \chi)
     %\right.
@@
     %\left.
-     - \frac 1 {\nu^2} \left[ \frac{\chi^2}{2} \left( f^{}_i f^{\prime\prime}_j + f_i^{\prime\prime} f^{}_j \right)(\chi)
-    + \frac{\chi^3}{6} \left( f^{}_i f^{\prime\prime\prime}_j + f^{\prime\prime\prime}_i f^{}_j \right)(\chi)
+     - \frac 1 {\nu^2} \left[ \frac{\chi^2}{2} \left( f^{}_i f^{\prime\prime}_j + f_i^{\prime\prime} f^{}_j \right)(\nu/\chi, \chi)
+    + \frac{\chi^3}{6} \left( f^{}_i f^{\prime\prime\prime}_j + f^{\prime\prime\prime}_i f^{}_j \right)(\nu/\chi, \chi)
     \right]
@@
   C^\gamma_{{\rm L1}, ij}(\ell) = & \, \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2 \int {\rm d} \chi \frac{ q_i(\chi) q_j(\chi) }{a^2(\chi)}
-  P_{\rm m}\left(k = \frac{\nu}{\chi}; \chi\right).
+  P_{\rm m}\left(\frac{\nu}{\chi}; \chi\right).
   \label{eq:C_ell_limber1}
@@
   C^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2} \, \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2
-    \int {\rm d} \chi \, \chi^{2} a^{-2} P_{\rm m}\left(k = \frac\nu\chi; \chi\right)
+    \int {\rm d} \chi \, \chi^{2} a^{-2} \sqrt{P_{\rm m}\left(\frac\nu\chi; \chi\right)}
     %\nonumber \\
     %& \times
-    \frac 1 2 D^{-1}_+(\chi) a(\chi) \chi^{3/2} \left[ q^{}_i f^{\prime\prime}_j + f^{\prime\prime}_i q^{}_j
+    \frac{a(\chi)}{2} \chi^{3/2} \left[ q^{}_i f^{\prime\prime}_j + f^{\prime\prime}_i q^{}_j
       + \frac{\chi}{3} \left( q^{}_i f^{\prime\prime\prime}_j + f^{\prime\prime\prime}_i q^{}_j
       \right)
+    \right](\nu/\chi, \chi)
+  \label{eq:C_ell_limber2_dr} 
+\end{align}
+%
+The higher-order derivatives of the filter functions have to be computed
+numerically in the general case. These suffer from numerical noise and are
+sensitive to the set-up, for example the step size. The tabulation and
+interpolation of those derivatives is time-taking since they depend on two
+arguments, $\nu$ and $\chi$. In the following section, we will separate the
+$k$- and $\chi$-dependend parts of the power spectrum to make the numerical
+derivatives faster and more smooth.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Time-independent power spectrum separation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+To further develop (\ref{eq:P_geom_mean}), we divide out the growth factor to
+define a redshift-independent power spectrum $P_{\rm m}(k)$,
+%
+\begin{equation}
+ P_{\rm m}(k, \chi) =: D_+(\chi) P_{\rm m}(k).
+  \label{eq:P_k_chi_sep_s}
+\end{equation}
+%
+This is not exact, since some non-linear prescriptions of the power spectrum
+depend on redshift other than the growth factor, for example when computing the
+non-linear scale $k_{\rm NL}(z)$ for \texttt{halofit}.
+
+With this approximation, the $k$-independent term factors out
+from (\ref{eq:f_LA08}), and we define the separated kernel function $f_{\rm s}$ as
+%
+\begin{equation}
+  f_{\rm s}(\chi) = \sqrt{P_{\rm m}(k)} D_+(\chi) a^{-1}(\chi) \chi^{-3/2} q(\chi).
+  \label{eq:f_LA08_s}
+\end{equation}
+%
+and does not need to be considered when taking the derivatives with respect to comoving distances.
+The second-order Limber term of the shear power spectrum can then be simplified to
+%
+\begin{align}
+  C^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2} \, \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2
+    \int {\rm d} \chi \, \chi^{2} a^{-2} P_{\rm m}\left(\frac\nu\chi; \chi\right)
+    %\nonumber \\
+    %& \times
+    \frac {a(\chi)}{2 D_+(\chi)} \chi^{3/2}
+    \left[ q^{}_i f^{\prime\prime}_{{\rm s} j} + f^{\prime\prime}_{{\rm s}i} q^{}_j
+      + \frac{\chi}{3} \left( q^{}_i f^{\prime\prime\prime}_{{\rm s}j} + f^{\prime\prime\prime}_{{\rm s}i} q^{}_j
+      \right)
     \right](\chi)
-  \label{eq:C_ell_limber2_dr} 
-\end{align}
-%
-The derivatives of the filter functions have to be computed numerically in the general case.
+  \label{eq:C_ell_limber2_dr_s}
+\end{align}
+%
+We compute the numerical higher derivatives as follows. The functions $f_{\rm
+s}(\chi)$ are fitted as power laws with index $\approx 1.5$. The fit is
+performed between $\chi_{\rm min} = 0.001 {\rm Mpc}/h$ and $\chi_{\rm max} =
+500 \mbox{Mpc}/h$. At larger comoving distances the kernel decreases faster
+than a power law, so we exclude this range from the fit. Even though the
+derivaties are larger due to the steeper decline, the associated errors are
+very small since those scales are down-weighed by the kernel function $f_{\rm
+s}$ itself. At $\chi = 500 \mbox{Mpc}/h$ the filter function is less than
+$10^{-4}$ of its value of unity at Mpc$/h$.
+
+%The error between filter and power-law fit
+%becomes larger than $50\%$ only for scales larger than $1,500 \mbox{Mpc}/h$. On the angular
+%scales where the second-order Limber approximation significantly contributes to the shear
+%power spectrum, $\ell \le 100$, this corresponds to $k < 0.03 h/$Mpc, linear
+%scales where the 3D power spectrum is small and does not strongly contribute to the lensing
+%power spectrum.
 
@@
     %& \times
-    \frac 1 2 D^{-1}_+(\chi) a(\chi) \chi^{3/2} \left[ q^{}_i f^{\prime\prime}_j + f^{\prime\prime}_i q^{}_j  
-      + \frac{\chi}{3} \left( q^{}_i f^{\prime\prime\prime}_j + f^{\prime\prime\prime}_i q^{}_j
+    \frac{a(\chi)}{2 D^{-1}_+(\chi)} \chi^{3/2} \left[ q^{}_i f^{\prime\prime}_{{\rm s}j} + f^{\prime\prime}_{{\rm s}i} q^{}_j  
+      + \frac{\chi}{3} \left( q^{}_i f^{\prime\prime\prime}_{{\rm s}j} + f^{\prime\prime\prime}_{{\rm s}i} q^{}_j
       \right)
@@
 \renewcommand{\baselinestretch}{1.3}
-\begin{table}[ht!]
+\begin{table}
 
@@
   %
-  $2^{\rm st}$-order extended Limber, flat sky & Ext2FlHyb & (\ref{eq:P_ell_limber2}) + (iii)
+  $2^{\rm st}$-order extended Limber, flat sky & Ext2FlHyb &  (\ref{eq:P_ell_limber1}) + (\ref{eq:P_ell_limber2}) + (iii)
     & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ & - \\ \hline
   %
-  $2^{\rm st}$-order extended Limber, spherical & Ext2Sph & (\ref{eq:C_ell_limber1})+(\ref{eq:C_ell_limber2_dr})
+  $2^{\rm st}$-order extended Limber, spherical & Ext2Sph & (\ref{eq:C_ell_limber1})+(\ref{eq:C_ell_limber2_dr_s})
     & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ & - \\ \hline
@@
 \cite{KiDS-450}, Fenech Compti). The state-of-the-art cosmological constraints
-for CFHTLenS including most of those updates are presented in
-\cite{joudaki/etal:2016}.
+for CFHTLenS including most of those updates are $\sigma_8 (\Omega_{\rm
+m}/0.3)^{0.4} = 0.78\pm{0.04}$, presented in \cite{joudaki/etal:2016}.
 
@@
 carry out the derivatives of the kernels $f$ under the assumption of a constant
-growth-suppression factor $D_+(a)/a$. We show the consistency between their
-result (eq.~7.19) and our (\ref{eq:C_ell_limber2_dr}), as follows.
-
-We write (\ref{eq:C_ell_limber2_dr}) without tomography, and insert again the
+growth-suppression factor $D_+(a)/a$, and a power spectrum that separates $k$-
+from $\chi$-terms. We show the consistency between their result (eq.~7.19) and
+our (\ref{eq:C_ell_limber2_dr_s}), as follows.
+
+We write (\ref{eq:C_ell_limber2_dr_s}) without tomography, and insert again the
 time-independent power spectrum (\ref{eq:P_geom_mean}),

### 2017-02-07 cfhtlens.tex
very minor
Updated CFHTLenS section - needs to sort out bibliography doubles Included new discussion section, but it needs work Some purple comments for you MK Won't get back to this before tomorrow morning! C

--- 2016-12-09 cfhtlens.tex
@@
 \begin{itemize}
- \item{\citet{choi/etal:2016} identified biases in the tomographic photometric redshift distributions using a more effective clustering analysis, in comparison to \citet{benjamin/etal:2013}, by incorporating newly overlapping spectroscopy from the Sloan Digital Sky Survey.
-The CFHTLenS tomographic cosmological analysis was then revisited by \citet{joudaki/etal:2016} in order to include a full redshift error analysis based on the results from \citet{choi/etal:2016}, discussed further in section~\ref{sec:photoz}.}
+ \item{\citet{choi/etal:2016} identified significant biases in the tomographic photometric redshift distributions using a more effective clustering analysis, in comparison to \citet{benjamin/etal:2013}, by incorporating newly overlapping spectroscopy from the Sloan Digital Sky Survey.
+The conclusion of this work was that any re-analysis of CFHTLenS should include systematic error terms to account for bias and scatter, with a prediction that accounting for these biases would be {\it reduce} the recovered amplitude of $\sigma_8$ by $\sim 4$\%.
+}
+\item{ The CFHTLenS tomographic cosmological analysis was then revisited by \citet{joudaki/etal:2016} in order to include a full redshift error analysis based on the results from \citet{choi/etal:2016}.
+The impact of correcting for these biases, including their associated errors, served to reduce the overall constraining power of the survey and hence also the tension between CFHTLenS and CMB constraints.}
  \item{\citet{asgari/etal:2016} used the stringent `COSEBI' statistic to identify significant non-lensing `B-mode' distortions when the CFHTLenS data was split into tomographic slices.}
@@
 \item{\citet{joudaki/etal:2016} updated the CFHTLenS covariance matrices using larger-box numerical simulations that were less subject to the lack of power on large scales.}
+\item{\cite{2012ApJ...761..152T} provided a more accurate non-linear power spectrum correction that that used in the original CFHTLenS analyses and the halo model from \cite{2015MNRAS.454.1958M} allowed for simultaneous modelling of baryonic modifications to the non-linear power spectrum.}
 \end{itemize}
-All these advances in our understanding were incorporated and accounted for in the recent KiDS cosmic shear analysis \citep{hildebrandt/etal:2016} which reports a $2.3 \sigma$ tension with Planck.
+All these advances in our understanding were incorporated and accounted for in the recent KiDS cosmic shear analysis \citep{KiDS-450} which reports a $2.3 \sigma$ tension with Planck.
 Efforts are now underway to fully re-analyse CFHTLenS using the advanced KiDS analysis pipeline with revised shape measurements and calibrations for the shear and photometric redshifts.
 Until this analysis is complete we note that these known shortcomings with the original CFHTLenS results impact in different ways on the cosmological conclusions that one can draw from the survey.
+As CFHTLenS has similar statistical power to current weak lensing surveys, however, it is nevertheless provides a very useful testbed with which to demonstrate the impact of adopting different approximations when constraining cosmological parameters.
 
-The \citet{kitching/etal:2016} re-analysis of the 2D CFHTLenS data from \citet{kilbinger/etal:2013} chose to only vary $\sigma_8$ in their analysis, fixing all other parameters to Planck values.
-They find a conditional value of $\sigma_8 = 0.789 \pm 0.015$ for their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}).
-This result can be compared to the full five-parameter fit from \citet{kilbinger/etal:2013} who find $S_8=\sigma_8(\Omega_m/0.3)^{0.6} = 0.74 \pm 0.03$.
-We argue that this reduction in the relevant error by a factor of $\sim 2$, could easily mislead, making it appear that the impact of removing all approximations from the theoretical analysis is more significant for current surveys than it is in reality.
-Nevertheless, we repeated the `one-parameter' analysis for the full range of Limber cases listed in Table~\ref{tab:Tl_nu} and are unable to confirm the results quoted by \citet{kitching/etal:2016}.
-We find the lowest conditional value of $\sigma_8 = 0.746 \pm 0.023$ for the `Standard' (KSt) case and the highest conditional value of $\sigma_8 = 0.749 \pm 0.023$ for the `Extended Limber Flat' (ELF) case, a maximum change of $\Delta \sigma_8 = 0.0026 = 0.11 \sigma$.
-These findings are in disagreement with \citet{kitching/etal:2016} who find a shift of $\Delta \sigma_8 = 0.007 = 0.5\sigma$ between their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) and their `Limber' analysis (which we believe corresponds to the Extended Limber spherical (ELS) case in Table~\ref{tab:Tl_nu}).
+We re-analyse the 2D CFHTLenS data from \cite{CFHTLenS-2pt-notomo}, adopting the same priors and non-linear power spectrum correction\footnote{As an example of significant effects that need to be accounted for using the revised non-linear power spectrum of \cite{2012ApJ...761..152T} in place of \cite{2003MNRAS.341.1311S} results in a decrease of $0.6 \sigma$ with $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6} =0.768^{+0.029}_{-0.031}$.} from \cite{2003MNRAS.341.1311S} as the original \cite{CFHTLenS-2pt-notomo} analysis.
+For a first-order standard Limber flat-sky approximation (L1Fl) we find $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6} =0.787^{+0.031}_{-0.033}$.
+For a second-order extended Limber flat-sky approximation we find $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6} =X^{+X}_{-0.X}$, a negligible change of $X\sigma$.
 
-The most relevant case to consider is differences between the fiducially used `Extended Standard Flat' (ESt) case with the preferred `Extended Limber Spherical' (ELS) case.
-Here we find that the constraints are identical at the $0.01\sigma$ level.
-As expected from the comparison in Figure~\ref{fig:Cl_xi}, and given the low signal-to-noise CFHTLenS measurements on large scales, we conclude that the different combinations of assuming flat or spherical sky, baseline or extended Limber, make little difference to the cosmological parameter constraints, even in a `one-parameter' analysis.
+Table \ref{tab:CFHTLenS_Sigma8} lists the mean and 68\% credible interval for $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$ for the various approximations to the lensing
+power spectrum projections listed in Table~\ref{tab:cases}
 
+\ch{This text taken from the comment on paper;
 We note that \citet{kitching/etal:2016} use their `Flat' approximation for their `Full' non-Limber analysis of the CFHTLenS data.
@@
 We would therefore argue that it is more appropriate to use a $T_\ell = 1$ flat-sky approximation when carrying out a `Full' non-Limber analysis of the shear correlation function obtained from the Hankel transformation (equation~\ref{eqn:xiGG}).
+We need to take a decision here about what to use.
+Do we need a Full Flat case in Table 1, and to demonstrate that Ext2Fl is very close to FullFl?
+And then use Ext2Fl as our "truth" for the correlation function?}
 
-\subsection{Comparison of two-point shear statistics; the two-point correlation function, mass aperture statistic and COSEBIs}
-\citet{kilbinger/etal:2013} present a detailed comparison of cosmological constraints obtained from a range of different two-point shear statistics including the shear correlation function, $\xi_\pm$, the aperture-mass dispersion, $\langle M_ {\rm ap} \rangle ^2$ \citep{schneider/etal:1998}, and the COSEBIs, $E_n$ \citep{schneider/etal:2010}.
-These statistics are linearly related to the power spectrum via integrals of the form,
-%
-\begin{align}
-\label{eqn:integ}
-& E_n =\int_0^{\infty}\frac{\d \ell \ell}{2\pi} W_n(\ell) P(\ell)\;,\\ \nonumber
-& \langle M_ {\rm ap} \rangle ^2(\theta)=\int_0^{\infty}\frac{\d \ell \ell}{2\pi} U^2_\theta(\ell) P(\ell)\;,
-\end{align}
-%
-where $W_n(\ell)$ and $U^2_\theta(\ell)$ are defined in \cite{schneider/etal:2010} and \cite{schneider/etal:1998}. The corresponding equation for $\xi_\pm$ is given in equation~\ref{eqn:xiGG}.
-Figure~\ref{fig:filters} shows the integrands of these statistics 
-for two cases, normalised to their maximum value, where the integrands are of the form $\ell F(\ell) P(\ell)$.
-For $\xi_\pm$, $P(\ell)$ is equal to the sum of the E and B-mode power spectra, motivating the development of the aperture-mass dispersion statistic, $\langle M_ {\rm ap} \rangle ^2$.
-This statistic is, however, a lossy conversion and is biased by small angular separations, where blending of galaxies makes shear measurement challenging \citep{kilbinger/etal:2006}.
-The COSEBIs statistic tackles both these shortcomings.
-The upper two panels of figure~\ref{fig:filters} show the integrands\footnote{Note that the lower left panel of Fig.
-1 in \citet{kitching/etal:2016} shows an integrated form of this function for a maximum angular separation of $100'$.
-However, in \citet{kilbinger/etal:2013}, the data used in \citet{kitching/etal:2016}, $\theta$ is between $0.8'$ and $350'$.} of $\xi_\pm$ for $\theta=100'$ and $\theta=350'$.
-The lower middle panel in Figure~\ref{fig:filters} shows the COSEBIs integrands for two angular ranges, $[1',100']$ and $[0.8',350']$, where we only show the integrands for the lowest COSEBIs mode, $E_1$, as the higher modes generally probe larger $\ell$-modes.
-Finally, the lowest panel shows the integrands of aperture mass dispersion statistics, for the same two maximum angular ranges.
+\begin{table}
 
-\begin{figure}[!htp]
-\begin{center}
-\begin{tabular}{ccc}
-\includegraphics[width=\textwidth]{figures/IntegAll.pdf} \\
+  \label{tab:CFHTLenS_Sigma8}
+
+  \caption{Mean and 68\% credible interval for 
+  $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$ for various approximations to the lensing
+  power spectrum projections.}
+
+  \begin{tabular}{lc} \hline
+  ID       & $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$ \\ \hline
+  L1Fl     & $0.787^{+0.031}_{-0.033}$ \\
+  ExtL2Sph & $0.788 \pm 0.032$ \\ \hline
   \end{tabular}
-\caption{ \small{\label{fig:filters}. Integrand of $\xi_+$ (upper), $\xi_-$ (upper middle), $E_1$ (lower middle, E-COSEBIs) and $\langle M_{\rm ap} \rangle^2$ (lower panel).
-All integrands are of the form $\ell F(\ell) P(\ell)$, where $F(\ell)$ is the corresponding weight-function
-for each statistic and $P(\ell)$ is the E-mode convergence power spectrum, with the exception of $\xi_\pm$, for which
-$P(\ell)$ is equal to the sum of the E and B-mode power spectra. 
-Two cases are shown for each statistic as listed in each caption.
-For the aperture mass statistic $\theta_{\rm max}=2\theta$ is shown. 
-Note that higher order COSEBIs modes generally probe larger $\ell$-modes, 
-hence here we only show the lowest mode $E_1$. All values are normalized with respect to their maximum value. }
-}
-\end{center}
-\end{figure}
 
-From Figure~\ref{fig:filters} we can see that the two-point cosmic shear statistics tested by \citet{kilbinger/etal:2013} exhibit different dependences between the angular scales sampled and the $\ell$-range probed.
-If a significant bias had been introduced at low-$\ell$ by using flat-sky and Limber approximations, we would then expect to see a systematic shift between the different two-point statistics with the COSEBIs statistic being essentially unaffected as it only includes modes with $\ell \gtrsim 20$.
-This is found not to be the case with all three statistics finding $\sigma_8 (\Omega_m/0.27)^\alpha = 0.79$ with errors that range from $0.03$ to $0.06$ for the full five-parameter fit, and $\alpha$ ranging from $0.59$ to 0.7 \citep[see Table 5 of][]{kilbinger/etal:2013}.
-This comparison further supports our argument that the approximations highlighted by \citet{kitching/etal:2016} have negligible impact for current surveys.
-
-\subsection{On the Validation of Methods on Simulations}
-It is discussed in \citet{kitching/etal:2016} that the validation of cosmic shear estimators on mock catalogues could also be affected by the approximations they investigate.
-We agree that a full sky mock should be compared to a full curved sky non-Limber prediction.
-It is then suggested, however, that the discrepancies already reported between existing mocks and the predictions could be attributed to these approximations, as opposed to a finite box effect \citep{kiessling/etal:2011, harnois-deraps/etal:2012, harnois-deraps/vanwaerbeke:2015}.
-Going beyond flat-sky and Limber could improve the agreement, however this cannot explain the results of \citet{harnois-deraps/vanwaerbeke:2015} who demonstrate that the large-scale under-estimation of power varies with the simulation box size.
-This volume effect was verified by comparing the $\xi_+$ statistic at large angular scales between simulation volumes with box sides  ranging from $147\;\rm{Mpc/h}$ to $515\;\rm{Mpc/h}$ \citep[see Fig.
-5 in][]{harnois-deraps/vanwaerbeke:2015}.
-The increase of power loss with decreasing box size was shown to be fully-modelled by excluding the super-box $k$-modes in the Limber predictions, something that the approximations discussed in \citet{kitching/etal:2016} would be unable to explain.
-
-We note that any future comparison of mock data with full curved sky non-Limber predictions would place requirements on the input weak lensing simulations.
-Many work with parallel plane mass-sheets as opposed to curved sky mass-sheets and at large angles these two approaches differ, regardless of the box size.
-
-\subsection{On the application to CMB lensing}
-\citet{kitching/etal:2016} discuss how corrections to the Limber and flat-sky approximations would also affect predictions involving the shear and convergence cross-spectrum, such that the cross-correlation of CMB lensing and galaxy lensing should include a pre-factor $ [\ell(\ell+1)]^2/(\ell+ 0.5)^4 = 1-{1\over 2\ell^2}+{\cal O}(\ell^{-3})$.
-We have verified that this term would have negligible impact on current measurements, given the relatively low signal to noise ratio.
-For example, most measurements \citep{hand/etal:2015, liu/hill:2015, kirk/etal:2016,harnois-deraps/etal:2016} are carried over angular multipoles in the range $\ell \in [20-2000]$.
-The size of the pre-factor, averaged over this range, is of the order of 0.01\%.
-In comparison, the size of the statistical error bars are of the order 25-35\% with additional uncertainty due to photometric redshifts (10-15\%) and intrinsic galaxy alignments (10-15\%).
-The pre-factor reaches 1\% only for $\ell < 7$, which may become relevant for very large upcoming surveys but is negligible for current surveys.
-
-\subsection{On the quadratic estimator of the cosmic shear power spectrum}
-
-\citet{kitching/etal:2016} state that `the derivative of a Limber-approximated power spectrum is not equal to the Limber-approximation of the derivative'.
-Based on this statement they conclude that `statistics that use Limber-approximated quadratic estimators to measure the cosmic shear power spectrum are not accurate' and refer explicitly to the quadratic estimator implementation used in \citet{Koehlinger2016} to measure the cosmic shear power spectrum from CFHTLenS.
-In this quadratic estimator implementation, however, the Limber approximation does not enter.
-
-The quadratic estimator algorithm was originally presented by \citet{Hu2001} in the context of cosmic shear and has also been applied to other shear data sets (e.g.
-\citealt{Brown2003, Heymans2005, Lin2012}).
-The aim of the method is to find the best-fitting power spectra assuming a Gaussian likelihood function $\mathcal{L}$.
-The likelihood depends on the shear data vector and its covariance $\mathbf{C}$ which consists of the sum of the shear correlation matrix $\mathbf{C}^\mathrm{sig}$ and the noise matrix $\mathbf{C}^\mathrm{noise}$.
-The shear correlation matrix can be written as a linear combination of piece-wise constant band powers $\mathcal{B}$ approximating the Fourier transforms of the shear correlations, i.e.
-their power spectra (cf.
-equations~3,~10 in \citealt{Koehlinger2016}).
-The best-fitting power spectra are found by iteratively stepping through a Newton--Raphson method in order to find the root of $\diff \mathcal{L}/ \diff \mathcal{B} = 0$ \citep{Bond1998, Seljak1998}.
-In the subsequent equations of the Newton--Raphson method only derivatives of the full covariance matrix enter, where the derivatives are taken with respect to band powers\footnote{i.e.
-$\partial \mathbf{C} / \partial \mathcal{B}_A$, where $A$ is a superindex over the type of the band, band-power bin and redshift correlation, see appendix\~A in \citealt{Koehlinger2016}.}.
-We emphasize that the only approximation entering this algorithm is the flat-sky approximation when introducing the Fourier decomposition of the spin-2 shear field.
-This approximation is appropriate and accurate for current surveys as $\ell>80$  in all analyses published to date.
+\end{table}

### 2017-02-07 discussion.tex
Updated CFHTLenS section - needs to sort out bibliography doubles Included new discussion section, but it needs work Some purple comments for you MK Won't get back to this before tomorrow morning! C

--- 2016-12-09 cfhtlens.tex
@@
-The Canada-France-Hawaii Telescope Lensing Survey (CFHTLenS) represented a major step forward for the field of weak gravitational lensing, in terms of improved accuracy in data reduction \citep{erben/etal:2013}, the implementation of PSF-Gaussianised matched multi-band photometry \citep{hildebrandt/etal:2012}, cross-correlation clustering analysis between photometric redshift slices to verify tomographic redshift distributions \citep{benjamin/etal:2013}, accurate calibrated shape measurements \citep{miller/etal:2013} and a full suite of informative systematic tests to select a clean data set \citep{heymans/etal:2012}.
-Since the public release of this survey in 2013, the community has continued to scrutinise and advance our understanding of CFHTLenS by identifying a number of areas where analyses could improve:
-\begin{itemize}
- \item{\citet{choi/etal:2016} identified biases in the tomographic photometric redshift distributions using a more effective clustering analysis, in comparison to \citet{benjamin/etal:2013}, by incorporating newly overlapping spectroscopy from the Sloan Digital Sky Survey.
-The CFHTLenS tomographic cosmological analysis was then revisited by \citet{joudaki/etal:2016} in order to include a full redshift error analysis based on the results from \citet{choi/etal:2016}, discussed further in section~\ref{sec:photoz}.}
-\item{\citet{asgari/etal:2016} used the stringent `COSEBI' statistic to identify significant non-lensing `B-mode' distortions when the CFHTLenS data was split into tomographic slices.}
-\item{\citet{kuijken/etal:2015} showed that the CFHTLenS shear calibration corrections derived in \citet{miller/etal:2013} were underestimated as a result of an imperfect match between the galaxy populations in the data and image simulations.}
-\item{\citet{fenechconti/etal:2016} demonstrated that the CFHTLenS data would have been subject to a weight bias that favours galaxies that are more intrinsically oriented with the point-spread function.
-They also showed that the impact of calibration selection biases, that were not considered in \citet{miller/etal:2013}, would have lead to the over-correction of multiplicative shear bias in the CFHTLenS analyses, by a few percent.}
-\item{\citet{joudaki/etal:2016} updated the CFHTLenS covariance matrices using larger-box numerical simulations that were less subject to the lack of power on large scales.}
-\end{itemize}
-All these advances in our understanding were incorporated and accounted for in the recent KiDS cosmic shear analysis \citep{hildebrandt/etal:2016} which reports a $2.3 \sigma$ tension with Planck.
-Efforts are now underway to fully re-analyse CFHTLenS using the advanced KiDS analysis pipeline with revised shape measurements and calibrations for the shear and photometric redshifts.
-Until this analysis is complete we note that these known shortcomings with the original CFHTLenS results impact in different ways on the cosmological conclusions that one can draw from the survey.
+\subsection{Comparison of two-point shear statistics; the two-point correlation function, mass aperture statistic and COSEBIs}
 
-The \citet{kitching/etal:2016} re-analysis of the 2D CFHTLenS data from \citet{kilbinger/etal:2013} chose to only vary $\sigma_8$ in their analysis, fixing all other parameters to Planck values.
-They find a conditional value of $\sigma_8 = 0.789 \pm 0.015$ for their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}).
-This result can be compared to the full five-parameter fit from \citet{kilbinger/etal:2013} who find $S_8=\sigma_8(\Omega_m/0.3)^{0.6} = 0.74 \pm 0.03$.
-We argue that this reduction in the relevant error by a factor of $\sim 2$, could easily mislead, making it appear that the impact of removing all approximations from the theoretical analysis is more significant for current surveys than it is in reality.
-Nevertheless, we repeated the `one-parameter' analysis for the full range of Limber cases listed in Table~\ref{tab:Tl_nu} and are unable to confirm the results quoted by \citet{kitching/etal:2016}.
-We find the lowest conditional value of $\sigma_8 = 0.746 \pm 0.023$ for the `Standard' (KSt) case and the highest conditional value of $\sigma_8 = 0.749 \pm 0.023$ for the `Extended Limber Flat' (ELF) case, a maximum change of $\Delta \sigma_8 = 0.0026 = 0.11 \sigma$.
-These findings are in disagreement with \citet{kitching/etal:2016} who find a shift of $\Delta \sigma_8 = 0.007 = 0.5\sigma$ between their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) and their `Limber' analysis (which we believe corresponds to the Extended Limber spherical (ELS) case in Table~\ref{tab:Tl_nu}).
+\ch{Copied this over from original comment paper - I would like to include this material somewhere in the paper - this needs work though to make it fit.... TBD}
 
-The most relevant case to consider is differences between the fiducially used `Extended Standard Flat' (ESt) case with the preferred `Extended Limber Spherical' (ELS) case.
-Here we find that the constraints are identical at the $0.01\sigma$ level.
-As expected from the comparison in Figure~\ref{fig:Cl_xi}, and given the low signal-to-noise CFHTLenS measurements on large scales, we conclude that the different combinations of assuming flat or spherical sky, baseline or extended Limber, make little difference to the cosmological parameter constraints, even in a `one-parameter' analysis.
-
-We note that \citet{kitching/etal:2016} use their `Flat' approximation for their `Full' non-Limber analysis of the CFHTLenS data.
-This is because on a sphere, correlation functions cannot be related to the power spectrum by a Hankel transform (e.g.
-equation~\ref{eqn:xiGG}) as the power spectrum is not defined for non-integer $\ell$.
-In Figure~\ref{fig:Cl_xi}, however, we show that this chosen version of a flat-sky approximation serves to exacerbate the tension in theoretical models when a flat-sky solution is compared with the spherical-sky solution in the Limber approximated case.
-This is not the case when considering the standard $T_\ell = 1$ flat-sky approximation that has been used in the majority of cosmic shear studies to date.
-We would therefore argue that it is more appropriate to use a $T_\ell = 1$ flat-sky approximation when carrying out a `Full' non-Limber analysis of the shear correlation function.
-
-\subsection{Comparison of two-point shear statistics; the two-point correlation function, mass aperture statistic and COSEBIs}
 \citet{kilbinger/etal:2013} present a detailed comparison of cosmological constraints obtained from a range of different two-point shear statistics including the shear correlation function, $\xi_\pm$, the aperture-mass dispersion, $\langle M_ {\rm ap} \rangle ^2$ \citep{schneider/etal:1998}, and the COSEBIs, $E_n$ \citep{schneider/etal:2010}.
@@
 \begin{align}
-\label{eqn:integ}
+%\label{eqn:integ}
 & E_n =\int_0^{\infty}\frac{\d \ell \ell}{2\pi} W_n(\ell) P(\ell)\;,\\ \nonumber
@@
 %
-where $W_n(\ell)$ and $U^2_\theta(\ell)$ are defined in \cite{schneider/etal:2010} and \cite{schneider/etal:1998}. The corresponding equation for $\xi_\pm$ is given in equation~\ref{eqn:xiGG}.
+where $W_n(\ell)$ and $U^2_\theta(\ell)$ are defined in \cite{schneider/etal:2010} and \cite{schneider/etal:1998}. The corresponding equations for $\xi_\pm$ are given in equation~\ref{eqn:xiGG}.
 Figure~\ref{fig:filters} shows the integrands of these statistics 
@@
 
-\begin{figure}[!htp]
+\begin{figure}%[!htp]
 \begin{center}
 \begin{tabular}{ccc}
-\includegraphics[width=\textwidth]{figures/IntegAll.pdf} \\
+\includegraphics[width=0.48\textwidth]{figures/IntegAll.pdf} \\
 \end{tabular}
@@
 This comparison further supports our argument that the approximations highlighted by \citet{kitching/etal:2016} have negligible impact for current surveys.
-
-\subsection{On the Validation of Methods on Simulations}
-It is discussed in \citet{kitching/etal:2016} that the validation of cosmic shear estimators on mock catalogues could also be affected by the approximations they investigate.
-We agree that a full sky mock should be compared to a full curved sky non-Limber prediction.
-It is then suggested, however, that the discrepancies already reported between existing mocks and the predictions could be attributed to these approximations, as opposed to a finite box effect \citep{kiessling/etal:2011, harnois-deraps/etal:2012, harnois-deraps/vanwaerbeke:2015}.
-Going beyond flat-sky and Limber could improve the agreement, however this cannot explain the results of \citet{harnois-deraps/vanwaerbeke:2015} who demonstrate that the large-scale under-estimation of power varies with the simulation box size.
-This volume effect was verified by comparing the $\xi_+$ statistic at large angular scales between simulation volumes with box sides  ranging from $147\;\rm{Mpc/h}$ to $515\;\rm{Mpc/h}$ \citep[see Fig.
-5 in][]{harnois-deraps/vanwaerbeke:2015}.
-The increase of power loss with decreasing box size was shown to be fully-modelled by excluding the super-box $k$-modes in the Limber predictions, something that the approximations discussed in \citet{kitching/etal:2016} would be unable to explain.
-
-We note that any future comparison of mock data with full curved sky non-Limber predictions would place requirements on the input weak lensing simulations.
-Many work with parallel plane mass-sheets as opposed to curved sky mass-sheets and at large angles these two approaches differ, regardless of the box size.
-
-\subsection{On the application to CMB lensing}
-\citet{kitching/etal:2016} discuss how corrections to the Limber and flat-sky approximations would also affect predictions involving the shear and convergence cross-spectrum, such that the cross-correlation of CMB lensing and galaxy lensing should include a pre-factor $ [\ell(\ell+1)]^2/(\ell+ 0.5)^4 = 1-{1\over 2\ell^2}+{\cal O}(\ell^{-3})$.
-We have verified that this term would have negligible impact on current measurements, given the relatively low signal to noise ratio.
-For example, most measurements \citep{hand/etal:2015, liu/hill:2015, kirk/etal:2016,harnois-deraps/etal:2016} are carried over angular multipoles in the range $\ell \in [20-2000]$.
-The size of the pre-factor, averaged over this range, is of the order of 0.01\%.
-In comparison, the size of the statistical error bars are of the order 25-35\% with additional uncertainty due to photometric redshifts (10-15\%) and intrinsic galaxy alignments (10-15\%).
-The pre-factor reaches 1\% only for $\ell < 7$, which may become relevant for very large upcoming surveys but is negligible for current surveys.
-
-\subsection{On the quadratic estimator of the cosmic shear power spectrum}
-
-\citet{kitching/etal:2016} state that `the derivative of a Limber-approximated power spectrum is not equal to the Limber-approximation of the derivative'.
-Based on this statement they conclude that `statistics that use Limber-approximated quadratic estimators to measure the cosmic shear power spectrum are not accurate' and refer explicitly to the quadratic estimator implementation used in \citet{Koehlinger2016} to measure the cosmic shear power spectrum from CFHTLenS.
-In this quadratic estimator implementation, however, the Limber approximation does not enter.
-
-The quadratic estimator algorithm was originally presented by \citet{Hu2001} in the context of cosmic shear and has also been applied to other shear data sets (e.g.
-\citealt{Brown2003, Heymans2005, Lin2012}).
-The aim of the method is to find the best-fitting power spectra assuming a Gaussian likelihood function $\mathcal{L}$.
-The likelihood depends on the shear data vector and its covariance $\mathbf{C}$ which consists of the sum of the shear correlation matrix $\mathbf{C}^\mathrm{sig}$ and the noise matrix $\mathbf{C}^\mathrm{noise}$.
-The shear correlation matrix can be written as a linear combination of piece-wise constant band powers $\mathcal{B}$ approximating the Fourier transforms of the shear correlations, i.e.
-their power spectra (cf.
-equations~3,~10 in \citealt{Koehlinger2016}).
-The best-fitting power spectra are found by iteratively stepping through a Newton--Raphson method in order to find the root of $\diff \mathcal{L}/ \diff \mathcal{B} = 0$ \citep{Bond1998, Seljak1998}.
-In the subsequent equations of the Newton--Raphson method only derivatives of the full covariance matrix enter, where the derivatives are taken with respect to band powers\footnote{i.e.
-$\partial \mathbf{C} / \partial \mathcal{B}_A$, where $A$ is a superindex over the type of the band, band-power bin and redshift correlation, see appendix\~A in \citealt{Koehlinger2016}.}.
-We emphasize that the only approximation entering this algorithm is the flat-sky approximation when introducing the Fourier decomposition of the spin-2 shear field.
-This approximation is appropriate and accurate for current surveys as $\ell>80$  in all analyses published to date.

### 2017-02-07 limber2.tex
Updated CFHTLenS section - needs to sort out bibliography doubles Included new discussion section, but it needs work Some purple comments for you MK Won't get back to this before tomorrow morning! C

--- 2017-02-06 limber2.tex
@@
 \renewcommand{\vec}{\bm}
+\renewcommand{\d}[0]{{\rm d}}
 
 \newcommand{\mk}[1]{{\bf\textcolor{blue}{#1}}}
+
+\definecolor{purple}{RGB}{76, 0,153}
+\newcommand{\ch}[1]{\textcolor{purple}{\bf #1}}
 
@@
 and the Canada-France-Hawaii Telescope Lensing Survey
-\citep[CFHTLenS;][]{2016arXiv160105786J}.  If the source of this tension is not
+\citep[CFHTLenS;][]{joudaki/etal:2016}.  If the source of this tension is not
 a result of so-far unconsidered sources of systematic errors in one or all
@@
 
-We run various projection modes on CFHTLenS single-redshift bin data
-\cite{CFHTLenS-2pt-notomo}. The setting is exactly the same as for the 2013
-results. Note that since then many improvements have been obtained, those
-results do not reflect the most up-to-date cosmological constraints. This is
-sufficient however for our purpose to show the effect of projection
-approximations for weak-lensing surveys. Thos improvement have been made on the
-theoretical modelling side (revised non-linear power spectrum
-\cite{2012ApJ...761..152T}, baryonic modifications of the total power spectrum
-\cite{2015MNRAS.454.1958M}), and the data processing (photometric redshifts
-\cite{2016MNRAS.463.3737C,joudaki/etal:2016}, shear calibration
-\cite{KiDS-450}, Fenech Compti). The state-of-the-art cosmological constraints
-for CFHTLenS including most of those updates are presented in
-\cite{joudaki/etal:2016}.
-
-The mean and 68\% credible interval for $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$
-published in \cite{CFHTLenS-2pt-notomo} were $0.787 \pm 0.032$. We make sure
-that changes introduced to \texttt{CosmoPMC} over the last four years do not
-change this result, we re-run the same setting using the newest version of
-\texttt{CosmoPMC} and obtain $0.787^{+0.031}_{-0.033}$.
-
-Table \ref{tab:CFHTLenS_Sigma8} lists the mean and 68\% credible interval for
-$\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$ for various approximations to the lensing
-power spectrum projections.
-
-As an example of significant effects that need to be accounted for, using the
-revised non-linear power spectrum of \cite{2012ApJ...761..152T} instead of
-\cite{2003MNRAS.341.1311S} yields $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6} =
-0.768^{+0.029}_{-0.031}$ for L1Fl, which is a lower corresponding to 60\% of
-the error bar.
-
-\begin{table}
-
-  \label{tab:CFHTLenS_Sigma8}
-
-  \caption{Mean and 68\% credible interval for 
-  $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$ for various approximations to the lensing
-  power spectrum projections.}
-
-  \begin{tabular}{lc} \hline
-  ID       & $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$ \\ \hline
-  L1Fl     & $0.787^{+0.031}_{-0.033}$ \\
-  ExtL2Sph & $0.788 \pm 0.032$ \\ \hline
-  \end{tabular}
-
-\end{table}
+\input{cfhtlens.tex}
+
+\input{discussion.tex}
 
@@
 
-The authors thank Tommaso Giannantonio for very helpful discussions.
+The authors thank Tommaso Giannantonio, Sarah Bridle, Ami Choi, Donnacha Kirk, Lance Miller, Benjamin Joachimi, Chris Blake and Adam Amara for very helpful discussions.
 

### 2017-02-07 limber2.tex
MK updated figure

--- 2017-02-06 limber2.tex
@@
 
+\mk{Not sure whether the following comments should be left in the draft.} One
+notes that the difference between the full projection and second-order Limber
+does not scale as expected with $\ell^{-4}$, but rather with $\ell^{-2}$. This
+might be due to numercical noise that creates residual terms at the ${\cal
+O}(\ell^{-2})$ which do not cancel. Also note that the numerical noise for
+$\ell > 20$ is due to numerical integration errors for the full projection.
+
 The flat extended Limber approximations (ExtL1Fl and ExtL2Fl) perform relatively poorly, and
@@
 
-\paragraph{Kitching et al.~2016}
-
-Eq.~\ref{eq:C_ell_full} is analogous to (7) and (8) from
-\cite{2016arXiv161104954K} for a flat Universe and in the case of perfect
+\subsection{Kitching et al.~2016}
+
+\cite{2016arXiv161104954K} compute the full projection of the weak-lensing power
+spectrum, which they present as spherical-radial representation the 3D shear field.
+Our results (\ref{eq:C_ell_full}) correspond to their equations (7) and (8)
+for a flat Universe and in the case of perfect
 photometric redshifts, $p(z | z_{\rm p}) = \delta_{\rm D}(z - z_{\rm p})$, and
@@
 
-In App.~A they derive the Limber approximation starting from the full spherical
-projection. Note that their filter function $q$ defined in (31) has an
-errornous factor of comoving distance $r$, and an additional factor $\pi/2$
-appears.
-
-Eq.~19 of \cite{2016arXiv161104954K} corresponds to our
-(\ref{eq:P_ell_gamma}). \mk{Has to be checked.}
-
-We can not reproduce the amplitude of the differences between the cases, neither for
-the power spectrum nor for the shear correlation function (see Fig.~\ref{fig:xi_pm_K16}).
+In App.~A \cite{2016arXiv161104954K} derives the spherical and extended
+Limber approximation starting from the full spherical projection. Note that
+their filter function $q$ defined in (31) has an errornous factor of comoving
+distance $r$, and an additional factor $\pi/2$ appears. \mk{This is probably worded
+too strongly.}
+
+We can not reproduce the amplitude of the differences between the cases,
+neither for the power spectrum nor for the shear correlation function (see
+Figs.~\ref{fig:Cl_cases} and \ref{fig:xi_pm_K16}).
 
@@
   \begin{center}
-    \resizebox{0.9\hsize}{!}{
+    \resizebox{0.5\hsize}{!}{
       \includegraphics{figures/P_kappa_limber_delta_Rijt}
@@
 
-    \caption{Differences in percentage of spherical shear power spectra terms
-    as function of wave mode $\ell$, see Table \ref{tab:cases}.
-    The blue and red curves corresponds to the ones shown in Fig.~7.3 of \citet{vande2012}.
+    \caption{Relative differences in percentage of spherical first- and second-order Limber
+    shear power spectra with respect to the full projection
+    as function of wave mode $\ell$, see Table \ref{tab:cases}. The redshift distribution
+    and the cosmological parameters (see text) are chosen to match
+    \citet{vande2012}, see their Fig.~7.3 for comparison.
     }

### 2017-02-07 limber2.tex

--- 2017-02-06 limber2.tex
@@
 
-We run various projection modes on CFHTLenS single-redshift bin data
-\cite{CFHTLenS-2pt-notomo}. The setting is exactly the same as for the 2013
-results. Note that since then many improvements have been obtained, those
-results do not reflect the most up-to-date cosmological constraints. This is
-sufficient however for our purpose to show the effect of projection
-approximations for weak-lensing surveys. Thos improvement have been made on the
-theoretical modelling side (revised non-linear power spectrum
-\cite{2012ApJ...761..152T}, baryonic modifications of the total power spectrum
-\cite{2015MNRAS.454.1958M}), and the data processing (photometric redshifts
-\cite{2016MNRAS.463.3737C,joudaki/etal:2016}, shear calibration
-\cite{KiDS-450}, Fenech Compti). The state-of-the-art cosmological constraints
-for CFHTLenS including most of those updates are $\sigma_8 (\Omega_{\rm
-m}/0.3)^{0.4} = 0.78\pm{0.04}$, presented in \cite{joudaki/etal:2016}.
-
-The mean and 68\% credible interval for $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$
-published in \cite{CFHTLenS-2pt-notomo} were $0.787 \pm 0.032$. We make sure
-that changes introduced to \texttt{CosmoPMC} over the last four years do not
-change this result, we re-run the same setting using the newest version of
-\texttt{CosmoPMC} and obtain $0.787^{+0.031}_{-0.033}$.
-
-Table \ref{tab:CFHTLenS_Sigma8} lists the mean and 68\% credible interval for
-$\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$ for various approximations to the lensing
-power spectrum projections.
-
-As an example of significant effects that need to be accounted for, using the
-revised non-linear power spectrum of \cite{2012ApJ...761..152T} instead of
-\cite{2003MNRAS.341.1311S} yields $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6} =
-0.768^{+0.029}_{-0.031}$ for L1Fl, which is a lower corresponding to 60\% of
-the error bar.
-
-\begin{table}
-
-  \label{tab:CFHTLenS_Sigma8}
-
-  \caption{Mean and 68\% credible interval for 
-  $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$ for various approximations to the lensing
-  power spectrum projections.}
-
-  \begin{tabular}{lc} \hline
-  ID       & $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$ \\ \hline
-  L1Fl     & $0.787^{+0.031}_{-0.033}$ \\
-  ExtL2Sph & $0.788 \pm 0.032$ \\ \hline
-  \end{tabular}
-
-\end{table}
+\input{cfhtlens.tex}
+\input{discussion.tex}
 

### 2017-02-07 cfhtlens.tex
MK edit text

@@
-The Canada-France-Hawaii Telescope Lensing Survey (CFHTLenS) represented a major step forward for the field of weak gravitational lensing, in terms of improved accuracy in data reduction \citep{erben/etal:2013}, the implementation of PSF-Gaussianised matched multi-band photometry \citep{hildebrandt/etal:2012}, cross-correlation clustering analysis between photometric redshift slices to verify tomographic redshift distributions \citep{benjamin/etal:2013}, accurate calibrated shape measurements \citep{miller/etal:2013} and a full suite of informative systematic tests to select a clean data set \citep{heymans/etal:2012}.
-Since the public release of this survey in 2013, the community has continued to scrutinise and advance our understanding of CFHTLenS by identifying a number of areas where analyses could improve:
+The Canada-France-Hawaii Telescope Lensing Survey (CFHTLenS) represented a
+major step forward for the field of weak gravitational lensing, in terms of
+improved accuracy in data reduction \citep{CFHTLenS-data}, the implementation
+of PSF-Gaussianised matched multi-band photometry
+\citep{CFHTLenS-photoz}, cross-correlation clustering analysis between
+photometric redshift slices to verify tomographic redshift distributions
+\citep{CFHTLenS-2pt-tomo}, accurate calibrated shape measurements
+\citep{CFHTLenS-shapes} and a full suite of informative systematic tests to
+select a clean data set \citep{CFHTLenS-sys}. Since the public release
+of this survey in 2013, the community has continued to scrutinise and advance
+our understanding of CFHTLenS by identifying a number of areas where analyses
+could improve:
+%
 \begin{itemize}
- \item{\citet{choi/etal:2016} identified significant biases in the tomographic photometric redshift distributions using a more effective clustering analysis, in comparison to \citet{benjamin/etal:2013}, by incorporating newly overlapping spectroscopy from the Sloan Digital Sky Survey.
-The conclusion of this work was that any re-analysis of CFHTLenS should include systematic error terms to account for bias and scatter, with a prediction that accounting for these biases would be {\it reduce} the recovered amplitude of $\sigma_8$ by $\sim 4$\%.
-}
-\item{ The CFHTLenS tomographic cosmological analysis was then revisited by \citet{joudaki/etal:2016} in order to include a full redshift error analysis based on the results from \citet{choi/etal:2016}.
-The impact of correcting for these biases, including their associated errors, served to reduce the overall constraining power of the survey and hence also the tension between CFHTLenS and CMB constraints.}
- \item{\citet{asgari/etal:2016} used the stringent `COSEBI' statistic to identify significant non-lensing `B-mode' distortions when the CFHTLenS data was split into tomographic slices.}
-\item{\citet{kuijken/etal:2015} showed that the CFHTLenS shear calibration corrections derived in \citet{miller/etal:2013} were underestimated as a result of an imperfect match between the galaxy populations in the data and image simulations.}
-\item{\citet{fenechconti/etal:2016} demonstrated that the CFHTLenS data would have been subject to a weight bias that favours galaxies that are more intrinsically oriented with the point-spread function.
-They also showed that the impact of calibration selection biases, that were not considered in \citet{miller/etal:2013}, would have lead to the over-correction of multiplicative shear bias in the CFHTLenS analyses, by a few percent.}
+%
+ \item{\citet{2016MNRAS.463.3737C} identified significant biases in the tomographic
+photometric redshift distributions using a more effective clustering analysis,
+in comparison to \citet{CFHTLenS-2pt-tomo}, by incorporating newly overlapping
+spectroscopy from the Sloan Digital Sky Survey.  The conclusion of this work
+was that any re-analysis of CFHTLenS should include systematic error terms to
+account for bias and scatter, with a prediction that accounting for these
+biases would be {\it reduce} the recovered amplitude of $\sigma_8$ by $\sim
+4$\%. }
+%
+\item{ The CFHTLenS tomographic cosmological analysis was then revisited by
+\citet{joudaki/etal:2016} in order to include a full redshift error analysis
+based on the results from \citet{2016MNRAS.463.3737C}.  The impact of
+correcting for these biases, including their associated errors, served to
+reduce the overall constraining power of the survey and hence also the tension
+between CFHTLenS and CMB constraints.}
+%
+ \item{\citet{2016arXiv160100115A} used the stringent `COSEBI' statistic to
+identify significant non-lensing `B-mode' distortions when the CFHTLenS data
+was split into tomographic slices.}
+%
+\item{\citet{2015MNRAS.454.3500K} showed that the CFHTLenS shear calibration
+corrections derived in \citet{CFHTLenS-shapes} were underestimated as a result
+of an imperfect match between the galaxy populations in the data and image
+simulations.}
+%
+\item{\citet{fenechconti/etal:2016} demonstrated that the CFHTLenS data would
+have been subject to a weight bias that favours galaxies that are more
+intrinsically oriented with the point-spread function.  They also showed that
+the impact of calibration selection biases, that were not considered in
+\citet{miller/etal:2013}, would have lead to the over-correction of
+multiplicative shear bias in the CFHTLenS analyses, by a few percent.}
+%
 \item{\citet{joudaki/etal:2016} updated the CFHTLenS covariance matrices using larger-box numerical simulations that were less subject to the lack of power on large scales.}
-\item{\cite{2012ApJ...761..152T} provided a more accurate non-linear power spectrum correction that that used in the original CFHTLenS analyses and the halo model from \cite{2015MNRAS.454.1958M} allowed for simultaneous modelling of baryonic modifications to the non-linear power spectrum.}
+\item{\cite{2012ApJ...761..152T} provided a more accurate non-linear power
+spectrum correction that that used in the original CFHTLenS analyses and the
+halo model from \cite{2015MNRAS.454.1958M} allowed for simultaneous modelling
+of baryonic modifications to the non-linear power spectrum.} 
+%
 \end{itemize}
-All these advances in our understanding were incorporated and accounted for in the recent KiDS cosmic shear analysis \citep{KiDS-450} which reports a $2.3 \sigma$ tension with Planck.
-Efforts are now underway to fully re-analyse CFHTLenS using the advanced KiDS analysis pipeline with revised shape measurements and calibrations for the shear and photometric redshifts.
-Until this analysis is complete we note that these known shortcomings with the original CFHTLenS results impact in different ways on the cosmological conclusions that one can draw from the survey.
-As CFHTLenS has similar statistical power to current weak lensing surveys, however, it is nevertheless provides a very useful testbed with which to demonstrate the impact of adopting different approximations when constraining cosmological parameters.
+%
+All these advances in our understanding were incorporated and accounted for in
+the recent KiDS cosmic shear analysis \citep{KiDS-450} which reports a $2.3
+\sigma$ tension with Planck.  Efforts are now underway to fully re-analyse
+CFHTLenS using the advanced KiDS analysis pipeline with revised shape
+measurements and calibrations for the shear and photometric redshifts.  Until
+this analysis is complete we note that these known shortcomings with the
+original CFHTLenS results impact in different ways on the cosmological
+conclusions that one can draw from the survey.  As CFHTLenS has similar
+statistical power to current weak lensing surveys, however, it is nevertheless
+provides a very useful testbed with which to demonstrate the impact of adopting
+different approximations when constraining cosmological parameters.
 

### 2017-02-07 discussion.tex
MK edit text

@@
 
-\citet{kilbinger/etal:2013} present a detailed comparison of cosmological constraints obtained from a range of different two-point shear statistics including the shear correlation function, $\xi_\pm$, the aperture-mass dispersion, $\langle M_ {\rm ap} \rangle ^2$ \citep{schneider/etal:1998}, and the COSEBIs, $E_n$ \citep{schneider/etal:2010}.
-These statistics are linearly related to the power spectrum via integrals of the form,
+\citet{CFHTLenS-2pt-notomo} present a detailed comparison of cosmological
+constraints obtained from a range of different two-point shear statistics
+including the shear correlation function, $\xi_\pm$, the aperture-mass
+dispersion, $\langle M_ {\rm ap} \rangle ^2$ \citep{1998MNRAS.296..873S}, and
+the COSEBIs, $E_n$ \citep{COSEBIs}.  These statistics are linearly related to
+the power spectrum via integrals of the form,
 %
@@
 %
-where $W_n(\ell)$ and $U^2_\theta(\ell)$ are defined in \cite{schneider/etal:2010} and \cite{schneider/etal:1998}. The corresponding equations for $\xi_\pm$ are given in equation~\ref{eqn:xiGG}.
-Figure~\ref{fig:filters} shows the integrands of these statistics 
-for two cases, normalised to their maximum value, where the integrands are of the form $\ell F(\ell) P(\ell)$.
-For $\xi_\pm$, $P(\ell)$ is equal to the sum of the E and B-mode power spectra, motivating the development of the aperture-mass dispersion statistic, $\langle M_ {\rm ap} \rangle ^2$.
-This statistic is, however, a lossy conversion and is biased by small angular separations, where blending of galaxies makes shear measurement challenging \citep{kilbinger/etal:2006}.
-The COSEBIs statistic tackles both these shortcomings.
-The upper two panels of figure~\ref{fig:filters} show the integrands\footnote{Note that the lower left panel of Fig.
-1 in \citet{kitching/etal:2016} shows an integrated form of this function for a maximum angular separation of $100'$.
-However, in \citet{kilbinger/etal:2013}, the data used in \citet{kitching/etal:2016}, $\theta$ is between $0.8'$ and $350'$.} of $\xi_\pm$ for $\theta=100'$ and $\theta=350'$.
-The lower middle panel in Figure~\ref{fig:filters} shows the COSEBIs integrands for two angular ranges, $[1',100']$ and $[0.8',350']$, where we only show the integrands for the lowest COSEBIs mode, $E_1$, as the higher modes generally probe larger $\ell$-modes.
-Finally, the lowest panel shows the integrands of aperture mass dispersion statistics, for the same two maximum angular ranges.
+where $W_n(\ell)$ and $U^2_\theta(\ell)$ are defined in \cite{COSEBIs} and
+\cite{1998MNRAS.296..873S}. The corresponding equations for $\xi_\pm$ are given
+in equation~\ref{eqn:xiGG}. Figure~\ref{fig:filters} shows the integrands of
+these statistics for two cases, normalised to their maximum value, where the
+integrands are of the form $\ell F(\ell) P(\ell)$. For $\xi_\pm$, $P(\ell)$ is
+equal to the sum of the E and B-mode power spectra, motivating the development
+of the aperture-mass dispersion statistic, $\langle M_ {\rm ap} \rangle ^2$.
+This statistic is, however, a lossy conversion and is biased by small angular
+separations, where blending of galaxies makes shear measurement challenging
+\citep{KSE06}.  The COSEBIs statistic tackles both these
+shortcomings.  The upper two panels of figure~\ref{fig:filters} show the
+integrands\footnote{Note that the lower left panel of Fig.~1 in
+\citet{2016arXiv161104954K} shows an integrated form of this function for a
+maximum angular separation of $100^\prime$. However, in \citet{CFHTLenS-2pt-notomo},
+the data used in \citet{2016arXiv161104954K}, $\theta$ is between $0.8'$ and
+$350'$.} of $\xi_\pm$ for $\theta=100'$ and $\theta=350'$. The lower middle
+panel in Figure~\ref{fig:filters} shows the COSEBIs integrands for two angular
+ranges, $[1',100']$ and $[0.8',350']$, where we only show the integrands for
+the lowest COSEBIs mode, $E_1$, as the higher modes generally probe larger
+$\ell$-modes.  Finally, the lowest panel shows the integrands of aperture mass
+dispersion statistics, for the same two maximum angular ranges.
 
@@
 \end{tabular}
-\caption{ \small{\label{fig:filters}. Integrand of $\xi_+$ (upper), $\xi_-$ (upper middle), $E_1$ (lower middle, E-COSEBIs) and $\langle M_{\rm ap} \rangle^2$ (lower panel).
-All integrands are of the form $\ell F(\ell) P(\ell)$, where $F(\ell)$ is the corresponding weight-function
-for each statistic and $P(\ell)$ is the E-mode convergence power spectrum, with the exception of $\xi_\pm$, for which
-$P(\ell)$ is equal to the sum of the E and B-mode power spectra. 
-Two cases are shown for each statistic as listed in each caption.
-For the aperture mass statistic $\theta_{\rm max}=2\theta$ is shown. 
-Note that higher order COSEBIs modes generally probe larger $\ell$-modes, 
-hence here we only show the lowest mode $E_1$. All values are normalized with respect to their maximum value. }
-}
+\caption{ \small{\label{fig:filters}. Integrand of $\xi_+$ (upper), $\xi_-$
+(upper middle), $E_1$ (lower middle, E-COSEBIs) and $\langle M_{\rm ap}
+\rangle^2$ (lower panel). All integrands are of the form $\ell F(\ell)
+P(\ell)$, where $F(\ell)$ is the corresponding weight-function for each
+statistic and $P(\ell)$ is the E-mode convergence power spectrum, with the
+exception of $\xi_\pm$, for which $P(\ell)$ is equal to the sum of the E and
+B-mode power spectra. Two cases are shown for each statistic as listed in each
+caption. For the aperture mass statistic $\theta_{\rm max}=2\theta$ is shown.
+Note that higher order COSEBIs modes generally probe larger $\ell$-modes, hence
+here we only show the lowest mode $E_1$. All values are normalized with respect
+to their maximum value. } }
 \end{center}
@@
 
-From Figure~\ref{fig:filters} we can see that the two-point cosmic shear statistics tested by \citet{kilbinger/etal:2013} exhibit different dependences between the angular scales sampled and the $\ell$-range probed.
-If a significant bias had been introduced at low-$\ell$ by using flat-sky and Limber approximations, we would then expect to see a systematic shift between the different two-point statistics with the COSEBIs statistic being essentially unaffected as it only includes modes with $\ell \gtrsim 20$.
-This is found not to be the case with all three statistics finding $\sigma_8 (\Omega_m/0.27)^\alpha = 0.79$ with errors that range from $0.03$ to $0.06$ for the full five-parameter fit, and $\alpha$ ranging from $0.59$ to 0.7 \citep[see Table 5 of][]{kilbinger/etal:2013}.
-This comparison further supports our argument that the approximations highlighted by \citet{kitching/etal:2016} have negligible impact for current surveys.
+From Figure~\ref{fig:filters} we can see that the two-point cosmic shear
+statistics tested by \citet{CFHTLenS-2pt-notomo} exhibit different dependences
+between the angular scales sampled and the $\ell$-range probed.   If a
+significant bias had been introduced at low-$\ell$ by using flat-sky and Limber
+approximations, we would then expect to see a systematic shift between the
+different two-point statistics with the COSEBIs statistic being essentially
+unaffected as it only includes modes with $\ell \gtrsim 20$.  This is found not
+to be the case with all three statistics finding $\sigma_8
+(\Omega_m/0.27)^\alpha = 0.79$ with errors that range from $0.03$ to $0.06$ for
+the full five-parameter fit, and $\alpha$ ranging from $0.59$ to 0.7 \citep[see
+Table 5 of][]{CFHTLenS-2pt-notomo}.  This comparison further supports our
+argument that the approximations highlighted by \citet{2016arXiv161104954K}
+have negligible impact for current surveys.

### 2017-02-07 cfhtlens.tex
MK references

@@
 %
-\item{\citet{fenechconti/etal:2016} demonstrated that the CFHTLenS data would
+\item{\citet{2016arXiv160605337F} demonstrated that the CFHTLenS data would
 have been subject to a weight bias that favours galaxies that are more
@@
 the impact of calibration selection biases, that were not considered in
-\citet{miller/etal:2013}, would have lead to the over-correction of
+\citet{CFHTLenS-shapes}, would have lead to the over-correction of
 multiplicative shear bias in the CFHTLenS analyses, by a few percent.}
 %
-\item{\citet{joudaki/etal:2016} updated the CFHTLenS covariance matrices using larger-box numerical simulations that were less subject to the lack of power on large scales.}
+\item{\citet{joudaki/etal:2016} updated the CFHTLenS covariance matrices using
+larger-box numerical simulations that were less subject to the lack of power on
+large scales.}
 \item{\cite{2012ApJ...761..152T} provided a more accurate non-linear power
@@
 
-We re-analyse the 2D CFHTLenS data from \cite{CFHTLenS-2pt-notomo}, adopting the same priors and non-linear power spectrum correction\footnote{As an example of significant effects that need to be accounted for using the revised non-linear power spectrum of \cite{2012ApJ...761..152T} in place of \cite{2003MNRAS.341.1311S} results in a decrease of $0.6 \sigma$ with $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6} =0.768^{+0.029}_{-0.031}$.} from \cite{2003MNRAS.341.1311S} as the original \cite{CFHTLenS-2pt-notomo} analysis.
-For a first-order standard Limber flat-sky approximation (L1Fl) we find $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6} =0.787^{+0.031}_{-0.033}$.
-For a second-order extended Limber flat-sky approximation we find $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6} =X^{+X}_{-0.X}$, a negligible change of $X\sigma$.
+We re-analyse the 2D CFHTLenS data from \cite{CFHTLenS-2pt-notomo}, adopting
+the same priors and non-linear power spectrum correction\footnote{As an example
+of significant effects that need to be accounted for using the revised
+non-linear power spectrum of \cite{2012ApJ...761..152T} in place of
+\cite{2003MNRAS.341.1311S} results in a decrease of $0.6 \sigma$ with $\sigma_8
+(\Omega_{\rm m}/0.3)^{0.6} =0.768^{+0.029}_{-0.031}$.} from
+\cite{2003MNRAS.341.1311S} as the original \cite{CFHTLenS-2pt-notomo} analysis.
+For a first-order standard Limber flat-sky approximation (L1Fl) we find
+$\sigma_8 (\Omega_{\rm m}/0.3)^{0.6} =0.787^{+0.031}_{-0.033}$.   For a
+second-order extended Limber flat-sky approximation we find $\sigma_8
+(\Omega_{\rm m}/0.3)^{0.6} =X^{+X}_{-0.X}$, a negligible change of $X\sigma$.
 
@@
 
-\ch{This text taken from the comment on paper;
-We note that \citet{kitching/etal:2016} use their `Flat' approximation for their `Full' non-Limber analysis of the CFHTLenS data.
-This is because on a sphere, correlation functions cannot be related to the power spectrum by a Hankel transform (e.g.
-equation~\ref{eqn:xiGG}) as the power spectrum is not defined for non-integer $\ell$.
-In Figure~\ref{fig:Cl_xi}, however, we show that this chosen version of a flat-sky approximation serves to exacerbate the tension in theoretical models when a flat-sky solution is compared with the spherical-sky solution in the Limber approximated case.
-This is not the case when considering the standard $T_\ell = 1$ flat-sky approximation that has been used in the majority of cosmic shear studies to date.
-We would therefore argue that it is more appropriate to use a $T_\ell = 1$ flat-sky approximation when carrying out a `Full' non-Limber analysis of the shear correlation function obtained from the Hankel transformation (equation~\ref{eqn:xiGG}).
-We need to take a decision here about what to use.
-Do we need a Full Flat case in Table 1, and to demonstrate that Ext2Fl is very close to FullFl?
-And then use Ext2Fl as our "truth" for the correlation function?}
+\ch{This text taken from the comment on paper; We note that
+\citet{2016arXiv161104954K} use their `Flat' approximation for their `Full'
+non-Limber analysis of the CFHTLenS data.   This is because on a sphere,
+correlation functions cannot be related to the power spectrum by a Hankel
+transform (e.g. equation~\ref{eqn:xiGG}) as the power spectrum is not defined
+for non-integer $\ell$. In Figure~\ref{fig:Cl_xi}, however, we show that this
+chosen version of a flat-sky approximation serves to exacerbate the tension in
+theoretical models when a flat-sky solution is compared with the spherical-sky
+solution in the Limber approximated case.  This is not the case when
+considering the standard $T_\ell = 1$ flat-sky approximation that has been used
+in the majority of cosmic shear studies to date.  We would therefore argue that
+it is more appropriate to use a $T_\ell = 1$ flat-sky approximation when
+carrying out a `Full' non-Limber analysis of the shear correlation function
+obtained from the Hankel transformation (equation~\ref{eqn:xiGG}). We need to
+take a decision here about what to use.  Do we need a Full Flat case in Table
+1, and to demonstrate that Ext2Fl is very close to FullFl?  And then use Ext2Fl
+as our "truth" for the correlation function?}
 

### 2017-02-08 cfhtlens.tex
MK added more Sigma_8 values

@@
 in comparison to \citet{CFHTLenS-2pt-tomo}, by incorporating newly overlapping
-spectroscopy from the Sloan Digital Sky Survey.  The conclusion of this work
-was that any re-analysis of CFHTLenS should include systematic error terms to
-account for bias and scatter, with a prediction that accounting for these
+spectroscopic data from the Sloan Digital Sky Survey.  The conclusion of this
+work was that any re-analysis of CFHTLenS should include systematic error terms
+to account for bias and scatter, with a prediction that accounting for these
 biases would be {\it reduce} the recovered amplitude of $\sigma_8$ by $\sim
@@
 %
- \item{\citet{2016arXiv160100115A} used the stringent `COSEBI' statistic to
-identify significant non-lensing `B-mode' distortions when the CFHTLenS data
-was split into tomographic slices.}
+ \item{\citet{2016arXiv160100115A} used the stringent COSEBI statistic
+\cite{COSEBIs} to identify significant non-lensing B-mode distortions when the
+CFHTLenS data was split into tomographic slices.}
 %
@@
 \item{\cite{2012ApJ...761..152T} provided a more accurate non-linear power
-spectrum correction that that used in the original CFHTLenS analyses and the
+spectrum correction than that used in the original CFHTLenS analyses, and the
 halo model from \cite{2015MNRAS.454.1958M} allowed for simultaneous modelling
@@
 this analysis is complete we note that these known shortcomings with the
-original CFHTLenS results impact in different ways on the cosmological
-conclusions that one can draw from the survey.  As CFHTLenS has similar
-statistical power to current weak lensing surveys, however, it is nevertheless
-provides a very useful testbed with which to demonstrate the impact of adopting
-different approximations when constraining cosmological parameters.
+original CFHTLenS results impact in different ways the cosmological conclusions
+that one can draw from the survey.  As CFHTLenS has similar statistical power
+to current weak lensing surveys, however, it nevertheless provides a very
+useful testbed with which to demonstrate the impact of adopting different
+approximations when constraining cosmological parameters.
 
-We re-analyse the 2D CFHTLenS data from \cite{CFHTLenS-2pt-notomo}, adopting
-the same priors and non-linear power spectrum correction\footnote{As an example
-of significant effects that need to be accounted for using the revised
-non-linear power spectrum of \cite{2012ApJ...761..152T} in place of
+In this work, we focus on the weak-lensing power spectrum projection, and
+assess the impact of various approximations on cosmological constraints from
+CFHTLenS. We re-analyse the 2D CFHTLenS data from \cite{CFHTLenS-2pt-notomo},
+adopting the same priors and non-linear power spectrum corrections\footnote{As
+an example of significant effects that need to be accounted for using the
+revised non-linear power spectrum of \cite{2012ApJ...761..152T} in place of
 \cite{2003MNRAS.341.1311S} results in a decrease of $0.6 \sigma$ with $\sigma_8
-(\Omega_{\rm m}/0.3)^{0.6} =0.768^{+0.029}_{-0.031}$.} from
+(\Omega_{\rm m}/0.27)^{0.6} =0.768^{+0.029}_{-0.031}$.} from
 \cite{2003MNRAS.341.1311S} as the original \cite{CFHTLenS-2pt-notomo} analysis.
 For a first-order standard Limber flat-sky approximation (L1Fl) we find
-$\sigma_8 (\Omega_{\rm m}/0.3)^{0.6} =0.787^{+0.031}_{-0.033}$.   For a
+$\sigma_8 (\Omega_{\rm m}/0.27)^{0.6} =0.787^{+0.031}_{-0.033}$. For a
 second-order extended Limber flat-sky approximation we find $\sigma_8
-(\Omega_{\rm m}/0.3)^{0.6} =X^{+X}_{-0.X}$, a negligible change of $X\sigma$.
+(\Omega_{\rm m}/0.27)^{0.6} =X^{+X}_{-X}$, a negligible change of
+$X\sigma$.
 
-Table \ref{tab:CFHTLenS_Sigma8} lists the mean and 68\% credible interval for $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$ for the various approximations to the lensing
-power spectrum projections listed in Table~\ref{tab:cases}
+Table \ref{tab:CFHTLenS_Sigma8} lists the mean and 68\% credible interval for
+$\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$ for the various approximations to the
+lensing power spectrum projections listed in Table~\ref{tab:cases}
 
@@
 
+\renewcommand{\baselinestretch}{1.5}
 \begin{table}
@@
 
-  \begin{tabular}{lc} \hline
-  ID       & $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$ \\ \hline
-  L1Fl     & $0.787^{+0.031}_{-0.033}$ \\
-  ExtL2Sph & $0.788 \pm 0.032$ \\ \hline
+  \begin{tabular}{lcc} \hline
+  ID         & $\sigma_8 (\Omega_{\rm m}/0.27)^{0.6}$ & $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$\\ \hline
+  L1Fl       & $0.787^{+0.031}_{-0.033}$ & $0.739^{+0.029}_{-0.031}$ \\
+  ExtL1FlHyb & $0.788^{+0.031}_{-0.033}$ & $0.740^{+0.029}_{-0.031}$ \\
+  ExtL2Sph   & $0.789^{+0.031}_{-0.032}$ & $0.740^{+0.029}_{-0.030}$ \\ \hline
   \end{tabular}
@@
 \end{table}
+\renewcommand{\baselinestretch}{1}

### 2017-02-08 discussion.tex
MK edit discussion

@@
-\subsection{Comparison of two-point shear statistics; the two-point correlation function, mass aperture statistic and COSEBIs}
+\subsection{Comparison of two-point shear statistics; the two-point correlation
+function, mass aperture statistic and COSEBIs}
 
-\ch{Copied this over from original comment paper - I would like to include this material somewhere in the paper - this needs work though to make it fit.... TBD}
+\ch{Copied this over from original comment paper - I would like to include this
+material somewhere in the paper - this needs work though to make it fit....
+TBD}
 
@@
 including the shear correlation function, $\xi_\pm$, the aperture-mass
-dispersion, $\langle M_ {\rm ap} \rangle ^2$ \citep{1998MNRAS.296..873S}, and
+dispersion, $\langle M_ {\rm ap}^2 \rangle2$ \citep{1998MNRAS.296..873S}, and
 the COSEBIs, $E_n$ \citep{COSEBIs}.  These statistics are linearly related to
-the power spectrum via integrals of the form,
+the shear power spectrum in the flat-sky approximation via integrals of the form (omitting tomographic indices),
 %
 \begin{align}
-%\label{eqn:integ}
-& E_n =\int_0^{\infty}\frac{\d \ell \ell}{2\pi} W_n(\ell) P(\ell)\;,\\ \nonumber
-& \langle M_ {\rm ap} \rangle ^2(\theta)=\int_0^{\infty}\frac{\d \ell \ell}{2\pi} U^2_\theta(\ell) P(\ell)\;,
+  \langle M_ {\rm ap}^2 \rangle(\theta) & = \int_0^{\infty}\frac{\d \ell \ell}{2\pi}
+  \hat U^2(\theta\ell) P^\gamma(\ell),
+  \label{eqn:integ}
+  \\
+  E_n & = \int_0^{\infty}\frac{\d \ell \ell}{2\pi} W_n(\ell) P^\gamma(\ell),
 \end{align}
 %
-where $W_n(\ell)$ and $U^2_\theta(\ell)$ are defined in \cite{COSEBIs} and
-\cite{1998MNRAS.296..873S}. The corresponding equations for $\xi_\pm$ are given
-in equation~\ref{eqn:xiGG}. Figure~\ref{fig:filters} shows the integrands of
-these statistics for two cases, normalised to their maximum value, where the
-integrands are of the form $\ell F(\ell) P(\ell)$. For $\xi_\pm$, $P(\ell)$ is
-equal to the sum of the E and B-mode power spectra, motivating the development
-of the aperture-mass dispersion statistic, $\langle M_ {\rm ap} \rangle ^2$.
-This statistic is, however, a lossy conversion and is biased by small angular
-separations, where blending of galaxies makes shear measurement challenging
-\citep{KSE06}.  The COSEBIs statistic tackles both these
-shortcomings.  The upper two panels of figure~\ref{fig:filters} show the
+where the Fourier-space filter functions $\hat U$ and $W_n$ are defined in
+\cite{1998MNRAS.296..873S} and \cite{COSEBIs}. The corresponding equations for
+$\xi_\pm$ are given in equation~\ref{eqn:xiGG}. Figure~\ref{fig:filters} shows
+the integrands of these statistics for two cases, normalised to their maximum
+value, where the integrands are of the form $\ell F(\ell) P^\gamma(\ell)$. For
+$\xi_\pm$, $P^\gamma(\ell)$ is equal to the sum of the E and B-mode power spectra
+which cannot easily be separated,
+motivating the development of the aperture-mass dispersion statistic, $\langle
+M_ {\rm ap}^2 \rangle$. This statistic is, however, a lossy conversion and is
+biased by small angular separations, where blending of galaxies makes shear
+measurement challenging \citep{KSE06}. The COSEBIs statistic tackles both
+these shortcomings.  The upper two panels of figure~\ref{fig:filters} show the
 integrands\footnote{Note that the lower left panel of Fig.~1 in
 \citet{2016arXiv161104954K} shows an integrated form of this function for a
-maximum angular separation of $100^\prime$. However, in \citet{CFHTLenS-2pt-notomo},
-the data used in \citet{2016arXiv161104954K}, $\theta$ is between $0.8'$ and
-$350'$.} of $\xi_\pm$ for $\theta=100'$ and $\theta=350'$. The lower middle
-panel in Figure~\ref{fig:filters} shows the COSEBIs integrands for two angular
-ranges, $[1',100']$ and $[0.8',350']$, where we only show the integrands for
-the lowest COSEBIs mode, $E_1$, as the higher modes generally probe larger
-$\ell$-modes.  Finally, the lowest panel shows the integrands of aperture mass
-dispersion statistics, for the same two maximum angular ranges.
+maximum angular separation of $100^\prime$. However, in
+\citet{CFHTLenS-2pt-notomo}, the data used in \citet{2016arXiv161104954K},
+$\theta$ is between $0.8'$ and $350'$.} of $\xi_\pm$ for $\theta=100'$ and
+$\theta=350'$. The lower middle panel in Figure~\ref{fig:filters} shows the
+COSEBIs integrands for two angular ranges, $[1',100']$ and $[0.8',350']$, where
+we only show the integrands for the lowest COSEBIs mode, $E_1$, as the higher
+modes generally probe larger $\ell$-modes.  Finally, the lowest panel shows the
+integrands of aperture mass dispersion statistics, for the same two maximum
+angular ranges.
 

### 2017-02-08 limber2.tex
MK edit text
Some updates to the intro

@@
 modifications to gravity.  As such it is the primary science goal of several
-current (KiDS, HSC, DES) and future (Euclid, LSST, WFIRST) large-scale surveys.
+current (KiDS, DES, HSC\footnote{KiDS: \href={http://kids.strw.leidenuniv.nl}, DES: \href={http://www.darkenergysurvey.org}, HSC: \href={http://hsc.mtk.nao.ac.jp/ssp/}})
+and future (Euclid, LSST, WFIRST\footnote{Euclid: \href={http://sci.esa.int/euclid}, LSST: \href={http://www.lsst.org}, WFIRST: \href={http://wfirst.gsfc.nasa.gov}}) surveys.
+%(Kilo-Degree Survey, KiDS \citet{kuijken/etal:2015}, Dark Energy Survey, DES, \citet{abbott/etal:2016}, Hyper-Suprime Camera Survey, HSC\footnote{HSC; \href={http://hsc.mtk.nao.ac.jp/ssp/}}) and future (Euclid, \citet{2011arXiv1110.3193L}, LSST, \citet{chang/etal:2013}, WFIRST\footnote{WFIRST; \href={http://wfirst.gsfc.nasa.gov}}) large-scale surveys.
 Interest in the results from these surveys is high as statistically significant
@@
 
-In the era of the upcoming large surveys that will provide measurements of
+In the era of the upcoming large-scale surveys that will provide measurements of
 cosmic shear with unprecedented precision, one needs to revisit the theoretical
-model predictions of the observables to ensure that the accuracy of the
-models meet the upcoming data. In this paper, we examine the widely used Limber
+predictions of the observables to ensure that the accuracy of the
+models meet the accuracy of the upcoming data. In this paper, we examine the widely used Limber
 approximation for the projected weak-lensing power spectrum. We consider
@@
 projection as well as first- and second-order Limber approximation. We show
-that the latter is an excellent approximation of the full projection. Since it
-involves only 1D integrals over the matter power spectrum, it is very fast to
+that the second-order Limber approximation is an accurate representation of the full projection, with better than percent level precision for scale $\ell > 3$. 
+Since this approximation involves only 1D integrals over the matter power spectrum, it is very fast to
 calculate numerically and can readily employed in Monte-Carlo sampling methods
@@
 In section~\ref{sec:L2} we derive weak lensing observables using a second-order limber approximation first introduced by \citet{2008PhRvD..78l3506L}.
-We compare the shear power spectrum and commonly-used two-point shear correlation function for a range of different approximations in section~\ref{sec:comp}, providing cosmological constraints for each case using CFHTLenS data from \citet{CFHTLenS-2pt-notomo} in section~\ref{sec:cfhtlens}.
+We compare the shear power spectrum and commonly-used two-point shear correlation function for the full solution to a range of different approximations in section~\ref{sec:comp}, providing cosmological constraints for each case using CFHTLenS data from \citet{CFHTLenS-2pt-notomo} in section~\ref{sec:cfhtlens}.
 This paper draws from several sources of literature which have previously reviewed the accuracy of the Limber approximation for weak lensing studies, namely \citet{2008PhRvD..78d3002S,2012PhRvD..86b3001B, 2012MNRAS.422.2854G}.
@@
 
-With this approximation, the $k$-independent term factors out
-from (\ref{eq:f_LA08}), and we define the separated kernel function $f_{\rm s}$ as
-%
-\begin{equation}
-  f_{\rm s}(\chi) = \sqrt{P_{\rm m}(k)} D_+(\chi) a^{-1}(\chi) \chi^{-3/2} q(\chi).
+With this approximation, the $k$-independent term factors out from
+(\ref{eq:f_LA08}), and we define the separated kernel function $f_{\rm s}$ as
+%
+\begin{equation}
+  f_{\rm s}(\chi) = D_+(\chi) a^{-1}(\chi) \chi^{-3/2} q(\chi).
   \label{eq:f_LA08_s}

### 2017-02-08 cfhtlens.tex
Some updates on the results section Purple text for MK to review

@@
 
-In this work, we focus on the weak-lensing power spectrum projection, and
+\ch{New stuff here - see if you approve - edit and then de-purple it!}
+
+\ch{In this work, we focus on the weak-lensing power spectrum projection, and
 assess the impact of various approximations on cosmological constraints from
-CFHTLenS. We re-analyse the 2D CFHTLenS data from \cite{CFHTLenS-2pt-notomo},
-adopting the same priors and non-linear power spectrum corrections\footnote{As
-an example of significant effects that need to be accounted for using the
+CFHTLenS. We re-analyse the 2D CFHTLenS measurement of the two-point shear correlation function $\xi_\pm(\theta)$ from \cite{CFHTLenS-2pt-notomo}, which is
+given by}
+\begin{equation}
+\xi_\pm^{ij}(\theta) = \frac{1}{2\pi}\int_0^\infty \d\ell \,\ell \,P^{ij}_\gamma(\ell) \, J_{0,4}(\ell \theta) \, , 
+\label{eqn:xiGG}
+\end{equation}
+\ch{where $J_{0,4} (\ell \theta)$ is the zeroth (for $\xi_+$) or fourth (for $\xi_- $) order Bessel function of the first kind and $P_\gamma(\ell)$ is the shear power spectrum at angular wave number $\ell$ which can be related to the underlying matter power spectrum through equation~\ref{eq:P_ell_limber1} when adopting a first-order extended Limber approximation, or equation~\ref{eq:P_ell_limber2} when adopting a second-order extended Limber approximation \citep[for more details see][and references therein]{miraldaescude:1991, kaiser:1992, bartelmann/schneider:2001}.
+Note that as we have shown in section~\ref{sec:comp} that the second-order extended Limber approximation provides a percent-level precision representation of the full spherical projection, we do not investigate predictions for the two-point shear correlation function using the full spherical projection.
+This is because on a sphere,
+correlation functions cannot be related to the power spectrum by a Hankel transform (e.g. equation~\ref{eqn:xiGG}) as the power spectrum is not defined for non-integer $\ell$.}
+
+For consistency, we adopt the same priors and non-linear power spectrum corrections\footnote{As
+an example of more significant effects that need to be accounted for, when using the
 revised non-linear power spectrum of \cite{2012ApJ...761..152T} in place of
-\cite{2003MNRAS.341.1311S} results in a decrease of $0.6 \sigma$ with $\sigma_8
+\cite{2003MNRAS.341.1311S}, there is a decrease of $0.6 \sigma$ with $\sigma_8
 (\Omega_{\rm m}/0.27)^{0.6} =0.768^{+0.029}_{-0.031}$.} from
@@
 lensing power spectrum projections listed in Table~\ref{tab:cases}
-
-\ch{This text taken from the comment on paper; We note that
-\citet{2016arXiv161104954K} use their `Flat' approximation for their `Full'
-non-Limber analysis of the CFHTLenS data.   This is because on a sphere,
-correlation functions cannot be related to the power spectrum by a Hankel
-transform (e.g. equation~\ref{eqn:xiGG}) as the power spectrum is not defined
-for non-integer $\ell$. In Figure~\ref{fig:Cl_xi}, however, we show that this
-chosen version of a flat-sky approximation serves to exacerbate the tension in
-theoretical models when a flat-sky solution is compared with the spherical-sky
-solution in the Limber approximated case.  This is not the case when
-considering the standard $T_\ell = 1$ flat-sky approximation that has been used
-in the majority of cosmic shear studies to date.  We would therefore argue that
-it is more appropriate to use a $T_\ell = 1$ flat-sky approximation when
-carrying out a `Full' non-Limber analysis of the shear correlation function
-obtained from the Hankel transformation (equation~\ref{eqn:xiGG}). We need to
-take a decision here about what to use.  Do we need a Full Flat case in Table
-1, and to demonstrate that Ext2Fl is very close to FullFl?  And then use Ext2Fl
-as our "truth" for the correlation function?}
 

### 2017-02-08 discussion.tex
Updated the alternative two-point discussion section

@@
-\subsection{Comparison of two-point shear statistics; the two-point correlation
-function, mass aperture statistic and COSEBIs}
+\subsection{Alternative two-point shear statistics; the mass aperture statistic and COSEBIs}
 
-\ch{Copied this over from original comment paper - I would like to include this
-material somewhere in the paper - this needs work though to make it fit....
-TBD}
+The two-point shear correlation function $\xi_\pm$ represents the current baseline observable for cosmic shear measurements.   
+As shown in Figure~\ref{fig:xi_pm_K16}, however, using the standard first-order extended Limber flat-sky approximation (ExtL1FlHyb) can result
+in errors exceeding 10 percent, on angular scales $\theta > 300$ arcmin.
+This is a result of the significant weight given to low $\ell$ modes in the $\xi_+$ statistic, as illustrated in Figure~\ref{fig:filters} which shows the integrand of $\xi_+$ and $\xi_-$ (upper two panels) for two cases ( $\theta = 100$ and $\theta = 350$ arcmin), normalised to their maximum
+value.
+This error does not impact CFHTLenS analyses, given the low signal-to-noise of the measurements on these scales.
+It will however become increasingly important for upcoming wider-field surveys which will accurately probe these scales.
 
-\citet{CFHTLenS-2pt-notomo} present a detailed comparison of cosmological
-constraints obtained from a range of different two-point shear statistics
-including the shear correlation function, $\xi_\pm$, the aperture-mass
-dispersion, $\langle M_ {\rm ap}^2 \rangle2$ \citep{1998MNRAS.296..873S}, and
-the COSEBIs, $E_n$ \citep{COSEBIs}.  These statistics are linearly related to
+In this paper we provide a solution in the form of the second-order extended Limber approximation, but another option is to consider alternative two-point shear statistics that are less sensitive to accuracy in shear power spectrum measurement at low $\ell$.
+Both the aperture-mass dispersion, $\langle M_ {\rm ap}^2 \rangle2$ \citep{1998MNRAS.296..873S}, and
+the Complete Orthogonal Sets of E/B-mode Integrals (COSEBIs), $E_n$ \citep{COSEBIs} statistics satisfy this requirement and are linearly related to
 the shear power spectrum in the flat-sky approximation via integrals of the form (omitting tomographic indices),
@@
 where the Fourier-space filter functions $\hat U$ and $W_n$ are defined in
-\cite{1998MNRAS.296..873S} and \cite{COSEBIs}. The corresponding equations for
-$\xi_\pm$ are given in equation~\ref{eqn:xiGG}. Figure~\ref{fig:filters} shows
-the integrands of these statistics for two cases, normalised to their maximum
-value, where the integrands are of the form $\ell F(\ell) P^\gamma(\ell)$. For
-$\xi_\pm$, $P^\gamma(\ell)$ is equal to the sum of the E and B-mode power spectra
-which cannot easily be separated,
-motivating the development of the aperture-mass dispersion statistic, $\langle
-M_ {\rm ap}^2 \rangle$. This statistic is, however, a lossy conversion and is
+\cite{1998MNRAS.296..873S} and \cite{COSEBIs}. 
+Figure~\ref{fig:filters} shows the integrands of these statistics, again normalised to their maximum
+value, where the integrands are of the form $\ell F(\ell) P^\gamma(\ell)$.  
+The lower middle panel in Figure~\ref{fig:filters} shows the
+COSEBIs integrands for two angular ranges, $[1',100']$ and $[0.8',350']$, where
+we only show the integrands for the lowest COSEBIs mode, $E_1$, as the higher
+modes generally probe larger $\ell$-modes.  The lowest panel shows the
+integrands of aperture mass dispersion statistics, for the same two maximum
+angular ranges.
+
+Note that the development of the aperture-mass dispersion statistic, $\langle
+M_ {\rm ap}^2 \rangle$ was initially motivated to enable the separation of the measured signal into an 
+E-mode (cosmological signal) and B-mode (systematics). This statistic is, however, a lossy conversion and is
 biased by small angular separations, where blending of galaxies makes shear
 measurement challenging \citep{KSE06}. The COSEBIs statistic tackles both
-these shortcomings.  The upper two panels of figure~\ref{fig:filters} show the
-integrands\footnote{Note that the lower left panel of Fig.~1 in
-\citet{2016arXiv161104954K} shows an integrated form of this function for a
-maximum angular separation of $100^\prime$. However, in
-\citet{CFHTLenS-2pt-notomo}, the data used in \citet{2016arXiv161104954K},
-$\theta$ is between $0.8'$ and $350'$.} of $\xi_\pm$ for $\theta=100'$ and
-$\theta=350'$. The lower middle panel in Figure~\ref{fig:filters} shows the
-COSEBIs integrands for two angular ranges, $[1',100']$ and $[0.8',350']$, where
-we only show the integrands for the lowest COSEBIs mode, $E_1$, as the higher
-modes generally probe larger $\ell$-modes.  Finally, the lowest panel shows the
-integrands of aperture mass dispersion statistics, for the same two maximum
-angular ranges.
+these shortcomings.  \citet{CFHTLenS-2pt-notomo} present a detailed comparison of cosmological
+constraints obtained from this range of different two-point shear statistics finding consistent results.
 
@@
 \end{tabular}
-\caption{ \small{\label{fig:filters}. Integrand of $\xi_+$ (upper), $\xi_-$
+\caption{ \small{\label{fig:filters}. 
+Integrand of $\xi_+$ (upper), $\xi_-$
 (upper middle), $E_1$ (lower middle, E-COSEBIs) and $\langle M_{\rm ap}
@@
 here we only show the lowest mode $E_1$. All values are normalized with respect
-to their maximum value. } }
+to their maximum value. This figure illustrates how different two-point cosmic shear
+statistics have different dependences between the angular scales sampled and the $\ell$-range probed. }}
 \end{center}
 \end{figure}
-
-From Figure~\ref{fig:filters} we can see that the two-point cosmic shear
-statistics tested by \citet{CFHTLenS-2pt-notomo} exhibit different dependences
-between the angular scales sampled and the $\ell$-range probed.   If a
-significant bias had been introduced at low-$\ell$ by using flat-sky and Limber
-approximations, we would then expect to see a systematic shift between the
-different two-point statistics with the COSEBIs statistic being essentially
-unaffected as it only includes modes with $\ell \gtrsim 20$.  This is found not
-to be the case with all three statistics finding $\sigma_8
-(\Omega_m/0.27)^\alpha = 0.79$ with errors that range from $0.03$ to $0.06$ for
-the full five-parameter fit, and $\alpha$ ranging from $0.59$ to 0.7 \citep[see
-Table 5 of][]{CFHTLenS-2pt-notomo}.  This comparison further supports our
-argument that the approximations highlighted by \citet{2016arXiv161104954K}
-have negligible impact for current surveys.

### 2017-02-08 limber2.tex
Some updates on the results section Purple text for MK to review
Added explicit links to the appendices in the intro

@@
 We compare the shear power spectrum and commonly-used two-point shear correlation function for the full solution to a range of different approximations in section~\ref{sec:comp}, providing cosmological constraints for each case using CFHTLenS data from \citet{CFHTLenS-2pt-notomo} in section~\ref{sec:cfhtlens}.
-This paper draws from several sources of literature which have previously reviewed the accuracy of the Limber approximation for weak lensing studies, namely \citet{2008PhRvD..78d3002S,2012PhRvD..86b3001B, 2012MNRAS.422.2854G}.
+This paper draws from several sources of literature which have previously reviewed the accuracy of the Limber approximation for weak lensing studies, namely \citet{2008PhRvD..78d3002S,2012PhRvD..86b3001B, 2012MNRAS.422.2854G, 2016arXiv161104954K}.
+We present a discussion and comparison of our results to these papers in Appendix~\ref{app:B}.
 
@@
 compute lensing power spectra for a spherical case, and in the flat-sky
-approximation. Derivations for those expressions can be found in the appendix.
+approximation. For completeness we provide a derivations of the weak lensing power spectra in Appendix~\ref{sec:derivations_C}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Comparison of the approximations}
+\section{Results}
+\subsection{Comparison of the approximations}
 \label{sec:comp}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Application to CFHTLenS data}
+\subsection{Application to CFHTLenS data}
 \label{sec:cfhtlens}
@@
 \input{discussion.tex}
+
+\section{Conclusions}
 
@@
 \section{Discussion and comparison to previously published work}
+\label{app:B}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-02-08 cfhtlens.tex
Moved Fig 2 into the applcation to CFHTLenS section Included definition of xi+ Big changes in purple please check and remove purple when you're happy

@@
 \ch{where $J_{0,4} (\ell \theta)$ is the zeroth (for $\xi_+$) or fourth (for $\xi_- $) order Bessel function of the first kind and $P_\gamma(\ell)$ is the shear power spectrum at angular wave number $\ell$ which can be related to the underlying matter power spectrum through equation~\ref{eq:P_ell_limber1} when adopting a first-order extended Limber approximation, or equation~\ref{eq:P_ell_limber2} when adopting a second-order extended Limber approximation \citep[for more details see][and references therein]{miraldaescude:1991, kaiser:1992, bartelmann/schneider:2001}.
-Note that as we have shown in section~\ref{sec:comp} that the second-order extended Limber approximation provides a percent-level precision representation of the full spherical projection, we do not investigate predictions for the two-point shear correlation function using the full spherical projection.
-This is because on a sphere,
-correlation functions cannot be related to the power spectrum by a Hankel transform (e.g. equation~\ref{eqn:xiGG}) as the power spectrum is not defined for non-integer $\ell$.}
+}
+
+\ch{On a sphere, correlation functions cannot be related to the power spectrum by a Hankel transform in equation~\ref{eqn:xiGG}, as the power spectrum is not defined for non-integer $\ell$ \citep[see][for alternative spherical-sky formulae for the two-point correlation function]{2005PhRvD..72b3516C}.
+As we have shown in section~\ref{sec:comp} that the spherical second-order extended Limber approximation provides a percent-level precision representation of the full spherical projection for $\ell > 3$, we do not present predictions for the two-point shear correlation function using the full spherical projection, instead choosing the spherical second-order extended Limber approximation (Ext2Sph) as our `truth' in this case.}
+
+\ch{Figure.~\ref{fig:xi_pm_K16} presents the two-point correlation functions $\xi_+$ (left) and $\xi_-$ (right) using the different cases for the shear power spectrum listed in Table~\ref{tab:cases}.
+The adopted CFHTLenS redshift distribution and fiducial cosmological model are the same as in Figure.~\ref{fig:Cl_cases}.
+}
+
+\begin{figure}
+
+  \begin{center}
+    \resizebox{1.0\hsize}{!}{
+      \includegraphics{figures/xi_p_comp}
+      \includegraphics{figures/xi_m_comp}
+    }
+
+    \resizebox{1.0\hsize}{!}{
+      \includegraphics{figures/xi_p_delta}
+      \includegraphics{figures/xi_m_delta}
+    }
+  \end{center}
+
+  \caption{Shear correlation functions $\xi_+$ (\emph{left}) and $\xi_-$ (\emph{right}).
+    The lower panels shows the relative differences to the case Ext2Sph,  see Table \ref{tab:cases} for the different
+    approximations and their symbols.
+    \mk{Probably remove ExtL1Fl, ExtL2Fl, we already showed for $P_\kappa$ that they are worse than standard
+    Limber.}
+    \ch{ExtL2Fl isn't in the table - so yes agreed to remove that from both plots}
+    \ch{I'd keep the ExtL1Fl, just incase someone is daft enough to do that approximation one day.}
+    %\cite{CFHTLenS-2pt-notomo}; the theoretical predictions correspond to the best-fit parameters with
+    %$\Omega_{\rm m} = 0.279$ and $\sigma_8 = 0.79$, except the red dashed curve with adapts a Planck-best fit
+    %normalisation $\sigma_8 = 0.83$.
+  }
+
+  \label{fig:xi_pm_K16}
+
+\end{figure}
 

### 2017-02-08 limber2.tex
Moved Fig 2 into the applcation to CFHTLenS section Included definition of xi+ Big changes in purple please check and remove purple when you're happy

@@
         See Table \ref{tab:cases} for more details on the different approximations.     
+       \ch{ExtL2Fl isn't in the table - so suggest to remove that from both plots}
         }
@@
   %
-  $2^{\rm st}$-order extended Limber, flat sky & Ext2FlHyb &  (\ref{eq:P_ell_limber1}) + (\ref{eq:P_ell_limber2}) + (iii)
-    & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ & - \\ \hline
-  %
-  $2^{\rm st}$-order extended Limber, spherical & Ext2Sph & (\ref{eq:C_ell_limber1})+(\ref{eq:C_ell_limber2_dr_s})
+  $2^{\rm st}$-order extended Limber, flat sky & ExtL2FlHyb &  (\ref{eq:P_ell_limber1}) + (\ref{eq:P_ell_limber2}) + (iii)
+    & \ch{I think this should be 1?}%$\ellbar^2(\ell, 2)/(\ell+1/2)^4$ 
+    & $\ell+1/2$ & - \\ \hline
+  %
+  $2^{\rm st}$-order extended Limber, spherical & ExtL2Sph & (\ref{eq:C_ell_limber1})+(\ref{eq:C_ell_limber2_dr_s})
     & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ & - \\ \hline
@@
 \renewcommand{\baselinestretch}{1}
-
-In Fig.~\ref{fig:xi_pm_K16} we show the correlation functions using the different cases
-for the shear power spectrum. The redshift distribution and cosmological model are the same 
-as in Fig.~\ref{fig:Cl_cases}.
-
-\begin{figure}
-
-  \begin{center}
-    \resizebox{1.0\hsize}{!}{
-      \includegraphics{figures/xi_p_comp}
-      \includegraphics{figures/xi_m_comp}
-    }
-
-    \resizebox{1.0\hsize}{!}{
-      \includegraphics{figures/xi_p_delta}
-      \includegraphics{figures/xi_m_delta}
-    }
-  \end{center}
-
-  \caption{Shear correlation funtions $\xi_+$ (\emph{left panels}) and $\xi_-$ (\emph{right}).
-    The lower row shows the relative differences to the case Ext2Sph,  see Table \ref{tab:cases} for the different
-    approximations and their symbols.
-    \mk{Probably remove ExtL1Fl, ExtL2Fl, we already showed for $P_\kappa$ that they are worse than standard
-    Limber.}
-    %\cite{CFHTLenS-2pt-notomo}; the theoretical predictions correspond to the best-fit parameters with
-    %$\Omega_{\rm m} = 0.279$ and $\sigma_8 = 0.79$, except the red dashed curve with adapts a Planck-best fit
-    %normalisation $\sigma_8 = 0.83$.
-  }
-
-  \label{fig:xi_pm_K16}
-
-\end{figure}
 

### 2017-02-08 limber2.tex
Started expanding the discussion of Fig 1 Now about to start all the meetings for the day Back online to work on this tomorrow :) C

@@
 
-In Fig.~\ref{fig:Cl_cases} we plot the full shear power spectrum and some of
-the approximations. The redshift distribution corresponds to CFHTLenS
-\cite{CFHTLenS-2pt-notomo}. \mk{NL power spectrum parameters.}
-For $\ell > 100$ all power spectra coincide to
-better than one percent. The standard first-order Limber approximation is
-better than 10\% but for the lowest $\ell$, but converges slowly to the true
-projection to higher $\ell$. For the extended Limber approximations, despite
-slightly worse for $\ell < 10$ in the hybrid cases, the errors with respect to
-the true power spectrum decrease much faster, with $\ell^{-2}$. Including the
+In Fig.~\ref{fig:Cl_cases} we plot the full spherical projection of the shear power spectrum in comparison to shear power spectra derived assuming
+the range of different approximations listed in Table~\ref{tab:Cl_cases}.  The adopted redshift distribution corresponds to CFHTLenS
+\cite{CFHTLenS-2pt-notomo} and we assume a flat $\Lambda$CDM cosmology with $\Omega=X$, $\Omega_b=$, $\sigma_8=X$, $H_0=X$, $n_s=X$. 
+For $\ell > 100$ we find that all shear power spectra predictions agree with the full spherical solution to better than one percent, with the majority of the approximations tested accurate to better than 0.1 per cent.
+
+Considering first the flat-sky cases, the standard first-order Limber approximation, (L1Fl), that was adopted for all pre-2014 CFHTLenS analyses, we find to be 
+accurate to better than 10\% for $\ell>3$, converging slowly to the true projection with percent level predicison at $\ell>100$. 
+For the extended Limber approximations `hybrid' cases (ExtL1FlHyb and ExtL2FlHyb), despite decreased accuracy
+for $\ell < 8$ in comparison to the standard first-order Limber case, the errors with respect to
+the true power spectrum decrease much faster, as $\ell^{-2}$, such that percent-level precision is reached at $\ell>15$.
+The first-order extended Limber approximation `hybrid' cases (ExtL1FlHyb) was adopted by both \citet{joudaki/etal:2016} and \cite{KiDS-450}\footnote{We confirm that there is a typographical error in equation 4 of \cite{KiDS-450} which should include the extra term of `+0.5' in $\nu(\ell)$ that was incorporated in the cosmological analysis.}
+
+The outlier in the flat-sky cases is the extended Limber approximation (ExtL1Fl) which performs relatively poorly, and
+reach 10\% precision only at $\ell > 100$.   To our knowledge this form of the flat-sky approximation has not been used in cosmic shear studies to date.
+
+Including the
 spherical prefactor decreases the difference by a factor of a few for $\ell <
@@
 does not scale as expected with $\ell^{-4}$, but rather with $\ell^{-2}$. This
-might be due to numercical noise that creates residual terms at the ${\cal
+might be due to numerical noise that creates residual terms at the ${\cal
 O}(\ell^{-2})$ which do not cancel. Also note that the numerical noise for

### 2017-02-08 cfhtlens.tex
MK edits

--- 2017-02-08 cfhtlens.tex
@@
 \cite{2003MNRAS.341.1311S} as the original \cite{CFHTLenS-2pt-notomo} analysis.
+We use the real-space two-point correlation function of shear, which in flat-sky
+coordinates is a Hankel transform of the shear power spectrum,
+%
+\begin{eqnarray}
+  \xi_+(\theta) 
+  % &
+  = \frac 1 {2\pi} \int {\rm d} \ell \, \ell {\rm J}_0(\ell
+   \theta)
+  P^\gamma(\ell);
+  \quad
+  %\nonumber \\
+   %
+   \xi_-(\theta)
+  %&
+  = \frac 1 {2\pi} \int
+   {\rm d} \ell \, \ell {\rm J}_4(\ell \theta)
+  P^\gamma(\ell).
+  %
+   \label{eqn:xiGG}
+\end{eqnarray}
+%
+As in \cite{CFHTLenS-2pt-notomo} we fit both components $\xi_+$ and $\xi_-$
+between angular scales $\theta = 0.8$ and $350$ arc minutes, and use a $N$-body
+simulation estimate of the non-Gaussian covariance including the
+cross-covariance between both components. The Bayesian Monte-Carlo parameter
+sampling is performed using the publically available software
+\textsc{CosmoPMC}\footnote{\texttt{www.cosmopmc.info}} \citep{WK09,KWR10}. The
+cosmological modelling part including the various lensing projections are
+performed with the library
+\textsc{nicaea}\footnote{\texttt{http://www.cosmostat.org/software/nicaea}}
+\citep{KB09}. \mk{Check reference.}
+
 For a first-order standard Limber flat-sky approximation (L1Fl) we find
-$\sigma_8 (\Omega_{\rm m}/0.27)^{0.6} =0.787^{+0.031}_{-0.033}$. For a
-second-order extended Limber flat-sky approximation we find $\sigma_8
-(\Omega_{\rm m}/0.27)^{0.6} =X^{+X}_{-X}$, a negligible change of
-$X\sigma$.
+$\sigma_8 (\Omega_{\rm m}/0.27)^{0.6} =0.787^{+0.031}_{-0.033}$, the same
+result that was published in \cite{CFHTLenS-2pt-notomo}. Using the second-order
+extended Limber flat-sky approximation results in $\sigma_8 (\Omega_{\rm
+m}/0.27)^{0.6} =X^{+X}_{-X}$, a negligible change of $X\sigma$.
 
@@
 correlation functions cannot be related to the power spectrum by a Hankel
-transform (e.g. equation~\ref{eqn:xiGG}) as the power spectrum is not defined
-for non-integer $\ell$. In Figure~\ref{fig:Cl_xi}, however, we show that this
+transform (\ref{eqn:xiGG}) as formally the power spectrum is not defined for
+non-integer $\ell$. In Fig.~\ref{fig:Cl_cases}, however, we show that this
 chosen version of a flat-sky approximation serves to exacerbate the tension in
@@
 solution in the Limber approximated case.  This is not the case when
-considering the standard $T_\ell = 1$ flat-sky approximation that has been used
-in the majority of cosmic shear studies to date.  We would therefore argue that
-it is more appropriate to use a $T_\ell = 1$ flat-sky approximation when
-carrying out a `Full' non-Limber analysis of the shear correlation function
+considering the standard and extended hybrid flat-sky Limber approximation
+(both for which $p(\ell) = 1$, which corresponds to $T_\ell$ in
+\citet{2016arXiv161104954K}, see Sect.~\ref{sec:Limber_flat_sky}) that has been
+used in the majority of cosmic shear studies to date.  We would therefore argue
+that it is more appropriate to use a $p(\ell) = 1$ flat-sky approximation when
+carrying out a `full' non-Limber analysis of the shear correlation function
 obtained from the Hankel transformation (equation~\ref{eqn:xiGG}). We need to
-take a decision here about what to use.  Do we need a Full Flat case in Table
-1, and to demonstrate that Ext2Fl is very close to FullFl?  And then use Ext2Fl
-as our "truth" for the correlation function?}
+take a decision here about what to use. Do we need a Full Flat case in Table 1,
+and to demonstrate that Ext2Fl is very close to FullFl?  And then use Ext2Fl as
+our "truth" for the correlation function?}
 

### 2017-02-08 discussion.tex
MK edits

--- 2017-02-08 discussion.tex
@@
 including the shear correlation function, $\xi_\pm$, the aperture-mass
-dispersion, $\langle M_ {\rm ap}^2 \rangle2$ \citep{1998MNRAS.296..873S}, and
+dispersion, $\langle M_ {\rm ap}^2 \rangle$ \citep{1998MNRAS.296..873S}, and
 the COSEBIs, $E_n$ \citep{COSEBIs}.  These statistics are linearly related to
-the shear power spectrum in the flat-sky approximation via integrals of the form (omitting tomographic indices),
+the shear power spectrum in the flat-sky approximation via integrals of the
+form (omitting tomographic indices),
 %

### 2017-02-08 limber2.tex
MK edits

--- 2017-02-08 limber2.tex
@@
 and the full projection are publicly available within the package
-\texttt{nicaea} at \texttt{http://www.cosmostat.org/software/nicaea}.
+\textsc{nicaea} at \texttt{http://www.cosmostat.org/software/nicaea}.
 
@@
 modifications to gravity.  As such it is the primary science goal of several
-current (KiDS, DES, HSC\footnote{KiDS: \href={http://kids.strw.leidenuniv.nl}, DES: \href={http://www.darkenergysurvey.org}, HSC: \href={http://hsc.mtk.nao.ac.jp/ssp/}})
-and future (Euclid, LSST, WFIRST\footnote{Euclid: \href={http://sci.esa.int/euclid}, LSST: \href={http://www.lsst.org}, WFIRST: \href={http://wfirst.gsfc.nasa.gov}}) surveys.
-%(Kilo-Degree Survey, KiDS \citet{kuijken/etal:2015}, Dark Energy Survey, DES, \citet{abbott/etal:2016}, Hyper-Suprime Camera Survey, HSC\footnote{HSC; \href={http://hsc.mtk.nao.ac.jp/ssp/}}) and future (Euclid, \citet{2011arXiv1110.3193L}, LSST, \citet{chang/etal:2013}, WFIRST\footnote{WFIRST; \href={http://wfirst.gsfc.nasa.gov}}) large-scale surveys.
+current (KiDS, HSC, DES) and future (Euclid, LSST, WFIRST) large-scale surveys.
 Interest in the results from these surveys is high as statistically significant
@@
 
-In the era of the upcoming large-scale surveys that will provide measurements of
+In the era of the upcoming large surveys that will provide measurements of
 cosmic shear with unprecedented precision, one needs to revisit the theoretical
-predictions of the observables to ensure that the accuracy of the
-models meet the accuracy of the upcoming data. In this paper, we examine the widely used Limber
+model predictions of the observables to ensure that the accuracy of the
+models meet the upcoming data. In this paper, we examine the widely used Limber
 approximation for the projected weak-lensing power spectrum. We consider
@@
 projection as well as first- and second-order Limber approximation. We show
-that the second-order Limber approximation is an accurate representation of the full projection, with better than percent level precision for scale $\ell > 3$. 
-Since this approximation involves only 1D integrals over the matter power spectrum, it is very fast to
+that the latter is an excellent approximation of the full projection. Since it
+involves only 1D integrals over the matter power spectrum, it is very fast to
 calculate numerically and can readily employed in Monte-Carlo sampling methods
@@
 In section~\ref{sec:L2} we derive weak lensing observables using a second-order limber approximation first introduced by \citet{2008PhRvD..78l3506L}.
-We compare the shear power spectrum and commonly-used two-point shear correlation function for the full solution to a range of different approximations in section~\ref{sec:comp}, providing cosmological constraints for each case using CFHTLenS data from \citet{CFHTLenS-2pt-notomo} in section~\ref{sec:cfhtlens}.
-This paper draws from several sources of literature which have previously reviewed the accuracy of the Limber approximation for weak lensing studies, namely \citet{2008PhRvD..78d3002S,2012PhRvD..86b3001B, 2012MNRAS.422.2854G, 2016arXiv161104954K}.
-We present a discussion and comparison of our results to these papers in Appendix~\ref{app:B}.
+We compare the shear power spectrum and commonly-used two-point shear correlation function for a range of different approximations in section~\ref{sec:comp}, providing cosmological constraints for each case using CFHTLenS data from \citet{CFHTLenS-2pt-notomo} in section~\ref{sec:cfhtlens}.
+This paper draws from several sources of literature which have previously reviewed the accuracy of the Limber approximation for weak lensing studies, namely \citet{2008PhRvD..78d3002S,2012PhRvD..86b3001B, 2012MNRAS.422.2854G}.
 
@@
 compute lensing power spectra for a spherical case, and in the flat-sky
-approximation. For completeness we provide a derivations of the weak lensing power spectra in Appendix~\ref{sec:derivations_C}.
+approximation. Derivations for those expressions can be found in the appendix.
 
@@
 %
-where for convenience we defined the normalisation constant $\pref$ as
+where ${\rm j}_\ell$ it the spherical Bessel function of order $\ell$. For
+convenience we defined the normalisation constant $\pref$ as
 %
@@
 %
-The spherical prefactor for the full projection power spectrum is $p(\ell) =
+The spherical prefactor for the full projection power spectrum is $p(\ell) :=
 \ellbar^2(\ell, 2)$, which will be modified under flat-sky and Limber
@@
 %
-in eq.~(\ref{eq:C_ell_full}). Next, \cite{2008PhRvD..78l3506L} solve
-integrals of the form
+in eq.~(\ref{eq:C_ell_full}), where ${\rm J}_\ell$ is the first-kind Bessel
+function of order $\ell$. Next, \cite{2008PhRvD..78l3506L} solve integrals of
+the form
 %
@@
 \subsection{Flat sky}
+\label{sec:Limber_flat_sky}
 
@@
 %
-Different further approximations are commonly made for the prefactor $p(\ell) = \ell^4/\nu^4$ and $\nu(\ell)$.
+Different further approximations are commonly made for the prefactor $p(\ell) = \ell^4/\nu^4$ and $\nu(\ell)$:
 %
@@
     Until recently, i.e.~for all pre-2014 CFHTlenS results, this was the approximation of choice.
-  \item $p(\ell) = \ell^4/\nu^4(\ell)$ with $\nu(\ell) = \ell + 1/2$. This corresponds to the extended Limber
-    approximation; however the following case is typically employed:
+  \item $p(\ell) = \ell^4/(\ell + 1/2)^4$. This corresponds to the extended Limber
+    approximation with $\nu(\ell) = \ell + 1/2$; however the following case is typically employed:
   \item $p(\ell) = 1$, but as the argument of the 3D power spectrum $\nu = \ell + 1/2$. This is a hybrid between
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
-\subsection{Comparison of the approximations}
+\section{Comparison of the approximations}
 \label{sec:comp}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Application to CFHTLenS data}
+\section{Application to CFHTLenS data}
 \label{sec:cfhtlens}
@@
 \input{discussion.tex}
-
-\section{Conclusions}
 
@@
 \section{Discussion and comparison to previously published work}
-\label{app:B}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-02-08 limber2.tex
Finished the discussion of Fig 1 @MK - what is the difference in compute time for full vs 2nd order?

--- 2017-02-08 limber2.tex
@@
 %
-For a flat Universe, this is given by
+For a zero-curvature Universe, this is given by
 %
@@
 Considering first the flat-sky cases, the standard first-order Limber approximation, (L1Fl), that was adopted for all pre-2014 CFHTLenS analyses, we find to be 
-accurate to better than 10\% for $\ell>3$, converging slowly to the true projection with percent level predicison at $\ell>100$. 
+accurate to better than 10\% for $\ell>3$, converging slowly to the true projection with percent level precison at $\ell>100$. 
 For the extended Limber approximations `hybrid' cases (ExtL1FlHyb and ExtL2FlHyb), despite decreased accuracy
@@
 the true power spectrum decrease much faster, as $\ell^{-2}$, such that percent-level precision is reached at $\ell>15$.
-The first-order extended Limber approximation `hybrid' cases (ExtL1FlHyb) was adopted by both \citet{joudaki/etal:2016} and \cite{KiDS-450}\footnote{We confirm that there is a typographical error in equation 4 of \cite{KiDS-450} which should include the extra term of `+0.5' in $\nu(\ell)$ that was incorporated in the cosmological analysis.}
+The first-order extended Limber approximation `hybrid' cases (ExtL1FlHyb) was adopted by both \citet{joudaki/etal:2016} and \cite{KiDS-450}\footnote{We confirm that there is a typographical error in equation 4 of \cite{KiDS-450} which should include the extra term of `+0.5' in $\nu(\ell)$ that was incorporated in the cosmological analysis.}.
 
 The outlier in the flat-sky cases is the extended Limber approximation (ExtL1Fl) which performs relatively poorly, and
-reach 10\% precision only at $\ell > 100$.   To our knowledge this form of the flat-sky approximation has not been used in cosmic shear studies to date.
-
-Including the
-spherical prefactor decreases the difference by a factor of a few for $\ell <
-5$. Going to second-order yields percent accuracy down to $\ell = 4$.
-
-\mk{Not sure whether the following comments should be left in the draft.} One
-notes that the difference between the full projection and second-order Limber
-does not scale as expected with $\ell^{-4}$, but rather with $\ell^{-2}$. This
-might be due to numerical noise that creates residual terms at the ${\cal
-O}(\ell^{-2})$ which do not cancel. Also note that the numerical noise for
-$\ell > 20$ is due to numerical integration errors for the full projection.
-
-The flat extended Limber approximations (ExtL1Fl and ExtL2Fl) perform relatively poorly, and
-reach 10\% precision only at $\ell > 100$.
+reaches 10\% precision only at $\ell > 100$.
+To our knowledge this form of the flat-sky approximation has not been used in any cosmic shear studies to date, and should not be used in any future studies given these results.
+The poor behaviour of this case, in comparison with the `hybrid' case, (e.g ExtL1FlHyb) can be understood by considering Taylor expansions of the different pre-factors.
+The spherical pre-factor,
+\begin{equation}
+p(\ell) = \frac{(\ell+2)(\ell+1)\ell(\ell-1)}{(\ell + 0.5)^4} = 1-{5\over 2\ell^2} +{\cal O}(\ell^{-3}) \, .
+\end{equation}
+can be compared to the flat-sky extended Limber pre-factor
+\begin{equation}
+p(\ell) = \ell^4 / (\ell + 0.5)^4 = 1-{2\over \ell}+{5\over 2\ell^2} +{\cal O}(\ell^{-3}) \, , 
+\end{equation} 
+showing it to be more deviant from the full spherical solution, than the `hybrid' $p(\ell) = 1$ case.
+
+Considering now the spherical-sky cases, we find that including the spherical pre-factor decreases the difference between the extended Limber approximated cases (ExtL1Sph and ExtL2Sph) and the full spherical solution by a factor of a few for $\ell < 5$.
+We find that using the spherical-sky second-order extended Limber approximation yields percent accuracy down to $\ell > 3$.
+The numerical calculation of the second-order extended Limber approximation is a factor of \ch{X} faster than the calculation of the full spherical solution.
+We note that the noise seen in the right panel of Fig.~\ref{fig:Cl_cases} is due to numerical noise arising from numerical integration errors the full spherical solution calculation for
+$\ell > 20$.  Increasing numerical precision would increase the calculation time still further, relative to the  second-order extended Limber calculation.
+
+%\mk{Not sure whether the following comments should be left in the draft.} One
+%notes that the difference between the full projection and second-order Limber
+%does not scale as expected with $\ell^{-4}$, but rather with $\ell^{-2}$. %
+%This
+%might be due to numerical noise that creates residual terms at the ${\cal
+%O}(\ell^{-2})$ which do not cancel. Also note that the numerical noise for
+%$\ell > 20$ is due to numerical integration errors for the full projection.
 

### 2017-02-08 cfhtlens.tex

@@
+%\subsubsection{CFHTLenS updates and advances since 2014}
+
 The Canada-France-Hawaii Telescope Lensing Survey (CFHTLenS) represented a
@@
 biases would be {\it reduce} the recovered amplitude of $\sigma_8$ by $\sim
-4$\%. }
+4$\%.}
 %
-\item{ The CFHTLenS tomographic cosmological analysis was then revisited by
+\item{The CFHTLenS tomographic cosmological analysis was then revisited by
 \citet{joudaki/etal:2016} in order to include a full redshift error analysis
@@
 
+%\subsubsection{Cosmological analysis setup}
+
 In this work, we focus on the weak-lensing power spectrum projection, and
 assess the impact of various approximations on cosmological constraints from
-CFHTLenS. We re-analyse the 2D CFHTLenS data from \cite{CFHTLenS-2pt-notomo},
-adopting the same priors and non-linear power spectrum corrections\footnote{As
-an example of significant effects that need to be accounted for using the
-revised non-linear power spectrum of \cite{2012ApJ...761..152T} in place of
-\cite{2003MNRAS.341.1311S} results in a decrease of $0.6 \sigma$ with $\sigma_8
-(\Omega_{\rm m}/0.27)^{0.6} =0.768^{+0.029}_{-0.031}$.} from
-\cite{2003MNRAS.341.1311S} as the original \cite{CFHTLenS-2pt-notomo} analysis.
-We use the real-space two-point correlation function of shear, which in flat-sky
-coordinates is a Hankel transform of the shear power spectrum,
-%
-\begin{eqnarray}
-  \xi_+(\theta) 
-  % &
-  = \frac 1 {2\pi} \int {\rm d} \ell \, \ell {\rm J}_0(\ell
-   \theta)
-  P^\gamma(\ell);
-  \quad
-  %\nonumber \\
-   %
-   \xi_-(\theta)
-  %&
-  = \frac 1 {2\pi} \int
-   {\rm d} \ell \, \ell {\rm J}_4(\ell \theta)
-  P^\gamma(\ell).
-  %
-   \label{eqn:xiGG}
-\end{eqnarray}
-%
-As in \cite{CFHTLenS-2pt-notomo} we fit both components $\xi_+$ and $\xi_-$
-between angular scales $\theta = 0.8$ and $350$ arc minutes, and use a $N$-body
-simulation estimate of the non-Gaussian covariance including the
-cross-covariance between both components. The Bayesian Monte-Carlo parameter
-sampling is performed using the publically available software
-\textsc{CosmoPMC}\footnote{\texttt{www.cosmopmc.info}} \citep{WK09,KWR10}. The
-cosmological modelling part including the various lensing projections are
-performed with the library
-\textsc{nicaea}\footnote{\texttt{http://www.cosmostat.org/software/nicaea}}
-\citep{KB09}. \mk{Check reference.}
+CFHTLenS. For consistency with the original analysis
+\citep{CFHTLenS-2pt-notomo}, we adopt the same priors and non-linear power
+spectrum corrections from \cite{2003MNRAS.341.1311S}.
+
+We re-analyse the 2D CFHTLenS measurement of the two-point shear correlation
+function $\xi_\pm(\theta)$ from \cite{CFHTLenS-2pt-notomo}, defined in
+(\ref{eqn:xiGG}). As in \cite{CFHTLenS-2pt-notomo} we fit both components
+$\xi_+$ and $\xi_-$ between angular scales $\theta = 0.8$ and $350$ arc
+minutes, and use a $N$-body simulation estimate of the non-Gaussian covariance
+including the cross-covariance between both components. The Bayesian
+Monte-Carlo parameter sampling is performed using the publically available
+software \textsc{CosmoPMC}\footnote{\texttt{www.cosmopmc.info}}
+\citep{WK09,KWR10}. The cosmological modelling part including the various
+lensing projections are performed with the library
+\textsc{nicaea}\footnote{\texttt{http://www.cosmostat.org/software/nicaea}}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsubsection{Cosmological parameter results}
+\label{ref:cosmo_results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$ for the various approximations to the
-lensing power spectrum projections listed in Table~\ref{tab:cases}
+lensing power spectrum projections listed in Table~\ref{tab:cases} Note again
+that these values do not represent the state-of-the-art cosmological results,
+since many of the above listed analysis advancements made since 2013 have not
+been taken into account. As an example of a significant effect, when using the
+revised non-linear power spectrum of \cite{2012ApJ...761..152T} in place of
+\cite{2003MNRAS.341.1311S}, there is a decrease of $0.6 \sigma$ with $\sigma_8
+(\Omega_{\rm m}/0.27)^{0.6} =0.768^{+0.029}_{-0.031}$.
 
@@
 
-  \begin{tabular}{lcc} \hline
-  ID         & $\sigma_8 (\Omega_{\rm m}/0.27)^{0.6}$ & $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$\\ \hline
-  L1Fl       & $0.787^{+0.031}_{-0.033}$ & $0.739^{+0.029}_{-0.031}$ \\
-  ExtL1FlHyb & $0.788^{+0.031}_{-0.033}$ & $0.740^{+0.029}_{-0.031}$ \\
-  ExtL2Sph   & $0.789^{+0.031}_{-0.032}$ & $0.740^{+0.029}_{-0.030}$ \\ \hline
+  \begin{tabular}{lccc} \hline
+  ID         & $\sigma_8 (\Omega_{\rm m}/0.27)^{0.6}$ & $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$ & Comment \\ \hline
+  L1Fl       & $0.787^{+0.031}_{-0.033}$ & $0.739^{+0.029}_{-0.031}$ & Used for pre-2014 CFHTLenS \\
+  ExtL1Fl    & $x^{+y}_{-z}$ & $x^{+y}_{-z}$ & Depreciated \\
+  ExtL1FlHyb & $0.788^{+0.031}_{-0.033}$ & $0.740^{+0.029}_{-0.031}$ & Used for post-2014 CFHTLenS, KiDS \\
+  ExtL2FlHyb & $x^{+y}_{-z}$ & $x^{+y}_{-z}$ & Best flat-sky approximation \\
+  ExtL2Sph   & $0.789^{+0.031}_{-0.032}$ & $0.740^{+0.029}_{-0.030}$ & Best approximation but mixing with flat-sky Hankel transform \\ \hline
   \end{tabular}

### 2017-02-08 limber2.tex

--- 2017-02-08 limber2.tex
@@
   \ellbar(\ell, s) = \sqrt{\frac{(\ell + s)!}{(\ell - s)!}}.
+  \label{eq:ellbar}
 \end{equation} 
@@
 %
-Different further approximations are commonly made for the prefactor $p(\ell) = \ell^4/\nu^4$ and $\nu(\ell)$.
+Different further approximations are commonly made for the prefactor $p(\ell) = \ell^4/\nu^4$ and $\nu(\ell)$:
 %
 \begin{enumerate}
-  \item $p(\ell) = 1$, this corresponds to setting $\nu(\ell) = \ell$, and is the standard Limber approximation.
+  \item $p(\ell) = 1$, this corresponds to $\nu(\ell) = \ell$, which is the \emph{standard} Limber approximation.
     Until recently, i.e.~for all pre-2014 CFHTlenS results, this was the approximation of choice.
-  \item $p(\ell) = \ell^4/\nu^4(\ell)$ with $\nu(\ell) = \ell + 1/2$. This corresponds to the extended Limber
-    approximation; however the following case is typically employed:
-  \item $p(\ell) = 1$, but as the argument of the 3D power spectrum $\nu = \ell + 1/2$. This is a hybrid between
+  \item $p(\ell) = \ell^4/(\ell + 1/2)^4$. This corresponds to the \emph{extended} Limber
+    approximation with $\nu(\ell) = \ell + 1/2$; however the following case is typically employed:
+  \item $p(\ell) = 1$, but as the argument of the 3D power spectrum $\nu = \ell + 1/2$. This is
+    a \emph{hybrid} between
     standard and extended Limber approximation, and was used in \cite{KiDS-450,joudaki/etal:2016}. As is shown
-    later, this is a much better approximation than case 2.
+    later, this is a much better approximation to the full projection than case (ii).
 \end{enumerate}
 
+% (i)  Standard Flat
+% (ii) Extended Flat
+% (iii) Extended Flat Hybrid
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Results}
-\subsection{Comparison of the approximations}
+\label{sec:results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Comparison of the approximations for the lensing power spectrum}
 \label{sec:comp}
@@
 
-In Fig.~\ref{fig:Cl_cases} we plot the full spherical projection of the shear power spectrum in comparison to shear power spectra derived assuming
-the range of different approximations listed in Table~\ref{tab:Cl_cases}.  The adopted redshift distribution corresponds to CFHTLenS
-\cite{CFHTLenS-2pt-notomo} and we assume a flat $\Lambda$CDM cosmology with $\Omega=X$, $\Omega_b=$, $\sigma_8=X$, $H_0=X$, $n_s=X$. 
-For $\ell > 100$ we find that all shear power spectra predictions agree with the full spherical solution to better than one percent, with the majority of the approximations tested accurate to better than 0.1 per cent.
-
-Considering first the flat-sky cases, the standard first-order Limber approximation, (L1Fl), that was adopted for all pre-2014 CFHTLenS analyses, we find to be 
-accurate to better than 10\% for $\ell>3$, converging slowly to the true projection with percent level predicison at $\ell>100$. 
-For the extended Limber approximations `hybrid' cases (ExtL1FlHyb and ExtL2FlHyb), despite decreased accuracy
-for $\ell < 8$ in comparison to the standard first-order Limber case, the errors with respect to
-the true power spectrum decrease much faster, as $\ell^{-2}$, such that percent-level precision is reached at $\ell>15$.
-The first-order extended Limber approximation `hybrid' cases (ExtL1FlHyb) was adopted by both \citet{joudaki/etal:2016} and \cite{KiDS-450}\footnote{We confirm that there is a typographical error in equation 4 of \cite{KiDS-450} which should include the extra term of `+0.5' in $\nu(\ell)$ that was incorporated in the cosmological analysis.}
-
-The outlier in the flat-sky cases is the extended Limber approximation (ExtL1Fl) which performs relatively poorly, and
-reach 10\% precision only at $\ell > 100$.   To our knowledge this form of the flat-sky approximation has not been used in cosmic shear studies to date.
-
-Including the
-spherical prefactor decreases the difference by a factor of a few for $\ell <
-5$. Going to second-order yields percent accuracy down to $\ell = 4$.
-
-\mk{Not sure whether the following comments should be left in the draft.} One
+In Fig.~\ref{fig:Cl_cases} we plot the full spherical projection of the shear
+power spectrum in comparison to shear power spectra derived assuming the range
+of different approximations listed in Table \ref{tab:cases}.  The adopted
+redshift distribution corresponds to CFHTLenS \cite{CFHTLenS-2pt-notomo} and we
+assume their best-fit flat $\Lambda$CDM cosmology with $\Omega=0.279$,
+$\Omega_b=0.046$, $\sigma_8=0.70$, $H_0=0.701$, $n_s=0.96$. For $\ell > 100$ we
+find that all shear power spectra predictions agree with the full spherical
+solution to better than one percent, with the majority of the approximations
+tested accurate to better than 0.1 per cent.
+
+Considering first the flat-sky cases, the standard first-order Limber
+approximation (L1Fl), that was adopted for all pre-2014 CFHTLenS analyses, we
+find to be accurate to better than 10\% for $\ell>3$, converging slowly to the
+true projection with percent level precison at $\ell>100$. For the extended
+Limber approximations `hybrid' cases (ExtL1FlHyb and ExtL2FlHyb), despite
+decreased accuracy for $\ell < 8$ in comparison to the standard first-order
+Limber case, the errors with respect to the true power spectrum decrease much
+faster, as $\ell^{-2}$, such that percent-level precision is reached at
+$\ell>15$.  The first-order extended Limber approximation `hybrid' case
+(ExtL1FlHyb) was adopted by both \citet{joudaki/etal:2016} and
+\cite{KiDS-450}\footnote{We confirm that there is a typographical error in
+equation 4 of \cite{KiDS-450} which should include the extra term of `+0.5' in
+$\nu(\ell)$ that was incorporated in the cosmological analysis.}
+
+The outlier in the flat-sky cases is the extended Limber approximation
+(ExtL1Fl) which performs relatively poorly, and reach 10\% precision only at
+$\ell > 100$. To our knowledge this form of the flat-sky approximation has not
+been used in cosmic shear studies to date. The same slow convergence can be
+observed for the corresponding second-order flat case, ExtL2Fl.
+
+Including the spherical prefactor (the case ExtL1Sph) decreases the difference
+by a factor of a few for $\ell < 5$. Going to second-order (ExtL2Sph) yields
+percent accuracy down to $\ell = 4$.
+
+\mk{Not sure whether this following paragraph should be left in the draft: One
 notes that the difference between the full projection and second-order Limber
@@
 O}(\ell^{-2})$ which do not cancel. Also note that the numerical noise for
-$\ell > 20$ is due to numerical integration errors for the full projection.
-
-The flat extended Limber approximations (ExtL1Fl and ExtL2Fl) perform relatively poorly, and
-reach 10\% precision only at $\ell > 100$.
+$\ell > 20$ is due to numerical integration errors for the full projection.}
 
@@
         See Table \ref{tab:cases} for more details on the different approximations.     
-       \ch{ExtL2Fl isn't in the table - so suggest to remove that from both plots}
         }
@@
 % limber2_la08      ExtL2Fl
-% limber2_la08_hyb  ExtL2Fl
+% limber2_la08_hyb  ExtL2FlHyb
 % limber2_la08_sph  ExtL2Sph
@@
   %
-  $2^{\rm st}$-order extended Limber, flat sky & ExtL2FlHyb &  (\ref{eq:P_ell_limber1}) + (\ref{eq:P_ell_limber2}) + (iii)
-    & \ch{I think this should be 1?}%$\ellbar^2(\ell, 2)/(\ell+1/2)^4$ 
+  $2^{\rm st}$-order extended Limber, flat sky & ExtL2Fl &  (\ref{eq:P_ell_limber1}) + (\ref{eq:P_ell_limber2}) + (iii)
+    & $\ell^4/(\ell+1/2)^4$ 
+    & $\ell+1/2$ & - \\ \hline
+  %
+  $2^{\rm st}$-order extended Limber, hybrid, flat sky & ExtL2FlHyb &  (\ref{eq:P_ell_limber1}) + (\ref{eq:P_ell_limber2}) + (iii)
+    & $1$ 
     & $\ell+1/2$ & - \\ \hline
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Effects on the shear correlation function}
+\label{sec:comp_xi}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Most cosmic shear analysis to date have been performed on real-space
+correlation statistics, since these can be measured direcaly from an observed
+galaxy shape catalogue. The basic quantity is the two-point correlation
+function \citep{miraldaescude:1991}, which is given by
+%
+\begin{eqnarray}
+  \xi_+(\theta) 
+  % &
+  = \frac 1 {2\pi} \int {\rm d} \ell \, \ell {\rm J}_0(\ell
+   \theta)
+  P^\gamma(\ell);
+  \quad
+  %\nonumber \\
+   %
+   \xi_-(\theta)
+  %&
+  = \frac 1 {2\pi} \int
+   {\rm d} \ell \, \ell {\rm J}_4(\ell \theta)
+  P^\gamma(\ell).
+  %
+   \label{eqn:xiGG}
+\end{eqnarray}
+%
+where ${\rm J}_\nu$ first-kind Bessel function of order $\nu$. The flat-sky
+shear power spectrum $P^\gamma$ an be related to the underlying matter power
+spectrum through equation \ref{eq:P_ell_limber1} when adopting a first-order
+extended Limber approximation, or equation~\ref{eq:P_ell_limber2} when adopting
+a second-order extended Limber approximation \citep[for more details see][and
+references therein]{miraldaescude:1991, kaiser:1992,
+bartelmann/schneider:2001}.
+
+On a sphere, correlation functions cannot be related to the power spectrum by a
+Hankel transform in equation~\ref{eqn:xiGG}, as the spherical power spectrum is
+formally not defined for non-integer $\ell$ \citep[see][for alternative
+spherical-sky formulae for the two-point correlation
+function]{2005PhRvD..72b3516C}. In particular, the spherical Bessel functions
+necessary to compute the full projection (\ref{eq:C_ell_full}) is defined only
+for integer order $\ell$. \mk{Is this really true?}
+
+However, in the Limber approximations the Bessel functions expanded to by
+polynomials, allowing for arbitrary wave modes $\ell$. The spherical prefactor
+$\ellbar(\ell, 2)$ (\ref{eq:ellbar}) can be generalised to non-integer
+arguments and is positive for $\ell \le 2$. We can thus use the spherical power
+spectrum in the Limber approximations for the Hankel transformation to compute
+the two-point correlation functions, This is not entirely consistent, but
+serves the purpose of comparison to the flat-sky case.
+
+In addition, as we have shown in section~\ref{sec:comp} that the spherical
+second-order extended Limber approximation provides a percent-level precision
+representation of the full spherical projection for $\ell > 3$, we do not
+present predictions for the two-point shear correlation function using the full
+spherical projection, instead choosing the spherical second-order extended
+Limber approximation (Ext2Sph) as our \mk{reference} in this case.
+
+Figure.~\ref{fig:xi_pm_K16} presents the two-point correlation functions
+$\xi_+$ (left) and $\xi_-$ (right) using the different cases for the shear
+power spectrum listed in Table~\ref{tab:cases}. The adopted CFHTLenS redshift
+distribution and fiducial cosmological model are the same as in
+Figure.~\ref{fig:Cl_cases}. As is clear by the red dotted curve, using the
+Planck cosmology \citep{2015arXiv150201589P} induces a much larger change in
+the amplitude of the shear correlation function than the different projection
+methods.
+
+\begin{figure}
+
+  \begin{center}
+    \resizebox{1.0\hsize}{!}{
+      \includegraphics{figures/xi_p_comp}
+      \includegraphics{figures/xi_m_comp}
+    }
+
+    \resizebox{1.0\hsize}{!}{
+      \includegraphics{figures/xi_p_delta}
+      \includegraphics{figures/xi_m_delta}
+    }
+  \end{center}
+
+  \caption{Shear correlation functions $\xi_+$ (\emph{left}) and $\xi_-$ (\emph{right}).
+    The lower panels shows the relative differences to the case ExtL2Sph,  see Table \ref{tab:cases} for the different
+    approximations and their symbols.
+    The theoretical model corresponds to the CFHTLenS best-fit parameters with
+    $\Omega_{\rm m} = 0.279$, $h=0.701$, and $\sigma_8 = 0.79$ \citep{2015arXiv150201589P},
+    except the red dashed curve with adapts a Planck-best fit
+    cosmology with $\Omega_{\rm m} = 0.3$, $h=0.67$ and $\sigma_8 = 0.83$ \citep{2015arXiv150201589P}.
+  }
+
+  \label{fig:xi_pm_K16}
+
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Application to CFHTLenS data}
@@
 \input{cfhtlens.tex}
+
 \input{discussion.tex}

### 2017-02-08 limber2.tex

@@
 
-In Fig.~\ref{fig:Cl_cases} we plot the full spherical projection of the shear
-power spectrum in comparison to shear power spectra derived assuming the range
-of different approximations listed in Table \ref{tab:cases}.  The adopted
-redshift distribution corresponds to CFHTLenS \cite{CFHTLenS-2pt-notomo} and we
-assume their best-fit flat $\Lambda$CDM cosmology with $\Omega=0.279$,
-$\Omega_b=0.046$, $\sigma_8=0.70$, $H_0=0.701$, $n_s=0.96$. For $\ell > 100$ we
-find that all shear power spectra predictions agree with the full spherical
-solution to better than one percent, with the majority of the approximations
-tested accurate to better than 0.1 per cent.
-
-Considering first the flat-sky cases, the standard first-order Limber
-approximation (L1Fl), that was adopted for all pre-2014 CFHTLenS analyses, we
-find to be accurate to better than 10\% for $\ell>3$, converging slowly to the
-true projection with percent level precison at $\ell>100$. For the extended
-Limber approximations `hybrid' cases (ExtL1FlHyb and ExtL2FlHyb), despite
-decreased accuracy for $\ell < 8$ in comparison to the standard first-order
-Limber case, the errors with respect to the true power spectrum decrease much
-faster, as $\ell^{-2}$, such that percent-level precision is reached at
-$\ell>15$.  The first-order extended Limber approximation `hybrid' case
-(ExtL1FlHyb) was adopted by both \citet{joudaki/etal:2016} and
-\cite{KiDS-450}\footnote{We confirm that there is a typographical error in
-equation 4 of \cite{KiDS-450} which should include the extra term of `+0.5' in
-$\nu(\ell)$ that was incorporated in the cosmological analysis.}
-
-The outlier in the flat-sky cases is the extended Limber approximation
-(ExtL1Fl) which performs relatively poorly, and reach 10\% precision only at
-$\ell > 100$. To our knowledge this form of the flat-sky approximation has not
-been used in cosmic shear studies to date. The same slow convergence can be
+In Fig.~\ref{fig:Cl_cases} we plot the full spherical projection of the shear power spectrum in comparison to shear power spectra derived assuming
+the range of different approximations listed in Table~\ref{tab:cases}.  The adopted redshift distribution corresponds to CFHTLenS
+\cite{CFHTLenS-2pt-notomo} and we assume their best-fit flat $\Lambda$CDM cosmology with $\Omega_{\rm m}=0.279$, $\Omega_{\rm b}=0.046$, $\sigma_8=0.79$, $H_0=0.701$, $n_{\rm s}=0.96$. 
+For $\ell > 100$ we find that all shear power spectra predictions agree with the full spherical solution to better than one percent, with the majority of the approximations tested accurate to better than 0.1 per cent.
+
+Considering first the flat-sky cases, the standard first-order Limber approximation, (L1Fl), that was adopted for all pre-2014 CFHTLenS analyses, we find to be 
+accurate to better than 10\% for $\ell>3$, converging slowly to the true projection with percent level precison at $\ell>100$. 
+For the extended Limber approximations `hybrid' cases (ExtL1FlHyb and ExtL2FlHyb), despite decreased accuracy
+for $\ell < 8$ in comparison to the standard first-order Limber case, the errors with respect to
+the true power spectrum decrease much faster, as $\ell^{-2}$, such that percent-level precision is reached at $\ell>15$.
+The first-order extended Limber approximation `hybrid' cases (ExtL1FlHyb) was adopted by both \citet{joudaki/etal:2016} and \cite{KiDS-450}\footnote{We confirm that there is a typographical error in equation 4 of \cite{KiDS-450} which should include the extra term of `+0.5' in $\nu(\ell)$ that was incorporated in the cosmological analysis.}.
+
+The outlier in the flat-sky cases is the extended Limber approximation (ExtL1Fl) which performs relatively poorly, and
+reaches 10\% precision only at $\ell > 100$. The same slow convergence can be
 observed for the corresponding second-order flat case, ExtL2Fl.
-
-Including the spherical prefactor (the case ExtL1Sph) decreases the difference
-by a factor of a few for $\ell < 5$. Going to second-order (ExtL2Sph) yields
-percent accuracy down to $\ell = 4$.
-
-\mk{Not sure whether this following paragraph should be left in the draft: One
-notes that the difference between the full projection and second-order Limber
-does not scale as expected with $\ell^{-4}$, but rather with $\ell^{-2}$. This
-might be due to numerical noise that creates residual terms at the ${\cal
-O}(\ell^{-2})$ which do not cancel. Also note that the numerical noise for
-$\ell > 20$ is due to numerical integration errors for the full projection.}
+To our knowledge this form of the flat-sky approximation has not been used in any cosmic shear studies to date, and should not be used in any future studies given these results.
+The poor behaviour of this case, in comparison with the `hybrid' case, (e.g ExtL1FlHyb) can be understood by considering Taylor expansions of the different pre-factors.
+The spherical pre-factor,
+\begin{equation}
+p(\ell) = \frac{(\ell+2)(\ell+1)\ell(\ell-1)}{(\ell + 0.5)^4} = 1-{5\over 2\ell^2} +{\cal O}(\ell^{-3}) \, .
+\end{equation}
+can be compared to the flat-sky extended Limber pre-factor
+\begin{equation}
+p(\ell) = \ell^4 / (\ell + 0.5)^4 = 1-{2\over \ell}+{5\over 2\ell^2} +{\cal O}(\ell^{-3}) \, , 
+\end{equation} 
+showing it to be more deviant from the full spherical solution, than the `hybrid' $p(\ell) = 1$ case.
+
+Considering now the spherical-sky cases, we find that including the spherical pre-factor decreases the difference between the extended Limber approximated cases (ExtL1Sph and ExtL2Sph) and the full spherical solution by a factor of a few for $\ell < 5$.
+We find that using the spherical-sky second-order extended Limber approximation (ExtL2Sph) yields percent accuracy down to $\ell > 3$.
+The numerical calculation of the second-order extended Limber approximation is a factor of \ch{X} faster than the calculation of the full spherical solution.
+We note that the noise seen in the right panel of Fig.~\ref{fig:Cl_cases} is due to numerical noise arising from numerical integration errors the full spherical solution calculation for
+$\ell > 20$.  Increasing numerical precision would increase the calculation time still further, relative to the  second-order extended Limber calculation.
 

### 2017-02-08 discussion.tex
MK cleaned up appendix B

--- 2017-02-08 discussion.tex
@@
 
-The two-point shear correlation function $\xi_\pm$ represents the current baseline observable for cosmic shear measurements.   
-As shown in Figure~\ref{fig:xi_pm_K16}, however, using the standard first-order extended Limber flat-sky approximation (ExtL1FlHyb) can result
-in errors exceeding 10 percent, on angular scales $\theta > 300$ arcmin.
-This is a result of the significant weight given to low $\ell$ modes in the $\xi_+$ statistic, as illustrated in Figure~\ref{fig:filters} which shows the integrand of $\xi_+$ and $\xi_-$ (upper two panels) for two cases ( $\theta = 100$ and $\theta = 350$ arcmin), normalised to their maximum
-value.
-This error does not impact CFHTLenS analyses, given the low signal-to-noise of the measurements on these scales.
-It will however become increasingly important for upcoming wider-field surveys which will accurately probe these scales.
+The two-point shear correlation function $\xi_\pm$ represents the current
+baseline observable for cosmic shear measurements.   As shown in
+Figure~\ref{fig:xi_pm}, however, using the standard first-order extended
+Limber flat-sky approximation (ExtL1FlHyb) can result in errors exceeding 10
+percent, on angular scales $\theta > 300$ arcmin.    This is a result of the
+significant weight given to low $\ell$ modes in the $\xi_+$ statistic, as
+illustrated in Figure~\ref{fig:filters} which shows the integrand of $\xi_+$
+and $\xi_-$ (upper two panels) for two cases ( $\theta = 100$ and $\theta =
+350$ arcmin), normalised to their maximum value.   This error does not impact
+CFHTLenS analyses, given the low signal-to-noise of the measurements on these
+scales.  It will however become increasingly important for upcoming wider-field
+surveys which will accurately probe these scales.
 
-In this paper we provide a solution in the form of the second-order extended Limber approximation, but another option is to consider alternative two-point shear statistics that are less sensitive to accuracy in shear power spectrum measurement at low $\ell$.
-Both the aperture-mass dispersion, $\langle M_ {\rm ap}^2 \rangle2$ \citep{1998MNRAS.296..873S}, and
-the Complete Orthogonal Sets of E/B-mode Integrals (COSEBIs), $E_n$ \citep{COSEBIs} statistics satisfy this requirement and are linearly related to
-the shear power spectrum in the flat-sky approximation via integrals of the form (omitting tomographic indices),
+In this paper we provide a solution in the form of the second-order extended
+Limber approximation, but another option is to consider alternative two-point
+shear statistics that are less sensitive to accuracy in shear power spectrum
+measurement at low $\ell$.   Both the aperture-mass dispersion, $\langle M_
+{\rm ap}^2 \rangle2$ \citep{1998MNRAS.296..873S}, and the Complete Orthogonal
+Sets of E/B-mode Integrals (COSEBIs), $E_n$ \citep{COSEBIs} statistics satisfy
+this requirement and are linearly related to the shear power spectrum in the
+flat-sky approximation via integrals of the form (omitting tomographic
+indices),
 %

### 2017-02-08 limber2.tex
MK cleaned up appendix B

@@
 
-Figure.~\ref{fig:xi_pm_K16} presents the two-point correlation functions
+Figure.~\ref{fig:xi_pm} presents the two-point correlation functions
 $\xi_+$ (left) and $\xi_-$ (right) using the different cases for the shear
@@
 
-  \label{fig:xi_pm_K16}
+  \label{fig:xi_pm}
 
@@
 
+In this section we briefly discuss previously published work on the full
+projection and second-order Limber equation of the lensing power spectrum. We
+compare those results with our findings.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Kitching et al.~2016}
-
-\cite{2016arXiv161104954K} compute the full projection of the weak-lensing power
-spectrum, which they present as spherical-radial representation the 3D shear field.
-Our results (\ref{eq:C_ell_full}) correspond to their equations (7) and (8)
-for a flat Universe and in the case of perfect
-photometric redshifts, $p(z | z_{\rm p}) = \delta_{\rm D}(z - z_{\rm p})$, and
-for a bin function that selects the redshift bin $i$, $W^{\rm SR}(z, z_{\rm p})
-= 1_{z \in i-\mbox{th bin}}$. In \cite{2016arXiv161104954K} eq.~(7) is however the
-factor $2/\pi$ missing.
-
-In App.~A \cite{2016arXiv161104954K} derives the spherical and extended
-Limber approximation starting from the full spherical projection. Note that
-their filter function $q$ defined in (31) has an errornous factor of comoving
-distance $r$, and an additional factor $\pi/2$ appears. \mk{This is probably worded
-too strongly.}
-
-We can not reproduce the amplitude of the differences between the cases,
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\cite{2016arXiv161104954K} compute the full projection of the weak-lensing
+power spectrum, which they present as spherical-radial representation the 3D
+shear field. Our results (\ref{eq:C_ell_full}) correspond to their equations
+(7) and (8) for a flat Universe and in the case of perfect photometric
+redshifts, $p(z | z_{\rm p}) = \delta_{\rm D}(z - z_{\rm p})$, and for a bin
+function that selects the redshift bin $i$, $W^{\rm SR}(z, z_{\rm p}) = 1_{z
+\in i-\mbox{th bin}}$. In \cite{2016arXiv161104954K} eq.~(7) the factor $2/\pi$
+is absent.
+
+In App.~A \cite{2016arXiv161104954K} derives the spherical and extended Limber
+approximation starting from the full spherical projection. Note that their
+filter function $q$ defined in (31) has an errornous additional factor of
+comoving distance $r$, and shows an additional factor of $\pi/2$.
+
+As shown in the main text of our paper,
+we can not reproduce the amplitude of the differences between the cases,
 neither for the power spectrum nor for the shear correlation function (see
-Figs.~\ref{fig:Cl_cases} and \ref{fig:xi_pm_K16}).
-
-\paragraph{Bernardeau, Bonvin, Van de Rijt, Vernizzi (2012); van de Rijt (2012)}
-
-Eq.~(44) of \cite{2012PhRvD..86b3001B} is the non-tomographic $C(\ell)$ in
-terms of the time-independent potential power spectrum $T^2(k) P(k)$, where $T$
-is the transfer function; the growth factor $D$ is contained in their window
-function $W$ (43) as growth-suppression factor $g(\chi) = D(\chi)/a(\chi)$
-(defined after eq.~{24}). For a single source redshift, we find the identity
-$W(\chi)$ = $q(\chi)\chi^{-1} D(\chi) a^{-1}(\chi)$.
-\cite{2012PhRvD..86b3001B} is consistent with our
-(\ref{eq:C_ell_full}), if we interpret the
-scale factors at distances $\chi$ and $\chi^\prime$, respectively.
+Figs.~\ref{fig:Cl_cases} and \ref{fig:xi_pm}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Bernardeau, Bonvin, Van de Rijt, Vernizzi (2012); van de Rijt (2012)}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Eq.~(44) of \cite{2012PhRvD..86b3001B} is the non-tomographic full projection
+$C(\ell)$ in the approximation of the 3D potential power spectrum $P^\Phi$ separating
+into $k$- and $\chi$-dependent functions. Their expression holds for a single
+source redshift.
 
 The PhD thesis of Van de Rijt \cite{vande2012} presents an explicit calculation
-of the second-order Limber approximation for a fixed source redshift. They
-carry out the derivatives of the kernels $f$ under the assumption of a constant
-growth-suppression factor $D_+(a)/a$, and a power spectrum that separates $k$-
-from $\chi$-terms. We show the consistency between their result (eq.~7.19) and
-our (\ref{eq:C_ell_limber2_dr_s}), as follows.
-
-We write (\ref{eq:C_ell_limber2_dr_s}) without tomography, and insert again the
-time-independent power spectrum (\ref{eq:P_geom_mean}),
-%
-\begin{align}
-  C^\gamma_{{\rm L2}}(\ell) = & - \frac 1 {\nu^2} \, \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2
-    \int {\rm d} \chi \, \chi^{2} P_{\rm m}\left(k = \frac\nu\chi\right)
-    \nonumber \\
-    & \times D_+(\chi) a^{-1}(\chi) \chi^{3/2} q(\chi) \left[ f^{\prime\prime} 
-      + \frac{\chi}{3} f^{\prime\prime\prime} 
-    \right](\chi)
-  \label{eq:C_ell_limber2_dr_notomo}
-\end{align}
-%
-For a fixed source comoving distance $\chi_{\rm S}$ the lensing efficiency is
-$q(\chi) = (\chi_{\rm S} - \chi) \chi_{\rm S}^{-1}$. Assuming that
-$D_+(\chi)/a(\chi) \approx g = \mbox{const}$, we get for the derivative terms,
-with $f(\chi) = g \chi_{\rm S}^{-1} (\chi_{\rm S} - \chi) \chi^{-3/2}$,
+of the second-order Limber approximation. They carry out the derivatives of the
+kernels $f$ under the assumption of a constant growth-suppression factor
+$D_+(a)/a$. Then, for a constant source comoving distance $\chi_{\rm S}$, the
+lensing efficiency (\ref{eq:lens_efficiency}) is $q(\chi) = (\chi_{\rm S} -
+\chi) \chi_{\rm S}^{-1}$, and the derivative of the separated kernel function
+(\ref{eq:f_LA08_s}) can be calculated analytically,
 %
@@
 %
-Therefore,
-%
-\begin{align}
-  C^\gamma_{{\rm L2}}(\ell) = \frac 1 {\nu^2} \, \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2
-    \int {\rm d} \chi \, \chi \, P_{\rm m}\left(k = \frac\nu\chi\right)
-    \frac{q(\chi)}{8} \left( \frac 5 \chi + \frac 1 {\chi_{\rm S}} \right)
-      \left(\frac{D_+(\chi)}{a(\chi)}\right)^2 
-\end{align}
-%
-We now replace the matter with the potential power spectrum, ${\cal A}^2 P_{\rm m}(k) = k^{4} a^2 P_\Phi(k)$, and pull into the integral $\nu^{-4} = \chi^{-4} k^{-4}$. This yields
-%
-\begin{align}
-  C^\gamma_{{\rm L2}}(\ell) = \frac 1 {\nu^2} \, \ellbar^2(\ell, 2)
-    \int \frac{{\rm d} \chi}{\chi^2} \, P_\Phi\left(k = \frac\nu\chi\right)
-    a^2(\chi) \frac{1}{8} \frac{\chi_{\rm S} - \chi}{\chi \chi_{\rm S}}
-    \left( \frac 5 \chi + \frac 1 {\chi_{\rm S}} \right)
-      \left(\frac{D_+(\chi)}{a(\chi)}\right)^2 .
-\end{align}
-%
-Note the additional factor $a^2(\chi)$. This difference is accounted for by the
-factor $a^{-1}$ in the propagation of primordial potential perturbations to
-late times, see eq.~(6.22) in \cite{vande2012}, where the transition is done
-using $g(a)$ instead of $D(a)$. \mk{Check this further.}
+This result confirms the power-law behaviour of the filter function, which we exploited earlier to fit
+this function.
+
+Inserting this into the second-order Limber power spectrum
+(\ref{eq:C_ell_limber2_dr_s}) and using the inverse Poisson equation to replace
+the matter with the potential power spectrum we obtain the same expression as
+\cite{vande2012} (their eq.~7.19), except for an additional factor $a^2(\chi)$.
+This difference is accounted for by the factor $a^{-1}$ in the propagation of
+primordial potential perturbations to late times, see eq.~(6.22) in
+\cite{vande2012}, where the transition is done using $g(a)$ instead of $D(a)$.
+\mk{Check this further.}
 
@@
 are at redshift $z_{\rm S} = 1$. The non-linear 3D matter power spectrum from
-\cite{2012ApJ...761..152T} is used. The ratio of the first-and second- Limber approximated
-power spectra to the full
-projection shows excellent agreement at the sub-percent level.
+\cite{2012ApJ...761..152T} is used. The ratio of the first-and second- Limber
+approximated power spectra to the full projection shows excellent agreement at
+the sub-percent level.
 
@@
 
-\paragraph{LoVerde \& Afshordi (2009)}
+\subsection{LoVerde \& Afshordi (2009)}
 
@@
 apply in this work. Although they present the specific case of 2D galaxy
-clustering, their calculations are general enough to apply to weak lensing.
-
-Their eq.~(5) is a general spherical power spectrum of a scalar field,
-projected from 3D to 2D via (4). Comparing their expressions with the
-weak-lensing potential (\ref{eq:psi}), we can set $F_A(\chi) = F_B(\chi) = 2
-c^{-2} D_+(\chi) q(\chi) \chi^{-1}$. With that, their eq.~(5) is identical to
-our (\ref{eq:C_ell_phi_Pphi}).
-
-The second-order Limber approximation in \cite{2008PhRvD..78l3506L} is presented in
-eq.~(12). This is consistent with our first-order (\ref{eq:C_ell_limber1}) and
-second-order (\ref{eq:C_ell_limber2_dr}) Limber approximation, when accounting for the difference between
-lensing potential and shear 2D power spectrum, and 3D potential and matter power spectrum.
-
-\paragraph{Schmidt (2009)}
+clustering, their calculations are general enough to apply to a weak-lensing
+context. Their eq.~(5) is a spherical cross-power spectrum of two scalar fields
+$A$ and $B$, projected from 3D to 2D via projection kernels $F_A$ and $F_B$
+defined in their eq.~(4). Comparing their expressions with the weak-lensing
+potential (\ref{eq:psi}), we set $F_A(\chi) = F_B(\chi) = 2 c^{-2}
+D_+(\chi) q(\chi) \chi^{-1}$. With that, their eq.~(5) is identical to our
+(\ref{eq:C_ell_phi_Pphi}).
+
+The second-order Limber approximation in \cite{2008PhRvD..78l3506L} is
+presented in eq.~(12). This is consistent with our first-order
+(\ref{eq:C_ell_limber1}) and second-order (\ref{eq:C_ell_limber2_dr}) Limber
+approximation terms, when accounting for the difference between lensing
+potential and shear 2D power spectrum, and 3D potential and matter power
+spectrum.
+
+\subsection{Schmidt (2009)}
 
 In eq.~(9) \cite{2008PhRvD..78d3002S} write the lensing power spectrum in the
-flat-sky limit. The Poisson factor $D_\phi$ is defined in their eq.~(5), see
-also our eq.~\ref{eq:poisson}, and $D_{\rm m}$ is the growth factor. The filter
-function $W_\kappa$ (eq.~10) can be written as
-%
-\begin{align}
-  W_\kappa(z) = & \frac 1 {H(z)} \int_z^\infty {\rm d} z_{\rm s} W_{\rm L}(z_{\rm s}, z) W_{\rm g}(z)
-              =  \frac 1 {H(z)} \chi \int_\chi^\infty {\rm d} \chi^\prime \frac{\chi^\prime - \chi}{\chi^\prime}
-                n(\chi)
-              \nonumber \\
-              & \equiv \frac 1 {H(z)} \chi q(\chi),
-\end{align}
-%
-using ${\rm d} z W_{\rm g}(z) = {\rm d} \chi n(\chi)$.
-To write the redshift integrals (9) in \cite{2008PhRvD..78d3002S} over 
-comoving distance, we make the variable transformation
-%
-\begin{equation}
-  {\rm d} \chi = \frac{c {\rm d} z}{H(z)} .
-\end{equation}
-%
-We recover our (\ref{eq:P_ell_gamma}).
-
-\paragraph{Giannantonio et al. (2012)}
+flat-sky limit. Inserting the Poisson factor $D_\phi$, 
+ the growth function $D_{\rm m}$, and writing the redshift filter
+function $W_\kappa$ (eq.~10) in terms of the lensing efficiency and comoving distances,
+$W_\kappa[z(\chi)] = H(z)^{-1} \chi q(\chi)$, we
+%
+%\begin{align}
+  %W_\kappa(z) = & \frac 1 {H(z)} \int_z^\infty {\rm d} z_{\rm s} W_{\rm L}(z_{\rm s}, z) W_{\rm g}(z)
+              %=  \frac 1 {H(z)} \chi \int_\chi^\infty {\rm d} \chi^\prime \frac{\chi^\prime - \chi}{\chi^\prime}
+                %n(\chi)
+              %\nonumber \\
+              %& \equiv \frac 1 {H(z)} \chi q(\chi),
+%\end{align}
+%%
+%using ${\rm d} z W_{\rm g}(z) = {\rm d} \chi n(\chi)$.
+%To write the redshift integrals (9) in \cite{2008PhRvD..78d3002S} over 
+%comoving distance, we make the variable transformation
+%%
+%\begin{equation}
+  %{\rm d} \chi = \frac{c {\rm d} z}{H(z)} .
+%\end{equation}
+%%
+%We
+recover our (\ref{eq:P_ell_gamma}).
+
+\subsection{Giannantonio et al. (2012)}
 
@@
 power spectrum. Their window function $W^{\varepsilon_i}$ defined in (25) for a
-flat Universe equals $\pref \times q(\chi) / a(\chi)$, since ${\rm d} z {\rm d}
-N(z)/{\rm d} z = {\rm d} \chi n(\chi)$; however there is a factor $r_K[r(z)]$
-missing in the window function, which translates into a missing $r_K[r]
-r_K[r^\prime]$ in the integral\footnote{Confirmed by T.~G., priv.~comm.}. This
-also leads to an errorous $r_K^{-2}(r)$ in the Limber equation (27). With these
-factors accounted for, we reproduce the expressions of \cite{2012MNRAS.422.2854G}.
+flat Universe equals $\pref \times q(\chi) / a(\chi)$, since ${\rm d} z \,
+({\rm d} N(z)/{\rm d} z) = {\rm d} \chi n(\chi)$; however due to a typo there
+is a factor $r_K[r(z)]$ missing in the window function, which translates into a
+missing $r_K[r] r_K[r^\prime]$ in the full projection integral\footnote{Typo confirmed by T.~G.,
+priv.~comm.}. This also leads to an errorous $r_K^{-2}(r)$ in the Limber
+equation (27). With these factors accounted for, we reproduce the expressions
+of \cite{2012MNRAS.422.2854G}.
 

### 2017-02-09 cfhtlens.tex
added ExtL2FlHyb prelim. Sigma_8

@@
   ExtL1FlHyb & $0.788^{+0.031}_{-0.033}$ & $0.740^{+0.029}_{-0.031}$ & Used for post-2014 CFHTLenS, KiDS \\
-  ExtL2FlHyb & $x^{+y}_{-z}$ & $x^{+y}_{-z}$ & Best flat-sky approximation \\
+  ExtL2FlHyb & $0.788^{+0.032}_{-0.032}$ & $0.749^{+0.030}_{-0.030}$ & Best flat-sky approximation \\
   ExtL2Sph   & $0.789^{+0.031}_{-0.032}$ & $0.740^{+0.029}_{-0.030}$ & Best approximation but mixing with flat-sky Hankel transform \\ \hline

### 2017-02-09 cfhtlens.tex
added empty conclusions.tex file will now fill it

@@
 
-\ch{This text taken from the comment on paper; We note that
-\citet{2016arXiv161104954K} use their `Flat' approximation for their `Full'
-non-Limber analysis of the CFHTLenS data. This is because on a sphere,
-correlation functions cannot be related to the power spectrum by a Hankel
-transform (\ref{eqn:xiGG}) as formally the power spectrum is not defined for
-non-integer $\ell$. In Fig.~\ref{fig:Cl_cases}, however, we show that this
-chosen version of a flat-sky approximation serves to exacerbate the tension in
-theoretical models when a flat-sky solution is compared with the spherical-sky
-solution in the Limber approximated case.  This is not the case when
-considering the standard and extended hybrid flat-sky Limber approximation
-(both for which $p(\ell) = 1$, which corresponds to $T_\ell$ in
-\citet{2016arXiv161104954K}, see Sect.~\ref{sec:Limber_flat_sky}) that has been
-used in the majority of cosmic shear studies to date.  We would therefore argue
-that it is more appropriate to use a $p(\ell) = 1$ flat-sky approximation when
-carrying out a `full' non-Limber analysis of the shear correlation function
-obtained from the Hankel transformation (equation~\ref{eqn:xiGG}). We need to
-take a decision here about what to use. Do we need a Full Flat case in Table 1,
-and to demonstrate that Ext2Fl is very close to FullFl?  And then use Ext2Fl as
-our "truth" for the correlation function?}
-
 \renewcommand{\baselinestretch}{1.5}

### 2017-02-09 cfhtlens.tex
MK small changes

--- 2017-02-09 cfhtlens.tex
@@
 Monte-Carlo parameter sampling is performed using the publically available
-software \textsc{CosmoPMC}\footnote{\texttt{www.cosmopmc.info}}
+software \textsc{CosmoPMC}\footnote{\texttt{http://www.cosmostat.org/software/cosmopmc}}
 \citep{WK09,KWR10}. The cosmological modelling part including the various

### 2017-02-09 conclusions.tex
short but sweet conclusion section

In this paper we evaluate precision theoretical calculations for cosmic shear observables, bringing together different sources from the literature to provide a pedagogical review of the impact of adopting flat-sky and Limber approximations.  We demonstrate that for current surveys, such as CFHTLenS, these approximations have a negligible impact on cosmological parameter constraints, in contrast to the recent claim in \citet{2016arXiv161104954K}.

For future surveys, the decrease in statistical errors places higher requirements on the accuracy of the theoretical modelling.    There is also, however, the need to be able to rapidly sample the multi-dimensional cosmological parameter likelihoods.  This requirement for computational speed is incompatible with a theoretical analysis that calculates a full spherical solution for the shear power spectrum, without adopting any approximation.  We therefore present alternative solutions, revisiting the work of  \citet{2012PhRvD..86b3001B} who showed that adopting the second-order extended Limber approximation of \citet{2008PhRvD..78l3506L} provides a representation of full spherical solution for the shear power spectrum that is accurate at the sub-percent level for $\ell > 3$.    We have verified this result and provide to the community our fast numerical implementation of all the approximations studied in this analysis,
and the slow calculation of the full projection within the publicly available package \textsc{nicaea} at \texttt{http://www.cosmostat.org/software/nicaea}.

Finally we propose that future surveys seek to optimise the statistical analyses of their cosmic shear data.  For example moving from the standard two-point shear correlation function statistic to the more stringent `COSEBI' statistic \citep{schneider/etal:2010} renders the cosmic shear measurement insensitive to the low-$\ell$ scales where the Limber and flat-sky approximations make any impact on the precision of the theoretical modelling.

### 2017-02-09 limber2.tex
added empty conclusions.tex file will now fill it
MK small changes
Added author list, addresses and the acks that I know about

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{document}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \title[Precision calculations for cosmic shear]{Precision calculations for cosmic shear}  %??
@@
 
-\author[M.~Kilbinger et~al.]
- {
-  \parbox[h]{\textwidth}
-  {
-      Martin Kilbinger$^{1,2}$\thanks{E-mail: martin.kilbinger@cea.fr},
-      %Catherine Heymans,
-      %Peter Schneider,
-      %Shahab Joudaki,
-      %Marika Asgari,   % note that we'll worry about order at the end - Marika and Shahab put a lot of work into the comment paper, so we might just want to go alpha
-      and other members of CFHTLenS and KiDS
-      $\ldots$,
-  }
-  % 
-  \vspace*{10pt} \\
-  \hspace{-.1cm}$^1$ CEA/Irfu/SAp Saclay, Laboratoire AIM, 91191 Gif-sur-Yvette, France\\
-  \hspace{-.1cm}$^2$ Institut d'Astrophysique de Paris, UMR7095 CNRS,
-           Universit\'e Pierre \& Marie Curie, 98 bis boulevard Arago, 75014 Paris,
-           France \\
- }
-
-\voffset-0.50in
+\input{authors.tex}
 
@@
 
+\begin{document}
+\setlength{\voffset}{-12mm}
+
+\label{firstpage}
+
 \maketitle
-
-\label{firstpage}
-
 \begin{abstract}
@@
 \section{Conclusions}
+\input{conclusions.tex}
 
@@
 The authors thank Tommaso Giannantonio, Sarah Bridle, Ami Choi, Donnacha Kirk, Lance Miller, Benjamin Joachimi, Chris Blake and Adam Amara for very helpful discussions.
+This work was financially supported by the DFG (Emmy Noether grants Hi 1495/2-1 and SI 1769/1-1; TR33 `The Dark Universe'), the Alexander von Humboldt Foundation, the ERC (grants 279396, 647112), the Seventh Framework Programme of the European Commission (Marie Sklodwoska Curie Fellowship grant 656869), NSERC and CIfAR.
+
+\ch{Check your acknowledgements}
 
@@
     as function of wave mode $\ell$, see Table \ref{tab:cases}. The redshift distribution
-    and the cosmological parameters (see text) are chosen to match
+    is a single source plane at $z_{\rm S}=1$, and the cosmological parameters (see text) are chosen to match
     \citet{vande2012}, see their Fig.~7.3 for comparison.

### 2017-02-09 cfhtlens.tex
Added author list, addresses and the acks that I know about
Centered Tab 2 Updated reference in Fig 2 (Planck referenced twice previously)

@@
 result that was published in \cite{CFHTLenS-2pt-notomo}. Using the second-order
-extended Limber flat-sky approximation results in $\sigma_8 (\Omega_{\rm
-m}/0.27)^{0.6} =X^{+X}_{-X}$, a negligible change of $X\sigma$.
+extended Limber flat-sky approximation results in \ch{$\sigma_8 (\Omega_{\rm
+m}/0.27)^{0.6} =X^{+X}_{-X}$}, a negligible change of $X\sigma$.
 
@@
 \begin{table}
-
+\begin{centering}
   \label{tab:CFHTLenS_Sigma8}
@@
 
+\end{centering}
 \end{table}

### 2017-02-09 limber2.tex
Centered Tab 2 Updated reference in Fig 2 (Planck referenced twice previously)

@@
     The theoretical model corresponds to the CFHTLenS best-fit parameters with
-    $\Omega_{\rm m} = 0.279$, $h=0.701$, and $\sigma_8 = 0.79$ \citep{2015arXiv150201589P},
+    $\Omega_{\rm m} = 0.279$, $h=0.701$, and $\sigma_8 = 0.79$ \citep{CFHTLenS-2pt-notomo},
     except the red dashed curve with adapts a Planck-best fit

### 2017-02-09 limber2.tex
Tidied up Tab1

@@
 
-\renewcommand{\baselinestretch}{1.3}
+\renewcommand{\baselinestretch}{1.5}
 \begin{table}
-
+\begin{centering}
   \label{tab:cases}
-
   \caption{Shear power spectrum approximations compared in this paper. 'ID' is the abbrevation used in the plots.
-    The third column shows the power-spectrum prefactor $p(\ell)$.  \mk{The last column will be removed in the
-        final version.}}
-
-  \begin{tabular}{|l|l|c|c|c|c}
+    The third column shows the power-spectrum prefactor $p(\ell)$. }  
+    \begin{tabular}{|l|l|c|c|c}
   \hline
-  Case & ID & eq.~ & prefactor & $\nu(\ell)$ & Label [Comment paper] \\ \hline
+  Case & ID & eq.~ & prefactor & $\nu(\ell)$ \\ \hline
   % 
   $1^{\rm st}$-order standard Limber, flat sky & L1Fl & (\ref{eq:P_ell_limber1}) + (i)
-    & $1$ & $\ell$ & Kst \\ \hline
+    & $1$ & $\ell$ \\ \hline
   %
   $1^{\rm st}$-order extended Limber, flat sky & ExtL1Fl & (\ref{eq:P_ell_limber1}) + (ii)
-    & $\ell^4/(\ell+1/2)^4$ & $\ell + 1/2$ & ELF \\ \hline
+    & $\ell^4/(\ell+1/2)^4$ & $\ell + 1/2$ \\ \hline
   %
   $1^{\rm st}$-order extended Limber, hybrid, flat sky & ExtL1FlHyb & (\ref{eq:P_ell_limber1}) + (iii)
-    & $1$ & $\ell + 1/2$ & ESt \\ \hline
+    & $1$ & $\ell + 1/2$ \\ \hline
   %
   $1^{\rm st}$-order extended Limber, spherical & ExtL1Sph & (\ref{eq:C_ell_limber1})
-    & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ & ELS \\ \hline
+    & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ \\ \hline
   %
@@
     & $\ell^4/(\ell+1/2)^4$ 
-    & $\ell+1/2$ & - \\ \hline
+    & $\ell+1/2$ \\ \hline
   %
@@
     & $1$ 
-    & $\ell+1/2$ & - \\ \hline
+    & $\ell+1/2$ \\ \hline
   %
   $2^{\rm st}$-order extended Limber, spherical & ExtL2Sph & (\ref{eq:C_ell_limber1})+(\ref{eq:C_ell_limber2_dr_s})
-    & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ & - \\ \hline
+    & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ \\ \hline
   %
   Full spherical & FullSph & (\ref{eq:C_ell_full}) &
-      $\ellbar^2(\ell, 2)$ & - & - \\ \hline
+      $\ellbar^2(\ell, 2)$ & - \\ \hline
   %

### 2017-02-09 conclusions.tex
Fixed the multiple entries in the bibliography

@@
 Finally we propose that future surveys seek to optimise the statistical analyses of their cosmic shear data.
-For example moving from the standard two-point shear correlation function statistic to the more stringent `COSEBI' statistic \citep{schneider/etal:2010} renders the cosmic shear measurement insensitive to the low-$\ell$ scales where the Limber and flat-sky approximations make any impact on the precision of the theoretical modelling.
+For example moving from the standard two-point shear correlation function statistic to the more stringent `COSEBI' statistic \citep{COSEBIs} renders the cosmic shear measurement insensitive to the low-$\ell$ scales where the Limber and flat-sky approximations make any impact on the precision of the theoretical modelling.

### 2017-02-09 limber2.tex
Fixed the multiple entries in the bibliography

@@
 a second-order extended Limber approximation \citep[for more details see][and
-references therein]{miraldaescude:1991, kaiser:1992,
-bartelmann/schneider:2001}.
+references therein]{miraldaescude:1991, kaiser:1992, BS01}.
 

### 2017-02-09 limber2.tex
MK discussion of full projection flat-sky Pgamma

--- 2017-02-09 limber2.tex
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{document}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \title[Precision calculations for cosmic shear]{Precision calculations for cosmic shear}  %??
@@
 
-\input{authors.tex}
+\author[M.~Kilbinger et~al.]
+ {
+  \parbox[h]{\textwidth}
+  {
+      Martin Kilbinger$^{1,2}$\thanks{E-mail: martin.kilbinger@cea.fr},
+      %Catherine Heymans,
+      %Peter Schneider,
+      %Shahab Joudaki,
+      %Marika Asgari,   % note that we'll worry about order at the end - Marika and Shahab put a lot of work into the comment paper, so we might just want to go alpha
+      and other members of CFHTLenS and KiDS
+      $\ldots$,
+  }
+  % 
+  \vspace*{10pt} \\
+  \hspace{-.1cm}$^1$ CEA/Irfu/SAp Saclay, Laboratoire AIM, 91191 Gif-sur-Yvette, France\\
+  \hspace{-.1cm}$^2$ Institut d'Astrophysique de Paris, UMR7095 CNRS,
+           Universit\'e Pierre \& Marie Curie, 98 bis boulevard Arago, 75014 Paris,
+           France \\
+ }
+
+\voffset-0.50in
 
@@
 
-\begin{document}
-\setlength{\voffset}{-12mm}
+\maketitle
 
@@
 
-\maketitle
 \begin{abstract}
@@
 
-This paper is organised as follows.
-In section~\ref{sec:wl} we provide a pedagogical introduction to weak gravitational lensing theory, projections and power spectra for the flat-sky and spherical cases.
-In section~\ref{sec:L2} we derive weak lensing observables using a second-order limber approximation first introduced by \citet{2008PhRvD..78l3506L}.
-We compare the shear power spectrum and commonly-used two-point shear correlation function for the full solution to a range of different approximations in section~\ref{sec:comp}, providing cosmological constraints for each case using CFHTLenS data from \citet{CFHTLenS-2pt-notomo} in section~\ref{sec:cfhtlens}.
-This paper draws from several sources of literature which have previously reviewed the accuracy of the Limber approximation for weak lensing studies, namely \citet{2008PhRvD..78d3002S,2012PhRvD..86b3001B, 2012MNRAS.422.2854G, 2016arXiv161104954K}.
-We present a discussion and comparison of our results to these papers in Appendix~\ref{app:B}.
+This paper is organised as follows.  In section~\ref{sec:wl} we provide a
+pedagogical introduction to weak gravitational lensing theory, projections and
+power spectra for the flat-sky and spherical cases, following the seminal work
+from \citet{2000PhRvD..62d3007H}, see also \citet{2005PhRvD..72b3516C}. In section~\ref{sec:L2} we
+derive weak lensing observables using a second-order limber approximation first
+introduced by \citet{2008PhRvD..78l3506L}. We compare the shear power spectrum
+and commonly-used two-point shear correlation function for the full solution to
+a range of different approximations in section~\ref{sec:comp}, providing
+cosmological constraints for each case using CFHTLenS data from
+\citet{CFHTLenS-2pt-notomo} in section~\ref{sec:cfhtlens}. This paper draws
+from several sources of literature which have previously discussed the full
+projection, or reviewed the accuracy of the Limber approximation for weak
+lensing studies, namely \citet{2008PhRvD..78d3002S,2012PhRvD..86b3001B,
+2012MNRAS.422.2854G, 2016arXiv161104954K}. We present a discussion and
+comparison of our results to these papers in Appendix~\ref{app:B}.
 
@@
 
-The lensing potential $\psi$ in the Born approximation is defined as the
-projected 3D metric potential $\Phi$ along the line of sight
-\citep{1998ApJ...498...26K,BS01},
+The lensing potential $\psi$ at a direction on the sky $(\theta, \varphi)$ in
+the Born approximation is defined as the projected 3D metric potential $\Phi$
+along the line of sight \citep{1998ApJ...498...26K,BS01},
 %
@@
 %
-corresponding to a population of lensed galaxies with normalised source redshift
-distribution $n(z) {\rm d}z = n(\chi) {\rm d} \chi$. Here, ${\rm c}$ is the
-speed of light, the projection is carried out over comoving distances $\chi$ up
-to a limiting distance $\chi_{\rm lim}$, and $f_K$ is the the comoving angular
-distance, which depend on the spatial curvature of the Universe $K$.
-%
-This assumes a homogeneous galaxy distribution without clustering, so that the
-redshift distribution in this approximation does not depend on the position
-$(\theta, \varphi)$. Accounting for this position dependence leads to
-correction of weak-lensing quantities due to clustering of source galaxies with
-other sources \citep{2002A&A...389..729S}, and with galaxies associated with
-lens structures \citep{1998A&A...338..375B,H02}.
+corresponding to a population of lensed galaxies with normalised source
+redshift distribution $n(z) {\rm d}z = n(\chi) {\rm d} \chi$. Here, ${\rm c}$
+is the speed of light, the projection is carried out over comoving distances
+$\chi$ up to a limiting distance $\chi_{\rm lim}$, and $f_K(\chi) = |K|^{-1/2}
+S_K(|K|^{1/2} \chi)$ is the the comoving angular distance, where the function
+$S_K$ equals $\sin$, ${\rm id}$, or $\sinh$ if the spatial curvature of the Universe
+$K$ is positive, zero, or negative, respectively.
+
+The form of the lensing efficiency $q$ (\ref{eq:lens_efficiency}) assumes a
+homogeneous galaxy distribution without clustering, so that the redshift
+distribution in this approximation does not depend on the direction on the sky.
+Accounting for this position-dependence leads to correction of weak-lensing
+quantities due to clustering of source galaxies with other sources
+\citep{2002A&A...389..729S}, and with galaxies associated with lens structures
+\citep{1998A&A...338..375B,H02}.
 
@@
 \begin{align}
-  \hat \Phi(\vec k; \chi) = &  \int {\rm d}^3 r \, \Phi(\vec r; \chi) {\rm e}^{{\rm i} \vec k \vec r} .
+  \hat \Phi(\vec k; \chi) = &  \int {\rm d}^3 r \, \Phi(\vec r; \chi) {\rm e}^{{\rm i} \vec k \vec r} ;
   \label{eq:hatPhi}
@@
 \end{align}
-
+%
 To specify tomographic redshift bins $i=0\ldots N_z-1$, we introduce a family
@@
 functions from the observed shear have been calculated using spherical
-coordinates, and the effect on large scales is not negligible \cite{FSHK08}.
+coordinates, and the effect on large scales is not negligible \citep{FSHK08}.
 Here we examine the effect of sky curvature on the theoretical models.
@@
 
-The power spectrum, the flat-sky version of
-(\ref{eq:C_ell_psi}) is defined by
+The flat-sky power spectrum, the flat-sky analogon of (\ref{eq:C_ell_psi}) is defined by
 %
@@
 \end{equation}
-
-\mk{I can derive a flat-sky shear power spectrum by replacing $\ellbar^2(\ell, 2)$ with $\ell^4$
-in (\ref{eq:C_ell_full}), equivalent to replacing the edth operators with Euclidian derivatives.
-However, this results in a different expression compared to other references, e.g.~\cite{2008PhRvD..78d3002S},
-which is the following equation.}
-
-The flat-sky power spectrum is
-%
-\begin{align}
-  P_{ij}^\gamma(\ell) = & \frac 2 \pi \, \pref^2
-                 \int_{0}^{\chi_{\rm lim}} {\rm d} \chi \chi \, \frac{q_i(\chi)}{a(\chi)}
-                \int_{0}^{\chi_{\rm lim}} {\rm d} \chi^\prime\, \chi^\prime
+%
+\cite{2000PhRvD..62d3007H} have shown that for small angles the harmonics
+expansion (\ref{eq:psi_harm_exp}) can be approximated by the the Fourier
+representation (\ref{eq:psi_fourier}). They also demonstrated that the power
+spectra are approximately equal, $P^\psi \approx C^\psi$.
+
+For a spin-2 field, \cite{2000PhRvD..62d3007H} approximates the edth operator by Cartesian derivatives, and approximates
+(\ref{eq:sYlm_def}) as
+%
+\begin{equation}
+  \ell^2 \, _{\pm2}\!{\rm Y}_{\ell m}(\theta, \varphi) =  {\rm e}^{{\mp}2 {\rm i} \phi_\ell}
+    (\partial_1 \pm \partial_2)^2 \, {\rm Y}_{\ell m}(\theta, \varphi).
+  \label{eq:sYlm_def_flat}
+\end{equation}
+%
+The spherical prefactor $\sqrt{(\ell-1) \ell (\ell+1) (\ell+2)}$ is replaced by $\ell^2$ in flat coordiates.
+We find for the flat-sky shear power spectrum
+%
+\begin{align}
+  P^\gamma_{ij}(\ell) 
+                 = & \frac 2 \pi \, \ell^4 \, \pref^2
+                 \int_{0}^{\chi_{\rm lim}} \frac{\rm d \chi}{\chi} \frac{q_i(\chi)}{a(\chi)}
+                \int_{0}^{\chi_{\rm lim}} \frac{\rm d \chi^\prime}{\chi^\prime}
                 \frac{q_j(\chi^\prime)}{a(\chi^\prime)}
-                \nonumber \\
-                & \times \int_0^\infty {\rm d} k \, k^2 \, P_{\rm m}(k; \chi, \chi^\prime) \,
+                %\nonumber \\
+                %& \times
+                \int_0^\infty \frac{{\rm d} k}{k^2} \, P_{\rm m}(k, \chi, \chi^\prime) \,
                 {\rm j}_\ell(k \chi) \, {\rm j}_\ell(k \chi^\prime) .
-  \label{eq:P_ell_gamma}
-\end{align}
-%
-
-\mk{I can get this by placing the prefactor under the integral and
-setting $\ell^4 = k^4 \chi^2 {\chi^\prime}^2$. This does not seem to be the proper way.
-Other derivations of the shear power spectrum (e.g.\cite{BS01} also assume other approximations
-such as small-angle and Limber, but I do not know how to derive this without Limber.}
+  \label{eq:P_ell_gamma_full_der}
+\end{align}
+%
+with flat-sky prefactor $p(\ell) = \ell^4$.
+\mk{See App.~\ref{sec:schmidt08} and \ref{sec:giannantonio12} for discussions of alternative expressions of the flat-sky power spectrum.}
 
@@
 galaxy shape catalogue. The basic quantity is the two-point correlation
-function \citep{miraldaescude:1991}, which is given by
-%
-\begin{eqnarray}
+function \citep{1991ApJ...370....1M}, which is given by
+%
+\begin{align}
   \xi_+(\theta) 
@@
    \label{eqn:xiGG}
-\end{eqnarray}
+\end{align}
 %
@@
 a second-order extended Limber approximation \citep[for more details see][and
-references therein]{miraldaescude:1991, kaiser:1992,
-bartelmann/schneider:2001}.
+references therein]{1991ApJ...370....1M,1992ApJ...388..272K,
+BS01}.
 
@@
     The theoretical model corresponds to the CFHTLenS best-fit parameters with
-    $\Omega_{\rm m} = 0.279$, $h=0.701$, and $\sigma_8 = 0.79$ \citep{CFHTLenS-2pt-notomo},
+    $\Omega_{\rm m} = 0.279$, $h=0.701$, and $\sigma_8 = 0.79$ \citep{2015arXiv150201589P},
     except the red dashed curve with adapts a Planck-best fit
@@
 The authors thank Tommaso Giannantonio, Sarah Bridle, Ami Choi, Donnacha Kirk, Lance Miller, Benjamin Joachimi, Chris Blake and Adam Amara for very helpful discussions.
-This work was financially supported by the DFG (Emmy Noether grants Hi 1495/2-1 and SI 1769/1-1; TR33 `The Dark Universe'), the Alexander von Humboldt Foundation, the ERC (grants 279396, 647112), the Seventh Framework Programme of the European Commission (Marie Sklodwoska Curie Fellowship grant 656869), NSERC and CIfAR.
-
-\ch{Check your acknowledgements}
 
@@
 \subsection{Schmidt (2009)}
+\label{sec:schmidt08}
 
@@
 function $W_\kappa$ (eq.~10) in terms of the lensing efficiency and comoving distances,
-$W_\kappa[z(\chi)] = H(z)^{-1} \chi q(\chi)$, we
-%
+$W_\kappa[z(\chi)] = H(z)^{-1} \chi q(\chi)$, their expression, using our notations, reads
+%
+\begin{align}
+  P_{ij}^\gamma(\ell) = & \frac 2 \pi \, \pref^2
+                 \int_{0}^{\chi_{\rm lim}} {\rm d} \chi \chi \, \frac{q_i(\chi)}{a(\chi)}
+                \int_{0}^{\chi_{\rm lim}} {\rm d} \chi^\prime\, \chi^\prime
+                \frac{q_j(\chi^\prime)}{a(\chi^\prime)}
+                \nonumber \\
+                & \times \int_0^\infty {\rm d} k \, k^2 \, P_{\rm m}(k; \chi, \chi^\prime) \,
+                {\rm j}_\ell(k \chi) \, {\rm j}_\ell(k \chi^\prime) ,
+  \label{eq:P_ell_gamma}
+\end{align}
+%
+This is consistent with our equation (\ref{eq:P_ell_gamma_full_der}) under the additional assumption that
+mainly modes with $k \chi \approx k \chi^\prime \approx \ell$ contribute to the integral; that is modes
+around the maxima of the Bessel functions. Then, we can draw out of the integral the factor $\ell^4 \approx k^4 \chi^2 {\chi^\prime}^2$,
+to recover (\ref{eq:P_ell_gamma_full_der}).
+\mk{This argument is very hand-wavey! In fact, using the approximation $k \chi = \ell$ seems to go too far, this is already halfway the Limber approximation.}
+
 %\begin{align}
@@
 %We
-recover our (\ref{eq:P_ell_gamma}).
 
 \subsection{Giannantonio et al. (2012)}
+\label{sec:giannantonio12}
 
@@
 is a factor $r_K[r(z)]$ missing in the window function, which translates into a
-missing $r_K[r] r_K[r^\prime]$ in the full projection integral\footnote{Typo confirmed by T.~G.,
-priv.~comm.}. This also leads to an errorous $r_K^{-2}(r)$ in the Limber
-equation (27). With these factors accounted for, we reproduce the expressions
-of \cite{2012MNRAS.422.2854G}.
+missing $r_K[r] r_K[r^\prime]$ in the full projection integral\footnote{Typo
+confirmed by T.~G., priv.~comm.}. This also leads to an errorous $r_K^{-2}(r)$
+in the Limber equation (27). With these factors accounted for, and making the
+additional approximation $k \chi \approx k \chi^\prime \ell$ (see
+App.~\ref{sec:schmidt08}) we reproduce the expressions of
+\cite{2012MNRAS.422.2854G}.
 

### 2017-02-09 authors.tex

@@
-\author[Heymans, Asgari, Joudaki et al.]
-{C. Heymans$^1$\thanks{Email: heymans@roe.ac.uk}, 
-M. Asgari$^1$, 
-S. Joudaki$^2$, 
-J. Harnois-D\'eraps$^1$,
-H. Hildebrandt$^3$,
+\author[M.~Kilbinger et~al.]
+{Martin Kilbinger$^{1,2}$\thanks{E-mail: martin.kilbinger@cea.fr},
+Catherine Heymans$^3$,
+Marika Asgari$^3$, 
+Shahab Joudaki$^4$, 
 \newauthor
-M. Kilbinger$^4$,
-F. K\"ohlinger$^5$,
-K. Kuijken$^5$,
-P. Schneider$^3$,
-P. Simon$^3$,
+Peter Schneider$^5$,
+Patrick Simon$^5$,
+Joachim Harnois-D\'eraps$^3$,
+Hendrik Hildebrandt$^5$,
 \newauthor
-L. Van Waerbeke$^6$,
-M. Viola$^5$
+Fabian K\"ohlinger$^6$,
+Konrad Kuijken$^6$,
+Ludovic Van Waerbeke$^7$ and
+Massimo Viola$^6$
 \\
-$^1$Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK\\
-$^2$Centre for Astrophysics \& Supercomputing, Swinburne University of Technology, PO Box 218, Hawthorn, VIC 3122, Australia\\
-$^3$Argelander-Institut f\"ur Astronomie, Auf dem H\"ugel 71, 53121 Bonn, Germany\\
-$^4$Laboratoire AIM, CEA Saclay - CNRS - Paris 6, Irfu/SAp, F-91191 Gif-sur-Yvette, France\\
-$^5$Leiden Observatory, Leiden University, Niels Bohrweg 2, 2333 CA Leiden, the Netherlands\\
-$^6$Department of Physics and Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC V6T 1Z1, Canada\\
+$^1$CEA/Irfu/SAp Saclay, Laboratoire AIM, 91191 Gif-sur-Yvette, France\\
+$^2$Institut d'Astrophysique de Paris, UMR7095 CNRS, Universit\'e Pierre \& Marie Curie, 98 bis boulevard Arago, 75014 Paris, France \\
+$^3$Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK\\
+$^4$Centre for Astrophysics \& Supercomputing, Swinburne University of Technology, PO Box 218, Hawthorn, VIC 3122, Australia\\
+$^5$Argelander-Institut f\"ur Astronomie, Auf dem H\"ugel 71, 53121 Bonn, Germany\\
+$^6$Leiden Observatory, Leiden University, Niels Bohrweg 2, 2333 CA Leiden, the Netherlands\\
+$^7$Department of Physics and Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC V6T 1Z1, Canada\\
 }

### 2017-02-09 cfhtlens.tex

@@
 large scales.}
-\item{\cite{2012ApJ...761..152T} provided a more accurate non-linear power
+\item{\cite{asgari/etal:2017} provided a more accurate non-linear power
 spectrum correction than that used in the original CFHTLenS analyses, and the

### 2017-02-09 cfhtlens.tex
MK small changes

--- 2017-02-09 cfhtlens.tex
@@
 %
- \item{\citet{2016arXiv160100115A} used the stringent COSEBI statistic
-\cite{COSEBIs} to identify significant non-lensing B-mode distortions when the
+ \item{\cite{asgari/etal:2017} used the stringent COSEBI statistic
+\citep{COSEBIs} to identify significant non-lensing B-mode distortions when the
 CFHTLenS data was split into tomographic slices.}
@@
 large scales.}
+%
 \item{\cite{2012ApJ...761..152T} provided a more accurate non-linear power
@@
 result that was published in \cite{CFHTLenS-2pt-notomo}. Using the second-order
-extended Limber flat-sky approximation results in \ch{$\sigma_8 (\Omega_{\rm
-m}/0.27)^{0.6} =X^{+X}_{-X}$}, a negligible change of $X\sigma$.
+extended Limber flat-sky hybrid approximation (ExtL2FlHyb) results in
+$\sigma_8 (\Omega_{\rm m}/0.27)^{0.6} = 0.788 \pm 0.032$, a negligible
+change of the amplitude that is well within the Monte-Carlo sampling noise.
 
@@
   ExtL1FlHyb & $0.788^{+0.031}_{-0.033}$ & $0.740^{+0.029}_{-0.031}$ & Used for post-2014 CFHTLenS, KiDS \\
-  ExtL2FlHyb & $0.788^{+0.032}_{-0.032}$ & $0.749^{+0.030}_{-0.030}$ & Best flat-sky approximation \\
+  ExtL2FlHyb & $0.788^{+0.032}_{-0.032}$ & $0.740^{+0.030}_{-0.030}$ & Best flat-sky approximation \\
   ExtL2Sph   & $0.789^{+0.031}_{-0.032}$ & $0.740^{+0.029}_{-0.030}$ & Best approximation but mixing with flat-sky Hankel transform \\ \hline

### 2017-02-09 limber2.tex
MK minor changes

@@
 spectrum of the lensing potential between two redshift bins $i$ and $j$,
-$C_{ij}^\psi$ is then defined by \cite{pee80}
+$C_{ij}^\psi$ \citep{pee80} is then defined as
 %
@@
 where ${\rm j}_\ell$ it the spherical Bessel function of order $\ell$. For
-convenience we defined the normalisation constant $\pref$ as
+convenience we introduce the normalisation constant $\pref$ as
 %
@@
 %
-The spherical prefactor $\sqrt{(\ell-1) \ell (\ell+1) (\ell+2)}$ is replaced by $\ell^2$ in flat coordiates.
+The spin prefactor $\sqrt{(\ell-1) \ell (\ell+1) (\ell+2)}$ is replaced by $\ell^2$ in flat coordiates.
 We find for the flat-sky shear power spectrum

### 2017-02-09 cfhtlens.tex
Post-read-through edits Mainly typos and putting in the word equation to make it MNRAS compliant A couple of notes for you in purple. I think this is more-or-less ready to circulate

@@
 to account for bias and scatter, with a prediction that accounting for these
-biases would be {\it reduce} the recovered amplitude of $\sigma_8$ by $\sim
+biases would {\it reduce} the recovered amplitude of $\sigma_8$ by $\sim
 4$\%.}
@@
 original CFHTLenS results impact in different ways the cosmological conclusions
-that one can draw from the survey. As CFHTLenS has similar statistical power
+that one can draw. As CFHTLenS has similar statistical power
 to current weak lensing surveys, however, it nevertheless provides a very
@@
 function $\xi_\pm(\theta)$ from \cite{CFHTLenS-2pt-notomo}, defined in
-(\ref{eqn:xiGG}). As in \cite{CFHTLenS-2pt-notomo} we fit both components
+equation~(\ref{eqn:xiGG}). As in \cite{CFHTLenS-2pt-notomo} we fit both components
 $\xi_+$ and $\xi_-$ between angular scales $\theta = 0.8$ and $350$ arc
@@
 software \textsc{CosmoPMC}\footnote{\texttt{http://www.cosmostat.org/software/cosmopmc}}
-\citep{WK09,KWR10}. The cosmological modelling part including the various
-lensing projections are performed with the library
+\citep{WK09,KWR10}. The cosmological modelling part includes the various
+lensing projections, calculated using the software library
 \textsc{nicaea}\footnote{\texttt{http://www.cosmostat.org/software/nicaea}}.
@@
 %\subsubsection{Cosmological parameter results}
-\label{ref:cosmo_results}
+%\label{ref:cosmo_results}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{centering}
-  \label{tab:CFHTLenS_Sigma8}
 
-  \caption{Mean and 68\% credible interval for 
+  \caption{\label{tab:CFHTLenS_Sigma8}Mean and 68\% confidence interval for 
   $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$ for various approximations to the lensing
-  power spectrum projections.}
+  power spectrum projections listed in Table~\ref{tab:cases}.}
 

### 2017-02-09 conclusions.tex
Post-read-through edits Mainly typos and putting in the word equation to make it MNRAS compliant A couple of notes for you in purple. I think this is more-or-less ready to circulate

@@
 In this paper we evaluate precision theoretical calculations for cosmic shear observables, bringing together different sources from the literature to provide a pedagogical review of the impact of adopting flat-sky and Limber approximations.
-We demonstrate that for current surveys, such as CFHTLenS, these approximations have a negligible impact on cosmological parameter constraints, in contrast to the recent claim in \citet{2016arXiv161104954K}.
+We demonstrate that for current surveys, such as CFHTLenS, these approximations have a negligible impact on cosmological parameter constraints.
 

### 2017-02-09 discussion.tex
Post-read-through edits Mainly typos and putting in the word equation to make it MNRAS compliant A couple of notes for you in purple. I think this is more-or-less ready to circulate

@@
 percent, on angular scales $\theta > 300$ arcmin.    This is a result of the
-significant weight given to low $\ell$ modes in the $\xi_+$ statistic, as
+weight given to low $\ell$ modes in the $\xi_+$ statistic, as
 illustrated in Figure~\ref{fig:filters} which shows the integrand of $\xi_+$
@@
 scales.  It will however become increasingly important for upcoming wider-field
-surveys which will accurately probe these scales.
+surveys that will accurately probe these scales.
 
 In this paper we provide a solution in the form of the second-order extended
-Limber approximation, but another option is to consider alternative two-point
+Limber approximation, but another option to consider is the used of alternative two-point
 shear statistics that are less sensitive to accuracy in shear power spectrum
 measurement at low $\ell$.   Both the aperture-mass dispersion, $\langle M_
-{\rm ap}^2 \rangle2$ \citep{1998MNRAS.296..873S}, and the Complete Orthogonal
+{\rm ap}^2 \rangle$ \citep{1998MNRAS.296..873S}, and the Complete Orthogonal
 Sets of E/B-mode Integrals (COSEBIs), $E_n$ \citep{COSEBIs} statistics satisfy
 this requirement and are linearly related to the shear power spectrum in the
-flat-sky approximation via integrals of the form (omitting tomographic
-indices),
+flat-sky approximation via integrals of the form 
 %

### 2017-02-09 limber2.tex
Post-read-through edits Mainly typos and putting in the word equation to make it MNRAS compliant A couple of notes for you in purple. I think this is more-or-less ready to circulate

@@
 second-order Limber approximation will provide sufficient accuracy, as it is in 
-agreement with the full projection at the percent level for $\ell > 3$.  
+agreement with the full projection at the sub-percent level for $\ell > 3$.  
 In the spirit of reproducible research, our numerical implementation of all approximations
@@
 predictions of the observables to ensure that the accuracy of the
-models meet the accuracy of the upcoming data. In this paper, we examine the widely used Limber
+models meet the accuracy of the observations. In this paper, we examine the widely used Limber
 approximation for the projected weak-lensing power spectrum. We consider
 spherical coordinates and the flat-sky approximation, and compute the full
-projection as well as first- and second-order Limber approximation. We show
-that the second-order Limber approximation is an accurate representation of the full projection, with better than percent level precision for scale $\ell > 3$. 
+projection. We show
+that the second-order Limber approximation is an accurate representation of the full projection, with better than percent level precision for scales $\ell > 3$. 
 Since this approximation involves only 1D integrals over the matter power spectrum, it is very fast to
@@
 and commonly-used two-point shear correlation function for the full solution to
-a range of different approximations in section~\ref{sec:comp}, providing
+a range of different approximations in section~\ref{sec:results}, providing
 cosmological constraints for each case using CFHTLenS data from
-\citet{CFHTLenS-2pt-notomo} in section~\ref{sec:cfhtlens}. This paper draws
+\citet{CFHTLenS-2pt-notomo}. This paper draws
 from several sources of literature which have previously discussed the full
@@
 %
-corresponding to a population of lensed galaxies with normalised source
+corresponding to a population of lensed galaxies with a normalised source
 redshift distribution $n(z) {\rm d}z = n(\chi) {\rm d} \chi$. Here, ${\rm c}$
@@
 
-The form of the lensing efficiency $q$ (\ref{eq:lens_efficiency}) assumes a
+The form of the lensing efficiency $q$ in equation (\ref{eq:lens_efficiency}) assumes a
 homogeneous galaxy distribution without clustering, so that the redshift
@@
 
-Following \cite{2000PhRvD..62d3007H} we decompose the lensing potential
-(\ref{eq:psi}) into a spherical harmonics expansion, in analogy of CMB
+Following \cite{2000PhRvD..62d3007H} we decompose the lensing potential (equation~\ref{eq:psi}) into a spherical harmonics expansion, in analogy of CMB
 temperature, both of which are scalar functions on the sphere. This
@@
 of lensing efficiency functions $q_i$ defined by a corresponding family of
-redshift distributions $n_i$ via eq.~(\ref{eq:lens_efficiency}). The resulting
+redshift distributions $n_i$ via equation~(\ref{eq:lens_efficiency}). The resulting
 lensing potential is denoted by $\psi_{\ell m, i}$. The tomographic power
@@
 %
-where ${\rm j}_\ell$ it the spherical Bessel function of order $\ell$. For
+where ${\rm j}_\ell$ is the spherical Bessel function of order $\ell$. For
 convenience we introduce the normalisation constant $\pref$ as
@@
 
-In the following section we will discuss the relations between of shear and
-convergence to the lensing potential on the sphere, and derive the power
+In the following section we will discuss the relations between shear and
+convergence to the lensing potential, on the sphere, and derive the power
 spectrum of the former two fields.
@@
 insert the harmonics expansion of the potential (\ref{eq:psi_harm_exp}). This
-requires to compute second derivatives of the spherical harmonic functions.
-This opereration defines a new object, the \emph{spin-weighted spherical
+requires the calculation of second derivatives of the spherical harmonic functions.
+This operation defines a new object, the \emph{spin-weighted spherical
 harmonic} $_s{\rm Y}_{\ell m}$. The shear can be written on the sphere in terms
@@
 The spin-weighted spherical harmonics $_s\!{\rm Y}_{\ell m}$ that are the basis function
-in the expansion of the shear (\ref{eq:gamma_harm_exp}) can be calculated via the relations
+in the expansion of the shear (equation~\ref{eq:gamma_harm_exp}) can be calculated via the relations
 %
@@
 %
-with the spin prefactor \citep{2012PhRvD..86b3001B}
+with the spin pre-factor \citep{2012PhRvD..86b3001B}
 %
@@
 %
-Inserting the lensing potential expansion (\ref{eq:psi_harm_exp}) into the
-expression for the shear (\ref{gamma_psi_spher}), and using (\ref{eq:sYlm_def})
+Inserting the lensing potential expansion (equation~\ref{eq:psi_harm_exp}) into the
+expression for the shear (equation~\ref{gamma_psi_spher}), and using equation~(\ref{eq:sYlm_def})
 to compute the derivatives, we find for the shear expansion coefficients
@@
 
-The tomographic shear power spectrum, in analogy to (\ref{eq:C_ell_phi_Pm}), is defined by
+The tomographic shear power spectrum, in analogy to equation~(\ref{eq:C_ell_phi_Pm}), is defined by
 %
@@
 %
-The spherical prefactor for the full projection power spectrum is $p(\ell) :=
+The spherical pre-factor for the full projection power spectrum is $p(\ell) :=
 \ellbar^2(\ell, 2)$, which will be modified under flat-sky and Limber
@@
   \nabla^2 {\rm Y}_{\ell m}(\theta, \varphi) = - \ell (\ell + 1) {\rm Y}_{\ell m}(\theta, \varphi)
-    = - \ellbar^2(\ell, 1) {\rm Y}_{\ell m}(\theta, \varphi),
+    = - \ellbar^2(\ell, 1) {\rm Y}_{\ell m}(\theta, \varphi).
   \label{eq:nabla_Ylm}
@@
 The convergence power spectrum is then similar to the shear power spectrum
-(\ref{eq:C_ell_gamma}) with a different spherical prefactor,
+(equation~\ref{eq:C_ell_gamma}) with a different spherical pre-factor, \citep{jk12}
 %
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Most previous work has used lensing quantities approximated on a flat sky,
+The majority of cosmic shear analyses have used lensing quantities approximated on a flat sky,
 neglecting the sky curvature. This is a valid approach for past and current
-survey areas that have extents up to 10 degrees or less. The correlation
-functions from the observed shear have been calculated using spherical
-coordinates, and the effect on large scales is not negligible \citep{FSHK08}.
+survey areas with extents less than 10 degrees. The correlation
+functions from the observed shear have, however, been calculated using spherical
+coordinates, and the effect on large scales has been shown to be significant \citep{FSHK08}.
 Here we examine the effect of sky curvature on the theoretical models.
 
-For a flat sky, the spherical harmonics expansions are approximated by Fourier
-transforms. The flat-sky equivalent of eqs.~(\ref{eq:psi_harm_exp}) and
+For a flat sky, the spherical harmonic expansions are approximated by Fourier
+transforms. The flat-sky equivalent of equations.~(\ref{eq:psi_harm_exp}) and
 (\ref{eq:psi_harm_exp_inv}) are
@@
 
-The flat-sky power spectrum, the flat-sky analogon of (\ref{eq:C_ell_psi}) is defined by
+The flat-sky power spectrum, the flat-sky analogue of equation~(\ref{eq:C_ell_psi}) is defined by
 %
@@
 \cite{2000PhRvD..62d3007H} have shown that for small angles the harmonics
-expansion (\ref{eq:psi_harm_exp}) can be approximated by the the Fourier
-representation (\ref{eq:psi_fourier}). They also demonstrated that the power
+expansion (equation~\ref{eq:psi_harm_exp}) can be approximated by the Fourier
+representation in equation~\ref{eq:psi_fourier}). They also demonstrated that the power
 spectra are approximately equal, $P^\psi \approx C^\psi$.
@@
 For a spin-2 field, \cite{2000PhRvD..62d3007H} approximates the edth operator by Cartesian derivatives, and approximates
-(\ref{eq:sYlm_def}) as
+equation~(\ref{eq:sYlm_def}) as
 %
@@
 %
-The spin prefactor $\sqrt{(\ell-1) \ell (\ell+1) (\ell+2)}$ is replaced by $\ell^2$ in flat coordiates.
+The spin pre-factor $\sqrt{(\ell-1) \ell (\ell+1) (\ell+2)}$ is replaced by $\ell^2$ in flat co-ordinates. \ch{@MK - say why this is so.  Is it just that flat by definition means large $\ell$?}
 We find for the flat-sky shear power spectrum
@@
 %
-with flat-sky prefactor $p(\ell) = \ell^4$.
-\mk{See App.~\ref{sec:schmidt08} and \ref{sec:giannantonio12} for discussions of alternative expressions of the flat-sky power spectrum.}
+with flat-sky pre-factor $p(\ell) = \ell^4$. 
+See App.~\ref{sec:schmidt08} and \ref{sec:giannantonio12} for discussions of alternative expressions for the flat-sky power spectrum.
 
@@
 %
-in eq.~(\ref{eq:C_ell_full}), where ${\rm J}_\ell$ is the first-kind Bessel
+in equation~(\ref{eq:C_ell_full}), where ${\rm J}_\ell$ is the first-kind Bessel
 function of order $\ell$. Next, \cite{2008PhRvD..78l3506L} solve integrals of
@@
 
-To separate the $k$- and $\chi, \chi^\prime$-terms in (\ref{eq:C_ell_full}), we
+To separate the $k$- and $\chi, \chi^\prime$-terms in equation~(\ref{eq:C_ell_full}), we
 first approximate the matter power cross-spectrum between two distances as
@@
 \begin{equation}
- P_{\rm m}(k; \chi, \chi^\prime) = \sqrt{ P_{\rm m}(k; \chi) P_{\rm m}(k; \chi^\prime) }
+ P_{\rm m}(k; \chi, \chi^\prime) = \sqrt{ P_{\rm m}(k; \chi) P_{\rm m}(k; \chi^\prime) } \, .
   \label{eq:P_geom_mean}
@@
 %
-With this, eq.~(\ref{eq:C_ell_full}) is written as
+With this, equation~(\ref{eq:C_ell_full}) is written as
 %
@@
                 \int_{0}^\infty \frac{{\rm d} \chi^\prime}{{\chi^\prime}^{3/2}}
-                \sqrt{P_{\rm m}(k; \chi^\prime)} \frac{q_j(\chi^\prime)}{a(\chi^\prime)} {\rm J}_{\ell+1/2}(k \chi^\prime)
+                \sqrt{P_{\rm m}(k; \chi^\prime)} \frac{q_j(\chi^\prime)}{a(\chi^\prime)} {\rm J}_{\ell+1/2}(k \chi^\prime) \, .
   \label{eq:C_ell_full_Pk}
@@
 We replaced the upper limits of the distance integral with infinity. \mk{Comment on this.}
-Note that this equation has a preactor $\ellbar^2(\ell, 2)$ corresponding to a spin-2 field, in contrast
+Note that this equation has a pre-factor $\ellbar^2(\ell, 2)$ corresponding to a spin-2 field, in contrast
 to \cite{2008PhRvD..78l3506L} who show calculations for a scalar field.
@@
 %
-(Add indices $i, j$ to $f$ and $q$ for the tomographic case.)
-%
-Replacing both distance integrals in (\ref{eq:C_ell_full_Pk}) by their Taylor-expansions around $\nu = k \chi$ and $\nu = k \chi^\prime$,
+\mk{Add indices $i, j$ to $f$ and $q$ for the tomographic case.}{\ch Do we want to do this?}
+%
+Replacing both distance integrals in equation~(\ref{eq:C_ell_full_Pk}) by their Taylor-expansions around $\nu = k \chi$ and $\nu = k \chi^\prime$,
 respectively, yields
@@
     \left[ f_j(k, \chi) - \frac{1}{2 k^2} f_j^{\prime\prime}(k, \chi)
-    - \frac{\nu}{6 k^3} f_j^{\prime\prime\prime}(k, \chi) + \ldots \right]
+    - \frac{\nu}{6 k^3} f_j^{\prime\prime\prime}(k, \chi) + \ldots \right] \, .
   \label{eq:C_ell_limber2_dk}
@@
     \right]
-    \right\}
+    \right\} \, .
     %\Bigg\}
@@
 The first term corresponds to the well-known first-order Limber approximation
-\cite{1953ApJ...117..134L,1992ApJ...388..272K}, which is very widely used in
+\citep{1953ApJ...117..134L,1992ApJ...388..272K}, which is widely used in
 weak gravitational lensing. We retrieve the (spherical) standard expression by
-inserting back the projection kernel (\ref{eq:f_LA08}) and the time-dependent
+inserting back the projection kernel equation~(\ref{eq:f_LA08}) and the time-dependent
 power spectrum,
@@
 
-The second-order Limber term in (\ref{eq:C_ell_limber12_dr}) has an additional
+The second-order Limber term in equation~(\ref{eq:C_ell_limber12_dr}) has an additional
 $\nu^{-2}$-dependence, and is therefore strongly suppressed for large $\ell$.
@@
       \right)
-    \right](\nu/\chi, \chi)
+    \right](\nu/\chi, \chi) \, .
   \label{eq:C_ell_limber2_dr} 
@@
 arguments, $\nu$ and $\chi$. In the following section, we will separate the
-$k$- and $\chi$-dependend parts of the power spectrum to make the numerical
+$k$- and $\chi$-dependent parts of the power spectrum to make the numerical
 derivatives faster and more smooth.
@@
 
-To further develop (\ref{eq:P_geom_mean}), we divide out the growth factor to
+To further develop equation~(\ref{eq:P_geom_mean}), we divide out the growth factor to
 define a redshift-independent power spectrum $P_{\rm m}(k)$,
@@
 
-With this approximation, the $k$-independent term factors out from
-(\ref{eq:f_LA08}), and we define the separated kernel function $f_{\rm s}$ as
-%
-\begin{equation}
-  f_{\rm s}(\chi) = D_+(\chi) a^{-1}(\chi) \chi^{-3/2} q(\chi).
+With this approximation, the $k$-independent term factors out from equation~(\ref{eq:f_LA08}), and we define the separated kernel function $f_{\rm s}$ as
+%
+\begin{equation}
+  f_{\rm s}(\chi) = D_+(\chi) a^{-1}(\chi) \chi^{-3/2} q(\chi) \, ,
   \label{eq:f_LA08_s}
@@
 %
-and does not need to be considered when taking the derivatives with respect to comoving distances.
+\ch{?? and - do you mean which?} does not need to be considered when taking the derivatives with respect to comoving distances.
 The second-order Limber term of the shear power spectrum can then be simplified to
@@
 We compute the numerical higher derivatives as follows. The functions $f_{\rm
-s}(\chi)$ are fitted as power laws with index $\approx 1.5$. The fit is
+s}(\chi)$ are fit as power laws with index $\approx 1.5$. The fit is
 performed between $\chi_{\rm min} = 0.001 {\rm Mpc}/h$ and $\chi_{\rm max} =
@@
 derivaties are larger due to the steeper decline, the associated errors are
-very small since those scales are down-weighed by the kernel function $f_{\rm
+very small as these scales are down-weighed by the kernel function $f_{\rm
 s}$ itself. At $\chi = 500 \mbox{Mpc}/h$ the filter function is less than
@@
 The extended flat-sky Limber approximation is readily derived from the
-spherical case, by replacing the prefactor $\ellbar^2(\ell, 2)$ with $\ell^4$,
+spherical case, by replacing the pre-factor $\ellbar^2(\ell, 2)$ with $\ell^4$,
 %
@@
 %
-Different further approximations are commonly made for the prefactor $p(\ell) = \ell^4/\nu^4$ and $\nu(\ell)$:
+Further approximations are commonly made for the pre-factor $p(\ell) = \ell^4/\nu^4$ and $\nu(\ell)$:
 %
@@
   \item $p(\ell) = 1$, this corresponds to $\nu(\ell) = \ell$, which is the \emph{standard} Limber approximation.
-    Until recently, i.e.~for all pre-2014 CFHTlenS results, this was the approximation of choice.
+    Until recently, i.e.~for all pre-2014 CFHTLenS results, this was the approximation of choice.
   \item $p(\ell) = \ell^4/(\ell + 1/2)^4$. This corresponds to the \emph{extended} Limber
     approximation with $\nu(\ell) = \ell + 1/2$; however the following case is typically employed:
-  \item $p(\ell) = 1$, but as the argument of the 3D power spectrum $\nu = \ell + 1/2$. This is
+  \item $p(\ell) = 1$, with $\nu = \ell + 1/2$. This is
     a \emph{hybrid} between
     standard and extended Limber approximation, and was used in \cite{KiDS-450,joudaki/etal:2016}. As is shown
-    later, this is a much better approximation to the full projection than case (ii).
+    later, this is a better approximation to the full projection than case (ii).
 \end{enumerate}
+\ch{@MK - in the second order hybrid case does $\ell^4 / \nu^6$ become $\ell^{-2}$ or 1?.  Would this section be clearer if we had $p(\ell)$ in the equations instead of 
+$\ell^4/\nu^4$?}
 
@@
 
-In Fig.~\ref{fig:Cl_cases} we plot the full spherical projection of the shear power spectrum in comparison to shear power spectra derived assuming
+In Fig.~\ref{fig:Cl_cases} we present the full spherical projection of the shear power spectrum in comparison to shear power spectra derived assuming
 the range of different approximations listed in Table~\ref{tab:cases}.  The adopted redshift distribution corresponds to CFHTLenS
@@
 \begin{equation}
-p(\ell) = \frac{(\ell+2)(\ell+1)\ell(\ell-1)}{(\ell + 0.5)^4} = 1-{5\over 2\ell^2} +{\cal O}(\ell^{-3}) \, .
+p(\ell) = \frac{(\ell+2)(\ell+1)\ell(\ell-1)}{(\ell + 0.5)^4} = 1-{5\over 2\ell^2} +{\cal O}(\ell^{-3}) \, ,
 \end{equation}
@@
 \begin{equation}
-p(\ell) = \ell^4 / (\ell + 0.5)^4 = 1-{2\over \ell}+{5\over 2\ell^2} +{\cal O}(\ell^{-3}) \, , 
+p(\ell) = \ell^4 / (\ell + 0.5)^4 = 1-{2\over \ell}+{5\over 2\ell^2} +{\cal O}(\ell^{-3}) \, . 
 \end{equation} 
@@
 The numerical calculation of the second-order extended Limber approximation is a factor of \ch{X} faster than the calculation of the full spherical solution.
-We note that the noise seen in the right panel of Fig.~\ref{fig:Cl_cases} is due to numerical noise arising from numerical integration errors the full spherical solution calculation for
-$\ell > 20$.  Increasing numerical precision would increase the calculation time still further, relative to the  second-order extended Limber calculation.
+We note that the noise seen in the right panel of Fig.~\ref{fig:Cl_cases} is due to numerical noise arising from numerical integration errors in the calculation of
+the full spherical solution when $\ell > 20$.  Increasing numerical precision would increase the calculation time still further, relative to the  second-order extended Limber calculation.
 
@@
 
-  \caption{Shear power spectrum for different approximation. Limber to first order: standard with flat-sky (L1Fl),
+  \caption{\label{fig:Cl_cases}The shear power spectrum for different approximations listed in Table~\ref{tab:cases}. Limber to first order: standard with flat-sky (L1Fl),
         extended for flat sky (ExtL1Fl), extended hybrid for flat sky (ExtL1FlHyb),
@@
         and extended spherical expansion (ExtL2Sph); full (exact) spherical projection (FullSph).
-        The left panels show the total power spectrum.
-        See Table \ref{tab:cases} for more details on the different approximations.     
+        The left panel shows the total shear power spectrum.  The right panel shows the fractional difference resulting from each approximation, 
+        relative to the full spherical projection of the shear power spectrum.
         }
-
-  \label{fig:Cl_cases}
-
 \end{figure}
@@
 % limber_la08       ExtL1Fl     ELF             blue
-% limber_la08_hyb   ExtL1FlHyb  ESt             magenta                                           prefactor~1 despite nu=ell+1/2
+% limber_la08_hyb   ExtL1FlHyb  ESt             magenta                                           pre-factor~1 despite nu=ell+1/2
 % limber_la08_sph   ExtL1Sph    ELS             cyan
@@
 \begin{centering}
-  \label{tab:cases}
-  \caption{Shear power spectrum approximations compared in this paper. 'ID' is the abbrevation used in the plots.
-    The third column shows the power-spectrum prefactor $p(\ell)$. }  
+  \caption{\label{tab:cases}The shear power spectrum approximations studied in this paper. 'ID' is the abbrevation used in the figures.
+    The third column shows the power-spectrum pre-factor $p(\ell)$. }  
     \begin{tabular}{|l|l|c|c|c}
   \hline
-  Case & ID & eq.~ & prefactor & $\nu(\ell)$ \\ \hline
+  Case & ID & equation & $p(\ell)$ & $\nu(\ell)$ \\ \hline
   % 
@@
 
-Most cosmic shear analysis to date have been performed on real-space
-correlation statistics, since these can be measured direcaly from an observed
-galaxy shape catalogue. The basic quantity is the two-point correlation
-function \citep{1991ApJ...370....1M}, which is given by
+The majority of cosmic shear analyses to date have adopted real-space
+correlation statistics, since these can be measured directly from an observed
+galaxy shape catalogue. The baseline quantity is the two-point correlation
+function \citep{1991ApJ...370....1M, 1992ApJ...388..272K,
+BS01}, given by
 %
@@
 shear power spectrum $P^\gamma$ an be related to the underlying matter power
-spectrum through equation \ref{eq:P_ell_limber1} when adopting a first-order
-extended Limber approximation, or equation~\ref{eq:P_ell_limber2} when adopting
-a second-order extended Limber approximation \citep[for more details see][and
-references therein]{1991ApJ...370....1M,1992ApJ...388..272K,
-BS01}.
-
-On a sphere, correlation functions cannot be related to the power spectrum by a
-Hankel transform in equation~\ref{eqn:xiGG}, as the spherical power spectrum is
+spectrum through equation~(\ref{eq:P_ell_limber1}) when adopting a first-order
+extended Limber approximation, or equation~(\ref{eq:P_ell_limber2}) when adopting
+a second-order extended Limber approximation.
+
+On a sphere, correlation functions cannot be related to the power spectrum by the
+Hankel transform in equation~(\ref{eqn:xiGG}), as the spherical power spectrum is
 formally not defined for non-integer $\ell$ \citep[see][for alternative
@@
 function]{2005PhRvD..72b3516C}. In particular, the spherical Bessel functions
-necessary to compute the full projection (\ref{eq:C_ell_full}) is defined only
+necessary to compute the full projection in equation~(\ref{eq:C_ell_full}) is defined only
 for integer order $\ell$. \mk{Is this really true?}
 
-However, in the Limber approximations the Bessel functions expanded to by
-polynomials, allowing for arbitrary wave modes $\ell$. The spherical prefactor
-$\ellbar(\ell, 2)$ (\ref{eq:ellbar}) can be generalised to non-integer
+As we have shown in section~\ref{sec:comp}, however, the spherical
+second-order extended Limber approximation provides a percent-level precision
+representation of the full spherical projection for $\ell > 3$.  
+In the Limber approximations the Bessel functions expanded \ch{to by ?? which one??}
+polynomials, allowing for arbitrary wave modes $\ell$. The spherical pre-factor
+$\ellbar(\ell, 2)$ (equation~ref{eq:ellbar}) can be generalised to non-integer
 arguments and is positive for $\ell \le 2$. We can thus use the spherical power
 spectrum in the Limber approximations for the Hankel transformation to compute
-the two-point correlation functions, This is not entirely consistent, but
-serves the purpose of comparison to the flat-sky case.
-
-In addition, as we have shown in section~\ref{sec:comp} that the spherical
-second-order extended Limber approximation provides a percent-level precision
-representation of the full spherical projection for $\ell > 3$, we do not
+the two-point correlation functions.  We therefore do not
 present predictions for the two-point shear correlation function using the full
 spherical projection, instead choosing the spherical second-order extended
-Limber approximation (Ext2Sph) as our \mk{reference} in this case.
+Limber approximation (Ext2Sph) as our reference in this case.
 
@@
 Figure.~\ref{fig:Cl_cases}. As is clear by the red dotted curve, using the
-Planck cosmology \citep{2015arXiv150201589P} induces a much larger change in
-the amplitude of the shear correlation function than the different projection
+Planck cosmology \citep{2015arXiv150201589P} induces a significant change in
+the amplitude of the shear correlation function in comparison to the different projection
 methods.
@@
 
-  \caption{Shear correlation functions $\xi_+$ (\emph{left}) and $\xi_-$ (\emph{right}).
-    The lower panels shows the relative differences to the case ExtL2Sph,  see Table \ref{tab:cases} for the different
-    approximations and their symbols.
-    The theoretical model corresponds to the CFHTLenS best-fit parameters with
-    $\Omega_{\rm m} = 0.279$, $h=0.701$, and $\sigma_8 = 0.79$ \citep{CFHTLenS-2pt-notomo},
-    except the red dashed curve with adapts a Planck-best fit
+  \caption{The two-point shear correlation functions $\xi_+$ (\emph{left}) and $\xi_-$ (\emph{right}).  The upper panels
+  show the total shear correlation functions for the range of cases listed in Table~\ref{tab:cases}.
+    The lower panels shows the relative differences to the spherical sky second-order extended Limber approximation, (ExtL2Sph).
+     The theoretical models correspond to the CFHTLenS best-fit cosmological parameters with
+    $\Omega_{\rm m} = 0.279$, $h=0.701$, and $\sigma_8 = 0.79$ \citep{CFHTLenS-2pt-notomo}.  For comparison we
+    	also show, in the upper panels, the spherical sky second-order extended Limber approximation model for the Planck-best fit
     cosmology with $\Omega_{\rm m} = 0.3$, $h=0.67$ and $\sigma_8 = 0.83$ \citep{2015arXiv150201589P}.
@@
 
-The following derivations are detailed e.g.~in \cite{2000PhRvD..62d3007H} and
-\cite{2005PhRvD..72b3516C}.
+The following derivations are detailed in \cite{2000PhRvD..62d3007H} and
+\cite{2005PhRvD..72b3516C}, and are provided here for completeness.
 
@@
 To obtain the power spectrum of the lensing potential for a flat Universe, 
-we insert the lensing projection (\ref{eq:psi}) for $K=0$ into the
-inverse harmonics expansion (\ref{eq:psi_harm_exp_inv}) and write the 3D potential
-as its Fourier transform (\ref{eq:hatPhi_inv}) to get
+we insert the lensing projection (equation~\ref{eq:psi}) for $K=0$ into the
+inverse harmonics expansion (equation~\ref{eq:psi_harm_exp_inv}) and write the 3D potential
+as its Fourier transform (equation~\ref{eq:hatPhi_inv}) to get
 %
@@
 %
-
 Making use of the orthogonality of the spherical harmonics
@@
 %
-We take the absolute square and use the definition of the 3D potential power spectrum (\ref{eq:p_phi}),
-to arrive at expression (\ref{eq:C_ell_phi_Pphi}).
-
-$P_{\rm m}$ is the 3D matter power cross-spectrum at line-of-sight comoving
+We take the absolute square and use the definition of the 3D potential power spectrum (equation~\ref{eq:p_phi}),
+to arrive at the expression in equation~(\ref{eq:C_ell_phi_Pphi}).
+Here, $P_{\rm m}$ is the 3D matter power cross-spectrum at line-of-sight comoving
 Fourier mode $k$ and comoving distances $\chi$ and $\chi^\prime$. We denote
@@
 the orthogonality of the spherical harmonics to resolve the spherical integral. 
-This leads to the potential power spectrum (\ref{eq:C_ell_phi_Pm}).
+This leads to the potential power spectrum in equation~(\ref{eq:C_ell_phi_Pm}).
 
@@
 In this section we briefly discuss previously published work on the full
-projection and second-order Limber equation of the lensing power spectrum. We
-compare those results with our findings.
+projection and second-order Limber equation of the lensing power spectrum, cross-checking and comparing their
+results with our independent findings.
+
+\ch{MNRAS rules;  equation when you refer to your equation.  Equation when it is in another paper.}
 
@@
 power spectrum, which they present as spherical-radial representation the 3D
-shear field. Our results (\ref{eq:C_ell_full}) correspond to their equations
-(7) and (8) for a flat Universe and in the case of perfect photometric
-redshifts, $p(z | z_{\rm p}) = \delta_{\rm D}(z - z_{\rm p})$, and for a bin
+shear field. Our results in equation~(\ref{eq:C_ell_full}) corresponds to their Equations
+(7) and (8) assuming a flat Universe and the case of perfect photometric
+redshifts, with $p(z | z_{\rm p}) = \delta_{\rm D}(z - z_{\rm p})$, and for a bin
 function that selects the redshift bin $i$, $W^{\rm SR}(z, z_{\rm p}) = 1_{z
-\in i-\mbox{th bin}}$. In \cite{2016arXiv161104954K} eq.~(7) the factor $2/\pi$
-is absent.
-
-In App.~A \cite{2016arXiv161104954K} derives the spherical and extended Limber
-approximation starting from the full spherical projection. Note that their
-filter function $q$ defined in (31) has an errornous additional factor of
-comoving distance $r$, and shows an additional factor of $\pi/2$.
-
-As shown in the main text of our paper,
-we can not reproduce the amplitude of the differences between the cases,
-neither for the power spectrum nor for the shear correlation function (see
-Figs.~\ref{fig:Cl_cases} and \ref{fig:xi_pm}).
+\in i-\mbox{th bin}}$. We find that Equation~(7) in \cite{2016arXiv161104954K} is missing a factor $2/\pi$.
+
+\cite{2016arXiv161104954K} derives the spherical and extended Limber
+approximation starting from the full spherical projection in their Appendix.~A.  We find that the
+filter function $q$ defined in their Equation~(31) has an additional factor of
+comoving distance $r$, and an additional factor of $\pi/2$.
+
+As shown in this paper, we are unable to reproduce the differences that \cite{2016arXiv161104954K} report,
+between the full spherical solution and the different approximations,
+neither for the power spectrum nor for the shear correlation function.
 
@@
 
-Eq.~(44) of \cite{2012PhRvD..86b3001B} is the non-tomographic full projection
+\cite{2012PhRvD..86b3001B} present the non-tomographic full projection
 $C(\ell)$ in the approximation of the 3D potential power spectrum $P^\Phi$ separating
-into $k$- and $\chi$-dependent functions. Their expression holds for a single
+into $k$- and $\chi$-dependent functions in their Equation~(44). Their expression holds for a single
 source redshift.
@@
 $D_+(a)/a$. Then, for a constant source comoving distance $\chi_{\rm S}$, the
-lensing efficiency (\ref{eq:lens_efficiency}) is $q(\chi) = (\chi_{\rm S} -
-\chi) \chi_{\rm S}^{-1}$, and the derivative of the separated kernel function
-(\ref{eq:f_LA08_s}) can be calculated analytically,
+lensing efficiency in equation~(\ref{eq:lens_efficiency}) is $q(\chi) = (\chi_{\rm S} -
+\chi) \chi_{\rm S}^{-1}$, and the derivative of the separated kernel function in equation~(\ref{eq:f_LA08_s}) can be calculated analytically,
 %
@@
           + \frac 1 {\chi_{\rm S}} \right) \frac{D_+(\chi)}{a(\chi)}.
+\label{eqn:B1}
 \end{equation}
@@
 
-Inserting this into the second-order Limber power spectrum
-(\ref{eq:C_ell_limber2_dr_s}) and using the inverse Poisson equation to replace
+Inserting equation~(\ref{eqn:B1}) into the second-order Limber power spectrum
+in equation~(\ref{eq:C_ell_limber2_dr_s}) and using the inverse Poisson equation to replace
 the matter with the potential power spectrum we obtain the same expression as
-\cite{vande2012} (their eq.~7.19), except for an additional factor $a^2(\chi)$.
+\cite{vande2012} (their Equation.~7.19), except for an additional factor $a^2(\chi)$.
 This difference is accounted for by the factor $a^{-1}$ in the propagation of
-primordial potential perturbations to late times, see eq.~(6.22) in
-\cite{vande2012}, where the transition is done using $g(a)$ instead of $D(a)$.
+primordial potential perturbations to late times, see Equation~(6.22) in
+\cite{vande2012}, where the transition is calculated using $g(a)$ instead of $D(a)$.
 \mk{Check this further.}
@@
 
-    \caption{Relative differences in percentage of spherical first- and second-order Limber
+    \caption{The relative differences in percentage of the spherical first- and second-order Limber
     shear power spectra with respect to the full projection
-    as function of wave mode $\ell$, see Table \ref{tab:cases}. The redshift distribution
-    is a single source plane at $z_{\rm S}=1$, and the cosmological parameters (see text) are chosen to match
-    \citet{vande2012}, see their Fig.~7.3 for comparison.
+    as function of wave mode $\ell$, (see Table \ref{tab:cases}). In this figure, the redshift distribution is chosen to be
+    at a single source plane at $z_{\rm S}=1$, with the cosmological parameters (see text) are chosen to match
+    \citet{vande2012}, see their Figure.~7.3 for comparison.
     }
@@
 clustering, their calculations are general enough to apply to a weak-lensing
-context. Their eq.~(5) is a spherical cross-power spectrum of two scalar fields
+context. Their Equation.~(5) is a spherical cross-power spectrum of two scalar fields
 $A$ and $B$, projected from 3D to 2D via projection kernels $F_A$ and $F_B$
-defined in their eq.~(4). Comparing their expressions with the weak-lensing
+defined in their Equation.~(4). Comparing their expressions with the weak-lensing
 potential (\ref{eq:psi}), we set $F_A(\chi) = F_B(\chi) = 2 c^{-2}
-D_+(\chi) q(\chi) \chi^{-1}$. With that, their eq.~(5) is identical to our
-(\ref{eq:C_ell_phi_Pphi}).
+D_+(\chi) q(\chi) \chi^{-1}$. With that, their Equations.~(5) is identical to equation~(\ref{eq:C_ell_phi_Pphi}).
 
@@
 presented in eq.~(12). This is consistent with our first-order
-(\ref{eq:C_ell_limber1}) and second-order (\ref{eq:C_ell_limber2_dr}) Limber
+(equation~\ref{eq:C_ell_limber1}) and second-order (equation~\ref{eq:C_ell_limber2_dr}) Limber
 approximation terms, when accounting for the difference between lensing
@@
 
-In eq.~(9) \cite{2008PhRvD..78d3002S} write the lensing power spectrum in the
-flat-sky limit. Inserting the Poisson factor $D_\phi$, 
+\cite{2008PhRvD..78d3002S} derive the lensing power spectrum in the
+flat-sky limit (see their Equation~(9)). Inserting the Poisson factor $D_\phi$, 
  the growth function $D_{\rm m}$, and writing the redshift filter
@@
 around the maxima of the Bessel functions. Then, we can draw out of the integral the factor $\ell^4 \approx k^4 \chi^2 {\chi^\prime}^2$,
-to recover (\ref{eq:P_ell_gamma_full_der}).
+to recover equation~(\ref{eq:P_ell_gamma_full_der}).
 \mk{This argument is very hand-wavey! In fact, using the approximation $k \chi = \ell$ seems to go too far, this is already halfway the Limber approximation.}
@@
 \label{sec:giannantonio12}
-
-In eqs.~(25) and (26) \cite{2012MNRAS.422.2854G} write the flat-sky lensing
-power spectrum. Their window function $W^{\varepsilon_i}$ defined in (25) for a
-flat Universe equals $\pref \times q(\chi) / a(\chi)$, since ${\rm d} z \,
+\cite{2012MNRAS.422.2854G} derive the flat-sky lensing
+power spectrum in their Equations.~(25) and (26) . Their window function $W^{\varepsilon_i}$ defined in their Equation~(25) for a
+flat Universe equals $\pref q(\chi) / a(\chi)$, since ${\rm d} z \,
 ({\rm d} N(z)/{\rm d} z) = {\rm d} \chi n(\chi)$; however due to a typo there
@@
 in the Limber equation (27). With these factors accounted for, and making the
-additional approximation $k \chi \approx k \chi^\prime \ell$ (see
-App.~\ref{sec:schmidt08}) we reproduce the expressions of
+additional approximation $k \chi \approx k \chi^\prime \ell$ (see their
+Appendix~\ref{sec:schmidt08}) we reproduce the expressions of
 \cite{2012MNRAS.422.2854G}.

### 2017-02-09 limber2.tex
MK: partially answered CH's questions; updated figures (less noise in FullSph)

@@
 
-\title[Precision calculations for cosmic shear]{Precision calculations for cosmic shear}  %??
+\title[Precision calculations for cosmic shear projections]{Precision calculations of cosmic shear projections}  %??
 %{Precision calculations of the cosmic shear power spectrum projection}
@@
 
-For a spin-2 field, \cite{2000PhRvD..62d3007H} approximates the edth operator by Cartesian derivatives, and approximates
-equation~(\ref{eq:sYlm_def}) as
-%
-\begin{equation}
-  \ell^2 \, _{\pm2}\!{\rm Y}_{\ell m}(\theta, \varphi) =  {\rm e}^{{\mp}2 {\rm i} \phi_\ell}
+For a spin-2 field, \cite{2000PhRvD..62d3007H} approximates the edth operator
+by Cartesian derivatives, and approximates equation~(\ref{eq:sYlm_def}) as
+%
+\begin{equation}
+  \ell^2 \, _{\pm2}\!{\rm Y}_{\ell m}(\theta, \varphi) \approx  {\rm e}^{{\mp}2 {\rm i} \phi_\ell}
     (\partial_1 \pm \partial_2)^2 \, {\rm Y}_{\ell m}(\theta, \varphi).
@@
 %
-The spin pre-factor $\sqrt{(\ell-1) \ell (\ell+1) (\ell+2)}$ is replaced by $\ell^2$ in flat co-ordinates. \ch{@MK - say why this is so.  Is it just that flat by definition means large $\ell$?}
-We find for the flat-sky shear power spectrum
+The spin pre-factor $\sqrt{(\ell-1) \ell (\ell+1) (\ell+2)}$ is replaced by
+$\ell^2$ in flat co-ordinates, \mk{an approximation that holds for large $\ell$.}
+ \ch{@MK - say why this is so.  Is it just that
+flat by definition means large $\ell$?} \mk{I think it's a large-ell approximation,
+but I don't know whether this is an assumption to derive this approximation, or whether it follows from that.
+I'll have to check this.}
+We find for the flat-sky shear power
+spectrum
 %
@@
   {\rm j}_\ell(x) = \sqrt{\frac{\pi}{2x}} {\rm J}_{\ell + 1/2}(x)
+  \label{eq:jJ}
 \end{equation}
@@
 
-With this approximation, the $k$-independent term factors out from equation~(\ref{eq:f_LA08}), and we define the separated kernel function $f_{\rm s}$ as
-%
-\begin{equation}
-  f_{\rm s}(\chi) = D_+(\chi) a^{-1}(\chi) \chi^{-3/2} q(\chi) \, ,
+With this approximation, the \mk{$\chi$-independent term $P_{\rm m}(k)$}
+factors out from equation~(\ref{eq:f_LA08}), and we define the separated kernel
+function $f_{\rm s}$ as
+%
+\begin{equation}
+  f_{\rm s}(\chi) = D_+(\chi) a^{-1}(\chi) \chi^{-3/2} q(\chi) \,
   \label{eq:f_LA08_s}
@@
 %
-\ch{?? and - do you mean which?} does not need to be considered when taking the derivatives with respect to comoving distances.
 The second-order Limber term of the shear power spectrum can then be simplified to
@@
 \end{enumerate}
-\ch{@MK - in the second order hybrid case does $\ell^4 / \nu^6$ become $\ell^{-2}$ or 1?.  Would this section be clearer if we had $p(\ell)$ in the equations instead of 
+%
+\ch{Would this section be clearer if we had $p(\ell)$ in the equations instead of 
 $\ell^4/\nu^4$?}
@@
 
-Considering now the spherical-sky cases, we find that including the spherical pre-factor decreases the difference between the extended Limber approximated cases (ExtL1Sph and ExtL2Sph) and the full spherical solution by a factor of a few for $\ell < 5$.
-We find that using the spherical-sky second-order extended Limber approximation (ExtL2Sph) yields percent accuracy down to $\ell > 3$.
-The numerical calculation of the second-order extended Limber approximation is a factor of \ch{X} faster than the calculation of the full spherical solution.
-We note that the noise seen in the right panel of Fig.~\ref{fig:Cl_cases} is due to numerical noise arising from numerical integration errors in the calculation of
-the full spherical solution when $\ell > 20$.  Increasing numerical precision would increase the calculation time still further, relative to the  second-order extended Limber calculation.
+Considering now the spherical-sky cases, we find that including the spherical
+pre-factor decreases the difference between the extended Limber approximated
+cases (ExtL1Sph and ExtL2Sph) and the full spherical solution by a factor of a
+few for $\ell < 5$.   We find that using the spherical-sky second-order
+extended Limber approximation (ExtL2Sph) yields percent accuracy down to $\ell
+> 3$.  The numerical calculation of the second-order extended Limber
+approximation is a factor of \mk{15 times} faster than the calculation of the
+full spherical solution \mk{for the first $18$ $\ell$-modes.} We note that the
+\mk{sub-$0.1\%$}-noise seen in the right panel of Fig.~\ref{fig:Cl_cases} is
+due to numerical noise arising from numerical integration errors in the
+calculation of the full spherical solution when $\ell > 20$.
+
+% Compuation times:
+% l>=20, 20 modes
+% full 37s
+% L2   2.14s
+% L1   0.8s
 
@@
 
-On a sphere, correlation functions cannot be related to the power spectrum by the
-Hankel transform in equation~(\ref{eqn:xiGG}), as the spherical power spectrum is
-formally not defined for non-integer $\ell$ \citep[see][for alternative
-spherical-sky formulae for the two-point correlation
+On a sphere, correlation functions cannot be related to the power spectrum by
+the Hankel transform in equation~(\ref{eqn:xiGG}), as the spherical power
+spectrum is formally not defined for non-integer $\ell$ \citep[see][for
+alternative spherical-sky formulae for the two-point correlation
 function]{2005PhRvD..72b3516C}. In particular, the spherical Bessel functions
-necessary to compute the full projection in equation~(\ref{eq:C_ell_full}) is defined only
-for integer order $\ell$. \mk{Is this really true?}
+necessary to compute the full projection in equation~(\ref{eq:C_ell_full}) is
+defined only for integer order $\ell$. \mk{I think this is actually not true,
+since J$_\nu$ can be computed for fractional $\nu$, and then one could use the
+identity (\ref{P_kappa_full_l1}). Or is it?}.
 
@@
 representation of the full spherical projection for $\ell > 3$.  
-In the Limber approximations the Bessel functions expanded \ch{to by ?? which one??}
+In the Limber approximations the Bessel functions \mk{are expanded into}
 polynomials, allowing for arbitrary wave modes $\ell$. The spherical pre-factor
@@
 
-\ch{MNRAS rules;  equation when you refer to your equation.  Equation when it is in another paper.}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 power spectrum, which they present as spherical-radial representation the 3D
-shear field. Our results in equation~(\ref{eq:C_ell_full}) corresponds to their Equations
-(7) and (8) assuming a flat Universe and the case of perfect photometric
-redshifts, with $p(z | z_{\rm p}) = \delta_{\rm D}(z - z_{\rm p})$, and for a bin
-function that selects the redshift bin $i$, $W^{\rm SR}(z, z_{\rm p}) = 1_{z
-\in i-\mbox{th bin}}$. We find that Equation~(7) in \cite{2016arXiv161104954K} is missing a factor $2/\pi$.
+shear field. Our results in equation~(\ref{eq:C_ell_full}) corresponds to their
+Equations (7) and (8) assuming a flat Universe and the case of perfect
+photometric redshifts, with $p(z | z_{\rm p}) = \delta_{\rm D}(z - z_{\rm p})$,
+and for a bin function that selects the redshift bin $i$, $W^{\rm SR}(z, z_{\rm
+p}) = 1_{z \in i-\mbox{th bin}}$. We find that Equation~(7) in
+\cite{2016arXiv161104954K} is missing a factor $2/\pi$.
 
 \cite{2016arXiv161104954K} derives the spherical and extended Limber
-approximation starting from the full spherical projection in their Appendix.~A.  We find that the
-filter function $q$ defined in their Equation~(31) has an additional factor of
-comoving distance $r$, and an additional factor of $\pi/2$.
-
-As shown in this paper, we are unable to reproduce the differences that \cite{2016arXiv161104954K} report,
-between the full spherical solution and the different approximations,
-neither for the power spectrum nor for the shear correlation function.
+approximation starting from the full spherical projection in their Appendix.~A.
+We find that the filter function $q$ defined in their Equation~(31) has an
+additional factor of comoving distance $r$, and an additional factor of
+$\pi/2$.
+
+As shown in this paper, we are unable to reproduce the differences that
+\cite{2016arXiv161104954K} report, between the full spherical solution and the
+different approximations, neither for the power spectrum nor for the shear
+correlation function.
 
@@
 \cite{2012PhRvD..86b3001B} present the non-tomographic full projection
-$C(\ell)$ in the approximation of the 3D potential power spectrum $P^\Phi$ separating
-into $k$- and $\chi$-dependent functions in their Equation~(44). Their expression holds for a single
-source redshift.
+$C(\ell)$ in the approximation of the 3D potential power spectrum $P^\Phi$
+separating into $k$- and $\chi$-dependent functions in their Equation~(44).
+Their expression holds for a single source redshift.
 
@@
 $D_+(a)/a$. Then, for a constant source comoving distance $\chi_{\rm S}$, the
-lensing efficiency in equation~(\ref{eq:lens_efficiency}) is $q(\chi) = (\chi_{\rm S} -
-\chi) \chi_{\rm S}^{-1}$, and the derivative of the separated kernel function in equation~(\ref{eq:f_LA08_s}) can be calculated analytically,
+lensing efficiency in equation~(\ref{eq:lens_efficiency}) is $q(\chi) =
+(\chi_{\rm S} - \chi) \chi_{\rm S}^{-1}$, and the derivative of the separated
+kernel function in equation~(\ref{eq:f_LA08_s}) can be calculated analytically,
 %
@@
 %
-This result confirms the power-law behaviour of the filter function, which we exploited earlier to fit
-this function.
+This result confirms the power-law behaviour of the filter function, which we
+exploited earlier to fit this function.
 
 Inserting equation~(\ref{eqn:B1}) into the second-order Limber power spectrum
-in equation~(\ref{eq:C_ell_limber2_dr_s}) and using the inverse Poisson equation to replace
-the matter with the potential power spectrum we obtain the same expression as
-\cite{vande2012} (their Equation.~7.19), except for an additional factor $a^2(\chi)$.
-This difference is accounted for by the factor $a^{-1}$ in the propagation of
-primordial potential perturbations to late times, see Equation~(6.22) in
-\cite{vande2012}, where the transition is calculated using $g(a)$ instead of $D(a)$.
-\mk{Check this further.}
+in equation~(\ref{eq:C_ell_limber2_dr_s}) and using the inverse Poisson
+equation to replace the matter with the potential power spectrum we obtain the
+same expression as \cite{vande2012} (their Equation.~7.19), except for an
+additional factor $a^2(\chi)$. This difference is accounted for by the factor
+$a^{-1}$ in the propagation of primordial potential perturbations to late
+times, see Equation~(6.22) in \cite{vande2012}, where the transition is
+calculated using $g(a)$ instead of $D(a)$. \mk{Check this further.}
 

### 2017-02-10 discussion.tex
Version v6

@@
-\subsection{Alternative two-point shear statistics; the mass aperture statistic and COSEBIs}
+\subsection{Alternative two-point shear statistics; the mass aperture statistic
+and COSEBIs}
 
@@
 where the Fourier-space filter functions $\hat U$ and $W_n$ are defined in
-\cite{1998MNRAS.296..873S} and \cite{COSEBIs}. 
-Figure~\ref{fig:filters} shows the integrands of these statistics, again normalised to their maximum
-value, where the integrands are of the form $\ell F(\ell) P^\gamma(\ell)$.  
-The lower middle panel in Figure~\ref{fig:filters} shows the
-COSEBIs integrands for two angular ranges, $[1',100']$ and $[0.8',350']$, where
-we only show the integrands for the lowest COSEBIs mode, $E_1$, as the higher
-modes generally probe larger $\ell$-modes.  The lowest panel shows the
-integrands of aperture mass dispersion statistics, for the same two maximum
-angular ranges.
+\cite{1998MNRAS.296..873S} and \cite{COSEBIs}, respectively.
+Figure~\ref{fig:filters} shows the integrands of these statistics, again
+normalised to their maximum value, where the integrands are of the form $\ell
+F(\ell) P^\gamma(\ell)$.  The lower middle panel in Figure~\ref{fig:filters}
+shows the COSEBIs integrands for two angular ranges, $[1',100']$ and
+$[0.8',350']$, where we only show the integrands for the lowest COSEBIs mode,
+$E_1$, as the higher modes generally probe larger $\ell$-modes.  The lowest
+panel shows the integrands of aperture mass dispersion statistics, for the same
+two maximum angular ranges.
 
 Note that the development of the aperture-mass dispersion statistic, $\langle
-M_ {\rm ap}^2 \rangle$ was initially motivated to enable the separation of the measured signal into an 
-E-mode (cosmological signal) and B-mode (systematics). This statistic is, however, a lossy conversion and is
-biased by small angular separations, where blending of galaxies makes shear
-measurement challenging \citep{KSE06}. The COSEBIs statistic tackles both
-these shortcomings.  \citet{CFHTLenS-2pt-notomo} present a detailed comparison of cosmological
-constraints obtained from this range of different two-point shear statistics finding consistent results.
+M_ {\rm ap}^2 \rangle$ was initially motivated to enable the separation of the
+measured signal into an E-mode (cosmological signal) and B-mode (systematics).
+This statistic is, however, a lossy conversion and is biased by small angular
+separations, where blending of galaxies makes shear measurement challenging
+\citep{KSE06}. The COSEBIs statistic tackles both these shortcomings.
+\citet{CFHTLenS-2pt-notomo} present a detailed comparison of cosmological
+constraints obtained from this range of different two-point shear statistics
+finding consistent results.
 

### 2017-02-10 limber2.tex
Version v6

@@
 \definecolor{purple}{RGB}{76, 0,153}
-\newcommand{\ch}[1]{\textcolor{purple}{\bf #1}}
+\newcommand{\ch}[1]{\textcolor{purple}{\textbf{#1}}}
 
@@
 The convergence power spectrum is then similar to the shear power spectrum
-(equation~\ref{eq:C_ell_gamma}) with a different spherical pre-factor, \citep{jk12}
+(equation~\ref{eq:C_ell_gamma}) with a different spherical pre-factor,
+\citep{2000PhRvD..62d3007H,jk12}
 %
@@
 %
-\mk{Add indices $i, j$ to $f$ and $q$ for the tomographic case.}{\ch Do we want to do this?}
+\mk{In the tomographic case, the index $i$ is added to $q$ and $f$.}
 %
@@
 approximation is a factor of \mk{15 times} faster than the calculation of the
-full spherical solution \mk{for the first $18$ $\ell$-modes.} We note that the
+full spherical solution \mk{(averaged over the first $18$ $\ell$-modes).} We note that the
 \mk{sub-$0.1\%$}-noise seen in the right panel of Fig.~\ref{fig:Cl_cases} is
@@
 since J$_\nu$ can be computed for fractional $\nu$, and then one could use the
-identity (\ref{P_kappa_full_l1}). Or is it?}.
+identity (\ref{eq:jJ}). Or is it?}.
 

### 2017-02-10 cfhtlens.tex
Fixed typo.

@@
   L1Fl       & $0.787^{+0.031}_{-0.033}$ & $0.739^{+0.029}_{-0.031}$ & Used for pre-2014 CFHTLenS \\
-  ExtL1Fl    & $x^{+y}_{-z}$ & $x^{+y}_{-z}$ & Depreciated \\
+  ExtL1Fl    & $x^{+y}_{-z}$ & $x^{+y}_{-z}$ & Deprecated \\
   ExtL1FlHyb & $0.788^{+0.031}_{-0.033}$ & $0.740^{+0.029}_{-0.031}$ & Used for post-2014 CFHTLenS, KiDS \\

### 2017-02-10 cfhtlens.tex
PMC run updated

@@
   L1Fl       & $0.787^{+0.031}_{-0.033}$ & $0.739^{+0.029}_{-0.031}$ & Used for pre-2014 CFHTLenS \\
-  ExtL1Fl    & $x^{+y}_{-z}$ & $x^{+y}_{-z}$ & Deprecated \\
+  ExtL1Fl    & $x^{+y}_{-z}$ & $x^{+y}_{-z}$ & Depreciated \\
   ExtL1FlHyb & $0.788^{+0.031}_{-0.033}$ & $0.740^{+0.029}_{-0.031}$ & Used for post-2014 CFHTLenS, KiDS \\
-  ExtL2FlHyb & $0.788^{+0.032}_{-0.032}$ & $0.740^{+0.030}_{-0.030}$ & Best flat-sky approximation \\
+  ExtL2FlHyb & $0.788^{+0.031}_{-0.033}$ & $0.740^{+0.029}_{-0.031}$ & Best flat-sky approximation \\
   ExtL2Sph   & $0.789^{+0.031}_{-0.032}$ & $0.740^{+0.029}_{-0.030}$ & Best approximation but mixing with flat-sky Hankel transform \\ \hline

### 2017-02-10 conclusions.tex

@@
 This requirement for computational speed is incompatible with a theoretical analysis that calculates a full spherical solution for the shear power spectrum, without adopting any approximation.
-We therefore present alternative solutions, revisiting the work of  \citet{2012PhRvD..86b3001B} who showed that adopting the second-order extended Limber approximation of \citet{2008PhRvD..78l3506L} provides a representation of full spherical solution for the shear power spectrum that is accurate at the sub-percent level for $\ell > 3$.
+We therefore present alternative solutions, revisiting the work of  \citet{2012PhRvD..86b3001B} who showed that adopting the second-order extended Limber approximation of \citet{2008PhRvD..78l3506L} provides a representation of the full spherical solution for the shear power spectrum that is accurate at the sub-percent level for $\ell > 3$.
 We have verified this result and provide to the community our fast numerical implementation of all the approximations studied in this analysis,
@@
 Finally we propose that future surveys seek to optimise the statistical analyses of their cosmic shear data.
-For example moving from the standard two-point shear correlation function statistic to the more stringent `COSEBI' statistic \citep{COSEBIs} renders the cosmic shear measurement insensitive to the low-$\ell$ scales where the Limber and flat-sky approximations make any impact on the precision of the theoretical modelling.
+For example moving from the standard two-point shear correlation function statistic to the more stringent `COSEBI' statistic \citep{COSEBIs} renders the cosmic shear measurement insensitive to the low-$\ell$ scales where the Limber and flat-sky approximations have an impact on the precision of the theoretical modelling.

### 2017-02-10 discussion.tex

@@
 In this paper we provide a solution in the form of the second-order extended
-Limber approximation, but another option to consider is the used of alternative two-point
+Limber approximation, but another option to consider is the use of alternative two-point
 shear statistics that are less sensitive to accuracy in shear power spectrum

### 2017-02-10 limber2.tex

@@
 Since this approximation involves only 1D integrals over the matter power spectrum, it is very fast to
-calculate numerically and can readily employed in Monte-Carlo sampling methods
+calculate numerically and can be readily employed in Monte-Carlo sampling methods
 to obtain precision constraints on cosmological parameters.
@@
 compute lensing power spectra for a spherical case, and in the flat-sky
-approximation. For completeness we provide a derivations of the weak lensing power spectra in Appendix~\ref{sec:derivations_C}.
+approximation. For completeness we provide a derivation of the weak lensing power spectra in Appendix~\ref{sec:derivations_C}.
 
@@
 $\chi$ up to a limiting distance $\chi_{\rm lim}$, and $f_K(\chi) = |K|^{-1/2}
-S_K(|K|^{1/2} \chi)$ is the the comoving angular distance, where the function
+S_K(|K|^{1/2} \chi)$ is the the comoving angular diameter distance, where the function
 $S_K$ equals $\sin$, ${\rm id}$, or $\sinh$ if the spatial curvature of the Universe
@@
 distribution in this approximation does not depend on the direction on the sky.
-Accounting for this position-dependence leads to correction of weak-lensing
+Accounting for this position-dependence leads to corrections of weak-lensing
 quantities due to clustering of source galaxies with other sources
@@
 
-Following \cite{2000PhRvD..62d3007H} we decompose the lensing potential (equation~\ref{eq:psi}) into a spherical harmonics expansion, in analogy of CMB
+Following \cite{2000PhRvD..62d3007H} we decompose the lensing
+potential (equation~\ref{eq:psi}) into spherical harmonics, in analogy
+to the CMB
 temperature, both of which are scalar functions on the sphere. This
@@
 neglecting the sky curvature. This is a valid approach for past and current
-survey areas with extents less than 10 degrees. The correlation
+survey areas with an extent less than 10 degrees. The correlation
 functions from the observed shear have, however, been calculated using spherical
@@
 For a flat sky, the spherical harmonic expansions are approximated by Fourier
-transforms. The flat-sky equivalent of equations.~(\ref{eq:psi_harm_exp}) and
+transforms. The flat-sky equivalent of equations~(\ref{eq:psi_harm_exp}) and
 (\ref{eq:psi_harm_exp_inv}) are
@@
 
-The flat-sky power spectrum, the flat-sky analogue of equation~(\ref{eq:C_ell_psi}) is defined by
+The flat-sky power spectrum, i.e. the flat-sky analogue of equation~(\ref{eq:C_ell_psi}), is defined by
 %
@@
 %
-\cite{2000PhRvD..62d3007H} have shown that for small angles the harmonics
+\cite{2000PhRvD..62d3007H} has shown that for small angles the harmonics
 expansion (equation~\ref{eq:psi_harm_exp}) can be approximated by the Fourier
@@
 To separate the $k$- and $\chi, \chi^\prime$-terms in equation~(\ref{eq:C_ell_full}), we
-first approximate the matter power cross-spectrum between two distances as
-geometric mean of the two involved distances \cite{2005PhRvD..72b3516C,2016arXiv161200770K},
+first approximate the matter power cross-spectrum between two
+distances by the
+geometric mean of the two involved distances \citep{2005PhRvD..72b3516C,2016arXiv161200770K},
 %
@@
 s}$ itself. At $\chi = 500 \mbox{Mpc}/h$ the filter function is less than
-$10^{-4}$ of its value of unity at Mpc$/h$.
+$10^{-4}$ of its value of unity at 1\,Mpc$/h$. \textbf{PLEASE CHECK!}
 
@@
 the range of different approximations listed in Table~\ref{tab:cases}.  The adopted redshift distribution corresponds to CFHTLenS
-\cite{CFHTLenS-2pt-notomo} and we assume their best-fit flat $\Lambda$CDM cosmology with $\Omega_{\rm m}=0.279$, $\Omega_{\rm b}=0.046$, $\sigma_8=0.79$, $H_0=0.701$, $n_{\rm s}=0.96$. 
+\citep{CFHTLenS-2pt-notomo} and we assume their best-fit flat $\Lambda$CDM cosmology with $\Omega_{\rm m}=0.279$, $\Omega_{\rm b}=0.046$, $\sigma_8=0.79$, $H_0=0.701$, $n_{\rm s}=0.96$. 
 For $\ell > 100$ we find that all shear power spectra predictions agree with the full spherical solution to better than one percent, with the majority of the approximations tested accurate to better than 0.1 per cent.
@@
 polynomials, allowing for arbitrary wave modes $\ell$. The spherical pre-factor
-$\ellbar(\ell, 2)$ (equation~ref{eq:ellbar}) can be generalised to non-integer
+$\ellbar(\ell, 2)$ (equation~\ref{eq:ellbar}) can be generalised to non-integer
 arguments and is positive for $\ell \le 2$. We can thus use the spherical power
@@
 spherical projection, instead choosing the spherical second-order extended
-Limber approximation (Ext2Sph) as our reference in this case.
+Limber approximation (ExtL2Sph) \textbf{PLEASE CHECK!} as our reference in this case.
 

### 2017-02-10 conclusions.tex
Figures updates labels

@@
-In this paper we evaluate precision theoretical calculations for cosmic shear observables, bringing together different sources from the literature to provide a pedagogical review of the impact of adopting flat-sky and Limber approximations.
-We demonstrate that for current surveys, such as CFHTLenS, these approximations have a negligible impact on cosmological parameter constraints.
+In this paper we evaluate precision theoretical calculations for cosmic shear
+observables, bringing together different sources from the literature to provide
+a pedagogical review of the impact of adopting flat-sky and Limber
+approximations.  We demonstrate that for current surveys, such as CFHTLenS,
+these approximations have a negligible impact on cosmological parameter
+constraints.
 
-For future surveys, the decrease in statistical errors places higher requirements on the accuracy of the theoretical modelling.
-There is also, however, the need to be able to rapidly sample the multi-dimensional cosmological parameter likelihoods.
-This requirement for computational speed is incompatible with a theoretical analysis that calculates a full spherical solution for the shear power spectrum, without adopting any approximation.
-We therefore present alternative solutions, revisiting the work of  \citet{2012PhRvD..86b3001B} who showed that adopting the second-order extended Limber approximation of \citet{2008PhRvD..78l3506L} provides a representation of the full spherical solution for the shear power spectrum that is accurate at the sub-percent level for $\ell > 3$.
-We have verified this result and provide to the community our fast numerical implementation of all the approximations studied in this analysis,
-and the slow calculation of the full projection within the publicly available package \textsc{nicaea} at \texttt{http://www.cosmostat.org/software/nicaea}.
+For future surveys, the decrease in statistical errors places higher
+requirements on the accuracy of the theoretical modelling.    There is also,
+however, the need to be able to rapidly sample the multi-dimensional
+cosmological parameter likelihoods.  This requirement for computational speed
+is incompatible with a theoretical analysis that calculates a full spherical
+solution for the shear power spectrum, without adopting any approximation.  We
+therefore present alternative solutions, revisiting the work of
+\citet{2012PhRvD..86b3001B} who showed that adopting the second-order extended
+Limber approximation of \citet{2008PhRvD..78l3506L} provides a representation
+of the full spherical solution for the shear power spectrum that is accurate at
+the sub-percent level for $\ell > 3$.    We have verified this result and
+provide to the community our fast numerical implementation of all the
+approximations studied in this analysis, and the slow calculation of the full
+projection within the publicly available package \textsc{nicaea} at
+\texttt{http://www.cosmostat.org/software/nicaea}.
 
-Finally we propose that future surveys seek to optimise the statistical analyses of their cosmic shear data.
-For example moving from the standard two-point shear correlation function statistic to the more stringent `COSEBI' statistic \citep{COSEBIs} renders the cosmic shear measurement insensitive to the low-$\ell$ scales where the Limber and flat-sky approximations have an impact on the precision of the theoretical modelling.
+Finally we propose that future surveys seek to optimise the statistical
+analyses of their cosmic shear data.  For example moving from the standard
+two-point shear correlation function statistic to the more stringent `COSEBI'
+statistic \citep{COSEBIs} renders the cosmic shear measurement insensitive to
+the low-$\ell$ scales where the Limber and flat-sky approximations have an
+impact on the precision of the theoretical modelling.
+
+\mk{TODO: comment on non-flat models.}

### 2017-02-10 limber2.tex
Figures updates labels

@@
 depend on redshift other than the growth factor, for example when computing the
-non-linear scale $k_{\rm NL}(z)$ for \texttt{halofit}.
+non-linear scale $k_{\rm NL}(z)$ for \texttt{halofit} \citep{2003MNRAS.341.1311S}.
 
@@
 very small as these scales are down-weighed by the kernel function $f_{\rm
-s}$ itself. At $\chi = 500 \mbox{Mpc}/h$ the filter function is less than
-$10^{-4}$ of its value of unity at 1\,Mpc$/h$. \textbf{PLEASE CHECK!}
+s}$ itself. At $\chi = 500 \, \mbox{Mpc}/h$ the filter function is less than
+$10^{-4}$ of its value of unity at $1$\,Mpc$/h$.
 
@@
       \includegraphics{figures/P_kappa_limber_comp}
+      \hspace*{2em}
       \includegraphics{figures/P_kappa_limber_delta}
@@
 spherical projection, instead choosing the spherical second-order extended
-Limber approximation (ExtL2Sph) \textbf{PLEASE CHECK!} as our reference in this case.
+Limber approximation (ExtL2Sph) as our reference in this case.
 
@@
 
-The authors thank Tommaso Giannantonio, Sarah Bridle, Ami Choi, Donnacha Kirk, Lance Miller, Benjamin Joachimi, Chris Blake and Adam Amara for very helpful discussions.
-This work was financially supported by the DFG (Emmy Noether grants Hi 1495/2-1 and SI 1769/1-1; TR33 `The Dark Universe'), the Alexander von Humboldt Foundation, the ERC (grants 279396, 647112), the Seventh Framework Programme of the European Commission (Marie Sklodwoska Curie Fellowship grant 656869), NSERC and CIfAR.
+The authors thank Tommaso Giannantonio, Sarah Bridle, Ami Choi, Donnacha Kirk,
+Lance Miller, Benjamin Joachimi, Chris Blake and Adam Amara for very helpful
+discussions. This work was financially supported by the DFG (Emmy Noether
+grant Hi 1495/2-1; SI 1769/1-1; TR33 `The Dark Universe'), the Alexander
+von Humboldt Foundation, the ERC (grants 279396, 647112), the Seventh Framework
+Programme of the European Commission (Marie Sklodwoska Curie Fellowship grant
+656869), NSERC and CIfAR.
 

### 2017-02-10 cfhtlens.tex

--- 2017-02-10 cfhtlens.tex
@@
   ExtL1FlHyb & $0.788^{+0.031}_{-0.033}$ & $0.740^{+0.029}_{-0.031}$ & Used for post-2014 CFHTLenS, KiDS \\
-  ExtL2FlHyb & $0.788^{+0.032}_{-0.032}$ & $0.740^{+0.030}_{-0.030}$ & Best flat-sky approximation \\
+  ExtL2FlHyb & $0.788^{+0.031}_{-0.033}$ & $0.740^{+0.029}_{-0.031}$ & Best flat-sky approximation \\
   ExtL2Sph   & $0.789^{+0.031}_{-0.032}$ & $0.740^{+0.029}_{-0.030}$ & Best approximation but mixing with flat-sky Hankel transform \\ \hline

### 2017-02-10 cfhtlens.tex
Included Hendrik's comments

@@
 biases would {\it reduce} the recovered amplitude of $\sigma_8$ by $\sim
-4$\%.}
+4$\%. Additional new techniques to calibrate the redshift distribution of tomographic
+bins was introduced recently in \cite{KiDS-450}.}
 %
@@
 larger-box numerical simulations that were less subject to the lack of power on
-large scales.}
+large scales. A complementary accurate estimate of the covariance matrix using
+analytical methods will be published soon (Joachimi et al.~in prep.}
 %
@@
 
-  \begin{tabular}{lccc} \hline
-  ID         & $\sigma_8 (\Omega_{\rm m}/0.27)^{0.6}$ & $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$ & Comment \\ \hline
-  L1Fl       & $0.787^{+0.031}_{-0.033}$ & $0.739^{+0.029}_{-0.031}$ & Used for pre-2014 CFHTLenS \\
-  ExtL1Fl    & $x^{+y}_{-z}$ & $x^{+y}_{-z}$ & Deprecated \\
-  ExtL1FlHyb & $0.788^{+0.031}_{-0.033}$ & $0.740^{+0.029}_{-0.031}$ & Used for post-2014 CFHTLenS, KiDS \\
-  ExtL2FlHyb & $0.788^{+0.031}_{-0.033}$ & $0.740^{+0.029}_{-0.031}$ & Best flat-sky approximation \\
-  ExtL2Sph   & $0.789^{+0.031}_{-0.032}$ & $0.740^{+0.029}_{-0.030}$ & Best approximation but mixing with flat-sky Hankel transform \\ \hline
+  \begin{tabular}{lcc} \hline
+  ID         & $\sigma_8 (\Omega_{\rm m}/0.27)^{0.6}$ & $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$ \\ \hline
+  L1Fl       & $0.787^{+0.031}_{-0.033}$ & $0.739^{+0.029}_{-0.031}$ \\
+  ExtL1Fl    & $x^{+y}_{-z}$ & $x^{+y}_{-z}$ \\
+  ExtL1FlHyb & $0.788^{+0.031}_{-0.033}$ & $0.740^{+0.029}_{-0.031}$ \\
+  ExtL2FlHyb & $0.788^{+0.031}_{-0.033}$ & $0.740^{+0.029}_{-0.031}$ \\
+  ExtL2Sph   & $0.789^{+0.031}_{-0.032}$ & $0.740^{+0.029}_{-0.030}$ \\ \hline
   \end{tabular}

### 2017-02-10 limber2.tex
xipm figures fixed
Included Hendrik's comments

@@
     The third column shows the power-spectrum pre-factor $p(\ell)$. }  
-    \begin{tabular}{|l|l|c|c|c}
+    \begin{tabular}{|l|l|c|c|c|p{0.21\textwidth}}
   \hline
-  Case & ID & equation & $p(\ell)$ & $\nu(\ell)$ \\ \hline
+  Case & ID & equation & $p(\ell)$ & $\nu(\ell)$ & Comment \\ \hline
   % 
   $1^{\rm st}$-order standard Limber, flat sky & L1Fl & (\ref{eq:P_ell_limber1}) + (i)
-    & $1$ & $\ell$ \\ \hline
+    & $1$ & $\ell$ & Used for pre-2014 CFHTLenS \\ \hline
   %
   $1^{\rm st}$-order extended Limber, flat sky & ExtL1Fl & (\ref{eq:P_ell_limber1}) + (ii)
-    & $\ell^4/(\ell+1/2)^4$ & $\ell + 1/2$ \\ \hline
+    & $\frac{\ell^4}{(\ell+1/2)^4}$ & $\ell + \frac 1 2$ & Converges only with ${\cal O}(\ell^{-1})$ \\ \hline
   %
   $1^{\rm st}$-order extended Limber, hybrid, flat sky & ExtL1FlHyb & (\ref{eq:P_ell_limber1}) + (iii)
-    & $1$ & $\ell + 1/2$ \\ \hline
+    & $1$ & $\ell + \frac 1 2$ & Used for post-2014 CFHTLenS, KiDS \\ \hline
   %
   $1^{\rm st}$-order extended Limber, spherical & ExtL1Sph & (\ref{eq:C_ell_limber1})
-    & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ \\ \hline
+    & $\frac{\ellbar^2(\ell, 2)}{(\ell+1/2)^4}$ & $\ell+ \frac 1 2$ & \\ \hline
   %
   $2^{\rm st}$-order extended Limber, flat sky & ExtL2Fl &  (\ref{eq:P_ell_limber1}) + (\ref{eq:P_ell_limber2}) + (iii)
-    & $\ell^4/(\ell+1/2)^4$ 
-    & $\ell+1/2$ \\ \hline
+    & $\frac{\ell^4}{(\ell+1/2)^4}$ 
+    & $\ell+\frac 1 2$ & Converges only with ${\cal O}(\ell^{-1})$ \\ \hline
   %
@@
     & $1$ 
-    & $\ell+1/2$ \\ \hline
+    & $\ell+ \frac 1 2$ & Best flat-sky approximation \\ \hline
   %
   $2^{\rm st}$-order extended Limber, spherical & ExtL2Sph & (\ref{eq:C_ell_limber1})+(\ref{eq:C_ell_limber2_dr_s})
-    & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ \\ \hline
+    & $\frac{\ellbar^2(\ell, 2)}{(\ell+1/2)^4}$ & $\ell+\frac 1 2$ & Best approximation but mixing with flat-sky Hankel transform \\ \hline
   %
   Full spherical & FullSph & (\ref{eq:C_ell_full}) &
-      $\ellbar^2(\ell, 2)$ & - \\ \hline
+      $\ellbar^2(\ell, 2)$ & - & Correct projection \\ \hline
   %
@@
       \includegraphics{figures/xi_p_comp}
+      \hspace*{2em}
       \includegraphics{figures/xi_m_comp}
@@
       \includegraphics{figures/xi_p_delta}
+      \hspace*{2em}
       \includegraphics{figures/xi_m_delta}

### 2017-02-11 limber2.tex
Included Ludo's comments

@@
 \newcommand{\mk}[1]{{\bf\textcolor{blue}{#1}}}
+\newcommand{\Label}[1]{\quad \mk{(\mbox{#1})}}
+\newcommand{\LabelTxt}[1]{\mk{(\mbox{#1})}}
 
@@
 and the Canada-France-Hawaii Telescope Lensing Survey
-\citep[CFHTLenS;][]{joudaki/etal:2016}.  If the source of this tension is not
-a result of so-far unconsidered sources of systematic errors in one or all
+\citep[CFHTLenS;][]{joudaki/etal:2016}.  If the source of this tension is not a
+result of so-far unconsidered sources of systematic errors in one or all
 experiments, extensions to the standard flat $\Lambda$CDM cosmological models
@@
 
-In the era of the upcoming large-scale surveys that will provide measurements of
-cosmic shear with unprecedented precision, one needs to revisit the theoretical
-predictions of the observables to ensure that the accuracy of the
-models meet the accuracy of the observations. In this paper, we examine the widely used Limber
-approximation for the projected weak-lensing power spectrum. We consider
-spherical coordinates and the flat-sky approximation, and compute the full
-projection. We show
-that the second-order Limber approximation is an accurate representation of the full projection, with better than percent level precision for scales $\ell > 3$. 
-Since this approximation involves only 1D integrals over the matter power spectrum, it is very fast to
-calculate numerically and can be readily employed in Monte-Carlo sampling methods
-to obtain precision constraints on cosmological parameters.
+In the era of the upcoming large-scale surveys that will provide measurements
+of cosmic shear with unprecedented precision, one needs to revisit the
+theoretical predictions of the observables to ensure that the accuracy of the
+models meet the accuracy of the observations. In this paper, we examine the
+widely used Limber approximation for the projected weak-lensing power spectrum.
+We consider spherical coordinates and the flat-sky approximation, and compute
+the full projection. We show that the second-order Limber approximation is an
+accurate representation of the full projection, with better than percent level
+precision for scales $\ell > 3$. Since this approximation involves only 1D
+integrals over the matter power spectrum, it is very fast to calculate
+numerically and can be readily employed in Monte-Carlo sampling methods to
+obtain precision constraints on cosmological parameters.
 
@@
 power spectra for the flat-sky and spherical cases, following the seminal work
-from \citet{2000PhRvD..62d3007H}, see also \citet{2005PhRvD..72b3516C}. In section~\ref{sec:L2} we
-derive weak lensing observables using a second-order limber approximation first
-introduced by \citet{2008PhRvD..78l3506L}. We compare the shear power spectrum
-and commonly-used two-point shear correlation function for the full solution to
-a range of different approximations in section~\ref{sec:results}, providing
-cosmological constraints for each case using CFHTLenS data from
-\citet{CFHTLenS-2pt-notomo}. This paper draws
-from several sources of literature which have previously discussed the full
+from \citet{2000PhRvD..62d3007H}, see also \citet{2005PhRvD..72b3516C}. In
+section~\ref{sec:L2} we derive weak lensing observables using a second-order
+limber approximation first introduced by \citet{2008PhRvD..78l3506L}. We
+compare the shear power spectrum and commonly-used two-point shear correlation
+function for the full solution to a range of different approximations in
+section~\ref{sec:results}, providing cosmological constraints for each case
+using CFHTLenS data from \citet{CFHTLenS-2pt-notomo}. This paper draws from
+several sources of literature which have previously discussed the full
 projection, or reviewed the accuracy of the Limber approximation for weak
@@
                 \int_0^\infty \frac{{\rm d} k}{k^2} \, P_{\rm m}(k, \chi, \chi^\prime) \,
-                {\rm j}_\ell(k \chi) \, {\rm j}_\ell(k \chi^\prime) .
+                {\rm j}_\ell(k \chi) \, {\rm j}_\ell(k \chi^\prime), \Label{FullSph}
   \label{eq:C_ell_full}
@@
 %
-The spherical pre-factor for the full projection power spectrum is $p(\ell) :=
-\ellbar^2(\ell, 2)$, which will be modified under flat-sky and Limber
-approximations below.
+where we use the label `FullSph', see Table \ref{tab:cases} for a list of cases discussed in this work.
+The spherical \mk{spin} pre-factor for the full projection \mk{shear} power
+spectrum is $p(\ell) := \ellbar^2(\ell, 2)$, which will be modified under
+flat-sky and Limber approximations below.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The majority of cosmic shear analyses have used lensing quantities approximated on a flat sky,
-neglecting the sky curvature. This is a valid approach for past and current
-survey areas with an extent less than 10 degrees. The correlation
-functions from the observed shear have, however, been calculated using spherical
-coordinates, and the effect on large scales has been shown to be significant \citep{FSHK08}.
-Here we examine the effect of sky curvature on the theoretical models.
+
+The majority of cosmic shear analyses have used \mk{the predicted} lensing
+power spectrum approximated on a flat sky, neglecting the sky curvature. This
+is a valid approach for past and current survey areas with an extent less than
+10 degrees. \mk{To account for the sky curvature of the observed data}, the
+shear correlation functions \mk{from observed galaxy ellipticities is now
+routinely} computed using spherical coordinates, \mk{since projecting to a
+Cartesian plane has been shown to cause significant biases of the two-point
+funtion on large scales \citep{FSHK08}}. Here we examine the effect of sky
+curvature on the theoretical \mk{models of the power spectrum, and the effect
+on cosmological parameter inference (see Sect.~\ref{sec:cfhtlens}).}
 
@@
                 \frac{q_i(\chi)}{a(\chi)} {\rm J}_{\ell+1/2}(k \chi)
-                \nonumber \\
-                 & \times
+                %\nonumber \\
+                 %& \times
                 \int_{0}^\infty \frac{{\rm d} \chi^\prime}{{\chi^\prime}^{3/2}}
@@
   C^\gamma_{{\rm L1}, ij}(\ell) = & \, \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2 \int {\rm d} \chi \frac{ q_i(\chi) q_j(\chi) }{a^2(\chi)}
-  P_{\rm m}\left(\frac{\nu}{\chi}; \chi\right).
+  P_{\rm m}\left(\frac{\nu}{\chi}; \chi\right) . \Label{ExtL1Sph}
   \label{eq:C_ell_limber1}
@@
       \right)
-    \right](\chi)
+    \right](\chi) \, . \Label{ExtL2Sph}
   \label{eq:C_ell_limber2_dr_s}
@@
 The extended flat-sky Limber approximation is readily derived from the
-spherical case, by replacing the pre-factor $\ellbar^2(\ell, 2)$ with $\ell^4$,
-%
-\begin{align}
-  P^\gamma_{{\rm L1}, ij}(\ell) = & \, \frac{\ell^4}{\nu^4} \, \pref^2 \int {\rm d} \chi \frac{ q_i(\chi) q_j(\chi) }{a^2(\chi)}
+spherical case (\ref{eq:C_ell_limber1}, \ref{eq:C_ell_limber2_dr_s}), by
+replacing the pre-factor $\ellbar^2(\ell, 2)$ with $\ell^4$,
+%
+\begin{align}
+  P^\gamma_{{\rm L1}, ij}(\ell) = & \, p(\ell) \, \pref^2 \int {\rm d} \chi \frac{ q_i(\chi) q_j(\chi) }{a^2(\chi)}
   P_{\rm m}\left(k = \frac{\nu}{\chi}; \chi\right);
@@
   \\
-    P^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2} \, \frac{\ell^4}{\nu^4} \, \pref^2
+    P^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2} \, p(\ell) \, \pref^2
     \int {\rm d} \chi \, \chi^{2} a^{-2} P_{\rm m}\left(k = \frac\nu\chi; \chi\right)
@@
 \begin{enumerate}
-  \item $p(\ell) = 1$, this corresponds to $\nu(\ell) = \ell$, which is the \emph{standard} Limber approximation.
+  \item $p(\ell) = 1$, this corresponds to $\nu(\ell) = \ell$, which is the
+    \emph{standard} Limber approximation \LabelTxt{L1Fl}
     Until recently, i.e.~for all pre-2014 CFHTLenS results, this was the approximation of choice.
-  \item $p(\ell) = \ell^4/(\ell + 1/2)^4$. This corresponds to the \emph{extended} Limber
-    approximation with $\nu(\ell) = \ell + 1/2$; however the following case is typically employed:
+    Note that we do not discuss the non-extended second-order Limber approximation here.
+  %
+  \item \Label{ExtL[1$|$2]Fl}: $p(\ell) = \ell^4/(\ell + 1/2)^4$. This corresponds to the \emph{extended} Limber
+    approximation \LabelTxt{ExtL1Fl,ExtL2Fl} with $\nu(\ell) = \ell + 1/2$; however the following case is typically employed:
+  %
   \item $p(\ell) = 1$, with $\nu = \ell + 1/2$. This is
     a \emph{hybrid} between
-    standard and extended Limber approximation, and was used in \cite{KiDS-450,joudaki/etal:2016}. As is shown
+    standard and extended Limber approximation \Label{ExtL1FlHyb,ExtL2FlHyb}, and this case to first order
+    was used in \cite{KiDS-450,joudaki/etal:2016}. As is shown
     later, this is a better approximation to the full projection than case (ii).
@@
 %
-\ch{Would this section be clearer if we had $p(\ell)$ in the equations instead of 
-$\ell^4/\nu^4$?}
 
@@
 \begin{centering}
-  \caption{\label{tab:cases}The shear power spectrum approximations studied in this paper. 'ID' is the abbrevation used in the figures.
+  \caption{\label{tab:cases}The shear power spectrum approximations studied in this paper. 'ID' is the \mk{label} used in the \mk{text and} figures.
     The third column shows the power-spectrum pre-factor $p(\ell)$. }  

### 2017-02-12 authors.tex
minor update to affiliation and acknowledgements

--- 2016-12-14 authors.tex
@@
-\author[Heymans, Asgari, Joudaki et al.]
-{C. Heymans$^1$\thanks{Email: heymans@roe.ac.uk}, 
-M. Asgari$^1$, 
-S. Joudaki$^2$, 
-J. Harnois-D\'eraps$^1$,
-H. Hildebrandt$^3$,
+\author[M.~Kilbinger et~al.]
+{Martin Kilbinger$^{1,2}$\thanks{E-mail: martin.kilbinger@cea.fr},
+Catherine Heymans$^3$,
+Marika Asgari$^3$, 
+Shahab Joudaki$^{4,5}$, 
 \newauthor
-M. Kilbinger$^4$,
-F. K\"ohlinger$^5$,
-K. Kuijken$^5$,
-P. Schneider$^3$,
-P. Simon$^3$,
+Peter Schneider$^6$,
+Patrick Simon$^6$,
+Joachim Harnois-D\'eraps$^3$,
+Hendrik Hildebrandt$^6$,
 \newauthor
-L. Van Waerbeke$^6$,
-M. Viola$^5$
+Fabian K\"ohlinger$^7$,
+Konrad Kuijken$^7$,
+Ludovic Van Waerbeke$^8$ and
+Massimo Viola$^7$
 \\
-$^1$Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK\\
-$^2$Centre for Astrophysics \& Supercomputing, Swinburne University of Technology, PO Box 218, Hawthorn, VIC 3122, Australia\\
-$^3$Argelander-Institut f\"ur Astronomie, Auf dem H\"ugel 71, 53121 Bonn, Germany\\
-$^4$Laboratoire AIM, CEA Saclay - CNRS - Paris 6, Irfu/SAp, F-91191 Gif-sur-Yvette, France\\
-$^5$Leiden Observatory, Leiden University, Niels Bohrweg 2, 2333 CA Leiden, the Netherlands\\
-$^6$Department of Physics and Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC V6T 1Z1, Canada\\
+$^1$CEA/Irfu/SAp Saclay, Laboratoire AIM, 91191 Gif-sur-Yvette, France\\
+$^2$Institut d'Astrophysique de Paris, UMR7095 CNRS, Universit\'e Pierre \& Marie Curie, 98 bis boulevard Arago, 75014 Paris, France \\
+$^3$Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK\\
+$^4$Centre for Astrophysics \& Supercomputing, Swinburne University of Technology, PO Box 218, Hawthorn, VIC 3122, Australia\\
+$^5$ARC Centre of Excellence for All-sky Astrophysics (CAASTRO)\\
+$^6$Argelander-Institut f\"ur Astronomie, Auf dem H\"ugel 71, 53121 Bonn, Germany\\
+$^7$Leiden Observatory, Leiden University, Niels Bohrweg 2, 2333 CA Leiden, the Netherlands\\
+$^8$Department of Physics and Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC V6T 1Z1, Canada\\
 }

### 2017-02-12 limber2.tex
minor update to affiliation and acknowledgements
Peter's comments part I included

@@
 \usepackage{bm,color}% bold math
+\usepackage[normalem]{ulem}
 %\usepackage{ulem}
@@
 integrals over the matter power spectrum, it is very fast to calculate
-numerically and can be readily employed in Monte-Carlo sampling methods to
+numerically and can readily be employed in Monte-Carlo sampling methods to
 obtain precision constraints on cosmological parameters.
@@
 section~\ref{sec:L2} we derive weak lensing observables using a second-order
-limber approximation first introduced by \citet{2008PhRvD..78l3506L}. We
+Limber approximation first introduced by \citet{2008PhRvD..78l3506L}. We
 compare the shear power spectrum and commonly-used two-point shear correlation
@@
 compute lensing power spectra for a spherical case, and in the flat-sky
-approximation. For completeness we provide a derivation of the weak lensing power spectra in Appendix~\ref{sec:derivations_C}.
+approximation. For completeness we provide a derivation of the weak lensing
+power spectra in Appendix~\ref{sec:derivations_C}.
 
@@
 the Born approximation is defined as the projected 3D metric potential $\Phi$
-along the line of sight \citep{1998ApJ...498...26K,BS01},
+along the line of sight \mk{of a flat Universe} \citep{1998ApJ...498...26K,BS01},
 %
@@
 \begin{equation}
-  \psi(\theta, \varphi) = \frac 2 {{\rm c}^2} \int_0^{\chi_{\rm lim}} \frac{{\rm d}\chi}{\chi}
-    \Phi[\chi, f_K(\chi) \theta, f_K(\chi) \varphi; \chi] \, q(\chi),
+  \psi(\theta, \varphi) = \frac 2 {{\rm c}^2} \int\limits_0^\infty \frac{{\rm d}\chi}{\chi}
+    %\Phi[\chi, f_K(\chi) \theta, f_K(\chi) \varphi; \chi] \, q(\chi),
+    \Phi[\chi, \chi \theta, \chi \varphi; \chi] \, q(\chi),
   \label{eq:psi}
@@
 \begin{equation}
-  q(\chi) = \int\limits_\chi^{\chi_{\rm lim}} {\rm d} \chi^\prime \, n(\chi^\prime)
-    \frac{f_K(\chi^\prime - \chi)}{f_K(\chi^\prime)},
+  q(\chi) = \int\limits_\chi^{\chi_{\rm h}} {\rm d} \chi^\prime \, n(\chi^\prime)
+    %\frac{f_K(\chi^\prime - \chi)}{f_K(\chi^\prime)},
+    \frac{\chi^\prime - \chi}{\chi^\prime},
   %
@@
 corresponding to a population of lensed galaxies with a normalised source
-redshift distribution $n(z) {\rm d}z = n(\chi) {\rm d} \chi$. Here, ${\rm c}$
-is the speed of light, the projection is carried out over comoving distances
-$\chi$ up to a limiting distance $\chi_{\rm lim}$, and $f_K(\chi) = |K|^{-1/2}
-S_K(|K|^{1/2} \chi)$ is the the comoving angular diameter distance, where the function
-$S_K$ equals $\sin$, ${\rm id}$, or $\sinh$ if the spatial curvature of the Universe
-$K$ is positive, zero, or negative, respectively.
-
-The form of the lensing efficiency $q$ in equation (\ref{eq:lens_efficiency}) assumes a
-homogeneous galaxy distribution without clustering, so that the redshift
-distribution in this approximation does not depend on the direction on the sky.
-Accounting for this position-dependence leads to corrections of weak-lensing
-quantities due to clustering of source galaxies with other sources
+redshift distribution $n_z(z) {\rm d}z = n(\chi) {\rm d} \chi$, \mk{with limit the
+comoving distance to the horizon $\chi_{\rm h}$.} Here, ${\rm c}$ is the speed
+of light, and the projection is carried out over comoving distances $\chi$
+%, and $f_K(\chi) = |K|^{-1/2} S_K(|K|^{1/2} \chi)$ is the comoving angular
+% diameter distance, where the function $S_K$ equals $\sin$, ${\rm id}$, or
+% $\sinh$ if the spatial curvature of the Universe $K$ is positive, zero, or
+% negative, respectively.
+\mk{The last argument of the potential $\Phi$ is not to
+be understood as coordinate, but rather as a substitute of cosmic time,
+$t(\chi)$, to express the time at which the potential is evaluated. This is
+true in the following for all fields and functions thereof that dynamically
+change with cosmic epoch.}
+
+The form of the lensing efficiency $q$ in equation (\ref{eq:lens_efficiency})
+assumes a homogeneous galaxy distribution without clustering, so that the
+redshift distribution in this approximation does not depend on the direction on
+the sky. Accounting for this position-dependence leads to corrections of
+weak-lensing quantities due to clustering of source galaxies with other sources
 \citep{2002A&A...389..729S}, and with galaxies associated with lens structures
@@
 %
-where $\Omega_{\rm m}$ is the matter density parameter, $H_0$ the Hubble constant, $\vec k$ a 3D Fourier wave
-vector, and $a$ the scale factor with $a=1$ today.
-The Fourier transform of the potential and its inverse are defined as
-%
-\begin{align}
-  \hat \Phi(\vec k; \chi) = &  \int {\rm d}^3 r \, \Phi(\vec r; \chi) {\rm e}^{{\rm i} \vec k \vec r} ;
+where $\Omega_{\rm m}$ is the matter density parameter, $H_0$ the Hubble
+constant, $\vec k$ a 3D Fourier wave vector \mk{with modulus $k$ being the comoving
+wave number}, and $a$ the scale factor with $a=1$ today. The Fourier transform
+of the potential and its inverse are defined as
+%
+\begin{align}
+  \hat \Phi(\vec k; \chi) = &  \int {\rm d}^3 r \, \Phi(\vec r; \chi) {\rm e}^{{\rm i} \vec k \cdot \vec r} ;
   \label{eq:hatPhi}
@@
   \Phi(\vec r; \chi) = &  \int \frac{{\rm d}^3 k}{(2\pi)^3}
-      \hat \Phi(\vec k; \chi) {\rm e}^{-{\rm i} \vec r \vec k},
+      \hat \Phi(\vec k; \chi) {\rm e}^{-{\rm i} \vec r \cdot \vec k},
   \label{eq:hatPhi_inv}
@@
 %
-with the spin pre-factor \citep{2012PhRvD..86b3001B}
+\mk{for $0 \le s \le \ell$,} with the spin pre-factor \citep{2012PhRvD..86b3001B}
 %
@@
 The two coefficients $_{+2} \gamma_{\ell m}$ and $_{-2} \gamma_{\ell m}$ are
-identical since the potential $\phi$ is a real function.
+identical since the potential $\psi$ is a real function.
 
@@
 %
-For a zero-curvature Universe, this is given by
+%For a zero-curvature Universe, this is given by
+This is given by
 %
@@
 The spherical \mk{spin} pre-factor for the full projection \mk{shear} power
-spectrum is $p(\ell) := \ellbar^2(\ell, 2)$, which will be modified under
+spectrum is $\ellbar^2(\ell, 2)$, which will be modified under
 flat-sky and Limber approximations below.
@@
 \begin{align}
-  \psi(\vec \vartheta) = & \int \frac{{\rm d}^2 \ell}{(2\pi)^2} \, {\rm e}^{-{\rm i} \vec \ell \vec \vartheta} \hat \psi(\vec \ell);
+  \psi(\vec \vartheta) = & \int \frac{{\rm d}^2 \ell}{(2\pi)^2} \, {\rm e}^{-{\rm i} \vec \ell \cdot \vec \vartheta} \hat \psi(\vec \ell);
   \label{eq:psi_fourier}
@@
   %
-  \hat \psi(\vec \ell) = & \int {\rm d}^2 \vartheta \, {\rm e}^{{\rm i} \vec \ell \vec \vartheta} \psi(\vec \vartheta);
+  \hat \psi(\vec \ell) = & \int {\rm d}^2 \vartheta \, {\rm e}^{{\rm i} \vec \ell \cdot \vec \vartheta} \psi(\vec \vartheta),
   \label{eq:psi_fourier_inv}
@@
   \ell^2 \, _{\pm2}\!{\rm Y}_{\ell m}(\theta, \varphi) \approx  {\rm e}^{{\mp}2 {\rm i} \phi_\ell}
-    (\partial_1 \pm \partial_2)^2 \, {\rm Y}_{\ell m}(\theta, \varphi).
+    (\partial_1 \pm {\rm i} \partial_2)^2 \, {\rm Y}_{\ell m}(\theta, \varphi).
   \label{eq:sYlm_def_flat}
@@
 %
-with flat-sky pre-factor $p(\ell) = \ell^4$. 
-See App.~\ref{sec:schmidt08} and \ref{sec:giannantonio12} for discussions of alternative expressions for the flat-sky power spectrum.
+with flat-sky pre-factor $\ell^4$. See App.~\ref{sec:schmidt08} and
+\ref{sec:giannantonio12} for discussions of alternative expressions for the
+flat-sky power spectrum.
 
@@
 \begin{equation}
-  \int_0^\infty {\rm d} \chi f(\chi) {\rm J}_{\ell + 1/2}(k \chi)
-  = \int_0^\infty {\rm d} x k^{-1} f(x/k) {\rm J}_{\ell + 1/2}(x)
+  \int_0^\infty {\rm d} \chi f(\chi) {\rm J}_\nu(k \chi)
+  = \int_0^\infty {\rm d} x k^{-1} f(x/k) {\rm J}_\nu(x)
   \label{eq:int_dchi}
@@
 %
-by performing a Taylor expansion of the function $f$ around $x = k \chi = \nu$, where
-the Bessel function has its approximate maximum.
+by performing a Taylor expansion of \mk{an arbitrary differentialble} function
+$f$ around $x = k \chi = \nu = \ell + 1/2$, where the Bessel function has its
+approximate maximum.
 
@@
 
-To separate the $k$- and $\chi, \chi^\prime$-terms in equation~(\ref{eq:C_ell_full}), we
-first approximate the matter power cross-spectrum between two
-distances by the
-geometric mean of the two involved distances \citep{2005PhRvD..72b3516C,2016arXiv161200770K},
+To separate the $k$- and $\chi, \chi^\prime$-terms in
+equation~(\ref{eq:C_ell_full}), we first approximate the matter power
+cross-spectrum between two distances by the geometric mean of the two involved
+distances \citep{2005PhRvD..72b3516C,2016arXiv161200770K},
 %
@@
 %
+\mk{TODO: expand more on this. Explain why there is a non-zero correlation across epochs.}
 With this, equation~(\ref{eq:C_ell_full}) is written as
@@
 %
-We replaced the upper limits of the distance integral with infinity. \mk{Comment on this.}
 Note that this equation has a pre-factor $\ellbar^2(\ell, 2)$ corresponding to a spin-2 field, in contrast
@@
   \approx g(\nu) - \frac 1 2 \left.\frac{{\rm d}^2 g}{{\rm d} x^2}\right|_{x=\nu}
-                 - \frac \nu 6 \left.\frac{{\rm d}^3 g}{{\rm d} x^3}\right|_{x=\nu} ,
+                 - \frac \nu 6 \left.\frac{{\rm d}^3 g}{{\rm d} x^3}\right|_{x=\nu},
 \end{equation}
@@
 with $g(x) = k^{-1} f(k, \chi)$, $\chi=x/k$, and its derivatives $g^{(n)}(x) =
-k^{-1-n} f^{(n)}(k, \chi)$ for a given $k$. In our case the projection kernel is
+k^{-1-n} f^{(n)}(k, \chi)$ for a given $k$, \mk{where the derivatives of $f$
+are with respect to the second argument $\chi$.} \mk{This series expansion, the
+replacement of the integral with the evaluation of $g$ and its derivatives at
+the maximum of the Bessel function is a good approximation of the integral if
+$g$ is varying more slowly than the oscillating Bessel function [Check this].
+As we will see below, $f$ is a slowly varying function of the comoving
+distance.} In our case the projection kernel is
 %
@@
 %
-Replacing both distance integrals in equation~(\ref{eq:C_ell_full_Pk}) by their Taylor-expansions around $\nu = k \chi$ and $\nu = k \chi^\prime$,
-respectively, yields
+Replacing both distance integrals in equation~(\ref{eq:C_ell_full_Pk}) by their
+Taylor-expansions around the maxima $\nu(\ell) = \ell + 1/2$ of the two Bessel
+functions, which are $k \chi$ and $k \chi^\prime$, respectively, yields
 %
@@
     \left[ f_i(k, \chi) - \frac{1}{2 k^2} f_i^{\prime\prime}(k, \chi)
-      - \frac{\nu}{6 k^3} f_i^{\prime\prime\prime}(k, \chi) + \ldots \right]
+      - \frac{\nu(\ell)}{6 k^3} f_i^{\prime\prime\prime}(k, \chi) + \ldots \right]
     %\nonumber \\
@@
     \left[ f_j(k, \chi) - \frac{1}{2 k^2} f_j^{\prime\prime}(k, \chi)
-    - \frac{\nu}{6 k^3} f_j^{\prime\prime\prime}(k, \chi) + \ldots \right] \, .
+    - \frac{\nu(\ell)}{6 k^3} f_j^{\prime\prime\prime}(k, \chi) + \ldots \right] \, .
   \label{eq:C_ell_limber2_dk}
@@
   C^\gamma_{ij}(\ell) \approx & \, C^\gamma_{{\rm L1}, ij}(\ell) + C^\gamma_{{\rm L2}, ij}(\ell)
+      %\nonumber \\
+    = %&
+    \frac{\ellbar^2(\ell, 2)}{\nu^4(\ell)} \, \pref^2
+    \int_0^\infty {\rm d} \chi \, \chi^3 \, % P_{\rm m}\left( k \right)
+    \Bigg\{
+    %\left\{
+    (f_i f_j)(\nu(\ell)/\chi, \chi)
+    %\right.
       \nonumber \\
-    = & \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2
-    \int_0^\infty {\rm d} \chi \, \chi^3 \, % P_{\rm m}\left( k \right)
-    %\Bigg\{
-    \left\{
-    (f_i f_j)(\nu/\chi, \chi)
-    %\right.
-      %\nonumber \\
-    %&
+    &
     %\left.
-     - \frac 1 {\nu^2} \left[ \frac{\chi^2}{2} \left( f^{}_i f^{\prime\prime}_j + f_i^{\prime\prime} f^{}_j \right)(\nu/\chi, \chi)
-    + \frac{\chi^3}{6} \left( f^{}_i f^{\prime\prime\prime}_j + f^{\prime\prime\prime}_i f^{}_j \right)(\nu/\chi, \chi)
+     - \frac 1 {\nu^2(\ell)}
+    \left[ \frac{\chi^2}{2} \left( f^{}_i f^{\prime\prime}_j + f_i^{\prime\prime} f^{}_j \right)(\nu(\ell)/\chi, \chi)
+     + \frac{\chi^3}{6} \left( f^{}_i f^{\prime\prime\prime}_j + f^{\prime\prime\prime}_i f^{}_j \right)(\nu(\ell)/\chi, \chi)
     \right]
-    \right\} \, .
-    %\Bigg\}
+    + {\cal O}(\nu^{-4})
+    %\right\}
+    \Bigg\}
+    \, .
   \label{eq:C_ell_limber12_dr}
@@
 \begin{align}
-  C^\gamma_{{\rm L1}, ij}(\ell) = & \, \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2 \int {\rm d} \chi \frac{ q_i(\chi) q_j(\chi) }{a^2(\chi)}
-  P_{\rm m}\left(\frac{\nu}{\chi}; \chi\right) . \Label{ExtL1Sph}
+  C^\gamma_{{\rm L1}, ij}(\ell) = & \, \frac{\ellbar^2(\ell, 2)}{\nu^4(\ell)} \, \pref^2 \int {\rm d} \chi \frac{ q_i(\chi) q_j(\chi) }{a^2(\chi)}
+  P_{\rm m}\left(\frac{\nu(\ell)}{\chi}; \chi\right) . \Label{ExtL1Sph}
   \label{eq:C_ell_limber1}
@@
 \begin{align}
-  C^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2} \, \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2
-    \int {\rm d} \chi \, \chi^{2} a^{-2} \sqrt{P_{\rm m}\left(\frac\nu\chi; \chi\right)}
+  C^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2(\ell)} \, \frac{\ellbar^2(\ell, 2)}{\nu^4(\ell)} \, \pref^2
+    \int {\rm d} \chi \, \chi^{2} a^{-2} P^{1/2}_{\rm m}\left(\frac{\nu(\ell)}\chi; \chi\right)
     %\nonumber \\
@@
       \right)
-    \right](\nu/\chi, \chi) \, . 
+    \right](\nu(\ell)/\chi, \chi) \, . 
   \label{eq:C_ell_limber2_dr} 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Time-independent power spectrum separation}
+%\subsubsection{Time-independent power spectrum separation}
+\subsubsection{\mk{Facoring out the growth factor}}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-To further develop equation~(\ref{eq:P_geom_mean}), we divide out the growth factor to
-define a redshift-independent power spectrum $P_{\rm m}(k)$,
-%
-\begin{equation}
- P_{\rm m}(k, \chi) =: D_+(\chi) P_{\rm m}(k).
+To further develop equation~(\ref{eq:P_geom_mean}), we divide out the growth factor of
+the power spectrum,
+%
+\mk{
+\begin{equation}
+ P_{\rm m}(k, \chi) =: D^2_+(\chi) \tilde P_{\rm m}(k, \chi).
   \label{eq:P_k_chi_sep_s}
 \end{equation}
-%
-This is not exact, since some non-linear prescriptions of the power spectrum
-depend on redshift other than the growth factor, for example when computing the
-non-linear scale $k_{\rm NL}(z)$ for \texttt{halofit} \citep{2003MNRAS.341.1311S}.
-
-With this approximation, the \mk{$\chi$-independent term $P_{\rm m}(k)$}
-factors out from equation~(\ref{eq:f_LA08}), and we define the separated kernel
-function $f_{\rm s}$ as
+}
+%
+\mk{The function $\tilde P_{\rm m}$ is in general not time-independent, except
+in the case of a linear matter power spectrum in the absence of massive
+neutrinos, and in General Relativity. However, the second-order Limber terms
+are expected to be important only for small $\ell$, that is either for small
+$k$ wher the evolution is linear, or for small $\chi$, where the lensing
+efficiency is small. The accuracy of a very nearby tomographic bin with low
+mean redshift should be further examined, but this is not the case for
+CFHTLenS.}
+
+\mk{With the definition (\ref{eq:P_k_chi_sep_s}), we factor out the function
+$\tilde P_{\rm m}(k, \chi)$} from equation~(\ref{eq:f_LA08}), and we define the
+separated kernel function $f_{\rm s}$ as
 %
@@
 %
-The second-order Limber term of the shear power spectrum can then be simplified to
-%
-\begin{align}
-  C^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2} \, \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2
-    \int {\rm d} \chi \, \chi^{2} a^{-2} P_{\rm m}\left(\frac\nu\chi; \chi\right)
+The second-order Limber term of the shear power spectrum can then be approximated as
+%
+\begin{align}
+  C^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2(\ell)} \, \frac{\ellbar^2(\ell, 2)}{\nu^4(\ell)} \, \pref^2
+    \int {\rm d} \chi \, \chi^{2} a^{-2} P_{\rm m}\left(\frac{\nu(\ell)}\chi; \chi\right)
     %\nonumber \\
@@
 We compute the numerical higher derivatives as follows. The functions $f_{\rm
-s}(\chi)$ are fit as power laws with index $\approx 1.5$. The fit is
+s}(\chi)$ are fitted as power laws with index $\approx 1.5$. The fit is
 performed between $\chi_{\rm min} = 0.001 {\rm Mpc}/h$ and $\chi_{\rm max} =
@@
   P^\gamma_{{\rm L1}, ij}(\ell) = & \, p(\ell) \, \pref^2 \int {\rm d} \chi \frac{ q_i(\chi) q_j(\chi) }{a^2(\chi)}
-  P_{\rm m}\left(k = \frac{\nu}{\chi}; \chi\right);
+  P_{\rm m}\left(\frac{\nu(\ell)}{\chi}; \chi\right);
   \label{eq:P_ell_limber1}
   \\
-    P^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2} \, p(\ell) \, \pref^2
-    \int {\rm d} \chi \, \chi^{2} a^{-2} P_{\rm m}\left(k = \frac\nu\chi; \chi\right)
+    P^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2(\ell)} \, p(\ell) \, \pref^2
+    \int {\rm d} \chi \, \chi^{2} a^{-2} P_{\rm m}\left(\frac{\nu(\ell)}\chi; \chi\right)
     %\nonumber \\
     %& \times
-    \frac{a(\chi)}{2 D^{-1}_+(\chi)} \chi^{3/2} \left[ q^{}_i f^{\prime\prime}_{{\rm s}j} + f^{\prime\prime}_{{\rm s}i} q^{}_j  
+    \frac{a(\chi)}{2 D_+(\chi)} \chi^{3/2} \left[ q^{}_i f^{\prime\prime}_{{\rm s}j} + f^{\prime\prime}_{{\rm s}i} q^{}_j  
       + \frac{\chi}{3} \left( q^{}_i f^{\prime\prime\prime}_{{\rm s}j} + f^{\prime\prime\prime}_{{\rm s}i} q^{}_j
@@
 %
-Further approximations are commonly made for the pre-factor $p(\ell) = \ell^4/\nu^4$ and $\nu(\ell)$:
+Further approximations are \mk{can} made for the pre-factor $p(\ell) = \ell^4/\nu^4(\ell)$ and $\nu(\ell)$:
 %
@@
 
-In Fig.~\ref{fig:Cl_cases} we present the full spherical projection of the shear power spectrum in comparison to shear power spectra derived assuming
-the range of different approximations listed in Table~\ref{tab:cases}.  The adopted redshift distribution corresponds to CFHTLenS
-\citep{CFHTLenS-2pt-notomo} and we assume their best-fit flat $\Lambda$CDM cosmology with $\Omega_{\rm m}=0.279$, $\Omega_{\rm b}=0.046$, $\sigma_8=0.79$, $H_0=0.701$, $n_{\rm s}=0.96$. 
-For $\ell > 100$ we find that all shear power spectra predictions agree with the full spherical solution to better than one percent, with the majority of the approximations tested accurate to better than 0.1 per cent.
-
-Considering first the flat-sky cases, the standard first-order Limber approximation, (L1Fl), that was adopted for all pre-2014 CFHTLenS analyses, we find to be 
-accurate to better than 10\% for $\ell>3$, converging slowly to the true projection with percent level precison at $\ell>100$. 
-For the extended Limber approximations `hybrid' cases (ExtL1FlHyb and ExtL2FlHyb), despite decreased accuracy
-for $\ell < 8$ in comparison to the standard first-order Limber case, the errors with respect to
-the true power spectrum decrease much faster, as $\ell^{-2}$, such that percent-level precision is reached at $\ell>15$.
-The first-order extended Limber approximation `hybrid' cases (ExtL1FlHyb) was adopted by both \citet{joudaki/etal:2016} and \cite{KiDS-450}\footnote{We confirm that there is a typographical error in equation 4 of \cite{KiDS-450} which should include the extra term of `+0.5' in $\nu(\ell)$ that was incorporated in the cosmological analysis.}.
-
-The outlier in the flat-sky cases is the extended Limber approximation (ExtL1Fl) which performs relatively poorly, and
-reaches 10\% precision only at $\ell > 100$. The same slow convergence can be
-observed for the corresponding second-order flat case, ExtL2Fl.
-To our knowledge this form of the flat-sky approximation has not been used in any cosmic shear studies to date, and should not be used in any future studies given these results.
-The poor behaviour of this case, in comparison with the `hybrid' case, (e.g ExtL1FlHyb) can be understood by considering Taylor expansions of the different pre-factors.
-The spherical pre-factor,
+In Fig.~\ref{fig:Cl_cases} we present the full spherical projection of the
+shear power spectrum in comparison to shear power spectra derived assuming the
+range of different approximations listed in Table~\ref{tab:cases}.  The adopted
+redshift distribution corresponds to CFHTLenS \citep{CFHTLenS-2pt-notomo} and
+we assume their best-fit flat $\Lambda$CDM cosmology with $\Omega_{\rm
+m}=0.279$, $\Omega_{\rm b}=0.046$, $\sigma_8=0.79$, $h=0.701$, $n_{\rm
+s}=0.96$. For $\ell > 100$ we find that all shear power spectra predictions
+agree with the full spherical solution to better than one percent, with the
+majority of the approximations tested accurate to better than 0.1 per cent.
+
+Considering first the flat-sky cases, the standard first-order Limber
+approximation, (L1Fl), that was adopted for all pre-2014 CFHTLenS analyses, we
+find to be accurate to better than 10\% for $\ell>3$, converging slowly to the
+true projection with percent level precison at $\ell>100$. For the extended
+Limber approximations `hybrid' cases (ExtL1FlHyb and ExtL2FlHyb), despite
+decreased accuracy for $\ell < 8$ in comparison to the standard first-order
+Limber case, the errors with respect to the true power spectrum decrease much
+faster, as $\ell^{-2}$, such that percent-level precision is reached at
+$\ell>15$.  The first-order extended Limber approximation `hybrid' cases
+(ExtL1FlHyb) was adopted by both \citet{joudaki/etal:2016} and
+\cite{KiDS-450}\footnote{We confirm that there is a typographical error in
+equation 4 of \cite{KiDS-450} which should include the extra term of `+0.5' in
+$\nu(\ell)$ that was incorporated in the cosmological analysis.}.
+
+The outlier in the flat-sky cases is the extended Limber approximation
+(ExtL1Fl) which performs relatively poorly, and reaches 10\% precision only at
+$\ell > 100$. The same slow convergence can be observed for the corresponding
+second-order flat case, ExtL2Fl. To our knowledge this form of the flat-sky
+approximation has not been used in any cosmic shear studies to date, and should
+not be used in any future studies given these results.  The poor behaviour of
+this case, in comparison with the `hybrid' case, (e.g ExtL1FlHyb) can be
+understood by considering Taylor expansions of the different pre-factors.  The
+spherical pre-factor,
+%
 \begin{equation}
@@
 \end{equation}
+%
 can be compared to the flat-sky extended Limber pre-factor
+%
 \begin{equation}
@@
 \end{equation} 
-showing it to be more deviant from the full spherical solution, than the `hybrid' $p(\ell) = 1$ case.
+%
+showing it to be more deviant from the full spherical solution, than the
+`hybrid' $p(\ell) = 1$ case.
 
@@
   $2^{\rm st}$-order extended Limber, spherical & ExtL2Sph & (\ref{eq:C_ell_limber1})+(\ref{eq:C_ell_limber2_dr_s})
-    & $\frac{\ellbar^2(\ell, 2)}{(\ell+1/2)^4}$ & $\ell+\frac 1 2$ & Best approximation but mixing with flat-sky Hankel transform \\ \hline
+    & $\frac{\ellbar^2(\ell, 2)}{(\ell+1/2)^4}$ & $\ell+\frac 1 2$ & Best approximation \\ \hline
   %
   Full spherical & FullSph & (\ref{eq:C_ell_full}) &
-      $\ellbar^2(\ell, 2)$ & - & Correct projection \\ \hline
+      - & - & Correct projection \\ \hline
   %
@@
   % &
-  = \frac 1 {2\pi} \int {\rm d} \ell \, \ell {\rm J}_0(\ell
+  = \frac 1 {2\pi} \int {\rm d} \ell \, \ell \, {\rm J}_0(\ell
    \theta)
@@
   = \frac 1 {2\pi} \int
-   {\rm d} \ell \, \ell {\rm J}_4(\ell \theta)
+   {\rm d} \ell \, \ell \, {\rm J}_4(\ell \theta)
   P^\gamma(\ell).
@@
 %
-where ${\rm J}_\nu$ first-kind Bessel function of order $\nu$. The flat-sky
-shear power spectrum $P^\gamma$ an be related to the underlying matter power
+The flat-sky
+shear power spectrum $P^\gamma$ can be related to the underlying matter power
 spectrum through equation~(\ref{eq:P_ell_limber1}) when adopting a first-order
-extended Limber approximation, or equation~(\ref{eq:P_ell_limber2}) when adopting
-a second-order extended Limber approximation.
-
-On a sphere, correlation functions cannot be related to the power spectrum by
-the Hankel transform in equation~(\ref{eqn:xiGG}), as the spherical power
-spectrum is formally not defined for non-integer $\ell$ \citep[see][for
-alternative spherical-sky formulae for the two-point correlation
-function]{2005PhRvD..72b3516C}. In particular, the spherical Bessel functions
-necessary to compute the full projection in equation~(\ref{eq:C_ell_full}) is
-defined only for integer order $\ell$. \mk{I think this is actually not true,
-since J$_\nu$ can be computed for fractional $\nu$, and then one could use the
-identity (\ref{eq:jJ}). Or is it?}.
+extended Limber approximation, or equation~(\ref{eq:P_ell_limber2}) when
+adopting a second-order extended Limber approximation.
+
+On a sphere, correlation functions \mk{formally} cannot be related to the power
+spectrum by the Hankel transform in equation~(\ref{eqn:xiGG}), \mk{and should be
+replaced by a Legendre transform}. The spherical power spectrum is formally not
+defined for non-integer $\ell$ \citep[see][for alternative spherical-sky
+formulae for the two-point correlation function]{2005PhRvD..72b3516C}. \sout{In
+particular, the spherical Bessel functions necessary to compute the full
+projection in equation~(\ref{eq:C_ell_full}) is defined only for integer order
+$\ell$.}
+%\mk{I think this is actually not true, since J$_\nu$ can be computed
+%for fractional $\nu$, and then one could use the identity (\ref{eq:jJ}). Or is
+%it?}.
 
@@
   \psi_{\ell m} = \frac 2 {c^2} \int {\rm d} \Omega {\rm Y}^\ast_{\ell m}(\theta, \varphi)
-    \int_0^{\chi_{\rm lim}} \frac{{\rm d}\chi}{\chi} q(\chi) \int \frac{{\rm d}^3 k}{(2\pi)^3} \hat \Phi(\vec k; \chi) {\rm e}^{-{\rm i} \vec k \vec r}.
+    \int_0^{\chi_{\rm lim}} \frac{{\rm d}\chi}{\chi} q(\chi) \int \frac{{\rm d}^3 k}{(2\pi)^3} \hat \Phi(\vec k; \chi) {\rm e}^{-{\rm i} \vec k \cdot \vec r}.
 \end{equation}
@@
 \begin{equation}
-  {\rm e}^{{\rm i} \vec k \vec r} = 4 \pi \sum_{\ell=0}^{\infty} \sum_{m=-\ell}^{\ell}
+  {\rm e}^{{\rm i} \vec k \cdot \vec r} = 4 \pi \sum_{\ell=0}^{\infty} \sum_{m=-\ell}^{\ell}
     {\rm i}^\ell \, {\rm j}_\ell(k \chi)
@@
 clustering, their calculations are general enough to apply to a weak-lensing
-context. Their Equation.~(5) is a spherical cross-power spectrum of two scalar fields
-$A$ and $B$, projected from 3D to 2D via projection kernels $F_A$ and $F_B$
-defined in their Equation.~(4). Comparing their expressions with the weak-lensing
-potential (\ref{eq:psi}), we set $F_A(\chi) = F_B(\chi) = 2 c^{-2}
-D_+(\chi) q(\chi) \chi^{-1}$. With that, their Equations.~(5) is identical to equation~(\ref{eq:C_ell_phi_Pphi}).
+context. Their Equation.~(5) is a spherical cross-power spectrum of two scalar
+fields $A$ and $B$, projected from 3D to 2D via projection kernels $F_A$ and
+$F_B$ defined in their Equation.~(4). Comparing their expressions with the
+weak-lensing potential (\ref{eq:psi}), we set $F_A(\chi) = F_B(\chi) = 2 c^{-2}
+D_+(\chi) q(\chi) \chi^{-1}$. With that, their Equations.~(5) is identical to
+equation~(\ref{eq:C_ell_phi_Pphi}).
 
@@
 presented in eq.~(12). This is consistent with our first-order
-(equation~\ref{eq:C_ell_limber1}) and second-order (equation~\ref{eq:C_ell_limber2_dr}) Limber
-approximation terms, when accounting for the difference between lensing
-potential and shear 2D power spectrum, and 3D potential and matter power
-spectrum.
+(equation~\ref{eq:C_ell_limber1}) and second-order
+(equation~\ref{eq:C_ell_limber2_dr}) Limber approximation terms, when
+accounting for the difference between lensing potential and shear 2D power
+spectrum, and 3D potential and matter power spectrum.
 
@@
                 \frac{q_j(\chi^\prime)}{a(\chi^\prime)}
-                \nonumber \\
-                & \times \int_0^\infty {\rm d} k \, k^2 \, P_{\rm m}(k; \chi, \chi^\prime) \,
+                %\nonumber \\
+                %& \times
+                \int_0^\infty {\rm d} k \, k^2 \, P_{\rm m}(k; \chi, \chi^\prime) \,
                 {\rm j}_\ell(k \chi) \, {\rm j}_\ell(k \chi^\prime) ,

### 2017-02-13 authors.tex
MK: Shahab's and peter's last comments; added Ludo's figure

@@
 $^6$Argelander-Institut f\"ur Astronomie, Auf dem H\"ugel 71, 53121 Bonn, Germany\\
-$^7$Leiden Observatory, Leiden University, Niels Bohrweg 2, 2333 CA Leiden, the Netherlands\\
+$^7$Kavli Institute for the Physics and Mathematics of the Universe (WPI), The University of Tokyo Institutes for Advanced Study, \\
+The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
 $^8$Department of Physics and Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC V6T 1Z1, Canada\\

### 2017-02-13 cfhtlens.tex
MK: Shahab's and peter's last comments; added Ludo's figure

@@
 including the cross-covariance between both components. The Bayesian
-Monte-Carlo parameter sampling is performed using the publically available
+Monte-Carlo parameter sampling is performed using the publicly available
 software \textsc{CosmoPMC}\footnote{\texttt{http://www.cosmostat.org/software/cosmopmc}}
@@
   L1Fl       & $0.787^{+0.031}_{-0.033}$ & $0.739^{+0.029}_{-0.031}$ \\
-  ExtL1Fl    & $x^{+y}_{-z}$ & $x^{+y}_{-z}$ \\
+  ExtL1Fl    & $0.792 \pm 0.032$ & $0.744 \pm 0.030$ \\
   ExtL1FlHyb & $0.788^{+0.031}_{-0.033}$ & $0.740^{+0.029}_{-0.031}$ \\

### 2017-02-13 limber2.tex
MK: Shahab's and peter's last comments; added Ludo's figure

@@
 
-\title[Precision calculations for cosmic shear projections]{Precision calculations of cosmic shear projections}  %??
-%{Precision calculations of the cosmic shear power spectrum projection}
+\title[Precision calculations of the cosmic shear projection]{Precision calculations of the cosmic shear power spectrum
+projection}
 
@@
 convergence. We discuss various approximations, such as flat-sky, first- and
-second-order Limber equations for the projection. We find that the impact of adopting 
-these approximations are negligible when constraining cosmological parameters from 
-current weak lensing surveys.
-This is demonstrated using data from the Canada-France-Hawaii Lensing Survey (CFHTLenS). 
-We find that the reported tension with Planck CMB temperature anisotropy results cannot be alleviated, in
-contrast to the recent claim made by \citet{2016arXiv161104954K}. 
-For future large-scale surveys with unprecedented precision, we show that the spherical
+second-order Limber equations for the projection. We find that the impact of
+adopting these approximations are negligible when constraining cosmological
+parameters from current weak lensing surveys.
+%
+This is demonstrated using data from the Canada-France-Hawaii Lensing Survey
+(CFHTLenS). We find that the reported tension with Planck Cosmic Microwave
+Background (CMB) temperature anisotropy results cannot be alleviated, in
+contrast to the recent claim made by \citet{2016arXiv161104954K}. For future
+large-scale surveys with unprecedented precision, we show that the spherical
 second-order Limber approximation will provide sufficient accuracy, as it is in
-agreement with the full projection at the sub-percent level for $\ell > 3$.  
-In the spirit of reproducible research, our numerical implementation of all approximations
-and the full projection are publicly available within the package
-\textsc{nicaea} at \texttt{http://www.cosmostat.org/software/nicaea}.
+agreement with the full projection at the sub-percent level for $\ell > 3$,
+\mk{and the corresponding errors an order of magnitude below cosmic
+variance for all $\ell$.}
+%
+In the spirit of reproducible research, our numerical implementation of all
+approximations and the full projection are publicly available within the
+package \textsc{nicaea} at \texttt{http://www.cosmostat.org/software/nicaea}.
 
@@
 We consider spherical coordinates and the flat-sky approximation, and compute
-the full projection. We show that the second-order Limber approximation is an
+the full projection. \mk{The first-order extended Limber approximation provides
+sub-percent accuracy for $\ell > 10$ and is sufficient for present surveys. The
+associated errors are sub-dominant even for future large surveys.}
+
+We \mk{further} show that the second-order Limber approximation is an
 accurate representation of the full projection, with better than percent level
@@
 %
+\mk{Complex conjugation is denoted with the superscript $^\ast$.}
 To specify tomographic redshift bins $i=0\ldots N_z-1$, we introduce a family
@@
 
+\mk{Peter's comment: What does the correlation between two
+epochs actually mean if they are not on the backward light cone?}
+
 In the following section we will discuss the relations between shear and
@@
 expansion for general projections from 3D to 2D scalar fields in the spherical,
-all-sky case. First, we use the identity of Bessel functions
+all-sky case. \mk{We apply ther general derivation to the case of weak lensing,
+and contrary to \cite{2008PhRvD..78l3506L} account for a time-dependent power
+spectrum using two approaches presented in Sects.~\ref{sec:geom_mean} and
+\ref{sec:factor_D}.}
+
+First, we use the identity of Bessel functions
 %
@@
 \subsubsection{Geometric mean cross-correlation power spectrum}
+\label{sec:geom_mean}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsubsection{\mk{Facoring out the growth factor}}
+\label{sec:factor_D}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 neutrinos, and in General Relativity. However, the second-order Limber terms
-are expected to be important only for small $\ell$, that is either for small
-$k$ wher the evolution is linear, or for small $\chi$, where the lensing
+are expected to be important only for small $\ell$, since for large $\ell$ the first-order
+Limber equation (\ref{eq:C_ell_limber1}) is dominant. Eq.~(\ref{eq:P_k_chi_sep_s})
+becomes a good approximation for small $\ell$, since that means either small
+$k$ where the evolution is linear, or small $\chi$, where the lensing
 efficiency is small. The accuracy of a very nearby tomographic bin with low
@@
   %
-  \item \Label{ExtL[1$|$2]Fl}: $p(\ell) = \ell^4/(\ell + 1/2)^4$. This corresponds to the \emph{extended} Limber
+  \item $p(\ell) = \ell^4/(\ell + 1/2)^4$. This corresponds to the \emph{extended} Limber
     approximation \LabelTxt{ExtL1Fl,ExtL2Fl} with $\nu(\ell) = \ell + 1/2$; however the following case is typically employed:
   %
-  \item $p(\ell) = 1$, with $\nu = \ell + 1/2$. This is
+  \item $p(\ell) = 1$, \mk{but} keeping as argument of the power spectrum $\nu(\ell) = \ell + 1/2$. This is
     a \emph{hybrid} between
-    standard and extended Limber approximation \Label{ExtL1FlHyb,ExtL2FlHyb}, and this case to first order
+    standard and extended Limber approximation \Label{ExtL1FlHyb,ExtL2FlHyb}, and this case of first order
     was used in \cite{KiDS-450,joudaki/etal:2016}. As is shown
-    later, this is a better approximation to the full projection than case (ii).
+    later, this is a better approximation to the full projection than case (ii). \mk{In (\ref{eq:P_ell_limber2})
+    the second-order suppression factor is also left to be $\nu^{-2}(\ell) = (\ell + 1/2)^{-2}$, providing
+    a slightly more accurate approximation compared to $\nu^{-2}(\ell) = \ell^{-2}$.}
 \end{enumerate}
@@
 $\ell>15$.  The first-order extended Limber approximation `hybrid' cases
-(ExtL1FlHyb) was adopted by both \citet{joudaki/etal:2016} and
+(ExtL1FlHyb) was adopted by \citet{joudaki/etal:2016}, \citet{joudaki/etal:2017}, and
 \cite{KiDS-450}\footnote{We confirm that there is a typographical error in
@@
 approximation is a factor of \mk{15 times} faster than the calculation of the
-full spherical solution \mk{(averaged over the first $18$ $\ell$-modes).} We note that the
-\mk{sub-$0.1\%$}-noise seen in the right panel of Fig.~\ref{fig:Cl_cases} is
-due to numerical noise arising from numerical integration errors in the
-calculation of the full spherical solution when $\ell > 20$.
+full spherical solution \mk{(averaged over the first $18$ $\ell$-modes).} We
+note that the \mk{sub-$0.1\%$}-noise seen in the right panel of
+Fig.~\ref{fig:Cl_cases} is due to numerical noise arising from numerical
+integration errors in the calculation of the full spherical solution when $\ell
+> 20$.
+
+\mk{Compared to the statistical power of current and future surveys, all
+approximations discussed here are subdominant to the cosmic variance, $\Delta
+C(\ell) / C(\ell) = [f_{\rm sky} (2 \ell + 1)]^{-1/2}$
+\citep{1992ApJ...388..272K}, where $f_{\rm sky}$ is the faction of sky observed
+by the survey. The uncertainties from the Limber approximation in the case of
+ExtL2Sph is an order of magnitude below the cosmic variance of a Euclid-like
+survey (sky area $15,000$ square degrees) for all $\ell$.}
 
@@
 
-  \caption{\label{fig:Cl_cases}The shear power spectrum for different approximations listed in Table~\ref{tab:cases}. Limber to first order: standard with flat-sky (L1Fl),
+  \caption{\label{fig:Cl_cases}%
+        The shear power spectrum for different approximations listed in Table~\ref{tab:cases}.
+        Limber to first order: standard with flat-sky (L1Fl),
         extended for flat sky (ExtL1Fl), extended hybrid for flat sky (ExtL1FlHyb),
@@
         and extended spherical expansion (ExtL2Sph); full (exact) spherical projection (FullSph).
-        The left panel shows the total shear power spectrum.  The right panel shows the fractional difference resulting from each approximation, 
-        relative to the full spherical projection of the shear power spectrum.
+        The left panel shows the total shear power spectrum.  The right panel shows the fractional difference
+        resulting from each approximation, 
+        relative to the full spherical projection of the shear power spectrum. \mk{The two light grey curves on the
+        top show the cosmic variance for KiDS- and Euclid-like surveys with areas of $1,500$ and $15,000$
+        square degrees, respectively.}
         }
@@
 galaxy shape catalogue. The baseline quantity is the two-point correlation
-function \citep{1991ApJ...370....1M, 1992ApJ...388..272K,
-BS01}, given by
+function \citep{1991ApJ...370....1M, 1992ApJ...388..272K, BS01}, given by
 %
@@
 %
-The flat-sky
-shear power spectrum $P^\gamma$ can be related to the underlying matter power
-spectrum through equation~(\ref{eq:P_ell_limber1}) when adopting a first-order
-extended Limber approximation, or equation~(\ref{eq:P_ell_limber2}) when
-adopting a second-order extended Limber approximation.
+The flat-sky shear power spectrum $P^\gamma$ can be related to the underlying
+matter power spectrum through equation~(\ref{eq:P_ell_limber1}) when adopting a
+first-order extended Limber approximation, or equation~(\ref{eq:P_ell_limber2})
+when adopting a second-order extended Limber approximation.
 
 On a sphere, correlation functions \mk{formally} cannot be related to the power
-spectrum by the Hankel transform in equation~(\ref{eqn:xiGG}), \mk{and should be
-replaced by a Legendre transform}. The spherical power spectrum is formally not
-defined for non-integer $\ell$ \citep[see][for alternative spherical-sky
-formulae for the two-point correlation function]{2005PhRvD..72b3516C}. \sout{In
-particular, the spherical Bessel functions necessary to compute the full
-projection in equation~(\ref{eq:C_ell_full}) is defined only for integer order
-$\ell$.}
+spectrum by the Hankel transform in equation~(\ref{eqn:xiGG}), \mk{and should
+be replaced by a Legendre transform}. The spherical power spectrum is formally
+not defined for non-integer $\ell$ \citep[see][for alternative spherical-sky
+formulae for the two-point correlation function]{2005PhRvD..72b3516C}, \mk{as
+functions defined on the sphere are necessarily periodic}. \sout{In particular,
+the spherical Bessel functions necessary to compute the full projection in
+equation~(\ref{eq:C_ell_full}) is defined only for integer order $\ell$.}
 %\mk{I think this is actually not true, since J$_\nu$ can be computed
@@
 
-As we have shown in section~\ref{sec:comp}, however, the spherical
-second-order extended Limber approximation provides a percent-level precision
-representation of the full spherical projection for $\ell > 3$.  
-In the Limber approximations the Bessel functions \mk{are expanded into}
-polynomials, allowing for arbitrary wave modes $\ell$. The spherical pre-factor
-$\ellbar(\ell, 2)$ (equation~\ref{eq:ellbar}) can be generalised to non-integer
-arguments and is positive for $\ell \le 2$. We can thus use the spherical power
-spectrum in the Limber approximations for the Hankel transformation to compute
-the two-point correlation functions.  We therefore do not
-present predictions for the two-point shear correlation function using the full
-spherical projection, instead choosing the spherical second-order extended
-Limber approximation (ExtL2Sph) as our reference in this case.
-
-Figure.~\ref{fig:xi_pm} presents the two-point correlation functions
-$\xi_+$ (left) and $\xi_-$ (right) using the different cases for the shear
-power spectrum listed in Table~\ref{tab:cases}. The adopted CFHTLenS redshift
-distribution and fiducial cosmological model are the same as in
+As we have shown in section~\ref{sec:comp}, however, the spherical second-order
+extended Limber approximation provides a percent-level precision representation
+of the full spherical projection for $\ell > 3$.
+%In the Limber approximations
+%the Bessel functions \mk{of order $\nu$ are expanded into} polynomials \mk{in
+%$\nu$}, allowing for arbitrary wave modes $\ell$.
+The spherical pre-factor $\ellbar(\ell, 2)$ (equation~\ref{eq:ellbar}) can be
+generalised to non-integer arguments and is positive for $\ell \ge 2$. We can
+thus use the spherical power spectrum in the Limber approximations for the
+Hankel transformation to compute the two-point correlation functions. \mk{This
+has the advantage of very fast numerical implementations of the Hankel
+tranforms using FFTs \citep{fftlog}, which can be used in
+Monte-Carlo sampling.}
+
+\mk{We compare predictions for the two-point shear correlation function using
+the Hankel transformation and the full spherical Legendre transformation in
+Fig.~\ref{fig:xi_p_legendre}. We show the full projection and the best
+approximation, ExtL2Sph. Note that for the `FullSph' case we replace the full
+projection with ExtL2Sph for $\ell > 200$ to save computation time. We see no
+qualitative differences between the three cases.} \mk{[Note: The differences in
+the actual figure probably come from the difference n $\ell_{\rm max}$, to be
+updated.]}
+
+%We therefore do not present predictions for the
+%two-point shear correlation function using the full spherical projection,
+%instead choosing the spherical second-order extended Limber approximation
+%(ExtL2Sph) as our reference in this case. \mk{Todo: Include Ludo's spherical
+%calcuations of $\xi_\pm$.}
+
+Figure.~\ref{fig:xi_pm} presents the Hankel-transform two-point correlation
+functions $\xi_+$ (left) and $\xi_-$ (right) using the different cases for the
+shear power spectrum listed in Table~\ref{tab:cases}. \mk{We use `ExtL2Sph' as reference case.}
+The adopted CFHTLenS
+redshift distribution and fiducial cosmological model are the same as in
 Figure.~\ref{fig:Cl_cases}. As is clear by the red dotted curve, using the
 Planck cosmology \citep{2015arXiv150201589P} induces a significant change in
-the amplitude of the shear correlation function in comparison to the different projection
-methods.
+the amplitude of the shear correlation function in comparison to the different
+projection methods.
+
+\begin{figure}
+
+  \begin{center}
+    \resizebox{0.5\hsize}{!}{
+      \includegraphics{figures/xi_p_legendre}
+    }
+  \end{center}
+
+  \caption{The shear correlation function component $\xi_+$ for the ExtL2Sph
+projection using the Hankel transform (green line), compared to the spherical
+Legendre transform of the same projection (blue squares), and the FullSph
+projection (red circles).}
+
+  \label{fig:xi_p_legendre}
+
+\end{figure}
 
@@
 Lance Miller, Benjamin Joachimi, Chris Blake and Adam Amara for very helpful
-discussions. This work was financially supported by the DFG (Emmy Noether
-grant Hi 1495/2-1; SI 1769/1-1; TR33 `The Dark Universe'), the Alexander
-von Humboldt Foundation, the ERC (grants 279396, 647112), the Seventh Framework
-Programme of the European Commission (Marie Sklodwoska Curie Fellowship grant
-656869), NSERC and CIfAR.
+discussions. This work was financially supported by the DFG (Emmy Noether grant
+Hi 1495/2-1; SI 1769/1-1; TR33 `The Dark Universe'), the Alexander von Humboldt
+Foundation, the ERC (grants 279396, 647112), the Seventh Framework Programme of
+the European Commission (Marie Sklodwoska Curie Fellowship grant 656869),
+NSERC, CIfAR, and the World Premier International Research Center Initiative
+(WPI), MEXT, Japan. Parts of this research were conducted by the Australian
+Research Council Centre of Excellence for All-sky Astrophysics (CAASTRO),
+through project number CE110001020. MV acknowledges support from the European
+Research Council under FP7 grant number 279396 and the Netherlands Organisation
+for Scientific Research (NWO) through grants 614.001.103.
 
@@
 %
-We take the absolute square and use the definition of the 3D potential power spectrum (equation~\ref{eq:p_phi}),
-to arrive at the expression in equation~(\ref{eq:C_ell_phi_Pphi}).
-Here, $P_{\rm m}$ is the 3D matter power cross-spectrum at line-of-sight comoving
-Fourier mode $k$ and comoving distances $\chi$ and $\chi^\prime$. We denote
-complex conjugation with superscript $^\ast$.
-\mk{Peter's comment: What does the correlation between two epochs actually mean if they
-are not on the backward light cone?}
-
-The delta-function resolves one 3D Fourier
-integral. We split the second integration into radial and spherical
-coordinates, ${\rm d}^3 k = {\rm d} k k^2 {\rm d} \Omega_k$ and use once again
-the orthogonality of the spherical harmonics to resolve the spherical integral. 
-This leads to the potential power spectrum in equation~(\ref{eq:C_ell_phi_Pm}).
+\mk{To obtain the potential power spectrum,} we take the absolute square of the
+last equation and use the definition of the 3D potential power spectrum
+(equation~\ref{eq:p_phi}). The delta-function resolves one 3D Fourier integral.
+We split the second integration into radial and spherical coordinates, ${\rm
+d}^3 k = {\rm d} k k^2 {\rm d} \Omega_k$ and use once again the orthogonality
+of the spherical harmonics to resolve the spherical integral. This leads to the
+potential power spectrum in equation~(\ref{eq:C_ell_phi_Pphi}).
 
@@
 \cite{2016arXiv161104954K} compute the full projection of the weak-lensing
-power spectrum, which they present as spherical-radial representation the 3D
+power spectrum, which they present as spherical-radial representation of the 3D
 shear field. Our results in equation~(\ref{eq:C_ell_full}) corresponds to their
@@
 photometric redshifts, with $p(z | z_{\rm p}) = \delta_{\rm D}(z - z_{\rm p})$,
-and for a bin function that selects the redshift bin $i$, $W^{\rm SR}(z, z_{\rm
-p}) = 1_{z \in i-\mbox{th bin}}$. We find that Equation~(7) in
-\cite{2016arXiv161104954K} is missing a factor $2/\pi$.
-
-\cite{2016arXiv161104954K} derives the spherical and extended Limber
+and for a bin function that selects the redshift bin of $z$, $W^{\rm SR}(z,
+z_{\rm p})$ \mk{is unity if $z_{\rm p}$ is in the redshift bin denoted by $z$,
+and zero otherwise.} We find that Equation (7) in \cite{2016arXiv161104954K} is
+missing a factor $2/\pi$.
+
+\cite{2016arXiv161104954K} derive the spherical and extended Limber
 approximation starting from the full spherical projection in their Appendix.~A.
-We find that the filter function $q$ defined in their Equation~(31) has an
+We find that the filter function $q$ defined in their Equation (31) has an
 additional factor of comoving distance $r$, and an additional factor of
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Bernardeau, Bonvin, Van de Rijt, Vernizzi (2012); van de Rijt (2012)}
+\subsection{Bernardeau, Bonvin, Van de Rijt, Vernizzi (2012); Van de Rijt (2012)}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \cite{2012PhRvD..86b3001B} present the non-tomographic full projection
-$C(\ell)$ in the approximation of the 3D potential power spectrum $P^\Phi$
-separating into $k$- and $\chi$-dependent functions in their Equation~(44).
+$C(\ell)$ in the approximation of the 3D potential power spectrum $P_\Phi$
+separating into $k$- and $\chi$-dependent functions in their Equation (44).
 Their expression holds for a single source redshift.
 
-The PhD thesis of Van de Rijt \cite{vande2012} presents an explicit calculation
-of the second-order Limber approximation. They carry out the derivatives of the
+The PhD thesis of \cite{vande2012} presents an explicit calculation of the
+second-order Limber approximation. They carry out the derivatives of the
 kernels $f$ under the assumption of a constant growth-suppression factor
@@
 \begin{equation}
-  f^{\prime\prime}(\chi) + \frac{\chi}{3} f^{\prime\prime\prime}(\chi)
+  f_{\rm s}^{\prime\prime}(\chi) + \frac{\chi}{3} f_{\rm s}^{\prime\prime\prime}(\chi)
     = - \frac 1 8 \chi^{-5/2} \left( \frac 5 \chi
@@
 %
-This result confirms the power-law behaviour of the filter function, which we
-exploited earlier to fit this function.
+This result confirms the power-law behaviour for $\chi \ll \chi_{\rm S}$ of the
+filter function, which we exploited earlier to fit this function.
 
@@
 equation to replace the matter with the potential power spectrum we obtain the
-same expression as \cite{vande2012} (their Equation.~7.19), except for an
+same expression as \cite{vande2012} (their Equation~7.19), except for an
 additional factor $a^2(\chi)$. This difference is accounted for by the factor
@@
 In Fig.~\ref{fig:L1L2E_Rijt} we reproduce Fig.~7.3 from \cite{vande2012} using
-a similar set up (flat $\Lambda$ Universe with $\Omega_{\rm m} = 0.3, h=0.65,
+a similar set up, a flat $\Lambda$ Universe with $\Omega_{\rm m} = 0.3, h=0.65,
 \Omega_{\rm b} = 0.0461, \sigma_8 = 0.8, n_{\rm s} = 0.96$. All source galaxies
 are at redshift $z_{\rm S} = 1$. The non-linear 3D matter power spectrum from
-\cite{2012ApJ...761..152T} is used. The ratio of the first-and second- Limber
-approximated power spectra to the full projection shows excellent agreement at
-the sub-percent level.
+\cite{2012ApJ...761..152T} is used. The ratio of the first-and second-order
+Limber approximated power spectra to the full projection shows excellent
+agreement at the sub-percent level.
 
@@
 clustering, their calculations are general enough to apply to a weak-lensing
-context. Their Equation.~(5) is a spherical cross-power spectrum of two scalar
+context. Their Equation (5) is a spherical cross-power spectrum of two scalar
 fields $A$ and $B$, projected from 3D to 2D via projection kernels $F_A$ and
-$F_B$ defined in their Equation.~(4). Comparing their expressions with the
+$F_B$ defined in their Equation (4). Comparing their expressions with the
 weak-lensing potential (\ref{eq:psi}), we set $F_A(\chi) = F_B(\chi) = 2 c^{-2}
-D_+(\chi) q(\chi) \chi^{-1}$. With that, their Equations.~(5) is identical to
+D_+(\chi) q(\chi) \chi^{-1}$. With that, their Equation~(5) is identical to
 equation~(\ref{eq:C_ell_phi_Pphi}).
@@
 
-\cite{2008PhRvD..78d3002S} derive the lensing power spectrum in the
-flat-sky limit (see their Equation~(9)). Inserting the Poisson factor $D_\phi$, 
- the growth function $D_{\rm m}$, and writing the redshift filter
-function $W_\kappa$ (eq.~10) in terms of the lensing efficiency and comoving distances,
-$W_\kappa[z(\chi)] = H(z)^{-1} \chi q(\chi)$, their expression, using our notations, reads
+\cite{2008PhRvD..78d3002S} derive the lensing power spectrum in the flat-sky
+limit, see their Equation (9). Inserting the Poisson equation and the
+growth function, and writing the redshift filter function
+$W_\kappa$ (eq.~10) in terms of the lensing efficiency and comoving distances,
+$W_\kappa[z(\chi)] = H(z)^{-1} \chi q(\chi)$, their expression, using our
+notations, reads
 %
@@
 %
-This is consistent with our equation (\ref{eq:P_ell_gamma_full_der}) under the additional assumption that
-mainly modes with $k \chi \approx k \chi^\prime \approx \ell$ contribute to the integral; that is modes
-around the maxima of the Bessel functions. Then, we can draw out of the integral the factor $\ell^4 \approx k^4 \chi^2 {\chi^\prime}^2$,
-to recover equation~(\ref{eq:P_ell_gamma_full_der}).
-\mk{This argument is very hand-wavey! In fact, using the approximation $k \chi = \ell$ seems to go too far, this is already halfway the Limber approximation.}
+This is consistent with our equation (\ref{eq:P_ell_gamma_full_der}) under the
+additional assumption that mainly modes with $k \chi \approx k \chi^\prime
+\approx \ell$ contribute to the integral; that is modes around the maxima of
+the Bessel functions. Then, we can draw out of the integral the factor $\ell^4
+\approx k^4 \chi^2 {\chi^\prime}^2$, to recover
+equation~(\ref{eq:P_ell_gamma_full_der}). \mk{This argument is very hand-wavey!
+In fact, using the approximation $k \chi = \ell$ seems to go too far, this is
+already halfway the Limber approximation.}
 
@@
 \label{sec:giannantonio12}
-\cite{2012MNRAS.422.2854G} derive the flat-sky lensing
-power spectrum in their Equations.~(25) and (26) . Their window function $W^{\varepsilon_i}$ defined in their Equation~(25) for a
-flat Universe equals $\pref q(\chi) / a(\chi)$, since ${\rm d} z \,
-({\rm d} N(z)/{\rm d} z) = {\rm d} \chi n(\chi)$; however due to a typo there
-is a factor $r_K[r(z)]$ missing in the window function, which translates into a
-missing $r_K[r] r_K[r^\prime]$ in the full projection integral\footnote{Typo
-confirmed by T.~G., priv.~comm.}. This also leads to an errorous $r_K^{-2}(r)$
-in the Limber equation (27). With these factors accounted for, and making the
-additional approximation $k \chi \approx k \chi^\prime \ell$ (see their
-Appendix~\ref{sec:schmidt08}) we reproduce the expressions of
-\cite{2012MNRAS.422.2854G}.
+
+\cite{2012MNRAS.422.2854G} derive the flat-sky lensing power spectrum in their
+Equations (25) and (26). Their window function $W^{\varepsilon_i}$ defined in
+their Equation (25) for a flat Universe equals $\pref q(\chi) / a(\chi)$, since
+${\rm d} z \, ({\rm d} N(z)/{\rm d} z) = {\rm d} \chi n(\chi)$; however due to
+a typo there is a factor $r_K[r(z)]$ missing in the window function, which
+translates into a missing $r_K[r] r_K[r^\prime]$ in the full projection
+integral\footnote{Typo confirmed by T.~G., priv.~comm.}. This also leads to an
+errorous $r_K^{-2}(r)$ in their Limber equation (27). With these factors
+accounted for, and making the additional approximation $k \chi \approx k
+\chi^\prime \approx \ell$ (see their Appendix~\ref{sec:schmidt08}) we reproduce
+the expressions of \cite{2012MNRAS.422.2854G}.
 

### 2017-02-13 authors.tex
changed author order

@@
 Patrick Simon$^6$,
+Ludovic Van Waerbeke$^8$,
 Joachim Harnois-D\'eraps$^3$,
+\newauthor
 Hendrik Hildebrandt$^6$,
-\newauthor
 Fabian K\"ohlinger$^7$,
-Konrad Kuijken$^7$,
-Ludovic Van Waerbeke$^8$ and
+Konrad Kuijken$^7$, and
 Massimo Viola$^7$

### 2017-02-14 limber2.tex
small changes sec 2

@@
 
+\newcommand{\MA}[1]{\textcolor{red}{#1}}
+
 \definecolor{purple}{RGB}{76, 0,153}
+%\definecolor{purple}{RGB}{76, 0,153}
 \newcommand{\ch}[1]{\textcolor{purple}{\textbf{#1}}}
@@
 
-The lensing potential $\psi$ at a direction on the sky $(\theta, \varphi)$ in
+The lensing potential $\psi$ at a direction (\MA {position}?) on the sky $(\theta, \varphi)$ in
 the Born approximation is defined as the projected 3D metric potential $\Phi$
@@
 corresponding to a population of lensed galaxies with a normalised source
-redshift distribution $n_z(z) {\rm d}z = n(\chi) {\rm d} \chi$, \mk{with limit the
-comoving distance to the horizon $\chi_{\rm h}$.} Here, ${\rm c}$ is the speed
-of light, and the projection is carried out over comoving distances $\chi$
+redshift distribution $n_z(z) {\rm d}z = n(\chi) {\rm d} \chi$, \MA{with  $\chi_{\rm h}$,
+the comoving distance to the horizon.} Here, ${\rm c}$ is the speed
+of light, and the projection is carried out over comoving distances $\chi$.
 %, and $f_K(\chi) = |K|^{-1/2} S_K(|K|^{1/2} \chi)$ is the comoving angular
@@
 where $\Omega_{\rm m}$ is the matter density parameter, $H_0$ the Hubble
-constant, $\vec k$ a 3D Fourier wave vector \mk{with modulus $k$ being the comoving
+constant, $\vec k$ a 3D Fourier wave vector, \mk{with $|\vec k|$ being the comoving
 wave number}, and $a$ the scale factor with $a=1$ today. The Fourier transform
@@
 potential (equation~\ref{eq:psi}) into spherical harmonics, in analogy
-to the CMB
+to the \MA{cosmic microwave background (CMB)}
 temperature, both of which are scalar functions on the sphere. This
@@
 differential operator on the sphere is called \emph{edth} derivative, $\edth$,
-see \cite{2005PhRvD..72b3516C} for a in-depth mathematical discussion of this
+see \cite{2005PhRvD..72b3516C} for an in-depth mathematical discussion of this
 concept. The edth operator $\edth$ ($\edth^\ast$) raises (lowers) the spin $s$

### 2017-02-14 limber2.tex
small changes sec 3

@@
 The majority of cosmic shear analyses have used \mk{the predicted} lensing
-power spectrum approximated on a flat sky, neglecting the sky curvature. This
+power spectrum approximated on a flat-sky, neglecting the sky curvature. This
 is a valid approach for past and current survey areas with an extent less than
@@
 
-For a flat sky, the spherical harmonic expansions are approximated by Fourier
+For a flat-sky, the spherical harmonic expansions are approximated by Fourier
 transforms. The flat-sky equivalent of equations~(\ref{eq:psi_harm_exp}) and
@@
 expansion (equation~\ref{eq:psi_harm_exp}) can be approximated by the Fourier
-representation in equation~\ref{eq:psi_fourier}). They also demonstrated that the power
+representation in equation~(\ref{eq:psi_fourier}). They also demonstrated that the power
 spectra are approximately equal, $P^\psi \approx C^\psi$.
@@
 but I don't know whether this is an assumption to derive this approximation, or whether it follows from that.
-I'll have to check this.}
+I'll have to check this.}\MA{I am pretty sure that flat means large $\ell$, as the sky is flatter for smaller angular scales.}
 We find for the flat-sky shear power
@@
 expansion for general projections from 3D to 2D scalar fields in the spherical,
-all-sky case. \mk{We apply ther general derivation to the case of weak lensing,
+all-sky case. \mk{We apply their general derivation to the case of weak lensing,
 and contrary to \cite{2008PhRvD..78l3506L} account for a time-dependent power
@@
 %
-in equation~(\ref{eq:C_ell_full}), where ${\rm J}_\ell$ is the first-kind Bessel
-function of order $\ell$. Next, \cite{2008PhRvD..78l3506L} solve integrals of
+in equation~(\ref{eq:C_ell_full}), \MA {where ${\rm J}_\ell$ is the Bessel function of the first kind
+and order $\ell$}. Next, \cite{2008PhRvD..78l3506L} solve integrals of
 the form
@@
 
-\subsection{Flat sky}
+\subsection{Flat-sky}
 \label{sec:Limber_flat_sky}

### 2017-02-14 cfhtlens.tex
Added delta figure for Ludo's data; worked on TODO's

@@
 
+\mk{We also find that the cosmological constraints from tomographic KiDS are robust
+to the flat-sky and Limber approximations. The case ExtL1FlHyb that was used
+for KiDS data in \citep{KiDS-450} and \cite{joudaki/etal:2017} introduces
+errors that are more than an order of magnitude lower than the cosmic variance
+for that survey, and thus this approximation has negligible effect on
+cosmological parameters.}
+
 \renewcommand{\baselinestretch}{1.5}

### 2017-02-14 conclusions.tex
Added delta figure for Ludo's data; worked on TODO's

@@
 a pedagogical review of the impact of adopting flat-sky and Limber
-approximations.  We demonstrate that for current surveys, such as CFHTLenS,
+approximations.  We demonstrate that for current surveys, such as CFHTLenS \mk{and KiDS},
 these approximations have a negligible impact on cosmological parameter

### 2017-02-14 limber2.tex
Added delta figure for Ludo's data; worked on TODO's

--- 2017-02-13 limber2.tex
@@
 large-scale surveys with unprecedented precision, we show that the spherical
-second-order Limber approximation will provide sufficient accuracy, as it is in
-agreement with the full projection at the sub-percent level for $\ell > 3$,
-\mk{and the corresponding errors an order of magnitude below cosmic
-variance for all $\ell$.}
+second-order Limber approximation will provide sufficient accuracy. \mk{The
+cosmic-shear power spectrum} is in agreement with the full projection at the
+sub-percent level for $\ell > 3$, and the corresponding errors an order of
+magnitude below cosmic variance for all $\ell$. \mk{The shear two-point
+correlation function is accurate well below up to a few hundred arc minutes.
+Using the fast Hankel transformation, formally defined only in flat
+coordinates, to compute the two-point function from the power spectrum results
+in errors below two percent compared to the spherical Legendre transformation.}
 %
@@
 modifications to gravity.  As such it is the primary science goal of several
-current (KiDS, DES, HSC\footnote{KiDS: \href={http://kids.strw.leidenuniv.nl}, DES: \href={http://www.darkenergysurvey.org}, HSC: \href={http://hsc.mtk.nao.ac.jp/ssp/}})
-and future (Euclid, LSST, WFIRST\footnote{Euclid: \href={http://sci.esa.int/euclid}, LSST: \href={http://www.lsst.org}, WFIRST: \href={http://wfirst.gsfc.nasa.gov}}) surveys.
+current (KiDS, DES, HSC\footnote{KiDS: \href={http://kids.strw.leidenuniv.nl},
+DES: \href={http://www.darkenergysurvey.org}, HSC:
+\href={http://hsc.mtk.nao.ac.jp/ssp}}) and future (Euclid, LSST,
+WFIRST\footnote{Euclid: \href={http://sci.esa.int/euclid}, LSST:
+\href={http://www.lsst.org}, WFIRST: \href={http://wfirst.gsfc.nasa.gov}})
+surveys.
 %(Kilo-Degree Survey, KiDS \citet{kuijken/etal:2015}, Dark Energy Survey, DES, \citet{abbott/etal:2016}, Hyper-Suprime Camera Survey, HSC\footnote{HSC; \href={http://hsc.mtk.nao.ac.jp/ssp/}}) and future (Euclid, \citet{2011arXiv1110.3193L}, LSST, \citet{chang/etal:2013}, WFIRST\footnote{WFIRST; \href={http://wfirst.gsfc.nasa.gov}}) large-scale surveys.
@@
 We consider spherical coordinates and the flat-sky approximation, and compute
-the full projection. \mk{The first-order extended Limber approximation provides
+the full projection. The first-order extended Limber approximation provides
 sub-percent accuracy for $\ell > 10$ and is sufficient for present surveys. The
-associated errors are sub-dominant even for future large surveys.}
-
-We \mk{further} show that the second-order Limber approximation is an
+associated errors are sub-dominant even for future large surveys.
+
+We further show that the second-order Limber approximation is an
 accurate representation of the full projection, with better than percent level
@@
 from \citet{2000PhRvD..62d3007H}, see also \citet{2005PhRvD..72b3516C}. In
-section~\ref{sec:L2} we derive weak lensing observables using a second-order
+section~\ref{sec:L2} we derive weak-lensing observables using a second-order
 Limber approximation first introduced by \citet{2008PhRvD..78l3506L}. We
-compare the shear power spectrum and commonly-used two-point shear correlation
-function for the full solution to a range of different approximations in
-section~\ref{sec:results}, providing cosmological constraints for each case
-using CFHTLenS data from \citet{CFHTLenS-2pt-notomo}. This paper draws from
-several sources of literature which have previously discussed the full
-projection, or reviewed the accuracy of the Limber approximation for weak
+compare the shear power spectrum and the commonly-used two-point shear
+correlation function for the full solution to a range of different
+approximations in section~\ref{sec:results}, providing cosmological constraints
+for each case using CFHTLenS data from \citet{CFHTLenS-2pt-notomo}. This paper
+draws from several sources of literature which have previously discussed the
+full projection, or reviewed the accuracy of the Limber approximation for weak
 lensing studies, namely \citet{2008PhRvD..78d3002S,2012PhRvD..86b3001B,
@@
 the Born approximation is defined as the projected 3D metric potential $\Phi$
-along the line of sight \mk{of a flat Universe} \citep{1998ApJ...498...26K,BS01},
+along the line of sight of a flat Universe \citep{1998ApJ...498...26K,BS01},
 %
@@
 corresponding to a population of lensed galaxies with a normalised source
-redshift distribution $n_z(z) {\rm d}z = n(\chi) {\rm d} \chi$, \mk{with limit the
-comoving distance to the horizon $\chi_{\rm h}$.} Here, ${\rm c}$ is the speed
+redshift distribution $n_z(z) {\rm d}z = n(\chi) {\rm d} \chi$, with limit the
+comoving distance to the horizon $\chi_{\rm h}$. Here, ${\rm c}$ is the speed
 of light, and the projection is carried out over comoving distances $\chi$
@@
 % negative, respectively.
-\mk{The last argument of the potential $\Phi$ is not to
+The last argument of the potential $\Phi$ is not to
 be understood as coordinate, but rather as a substitute of cosmic time,
@@
 true in the following for all fields and functions thereof that dynamically
-change with cosmic epoch.}
+change with cosmic epoch.
 
@@
 where $\Omega_{\rm m}$ is the matter density parameter, $H_0$ the Hubble
-constant, $\vec k$ a 3D Fourier wave vector \mk{with modulus $k$ being the comoving
-wave number}, and $a$ the scale factor with $a=1$ today. The Fourier transform
+constant, $\vec k$ a 3D Fourier wave vector with modulus $k$ being the comoving
+wave number, and $a$ the scale factor with $a=1$ today. The Fourier transform
 of the potential and its inverse are defined as
@@
 %
-\mk{Complex conjugation is denoted with the superscript $^\ast$.}
+Complex conjugation is denoted with the superscript $^\ast$.
 To specify tomographic redshift bins $i=0\ldots N_z-1$, we introduce a family
@@
   C_{ij}^\psi(\ell) = & \frac 8 {c^4 \pi} 
-  \int_0^{\chi_{\rm lim}} \frac{{\rm d}\chi}{\chi} q_i(\chi)
-  \int_0^{\chi^\prime_{\rm lim}} \frac{{\rm d}\chi^\prime}{\chi^\prime} q_j(\chi^\prime)
+  \int_0^\infty \frac{{\rm d}\chi}{\chi} q_i(\chi)
+  \int_0^\infty \frac{{\rm d}\chi^\prime}{\chi^\prime} q_j(\chi^\prime)
   \int {\rm d} k k^2 \, {\rm j}_\ell(k \chi) {\rm j}_\ell(k \chi^\prime) P_\Phi(k; \chi, \chi^\prime)
@@
   = & \frac 8 \pi \pref^2
-  \int_0^{\chi_{\rm lim}} \frac{{\rm d}\chi}{\chi} \frac{q_i(\chi)}{a(\chi)}
-  \int_0^{\chi^\prime_{\rm lim}} \frac{{\rm d}\chi^\prime}{\chi^\prime} \frac{q_j(\chi^\prime)}{a(\chi^\prime)}
+  \int_0^\infty \frac{{\rm d}\chi}{\chi} \frac{q_i(\chi)}{a(\chi)}
+  \int_0^\infty \frac{{\rm d}\chi^\prime}{\chi^\prime} \frac{q_j(\chi^\prime)}{a(\chi^\prime)}
   \int \frac{{\rm d} k}{k^2} \, {\rm j}_\ell(k \chi) {\rm j}_\ell(k \chi^\prime) P_{\rm m}(k; \chi, \chi^\prime) ;
@@
 %
-and is
-related to $P_\Phi$ via the absolute square of the Poisson equation (\ref{eq:poisson}).
-
-\mk{Peter's comment: What does the correlation between two
-epochs actually mean if they are not on the backward light cone?}
+and is related to $P_\Phi$ via the absolute square of the Poisson equation
+(\ref{eq:poisson}).
+
+\mk{This type of cross-power spectrum between different cosmological epochs
+$\chi$ and $\chi^\prime$ was introduced in \cite{2005PhRvD..72b3516C}. In
+Sects.~\ref{sec:geom_mean} and \ref{sec:factor_D} this unequal-time
+cross-spectrum \cite{2016arXiv161200770K} will be further evaluated and
+simplified in the context of the Limber approximation. The oscillating Bessel
+functions  in (\ref{eq:C_ell_phi_Pm}) ensure that only relatively close epochs
+contribute to the lensing potential correlation. This make sense since observed
+light rays from two galaxies at different positions on the sky that necessarily
+converge at the observer today, pick up the density fluctuations at similar
+times while propagating through the large-scale structure. A similar argument
+has been made in \cite{BS01}: since the matter power spectrum scales with $k$
+for $k \rightarrow 0$, there is decreasing power towards larger and larger
+scales. In particular, the correlation of cosmic fields decreases strongly
+above a coherence scale $|\chi - \chi^\prime| \le L_{\rm coh}$ which is much
+smaller than the horizon scale. }
 
@@
 %
-\mk{for $0 \le s \le \ell$,} with the spin pre-factor \citep{2012PhRvD..86b3001B}
+for $0 \le s \le \ell$, with the spin pre-factor \citep{2012PhRvD..86b3001B}
 %
@@
                  = & \frac 2 \pi \, \ellbar^2(\ell, 2) \, \pref^2
-                 \int_{0}^{\chi_{\rm lim}} \frac{\rm d \chi}{\chi} \frac{q_i(\chi)}{a(\chi)}
-                \int_{0}^{\chi_{\rm lim}} \frac{\rm d \chi^\prime}{\chi^\prime}
+                 \int_{0}^\infty \frac{\rm d \chi}{\chi} \frac{q_i(\chi)}{a(\chi)}
+                \int_{0}^\infty \frac{\rm d \chi^\prime}{\chi^\prime}
                 \frac{q_j(\chi^\prime)}{a(\chi^\prime)}
@@
 where we use the label `FullSph', see Table \ref{tab:cases} for a list of cases discussed in this work.
-The spherical \mk{spin} pre-factor for the full projection \mk{shear} power
+The spherical spin pre-factor for the full projection shear power
 spectrum is $\ellbar^2(\ell, 2)$, which will be modified under
@@
 
-The majority of cosmic shear analyses have used \mk{the predicted} lensing
+The majority of cosmic shear analyses have used the predicted lensing
 power spectrum approximated on a flat sky, neglecting the sky curvature. This
 is a valid approach for past and current survey areas with an extent less than
-10 degrees. \mk{To account for the sky curvature of the observed data}, the
-shear correlation functions \mk{from observed galaxy ellipticities is now
-routinely} computed using spherical coordinates, \mk{since projecting to a
+10 degrees. To account for the sky curvature of the observed data, the
+shear correlation functions from observed galaxy ellipticities is now
+routinely computed using spherical coordinates, since projecting to a
 Cartesian plane has been shown to cause significant biases of the two-point
-funtion on large scales \citep{FSHK08}}. Here we examine the effect of sky
-curvature on the theoretical \mk{models of the power spectrum, and the effect
-on cosmological parameter inference (see Sect.~\ref{sec:cfhtlens}).}
+funtion on large scales \citep{FSHK08}. Here we examine the effect of sky
+curvature on the theoretical models of the power spectrum, and the effect
+on cosmological parameter inference (see Sect.~\ref{sec:cfhtlens}).
 
@@
 %
-The spin pre-factor $\sqrt{(\ell-1) \ell (\ell+1) (\ell+2)}$ is replaced by
-$\ell^2$ in flat co-ordinates, \mk{an approximation that holds for large $\ell$.}
+The spin pre-factor $\ellbar(\ell, 2) = \sqrt{(\ell-1) \ell (\ell+1) (\ell+2)}$ is replaced by
+$\ell^2$ in flat co-ordinates, an approximation that holds for large $\ell$.
  \ch{@MK - say why this is so.  Is it just that
@@
                  = & \frac 2 \pi \, \ell^4 \, \pref^2
-                 \int_{0}^{\chi_{\rm lim}} \frac{\rm d \chi}{\chi} \frac{q_i(\chi)}{a(\chi)}
-                \int_{0}^{\chi_{\rm lim}} \frac{\rm d \chi^\prime}{\chi^\prime}
+                 \int_{0}^\infty \frac{\rm d \chi}{\chi} \frac{q_i(\chi)}{a(\chi)}
+                \int_{0}^\infty \frac{\rm d \chi^\prime}{\chi^\prime}
                 \frac{q_j(\chi^\prime)}{a(\chi^\prime)}
@@
 expansion for general projections from 3D to 2D scalar fields in the spherical,
-all-sky case. \mk{We apply ther general derivation to the case of weak lensing,
+all-sky case. We apply ther general derivation to the case of weak lensing,
 and contrary to \cite{2008PhRvD..78l3506L} account for a time-dependent power
 spectrum using two approaches presented in Sects.~\ref{sec:geom_mean} and
-\ref{sec:factor_D}.}
+\ref{sec:factor_D}.
 
@@
 %
-by performing a Taylor expansion of \mk{an arbitrary differentialble} function
+by performing a Taylor expansion of an arbitrary differentialble function
 $f$ around $x = k \chi = \nu = \ell + 1/2$, where the Bessel function has its
@@
 %
-\mk{TODO: expand more on this. Explain why there is a non-zero correlation across epochs.}
+\mk{This form is justified when considering the linear power spectrum, and
+follows when inserting the linearly evolving density contrast $\hat \delta(\vec
+k; \chi) = D_+(\chi) \hat \delta_0(\vec k)$ into (\ref{eq:p_m}), whhere
+$\delta_0$ is the present-day linearly extrapolated density contrast, and $D_+$
+the linear growth factor with $D_+(0) = 1$. This is a very good approximation
+also in the non-linear case as shown in \cite{2016arXiv161200770K}.}
+
 With this, equation~(\ref{eq:C_ell_full}) is written as
@@
 with $g(x) = k^{-1} f(k, \chi)$, $\chi=x/k$, and its derivatives $g^{(n)}(x) =
-k^{-1-n} f^{(n)}(k, \chi)$ for a given $k$, \mk{where the derivatives of $f$
-are with respect to the second argument $\chi$.} \mk{This series expansion, the
+k^{-1-n} f^{(n)}(k, \chi)$ for a given $k$, where the derivatives of $f$
+are with respect to the second argument $\chi$. \mk{This series expansion, the
 replacement of the integral with the evaluation of $g$ and its derivatives at
@@
 %
-\mk{In the tomographic case, the index $i$ is added to $q$ and $f$.}
+In the tomographic case, the index $i$ is added to $q$ and $f$.
 %
@@
 %\subsubsection{Time-independent power spectrum separation}
-\subsubsection{\mk{Facoring out the growth factor}}
+\subsubsection{Facoring out the growth factor}
 \label{sec:factor_D}
@@
 %
-\mk{
 \begin{equation}
@@
 \end{equation}
-}
-%
-\mk{The function $\tilde P_{\rm m}$ is in general not time-independent, except
+%
+The function $\tilde P_{\rm m}$ is in general not time-independent, except
 in the case of a linear matter power spectrum in the absence of massive
@@
 mean redshift should be further examined, but this is not the case for
-CFHTLenS.}
-
-\mk{With the definition (\ref{eq:P_k_chi_sep_s}), we factor out the function
-$\tilde P_{\rm m}(k, \chi)$} from equation~(\ref{eq:f_LA08}), and we define the
+CFHTLenS.
+
+\mk{TODO: Make this clearer.}
+
+With the definition (\ref{eq:P_k_chi_sep_s}), we factor out the function
+$\tilde P_{\rm m}(k, \chi)$ from equation~(\ref{eq:f_LA08}), and we define the
 separated kernel function $f_{\rm s}$ as
@@
 %
-Further approximations are \mk{can} made for the pre-factor $p(\ell) = \ell^4/\nu^4(\ell)$ and $\nu(\ell)$:
+Further approximations are can made for the pre-factor $p(\ell) = \ell^4/\nu^4(\ell)$ and $\nu(\ell)$:
 %
@@
   %
-  \item $p(\ell) = 1$, \mk{but} keeping as argument of the power spectrum $\nu(\ell) = \ell + 1/2$. This is
+  \item $p(\ell) = 1$, but keeping as argument of the power spectrum $\nu(\ell) = \ell + 1/2$. This is
     a \emph{hybrid} between
@@
     was used in \cite{KiDS-450,joudaki/etal:2016}. As is shown
-    later, this is a better approximation to the full projection than case (ii). \mk{In (\ref{eq:P_ell_limber2})
+    later, this is a better approximation to the full projection than case (ii). In (\ref{eq:P_ell_limber2})
     the second-order suppression factor is also left to be $\nu^{-2}(\ell) = (\ell + 1/2)^{-2}$, providing
-    a slightly more accurate approximation compared to $\nu^{-2}(\ell) = \ell^{-2}$.}
+    a slightly more accurate approximation compared to $\nu^{-2}(\ell) = \ell^{-2}$.
 \end{enumerate}
@@
 > 3$.  The numerical calculation of the second-order extended Limber
-approximation is a factor of \mk{15 times} faster than the calculation of the
-full spherical solution \mk{(averaged over the first $18$ $\ell$-modes).} We
-note that the \mk{sub-$0.1\%$}-noise seen in the right panel of
+approximation is a factor of 15 times faster than the calculation of the
+full spherical solution (averaged over the first $18$ $\ell$-modes). We
+note that the sub-$0.1\%$-noise seen in the right panel of
 Fig.~\ref{fig:Cl_cases} is due to numerical noise arising from numerical
@@
 
-\mk{Compared to the statistical power of current and future surveys, all
+Compared to the statistical power of current and future surveys, all
 approximations discussed here are subdominant to the cosmic variance, $\Delta
@@
 ExtL2Sph is an order of magnitude below the cosmic variance of a Euclid-like
-survey (sky area $15,000$ square degrees) for all $\ell$.}
+survey (sky area $15,000$ square degrees) for all $\ell$.
 
@@
         resulting from each approximation, 
-        relative to the full spherical projection of the shear power spectrum. \mk{The two light grey curves on the
+        relative to the full spherical projection of the shear power spectrum. The two light grey curves on the
         top show the cosmic variance for KiDS- and Euclid-like surveys with areas of $1,500$ and $15,000$
-        square degrees, respectively.}
+        square degrees, respectively.
         }
@@
 \begin{centering}
-  \caption{\label{tab:cases}The shear power spectrum approximations studied in this paper. 'ID' is the \mk{label} used in the \mk{text and} figures.
+  %
+  \caption{\label{tab:cases}The shear power spectrum approximations studied in this paper. 'ID' is the label
+    used in the text and figures.
     The third column shows the power-spectrum pre-factor $p(\ell)$. } 
+    %
     \begin{tabular}{|l|l|c|c|c|p{0.21\textwidth}}
@@
 
-On a sphere, correlation functions \mk{formally} cannot be related to the power
-spectrum by the Hankel transform in equation~(\ref{eqn:xiGG}), \mk{and should
-be replaced by a Legendre transform}. The spherical power spectrum is formally
-not defined for non-integer $\ell$ \citep[see][for alternative spherical-sky
-formulae for the two-point correlation function]{2005PhRvD..72b3516C}, \mk{as
-functions defined on the sphere are necessarily periodic}. \sout{In particular,
-the spherical Bessel functions necessary to compute the full projection in
-equation~(\ref{eq:C_ell_full}) is defined only for integer order $\ell$.}
-%\mk{I think this is actually not true, since J$_\nu$ can be computed
-%for fractional $\nu$, and then one could use the identity (\ref{eq:jJ}). Or is
-%it?}.
+On a sphere, correlation functions formally cannot be related to the power
+spectrum by the Hankel transform in equation~(\ref{eqn:xiGG}), and should
+be replaced by a Legendre transform,
+%
+\mk{
+\begin{equation}
+ \xi_+(\theta) = \frac 1{4\pi} \sum\limits_{\ell=2}^\infty (2 \ell + 1) C^\gamma(\ell) {\rm P}_\ell[\cos(\theta)],
+  \label{eq:xi_Legendre}
+\end{equation}
+%
+where ${\rm P}_\ell(x)$ are the Legendre polynomials in $x$ of order $\ell$.}
+
+The spherical power spectrum is formally not defined for non-integer $\ell$
+\citep[see][for alternative spherical-sky formulae for the two-point
+correlation function]{2005PhRvD..72b3516C}, as functions defined on the
+sphere are necessarily periodic.
 
@@
 of the full spherical projection for $\ell > 3$.
-%In the Limber approximations
-%the Bessel functions \mk{of order $\nu$ are expanded into} polynomials \mk{in
-%$\nu$}, allowing for arbitrary wave modes $\ell$.
 The spherical pre-factor $\ellbar(\ell, 2)$ (equation~\ref{eq:ellbar}) can be
 generalised to non-integer arguments and is positive for $\ell \ge 2$. We can
-thus use the spherical power spectrum in the Limber approximations for the
-Hankel transformation to compute the two-point correlation functions. \mk{This
-has the advantage of very fast numerical implementations of the Hankel
-tranforms using FFTs \citep{fftlog}, which can be used in
-Monte-Carlo sampling.}
+thus use the spherical power spectrum \sout{in the Limber approximations} in
+the Hankel transformation (\ref{eqn:xiGG}) to compute the two-point correlation
+functions. This has the advantage of very fast numerical implementations of
+the Hankel tranforms using FFTs \citep{fftlog}, which can be used in
+Monte-Carlo sampling.
 
@@
 approximation, ExtL2Sph. Note that for the `FullSph' case we replace the full
-projection with ExtL2Sph for $\ell > 200$ to save computation time. We see no
-qualitative differences between the three cases.} \mk{[Note: The differences in
-the actual figure probably come from the difference n $\ell_{\rm max}$, to be
-updated.]}
-
-%We therefore do not present predictions for the
-%two-point shear correlation function using the full spherical projection,
-%instead choosing the spherical second-order extended Limber approximation
-%(ExtL2Sph) as our reference in this case. \mk{Todo: Include Ludo's spherical
-%calcuations of $\xi_\pm$.}
-
-Figure.~\ref{fig:xi_pm} presents the Hankel-transform two-point correlation
+projection with ExtL2Sph for $\ell > 200$ to save computation time.
+%
+2he Hankel transform (\ref{eqn:xiGG}) is accurate at the $1$ percent level.
+%
+The difference between second-order Limber and full projection using the
+spherical Legendre transform (\ref{eq:xi_Legendre}) is well below one percent
+for all but the very large scales.}
+
+\mk{The green curve in Fig.~\ref{fig:xi_p_legendre} presents the limit of
+precision we can achieve with the current fast Hankel transform implementation
+for the correlation function. The blue points shows the limit of the
+second-order Limber approximation on the correlation function.}
+
+Figure~\ref{fig:xi_pm} shows the Hankel-transform two-point correlation
 functions $\xi_+$ (left) and $\xi_-$ (right) using the different cases for the
-shear power spectrum listed in Table~\ref{tab:cases}. \mk{We use `ExtL2Sph' as reference case.}
-The adopted CFHTLenS
-redshift distribution and fiducial cosmological model are the same as in
-Figure.~\ref{fig:Cl_cases}. As is clear by the red dotted curve, using the
-Planck cosmology \citep{2015arXiv150201589P} induces a significant change in
-the amplitude of the shear correlation function in comparison to the different
-projection methods.
+shear power spectrum listed in Table~\ref{tab:cases}. \mk{We use `ExtL2Sph' as
+reference case.} The adopted CFHTLenS redshift distribution and fiducial
+cosmological model are the same as in Figure~\ref{fig:Cl_cases}. As is clear by
+the red dotted curve, using the Planck cosmology \citep{2015arXiv150201589P}
+induces a significant change in the amplitude of the shear correlation function
+in comparison to the different projection methods.
 
@@
   \begin{center}
-    \resizebox{0.5\hsize}{!}{
+    \resizebox{1.0\hsize}{!}{
       \includegraphics{figures/xi_p_legendre}
+      \hspace*{2em}
+      \includegraphics{figures/xi_p_legendre_delta}
     }
@@
 
-  \caption{The shear correlation function component $\xi_+$ for the ExtL2Sph
-projection using the Hankel transform (green line), compared to the spherical
-Legendre transform of the same projection (blue squares), and the FullSph
-projection (red circles).}
+  \caption{\emph{Left panel:} The shear correlation function component $\xi_+$
+for the ExtL2Sph projection using the Hankel transform (green line), compared
+to the spherical Legendre transform of the same projection (blue squares), and
+the FullSph projection (red circles). \emph{Left panel:} The relative
+difference with respect to the full spherical case (FullSph with Legendre
+transformation) of ExtL2Sph with Hankel transform (green line), and ExtL2Sph
+with Legendre transform (blue squares).}
 
@@
   \psi_{\ell m} = \frac 2 {c^2} \int {\rm d} \Omega {\rm Y}^\ast_{\ell m}(\theta, \varphi)
-    \int_0^{\chi_{\rm lim}} \frac{{\rm d}\chi}{\chi} q(\chi) \int \frac{{\rm d}^3 k}{(2\pi)^3} \hat \Phi(\vec k; \chi) {\rm e}^{-{\rm i} \vec k \cdot \vec r}.
+    \int_0^\infty \frac{{\rm d}\chi}{\chi} q(\chi) \int \frac{{\rm d}^3 k}{(2\pi)^3} \hat \Phi(\vec k; \chi) {\rm e}^{-{\rm i} \vec k \cdot \vec r}.
 \end{equation}
@@
 \begin{equation}
-  \psi_{\ell m} = \frac {{\rm i}^\ell}{c^2 \pi^2} \int_0^{\chi_{\rm lim}} \frac{{\rm d}\chi}{\chi} q(\chi) \int {\rm d}^3 k \,
+  \psi_{\ell m} = \frac {{\rm i}^\ell}{c^2 \pi^2} \int_0^\infty \frac{{\rm d}\chi}{\chi} q(\chi) \int {\rm d}^3 k \,
     \hat \Phi(\vec k; \chi) {\rm j}_\ell(k \chi) {\rm Y}_{\ell m}(\theta_k, \varphi_k).
@@
 %
-\mk{To obtain the potential power spectrum,} we take the absolute square of the
+To obtain the potential power spectrum, we take the absolute square of the
 last equation and use the definition of the 3D potential power spectrum
@@
 and for a bin function that selects the redshift bin of $z$, $W^{\rm SR}(z,
-z_{\rm p})$ \mk{is unity if $z_{\rm p}$ is in the redshift bin denoted by $z$,
-and zero otherwise.} We find that Equation (7) in \cite{2016arXiv161104954K} is
+z_{\rm p})$ is unity if $z_{\rm p}$ is in the redshift bin denoted by $z$,
+and zero otherwise. We find that Equation (7) in \cite{2016arXiv161104954K} is
 missing a factor $2/\pi$.
@@
 times, see Equation~(6.22) in \cite{vande2012}, where the transition is
-calculated using $g(a)$ instead of $D(a)$. \mk{Check this further.}
+calculated using $g(a)$ instead of $D(a)$. \mk{TODO: Check this further.}
 
@@
     at a single source plane at $z_{\rm S}=1$, with the cosmological parameters (see text) are chosen to match
-    \citet{vande2012}, see their Figure.~7.3 for comparison.
+    \citet{vande2012}, see their Figure~7.3 for comparison.
     }
@@
   P_{ij}^\gamma(\ell) = & \frac 2 \pi \, \pref^2
-                 \int_{0}^{\chi_{\rm lim}} {\rm d} \chi \chi \, \frac{q_i(\chi)}{a(\chi)}
-                \int_{0}^{\chi_{\rm lim}} {\rm d} \chi^\prime\, \chi^\prime
+                 \int_{0}^\infty {\rm d} \chi \chi \, \frac{q_i(\chi)}{a(\chi)}
+                \int_{0}^\infty {\rm d} \chi^\prime\, \chi^\prime
                 \frac{q_j(\chi^\prime)}{a(\chi^\prime)}

### 2017-02-14 limber2.tex

@@
 corresponding to a population of lensed galaxies with a normalised source
-redshift distribution $n_z(z) {\rm d}z = n(\chi) {\rm d} \chi$, with limit the
+redshift distribution $n_z(z) {\rm d}z = n(\chi) {\rm d} \chi$, with the limit being the
 comoving distance to the horizon $\chi_{\rm h}$. Here, ${\rm c}$ is the speed
@@
 
-The majority of cosmic shear analyses have used the predicted lensing
-power spectrum approximated on a flat sky, neglecting the sky curvature. This
-is a valid approach for past and current survey areas with an extent less than
-10 degrees. To account for the sky curvature of the observed data, the
-shear correlation functions from observed galaxy ellipticities is now
-routinely computed using spherical coordinates, since projecting to a
-Cartesian plane has been shown to cause significant biases of the two-point
-funtion on large scales \citep{FSHK08}. Here we examine the effect of sky
-curvature on the theoretical models of the power spectrum, and the effect
-on cosmological parameter inference (see Sect.~\ref{sec:cfhtlens}).
-
-For a flat sky, the spherical harmonic expansions are approximated by Fourier
+The majority of cosmic shear analyses have used the predicted lensing power
+spectrum approximated on a flat sky, neglecting the sky curvature. This is a
+valid approach for past and current survey areas with an extent less than 10
+degrees. To account for the sky curvature of the observed data, the shear
+correlation functions from observed galaxy ellipticities is now routinely
+computed using spherical coordinates, since projecting to a Cartesian plane has
+been shown to cause significant biases of the two-point funtion on large scales
+\citep{FSHK08}. Here we examine the effect of sky curvature on the theoretical
+models of the power spectrum, and the effect on cosmological parameter
+inference (see Sect.~\ref{sec:cfhtlens}).
+
+For a flat-sky, the spherical harmonic expansions are approximated by Fourier
 transforms. The flat-sky equivalent of equations~(\ref{eq:psi_harm_exp}) and
@@
 expansion for general projections from 3D to 2D scalar fields in the spherical,
-all-sky case. We apply ther general derivation to the case of weak lensing,
+all-sky case. We apply their general derivation to the case of weak lensing,
 and contrary to \cite{2008PhRvD..78l3506L} account for a time-dependent power

### 2017-02-14 limber2.tex
Added footnote

@@
 corresponding to a population of lensed galaxies with a normalised source
-redshift distribution $n_z(z) {\rm d}z = n(\chi) {\rm d} \chi$, with the limit being the
-comoving distance to the horizon $\chi_{\rm h}$. Here, ${\rm c}$ is the speed
-of light, and the projection is carried out over comoving distances $\chi$
+redshift distribution $n_z(z) {\rm d}z = n(\chi) {\rm d} \chi$, with the limit
+being the comoving distance to the horizon $\chi_{\rm h}$\footnote{\mk{In
+(\ref{eq:psi}) we have replaced this limit without loss of generality by
+$\infty$, since $q(\chi > \chi_{\rm h}) = 0$.}}. Here, ${\rm c}$ is the speed of
+light, and the projection is carried out over comoving distances $\chi$
 %, and $f_K(\chi) = |K|^{-1/2} S_K(|K|^{1/2} \chi)$ is the comoving angular

### 2017-02-14 limber2.tex
Included Ludo's Legendre trafos for all spherical xi_+ cases; figures changed

@@
 magnitude below cosmic variance for all $\ell$. \mk{The shear two-point
-correlation function is accurate well below up to a few hundred arc minutes.
-Using the fast Hankel transformation, formally defined only in flat
+correlation function is accurate well below one percent up to a few hundred arc
+minutes. Using the fast Hankel transformation, formally defined only in flat
 coordinates, to compute the two-point function from the power spectrum results
@@
 %
+\mk{Note that the argument $\ell$ is a discrete integer variable, and is often written as index, $C_\ell$.}
 Using the properties of the spherical harmonics (see
@@
 been shown to cause significant biases of the two-point funtion on large scales
-\citep{FSHK08}. Here we examine the effect of sky curvature on the theoretical
-models of the power spectrum, and the effect on cosmological parameter
-inference (see Sect.~\ref{sec:cfhtlens}).
+\citep{FSHK08}, \mk{and lead to spurious B-modes \cite{asgari/etal:2017}}. Here
+we examine the effect of sky curvature on the theoretical models of the power
+spectrum, and the effect on cosmological parameter inference (see
+Sect.~\ref{sec:cfhtlens}).
 
@@
 
-Figure~\ref{fig:xi_pm} shows the Hankel-transform two-point correlation
-functions $\xi_+$ (left) and $\xi_-$ (right) using the different cases for the
-shear power spectrum listed in Table~\ref{tab:cases}. \mk{We use `ExtL2Sph' as
-reference case.} The adopted CFHTLenS redshift distribution and fiducial
-cosmological model are the same as in Figure~\ref{fig:Cl_cases}. As is clear by
-the red dotted curve, using the Planck cosmology \citep{2015arXiv150201589P}
-induces a significant change in the amplitude of the shear correlation function
-in comparison to the different projection methods.
+Figure~\ref{fig:xi_pm} shows the two-point correlation functions $\xi_+$ (left)
+and $\xi_-$ (right) using the different cases for the shear power spectrum
+listed in Table~\ref{tab:cases}. \mk{The component $\xi_+$ is calculated with
+the appropriate transformation, i.e.~Hankel for the flat cases, and Legendre
+for the spherical ones.} \mk{For $\xi_-$ which is much less dominated by large
+scales and thus Limber and flat-sky approximations than $\xi_+$, we use the
+Hankel transofm in all cases. In addition, for $\xi_-$ the approximation
+`ExtL2Sph' is our reference case.} The adopted CFHTLenS redshift distribution
+and fiducial cosmological model are the same as in Figure~\ref{fig:Cl_cases}.
+As is clear by the red dotted curve, using the Planck cosmology
+\citep{2015arXiv150201589P} induces a significant change in the amplitude of
+the shear correlation function in comparison to the different projection
+methods.
 
@@
 
-  \caption{The two-point shear correlation functions $\xi_+$ (\emph{left}) and $\xi_-$ (\emph{right}).  The upper panels
+  \caption{The two-point shear correlation functions $\xi_+$ (\emph{left}) and $\xi_-$ (\emph{right}).
+  \mk{In the spherical cases (ExtL1Sph, ExtL2Sph, FullSph), $\xi_+$ has been computed using the Legendre
+  transform (\ref{eq:xi_Legendre}). For the flat cases, and all instances of $\xi_-$, the Hankel transform
+  (\ref{eqn:xiGG}) was used.}
+  The upper panels
   show the total shear correlation functions for the range of cases listed in Table~\ref{tab:cases}.

### 2017-02-14 limber2.tex
Plots updated

@@
   \caption{\emph{Left panel:} The shear correlation function component $\xi_+$
-for the ExtL2Sph projection using the Hankel transform (green line), compared
-to the spherical Legendre transform of the same projection (blue squares), and
-the FullSph projection (red circles). \emph{Left panel:} The relative
+for the ExtL2Sph projection using the spherical Legendre transform (green line for ExtL2Sph, grey squares for FullSph),
+compared to the flat-sky Hankel transform of ExtL2Sph (red circles).
+\emph{Left panel:} The relative
 difference with respect to the full spherical case (FullSph with Legendre
-transformation) of ExtL2Sph with Hankel transform (green line), and ExtL2Sph
-with Legendre transform (blue squares).}
+transformation) of ExtL2Sph with Legendre (green line), 
+and Hankel transform (red circles).}
 

### 2017-02-15 conclusions.tex
Peter's comments IV

--- 2017-02-10 conclusions.tex
@@
 a pedagogical review of the impact of adopting flat-sky and Limber
-approximations.  We demonstrate that for current surveys, such as CFHTLenS,
-these approximations have a negligible impact on cosmological parameter
-constraints.
+approximations.  We demonstrate that for current surveys, such as CFHTLenS
+\mk{and KiDS}, these approximations have a negligible impact on cosmological
+parameter constraints.
 
@@
 
-\mk{TODO: comment on non-flat models.}
+\mk{ We have considered a flat Universe throughout this paper. To generalise
+the calculations to non-flat models, one needs to modify the comoving angular
+diameter distance to account for the spatial curvature $K \ne 0$. In addition,
+the spherical Bessel functions are replaced with hyperspherical Bessel
+functions \citep{1986ApJ...308..546A}. In a universe with positive curvature
+$K>0$ the 3D wave modes become discrete integer variables. For non-flat models,
+we do however not expect qualitative differences from our results.}

### 2017-02-15 limber2.tex
Peter's comments IV

@@
 \newcommand{\mk}[1]{{\bf\textcolor{blue}{#1}}}
-\newcommand{\Label}[1]{\quad \mk{(\mbox{#1})}}
-\newcommand{\LabelTxt}[1]{\mk{(\mbox{#1})}}
+\newcommand{\Label}[1]{\quad (\mbox{#1})}
+\newcommand{\LabelTxt}[1]{(\mbox{#1})}
 
@@
 $\infty$, since $q(\chi > \chi_{\rm h}) = 0$.}}. Here, ${\rm c}$ is the speed of
-light, and the projection is carried out over comoving distances $\chi$
+light, and the projection is carried out over comoving distances $\chi$.
 %, and $f_K(\chi) = |K|^{-1/2} S_K(|K|^{1/2} \chi)$ is the comoving angular
@@
 Complex conjugation is denoted with the superscript $^\ast$.
-To specify tomographic redshift bins $i=0\ldots N_z-1$, we introduce a family
+To specify tomographic redshift bins $i=1\ldots N_z$, we introduce a family
 of lensing efficiency functions $q_i$ defined by a corresponding family of
@@
 The second-order Limber term in equation~(\ref{eq:C_ell_limber12_dr}) has an additional
-$\nu^{-2}$-dependence, and is therefore strongly suppressed for large $\ell$.
-%
-\begin{align}
-  C^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2(\ell)} \, \frac{\ellbar^2(\ell, 2)}{\nu^4(\ell)} \, \pref^2
-    \int {\rm d} \chi \, \chi^{2} a^{-2} P^{1/2}_{\rm m}\left(\frac{\nu(\ell)}\chi; \chi\right)
+$\nu^{-2}$-dependence, and is therefore strongly suppressed for large $\ell$,
+%
+\begin{align}
+  C^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2(\ell)} \, \frac{\ellbar^2(\ell, 2)}{\nu^4(\ell)} \,
+    \frac{\pref^2}{2}
+    \int {\rm d} \chi \, \chi^{7/2} a^{-1} P^{1/2}_{\rm m}\left(\frac{\nu(\ell)}\chi; \chi\right)
     %\nonumber \\
     %& \times
-    \frac{a(\chi)}{2} \chi^{3/2} \left[ q^{}_i f^{\prime\prime}_j + f^{\prime\prime}_i q^{}_j
+    \left[ q^{}_i f^{\prime\prime}_j + f^{\prime\prime}_i q^{}_j
       + \frac{\chi}{3} \left( q^{}_i f^{\prime\prime\prime}_j + f^{\prime\prime\prime}_i q^{}_j
@@
 sensitive to the set-up, for example the step size. The tabulation and
-interpolation of those derivatives is time-taking since they depend on two
+interpolation of those derivatives is time-consuming since they depend on two
 arguments, $\nu$ and $\chi$. In the following section, we will separate the
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsubsection{Time-independent power spectrum separation}
-\subsubsection{Facoring out the growth factor}
+\subsubsection{\mk{Approximation for small $\ell$}}
 \label{sec:factor_D}
@@
 
-\mk{TODO: Make this clearer.}
+%\mk{TODO: Make this clearer.}
 
@@
 \begin{align}
-  C^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2(\ell)} \, \frac{\ellbar^2(\ell, 2)}{\nu^4(\ell)} \, \pref^2
-    \int {\rm d} \chi \, \chi^{2} a^{-2} P_{\rm m}\left(\frac{\nu(\ell)}\chi; \chi\right)
+  C^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2(\ell)} \, \frac{\ellbar^2(\ell, 2)}{\nu^4(\ell)} \,
+    \frac{\pref^2}{2}
+    \int {\rm d} \chi \, \chi^{7/2} a^{-1}(\chi) D_+^{-1}(\chi) P_{\rm m}\left(\frac{\nu(\ell)}\chi; \chi\right)
     %\nonumber \\
     %& \times
-    \frac {a(\chi)}{2 D_+(\chi)} \chi^{3/2}
     \left[ q^{}_i f^{\prime\prime}_{{\rm s} j} + f^{\prime\prime}_{{\rm s}i} q^{}_j
@@
 We compute the numerical higher derivatives as follows. The functions $f_{\rm
-s}(\chi)$ are fitted as power laws with index $\approx 1.5$. The fit is
-performed between $\chi_{\rm min} = 0.001 {\rm Mpc}/h$ and $\chi_{\rm max} =
-500 \mbox{Mpc}/h$. At larger comoving distances the kernel decreases faster
-than a power law, so we exclude this range from the fit. Even though the
-derivaties are larger due to the steeper decline, the associated errors are
-very small as these scales are down-weighed by the kernel function $f_{\rm
-s}$ itself. At $\chi = 500 \, \mbox{Mpc}/h$ the filter function is less than
-$10^{-4}$ of its value of unity at $1$\,Mpc$/h$.
+s}(\chi)$ are fitted as power laws with index $\approx \mk{-1.5}$, \mk{which
+follows since the growth suppression factor $D_+(a)/a$ varies slowly with
+$\chi$, and the lensing efficiency $q ~ 1$ for small and medium $\chi$ given
+the CFHTLenS redshift range.} The fit is performed between $\chi_{\rm min} =
+0.001 {\rm Mpc}/h$ and $\chi_{\rm max} = 500 \mbox{Mpc}/h$. At larger comoving
+distances the kernel decreases faster than a power law, so we exclude this
+range from the fit. Even though the derivaties are larger due to the steeper
+decline, the associated errors are very small as these scales are down-weighed
+by the kernel function $f_{\rm s}$ itself. At $\chi = 500 \, \mbox{Mpc}/h$ the
+filter function is less than $10^{-4}$ of its value of unity at $1$\,Mpc$/h$.
 
@@
   \\
-    P^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2(\ell)} \, p(\ell) \, \pref^2
-    \int {\rm d} \chi \, \chi^{2} a^{-2} P_{\rm m}\left(\frac{\nu(\ell)}\chi; \chi\right)
+    P^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2(\ell)} \, p(\ell) \, \frac{\pref^2}{2}
+    \int {\rm d} \chi \, \chi^{7/2} a^{-1}(\chi) D_+^{-1}(\chi) P_{\rm m}\left(\frac{\nu(\ell)}\chi; \chi\right)
     %\nonumber \\
     %& \times
-    \frac{a(\chi)}{2 D_+(\chi)} \chi^{3/2} \left[ q^{}_i f^{\prime\prime}_{{\rm s}j} + f^{\prime\prime}_{{\rm s}i} q^{}_j  
+    \left[ q^{}_i f^{\prime\prime}_{{\rm s}j} + f^{\prime\prime}_{{\rm s}i} q^{}_j  
       + \frac{\chi}{3} \left( q^{}_i f^{\prime\prime\prime}_{{\rm s}j} + f^{\prime\prime\prime}_{{\rm s}i} q^{}_j
@@
 %
-Further approximations are can made for the pre-factor $p(\ell) = \ell^4/\nu^4(\ell)$ and $\nu(\ell)$:
+Further approximations can be made for the pre-factor $p(\ell) = \ell^4/\nu^4(\ell)$ and $\nu(\ell)$:
 %
@@
     Until recently, i.e.~for all pre-2014 CFHTLenS results, this was the approximation of choice.
-    Note that we do not discuss the non-extended second-order Limber approximation here.
+    Note that we do not discuss the second-order Limber approximation \mk{with this $p$} here.
   %
@@
 C(\ell) / C(\ell) = [f_{\rm sky} (2 \ell + 1)]^{-1/2}$
-\citep{1992ApJ...388..272K}, where $f_{\rm sky}$ is the faction of sky observed
+\citep{1992ApJ...388..272K}, where $f_{\rm sky}$ is the fraction of sky observed
 by the survey. The uncertainties from the Limber approximation in the case of
@@
 times, see Equation~(6.22) in \cite{vande2012}, where the transition is
-calculated using $g(a)$ instead of $D(a)$. \mk{TODO: Check this further.}
+calculated using $g(a)$ instead of $D(a)$.
+%\mk{TODO: Check this further.}
 

### 2017-02-15 cfhtlens.tex
Peter's comments IV
Read through it once, made minor changes

@@
 function $\xi_\pm(\theta)$ from \cite{CFHTLenS-2pt-notomo}, defined in
-equation~(\ref{eqn:xiGG}). As in \cite{CFHTLenS-2pt-notomo} we fit both components
-$\xi_+$ and $\xi_-$ between angular scales $\theta = 0.8$ and $350$ arc
-minutes, and use a $N$-body simulation estimate of the non-Gaussian covariance
-including the cross-covariance between both components. The Bayesian
-Monte-Carlo parameter sampling is performed using the publicly available
-software \textsc{CosmoPMC}\footnote{\texttt{http://www.cosmostat.org/software/cosmopmc}}
+equation~(\ref{eqn:xiGG}). As in \cite{CFHTLenS-2pt-notomo} we fit both
+components $\xi_+$ and $\xi_-$ between angular scales $\theta = 0.8$ and $350$
+arc minutes, and use a $N$-body simulation estimate of the non-Gaussian
+covariance including the cross-covariance between both components. Bayesian
+Population Monte-Carlo parameter sampling is performed using the publicly
+available software
+\textsc{CosmoPMC}\footnote{\texttt{http://www.cosmostat.org/software/cosmopmc}}
 \citep{WK09,KWR10}. The cosmological modelling part includes the various
@@
 result that was published in \cite{CFHTLenS-2pt-notomo}. Using the second-order
-extended Limber flat-sky hybrid approximation (ExtL2FlHyb) results in
-$\sigma_8 (\Omega_{\rm m}/0.27)^{0.6} = 0.788 \pm 0.032$, a negligible
-change of the amplitude that is well within the Monte-Carlo sampling noise.
+extended Limber flat-sky hybrid approximation (ExtL2FlHyb) results in $\sigma_8
+(\Omega_{\rm m}/0.27)^{0.6} = 0.788 \pm 0.032$, a negligible change of the
+amplitude that is well within the Monte-Carlo sampling noise. \mk{The largest
+difference is measured with the depreciated case ExtL1Fl, for which the
+recovered amplitude is larger by $16\%$ of the statistical error.} \mk{These
+negligible changes relative to the error bars were to be expected owing to the
+much larger cosmic variance, compared to the differences in the various
+approximations shown in Fig.~\ref{fig:Cl_cases}, which has been taken into
+account in the calculation of the uncertainty.}
 
 Table \ref{tab:CFHTLenS_Sigma8} lists the mean and 68\% credible interval for
-$\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$ for the various approximations to the
+$\sigma_8 \Omega_{\rm m}^{0.6}$ for the various approximations to the
 lensing power spectrum projections listed in Table~\ref{tab:cases} Note again
@@
   \caption{\label{tab:CFHTLenS_Sigma8}Mean and 68\% confidence interval for 
-  $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$ for various approximations to the lensing
+  $\sigma_8 (\Omega_{\rm m}/0.27)^{0.6}$ and $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$
+  for various approximations to the lensing
   power spectrum projections listed in Table~\ref{tab:cases}.}

### 2017-02-15 limber2.tex
Added TODO file
Read through it once, made minor changes

@@
 
+% symbol on top of another
+\newcommand{\ontop}[2]{
+  \renewcommand{\arraystretch}{0.2}
+  \begin{array}{c}
+  #1 \\ #2
+  \end{array}
+  \renewcommand{\arraystretch}{1.0}
+}
+% lesser similar, <~
+\newcommand{\lsim}{\ontop{<}{\sim}}
+% greater similar >~
+\newcommand{\gsim}{\ontop{>}{\sim}}
+
 \title[Precision calculations of the cosmic shear projection]{Precision calculations of the cosmic shear power spectrum
@@
 We compute the spherical-sky weak-lensing power spectrum of the shear and
-convergence. We discuss various approximations, such as flat-sky, first- and
+convergence. We discuss various approximations, such as flat-sky, and first- and
 second-order Limber equations for the projection. We find that the impact of
@@
 
+\mk{We also compute the shear correlation function using a spherical Legendre
+transformation, and compare this to the flat-sky approximated, commonly used
+fast Hankel transformation.}
+
 This paper is organised as follows.  In section~\ref{sec:wl} we provide a
@@
 
-The lensing potential $\psi$ at a direction (\MA {position}?) on the sky $(\theta, \varphi)$ in
+The lensing potential $\psi$ at a position on the sky $(\theta, \varphi)$ in
 the Born approximation is defined as the projected 3D metric potential $\Phi$
@@
 being the comoving distance to the horizon $\chi_{\rm h}$\footnote{\mk{In
-(\ref{eq:psi}) we have replaced this limit without loss of generality by
+(\ref{eq:psi}) we have replaced this limit without loss of generality with
 $\infty$, since $q(\chi > \chi_{\rm h}) = 0$.}}. Here, ${\rm c}$ is the speed of
@@
 weak-lensing quantities due to clustering of source galaxies with other sources
-\citep{2002A&A...389..729S}, and with galaxies associated with lens structures
+\citep{2002A&A...389..729S}, and with galaxies associated to lens structures
 \citep{1998A&A...338..375B,H02}.
@@
 potential (equation~\ref{eq:psi}) into spherical harmonics, in analogy
-to the \MA{cosmic microwave background (CMB)}
+to the cosmic microwave background (CMB)
 temperature, both of which are scalar functions on the sphere. This
@@
 Sects.~\ref{sec:geom_mean} and \ref{sec:factor_D} this unequal-time
-cross-spectrum \cite{2016arXiv161200770K} will be further evaluated and
+cross-spectrum \citep{2016arXiv161200770K} will be further evaluated and
 simplified in the context of the Limber approximation. The oscillating Bessel
@@
 scales. In particular, the correlation of cosmic fields decreases strongly
-above a coherence scale $|\chi - \chi^\prime| \le L_{\rm coh}$ which is much
-smaller than the horizon scale. }
+above a coherence scale $|\chi - \chi^\prime| \gsim L_{\rm coh}$ which is much
+smaller than the horizon scale $\chi_{\rm h}$. }
 
 In the following section we will discuss the relations between shear and
-convergence to the lensing potential, on the sphere, and derive the power
+convergence to the lensing potential on the sphere, and derive the power
 spectrum of the former two fields.
@@
 \begin{align}
-  \gamma(\theta, \varphi) = & \frac 1 2 \edth \edth \psi(\theta, \varphi).
+  \gamma(\theta, \varphi) = & \frac 1 2 \edth \edth \psi(\theta, \varphi);
     \nonumber \\
@@
 Instead of a harmonics coefficients $\psi_{\ell m}$, the Fourier representation of the potential
-$\hat \psi$ now depends on the vector $\vec \ell \in R^2$.
+$\hat \psi$ now depends on the vector $\vec \ell \in \mathbb{R}^2$.
 
@@
 %
-The spin pre-factor $\ellbar(\ell, 2) = \sqrt{(\ell-1) \ell (\ell+1) (\ell+2)}$ is replaced by
-$\ell^2$ in flat co-ordinates, an approximation that holds for large $\ell$.
- \ch{@MK - say why this is so.  Is it just that
-flat by definition means large $\ell$?} \mk{I think it's a large-ell approximation,
-but I don't know whether this is an assumption to derive this approximation, or whether it follows from that.
-I'll have to check this.}\MA{I am pretty sure that flat means large $\ell$, as the sky is flatter for smaller angular scales.}
-We find for the flat-sky shear power
-spectrum
+The spin pre-factor $\ellbar(\ell, 2) = \sqrt{(\ell-1) \ell (\ell+1) (\ell+2)}$
+is replaced by $\ell^2$ in flat co-ordinates, an approximation that holds for
+large $\ell$, \mk{since sky curvature can be neglected for small angular
+scales.} We find for the flat-sky shear power spectrum
 %
@@
 %
-in equation~(\ref{eq:C_ell_full}), \MA {where ${\rm J}_\ell$ is the Bessel function of the first kind
-and order $\ell$}. Next, \cite{2008PhRvD..78l3506L} solve integrals of
+in equation~(\ref{eq:C_ell_full}), where ${\rm J}_\nu$ is the Bessel function of the first kind
+and order $\nu$. Next, \cite{2008PhRvD..78l3506L} solve integrals of
 the form
@@
 the maximum of the Bessel function is a good approximation of the integral if
-$g$ is varying more slowly than the oscillating Bessel function [Check this].
+$g$ is varying more slowly than the oscillating Bessel function.
+% [Check this].
 As we will see below, $f$ is a slowly varying function of the comoving
@@
 weak gravitational lensing. We retrieve the (spherical) standard expression by
-inserting back the projection kernel equation~(\ref{eq:f_LA08}) and the time-dependent
-power spectrum,
+inserting back the projection kernel (equation~\ref{eq:f_LA08}),
 %
@@
 
-%\mk{TODO: Make this clearer.}
-
 With the definition (\ref{eq:P_k_chi_sep_s}), we factor out the function
@@
 %
-The second-order Limber term of the shear power spectrum can then be approximated as
-%
-\begin{align}
-  C^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2(\ell)} \, \frac{\ellbar^2(\ell, 2)}{\nu^4(\ell)} \,
+The \mk{Limber equation up to second order} of the shear power spectrum can then be approximated as
+%
+\begin{align}
+  C^\gamma_{ij}(\ell) = & \, C^\gamma_{{\rm L1}, ij}(\ell) 
+    \nonumber \\
+    & - \frac 1 {\nu^2(\ell)} \, \frac{\ellbar^2(\ell, 2)}{\nu^4(\ell)} \,
     \frac{\pref^2}{2}
@@
 We compute the numerical higher derivatives as follows. The functions $f_{\rm
-s}(\chi)$ are fitted as power laws with index $\approx \mk{-1.5}$, \mk{which
-follows since the growth suppression factor $D_+(a)/a$ varies slowly with
-$\chi$, and the lensing efficiency $q ~ 1$ for small and medium $\chi$ given
-the CFHTLenS redshift range.} The fit is performed between $\chi_{\rm min} =
-0.001 {\rm Mpc}/h$ and $\chi_{\rm max} = 500 \mbox{Mpc}/h$. At larger comoving
+s}(\chi)$ are fitted as power laws with index $\approx \mk{-1.5}$, \mk{which is
+expected if the growth suppression factor $D_+(a)/a$ varies slowly with $\chi$,
+and the lensing efficiency $q \approx 1$ for small and medium $\chi$ given the
+CFHTLenS redshift range.} The fit is performed between $\chi_{\rm min} = 0.001
+\, {\rm Mpc}/h$ and $\chi_{\rm max} = 500 \, \mbox{Mpc}/h$. At larger comoving
 distances the kernel decreases faster than a power law, so we exclude this
-range from the fit. Even though the derivaties are larger due to the steeper
-decline, the associated errors are very small as these scales are down-weighed
-by the kernel function $f_{\rm s}$ itself. At $\chi = 500 \, \mbox{Mpc}/h$ the
-filter function is less than $10^{-4}$ of its value of unity at $1$\,Mpc$/h$.
+range from the fit. Even though on those scales the derivatives are larger due
+to the steeper decline, the associated errors are very small as these scales
+are down-weighed by the kernel function $f_{\rm s}$ itself. At $\chi = 500 \,
+\mbox{Mpc}/h$ the filter function is less than $10^{-4}$ of its value 
+at $1$\,Mpc$/h$.
 
@@
     a \emph{hybrid} between
-    standard and extended Limber approximation \Label{ExtL1FlHyb,ExtL2FlHyb}, and this case of first order
-    was used in \cite{KiDS-450,joudaki/etal:2016}. As is shown
-    later, this is a better approximation to the full projection than case (ii). In (\ref{eq:P_ell_limber2})
+    standard and extended Limber approximation \Label{ExtL1FlHyb,ExtL2FlHyb}, and the first-order case 
+    was used in \cite{KiDS-450,joudaki/etal:2016,joudaki/etal:2017}. As is shown
+    below, this is a better approximation to the full projection than case (ii). In (\ref{eq:P_ell_limber2})
     the second-order suppression factor is also left to be $\nu^{-2}(\ell) = (\ell + 1/2)^{-2}$, providing
@@
 approximation, (L1Fl), that was adopted for all pre-2014 CFHTLenS analyses, we
-find to be accurate to better than 10\% for $\ell>3$, converging slowly to the
+find \mk{it} to be accurate to better than 10\% for $\ell>3$, converging slowly to the
 true projection with percent level precison at $\ell>100$. For the extended
@@
 full spherical solution (averaged over the first $18$ $\ell$-modes). We
-note that the sub-$0.1\%$-noise seen in the right panel of
+note that the sub-$0.1\%$-\mk{fluctuations} seen in the right panel of
 Fig.~\ref{fig:Cl_cases} is due to numerical noise arising from numerical
@@
 sphere are necessarily periodic.
-
 As we have shown in section~\ref{sec:comp}, however, the spherical second-order
@@
 generalised to non-integer arguments and is positive for $\ell \ge 2$. We can
-thus use the spherical power spectrum \sout{in the Limber approximations} in
+thus use the spherical power spectrum \sout{in the Limber approximations} with
 the Hankel transformation (\ref{eqn:xiGG}) to compute the two-point correlation
@@
 %
-2he Hankel transform (\ref{eqn:xiGG}) is accurate at the $1$ percent level.
+The Hankel transform (\ref{eqn:xiGG}) is accurate at the $1$ percent level.
 %
@@
 
-\mk{The green curve in Fig.~\ref{fig:xi_p_legendre} presents the limit of
+\mk{The red circles in Fig.~\ref{fig:xi_p_legendre} present the limit of
 precision we can achieve with the current fast Hankel transform implementation
-for the correlation function. The blue points shows the limit of the
+for the correlation function. The green line shows the limit of the
 second-order Limber approximation on the correlation function.}
@@
 scales and thus Limber and flat-sky approximations than $\xi_+$, we use the
-Hankel transofm in all cases. In addition, for $\xi_-$ the approximation
+Hankel transform in all cases. In addition, for $\xi_-$ the approximation
 `ExtL2Sph' is our reference case.} The adopted CFHTLenS redshift distribution
@@
 
-\ch{Check your acknowledgements}
-
 \bibliographystyle{mnras}
@@
 calculated using $g(a)$ instead of $D(a)$.
-%\mk{TODO: Check this further.}
 

### 2017-02-16 cfhtlens.tex
very minor

@@
 to the flat-sky and Limber approximations. The case ExtL1FlHyb that was used
-for KiDS data in \citep{KiDS-450} and \cite{joudaki/etal:2017} introduces
+for KiDS data in \citet{KiDS-450} and \cite{joudaki/etal:2017} introduces
 errors that are more than an order of magnitude lower than the cosmic variance
-for that survey, and thus this approximation has negligible effect on
+for that survey, and thus this approximation has a negligible impact on the
 cosmological parameters.}

### 2017-02-16 limber2.tex
Made the abstract more concise

@@
 Background (CMB) temperature anisotropy results cannot be alleviated, in
-contrast to the recent claim made by \citet{2016arXiv161104954K}. For future
+contrast to the recent claim made by \citet{2016arXiv161104954K}.
+
+For future
 large-scale surveys with unprecedented precision, we show that the spherical
-second-order Limber approximation will provide sufficient accuracy. \mk{The
-cosmic-shear power spectrum} is in agreement with the full projection at the
-sub-percent level for $\ell > 3$, and the corresponding errors an order of
-magnitude below cosmic variance for all $\ell$. \mk{The shear two-point
-correlation function is accurate well below one percent up to a few hundred arc
-minutes. Using the fast Hankel transformation, formally defined only in flat
-coordinates, to compute the two-point function from the power spectrum results
-in errors below two percent compared to the spherical Legendre transformation.}
+second-order Limber approximation will provide sufficient accuracy. \ch{In this case, the
+cosmic-shear power spectrum is shown to be in agreement with the full projection at the
+sub-percent level for $\ell > 3$, with the corresponding errors an order of
+magnitude below cosmic variance for all $\ell$.
+%We show that the commonly used 
+%shear two-point correlation function is accurate well below one percent up to a few hundred arc
+%minutes when adopting. 
+%We find that when using the fast Hankel transformation, formally defined only in flat
+%%coordinates, to compute the commonly-used two-point function from the power spectrum results
+%in errors below two percent compared to the spherical Legendre transformation.}
+When computing the two-point shear correlation function, we show that the flat-sky fast Hankel 
+transformation results in errors below two percent compared to the full spherical Legendre transformation.}
 %

### 2017-02-16 limber2.tex
Added refs for DLS and DES-SV to add to Table 1 Some minor edits Anything more significant is in purple One TODO martin - add a ref for the Legendre equation

@@
 obtain precision constraints on cosmological parameters.
-
 \mk{We also compute the shear correlation function using a spherical Legendre
@@
 power spectra for the flat-sky and spherical cases, following the seminal work
-from \citet{2000PhRvD..62d3007H}, see also \citet{2005PhRvD..72b3516C}. In
+from \citet{2000PhRvD..62d3007H} \cite[see also][]{2005PhRvD..72b3516C}. In
 section~\ref{sec:L2} we derive weak-lensing observables using a second-order
@@
 simplified in the context of the Limber approximation. The oscillating Bessel
-functions  in (\ref{eq:C_ell_phi_Pm}) ensure that only relatively close epochs
+functions in equation~(\ref{eq:C_ell_phi_Pm}) ensure that only relatively close epochs
 contribute to the lensing potential correlation. This make sense since observed
@@
 scales. In particular, the correlation of cosmic fields decreases strongly
-above a coherence scale $|\chi - \chi^\prime| \gsim L_{\rm coh}$ which is much
+above a coherence scale $|\chi - \chi^\prime| \gsim L_{\rm coh}$ which is significantly
 smaller than the horizon scale $\chi_{\rm h}$. }
@@
 been shown to cause significant biases of the two-point funtion on large scales
-\citep{FSHK08}, \mk{and lead to spurious B-modes \cite{asgari/etal:2017}}. Here
+\citep{FSHK08}, \mk{and lead to spurious B-modes \citep{asgari/etal:2017}}. Here
 we examine the effect of sky curvature on the theoretical models of the power
@@
 follows when inserting the linearly evolving density contrast $\hat \delta(\vec
-k; \chi) = D_+(\chi) \hat \delta_0(\vec k)$ into (\ref{eq:p_m}), whhere
+k; \chi) = D_+(\chi) \hat \delta_0(\vec k)$ into equation~(\ref{eq:p_m}), where
 $\delta_0$ is the present-day linearly extrapolated density contrast, and $D_+$
-the linear growth factor with $D_+(0) = 1$. This is a very good approximation
+the linear growth factor with $D_+(0) = 1$. This is a good approximation
 also in the non-linear case as shown in \cite{2016arXiv161200770K}.}
@@
 k^{-1-n} f^{(n)}(k, \chi)$ for a given $k$, where the derivatives of $f$
-are with respect to the second argument $\chi$. \mk{This series expansion, the
+are with respect to the second argument $\chi$. \mk{In this series expansion, the
 replacement of the integral with the evaluation of $g$ and its derivatives at
@@
 % [Check this].
-As we will see below, $f$ is a slowly varying function of the comoving
+As we will show below, $f$ is a slowly varying function of the comoving
 distance.} In our case the projection kernel is
@@
 \begin{equation}
-  f_{\rm s}(\chi) = D_+(\chi) a^{-1}(\chi) \chi^{-3/2} q(\chi) \,
+  f_{\rm s}(\chi) = D_+(\chi) a^{-1}(\chi) \chi^{-3/2} q(\chi) \, .
   \label{eq:f_LA08_s}
@@
 expected if the growth suppression factor $D_+(a)/a$ varies slowly with $\chi$,
-and the lensing efficiency $q \approx 1$ for small and medium $\chi$ given the
-CFHTLenS redshift range.} The fit is performed between $\chi_{\rm min} = 0.001
+and the lensing efficiency $q \approx 1$ for small and medium $\chi$, given the
+CFHTLenS redshift range.} The fit is carried out between $\chi_{\rm min} = 0.001
 \, {\rm Mpc}/h$ and $\chi_{\rm max} = 500 \, \mbox{Mpc}/h$. At larger comoving
@@
 The extended flat-sky Limber approximation is readily derived from the
-spherical case (\ref{eq:C_ell_limber1}, \ref{eq:C_ell_limber2_dr_s}), by
+spherical case equations~(\ref{eq:C_ell_limber1}, \ref{eq:C_ell_limber2_dr_s}), by
 replacing the pre-factor $\ellbar^2(\ell, 2)$ with $\ell^4$,
@@
     \emph{standard} Limber approximation \LabelTxt{L1Fl}
-    Until recently, i.e.~for all pre-2014 CFHTLenS results, this was the approximation of choice.
-    Note that we do not discuss the second-order Limber approximation \mk{with this $p$} here.
+    Until recently, i.e.~for all pre-2014 CFHTLenS results, \ch{DES-SV \citep{abbott/etal:2016} and DLS \citep{jee/etal:2016} analyses, 
+    this was the approximation of choice.}
+    Note that we do not discuss the second-order Limber approximation \ch{with $p(\ell)=1$}.
   %
   \item $p(\ell) = \ell^4/(\ell + 1/2)^4$. This corresponds to the \emph{extended} Limber
-    approximation \LabelTxt{ExtL1Fl,ExtL2Fl} with $\nu(\ell) = \ell + 1/2$; however the following case is typically employed:
+    approximation \LabelTxt{ExtL1Fl, ExtL2Fl} with $\nu(\ell) = \ell + 1/2$; however the following case is typically employed:
   %
@@
     a \emph{hybrid} between
-    standard and extended Limber approximation \Label{ExtL1FlHyb,ExtL2FlHyb}, and the first-order case 
+    standard and extended Limber approximation~\LabelTxt{ExtL1FlHyb, ExtL2FlHyb}, and the first-order case 
     was used in \cite{KiDS-450,joudaki/etal:2016,joudaki/etal:2017}. As is shown
-    below, this is a better approximation to the full projection than case (ii). In (\ref{eq:P_ell_limber2})
+    below, this is a better approximation to the full projection than case (ii). In equation~(\ref{eq:P_ell_limber2})
     the second-order suppression factor is also left to be $\nu^{-2}(\ell) = (\ell + 1/2)^{-2}$, providing
@@
 Considering first the flat-sky cases, the standard first-order Limber
-approximation, (L1Fl), that was adopted for all pre-2014 CFHTLenS analyses, we
+approximation, (L1Fl), that was adopted for all pre-2014 CFHTLenS analyses, \ch{DES-SV and DLS analyses}, we
 find \mk{it} to be accurate to better than 10\% for $\ell>3$, converging slowly to the
@@
   $1^{\rm st}$-order standard Limber, flat sky & L1Fl & (\ref{eq:P_ell_limber1}) + (i)
-    & $1$ & $\ell$ & Used for pre-2014 CFHTLenS \\ \hline
+    & $1$ & $\ell$ & \ch{Pre-2014 CFHTLenS, DES-SV and DLS} \\ \hline
   %
@@
   $1^{\rm st}$-order extended Limber, hybrid, flat sky & ExtL1FlHyb & (\ref{eq:P_ell_limber1}) + (iii)
-    & $1$ & $\ell + \frac 1 2$ & Used for post-2014 CFHTLenS, KiDS \\ \hline
+    & $1$ & $\ell + \frac 1 2$ & \ch{Post-2014 CFHTLenS, KiDS} \\ \hline
   %
@@
 spectrum by the Hankel transform in equation~(\ref{eqn:xiGG}), and should
-be replaced by a Legendre transform,
+be replaced by a Legendre transform \ch{@MK - ADD A REF HERE},
 %
@@
 thus use the spherical power spectrum \sout{in the Limber approximations} with
-the Hankel transformation (\ref{eqn:xiGG}) to compute the two-point correlation
-functions. This has the advantage of very fast numerical implementations of
-the Hankel tranforms using FFTs \citep{fftlog}, which can be used in
-Monte-Carlo sampling.
+the Hankel transformation in equation~(\ref{eqn:xiGG}) to compute the two-point correlation
+functions. This has the advantage being able to use very fast numerical implementations of
+the Hankel tranforms using FFTs \citep{fftlog}, when Monte-Carlo sampling.
 
@@
 approximation, ExtL2Sph. Note that for the `FullSph' case we replace the full
-projection with ExtL2Sph for $\ell > 200$ to save computation time.
-%
-The Hankel transform (\ref{eqn:xiGG}) is accurate at the $1$ percent level.
+projection with ExtL2Sph for $\ell > 200$ to reduce computation time.}
+%
+\ch{We find that the Hankel transform (equation~\ref{eqn:xiGG}) is accurate to better than $2$ percent level.
 %
@@
 spherical Legendre transform (\ref{eq:xi_Legendre}) is well below one percent
-for all but the very large scales.}
-
+for $\vartheta < 200$ arcminutes.}
 \mk{The red circles in Fig.~\ref{fig:xi_p_legendre} present the limit of
-precision we can achieve with the current fast Hankel transform implementation
+precision that we can achieve with the current fast Hankel transform implementation
 for the correlation function. The green line shows the limit of the
@@
 the appropriate transformation, i.e.~Hankel for the flat cases, and Legendre
-for the spherical ones.} \mk{For $\xi_-$ which is much less dominated by large
-scales and thus Limber and flat-sky approximations than $\xi_+$, we use the
+for the spherical cases.} \mk{For $\xi_-$ which is less dominated by large
+scales and thus Limber and flat-sky approximations, in comparison to $\xi_+$, we use the
 Hankel transform in all cases. In addition, for $\xi_-$ the approximation
@@
   \mk{In the spherical cases (ExtL1Sph, ExtL2Sph, FullSph), $\xi_+$ has been computed using the Legendre
-  transform (\ref{eq:xi_Legendre}). For the flat cases, and all instances of $\xi_-$, the Hankel transform
-  (\ref{eqn:xiGG}) was used.}
+  transform (equation~\ref{eq:xi_Legendre}). For the flat cases, and all instances of $\xi_-$, the Hankel transform
+  in equation~(\ref{eqn:xiGG}) was used.}
   The upper panels

### 2017-02-16 cfhtlens.tex
Minor stuff I think this is ready to go!!

--- 2017-02-15 cfhtlens.tex
@@
 difference is measured with the depreciated case ExtL1Fl, for which the
-recovered amplitude is larger by $16\%$ of the statistical error.} \mk{These
-negligible changes relative to the error bars were to be expected owing to the
-much larger cosmic variance, compared to the differences in the various
-approximations shown in Fig.~\ref{fig:Cl_cases}, which has been taken into
-account in the calculation of the uncertainty.}
+recovered amplitude is larger by $16\%$ of the statistical error.} \ch{These
+negligible changes to the error bars were to be expected owing to the
+high level of statistical noise and cosmic variance in comparison to the low-level impact of the various
+approximations shown in Fig.~\ref{fig:Cl_cases}.}
 
@@
 
-\mk{We also find that the cosmological constraints from tomographic KiDS are robust
-to the flat-sky and Limber approximations. The case ExtL1FlHyb that was used
-for KiDS data in \citep{KiDS-450} and \cite{joudaki/etal:2017} introduces
+\ch{Considering the cosmological constraints from tomographic Kilo-Degree Survey (KiDS), we conclude that
+these are robust to flat-sky and Limber approximations. The case ExtL1FlHyb that was used
+for the analysis of KiDS data in \citet{KiDS-450} and \cite{joudaki/etal:2017} introduces
 errors that are more than an order of magnitude lower than the cosmic variance
-for that survey, and thus this approximation has negligible effect on
+for that survey, and thus this approximation has a negligible impact on the
 cosmological parameters.}

### 2017-02-16 limber2.tex
Minor stuff I think this is ready to go!!

@@
 Foundation, the ERC (grants 279396, 647112), the Seventh Framework Programme of
-the European Commission (Marie Sklodwoska Curie Fellowship grant 656869),
+the European Commission (Marie Sklodwoska Curie Fellowship grant 656869), the
+Netherlands Organisation for Scientific Research (NWO) (grants 614.001.103),
 NSERC, CIfAR, and the World Premier International Research Center Initiative
@@
 Research Council Centre of Excellence for All-sky Astrophysics (CAASTRO),
-through project number CE110001020. MV acknowledges support from the European
-Research Council under FP7 grant number 279396 and the Netherlands Organisation
-for Scientific Research (NWO) through grants 614.001.103.
+through project number CE110001020.
 

### 2017-02-16 cfhtlens.tex
MK: Replaced Legendre transform with spherical transform; added ref Peebles 73

@@
 (\Omega_{\rm m}/0.27)^{0.6} = 0.788 \pm 0.032$, a negligible change of the
-amplitude that is well within the Monte-Carlo sampling noise. \mk{The largest
+amplitude that is well within the Monte-Carlo sampling noise. The largest
 difference is measured with the depreciated case ExtL1Fl, for which the
-recovered amplitude is larger by $16\%$ of the statistical error.} \ch{These
+recovered amplitude is larger by $16\%$ of the statistical error. \ch{These
 negligible changes to the error bars were to be expected owing to the

### 2017-02-16 conclusions.tex
MK: Replaced Legendre transform with spherical transform; added ref Peebles 73

@@
 approximations.  We demonstrate that for current surveys, such as CFHTLenS
-\mk{and KiDS}, these approximations have a negligible impact on cosmological
+and KiDS, these approximations have a negligible impact on cosmological
 parameter constraints.
@@
 
-\mk{ We have considered a flat Universe throughout this paper. To generalise
+We have considered a flat Universe throughout this paper. To generalise
 the calculations to non-flat models, one needs to modify the comoving angular
@@
 $K>0$ the 3D wave modes become discrete integer variables. For non-flat models,
-we do however not expect qualitative differences from our results.}
+we do however not expect qualitative differences from our results.

### 2017-02-16 limber2.tex
MK: Replaced Legendre transform with spherical transform; added ref Peebles 73

@@
 magnitude below cosmic variance for all $\ell$.
-%We show that the commonly used 
-%shear two-point correlation function is accurate well below one percent up to a few hundred arc
-%minutes when adopting. 
-%We find that when using the fast Hankel transformation, formally defined only in flat
-%%coordinates, to compute the commonly-used two-point function from the power spectrum results
-%in errors below two percent compared to the spherical Legendre transformation.}
 When computing the two-point shear correlation function, we show that the flat-sky fast Hankel 
-transformation results in errors below two percent compared to the full spherical Legendre transformation.}
+transformation results in errors below two percent compared to the full spherical transformation.}
 %
@@
 obtain precision constraints on cosmological parameters.
-\mk{We also compute the shear correlation function using a spherical Legendre
+We also compute the shear correlation function using a spherical 
 transformation, and compare this to the flat-sky approximated, commonly used
-fast Hankel transformation.}
+fast Hankel transformation.
 
@@
 redshift distribution $n_z(z) {\rm d}z = n(\chi) {\rm d} \chi$, with the limit
-being the comoving distance to the horizon $\chi_{\rm h}$\footnote{\mk{In
+being the comoving distance to the horizon $\chi_{\rm h}$\footnote{In
 (\ref{eq:psi}) we have replaced this limit without loss of generality with
-$\infty$, since $q(\chi > \chi_{\rm h}) = 0$.}}. Here, ${\rm c}$ is the speed of
+$\infty$, since $q(\chi > \chi_{\rm h}) = 0$.}. Here, ${\rm c}$ is the speed of
 light, and the projection is carried out over comoving distances $\chi$.
@@
 %
-\mk{Note that the argument $\ell$ is a discrete integer variable, and is often written as index, $C_\ell$.}
+Note that the argument $\ell$ is a discrete integer variable, and is often written as index, $C_\ell$.
 Using the properties of the spherical harmonics (see
@@
 
-\mk{This type of cross-power spectrum between different cosmological epochs
+This type of cross-power spectrum between different cosmological epochs
 $\chi$ and $\chi^\prime$ was introduced in \cite{2005PhRvD..72b3516C}. In
@@
 above a coherence scale $|\chi - \chi^\prime| \gsim L_{\rm coh}$ which is significantly
-smaller than the horizon scale $\chi_{\rm h}$. }
+smaller than the horizon scale $\chi_{\rm h}$.
 
@@
 been shown to cause significant biases of the two-point funtion on large scales
-\citep{FSHK08}, \mk{and lead to spurious B-modes \citep{asgari/etal:2017}}. Here
+\citep{FSHK08}, and lead to spurious B-modes \citep{asgari/etal:2017}. Here
 we examine the effect of sky curvature on the theoretical models of the power
@@
 is replaced by $\ell^2$ in flat co-ordinates, an approximation that holds for
-large $\ell$, \mk{since sky curvature can be neglected for small angular
-scales.} We find for the flat-sky shear power spectrum
+large $\ell$, since sky curvature can be neglected for small angular
+scales. We find for the flat-sky shear power spectrum
 %
@@
 %
-\mk{This form is justified when considering the linear power spectrum, and
+This form is justified when considering the linear power spectrum, and
 follows when inserting the linearly evolving density contrast $\hat \delta(\vec
@@
 the linear growth factor with $D_+(0) = 1$. This is a good approximation
-also in the non-linear case as shown in \cite{2016arXiv161200770K}.}
+also in the non-linear case as shown in \cite{2016arXiv161200770K}.
 
@@
 k^{-1-n} f^{(n)}(k, \chi)$ for a given $k$, where the derivatives of $f$
-are with respect to the second argument $\chi$. \mk{In this series expansion, the
+are with respect to the second argument $\chi$. In this series expansion, the
 replacement of the integral with the evaluation of $g$ and its derivatives at
@@
 As we will show below, $f$ is a slowly varying function of the comoving
-distance.} In our case the projection kernel is
+distance. In our case the projection kernel is
 %
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{\mk{Approximation for small $\ell$}}
+\subsubsection{Approximation for small $\ell$}
 \label{sec:factor_D}
@@
 %
-The \mk{Limber equation up to second order} of the shear power spectrum can then be approximated as
+The Limber equation up to second order of the shear power spectrum can then be approximated as
 %
@@
 We compute the numerical higher derivatives as follows. The functions $f_{\rm
-s}(\chi)$ are fitted as power laws with index $\approx \mk{-1.5}$, \mk{which is
+s}(\chi)$ are fitted as power laws with index $\approx -1.5$, which is
 expected if the growth suppression factor $D_+(a)/a$ varies slowly with $\chi$,
 and the lensing efficiency $q \approx 1$ for small and medium $\chi$, given the
-CFHTLenS redshift range.} The fit is carried out between $\chi_{\rm min} = 0.001
+CFHTLenS redshift range. The fit is carried out between $\chi_{\rm min} = 0.001
 \, {\rm Mpc}/h$ and $\chi_{\rm max} = 500 \, \mbox{Mpc}/h$. At larger comoving
@@
 approximation, (L1Fl), that was adopted for all pre-2014 CFHTLenS analyses, \ch{DES-SV and DLS analyses}, we
-find \mk{it} to be accurate to better than 10\% for $\ell>3$, converging slowly to the
+find it to be accurate to better than 10\% for $\ell>3$, converging slowly to the
 true projection with percent level precison at $\ell>100$. For the extended
@@
 full spherical solution (averaged over the first $18$ $\ell$-modes). We
-note that the sub-$0.1\%$-\mk{fluctuations} seen in the right panel of
+note that the sub-$0.1\%$-fluctuations seen in the right panel of
 Fig.~\ref{fig:Cl_cases} is due to numerical noise arising from numerical
@@
 spectrum by the Hankel transform in equation~(\ref{eqn:xiGG}), and should
-be replaced by a Legendre transform \ch{@MK - ADD A REF HERE},
-%
-\mk{
-\begin{equation}
- \xi_+(\theta) = \frac 1{4\pi} \sum\limits_{\ell=2}^\infty (2 \ell + 1) C^\gamma(\ell) {\rm P}_\ell[\cos(\theta)],
+be replaced by the \mk{spherical} transform \citep{1973ApJ...185..413P}
+%
+\begin{equation}
+ \xi_+(\theta) = \mk{\left\langle \gamma \gamma^\ast \right\rangle(\theta)}
+  =  \frac 1{4\pi} \sum\limits_{\ell=2}^\infty (2 \ell + 1) C^\gamma(\ell) {\rm P}_\ell[\cos(\theta)],
   \label{eq:xi_Legendre}
@@
 %
-where ${\rm P}_\ell(x)$ are the Legendre polynomials in $x$ of order $\ell$.}
+where ${\rm P}_\ell(x)$ are the Legendre polynomials in $x$ of order $\ell$. \mk{This equation is easily derived
+using the harmonics expansion of the shear (\ref{eq:gamma_harm_exp}) and the orthogonality relation of
+the spherical harmonics (\ref{eq:Yellm_ortho}).}
 
@@
 
-\mk{We compare predictions for the two-point shear correlation function using
-the Hankel transformation and the full spherical Legendre transformation in
+We compare predictions for the two-point shear correlation function using
+the Hankel transformation and the full spherical transformation in
 Fig.~\ref{fig:xi_p_legendre}. We show the full projection and the best
 approximation, ExtL2Sph. Note that for the `FullSph' case we replace the full
-projection with ExtL2Sph for $\ell > 200$ to reduce computation time.}
+projection with ExtL2Sph for $\ell > 200$ to reduce computation time.
 %
@@
 The difference between second-order Limber and full projection using the
-spherical Legendre transform (\ref{eq:xi_Legendre}) is well below one percent
+spherical transform (\ref{eq:xi_Legendre}) is well below one percent
 for $\vartheta < 200$ arcminutes.}
-\mk{The red circles in Fig.~\ref{fig:xi_p_legendre} present the limit of
+The red circles in Fig.~\ref{fig:xi_p_legendre} present the limit of
 precision that we can achieve with the current fast Hankel transform implementation
 for the correlation function. The green line shows the limit of the
-second-order Limber approximation on the correlation function.}
+second-order Limber approximation on the correlation function.
 
@@
 and $\xi_-$ (right) using the different cases for the shear power spectrum
-listed in Table~\ref{tab:cases}. \mk{The component $\xi_+$ is calculated with
-the appropriate transformation, i.e.~Hankel for the flat cases, and Legendre
-for the spherical cases.} \mk{For $\xi_-$ which is less dominated by large
-scales and thus Limber and flat-sky approximations, in comparison to $\xi_+$, we use the
-Hankel transform in all cases. In addition, for $\xi_-$ the approximation
-`ExtL2Sph' is our reference case.} The adopted CFHTLenS redshift distribution
-and fiducial cosmological model are the same as in Figure~\ref{fig:Cl_cases}.
-As is clear by the red dotted curve, using the Planck cosmology
-\citep{2015arXiv150201589P} induces a significant change in the amplitude of
-the shear correlation function in comparison to the different projection
-methods.
+listed in Table~\ref{tab:cases}. The component $\xi_+$ is calculated with the
+appropriate transformation, i.e.~Hankel for the flat cases, and {spherical
+involving Legendre polynomials} for the spherical cases. For $\xi_-$ which is
+less dominated by large scales and thus Limber and flat-sky approximations, in
+comparison to $\xi_+$, we use the Hankel transform in all cases. In addition,
+for $\xi_-$ the approximation `ExtL2Sph' is our reference case. The adopted
+CFHTLenS redshift distribution and fiducial cosmological model are the same as
+in Figure~\ref{fig:Cl_cases}. As is clear by the red dotted curve, using the
+Planck cosmology \citep{2015arXiv150201589P} induces a significant change in
+the amplitude of the shear correlation function in comparison to the different
+projection methods.
 
@@
   \caption{\emph{Left panel:} The shear correlation function component $\xi_+$
-for the ExtL2Sph projection using the spherical Legendre transform (green line for ExtL2Sph, grey squares for FullSph),
+for the ExtL2Sph projection using the spherical transform (green line for ExtL2Sph, grey squares for FullSph),
 compared to the flat-sky Hankel transform of ExtL2Sph (red circles).
-\emph{Left panel:} The relative
-difference with respect to the full spherical case (FullSph with Legendre
-transformation) of ExtL2Sph with Legendre (green line), 
-and Hankel transform (red circles).}
+\emph{Right panel:} The relative
+difference \mk{compared to the full spherical case FullSph of ExtL2Sph with spherical transform
+(green line), 
+and Hankel transform (red circles).}}
 
@@
   \caption{The two-point shear correlation functions $\xi_+$ (\emph{left}) and $\xi_-$ (\emph{right}).
-  \mk{In the spherical cases (ExtL1Sph, ExtL2Sph, FullSph), $\xi_+$ has been computed using the Legendre
+  In the spherical cases (ExtL1Sph, ExtL2Sph, FullSph), $\xi_+$ has been computed using the spherical
   transform (equation~\ref{eq:xi_Legendre}). For the flat cases, and all instances of $\xi_-$, the Hankel transform
-  in equation~(\ref{eqn:xiGG}) was used.}
+  in equation~(\ref{eqn:xiGG}) was used.
   The upper panels
@@
 \approx k^4 \chi^2 {\chi^\prime}^2$, to recover
-equation~(\ref{eq:P_ell_gamma_full_der}). \mk{This argument is very hand-wavey!
+equation~(\ref{eq:P_ell_gamma_full_der}). This argument is very hand-wavey!
 In fact, using the approximation $k \chi = \ell$ seems to go too far, this is
-already halfway the Limber approximation.}
+already halfway the Limber approximation.
 

### 2017-02-16 authors.tex
Removed line about flat universe in appendix

@@
 $^7$Kavli Institute for the Physics and Mathematics of the Universe (WPI), The University of Tokyo Institutes for Advanced Study, \\
-The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
+\phantom{$^7$}The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
 $^8$Department of Physics and Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC V6T 1Z1, Canada\\

### 2017-02-16 cfhtlens.tex
Changes from Marika added
Removed line about flat universe in appendix

@@
 large scales. A complementary accurate estimate of the covariance matrix using
-analytical methods will be published soon (Joachimi et al.~in prep.}
+analytical methods will be published soon (Joachimi et al.~in prep.)}
 %
@@
 difference is measured with the depreciated case ExtL1Fl, for which the
-recovered amplitude is larger by $16\%$ of the statistical error. \ch{These
-negligible changes to the error bars were to be expected owing to the
-high level of statistical noise and cosmic variance in comparison to the low-level impact of the various
-approximations shown in Fig.~\ref{fig:Cl_cases}.}
+recovered amplitude is larger by $16\%$ of the statistical error. These
+negligible changes to the error bars were to be expected owing to the high
+level of statistical noise and cosmic variance in comparison to the low-level
+impact of the various approximations shown in Fig.~\ref{fig:Cl_cases}.
 
@@
 
-\ch{Considering the cosmological constraints from tomographic Kilo-Degree Survey (KiDS), we conclude that
-these are robust to flat-sky and Limber approximations. The case ExtL1FlHyb that was used
-for the analysis of KiDS data in \citet{KiDS-450} and \cite{joudaki/etal:2017} introduces
-errors that are more than an order of magnitude lower than the cosmic variance
-for that survey, and thus this approximation has a negligible impact on the
-cosmological parameters.}
+Considering the cosmological constraints from tomographic Kilo-Degree Survey
+(KiDS), we conclude that these are robust to flat-sky and Limber
+approximations. The case ExtL1FlHyb that was used for the analysis of KiDS data
+in \citet{KiDS-450} and \cite{joudaki/etal:2017} introduces errors that are
+more than an order of magnitude lower than the cosmic variance for that survey,
+and thus this approximation has a negligible impact on the cosmological
+parameters.
 

### 2017-02-16 limber2.tex
Changes from Marika added
Removed line about flat universe in appendix

@@
 
-For future
-large-scale surveys with unprecedented precision, we show that the spherical
-second-order Limber approximation will provide sufficient accuracy. \ch{In this case, the
-cosmic-shear power spectrum is shown to be in agreement with the full projection at the
-sub-percent level for $\ell > 3$, with the corresponding errors an order of
-magnitude below cosmic variance for all $\ell$.
-When computing the two-point shear correlation function, we show that the flat-sky fast Hankel 
-transformation results in errors below two percent compared to the full spherical transformation.}
+For future large-scale surveys with unprecedented precision, we show that the
+spherical second-order Limber approximation will provide sufficient accuracy.
+In this case, the cosmic-shear power spectrum is shown to be in agreement with
+the full projection at the sub-percent level for $\ell > 3$, with the
+corresponding errors an order of magnitude below cosmic variance for all
+$\ell$. When computing the two-point shear correlation function, we show that
+the flat-sky fast Hankel transformation results in errors below two percent
+compared to the full spherical transformation.
 %
@@
   \item $p(\ell) = 1$, this corresponds to $\nu(\ell) = \ell$, which is the
-    \emph{standard} Limber approximation \LabelTxt{L1Fl}
-    Until recently, i.e.~for all pre-2014 CFHTLenS results, \ch{DES-SV \citep{abbott/etal:2016} and DLS \citep{jee/etal:2016} analyses, 
-    this was the approximation of choice.}
-    Note that we do not discuss the second-order Limber approximation \ch{with $p(\ell)=1$}.
-  %
-  \item $p(\ell) = \ell^4/(\ell + 1/2)^4$. This corresponds to the \emph{extended} Limber
-    approximation \LabelTxt{ExtL1Fl, ExtL2Fl} with $\nu(\ell) = \ell + 1/2$; however the following case is typically employed:
+    \emph{standard} Limber approximation \LabelTxt{L1Fl} Until recently,
+  i.e.~for all pre-2014 CFHTLenS results, DES-SV \citep{abbott/etal:2016} and DLS
+  \citep{jee/etal:2016} analyses, this was the approximation of choice. Note that
+  we do not discuss the second-order Limber approximation with $p(\ell)=1$.
+  %
+  \item $p(\ell) = \ell^4/(\ell + 1/2)^4$. This corresponds to the
+  \emph{extended} Limber approximation \LabelTxt{ExtL1Fl, ExtL2Fl} with
+  $\nu(\ell) = \ell + 1/2$; however the following case is typically employed:
   %
@@
 Considering first the flat-sky cases, the standard first-order Limber
-approximation, (L1Fl), that was adopted for all pre-2014 CFHTLenS analyses, \ch{DES-SV and DLS analyses}, we
+approximation, (L1Fl), that was adopted for all pre-2014 CFHTLenS analyses, DES-SV and DLS analyses, we
 find it to be accurate to better than 10\% for $\ell>3$, converging slowly to the
@@
   $1^{\rm st}$-order standard Limber, flat sky & L1Fl & (\ref{eq:P_ell_limber1}) + (i)
-    & $1$ & $\ell$ & \ch{Pre-2014 CFHTLenS, DES-SV and DLS} \\ \hline
+    & $1$ & $\ell$ & Pre-2014 CFHTLenS, DES-SV and DLS \\ \hline
   %
@@
   $1^{\rm st}$-order extended Limber, hybrid, flat sky & ExtL1FlHyb & (\ref{eq:P_ell_limber1}) + (iii)
-    & $1$ & $\ell + \frac 1 2$ & \ch{Post-2014 CFHTLenS, KiDS} \\ \hline
+    & $1$ & $\ell + \frac 1 2$ & Post-2014 CFHTLenS, KiDS \\ \hline
   %
@@
 spectrum by the Hankel transform in equation~(\ref{eqn:xiGG}), and should
-be replaced by the \mk{spherical} transform \citep{1973ApJ...185..413P}
-%
-\begin{equation}
- \xi_+(\theta) = \mk{\left\langle \gamma \gamma^\ast \right\rangle(\theta)}
+be replaced by the spherical transform \citep{1973ApJ...185..413P}
+%
+\begin{equation}
+ \xi_+(\theta) = \left\langle \gamma \gamma^\ast \right\rangle(\theta)
   =  \frac 1{4\pi} \sum\limits_{\ell=2}^\infty (2 \ell + 1) C^\gamma(\ell) {\rm P}_\ell[\cos(\theta)],
@@
 %
-where ${\rm P}_\ell(x)$ are the Legendre polynomials in $x$ of order $\ell$. \mk{This equation is easily derived
+where ${\rm P}_\ell(x)$ are the Legendre polynomials in $x$ of order $\ell$. This equation is easily derived
 using the harmonics expansion of the shear (\ref{eq:gamma_harm_exp}) and the orthogonality relation of
-the spherical harmonics (\ref{eq:Yellm_ortho}).}
+the spherical harmonics (\ref{eq:Yellm_ortho}).
 
@@
 %
-\ch{We find that the Hankel transform (equation~\ref{eqn:xiGG}) is accurate to better than $2$ percent level.
+We find that the Hankel transform (equation~\ref{eqn:xiGG}) is accurate to better than $2$ percent level.
 %
 The difference between second-order Limber and full projection using the
-spherical transform (\ref{eq:xi_Legendre}) is well below one percent
-for $\vartheta < 200$ arcminutes.}
-The red circles in Fig.~\ref{fig:xi_p_legendre} present the limit of
-precision that we can achieve with the current fast Hankel transform implementation
-for the correlation function. The green line shows the limit of the
-second-order Limber approximation on the correlation function.
+spherical transform (\ref{eq:xi_Legendre}) is well below one percent for
+$\vartheta < 200$ arcminutes. The red circles in Fig.~\ref{fig:xi_p_legendre}
+present the limit of precision that we can achieve with the current fast Hankel
+transform implementation for the correlation function. The green line shows the
+limit of the second-order Limber approximation on the correlation function.
 
@@
   \caption{\emph{Left panel:} The shear correlation function component $\xi_+$
-for the ExtL2Sph projection using the spherical transform (green line for ExtL2Sph, grey squares for FullSph),
-compared to the flat-sky Hankel transform of ExtL2Sph (red circles).
-\emph{Right panel:} The relative
-difference \mk{compared to the full spherical case FullSph of ExtL2Sph with spherical transform
-(green line), 
-and Hankel transform (red circles).}}
+for the ExtL2Sph projection using the spherical transform (green line for
+ExtL2Sph, grey squares for FullSph), compared to the flat-sky Hankel transform
+of ExtL2Sph (red circles). \emph{Right panel:} The relative difference compared
+to the full spherical case FullSph of ExtL2Sph with spherical transform (green
+line), and Hankel transform (red circles).}
 
@@
 
-To obtain the power spectrum of the lensing potential for a flat Universe, 
-we insert the lensing projection (equation~\ref{eq:psi}) for $K=0$ into the
+To obtain the power spectrum of the lensing potential, 
+we insert the lensing projection (equation~\ref{eq:psi}) into the
 inverse harmonics expansion (equation~\ref{eq:psi_harm_exp_inv}) and write the 3D potential
@@
 \approx k^4 \chi^2 {\chi^\prime}^2$, to recover
-equation~(\ref{eq:P_ell_gamma_full_der}). This argument is very hand-wavey!
+equation~(\ref{eq:P_ell_gamma_full_der}).
 In fact, using the approximation $k \chi = \ell$ seems to go too far, this is

### 2017-02-17 limber2.tex
Added (version 1) to the abstract and App B1

--- 2017-02-16 limber2.tex
@@
 Background (CMB) temperature anisotropy results cannot be alleviated, in
-contrast to the recent claim made by \citet{2016arXiv161104954K}.
+contrast to the recent claim made by Kitching et al. (2016, version 1)
+
+%\citet{2016arXiv161104954K}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Kitching et al.~2016}
+\subsection{Kitching et al.~2016 (version 1)}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-02-17 limber2.tex
Added in some instances of "equation"~\ref{} for MNRAS style

@@
 %
-This is demonstrated using data from the Canada-France-Hawaii Lensing Survey
+This is demonstrated using data from the Canada-France-Hawaii Telescope Lensing Survey
 (CFHTLenS). We find that the reported tension with Planck Cosmic Microwave
@@
 where ${\rm P}_\ell(x)$ are the Legendre polynomials in $x$ of order $\ell$. \mk{This equation is easily derived
-using the harmonics expansion of the shear (\ref{eq:gamma_harm_exp}) and the orthogonality relation of
-the spherical harmonics (\ref{eq:Yellm_ortho}).}
+using the harmonics expansion of the shear (equation~\ref{eq:gamma_harm_exp}) and the orthogonality relation of
+the spherical harmonics (equation~\ref{eq:Yellm_ortho}).}
 
@@
 generalised to non-integer arguments and is positive for $\ell \ge 2$. We can
-thus use the spherical power spectrum \sout{in the Limber approximations} with
+thus use the spherical power spectrum with
 the Hankel transformation in equation~(\ref{eqn:xiGG}) to compute the two-point correlation
-functions. This has the advantage being able to use very fast numerical implementations of
-the Hankel tranforms using FFTs \citep{fftlog}, when Monte-Carlo sampling.
+functions. This has the advantage being able to employ fast FFT numerical implementations of
+the Hankel tranforms \citep{fftlog}, when Monte-Carlo sampling.
 
@@
 %
-The difference between second-order Limber and full projection using the
-spherical transform (\ref{eq:xi_Legendre}) is well below one percent
+The difference between the second-order Limber and full projection solution using the
+spherical transform (equation~\ref{eq:xi_Legendre}) is well below one percent
 for $\vartheta < 200$ arcminutes.}

### 2017-02-17 limber2.tex
Removed commented lines from .tex for submission

--- 2017-02-16 limber2.tex
@@
 \usepackage[normalem]{ulem}
-%\usepackage{ulem}
 \usepackage{mathtools}
@@
 \usepackage{footnote}
-%\makesavenoteenv{tabular}
 \makesavenoteenv{table}
@@
 
-\pagestyle{empty}
+%\pagestyle{empty}
 \usepackage{psfrag, epsfig}
@@
 \definecolor{purple}{RGB}{76, 0,153}
-%\definecolor{purple}{RGB}{76, 0,153}
 \newcommand{\ch}[1]{\textcolor{purple}{\textbf{#1}}}
@@
 %
-This is demonstrated using data from the Canada-France-Hawaii Lensing Survey
+This is demonstrated using data from the Canada-France-Hawaii Telescope Lensing Survey
 (CFHTLenS). We find that the reported tension with Planck Cosmic Microwave
 Background (CMB) temperature anisotropy results cannot be alleviated, in
-contrast to the recent claim made by \citet{2016arXiv161104954K}.
+contrast to the recent claim made by Kitching et al. (2016, version 1)
+
+%\citet{2016arXiv161104954K}.
 
@@
 surveys.
-%(Kilo-Degree Survey, KiDS \citet{kuijken/etal:2015}, Dark Energy Survey, DES, \citet{abbott/etal:2016}, Hyper-Suprime Camera Survey, HSC\footnote{HSC; \href={http://hsc.mtk.nao.ac.jp/ssp/}}) and future (Euclid, \citet{2011arXiv1110.3193L}, LSST, \citet{chang/etal:2013}, WFIRST\footnote{WFIRST; \href={http://wfirst.gsfc.nasa.gov}}) large-scale surveys.
 Interest in the results from these surveys is high as statistically significant
@@
 light, and the projection is carried out over comoving distances $\chi$.
-%, and $f_K(\chi) = |K|^{-1/2} S_K(|K|^{1/2} \chi)$ is the comoving angular
-% diameter distance, where the function $S_K$ equals $\sin$, ${\rm id}$, or
-% $\sinh$ if the spatial curvature of the Universe $K$ is positive, zero, or
-% negative, respectively.
 The last argument of the potential $\Phi$ is not to
@@
   \lim_{\varepsilon \rightarrow 0} \int_0^\infty {\rm d} x \, {\rm e}^{-\epsilon (x - \nu)} g(x) {\rm J}_\nu(x)
-  %\approx g(\nu) - \frac 1 2 g^{\prime\prime}(\nu) - \frac \nu 6 g^{\prime\prime\prime}(\nu) 
   \approx g(\nu) - \frac 1 2 \left.\frac{{\rm d}^2 g}{{\rm d} x^2}\right|_{x=\nu}
@@
 
-%The error between filter and power-law fit
-%becomes larger than $50\%$ only for scales larger than $1,500 \mbox{Mpc}/h$. On the angular
-%scales where the second-order Limber approximation significantly contributes to the shear
-%power spectrum, $\ell \le 100$, this corresponds to $k < 0.03 h/$Mpc, linear
-%scales where the 3D power spectrum is small and does not strongly contribute to the lensing
-%power spectrum.
-
 \subsection{Flat-sky}
@@
 \end{enumerate}
-%
-
-% (i)  Standard Flat
-% (ii) Extended Flat
-% (iii) Extended Flat Hybrid
 
@@
 survey (sky area $15,000$ square degrees) for all $\ell$.
-
-% Compuation times:
-% l>=20, 20 modes
-% full 37s
-% L2   2.14s
-% L1   0.8s
 
@@
 
-% nicaea            Kil+17      'Comment paper' Plot color    Kit+16                Plot color    my comment
-% limber            L1Fl        Kst             black         Limber+Tl=1+Flat-sky  blue
-% limber_la08       ExtL1Fl     ELF             blue
-% limber_la08_hyb   ExtL1FlHyb  ESt             magenta                                           pre-factor~1 despite nu=ell+1/2
-% limber_la08_sph   ExtL1Sph    ELS             cyan
-% limber2_la08      ExtL2Fl
-% limber2_la08_hyb  ExtL2FlHyb
-% limber2_la08_sph  ExtL2Sph
-% full              Full
-
 \renewcommand{\baselinestretch}{1.5}
@@
 where ${\rm P}_\ell(x)$ are the Legendre polynomials in $x$ of order $\ell$. This equation is easily derived
-using the harmonics expansion of the shear (\ref{eq:gamma_harm_exp}) and the orthogonality relation of
+using the harmonics expansion of the shear (equation~\ref{eq:gamma_harm_exp}) and the orthogonality relation of
 the spherical harmonics (\ref{eq:Yellm_ortho}).
@@
 %
-The difference between second-order Limber and full projection using the
-spherical transform (\ref{eq:xi_Legendre}) is well below one percent for
-$\vartheta < 200$ arcminutes. The red circles in Fig.~\ref{fig:xi_p_legendre}
-present the limit of precision that we can achieve with the current fast Hankel
-transform implementation for the correlation function. The green line shows the
-limit of the second-order Limber approximation on the correlation function.
+The difference between the second-order Limber and full projection solution using the
+spherical transform (equation~\ref{eq:xi_Legendre}) is well below one percent
+for $\vartheta < 200$ arcminutes.}
+The red circles in Fig.~\ref{fig:xi_p_legendre} present the limit of
+precision that we can achieve with the current fast Hankel transform implementation
+for the correlation function. The green line shows the limit of the
+second-order Limber approximation on the correlation function.
 
@@
 already halfway the Limber approximation.
-
-%\begin{align}
-  %W_\kappa(z) = & \frac 1 {H(z)} \int_z^\infty {\rm d} z_{\rm s} W_{\rm L}(z_{\rm s}, z) W_{\rm g}(z)
-              %=  \frac 1 {H(z)} \chi \int_\chi^\infty {\rm d} \chi^\prime \frac{\chi^\prime - \chi}{\chi^\prime}
-                %n(\chi)
-              %\nonumber \\
-              %& \equiv \frac 1 {H(z)} \chi q(\chi),
-%\end{align}
-%%
-%using ${\rm d} z W_{\rm g}(z) = {\rm d} \chi n(\chi)$.
-%To write the redshift integrals (9) in \cite{2008PhRvD..78d3002S} over 
-%comoving distance, we make the variable transformation
-%%
-%\begin{equation}
-  %{\rm d} \chi = \frac{c {\rm d} z}{H(z)} .
-%\end{equation}
-%%
-%We
 

### 2017-02-17 limber2.tex
consistent version

@@
 spherical transform (equation~\ref{eq:xi_Legendre}) is well below one percent
-for $\vartheta < 200$ arcminutes.}
+for $\vartheta < 200$ arcminutes.
 The red circles in Fig.~\ref{fig:xi_p_legendre} present the limit of

### 2017-02-20 limber2.tex
Added funding (PS)

@@
 
-\title[Precision calculations of the cosmic shear projection]{Precision calculations of the cosmic shear power spectrum
-projection}
+\title[Precision calculations of the cosmic shear projection]{Precision calculations of the cosmic shear power spectrum projection}
 
@@
 Research Council Centre of Excellence for All-sky Astrophysics (CAASTRO),
-through project number CE110001020.
+through project number CE110001020i, and by the German Federal
+Ministry for Economic Affairs and Energy (BMWi) under
+project no. 50QE1103.
 

### 2017-02-20 limber2.tex
Added to footnote that DES-SV also has a typo in Abbott et al about the 0.5 factor (after discussion with Joe Zuntz). Modified Table accordingly Added to acknowledgements - forgot to include Joanne Cohn who had lots of helpful advice on the comment paper Also added in Zuntz and A Hall after this mornings helpful e-mail

@@
     \emph{standard} Limber approximation \LabelTxt{L1Fl} Until recently,
-  i.e.~for all pre-2014 CFHTLenS results, DES-SV \citep{abbott/etal:2016} and DLS
+  i.e.~for all pre-2014 CFHTLenS results and DLS
   \citep{jee/etal:2016} analyses, this was the approximation of choice. Note that
@@
     standard and extended Limber approximation~\LabelTxt{ExtL1FlHyb, ExtL2FlHyb}, and the first-order case 
-    was used in \cite{KiDS-450,joudaki/etal:2016,joudaki/etal:2017}. As is shown
+    was used in \cite{KiDS-450,joudaki/etal:2016,joudaki/etal:2017,abbott/etal:2016}. As is shown
     below, this is a better approximation to the full projection than case (ii). In equation~(\ref{eq:P_ell_limber2})
@@
 Considering first the flat-sky cases, the standard first-order Limber
-approximation, (L1Fl), that was adopted for all pre-2014 CFHTLenS analyses, DES-SV and DLS analyses, we
+approximation, (L1Fl), that was adopted for all pre-2014 CFHTLenS analyses and DLS analyses, we
 find it to be accurate to better than 10\% for $\ell>3$, converging slowly to the
@@
 $\ell>15$.  The first-order extended Limber approximation `hybrid' cases
-(ExtL1FlHyb) was adopted by \citet{joudaki/etal:2016}, \citet{joudaki/etal:2017}, and
+(ExtL1FlHyb) was adopted by \citet{joudaki/etal:2016}, \citet{joudaki/etal:2017}, DES-SV \citep{abbott/etal:2016} and
 \cite{KiDS-450}\footnote{We confirm that there is a typographical error in
-equation 4 of \cite{KiDS-450} which should include the extra term of `+0.5' in
-$\nu(\ell)$ that was incorporated in the cosmological analysis.}.
+equation 4 of \cite{KiDS-450} and in equation 2 of \citet{abbott/etal:2016} (private communication with Joe Zuntz) 
+which should include the extra term of `+0.5' in
+$\nu(\ell)$ that was incorporated in both cosmological analyses.}.
 
@@
   $1^{\rm st}$-order standard Limber, flat sky & L1Fl & (\ref{eq:P_ell_limber1}) + (i)
-    & $1$ & $\ell$ & Pre-2014 CFHTLenS, DES-SV and DLS \\ \hline
+    & $1$ & $\ell$ & Pre-2014 CFHTLenS and DLS \\ \hline
   %
@@
   $1^{\rm st}$-order extended Limber, hybrid, flat sky & ExtL1FlHyb & (\ref{eq:P_ell_limber1}) + (iii)
-    & $1$ & $\ell + \frac 1 2$ & Post-2014 CFHTLenS, KiDS \\ \hline
+    & $1$ & $\ell + \frac 1 2$ & Post-2014 CFHTLenS, DES-SV and KiDS \\ \hline
   %
@@
 The authors thank Tommaso Giannantonio, Sarah Bridle, Ami Choi, Donnacha Kirk,
-Lance Miller, Benjamin Joachimi, Chris Blake and Adam Amara for very helpful
+Lance Miller, Benjamin Joachimi, Chris Blake, Joe Zuntz, Joanne Cohn, Alex Hall and Adam Amara for very helpful
 discussions. This work was financially supported by the DFG (Emmy Noether grant

### 2017-03-09 limber2.tex
Updated figures with Ludo's wigner-d calculations (however; more updates need to be done using the corrected calculations); added comment on missing (now correct) a^2 in the Van de Rijt derivation

--- 2017-02-20 limber2.tex
@@
 equation to replace the matter with the potential power spectrum we obtain the
-same expression as \cite{vande2012} (their Equation~7.19), except for an
-additional factor $a^2(\chi)$. This difference is accounted for by the factor
-$a^{-1}$ in the propagation of primordial potential perturbations to late
-times, see Equation~(6.22) in \cite{vande2012}, where the transition is
-calculated using $g(a)$ instead of $D(a)$.
+same expression as \cite{vande2012} (their Equation~7.19).
+
+\EDIT{Note: The factor of $a^2$ has been resolved, it is correctly reproduced
+when propagating the primordial potential power spectrum to late times $a$
+with $[D+(a)/a]^2$ instead of $D^2+(a)$.}
+
+%, except for an
+%%additional factor $a^2(\chi)$. This difference is accounted for by the factor
+%$a^{-1}$ in the propagation of primordial potential perturbations to late
+%times, see Equation~(6.22) in \cite{vande2012}, where the transition is
+%calculated using $g(a)$ instead of $D(a)$.
 
@@
 integral\footnote{Typo confirmed by T.~G., priv.~comm.}. This also leads to an
-errorous $r_K^{-2}(r)$ in their Limber equation (27). With these factors
+errornous $r_K^{-2}(r)$ in their Limber equation (27). With these factors
 accounted for, and making the additional approximation $k \chi \approx k

### 2017-03-09 limber2.tex
command EDIT

--- 2017-02-20 limber2.tex
@@
 \usepackage{bm,color}% bold math
-\usepackage[normalem]{ulem}
+%\usepackage{ulem}
 \usepackage{mathtools}
@@
 \usepackage{footnote}
+%\makesavenoteenv{tabular}
 \makesavenoteenv{table}
@@
 
-%\pagestyle{empty}
+\pagestyle{empty}
 \usepackage{psfrag, epsfig}
@@
 \newcommand{\mk}[1]{{\bf\textcolor{blue}{#1}}}
-\newcommand{\Label}[1]{\quad (\mbox{#1})}
-\newcommand{\LabelTxt}[1]{(\mbox{#1})}
-
-\newcommand{\MA}[1]{\textcolor{red}{#1}}
+\newcommand{\EDIT}[1]{{\bf\textcolor{red}{#1}}}
 
@@
 
-% symbol on top of another
-\newcommand{\ontop}[2]{
-  \renewcommand{\arraystretch}{0.2}
-  \begin{array}{c}
-  #1 \\ #2
-  \end{array}
-  \renewcommand{\arraystretch}{1.0}
-}
-% lesser similar, <~
-\newcommand{\lsim}{\ontop{<}{\sim}}
-% greater similar >~
-\newcommand{\gsim}{\ontop{>}{\sim}}
-
-\title[Precision calculations of the cosmic shear projection]{Precision calculations of the cosmic shear power spectrum projection}
+\title[Precision calculations for cosmic shear projections]{Precision calculations of cosmic shear projections}  %??
+%{Precision calculations of the cosmic shear power spectrum projection}
 
@@
 We compute the spherical-sky weak-lensing power spectrum of the shear and
-convergence. We discuss various approximations, such as flat-sky, and first- and
-second-order Limber equations for the projection. We find that the impact of
-adopting these approximations are negligible when constraining cosmological
-parameters from current weak lensing surveys.
-%
-This is demonstrated using data from the Canada-France-Hawaii Telescope Lensing Survey
-(CFHTLenS). We find that the reported tension with Planck Cosmic Microwave
-Background (CMB) temperature anisotropy results cannot be alleviated, in
-contrast to the recent claim made by Kitching et al. (2016, version 1)
-
-%\citet{2016arXiv161104954K}.
-
-For future large-scale surveys with unprecedented precision, we show that the
-spherical second-order Limber approximation will provide sufficient accuracy.
-In this case, the cosmic-shear power spectrum is shown to be in agreement with
-the full projection at the sub-percent level for $\ell > 3$, with the
-corresponding errors an order of magnitude below cosmic variance for all
-$\ell$. When computing the two-point shear correlation function, we show that
-the flat-sky fast Hankel transformation results in errors below two percent
-compared to the full spherical transformation.
-%
-In the spirit of reproducible research, our numerical implementation of all
-approximations and the full projection are publicly available within the
-package \textsc{nicaea} at \texttt{http://www.cosmostat.org/software/nicaea}.
+convergence. We discuss various approximations, such as flat-sky, first- and
+second-order Limber equations for the projection. We find that the impact of adopting 
+these approximations are negligible when constraining cosmological parameters from 
+current weak lensing surveys.
+This is demonstrated using data from the Canada-France-Hawaii Lensing Survey (CFHTLenS). 
+We find that the reported tension with Planck CMB temperature anisotropy results cannot be alleviated, in
+contrast to the recent claim made by \citet{2016arXiv161104954K}. 
+For future large-scale surveys with unprecedented precision, we show that the spherical
+second-order Limber approximation will provide sufficient accuracy, as it is in 
+agreement with the full projection at the sub-percent level for $\ell > 3$.  
+In the spirit of reproducible research, our numerical implementation of all approximations
+and the full projection are publicly available within the package
+\textsc{nicaea} at \texttt{http://www.cosmostat.org/software/nicaea}.
 
@@
 modifications to gravity.  As such it is the primary science goal of several
-current (KiDS, DES, HSC\footnote{KiDS: \href={http://kids.strw.leidenuniv.nl},
-DES: \href={http://www.darkenergysurvey.org}, HSC:
-\href={http://hsc.mtk.nao.ac.jp/ssp}}) and future (Euclid, LSST,
-WFIRST\footnote{Euclid: \href={http://sci.esa.int/euclid}, LSST:
-\href={http://www.lsst.org}, WFIRST: \href={http://wfirst.gsfc.nasa.gov}})
-surveys.
+current (KiDS, DES, HSC\footnote{KiDS: \href={http://kids.strw.leidenuniv.nl}, DES: \href={http://www.darkenergysurvey.org}, HSC: \href={http://hsc.mtk.nao.ac.jp/ssp/}})
+and future (Euclid, LSST, WFIRST\footnote{Euclid: \href={http://sci.esa.int/euclid}, LSST: \href={http://www.lsst.org}, WFIRST: \href={http://wfirst.gsfc.nasa.gov}}) surveys.
+%(Kilo-Degree Survey, KiDS \citet{kuijken/etal:2015}, Dark Energy Survey, DES, \citet{abbott/etal:2016}, Hyper-Suprime Camera Survey, HSC\footnote{HSC; \href={http://hsc.mtk.nao.ac.jp/ssp/}}) and future (Euclid, \citet{2011arXiv1110.3193L}, LSST, \citet{chang/etal:2013}, WFIRST\footnote{WFIRST; \href={http://wfirst.gsfc.nasa.gov}}) large-scale surveys.
 Interest in the results from these surveys is high as statistically significant
@@
 and the Canada-France-Hawaii Telescope Lensing Survey
-\citep[CFHTLenS;][]{joudaki/etal:2016}.  If the source of this tension is not a
-result of so-far unconsidered sources of systematic errors in one or all
+\citep[CFHTLenS;][]{joudaki/etal:2016}.  If the source of this tension is not
+a result of so-far unconsidered sources of systematic errors in one or all
 experiments, extensions to the standard flat $\Lambda$CDM cosmological models
@@
 
-In the era of the upcoming large-scale surveys that will provide measurements
-of cosmic shear with unprecedented precision, one needs to revisit the
-theoretical predictions of the observables to ensure that the accuracy of the
-models meet the accuracy of the observations. In this paper, we examine the
-widely used Limber approximation for the projected weak-lensing power spectrum.
-We consider spherical coordinates and the flat-sky approximation, and compute
-the full projection. The first-order extended Limber approximation provides
-sub-percent accuracy for $\ell > 10$ and is sufficient for present surveys. The
-associated errors are sub-dominant even for future large surveys.
-
-We further show that the second-order Limber approximation is an
-accurate representation of the full projection, with better than percent level
-precision for scales $\ell > 3$. Since this approximation involves only 1D
-integrals over the matter power spectrum, it is very fast to calculate
-numerically and can readily be employed in Monte-Carlo sampling methods to
-obtain precision constraints on cosmological parameters.
-We also compute the shear correlation function using a spherical 
-transformation, and compare this to the flat-sky approximated, commonly used
-fast Hankel transformation.
+In the era of the upcoming large-scale surveys that will provide measurements of
+cosmic shear with unprecedented precision, one needs to revisit the theoretical
+predictions of the observables to ensure that the accuracy of the
+models meet the accuracy of the observations. In this paper, we examine the widely used Limber
+approximation for the projected weak-lensing power spectrum. We consider
+spherical coordinates and the flat-sky approximation, and compute the full
+projection. We show
+that the second-order Limber approximation is an accurate representation of the full projection, with better than percent level precision for scales $\ell > 3$. 
+Since this approximation involves only 1D integrals over the matter power spectrum, it is very fast to
+calculate numerically and can be readily employed in Monte-Carlo sampling methods
+to obtain precision constraints on cosmological parameters.
 
@@
 power spectra for the flat-sky and spherical cases, following the seminal work
-from \citet{2000PhRvD..62d3007H} \cite[see also][]{2005PhRvD..72b3516C}. In
-section~\ref{sec:L2} we derive weak-lensing observables using a second-order
-Limber approximation first introduced by \citet{2008PhRvD..78l3506L}. We
-compare the shear power spectrum and the commonly-used two-point shear
-correlation function for the full solution to a range of different
-approximations in section~\ref{sec:results}, providing cosmological constraints
-for each case using CFHTLenS data from \citet{CFHTLenS-2pt-notomo}. This paper
-draws from several sources of literature which have previously discussed the
-full projection, or reviewed the accuracy of the Limber approximation for weak
+from \citet{2000PhRvD..62d3007H}, see also \citet{2005PhRvD..72b3516C}. In section~\ref{sec:L2} we
+derive weak lensing observables using a second-order limber approximation first
+introduced by \citet{2008PhRvD..78l3506L}. We compare the shear power spectrum
+and commonly-used two-point shear correlation function for the full solution to
+a range of different approximations in section~\ref{sec:results}, providing
+cosmological constraints for each case using CFHTLenS data from
+\citet{CFHTLenS-2pt-notomo}. This paper draws
+from several sources of literature which have previously discussed the full
+projection, or reviewed the accuracy of the Limber approximation for weak
 lensing studies, namely \citet{2008PhRvD..78d3002S,2012PhRvD..86b3001B,
@@
 compute lensing power spectra for a spherical case, and in the flat-sky
-approximation. For completeness we provide a derivation of the weak lensing
-power spectra in Appendix~\ref{sec:derivations_C}.
+approximation. For completeness we provide a derivation of the weak lensing power spectra in Appendix~\ref{sec:derivations_C}.
 
@@
 
-The lensing potential $\psi$ at a position on the sky $(\theta, \varphi)$ in
+The lensing potential $\psi$ at a direction on the sky $(\theta, \varphi)$ in
 the Born approximation is defined as the projected 3D metric potential $\Phi$
-along the line of sight of a flat Universe \citep{1998ApJ...498...26K,BS01},
+along the line of sight \citep{1998ApJ...498...26K,BS01},
 %
@@
 \begin{equation}
-  \psi(\theta, \varphi) = \frac 2 {{\rm c}^2} \int\limits_0^\infty \frac{{\rm d}\chi}{\chi}
-    %\Phi[\chi, f_K(\chi) \theta, f_K(\chi) \varphi; \chi] \, q(\chi),
-    \Phi[\chi, \chi \theta, \chi \varphi; \chi] \, q(\chi),
+  \psi(\theta, \varphi) = \frac 2 {{\rm c}^2} \int_0^{\chi_{\rm lim}} \frac{{\rm d}\chi}{\chi}
+    \Phi[\chi, f_K(\chi) \theta, f_K(\chi) \varphi; \chi] \, q(\chi),
   \label{eq:psi}
@@
 \begin{equation}
-  q(\chi) = \int\limits_\chi^{\chi_{\rm h}} {\rm d} \chi^\prime \, n(\chi^\prime)
-    %\frac{f_K(\chi^\prime - \chi)}{f_K(\chi^\prime)},
-    \frac{\chi^\prime - \chi}{\chi^\prime},
+  q(\chi) = \int\limits_\chi^{\chi_{\rm lim}} {\rm d} \chi^\prime \, n(\chi^\prime)
+    \frac{f_K(\chi^\prime - \chi)}{f_K(\chi^\prime)},
   %
@@
 corresponding to a population of lensed galaxies with a normalised source
-redshift distribution $n_z(z) {\rm d}z = n(\chi) {\rm d} \chi$, with the limit
-being the comoving distance to the horizon $\chi_{\rm h}$\footnote{In
-(\ref{eq:psi}) we have replaced this limit without loss of generality with
-$\infty$, since $q(\chi > \chi_{\rm h}) = 0$.}. Here, ${\rm c}$ is the speed of
-light, and the projection is carried out over comoving distances $\chi$.
-The last argument of the potential $\Phi$ is not to
-be understood as coordinate, but rather as a substitute of cosmic time,
-$t(\chi)$, to express the time at which the potential is evaluated. This is
-true in the following for all fields and functions thereof that dynamically
-change with cosmic epoch.
-
-The form of the lensing efficiency $q$ in equation (\ref{eq:lens_efficiency})
-assumes a homogeneous galaxy distribution without clustering, so that the
-redshift distribution in this approximation does not depend on the direction on
-the sky. Accounting for this position-dependence leads to corrections of
-weak-lensing quantities due to clustering of source galaxies with other sources
-\citep{2002A&A...389..729S}, and with galaxies associated to lens structures
+redshift distribution $n(z) {\rm d}z = n(\chi) {\rm d} \chi$. Here, ${\rm c}$
+is the speed of light, the projection is carried out over comoving distances
+$\chi$ up to a limiting distance $\chi_{\rm lim}$, and $f_K(\chi) = |K|^{-1/2}
+S_K(|K|^{1/2} \chi)$ is the the comoving angular diameter distance, where the function
+$S_K$ equals $\sin$, ${\rm id}$, or $\sinh$ if the spatial curvature of the Universe
+$K$ is positive, zero, or negative, respectively.
+
+The form of the lensing efficiency $q$ in equation (\ref{eq:lens_efficiency}) assumes a
+homogeneous galaxy distribution without clustering, so that the redshift
+distribution in this approximation does not depend on the direction on the sky.
+Accounting for this position-dependence leads to corrections of weak-lensing
+quantities due to clustering of source galaxies with other sources
+\citep{2002A&A...389..729S}, and with galaxies associated with lens structures
 \citep{1998A&A...338..375B,H02}.
@@
 %
-where $\Omega_{\rm m}$ is the matter density parameter, $H_0$ the Hubble
-constant, $\vec k$ a 3D Fourier wave vector with modulus $k$ being the comoving
-wave number, and $a$ the scale factor with $a=1$ today. The Fourier transform
-of the potential and its inverse are defined as
-%
-\begin{align}
-  \hat \Phi(\vec k; \chi) = &  \int {\rm d}^3 r \, \Phi(\vec r; \chi) {\rm e}^{{\rm i} \vec k \cdot \vec r} ;
+where $\Omega_{\rm m}$ is the matter density parameter, $H_0$ the Hubble constant, $\vec k$ a 3D Fourier wave
+vector, and $a$ the scale factor with $a=1$ today.
+The Fourier transform of the potential and its inverse are defined as
+%
+\begin{align}
+  \hat \Phi(\vec k; \chi) = &  \int {\rm d}^3 r \, \Phi(\vec r; \chi) {\rm e}^{{\rm i} \vec k \vec r} ;
   \label{eq:hatPhi}
@@
   \Phi(\vec r; \chi) = &  \int \frac{{\rm d}^3 k}{(2\pi)^3}
-      \hat \Phi(\vec k; \chi) {\rm e}^{-{\rm i} \vec r \cdot \vec k},
+      \hat \Phi(\vec k; \chi) {\rm e}^{-{\rm i} \vec r \vec k},
   \label{eq:hatPhi_inv}
@@
 potential (equation~\ref{eq:psi}) into spherical harmonics, in analogy
-to the cosmic microwave background (CMB)
+to the CMB
 temperature, both of which are scalar functions on the sphere. This
@@
 %
-Complex conjugation is denoted with the superscript $^\ast$.
-To specify tomographic redshift bins $i=1\ldots N_z$, we introduce a family
+To specify tomographic redshift bins $i=0\ldots N_z-1$, we introduce a family
 of lensing efficiency functions $q_i$ defined by a corresponding family of
@@
 %
-Note that the argument $\ell$ is a discrete integer variable, and is often written as index, $C_\ell$.
 Using the properties of the spherical harmonics (see
@@
   C_{ij}^\psi(\ell) = & \frac 8 {c^4 \pi} 
-  \int_0^\infty \frac{{\rm d}\chi}{\chi} q_i(\chi)
-  \int_0^\infty \frac{{\rm d}\chi^\prime}{\chi^\prime} q_j(\chi^\prime)
+  \int_0^{\chi_{\rm lim}} \frac{{\rm d}\chi}{\chi} q_i(\chi)
+  \int_0^{\chi^\prime_{\rm lim}} \frac{{\rm d}\chi^\prime}{\chi^\prime} q_j(\chi^\prime)
   \int {\rm d} k k^2 \, {\rm j}_\ell(k \chi) {\rm j}_\ell(k \chi^\prime) P_\Phi(k; \chi, \chi^\prime)
@@
   = & \frac 8 \pi \pref^2
-  \int_0^\infty \frac{{\rm d}\chi}{\chi} \frac{q_i(\chi)}{a(\chi)}
-  \int_0^\infty \frac{{\rm d}\chi^\prime}{\chi^\prime} \frac{q_j(\chi^\prime)}{a(\chi^\prime)}
+  \int_0^{\chi_{\rm lim}} \frac{{\rm d}\chi}{\chi} \frac{q_i(\chi)}{a(\chi)}
+  \int_0^{\chi^\prime_{\rm lim}} \frac{{\rm d}\chi^\prime}{\chi^\prime} \frac{q_j(\chi^\prime)}{a(\chi^\prime)}
   \int \frac{{\rm d} k}{k^2} \, {\rm j}_\ell(k \chi) {\rm j}_\ell(k \chi^\prime) P_{\rm m}(k; \chi, \chi^\prime) ;
@@
 %
-and is related to $P_\Phi$ via the absolute square of the Poisson equation
-(\ref{eq:poisson}).
-
-This type of cross-power spectrum between different cosmological epochs
-$\chi$ and $\chi^\prime$ was introduced in \cite{2005PhRvD..72b3516C}. In
-Sects.~\ref{sec:geom_mean} and \ref{sec:factor_D} this unequal-time
-cross-spectrum \citep{2016arXiv161200770K} will be further evaluated and
-simplified in the context of the Limber approximation. The oscillating Bessel
-functions in equation~(\ref{eq:C_ell_phi_Pm}) ensure that only relatively close epochs
-contribute to the lensing potential correlation. This make sense since observed
-light rays from two galaxies at different positions on the sky that necessarily
-converge at the observer today, pick up the density fluctuations at similar
-times while propagating through the large-scale structure. A similar argument
-has been made in \cite{BS01}: since the matter power spectrum scales with $k$
-for $k \rightarrow 0$, there is decreasing power towards larger and larger
-scales. In particular, the correlation of cosmic fields decreases strongly
-above a coherence scale $|\chi - \chi^\prime| \gsim L_{\rm coh}$ which is significantly
-smaller than the horizon scale $\chi_{\rm h}$.
+and is
+related to $P_\Phi$ via the absolute square of the Poisson equation (\ref{eq:poisson}).
 
 In the following section we will discuss the relations between shear and
-convergence to the lensing potential on the sphere, and derive the power
+convergence to the lensing potential, on the sphere, and derive the power
 spectrum of the former two fields.
@@
 differential operator on the sphere is called \emph{edth} derivative, $\edth$,
-see \cite{2005PhRvD..72b3516C} for an in-depth mathematical discussion of this
+see \cite{2005PhRvD..72b3516C} for a in-depth mathematical discussion of this
 concept. The edth operator $\edth$ ($\edth^\ast$) raises (lowers) the spin $s$
@@
 \begin{align}
-  \gamma(\theta, \varphi) = & \frac 1 2 \edth \edth \psi(\theta, \varphi);
+  \gamma(\theta, \varphi) = & \frac 1 2 \edth \edth \psi(\theta, \varphi).
     \nonumber \\
@@
 %
-for $0 \le s \le \ell$, with the spin pre-factor \citep{2012PhRvD..86b3001B}
+with the spin pre-factor \citep{2012PhRvD..86b3001B}
 %
@@
 The two coefficients $_{+2} \gamma_{\ell m}$ and $_{-2} \gamma_{\ell m}$ are
-identical since the potential $\psi$ is a real function.
+identical since the potential $\phi$ is a real function.
 
@@
 %
-%For a zero-curvature Universe, this is given by
-This is given by
+For a zero-curvature Universe, this is given by
 %
@@
                  = & \frac 2 \pi \, \ellbar^2(\ell, 2) \, \pref^2
-                 \int_{0}^\infty \frac{\rm d \chi}{\chi} \frac{q_i(\chi)}{a(\chi)}
-                \int_{0}^\infty \frac{\rm d \chi^\prime}{\chi^\prime}
+                 \int_{0}^{\chi_{\rm lim}} \frac{\rm d \chi}{\chi} \frac{q_i(\chi)}{a(\chi)}
+                \int_{0}^{\chi_{\rm lim}} \frac{\rm d \chi^\prime}{\chi^\prime}
                 \frac{q_j(\chi^\prime)}{a(\chi^\prime)}
@@
                 \int_0^\infty \frac{{\rm d} k}{k^2} \, P_{\rm m}(k, \chi, \chi^\prime) \,
-                {\rm j}_\ell(k \chi) \, {\rm j}_\ell(k \chi^\prime), \Label{FullSph}
+                {\rm j}_\ell(k \chi) \, {\rm j}_\ell(k \chi^\prime) .
   \label{eq:C_ell_full}
@@
 %
-where we use the label `FullSph', see Table \ref{tab:cases} for a list of cases discussed in this work.
-The spherical spin pre-factor for the full projection shear power
-spectrum is $\ellbar^2(\ell, 2)$, which will be modified under
-flat-sky and Limber approximations below.
+The spherical pre-factor for the full projection power spectrum is $p(\ell) :=
+\ellbar^2(\ell, 2)$, which will be modified under flat-sky and Limber
+approximations below.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The majority of cosmic shear analyses have used the predicted lensing power
-spectrum approximated on a flat sky, neglecting the sky curvature. This is a
-valid approach for past and current survey areas with an extent less than 10
-degrees. To account for the sky curvature of the observed data, the shear
-correlation functions from observed galaxy ellipticities is now routinely
-computed using spherical coordinates, since projecting to a Cartesian plane has
-been shown to cause significant biases of the two-point funtion on large scales
-\citep{FSHK08}, and lead to spurious B-modes \citep{asgari/etal:2017}. Here
-we examine the effect of sky curvature on the theoretical models of the power
-spectrum, and the effect on cosmological parameter inference (see
-Sect.~\ref{sec:cfhtlens}).
-
-For a flat-sky, the spherical harmonic expansions are approximated by Fourier
+The majority of cosmic shear analyses have used lensing quantities approximated on a flat sky,
+neglecting the sky curvature. This is a valid approach for past and current
+survey areas with an extent less than 10 degrees. The correlation
+functions from the observed shear have, however, been calculated using spherical
+coordinates, and the effect on large scales has been shown to be significant \citep{FSHK08}.
+Here we examine the effect of sky curvature on the theoretical models.
+
+For a flat sky, the spherical harmonic expansions are approximated by Fourier
 transforms. The flat-sky equivalent of equations~(\ref{eq:psi_harm_exp}) and
@@
 \begin{align}
-  \psi(\vec \vartheta) = & \int \frac{{\rm d}^2 \ell}{(2\pi)^2} \, {\rm e}^{-{\rm i} \vec \ell \cdot \vec \vartheta} \hat \psi(\vec \ell);
+  \psi(\vec \vartheta) = & \int \frac{{\rm d}^2 \ell}{(2\pi)^2} \, {\rm e}^{-{\rm i} \vec \ell \vec \vartheta} \hat \psi(\vec \ell);
   \label{eq:psi_fourier}
@@
   %
-  \hat \psi(\vec \ell) = & \int {\rm d}^2 \vartheta \, {\rm e}^{{\rm i} \vec \ell \cdot \vec \vartheta} \psi(\vec \vartheta),
+  \hat \psi(\vec \ell) = & \int {\rm d}^2 \vartheta \, {\rm e}^{{\rm i} \vec \ell \vec \vartheta} \psi(\vec \vartheta);
   \label{eq:psi_fourier_inv}
@@
 Instead of a harmonics coefficients $\psi_{\ell m}$, the Fourier representation of the potential
-$\hat \psi$ now depends on the vector $\vec \ell \in \mathbb{R}^2$.
+$\hat \psi$ now depends on the vector $\vec \ell \in R^2$.
 
@@
 expansion (equation~\ref{eq:psi_harm_exp}) can be approximated by the Fourier
-representation in equation~(\ref{eq:psi_fourier}). They also demonstrated that the power
+representation in equation~\ref{eq:psi_fourier}). They also demonstrated that the power
 spectra are approximately equal, $P^\psi \approx C^\psi$.
@@
   \ell^2 \, _{\pm2}\!{\rm Y}_{\ell m}(\theta, \varphi) \approx  {\rm e}^{{\mp}2 {\rm i} \phi_\ell}
-    (\partial_1 \pm {\rm i} \partial_2)^2 \, {\rm Y}_{\ell m}(\theta, \varphi).
+    (\partial_1 \pm \partial_2)^2 \, {\rm Y}_{\ell m}(\theta, \varphi).
   \label{eq:sYlm_def_flat}
@@
 %
-The spin pre-factor $\ellbar(\ell, 2) = \sqrt{(\ell-1) \ell (\ell+1) (\ell+2)}$
-is replaced by $\ell^2$ in flat co-ordinates, an approximation that holds for
-large $\ell$, since sky curvature can be neglected for small angular
-scales. We find for the flat-sky shear power spectrum
+The spin pre-factor $\sqrt{(\ell-1) \ell (\ell+1) (\ell+2)}$ is replaced by
+$\ell^2$ in flat co-ordinates, \mk{an approximation that holds for large $\ell$.}
+ \ch{@MK - say why this is so.  Is it just that
+flat by definition means large $\ell$?} \mk{I think it's a large-ell approximation,
+but I don't know whether this is an assumption to derive this approximation, or whether it follows from that.
+I'll have to check this.}
+We find for the flat-sky shear power
+spectrum
 %
@@
                  = & \frac 2 \pi \, \ell^4 \, \pref^2
-                 \int_{0}^\infty \frac{\rm d \chi}{\chi} \frac{q_i(\chi)}{a(\chi)}
-                \int_{0}^\infty \frac{\rm d \chi^\prime}{\chi^\prime}
+                 \int_{0}^{\chi_{\rm lim}} \frac{\rm d \chi}{\chi} \frac{q_i(\chi)}{a(\chi)}
+                \int_{0}^{\chi_{\rm lim}} \frac{\rm d \chi^\prime}{\chi^\prime}
                 \frac{q_j(\chi^\prime)}{a(\chi^\prime)}
@@
 %
-with flat-sky pre-factor $\ell^4$. See App.~\ref{sec:schmidt08} and
-\ref{sec:giannantonio12} for discussions of alternative expressions for the
-flat-sky power spectrum.
+with flat-sky pre-factor $p(\ell) = \ell^4$. 
+See App.~\ref{sec:schmidt08} and \ref{sec:giannantonio12} for discussions of alternative expressions for the flat-sky power spectrum.
 
@@
 expansion for general projections from 3D to 2D scalar fields in the spherical,
-all-sky case. We apply their general derivation to the case of weak lensing,
-and contrary to \cite{2008PhRvD..78l3506L} account for a time-dependent power
-spectrum using two approaches presented in Sects.~\ref{sec:geom_mean} and
-\ref{sec:factor_D}.
-
-First, we use the identity of Bessel functions
+all-sky case. First, we use the identity of Bessel functions
 %
@@
 %
-in equation~(\ref{eq:C_ell_full}), where ${\rm J}_\nu$ is the Bessel function of the first kind
-and order $\nu$. Next, \cite{2008PhRvD..78l3506L} solve integrals of
+in equation~(\ref{eq:C_ell_full}), where ${\rm J}_\ell$ is the first-kind Bessel
+function of order $\ell$. Next, \cite{2008PhRvD..78l3506L} solve integrals of
 the form
@@
 \begin{equation}
-  \int_0^\infty {\rm d} \chi f(\chi) {\rm J}_\nu(k \chi)
-  = \int_0^\infty {\rm d} x k^{-1} f(x/k) {\rm J}_\nu(x)
+  \int_0^\infty {\rm d} \chi f(\chi) {\rm J}_{\ell + 1/2}(k \chi)
+  = \int_0^\infty {\rm d} x k^{-1} f(x/k) {\rm J}_{\ell + 1/2}(x)
   \label{eq:int_dchi}
@@
 %
-by performing a Taylor expansion of an arbitrary differentialble function
-$f$ around $x = k \chi = \nu = \ell + 1/2$, where the Bessel function has its
-approximate maximum.
+by performing a Taylor expansion of the function $f$ around $x = k \chi = \nu$, where
+the Bessel function has its approximate maximum.
 
@@
 \subsubsection{Geometric mean cross-correlation power spectrum}
-\label{sec:geom_mean}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-To separate the $k$- and $\chi, \chi^\prime$-terms in
-equation~(\ref{eq:C_ell_full}), we first approximate the matter power
-cross-spectrum between two distances by the geometric mean of the two involved
-distances \citep{2005PhRvD..72b3516C,2016arXiv161200770K},
+To separate the $k$- and $\chi, \chi^\prime$-terms in equation~(\ref{eq:C_ell_full}), we
+first approximate the matter power cross-spectrum between two
+distances by the
+geometric mean of the two involved distances \citep{2005PhRvD..72b3516C,2016arXiv161200770K},
 %
@@
 %
-This form is justified when considering the linear power spectrum, and
-follows when inserting the linearly evolving density contrast $\hat \delta(\vec
-k; \chi) = D_+(\chi) \hat \delta_0(\vec k)$ into equation~(\ref{eq:p_m}), where
-$\delta_0$ is the present-day linearly extrapolated density contrast, and $D_+$
-the linear growth factor with $D_+(0) = 1$. This is a good approximation
-also in the non-linear case as shown in \cite{2016arXiv161200770K}.
-
 With this, equation~(\ref{eq:C_ell_full}) is written as
@@
                 \frac{q_i(\chi)}{a(\chi)} {\rm J}_{\ell+1/2}(k \chi)
-                %\nonumber \\
-                 %& \times
+                \nonumber \\
+                 & \times
                 \int_{0}^\infty \frac{{\rm d} \chi^\prime}{{\chi^\prime}^{3/2}}
@@
 %
+We replaced the upper limits of the distance integral with infinity. \mk{Comment on this.}
 Note that this equation has a pre-factor $\ellbar^2(\ell, 2)$ corresponding to a spin-2 field, in contrast
@@
   \lim_{\varepsilon \rightarrow 0} \int_0^\infty {\rm d} x \, {\rm e}^{-\epsilon (x - \nu)} g(x) {\rm J}_\nu(x)
+  %\approx g(\nu) - \frac 1 2 g^{\prime\prime}(\nu) - \frac \nu 6 g^{\prime\prime\prime}(\nu) 
   \approx g(\nu) - \frac 1 2 \left.\frac{{\rm d}^2 g}{{\rm d} x^2}\right|_{x=\nu}
-                 - \frac \nu 6 \left.\frac{{\rm d}^3 g}{{\rm d} x^3}\right|_{x=\nu},
+                 - \frac \nu 6 \left.\frac{{\rm d}^3 g}{{\rm d} x^3}\right|_{x=\nu} ,
 \end{equation}
@@
 with $g(x) = k^{-1} f(k, \chi)$, $\chi=x/k$, and its derivatives $g^{(n)}(x) =
-k^{-1-n} f^{(n)}(k, \chi)$ for a given $k$, where the derivatives of $f$
-are with respect to the second argument $\chi$. In this series expansion, the
-replacement of the integral with the evaluation of $g$ and its derivatives at
-the maximum of the Bessel function is a good approximation of the integral if
-$g$ is varying more slowly than the oscillating Bessel function.
-% [Check this].
-As we will show below, $f$ is a slowly varying function of the comoving
-distance. In our case the projection kernel is
+k^{-1-n} f^{(n)}(k, \chi)$ for a given $k$. In our case the projection kernel is
 %
@@
 %
-In the tomographic case, the index $i$ is added to $q$ and $f$.
-%
-Replacing both distance integrals in equation~(\ref{eq:C_ell_full_Pk}) by their
-Taylor-expansions around the maxima $\nu(\ell) = \ell + 1/2$ of the two Bessel
-functions, which are $k \chi$ and $k \chi^\prime$, respectively, yields
+\mk{In the tomographic case, the index $i$ is added to $q$ and $f$.}
+%
+Replacing both distance integrals in equation~(\ref{eq:C_ell_full_Pk}) by their Taylor-expansions around $\nu = k \chi$ and $\nu = k \chi^\prime$,
+respectively, yields
 %
@@
     \left[ f_i(k, \chi) - \frac{1}{2 k^2} f_i^{\prime\prime}(k, \chi)
-      - \frac{\nu(\ell)}{6 k^3} f_i^{\prime\prime\prime}(k, \chi) + \ldots \right]
+      - \frac{\nu}{6 k^3} f_i^{\prime\prime\prime}(k, \chi) + \ldots \right]
     %\nonumber \\
@@
     \left[ f_j(k, \chi) - \frac{1}{2 k^2} f_j^{\prime\prime}(k, \chi)
-    - \frac{\nu(\ell)}{6 k^3} f_j^{\prime\prime\prime}(k, \chi) + \ldots \right] \, .
+    - \frac{\nu}{6 k^3} f_j^{\prime\prime\prime}(k, \chi) + \ldots \right] \, .
   \label{eq:C_ell_limber2_dk}
@@
   C^\gamma_{ij}(\ell) \approx & \, C^\gamma_{{\rm L1}, ij}(\ell) + C^\gamma_{{\rm L2}, ij}(\ell)
+      \nonumber \\
+    = & \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2
+    \int_0^\infty {\rm d} \chi \, \chi^3 \, % P_{\rm m}\left( k \right)
+    %\Bigg\{
+    \left\{
+    (f_i f_j)(\nu/\chi, \chi)
+    %\right.
       %\nonumber \\
-    = %&
-    \frac{\ellbar^2(\ell, 2)}{\nu^4(\ell)} \, \pref^2
-    \int_0^\infty {\rm d} \chi \, \chi^3 \, % P_{\rm m}\left( k \right)
-    \Bigg\{
-    %\left\{
-    (f_i f_j)(\nu(\ell)/\chi, \chi)
-    %\right.
-      \nonumber \\
-    &
+    %&
     %\left.
-     - \frac 1 {\nu^2(\ell)}
-    \left[ \frac{\chi^2}{2} \left( f^{}_i f^{\prime\prime}_j + f_i^{\prime\prime} f^{}_j \right)(\nu(\ell)/\chi, \chi)
-     + \frac{\chi^3}{6} \left( f^{}_i f^{\prime\prime\prime}_j + f^{\prime\prime\prime}_i f^{}_j \right)(\nu(\ell)/\chi, \chi)
+     - \frac 1 {\nu^2} \left[ \frac{\chi^2}{2} \left( f^{}_i f^{\prime\prime}_j + f_i^{\prime\prime} f^{}_j \right)(\nu/\chi, \chi)
+    + \frac{\chi^3}{6} \left( f^{}_i f^{\prime\prime\prime}_j + f^{\prime\prime\prime}_i f^{}_j \right)(\nu/\chi, \chi)
     \right]
-    + {\cal O}(\nu^{-4})
-    %\right\}
-    \Bigg\}
-    \, .
+    \right\} \, .
+    %\Bigg\}
   \label{eq:C_ell_limber12_dr}
@@
 weak gravitational lensing. We retrieve the (spherical) standard expression by
-inserting back the projection kernel (equation~\ref{eq:f_LA08}),
-%
-\begin{align}
-  C^\gamma_{{\rm L1}, ij}(\ell) = & \, \frac{\ellbar^2(\ell, 2)}{\nu^4(\ell)} \, \pref^2 \int {\rm d} \chi \frac{ q_i(\chi) q_j(\chi) }{a^2(\chi)}
-  P_{\rm m}\left(\frac{\nu(\ell)}{\chi}; \chi\right) . \Label{ExtL1Sph}
+inserting back the projection kernel equation~(\ref{eq:f_LA08}) and the time-dependent
+power spectrum,
+%
+\begin{align}
+  C^\gamma_{{\rm L1}, ij}(\ell) = & \, \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2 \int {\rm d} \chi \frac{ q_i(\chi) q_j(\chi) }{a^2(\chi)}
+  P_{\rm m}\left(\frac{\nu}{\chi}; \chi\right).
   \label{eq:C_ell_limber1}
@@
 The second-order Limber term in equation~(\ref{eq:C_ell_limber12_dr}) has an additional
-$\nu^{-2}$-dependence, and is therefore strongly suppressed for large $\ell$,
-%
-\begin{align}
-  C^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2(\ell)} \, \frac{\ellbar^2(\ell, 2)}{\nu^4(\ell)} \,
-    \frac{\pref^2}{2}
-    \int {\rm d} \chi \, \chi^{7/2} a^{-1} P^{1/2}_{\rm m}\left(\frac{\nu(\ell)}\chi; \chi\right)
+$\nu^{-2}$-dependence, and is therefore strongly suppressed for large $\ell$.
+%
+\begin{align}
+  C^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2} \, \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2
+    \int {\rm d} \chi \, \chi^{2} a^{-2} \sqrt{P_{\rm m}\left(\frac\nu\chi; \chi\right)}
     %\nonumber \\
     %& \times
-    \left[ q^{}_i f^{\prime\prime}_j + f^{\prime\prime}_i q^{}_j
+    \frac{a(\chi)}{2} \chi^{3/2} \left[ q^{}_i f^{\prime\prime}_j + f^{\prime\prime}_i q^{}_j
       + \frac{\chi}{3} \left( q^{}_i f^{\prime\prime\prime}_j + f^{\prime\prime\prime}_i q^{}_j
       \right)
-    \right](\nu(\ell)/\chi, \chi) \, . 
+    \right](\nu/\chi, \chi) \, .
   \label{eq:C_ell_limber2_dr} 
@@
 sensitive to the set-up, for example the step size. The tabulation and
-interpolation of those derivatives is time-consuming since they depend on two
+interpolation of those derivatives is time-taking since they depend on two
 arguments, $\nu$ and $\chi$. In the following section, we will separate the
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Approximation for small $\ell$}
-\label{sec:factor_D}
+\subsubsection{Time-independent power spectrum separation}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-To further develop equation~(\ref{eq:P_geom_mean}), we divide out the growth factor of
-the power spectrum,
-%
-\begin{equation}
- P_{\rm m}(k, \chi) =: D^2_+(\chi) \tilde P_{\rm m}(k, \chi).
+To further develop equation~(\ref{eq:P_geom_mean}), we divide out the growth factor to
+define a redshift-independent power spectrum $P_{\rm m}(k)$,
+%
+\begin{equation}
+ P_{\rm m}(k, \chi) =: D_+(\chi) P_{\rm m}(k).
   \label{eq:P_k_chi_sep_s}
@@
 %
-The function $\tilde P_{\rm m}$ is in general not time-independent, except
-in the case of a linear matter power spectrum in the absence of massive
-neutrinos, and in General Relativity. However, the second-order Limber terms
-are expected to be important only for small $\ell$, since for large $\ell$ the first-order
-Limber equation (\ref{eq:C_ell_limber1}) is dominant. Eq.~(\ref{eq:P_k_chi_sep_s})
-becomes a good approximation for small $\ell$, since that means either small
-$k$ where the evolution is linear, or small $\chi$, where the lensing
-efficiency is small. The accuracy of a very nearby tomographic bin with low
-mean redshift should be further examined, but this is not the case for
-CFHTLenS.
-
-With the definition (\ref{eq:P_k_chi_sep_s}), we factor out the function
-$\tilde P_{\rm m}(k, \chi)$ from equation~(\ref{eq:f_LA08}), and we define the
-separated kernel function $f_{\rm s}$ as
-%
-\begin{equation}
-  f_{\rm s}(\chi) = D_+(\chi) a^{-1}(\chi) \chi^{-3/2} q(\chi) \, .
+This is not exact, since some non-linear prescriptions of the power spectrum
+depend on redshift other than the growth factor, for example when computing the
+non-linear scale $k_{\rm NL}(z)$ for \texttt{halofit} \citep{2003MNRAS.341.1311S}.
+
+With this approximation, the \mk{$\chi$-independent term $P_{\rm m}(k)$}
+factors out from equation~(\ref{eq:f_LA08}), and we define the separated kernel
+function $f_{\rm s}$ as
+%
+\begin{equation}
+  f_{\rm s}(\chi) = D_+(\chi) a^{-1}(\chi) \chi^{-3/2} q(\chi) \,
   \label{eq:f_LA08_s}
@@
 %
-The Limber equation up to second order of the shear power spectrum can then be approximated as
-%
-\begin{align}
-  C^\gamma_{ij}(\ell) = & \, C^\gamma_{{\rm L1}, ij}(\ell) 
-    \nonumber \\
-    & - \frac 1 {\nu^2(\ell)} \, \frac{\ellbar^2(\ell, 2)}{\nu^4(\ell)} \,
-    \frac{\pref^2}{2}
-    \int {\rm d} \chi \, \chi^{7/2} a^{-1}(\chi) D_+^{-1}(\chi) P_{\rm m}\left(\frac{\nu(\ell)}\chi; \chi\right)
+The second-order Limber term of the shear power spectrum can then be simplified to
+%
+\begin{align}
+  C^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2} \, \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2
+    \int {\rm d} \chi \, \chi^{2} a^{-2} P_{\rm m}\left(\frac\nu\chi; \chi\right)
     %\nonumber \\
     %& \times
+    \frac {a(\chi)}{2 D_+(\chi)} \chi^{3/2}
     \left[ q^{}_i f^{\prime\prime}_{{\rm s} j} + f^{\prime\prime}_{{\rm s}i} q^{}_j
@@
       \right)
-    \right](\chi) \, . \Label{ExtL2Sph}
+    \right](\chi)
   \label{eq:C_ell_limber2_dr_s}
@@
 We compute the numerical higher derivatives as follows. The functions $f_{\rm
-s}(\chi)$ are fitted as power laws with index $\approx -1.5$, which is
-expected if the growth suppression factor $D_+(a)/a$ varies slowly with $\chi$,
-and the lensing efficiency $q \approx 1$ for small and medium $\chi$, given the
-CFHTLenS redshift range. The fit is carried out between $\chi_{\rm min} = 0.001
-\, {\rm Mpc}/h$ and $\chi_{\rm max} = 500 \, \mbox{Mpc}/h$. At larger comoving
-distances the kernel decreases faster than a power law, so we exclude this
-range from the fit. Even though on those scales the derivatives are larger due
-to the steeper decline, the associated errors are very small as these scales
-are down-weighed by the kernel function $f_{\rm s}$ itself. At $\chi = 500 \,
-\mbox{Mpc}/h$ the filter function is less than $10^{-4}$ of its value 
-at $1$\,Mpc$/h$.
-
-\subsection{Flat-sky}
+s}(\chi)$ are fit as power laws with index $\approx 1.5$. The fit is
+performed between $\chi_{\rm min} = 0.001 {\rm Mpc}/h$ and $\chi_{\rm max} =
+500 \mbox{Mpc}/h$. At larger comoving distances the kernel decreases faster
+than a power law, so we exclude this range from the fit. Even though the
+derivaties are larger due to the steeper decline, the associated errors are
+very small as these scales are down-weighed by the kernel function $f_{\rm
+s}$ itself. At $\chi = 500 \, \mbox{Mpc}/h$ the filter function is less than
+$10^{-4}$ of its value of unity at $1$\,Mpc$/h$.
+
+%The error between filter and power-law fit
+%becomes larger than $50\%$ only for scales larger than $1,500 \mbox{Mpc}/h$. On the angular
+%scales where the second-order Limber approximation significantly contributes to the shear
+%power spectrum, $\ell \le 100$, this corresponds to $k < 0.03 h/$Mpc, linear
+%scales where the 3D power spectrum is small and does not strongly contribute to the lensing
+%power spectrum.
+
+\subsection{Flat sky}
 \label{sec:Limber_flat_sky}
@@
 The extended flat-sky Limber approximation is readily derived from the
-spherical case equations~(\ref{eq:C_ell_limber1}, \ref{eq:C_ell_limber2_dr_s}), by
-replacing the pre-factor $\ellbar^2(\ell, 2)$ with $\ell^4$,
-%
-\begin{align}
-  P^\gamma_{{\rm L1}, ij}(\ell) = & \, p(\ell) \, \pref^2 \int {\rm d} \chi \frac{ q_i(\chi) q_j(\chi) }{a^2(\chi)}
-  P_{\rm m}\left(\frac{\nu(\ell)}{\chi}; \chi\right);
+spherical case, by replacing the pre-factor $\ellbar^2(\ell, 2)$ with $\ell^4$,
+%
+\begin{align}
+  P^\gamma_{{\rm L1}, ij}(\ell) = & \, \frac{\ell^4}{\nu^4} \, \pref^2 \int {\rm d} \chi \frac{ q_i(\chi) q_j(\chi) }{a^2(\chi)}
+  P_{\rm m}\left(k = \frac{\nu}{\chi}; \chi\right);
   \label{eq:P_ell_limber1}
   \\
-    P^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2(\ell)} \, p(\ell) \, \frac{\pref^2}{2}
-    \int {\rm d} \chi \, \chi^{7/2} a^{-1}(\chi) D_+^{-1}(\chi) P_{\rm m}\left(\frac{\nu(\ell)}\chi; \chi\right)
+    P^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2} \, \frac{\ell^4}{\nu^4} \, \pref^2
+    \int {\rm d} \chi \, \chi^{2} a^{-2} P_{\rm m}\left(k = \frac\nu\chi; \chi\right)
     %\nonumber \\
     %& \times
-    \left[ q^{}_i f^{\prime\prime}_{{\rm s}j} + f^{\prime\prime}_{{\rm s}i} q^{}_j  
+    \frac{a(\chi)}{2 D^{-1}_+(\chi)} \chi^{3/2} \left[ q^{}_i f^{\prime\prime}_{{\rm s}j} + f^{\prime\prime}_{{\rm s}i} q^{}_j  
       + \frac{\chi}{3} \left( q^{}_i f^{\prime\prime\prime}_{{\rm s}j} + f^{\prime\prime\prime}_{{\rm s}i} q^{}_j
@@
 %
-Further approximations can be made for the pre-factor $p(\ell) = \ell^4/\nu^4(\ell)$ and $\nu(\ell)$:
+Further approximations are commonly made for the pre-factor $p(\ell) = \ell^4/\nu^4$ and $\nu(\ell)$:
 %
 \begin{enumerate}
-  \item $p(\ell) = 1$, this corresponds to $\nu(\ell) = \ell$, which is the
-    \emph{standard} Limber approximation \LabelTxt{L1Fl} Until recently,
-  i.e.~for all pre-2014 CFHTLenS results and DLS
-  \citep{jee/etal:2016} analyses, this was the approximation of choice. Note that
-  we do not discuss the second-order Limber approximation with $p(\ell)=1$.
-  %
-  \item $p(\ell) = \ell^4/(\ell + 1/2)^4$. This corresponds to the
-  \emph{extended} Limber approximation \LabelTxt{ExtL1Fl, ExtL2Fl} with
-  $\nu(\ell) = \ell + 1/2$; however the following case is typically employed:
-  %
-  \item $p(\ell) = 1$, but keeping as argument of the power spectrum $\nu(\ell) = \ell + 1/2$. This is
+  \item $p(\ell) = 1$, this corresponds to $\nu(\ell) = \ell$, which is the \emph{standard} Limber approximation.
+    Until recently, i.e.~for all pre-2014 CFHTLenS results, this was the approximation of choice.
+  \item $p(\ell) = \ell^4/(\ell + 1/2)^4$. This corresponds to the \emph{extended} Limber
+    approximation with $\nu(\ell) = \ell + 1/2$; however the following case is typically employed:
+  \item $p(\ell) = 1$, with $\nu = \ell + 1/2$. This is
     a \emph{hybrid} between
-    standard and extended Limber approximation~\LabelTxt{ExtL1FlHyb, ExtL2FlHyb}, and the first-order case 
-    was used in \cite{KiDS-450,joudaki/etal:2016,joudaki/etal:2017,abbott/etal:2016}. As is shown
-    below, this is a better approximation to the full projection than case (ii). In equation~(\ref{eq:P_ell_limber2})
-    the second-order suppression factor is also left to be $\nu^{-2}(\ell) = (\ell + 1/2)^{-2}$, providing
-    a slightly more accurate approximation compared to $\nu^{-2}(\ell) = \ell^{-2}$.
+    standard and extended Limber approximation, and was used in \cite{KiDS-450,joudaki/etal:2016}. As is shown
+    later, this is a better approximation to the full projection than case (ii).
 \end{enumerate}
+%
+\ch{Would this section be clearer if we had $p(\ell)$ in the equations instead of 
+$\ell^4/\nu^4$?}
+
+% (i)  Standard Flat
+% (ii) Extended Flat
+% (iii) Extended Flat Hybrid
 
@@
 
-In Fig.~\ref{fig:Cl_cases} we present the full spherical projection of the
-shear power spectrum in comparison to shear power spectra derived assuming the
-range of different approximations listed in Table~\ref{tab:cases}.  The adopted
-redshift distribution corresponds to CFHTLenS \citep{CFHTLenS-2pt-notomo} and
-we assume their best-fit flat $\Lambda$CDM cosmology with $\Omega_{\rm
-m}=0.279$, $\Omega_{\rm b}=0.046$, $\sigma_8=0.79$, $h=0.701$, $n_{\rm
-s}=0.96$. For $\ell > 100$ we find that all shear power spectra predictions
-agree with the full spherical solution to better than one percent, with the
-majority of the approximations tested accurate to better than 0.1 per cent.
-
-Considering first the flat-sky cases, the standard first-order Limber
-approximation, (L1Fl), that was adopted for all pre-2014 CFHTLenS analyses and DLS analyses, we
-find it to be accurate to better than 10\% for $\ell>3$, converging slowly to the
-true projection with percent level precison at $\ell>100$. For the extended
-Limber approximations `hybrid' cases (ExtL1FlHyb and ExtL2FlHyb), despite
-decreased accuracy for $\ell < 8$ in comparison to the standard first-order
-Limber case, the errors with respect to the true power spectrum decrease much
-faster, as $\ell^{-2}$, such that percent-level precision is reached at
-$\ell>15$.  The first-order extended Limber approximation `hybrid' cases
-(ExtL1FlHyb) was adopted by \citet{joudaki/etal:2016}, \citet{joudaki/etal:2017}, DES-SV \citep{abbott/etal:2016} and
-\cite{KiDS-450}\footnote{We confirm that there is a typographical error in
-equation 4 of \cite{KiDS-450} and in equation 2 of \citet{abbott/etal:2016} (private communication with Joe Zuntz) 
-which should include the extra term of `+0.5' in
-$\nu(\ell)$ that was incorporated in both cosmological analyses.}.
-
-The outlier in the flat-sky cases is the extended Limber approximation
-(ExtL1Fl) which performs relatively poorly, and reaches 10\% precision only at
-$\ell > 100$. The same slow convergence can be observed for the corresponding
-second-order flat case, ExtL2Fl. To our knowledge this form of the flat-sky
-approximation has not been used in any cosmic shear studies to date, and should
-not be used in any future studies given these results.  The poor behaviour of
-this case, in comparison with the `hybrid' case, (e.g ExtL1FlHyb) can be
-understood by considering Taylor expansions of the different pre-factors.  The
-spherical pre-factor,
-%
+In Fig.~\ref{fig:Cl_cases} we present the full spherical projection of the shear power spectrum in comparison to shear power spectra derived assuming
+the range of different approximations listed in Table~\ref{tab:cases}.  The adopted redshift distribution corresponds to CFHTLenS
+\citep{CFHTLenS-2pt-notomo} and we assume their best-fit flat $\Lambda$CDM cosmology with $\Omega_{\rm m}=0.279$, $\Omega_{\rm b}=0.046$, $\sigma_8=0.79$, $H_0=0.701$, $n_{\rm s}=0.96$. 
+For $\ell > 100$ we find that all shear power spectra predictions agree with the full spherical solution to better than one percent, with the majority of the approximations tested accurate to better than 0.1 per cent.
+
+Considering first the flat-sky cases, the standard first-order Limber approximation, (L1Fl), that was adopted for all pre-2014 CFHTLenS analyses, we find to be 
+accurate to better than 10\% for $\ell>3$, converging slowly to the true projection with percent level precison at $\ell>100$. 
+For the extended Limber approximations `hybrid' cases (ExtL1FlHyb and ExtL2FlHyb), despite decreased accuracy
+for $\ell < 8$ in comparison to the standard first-order Limber case, the errors with respect to
+the true power spectrum decrease much faster, as $\ell^{-2}$, such that percent-level precision is reached at $\ell>15$.
+The first-order extended Limber approximation `hybrid' cases (ExtL1FlHyb) was adopted by both \citet{joudaki/etal:2016} and \cite{KiDS-450}\footnote{We confirm that there is a typographical error in equation 4 of \cite{KiDS-450} which should include the extra term of `+0.5' in $\nu(\ell)$ that was incorporated in the cosmological analysis.}.
+
+The outlier in the flat-sky cases is the extended Limber approximation (ExtL1Fl) which performs relatively poorly, and
+reaches 10\% precision only at $\ell > 100$. The same slow convergence can be
+observed for the corresponding second-order flat case, ExtL2Fl.
+To our knowledge this form of the flat-sky approximation has not been used in any cosmic shear studies to date, and should not be used in any future studies given these results.
+The poor behaviour of this case, in comparison with the `hybrid' case, (e.g ExtL1FlHyb) can be understood by considering Taylor expansions of the different pre-factors.
+The spherical pre-factor,
 \begin{equation}
@@
 \end{equation}
-%
 can be compared to the flat-sky extended Limber pre-factor
-%
 \begin{equation}
@@
 \end{equation} 
-%
-showing it to be more deviant from the full spherical solution, than the
-`hybrid' $p(\ell) = 1$ case.
+showing it to be more deviant from the full spherical solution, than the `hybrid' $p(\ell) = 1$ case.
 
@@
 > 3$.  The numerical calculation of the second-order extended Limber
-approximation is a factor of 15 times faster than the calculation of the
-full spherical solution (averaged over the first $18$ $\ell$-modes). We
-note that the sub-$0.1\%$-fluctuations seen in the right panel of
-Fig.~\ref{fig:Cl_cases} is due to numerical noise arising from numerical
-integration errors in the calculation of the full spherical solution when $\ell
-> 20$.
-
-Compared to the statistical power of current and future surveys, all
-approximations discussed here are subdominant to the cosmic variance, $\Delta
-C(\ell) / C(\ell) = [f_{\rm sky} (2 \ell + 1)]^{-1/2}$
-\citep{1992ApJ...388..272K}, where $f_{\rm sky}$ is the fraction of sky observed
-by the survey. The uncertainties from the Limber approximation in the case of
-ExtL2Sph is an order of magnitude below the cosmic variance of a Euclid-like
-survey (sky area $15,000$ square degrees) for all $\ell$.
+approximation is a factor of \mk{15 times} faster than the calculation of the
+full spherical solution \mk{(averaged over the first $18$ $\ell$-modes).} We note that the
+\mk{sub-$0.1\%$}-noise seen in the right panel of Fig.~\ref{fig:Cl_cases} is
+due to numerical noise arising from numerical integration errors in the
+calculation of the full spherical solution when $\ell > 20$.
+
+% Compuation times:
+% l>=20, 20 modes
+% full 37s
+% L2   2.14s
+% L1   0.8s
 
@@
 
-  \caption{\label{fig:Cl_cases}%
-        The shear power spectrum for different approximations listed in Table~\ref{tab:cases}.
-        Limber to first order: standard with flat-sky (L1Fl),
+  \caption{\label{fig:Cl_cases}The shear power spectrum for different approximations listed in Table~\ref{tab:cases}. Limber to first order: standard with flat-sky (L1Fl),
         extended for flat sky (ExtL1Fl), extended hybrid for flat sky (ExtL1FlHyb),
@@
         and extended spherical expansion (ExtL2Sph); full (exact) spherical projection (FullSph).
-        The left panel shows the total shear power spectrum.  The right panel shows the fractional difference
-        resulting from each approximation, 
-        relative to the full spherical projection of the shear power spectrum. The two light grey curves on the
-        top show the cosmic variance for KiDS- and Euclid-like surveys with areas of $1,500$ and $15,000$
-        square degrees, respectively.
+        The left panel shows the total shear power spectrum.  The right panel shows the fractional difference resulting from each approximation, 
+        relative to the full spherical projection of the shear power spectrum.
         }
 \end{figure}
+
+% nicaea            Kil+17      'Comment paper' Plot color    Kit+16                Plot color    my comment
+% limber            L1Fl        Kst             black         Limber+Tl=1+Flat-sky  blue
+% limber_la08       ExtL1Fl     ELF             blue
+% limber_la08_hyb   ExtL1FlHyb  ESt             magenta                                           pre-factor~1 despite nu=ell+1/2
+% limber_la08_sph   ExtL1Sph    ELS             cyan
+% limber2_la08      ExtL2Fl
+% limber2_la08_hyb  ExtL2FlHyb
+% limber2_la08_sph  ExtL2Sph
+% full              Full
 
@@
 \begin{centering}
-  %
-  \caption{\label{tab:cases}The shear power spectrum approximations studied in this paper. 'ID' is the label
-    used in the text and figures.
+  \caption{\label{tab:cases}The shear power spectrum approximations studied in this paper. 'ID' is the abbrevation used in the figures.
     The third column shows the power-spectrum pre-factor $p(\ell)$. }  
-    %
-    \begin{tabular}{|l|l|c|c|c|p{0.21\textwidth}}
+    \begin{tabular}{|l|l|c|c|c}
   \hline
-  Case & ID & equation & $p(\ell)$ & $\nu(\ell)$ & Comment \\ \hline
+  Case & ID & equation & $p(\ell)$ & $\nu(\ell)$ \\ \hline
   % 
   $1^{\rm st}$-order standard Limber, flat sky & L1Fl & (\ref{eq:P_ell_limber1}) + (i)
-    & $1$ & $\ell$ & Pre-2014 CFHTLenS and DLS \\ \hline
+    & $1$ & $\ell$ \\ \hline
   %
   $1^{\rm st}$-order extended Limber, flat sky & ExtL1Fl & (\ref{eq:P_ell_limber1}) + (ii)
-    & $\frac{\ell^4}{(\ell+1/2)^4}$ & $\ell + \frac 1 2$ & Converges only with ${\cal O}(\ell^{-1})$ \\ \hline
+    & $\ell^4/(\ell+1/2)^4$ & $\ell + 1/2$ \\ \hline
   %
   $1^{\rm st}$-order extended Limber, hybrid, flat sky & ExtL1FlHyb & (\ref{eq:P_ell_limber1}) + (iii)
-    & $1$ & $\ell + \frac 1 2$ & Post-2014 CFHTLenS, DES-SV and KiDS \\ \hline
+    & $1$ & $\ell + 1/2$ \\ \hline
   %
   $1^{\rm st}$-order extended Limber, spherical & ExtL1Sph & (\ref{eq:C_ell_limber1})
-    & $\frac{\ellbar^2(\ell, 2)}{(\ell+1/2)^4}$ & $\ell+ \frac 1 2$ & \\ \hline
+    & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ \\ \hline
   %
   $2^{\rm st}$-order extended Limber, flat sky & ExtL2Fl &  (\ref{eq:P_ell_limber1}) + (\ref{eq:P_ell_limber2}) + (iii)
-    & $\frac{\ell^4}{(\ell+1/2)^4}$ 
-    & $\ell+\frac 1 2$ & Converges only with ${\cal O}(\ell^{-1})$ \\ \hline
+    & $\ell^4/(\ell+1/2)^4$ 
+    & $\ell+1/2$ \\ \hline
   %
@@
     & $1$ 
-    & $\ell+ \frac 1 2$ & Best flat-sky approximation \\ \hline
+    & $\ell+1/2$ \\ \hline
   %
   $2^{\rm st}$-order extended Limber, spherical & ExtL2Sph & (\ref{eq:C_ell_limber1})+(\ref{eq:C_ell_limber2_dr_s})
-    & $\frac{\ellbar^2(\ell, 2)}{(\ell+1/2)^4}$ & $\ell+\frac 1 2$ & Best approximation \\ \hline
+    & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ \\ \hline
   %
   Full spherical & FullSph & (\ref{eq:C_ell_full}) &
-      - & - & Correct projection \\ \hline
+      $\ellbar^2(\ell, 2)$ & - \\ \hline
   %
@@
 galaxy shape catalogue. The baseline quantity is the two-point correlation
-function \citep{1991ApJ...370....1M, 1992ApJ...388..272K, BS01}, given by
+function \citep{1991ApJ...370....1M, 1992ApJ...388..272K,
+BS01}, given by
 %
@@
   % &
-  = \frac 1 {2\pi} \int {\rm d} \ell \, \ell \, {\rm J}_0(\ell
+  = \frac 1 {2\pi} \int {\rm d} \ell \, \ell {\rm J}_0(\ell
    \theta)
@@
   = \frac 1 {2\pi} \int
-   {\rm d} \ell \, \ell \, {\rm J}_4(\ell \theta)
+   {\rm d} \ell \, \ell {\rm J}_4(\ell \theta)
   P^\gamma(\ell).
@@
 %
-The flat-sky shear power spectrum $P^\gamma$ can be related to the underlying
-matter power spectrum through equation~(\ref{eq:P_ell_limber1}) when adopting a
-first-order extended Limber approximation, or equation~(\ref{eq:P_ell_limber2})
-when adopting a second-order extended Limber approximation.
-
-On a sphere, correlation functions formally cannot be related to the power
-spectrum by the Hankel transform in equation~(\ref{eqn:xiGG}), and should
-be replaced by the spherical transform \citep{1973ApJ...185..413P}
-%
-\begin{equation}
- \xi_+(\theta) = \left\langle \gamma \gamma^\ast \right\rangle(\theta)
-  =  \frac 1{4\pi} \sum\limits_{\ell=2}^\infty (2 \ell + 1) C^\gamma(\ell) {\rm P}_\ell[\cos(\theta)],
-  \label{eq:xi_Legendre}
-\end{equation}
-%
-where ${\rm P}_\ell(x)$ are the Legendre polynomials in $x$ of order $\ell$. This equation is easily derived
-using the harmonics expansion of the shear (equation~\ref{eq:gamma_harm_exp}) and the orthogonality relation of
-the spherical harmonics (\ref{eq:Yellm_ortho}).
-
-The spherical power spectrum is formally not defined for non-integer $\ell$
-\citep[see][for alternative spherical-sky formulae for the two-point
-correlation function]{2005PhRvD..72b3516C}, as functions defined on the
-sphere are necessarily periodic.
-As we have shown in section~\ref{sec:comp}, however, the spherical second-order
-extended Limber approximation provides a percent-level precision representation
-of the full spherical projection for $\ell > 3$.
-The spherical pre-factor $\ellbar(\ell, 2)$ (equation~\ref{eq:ellbar}) can be
-generalised to non-integer arguments and is positive for $\ell \ge 2$. We can
-thus use the spherical power spectrum with
-the Hankel transformation in equation~(\ref{eqn:xiGG}) to compute the two-point correlation
-functions. This has the advantage being able to employ fast FFT numerical implementations of
-the Hankel tranforms \citep{fftlog}, when Monte-Carlo sampling.
-
-We compare predictions for the two-point shear correlation function using
-the Hankel transformation and the full spherical transformation in
-Fig.~\ref{fig:xi_p_legendre}. We show the full projection and the best
-approximation, ExtL2Sph. Note that for the `FullSph' case we replace the full
-projection with ExtL2Sph for $\ell > 200$ to reduce computation time.
-%
-We find that the Hankel transform (equation~\ref{eqn:xiGG}) is accurate to better than $2$ percent level.
-%
-The difference between the second-order Limber and full projection solution using the
-spherical transform (equation~\ref{eq:xi_Legendre}) is well below one percent
-for $\vartheta < 200$ arcminutes.
-The red circles in Fig.~\ref{fig:xi_p_legendre} present the limit of
-precision that we can achieve with the current fast Hankel transform implementation
-for the correlation function. The green line shows the limit of the
-second-order Limber approximation on the correlation function.
-
-Figure~\ref{fig:xi_pm} shows the two-point correlation functions $\xi_+$ (left)
-and $\xi_-$ (right) using the different cases for the shear power spectrum
-listed in Table~\ref{tab:cases}. The component $\xi_+$ is calculated with the
-appropriate transformation, i.e.~Hankel for the flat cases, and {spherical
-involving Legendre polynomials} for the spherical cases. For $\xi_-$ which is
-less dominated by large scales and thus Limber and flat-sky approximations, in
-comparison to $\xi_+$, we use the Hankel transform in all cases. In addition,
-for $\xi_-$ the approximation `ExtL2Sph' is our reference case. The adopted
-CFHTLenS redshift distribution and fiducial cosmological model are the same as
-in Figure~\ref{fig:Cl_cases}. As is clear by the red dotted curve, using the
+where ${\rm J}_\nu$ first-kind Bessel function of order $\nu$. The flat-sky
+shear power spectrum $P^\gamma$ an be related to the underlying matter power
+spectrum through equation~(\ref{eq:P_ell_limber1}) when adopting a first-order
+extended Limber approximation, or equation~(\ref{eq:P_ell_limber2}) when adopting
+a second-order extended Limber approximation.
+
+On a sphere, correlation functions cannot be related to the power spectrum by
+the Hankel transform in equation~(\ref{eqn:xiGG}), as the spherical power
+spectrum is formally not defined for non-integer $\ell$ \citep[see][for
+alternative spherical-sky formulae for the two-point correlation
+function]{2005PhRvD..72b3516C}. In particular, the spherical Bessel functions
+necessary to compute the full projection in equation~(\ref{eq:C_ell_full}) is
+defined only for integer order $\ell$. \mk{I think this is actually not true,
+since J$_\nu$ can be computed for fractional $\nu$, and then one could use the
+identity (\ref{eq:jJ}). Or is it?}.
+
+As we have shown in section~\ref{sec:comp}, however, the spherical
+second-order extended Limber approximation provides a percent-level precision
+representation of the full spherical projection for $\ell > 3$.  
+In the Limber approximations the Bessel functions \mk{are expanded into}
+polynomials, allowing for arbitrary wave modes $\ell$. The spherical pre-factor
+$\ellbar(\ell, 2)$ (equation~\ref{eq:ellbar}) can be generalised to non-integer
+arguments and is positive for $\ell \le 2$. We can thus use the spherical power
+spectrum in the Limber approximations for the Hankel transformation to compute
+the two-point correlation functions.  We therefore do not
+present predictions for the two-point shear correlation function using the full
+spherical projection, instead choosing the spherical second-order extended
+Limber approximation (ExtL2Sph) as our reference in this case.
+
+Figure.~\ref{fig:xi_pm} presents the two-point correlation functions
+$\xi_+$ (left) and $\xi_-$ (right) using the different cases for the shear
+power spectrum listed in Table~\ref{tab:cases}. The adopted CFHTLenS redshift
+distribution and fiducial cosmological model are the same as in
+Figure.~\ref{fig:Cl_cases}. As is clear by the red dotted curve, using the
 Planck cosmology \citep{2015arXiv150201589P} induces a significant change in
-the amplitude of the shear correlation function in comparison to the different
-projection methods.
-
-\begin{figure}
-
-  \begin{center}
-    \resizebox{1.0\hsize}{!}{
-      \includegraphics{figures/xi_p_legendre}
-      \hspace*{2em}
-      \includegraphics{figures/xi_p_legendre_delta}
-    }
-  \end{center}
-
-  \caption{\emph{Left panel:} The shear correlation function component $\xi_+$
-for the ExtL2Sph projection using the spherical transform (green line for
-ExtL2Sph, grey squares for FullSph), compared to the flat-sky Hankel transform
-of ExtL2Sph (red circles). \emph{Right panel:} The relative difference compared
-to the full spherical case FullSph of ExtL2Sph with spherical transform (green
-line), and Hankel transform (red circles).}
-
-  \label{fig:xi_p_legendre}
-
-\end{figure}
+the amplitude of the shear correlation function in comparison to the different projection
+methods.
 
@@
       \includegraphics{figures/xi_p_comp}
-      \hspace*{2em}
       \includegraphics{figures/xi_m_comp}
@@
       \includegraphics{figures/xi_p_delta}
-      \hspace*{2em}
       \includegraphics{figures/xi_m_delta}
@@
 
-  \caption{The two-point shear correlation functions $\xi_+$ (\emph{left}) and $\xi_-$ (\emph{right}).
-  In the spherical cases (ExtL1Sph, ExtL2Sph, FullSph), $\xi_+$ has been computed using the spherical
-  transform (equation~\ref{eq:xi_Legendre}). For the flat cases, and all instances of $\xi_-$, the Hankel transform
-  in equation~(\ref{eqn:xiGG}) was used.
-  The upper panels
+  \caption{The two-point shear correlation functions $\xi_+$ (\emph{left}) and $\xi_-$ (\emph{right}).  The upper panels
   show the total shear correlation functions for the range of cases listed in Table~\ref{tab:cases}.
@@
 The authors thank Tommaso Giannantonio, Sarah Bridle, Ami Choi, Donnacha Kirk,
-Lance Miller, Benjamin Joachimi, Chris Blake, Joe Zuntz, Joanne Cohn, Alex Hall and Adam Amara for very helpful
-discussions. This work was financially supported by the DFG (Emmy Noether grant
-Hi 1495/2-1; SI 1769/1-1; TR33 `The Dark Universe'), the Alexander von Humboldt
-Foundation, the ERC (grants 279396, 647112), the Seventh Framework Programme of
-the European Commission (Marie Sklodwoska Curie Fellowship grant 656869), the
-Netherlands Organisation for Scientific Research (NWO) (grants 614.001.103),
-NSERC, CIfAR, and the World Premier International Research Center Initiative
-(WPI), MEXT, Japan. Parts of this research were conducted by the Australian
-Research Council Centre of Excellence for All-sky Astrophysics (CAASTRO),
-through project number CE110001020i, and by the German Federal
-Ministry for Economic Affairs and Energy (BMWi) under
-project no. 50QE1103.
+Lance Miller, Benjamin Joachimi, Chris Blake and Adam Amara for very helpful
+discussions. This work was financially supported by the DFG (Emmy Noether
+grant Hi 1495/2-1; SI 1769/1-1; TR33 `The Dark Universe'), the Alexander
+von Humboldt Foundation, the ERC (grants 279396, 647112), the Seventh Framework
+Programme of the European Commission (Marie Sklodwoska Curie Fellowship grant
+656869), NSERC and CIfAR.
+
+\ch{Check your acknowledgements}
 
@@
 
-To obtain the power spectrum of the lensing potential, 
-we insert the lensing projection (equation~\ref{eq:psi}) into the
+To obtain the power spectrum of the lensing potential for a flat Universe, 
+we insert the lensing projection (equation~\ref{eq:psi}) for $K=0$ into the
 inverse harmonics expansion (equation~\ref{eq:psi_harm_exp_inv}) and write the 3D potential
@@
   \psi_{\ell m} = \frac 2 {c^2} \int {\rm d} \Omega {\rm Y}^\ast_{\ell m}(\theta, \varphi)
-    \int_0^\infty \frac{{\rm d}\chi}{\chi} q(\chi) \int \frac{{\rm d}^3 k}{(2\pi)^3} \hat \Phi(\vec k; \chi) {\rm e}^{-{\rm i} \vec k \cdot \vec r}.
+    \int_0^{\chi_{\rm lim}} \frac{{\rm d}\chi}{\chi} q(\chi) \int \frac{{\rm d}^3 k}{(2\pi)^3} \hat \Phi(\vec k; \chi) {\rm e}^{-{\rm i} \vec k \vec r}.
 \end{equation}
@@
 \begin{equation}
-  {\rm e}^{{\rm i} \vec k \cdot \vec r} = 4 \pi \sum_{\ell=0}^{\infty} \sum_{m=-\ell}^{\ell}
+  {\rm e}^{{\rm i} \vec k \vec r} = 4 \pi \sum_{\ell=0}^{\infty} \sum_{m=-\ell}^{\ell}
     {\rm i}^\ell \, {\rm j}_\ell(k \chi)
@@
 \begin{equation}
-  \psi_{\ell m} = \frac {{\rm i}^\ell}{c^2 \pi^2} \int_0^\infty \frac{{\rm d}\chi}{\chi} q(\chi) \int {\rm d}^3 k \,
+  \psi_{\ell m} = \frac {{\rm i}^\ell}{c^2 \pi^2} \int_0^{\chi_{\rm lim}} \frac{{\rm d}\chi}{\chi} q(\chi) \int {\rm d}^3 k \,
     \hat \Phi(\vec k; \chi) {\rm j}_\ell(k \chi) {\rm Y}_{\ell m}(\theta_k, \varphi_k).
@@
 %
-To obtain the potential power spectrum, we take the absolute square of the
-last equation and use the definition of the 3D potential power spectrum
-(equation~\ref{eq:p_phi}). The delta-function resolves one 3D Fourier integral.
-We split the second integration into radial and spherical coordinates, ${\rm
-d}^3 k = {\rm d} k k^2 {\rm d} \Omega_k$ and use once again the orthogonality
-of the spherical harmonics to resolve the spherical integral. This leads to the
-potential power spectrum in equation~(\ref{eq:C_ell_phi_Pphi}).
+We take the absolute square and use the definition of the 3D potential power spectrum (equation~\ref{eq:p_phi}),
+to arrive at the expression in equation~(\ref{eq:C_ell_phi_Pphi}).
+Here, $P_{\rm m}$ is the 3D matter power cross-spectrum at line-of-sight comoving
+Fourier mode $k$ and comoving distances $\chi$ and $\chi^\prime$. We denote
+complex conjugation with superscript $^\ast$.
+\mk{Peter's comment: What does the correlation between two epochs actually mean if they
+are not on the backward light cone?}
+
+The delta-function resolves one 3D Fourier
+integral. We split the second integration into radial and spherical
+coordinates, ${\rm d}^3 k = {\rm d} k k^2 {\rm d} \Omega_k$ and use once again
+the orthogonality of the spherical harmonics to resolve the spherical integral. 
+This leads to the potential power spectrum in equation~(\ref{eq:C_ell_phi_Pm}).
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Kitching et al.~2016 (version 1)}
+\subsection{Kitching et al.~2016}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \cite{2016arXiv161104954K} compute the full projection of the weak-lensing
-power spectrum, which they present as spherical-radial representation of the 3D
+power spectrum, which they present as spherical-radial representation the 3D
 shear field. Our results in equation~(\ref{eq:C_ell_full}) corresponds to their
@@
 photometric redshifts, with $p(z | z_{\rm p}) = \delta_{\rm D}(z - z_{\rm p})$,
-and for a bin function that selects the redshift bin of $z$, $W^{\rm SR}(z,
-z_{\rm p})$ is unity if $z_{\rm p}$ is in the redshift bin denoted by $z$,
-and zero otherwise. We find that Equation (7) in \cite{2016arXiv161104954K} is
-missing a factor $2/\pi$.
-
-\cite{2016arXiv161104954K} derive the spherical and extended Limber
+and for a bin function that selects the redshift bin $i$, $W^{\rm SR}(z, z_{\rm
+p}) = 1_{z \in i-\mbox{th bin}}$. We find that Equation~(7) in
+\cite{2016arXiv161104954K} is missing a factor $2/\pi$.
+
+\cite{2016arXiv161104954K} derives the spherical and extended Limber
 approximation starting from the full spherical projection in their Appendix.~A.
-We find that the filter function $q$ defined in their Equation (31) has an
+We find that the filter function $q$ defined in their Equation~(31) has an
 additional factor of comoving distance $r$, and an additional factor of
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Bernardeau, Bonvin, Van de Rijt, Vernizzi (2012); Van de Rijt (2012)}
+\subsection{Bernardeau, Bonvin, Van de Rijt, Vernizzi (2012); van de Rijt (2012)}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \cite{2012PhRvD..86b3001B} present the non-tomographic full projection
-$C(\ell)$ in the approximation of the 3D potential power spectrum $P_\Phi$
-separating into $k$- and $\chi$-dependent functions in their Equation (44).
+$C(\ell)$ in the approximation of the 3D potential power spectrum $P^\Phi$
+separating into $k$- and $\chi$-dependent functions in their Equation~(44).
 Their expression holds for a single source redshift.
 
-The PhD thesis of \cite{vande2012} presents an explicit calculation of the
-second-order Limber approximation. They carry out the derivatives of the
+The PhD thesis of Van de Rijt \cite{vande2012} presents an explicit calculation
+of the second-order Limber approximation. They carry out the derivatives of the
 kernels $f$ under the assumption of a constant growth-suppression factor
@@
 \begin{equation}
-  f_{\rm s}^{\prime\prime}(\chi) + \frac{\chi}{3} f_{\rm s}^{\prime\prime\prime}(\chi)
+  f^{\prime\prime}(\chi) + \frac{\chi}{3} f^{\prime\prime\prime}(\chi)
     = - \frac 1 8 \chi^{-5/2} \left( \frac 5 \chi
@@
 %
-This result confirms the power-law behaviour for $\chi \ll \chi_{\rm S}$ of the
-filter function, which we exploited earlier to fit this function.
+This result confirms the power-law behaviour of the filter function, which we
+exploited earlier to fit this function.
 
@@
 equation to replace the matter with the potential power spectrum we obtain the
-same expression as \cite{vande2012} (their Equation~7.19), except for an
+same expression as \cite{vande2012} (their Equation.~7.19), except for an
 additional factor $a^2(\chi)$. This difference is accounted for by the factor
@@
 times, see Equation~(6.22) in \cite{vande2012}, where the transition is
-calculated using $g(a)$ instead of $D(a)$.
+calculated using $g(a)$ instead of $D(a)$. \mk{Check this further.}
 
 In Fig.~\ref{fig:L1L2E_Rijt} we reproduce Fig.~7.3 from \cite{vande2012} using
-a similar set up, a flat $\Lambda$ Universe with $\Omega_{\rm m} = 0.3, h=0.65,
+a similar set up (flat $\Lambda$ Universe with $\Omega_{\rm m} = 0.3, h=0.65,
 \Omega_{\rm b} = 0.0461, \sigma_8 = 0.8, n_{\rm s} = 0.96$. All source galaxies
 are at redshift $z_{\rm S} = 1$. The non-linear 3D matter power spectrum from
-\cite{2012ApJ...761..152T} is used. The ratio of the first-and second-order
-Limber approximated power spectra to the full projection shows excellent
-agreement at the sub-percent level.
+\cite{2012ApJ...761..152T} is used. The ratio of the first-and second- Limber
+approximated power spectra to the full projection shows excellent agreement at
+the sub-percent level.
 
@@
     at a single source plane at $z_{\rm S}=1$, with the cosmological parameters (see text) are chosen to match
-    \citet{vande2012}, see their Figure~7.3 for comparison.
+    \citet{vande2012}, see their Figure.~7.3 for comparison.
     }
@@
 clustering, their calculations are general enough to apply to a weak-lensing
-context. Their Equation (5) is a spherical cross-power spectrum of two scalar
-fields $A$ and $B$, projected from 3D to 2D via projection kernels $F_A$ and
-$F_B$ defined in their Equation (4). Comparing their expressions with the
-weak-lensing potential (\ref{eq:psi}), we set $F_A(\chi) = F_B(\chi) = 2 c^{-2}
-D_+(\chi) q(\chi) \chi^{-1}$. With that, their Equation~(5) is identical to
-equation~(\ref{eq:C_ell_phi_Pphi}).
+context. Their Equation.~(5) is a spherical cross-power spectrum of two scalar fields
+$A$ and $B$, projected from 3D to 2D via projection kernels $F_A$ and $F_B$
+defined in their Equation.~(4). Comparing their expressions with the weak-lensing
+potential (\ref{eq:psi}), we set $F_A(\chi) = F_B(\chi) = 2 c^{-2}
+D_+(\chi) q(\chi) \chi^{-1}$. With that, their Equations.~(5) is identical to equation~(\ref{eq:C_ell_phi_Pphi}).
 
@@
 presented in eq.~(12). This is consistent with our first-order
-(equation~\ref{eq:C_ell_limber1}) and second-order
-(equation~\ref{eq:C_ell_limber2_dr}) Limber approximation terms, when
-accounting for the difference between lensing potential and shear 2D power
-spectrum, and 3D potential and matter power spectrum.
+(equation~\ref{eq:C_ell_limber1}) and second-order (equation~\ref{eq:C_ell_limber2_dr}) Limber
+approximation terms, when accounting for the difference between lensing
+potential and shear 2D power spectrum, and 3D potential and matter power
+spectrum.
 
@@
 
-\cite{2008PhRvD..78d3002S} derive the lensing power spectrum in the flat-sky
-limit, see their Equation (9). Inserting the Poisson equation and the
-growth function, and writing the redshift filter function
-$W_\kappa$ (eq.~10) in terms of the lensing efficiency and comoving distances,
-$W_\kappa[z(\chi)] = H(z)^{-1} \chi q(\chi)$, their expression, using our
-notations, reads
+\cite{2008PhRvD..78d3002S} derive the lensing power spectrum in the
+flat-sky limit (see their Equation~(9)). Inserting the Poisson factor $D_\phi$, 
+ the growth function $D_{\rm m}$, and writing the redshift filter
+function $W_\kappa$ (eq.~10) in terms of the lensing efficiency and comoving distances,
+$W_\kappa[z(\chi)] = H(z)^{-1} \chi q(\chi)$, their expression, using our notations, reads
 %
@@
   P_{ij}^\gamma(\ell) = & \frac 2 \pi \, \pref^2
-                 \int_{0}^\infty {\rm d} \chi \chi \, \frac{q_i(\chi)}{a(\chi)}
-                \int_{0}^\infty {\rm d} \chi^\prime\, \chi^\prime
+                 \int_{0}^{\chi_{\rm lim}} {\rm d} \chi \chi \, \frac{q_i(\chi)}{a(\chi)}
+                \int_{0}^{\chi_{\rm lim}} {\rm d} \chi^\prime\, \chi^\prime
                 \frac{q_j(\chi^\prime)}{a(\chi^\prime)}
-                %\nonumber \\
-                %& \times
-                \int_0^\infty {\rm d} k \, k^2 \, P_{\rm m}(k; \chi, \chi^\prime) \,
+                \nonumber \\
+                & \times \int_0^\infty {\rm d} k \, k^2 \, P_{\rm m}(k; \chi, \chi^\prime) \,
                 {\rm j}_\ell(k \chi) \, {\rm j}_\ell(k \chi^\prime) ,
@@
 %
-This is consistent with our equation (\ref{eq:P_ell_gamma_full_der}) under the
-additional assumption that mainly modes with $k \chi \approx k \chi^\prime
-\approx \ell$ contribute to the integral; that is modes around the maxima of
-the Bessel functions. Then, we can draw out of the integral the factor $\ell^4
-\approx k^4 \chi^2 {\chi^\prime}^2$, to recover
-equation~(\ref{eq:P_ell_gamma_full_der}).
-In fact, using the approximation $k \chi = \ell$ seems to go too far, this is
-already halfway the Limber approximation.
+This is consistent with our equation (\ref{eq:P_ell_gamma_full_der}) under the additional assumption that
+mainly modes with $k \chi \approx k \chi^\prime \approx \ell$ contribute to the integral; that is modes
+around the maxima of the Bessel functions. Then, we can draw out of the integral the factor $\ell^4 \approx k^4 \chi^2 {\chi^\prime}^2$,
+to recover equation~(\ref{eq:P_ell_gamma_full_der}).
+\mk{This argument is very hand-wavey! In fact, using the approximation $k \chi = \ell$ seems to go too far, this is already halfway the Limber approximation.}
+
+%\begin{align}
+  %W_\kappa(z) = & \frac 1 {H(z)} \int_z^\infty {\rm d} z_{\rm s} W_{\rm L}(z_{\rm s}, z) W_{\rm g}(z)
+              %=  \frac 1 {H(z)} \chi \int_\chi^\infty {\rm d} \chi^\prime \frac{\chi^\prime - \chi}{\chi^\prime}
+                %n(\chi)
+              %\nonumber \\
+              %& \equiv \frac 1 {H(z)} \chi q(\chi),
+%\end{align}
+%%
+%using ${\rm d} z W_{\rm g}(z) = {\rm d} \chi n(\chi)$.
+%To write the redshift integrals (9) in \cite{2008PhRvD..78d3002S} over 
+%comoving distance, we make the variable transformation
+%%
+%\begin{equation}
+  %{\rm d} \chi = \frac{c {\rm d} z}{H(z)} .
+%\end{equation}
+%%
+%We
 
@@
 \label{sec:giannantonio12}
-
-\cite{2012MNRAS.422.2854G} derive the flat-sky lensing power spectrum in their
-Equations (25) and (26). Their window function $W^{\varepsilon_i}$ defined in
-their Equation (25) for a flat Universe equals $\pref q(\chi) / a(\chi)$, since
-${\rm d} z \, ({\rm d} N(z)/{\rm d} z) = {\rm d} \chi n(\chi)$; however due to
-a typo there is a factor $r_K[r(z)]$ missing in the window function, which
-translates into a missing $r_K[r] r_K[r^\prime]$ in the full projection
-integral\footnote{Typo confirmed by T.~G., priv.~comm.}. This also leads to an
-errorous $r_K^{-2}(r)$ in their Limber equation (27). With these factors
-accounted for, and making the additional approximation $k \chi \approx k
-\chi^\prime \approx \ell$ (see their Appendix~\ref{sec:schmidt08}) we reproduce
-the expressions of \cite{2012MNRAS.422.2854G}.
+\cite{2012MNRAS.422.2854G} derive the flat-sky lensing
+power spectrum in their Equations.~(25) and (26) . Their window function $W^{\varepsilon_i}$ defined in their Equation~(25) for a
+flat Universe equals $\pref q(\chi) / a(\chi)$, since ${\rm d} z \,
+({\rm d} N(z)/{\rm d} z) = {\rm d} \chi n(\chi)$; however due to a typo there
+is a factor $r_K[r(z)]$ missing in the window function, which translates into a
+missing $r_K[r] r_K[r^\prime]$ in the full projection integral\footnote{Typo
+confirmed by T.~G., priv.~comm.}. This also leads to an errorous $r_K^{-2}(r)$
+in the Limber equation (27). With these factors accounted for, and making the
+additional approximation $k \chi \approx k \chi^\prime \ell$ (see their
+Appendix~\ref{sec:schmidt08}) we reproduce the expressions of
+\cite{2012MNRAS.422.2854G}.
 

### 2017-03-09 authors.tex

--- 2017-02-13 authors.tex
@@
 Patrick Simon$^6$,
+Ludovic Van Waerbeke$^7$,
 Joachim Harnois-D\'eraps$^3$,
+\newauthor
 Hendrik Hildebrandt$^6$,
-\newauthor
 Fabian K\"ohlinger$^7$,
-Konrad Kuijken$^7$,
-Ludovic Van Waerbeke$^8$ and
-Massimo Viola$^7$
+Konrad Kuijken$^8$, and
+Massimo Viola$^8$
 \\
@@
 $^6$Argelander-Institut f\"ur Astronomie, Auf dem H\"ugel 71, 53121 Bonn, Germany\\
+$^7$Department of Physics and Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC V6T 1Z1, Canada\\
 $^7$Kavli Institute for the Physics and Mathematics of the Universe (WPI), The University of Tokyo Institutes for Advanced Study, \\
-The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
-$^8$Department of Physics and Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC V6T 1Z1, Canada\\
+\phantom{$^7$}The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
+$^8$Leiden Observatory, Leiden University, Niels Bohrweg 2, 2333 CA Leiden, the Netherlands
 }

### 2017-04-20 answer_to_referee.txt
First draft of referee reply and modifications.

We would like to thank the referee for their positive report and useful comments and suggestions.
Please fine below our replies to the referee's points. All modifications to the draft are highlighted
in red.

- Shear correlation function, eq. (47-48).
  We had indeed used a transformation (with the Legendre polynomial) that is incorrect for spin-2 correlations.
  We have replaced this with the correct transformations using the reduced Wigner D-matrices. We state their
  form in a new Appendix C. Figures 2 and 3, involving the shear correlation functions, have been updated
  accordingly.

- p. 6, chi-dependence of \tilde P_m.
  We added to the equation an approximate expression of P_m(k), without the chi-dependence. We hope that the
  subsequent text as it stands should make the conditions under which this approximation holds sufficiently clear.

- p. 7, accuracy of the ExtL2FlHyb.
  * Not sure about the reason. *

- Making Fig. 1 and following clearer.
  * Not sure that adding labels or anything else would make those clearer. *

- Table 1, extra column.
  We added columns indicating the ell_x such that for ell>ell_x the power spectrum projection has better
  accuracy than x, with x=10% and 1%.

- Fig. 3, comparison for xi_-.
  This plot has been updated, both xi_+ and xi_- are now compared to the full spherical case.

- Table 2, adding plot.
  * Really necessary? *

- Conclusions
  * I think present tense is fine *

- Fig. 4.
  * On my screen I don't have a problem with this figure. *

Other modifications.

- End of introduction: Lemos et al. reference added.

- Eq. 47: The definitions as <gamma gamma^*> and <gamma gamma> for xi_+ and xi_- have been added here,
  moved from eq. 48.

- Typos:
  All typos have been fixed.

### 2017-04-20 cfhtlens.tex
First draft of referee reply and modifications.

@@
 to account for bias and scatter, with a prediction that accounting for these
-biases would {\it reduce} the recovered amplitude of $\sigma_8$ by $\sim
+biases would {\it reduce}\/ the recovered amplitude of $\sigma_8$ by $\sim
 4$\%. Additional new techniques to calibrate the redshift distribution of tomographic
@@
 analytical methods will be published soon (Joachimi et al.~in prep.)}
-%
+%\
 \item{\cite{2012ApJ...761..152T} provided a more accurate non-linear power
@@
 amplitude that is well within the Monte-Carlo sampling noise. The largest
-difference is measured with the depreciated case ExtL1Fl, for which the
+difference is measured with the \forref{depreciated} case ExtL1Fl, for which the
 recovered amplitude is larger by $16\%$ of the statistical error. These
@@
 
-Table \ref{tab:CFHTLenS_Sigma8} lists the mean and 68\% credible interval for
+Table~\ref{tab:CFHTLenS_Sigma8} lists the mean and 68\% credible interval for
 $\sigma_8 \Omega_{\rm m}^{0.6}$ for the various approximations to the
-lensing power spectrum projections listed in Table~\ref{tab:cases} Note again
+lensing power spectrum projections listed in Table~\ref{tab:cases}. Note again
 that these values do not represent the state-of-the-art cosmological results,
@@
 \cite{2003MNRAS.341.1311S}, there is a decrease of $0.6 \sigma$ with $\sigma_8
-(\Omega_{\rm m}/0.27)^{0.6} =0.768^{+0.029}_{-0.031}$.
+(\Omega_{\rm m}/0.27)^{0.6} = 0.768^{+0.029}_{-0.031}$\forref{, using L1Fl}.
 

### 2017-04-20 limber2.tex
First draft of referee reply and modifications.

--- 2017-03-09 limber2.tex
@@
 
+\definecolor{darkred}{rgb}{0.8,0.1,0.1}
 \newcommand{\mk}[1]{{\bf\textcolor{blue}{#1}}}
+\newcommand{\EDIT}[1]{{\bf\textcolor{red}{#1}}}
+\newcommand{\forref}[1]{{\bf\textcolor{darkred}{#1}}}
 \newcommand{\Label}[1]{\quad (\mbox{#1})}
@@
 second-order Limber equations for the projection. We find that the impact of
-adopting these approximations are negligible when constraining cosmological
+adopting these approximations \forref{is} negligible when constraining cosmological
 parameters from current weak lensing surveys.
@@
 We consider spherical coordinates and the flat-sky approximation, and compute
-the full projection. The first-order extended Limber approximation provides
-sub-percent accuracy for $\ell > 10$ and is sufficient for present surveys. The
-associated errors are sub-dominant even for future large surveys.
+the full projection \forref{of the lensing power spectrum}. The first-order
+extended Limber approximation provides sub-percent accuracy for $\ell > 10$ and
+is sufficient for present surveys. The associated errors are sub-dominant even
+for future large surveys.
 
@@
 power spectra for the flat-sky and spherical cases, following the seminal work
-from \citet{2000PhRvD..62d3007H} \cite[see also][]{2005PhRvD..72b3516C}. In
+\forref{by} \citet{2000PhRvD..62d3007H} \cite[see also][]{2005PhRvD..72b3516C}. In
 section~\ref{sec:L2} we derive weak-lensing observables using a second-order
@@
 lensing studies, namely \citet{2008PhRvD..78d3002S,2012PhRvD..86b3001B,
-2012MNRAS.422.2854G, 2016arXiv161104954K}. We present a discussion and
+2012MNRAS.422.2854G, 2016arXiv161104954K}\forref{, see also
+\cite{2017arXiv170401054L} for a more recent work.} We present a discussion and
 comparison of our results to these papers in Appendix~\ref{app:B}.
@@
 $\chi$ and $\chi^\prime$ was introduced in \cite{2005PhRvD..72b3516C}. In
-Sects.~\ref{sec:geom_mean} and \ref{sec:factor_D} this unequal-time
+Sects.~\ref{sec:geom_mean} and~\ref{sec:factor_D} this unequal-time
 cross-spectrum \citep{2016arXiv161200770K} will be further evaluated and
@@
 %
-where we use the label `FullSph', see Table \ref{tab:cases} for a list of cases discussed in this work.
+where we use the label `FullSph', see Table~\ref{tab:cases} for a list of cases discussed in this work.
 The spherical spin pre-factor for the full projection shear power
@@
 degrees. To account for the sky curvature of the observed data, the shear
-correlation functions from observed galaxy ellipticities is now routinely
+correlation functions from observed galaxy ellipticities \forref{are} now routinely
 computed using spherical coordinates, since projecting to a Cartesian plane has
@@
 
-The flat-sky power spectrum, i.e. the flat-sky analogue of equation~(\ref{eq:C_ell_psi}), is defined by
+The flat-sky power spectrum, i.e.\ the flat-sky analogue of equation~(\ref{eq:C_ell_psi}), is defined by
 %
@@
 %
-with flat-sky pre-factor $\ell^4$. See App.~\ref{sec:schmidt08} and
-\ref{sec:giannantonio12} for discussions of alternative expressions for the
+with flat-sky pre-factor $\ell^4$. See App.~\ref{sec:schmidt08} and~\ref{sec:giannantonio12} for discussions of alternative expressions for the
 flat-sky power spectrum.
@@
 and contrary to \cite{2008PhRvD..78l3506L} account for a time-dependent power
-spectrum using two approaches presented in Sects.~\ref{sec:geom_mean} and
-\ref{sec:factor_D}.
+spectrum using two approaches presented in Sects.~\ref{sec:geom_mean} and~\ref{sec:factor_D}.
 
@@
 %
-by performing a Taylor expansion of an arbitrary differentialble function
+by performing a Taylor expansion of an arbitrary \forref{differentiable} function
 $f$ around $x = k \chi = \nu = \ell + 1/2$, where the Bessel function has its
@@
 \begin{equation}
- P_{\rm m}(k, \chi) =: D^2_+(\chi) \tilde P_{\rm m}(k, \chi).
+ P_{\rm m}(k, \chi) =: D^2_+(\chi) \tilde P_{\rm m}(k, \chi) \forref{\approx D^2_+(\chi) \tilde P_{\rm m}(k)}.
   \label{eq:P_k_chi_sep_s}
@@
     \left[ q^{}_i f^{\prime\prime}_{{\rm s} j} + f^{\prime\prime}_{{\rm s}i} q^{}_j
-      + \frac{\chi}{3} \left( q^{}_i f^{\prime\prime\prime}_{{\rm s}j} + f^{\prime\prime\prime}_{{\rm s}i} q^{}_j
+      + \frac{\chi}{3} \left(
+        q^{}_i f^{\prime\prime\prime}_{{\rm s}j} + f^{\prime\prime\prime}_{{\rm s}i} q^{}_j
       \right)
@@
 The extended flat-sky Limber approximation is readily derived from the
-spherical case equations~(\ref{eq:C_ell_limber1}, \ref{eq:C_ell_limber2_dr_s}), by
+spherical case equations~(\ref{eq:C_ell_limber1},~\ref{eq:C_ell_limber2_dr_s}), by
 replacing the pre-factor $\ellbar^2(\ell, 2)$ with $\ell^4$,
@@
   %
-  \caption{\label{tab:cases}The shear power spectrum approximations studied in this paper. 'ID' is the label
+  \caption{\label{tab:cases}The shear power spectrum approximations studied in this paper. `ID' is the label
     used in the text and figures.
@@
     %
-    \begin{tabular}{|l|l|c|c|c|p{0.21\textwidth}}
+    \begin{tabular}{|p{0.22\textwidth}|l|c|c|c|c|c|p{0.21\textwidth}}
   \hline
-  Case & ID & equation & $p(\ell)$ & $\nu(\ell)$ & Comment \\ \hline
-  % 
-  $1^{\rm st}$-order standard Limber, flat sky & L1Fl & (\ref{eq:P_ell_limber1}) + (i)
-    & $1$ & $\ell$ & Pre-2014 CFHTLenS and DLS \\ \hline
-  %
-  $1^{\rm st}$-order extended Limber, flat sky & ExtL1Fl & (\ref{eq:P_ell_limber1}) + (ii)
-    & $\frac{\ell^4}{(\ell+1/2)^4}$ & $\ell + \frac 1 2$ & Converges only with ${\cal O}(\ell^{-1})$ \\ \hline
-  %
-  $1^{\rm st}$-order extended Limber, hybrid, flat sky & ExtL1FlHyb & (\ref{eq:P_ell_limber1}) + (iii)
-    & $1$ & $\ell + \frac 1 2$ & Post-2014 CFHTLenS, DES-SV and KiDS \\ \hline
+  Case & ID & equation & $p(\ell)$ & $\nu(\ell)$ & \forref{$\ell_{0.1}$} & \forref{$\ell_{0.01}$} & Comment \\ \hline
+  % 
+  $1^{\rm st}$-order standard Limber, flat & L1Fl & (\ref{eq:P_ell_limber1})+(i)
+    & $1$ & $\ell$ & $4$ & $60$ & Pre-2014 CFHTLenS and DLS \\ \hline
+  %
+  $1^{\rm st}$-order extended Limber, flat & ExtL1Fl & (\ref{eq:P_ell_limber1})+(ii)
+    & $\frac{\ell^4}{(\ell+1/2)^4}$ & $\ell + \frac 1 2$ & & & Converges only with ${\cal O}(\ell^{-1})$ \\ \hline
+  %
+  $1^{\rm st}$-order extended Limber, hybrid, flat & ExtL1FlHyb & (\ref{eq:P_ell_limber1})+(iii)
+    & $1$ & $\ell + \frac 1 2$ & & & Post-2014 CFHTLenS, DES-SV and KiDS \\ \hline
   %
   $1^{\rm st}$-order extended Limber, spherical & ExtL1Sph & (\ref{eq:C_ell_limber1})
-    & $\frac{\ellbar^2(\ell, 2)}{(\ell+1/2)^4}$ & $\ell+ \frac 1 2$ & \\ \hline
-  %
-  $2^{\rm st}$-order extended Limber, flat sky & ExtL2Fl &  (\ref{eq:P_ell_limber1}) + (\ref{eq:P_ell_limber2}) + (iii)
+    & $\frac{\ellbar^2(\ell, 2)}{(\ell+1/2)^4}$ & $\ell+ \frac 1 2$ & & & \\ \hline
+  %
+  $2^{\rm st}$-order extended Limber, flat & ExtL2Fl &  (\ref{eq:P_ell_limber1})+(\ref{eq:P_ell_limber2})+(iii)
     & $\frac{\ell^4}{(\ell+1/2)^4}$ 
-    & $\ell+\frac 1 2$ & Converges only with ${\cal O}(\ell^{-1})$ \\ \hline
-  %
-  $2^{\rm st}$-order extended Limber, hybrid, flat sky & ExtL2FlHyb &  (\ref{eq:P_ell_limber1}) + (\ref{eq:P_ell_limber2}) + (iii)
+    & $\ell+\frac 1 2$ & & & Converges only with ${\cal O}(\ell^{-1})$ \\ \hline
+  %
+  $2^{\rm st}$-order extended Limber, hybrid, flat & ExtL2FlHyb &  (\ref{eq:P_ell_limber1})+(\ref{eq:P_ell_limber2})+(iii)
     & $1$ 
-    & $\ell+ \frac 1 2$ & Best flat-sky approximation \\ \hline
+    & $\ell+ \frac 1 2$ & & & Best flat-sky approximation \\ \hline
   %
   $2^{\rm st}$-order extended Limber, spherical & ExtL2Sph & (\ref{eq:C_ell_limber1})+(\ref{eq:C_ell_limber2_dr_s})
-    & $\frac{\ellbar^2(\ell, 2)}{(\ell+1/2)^4}$ & $\ell+\frac 1 2$ & Best approximation \\ \hline
+    & $\frac{\ellbar^2(\ell, 2)}{(\ell+1/2)^4}$ & $\ell+\frac 1 2$ & & & Best approximation \\ \hline
   %
   Full spherical & FullSph & (\ref{eq:C_ell_full}) &
-      - & - & Correct projection \\ \hline
+      - & - & - & - & Correct projection \\ \hline
   %
@@
 galaxy shape catalogue. The baseline quantity is the two-point correlation
-function \citep{1991ApJ...370....1M, 1992ApJ...388..272K, BS01}, given by
+function \citep{1991ApJ...370....1M, 1992ApJ...388..272K, BS01}, given \forref{in the flat-sky approximation} by
 %
@@
   % &
-  = \frac 1 {2\pi} \int {\rm d} \ell \, \ell \, {\rm J}_0(\ell
+  = \forref{\left\langle \gamma \gamma^\ast \right\rangle(\theta) =} \frac 1 {2\pi} \int {\rm d} \ell \, \ell \, {\rm J}_0(\ell
    \theta)
@@
   %&
-  = \frac 1 {2\pi} \int
+  = \forref{\left\langle \gamma \gamma \right\rangle(\theta) =} \frac 1 {2\pi} \int
    {\rm d} \ell \, \ell \, {\rm J}_4(\ell \theta)
@@
 spectrum by the Hankel transform in equation~(\ref{eqn:xiGG}), and should
-be replaced by the spherical transform \citep{1973ApJ...185..413P}
-%
-\begin{equation}
- \xi_+(\theta) = \left\langle \gamma \gamma^\ast \right\rangle(\theta)
-  =  \frac 1{4\pi} \sum\limits_{\ell=2}^\infty (2 \ell + 1) C^\gamma(\ell) {\rm P}_\ell[\cos(\theta)],
-  \label{eq:xi_Legendre}
-\end{equation}
-%
-where ${\rm P}_\ell(x)$ are the Legendre polynomials in $x$ of order $\ell$. This equation is easily derived
-using the harmonics expansion of the shear (equation~\ref{eq:gamma_harm_exp}) and the orthogonality relation of
-the spherical harmonics (\ref{eq:Yellm_ortho}).
+be replaced by the spherical transform \forref{\citep{1999IJMPD...8...61N,2004MNRAS.350..914C}}
+%
+\forref{
+\begin{equation}
+ \xi_+(\theta) 
+  =  \frac 1{4\pi} \sum\limits_{\ell=2}^\infty (2 \ell + 1) C^\gamma(\ell) {\rm d}^\ell_{2\,2}(\theta); \quad 
+ \xi_0(\theta) 
+  =  \frac 1{4\pi} \sum\limits_{\ell=2}^\infty (2 \ell + 1) C^\gamma(\ell) {\rm d}^\ell_{2\,-2}(\theta)
+  \label{eq:xi_wigner}
+\end{equation}
+}
+%
+\forref{where ${\rm d}^\ell_{m\,n}$ are the reduced Wigner ${\rm D}$-matrices, see App.~\ref{app:C} for details.}
 
@@
 the Hankel transformation and the full spherical transformation in
-Fig.~\ref{fig:xi_p_legendre}. We show the full projection and the best
+Fig.~\ref{fig:xi_p_wigner}. We show the full projection and the best
 approximation, ExtL2Sph. Note that for the `FullSph' case we replace the full
@@
 The difference between the second-order Limber and full projection solution using the
-spherical transform (equation~\ref{eq:xi_Legendre}) is well below one percent
+spherical transform (equation~\ref{eq:xi_wigner}) is well below one percent
 for $\vartheta < 200$ arcminutes.
-The red circles in Fig.~\ref{fig:xi_p_legendre} present the limit of
+The red circles in Fig.~\ref{fig:xi_p_wigner} present the limit of
 precision that we can achieve with the current fast Hankel transform implementation
@@
     \resizebox{1.0\hsize}{!}{
-      \includegraphics{figures/xi_p_legendre}
+      \includegraphics{figures/xi_p_wigner}
       \hspace*{2em}
-      \includegraphics{figures/xi_p_legendre_delta}
+      \includegraphics{figures/xi_p_wigner_delta}
     }
@@
 
-  \caption{\emph{Left panel:} The shear correlation function component $\xi_+$
+  \caption{\emph{Left panel \mk{Needs to be updated}:} The shear correlation function component $\xi_+$
 for the ExtL2Sph projection using the spherical transform (green line for
@@
 
-  \label{fig:xi_p_legendre}
+  \label{fig:xi_p_wigner}
 
@@
   In the spherical cases (ExtL1Sph, ExtL2Sph, FullSph), $\xi_+$ has been computed using the spherical
-  transform (equation~\ref{eq:xi_Legendre}). For the flat cases, and all instances of $\xi_-$, the Hankel transform
+  transform (equation~\ref{eq:xi_wigner}). For the flat cases, and all instances of $\xi_-$, the Hankel transform
   in equation~(\ref{eqn:xiGG}) was used.
@@
 
-\EDIT{Note: The factor of $a^2$ has been resolved, it is correctly reproduced
-when propagating the primordial potential power spectrum to late times $a$
-with $[D+(a)/a]^2$ instead of $D^2+(a)$.}
-
-%, except for an
-%%additional factor $a^2(\chi)$. This difference is accounted for by the factor
-%$a^{-1}$ in the propagation of primordial potential perturbations to late
-%times, see Equation~(6.22) in \cite{vande2012}, where the transition is
-%calculated using $g(a)$ instead of $D(a)$.
-
 In Fig.~\ref{fig:L1L2E_Rijt} we reproduce Fig.~7.3 from \cite{vande2012} using
@@
     shear power spectra with respect to the full projection
-    as function of wave mode $\ell$, (see Table \ref{tab:cases}). In this figure, the redshift distribution is chosen to be
+    as function of wave mode $\ell$, (see Table~\ref{tab:cases}). In this figure, the redshift distribution is chosen to be
     at a single source plane at $z_{\rm S}=1$, with the cosmological parameters (see text) are chosen to match
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{The shear correlation function on the sphere}
+\label{app:C}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \label{lastpage}

### 2017-04-24 arXiv/limber2.tex
Paper updated xi plots and table

--- 2017-03-09 limber2.tex
@@
 
-\title[Precision calculations of the cosmic shear projection]{Precision calculations of the cosmic shear power spectrum projection}
+\title[Precision calculations of the cosmic shear projection]{Precision calculations of the cosmic shear power spectrum
+projection}
 
@@
     \emph{standard} Limber approximation \LabelTxt{L1Fl} Until recently,
-  i.e.~for all pre-2014 CFHTLenS results and DLS
+  i.e.~for all pre-2014 CFHTLenS results, DES-SV \citep{abbott/etal:2016} and DLS
   \citep{jee/etal:2016} analyses, this was the approximation of choice. Note that
@@
     standard and extended Limber approximation~\LabelTxt{ExtL1FlHyb, ExtL2FlHyb}, and the first-order case 
-    was used in \cite{KiDS-450,joudaki/etal:2016,joudaki/etal:2017,abbott/etal:2016}. As is shown
+    was used in \cite{KiDS-450,joudaki/etal:2016,joudaki/etal:2017}. As is shown
     below, this is a better approximation to the full projection than case (ii). In equation~(\ref{eq:P_ell_limber2})
@@
 Considering first the flat-sky cases, the standard first-order Limber
-approximation, (L1Fl), that was adopted for all pre-2014 CFHTLenS analyses and DLS analyses, we
+approximation, (L1Fl), that was adopted for all pre-2014 CFHTLenS analyses, DES-SV and DLS analyses, we
 find it to be accurate to better than 10\% for $\ell>3$, converging slowly to the
@@
 $\ell>15$.  The first-order extended Limber approximation `hybrid' cases
-(ExtL1FlHyb) was adopted by \citet{joudaki/etal:2016}, \citet{joudaki/etal:2017}, DES-SV \citep{abbott/etal:2016} and
+(ExtL1FlHyb) was adopted by \citet{joudaki/etal:2016}, \citet{joudaki/etal:2017}, and
 \cite{KiDS-450}\footnote{We confirm that there is a typographical error in
-equation 4 of \cite{KiDS-450} and in equation 2 of \citet{abbott/etal:2016} (private communication with Joe Zuntz) 
-which should include the extra term of `+0.5' in
-$\nu(\ell)$ that was incorporated in both cosmological analyses.}.
+equation 4 of \cite{KiDS-450} which should include the extra term of `+0.5' in
+$\nu(\ell)$ that was incorporated in the cosmological analysis.}.
 
@@
   $1^{\rm st}$-order standard Limber, flat sky & L1Fl & (\ref{eq:P_ell_limber1}) + (i)
-    & $1$ & $\ell$ & Pre-2014 CFHTLenS and DLS \\ \hline
+    & $1$ & $\ell$ & Pre-2014 CFHTLenS, DES-SV and DLS \\ \hline
   %
@@
   $1^{\rm st}$-order extended Limber, hybrid, flat sky & ExtL1FlHyb & (\ref{eq:P_ell_limber1}) + (iii)
-    & $1$ & $\ell + \frac 1 2$ & Post-2014 CFHTLenS, DES-SV and KiDS \\ \hline
+    & $1$ & $\ell + \frac 1 2$ & Post-2014 CFHTLenS, KiDS \\ \hline
   %
@@
 The authors thank Tommaso Giannantonio, Sarah Bridle, Ami Choi, Donnacha Kirk,
-Lance Miller, Benjamin Joachimi, Chris Blake, Joe Zuntz, Joanne Cohn, Alex Hall and Adam Amara for very helpful
+Lance Miller, Benjamin Joachimi, Chris Blake and Adam Amara for very helpful
 discussions. This work was financially supported by the DFG (Emmy Noether grant
@@
 Research Council Centre of Excellence for All-sky Astrophysics (CAASTRO),
-through project number CE110001020i, and by the German Federal
-Ministry for Economic Affairs and Energy (BMWi) under
-project no. 50QE1103.
+through project number CE110001020.
 
@@
 \bibliography{astro}
+
+\newpage
 
@@
 equation to replace the matter with the potential power spectrum we obtain the
-same expression as \cite{vande2012} (their Equation~7.19).
-
-\EDIT{Note: The factor of $a^2$ has been resolved, it is correctly reproduced
-when propagating the primordial potential power spectrum to late times $a$
-with $[D+(a)/a]^2$ instead of $D^2+(a)$.}
-
-%, except for an
-%%additional factor $a^2(\chi)$. This difference is accounted for by the factor
-%$a^{-1}$ in the propagation of primordial potential perturbations to late
-%times, see Equation~(6.22) in \cite{vande2012}, where the transition is
-%calculated using $g(a)$ instead of $D(a)$.
+same expression as \cite{vande2012} (their Equation~7.19), except for an
+additional factor $a^2(\chi)$. This difference is accounted for by the factor
+$a^{-1}$ in the propagation of primordial potential perturbations to late
+times, see Equation~(6.22) in \cite{vande2012}, where the transition is
+calculated using $g(a)$ instead of $D(a)$.
 
@@
 integral\footnote{Typo confirmed by T.~G., priv.~comm.}. This also leads to an
-errornous $r_K^{-2}(r)$ in their Limber equation (27). With these factors
+errorous $r_K^{-2}(r)$ in their Limber equation (27). With these factors
 accounted for, and making the additional approximation $k \chi \approx k

### 2017-04-24 limber2.tex
undefined reference fixed

@@
     used in the text and figures.
-    The third column shows the power-spectrum pre-factor $p(\ell)$. } 
+    \forref{The sixth (seventh) column indicates the mode $\ell_x$ such that for $\ell \leq \ell_x$, the approximated
+    power spectrum is more accurate than $x$, with $x=0.1$ ($0.01$).}
+    } 
     %
@@
   Case & ID & equation & $p(\ell)$ & $\nu(\ell)$ & \forref{$\ell_{0.1}$} & \forref{$\ell_{0.01}$} & Comment \\ \hline
-  % 
+  %  black
   $1^{\rm st}$-order standard Limber, flat & L1Fl & (\ref{eq:P_ell_limber1})+(i)
     & $1$ & $\ell$ & $4$ & $60$ & Pre-2014 CFHTLenS and DLS \\ \hline
-  %
+  % blue
   $1^{\rm st}$-order extended Limber, flat & ExtL1Fl & (\ref{eq:P_ell_limber1})+(ii)
-    & $\frac{\ell^4}{(\ell+1/2)^4}$ & $\ell + \frac 1 2$ & & & Converges only with ${\cal O}(\ell^{-1})$ \\ \hline
-  %
+    & $\frac{\ell^4}{(\ell+1/2)^4}$ & $\ell + \frac 1 2$ & $20$ & $200$ & Converges only with ${\cal O}(\ell^{-1})$ \\ \hline
+  % pink
   $1^{\rm st}$-order extended Limber, hybrid, flat & ExtL1FlHyb & (\ref{eq:P_ell_limber1})+(iii)
-    & $1$ & $\ell + \frac 1 2$ & & & Post-2014 CFHTLenS, DES-SV and KiDS \\ \hline
-  %
+    & $1$ & $\ell + \frac 1 2$ & $4$ & $10$ & Post-2014 CFHTLenS, DES-SV and KiDS \\ \hline
+  % cyan
   $1^{\rm st}$-order extended Limber, spherical & ExtL1Sph & (\ref{eq:C_ell_limber1})
-    & $\frac{\ellbar^2(\ell, 2)}{(\ell+1/2)^4}$ & $\ell+ \frac 1 2$ & & & \\ \hline
-  %
+    & $\frac{\ellbar^2(\ell, 2)}{(\ell+1/2)^4}$ & $\ell+ \frac 1 2$ & $3$ & $12$ & \\ \hline
+  % grey
   $2^{\rm st}$-order extended Limber, flat & ExtL2Fl &  (\ref{eq:P_ell_limber1})+(\ref{eq:P_ell_limber2})+(iii)
     & $\frac{\ell^4}{(\ell+1/2)^4}$ 
-    & $\ell+\frac 1 2$ & & & Converges only with ${\cal O}(\ell^{-1})$ \\ \hline
-  %
+    & $\ell+\frac 1 2$ & $19$ & $200$ & Converges only with ${\cal O}(\ell^{-1})$ \\ \hline
+  % orange
   $2^{\rm st}$-order extended Limber, hybrid, flat & ExtL2FlHyb &  (\ref{eq:P_ell_limber1})+(\ref{eq:P_ell_limber2})+(iii)
     & $1$ 
-    & $\ell+ \frac 1 2$ & & & Best flat-sky approximation \\ \hline
-  %
+    & $\ell+ \frac 1 2$ & $5$ & $16$ & Best flat-sky approximation \\ \hline
+  % green
   $2^{\rm st}$-order extended Limber, spherical & ExtL2Sph & (\ref{eq:C_ell_limber1})+(\ref{eq:C_ell_limber2_dr_s})
-    & $\frac{\ellbar^2(\ell, 2)}{(\ell+1/2)^4}$ & $\ell+\frac 1 2$ & & & Best approximation \\ \hline
+    & $\frac{\ellbar^2(\ell, 2)}{(\ell+1/2)^4}$ & $\ell+\frac 1 2$ & $2$ & $5$ & Best approximation \\ \hline
   %
@@
 On a sphere, correlation functions formally cannot be related to the power
-spectrum by the Hankel transform in equation~(\ref{eqn:xiGG}), and should
-be replaced by the spherical transform \forref{\citep{1999IJMPD...8...61N,2004MNRAS.350..914C}}
+spectrum by the Hankel transform in equation~(\ref{eqn:xiGG}), and should be
+replaced by the spherical transform
+\forref{\citep{1999IJMPD...8...61N,2004MNRAS.350..914C}}
 %
@@
 functions. This has the advantage being able to employ fast FFT numerical implementations of
-the Hankel tranforms \citep{fftlog}, when Monte-Carlo sampling.
+the Hankel tranforms \citep{2000MNRAS.312..257H}, when Monte-Carlo sampling.
 
@@
 %
-We find that the Hankel transform (equation~\ref{eqn:xiGG}) is accurate to better than $2$ percent level.
+We find that the Hankel transform (equation~\ref{eqn:xiGG}) is accurate to better than \forref{$5$ ($0.2$) percent
+for $\xi_+$ ($\xi_-$)}.
 %
 The difference between the second-order Limber and full projection solution using the
-spherical transform (equation~\ref{eq:xi_wigner}) is well below one percent
-for $\vartheta < 200$ arcminutes.
-The red circles in Fig.~\ref{fig:xi_p_wigner} present the limit of
+spherical transform (equation~\ref{eq:xi_wigner}) is well below one \forref{($0.03$) percent
+on scales of $\vartheta < 300$ arcminutes for $\xi_+$ ($\xi_-$)}.
+The red lines in Fig.~\ref{fig:xi_p_wigner} present the limit of
 precision that we can achieve with the current fast Hankel transform implementation
-for the correlation function. The green line shows the limit of the
+for the correlation function. The green \forref{lines show} the limit of the
 second-order Limber approximation on the correlation function.
@@
     \resizebox{1.0\hsize}{!}{
-      \includegraphics{figures/xi_p_wigner}
+      \includegraphics{figures/xi_p_wigner_delta}
       \hspace*{2em}
-      \includegraphics{figures/xi_p_wigner_delta}
+      \includegraphics{figures/xi_m_wigner_delta}
     }
@@
 
-  \caption{\emph{Left panel \mk{Needs to be updated}:} The shear correlation function component $\xi_+$
-for the ExtL2Sph projection using the spherical transform (green line for
-ExtL2Sph, grey squares for FullSph), compared to the flat-sky Hankel transform
-of ExtL2Sph (red circles). \emph{Right panel:} The relative difference compared
-to the full spherical case FullSph of ExtL2Sph with spherical transform (green
-line), and Hankel transform (red circles).}
+  \caption{%
+    \forref{The difference of the two-point shear correlation functions $\xi_+$ (\emph{left}) and $\xi_-$ (\emph{right})
+    of the ExtL2Sph projection relative to the full spherical case (FullSph). Two cases of the shear correlation function transformation for
+    ExtL2Spha are shown,
+    the full spherical case (eq.~\ref{eq:xi_wigner}, green solid lines), and the flat-sky Hankel transform (eq.~\ref{eqn:xiGG}, red dashed curves).}
+  }
 

### 2017-04-24 answer_to_referee.txt
Paper updated xi plots and table
Updated answer to referee, paper minor changes

@@
 
-- Shear correlation function, eq. (47-48).
+- Major point, shear correlation function, eq. (47-48).
   We had indeed used a transformation (with the Legendre polynomial) that is incorrect for spin-2 correlations.
@@
   form in a new Appendix C. Figures 2 and 3, involving the shear correlation functions, have been updated
-  accordingly.
+  accordingly, as well as some of the explanatory text.
+
+Minor points:
 
@@
 - p. 7, accuracy of the ExtL2FlHyb.
-  * Not sure about the reason. *
+  We have not tried to look for the reason why ExtL2Hyb is slightly worse than ExtL1Hyb, whereas the opposite is
+  true (as expected) for ExtL2Sph and ExtL1Sph.
 
 - Making Fig. 1 and following clearer.
-  * Not sure that adding labels or anything else would make those clearer. *
+  We could not think of straight-forward ways to improve the readibility of the plots. We hope that the combination
+  of colors and line styles is sufficient to tell apart the different cases.
 
 - Table 1, extra column.
-  We added columns indicating the ell_x such that for ell>ell_x the power spectrum projection has better
+  We added two columns indicating ell_x such that for ell>ell_x the power spectrum projection has better
   accuracy than x, with x=10% and 1%.
@@
 - Table 2, adding plot.
-  * Really necessary? *
+  We believe that a plot version of Table 2 does not enhance the value of the paper, since the values of sigma_8 (Omega_m/0.27)^0.6
+  are so close together, well within the 68% credible interval.
 
 - Conclusions
-  * I think present tense is fine *
+  We believe that the present tense mode is appropriate for the conclusion of the paper.
 
 - Fig. 4.
-  * On my screen I don't have a problem with this figure. *
+  This plot seems fine on our screens and printouts, we do not detect a problem of poor resolution.
 
-Other modifications.
+Other small modifications.
 
@@
 
+- Table 2: In the caption, we replaced the expression "confidence interval" with "credible interval". For the ExtL2Sph case,
+  we added "Hankel" to clarify that we use this approximation for the correlation function.
+
 - Typos:

### 2017-04-24 cfhtlens.tex
Updated answer to referee, paper minor changes

@@
 amplitude that is well within the Monte-Carlo sampling noise. The largest
-difference is measured with the \forref{depreciated} case ExtL1Fl, for which the
+difference is measured with the \forref{deprecated} case ExtL1Fl, for which the
 recovered amplitude is larger by $16\%$ of the statistical error. These
@@
 
-  \caption{\label{tab:CFHTLenS_Sigma8}Mean and 68\% confidence interval for 
+  \caption{\label{tab:CFHTLenS_Sigma8}Mean and 68\% \forref{credible} interval for 
   $\sigma_8 (\Omega_{\rm m}/0.27)^{0.6}$ and $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$
@@
   ExtL2FlHyb & $0.788^{+0.031}_{-0.033}$ & $0.740^{+0.029}_{-0.031}$ \\
-  ExtL2Sph   & $0.789^{+0.031}_{-0.032}$ & $0.740^{+0.029}_{-0.030}$ \\ \hline
+  ExtL2Sph\forref{(Hankel)} & $0.789^{+0.031}_{-0.032}$ & $0.740^{+0.029}_{-0.030}$ \\ \hline
   \end{tabular}

### 2017-04-24 limber2.tex
Updated answer to referee, paper minor changes

@@
   \caption{The two-point shear correlation functions $\xi_+$ (\emph{left}) and $\xi_-$ (\emph{right}).
-  In the spherical cases (ExtL1Sph, ExtL2Sph, FullSph), $\xi_+$ has been computed using the spherical
-  transform (equation~\ref{eq:xi_wigner}). For the flat cases, and all instances of $\xi_-$, the Hankel transform
-  in equation~(\ref{eqn:xiGG}) was used.
+  In the spherical cases (ExtL1Sph, ExtL2Sph, FullSph), \forref{$\xi_+$ and $\xi_-$ have} been computed using the spherical
+  transform (equation~\ref{eq:xi_wigner}). \forref{For the flat cases the Hankel transform
+  in equation~(\ref{eqn:xiGG}) was used.}
   The upper panels

### 2017-05-22 answer_to_referee.txt
answer to ref
small motifs

@@
 - p. 7, accuracy of the ExtL2FlHyb.
-  We have not tried to look for the reason why ExtL2Hyb is slightly worse than ExtL1Hyb, whereas the opposite is
-  true (as expected) for ExtL2Sph and ExtL1Sph.
+  In all cases, the second-order expansion adds power to the first-order term, as can be seen in Fig. 1. ExtL1FlHyb over-estimates the full spherical projection,
+  and thus ExtL2FlHyb increases this over-estimation even more. This expansion would converge to a full flat case (eq. 29), which we do not plot, and there is no
+  reason to believe that the difference to FullSph decreases with the expansion order.
+  For ExtL1FlHyb versus L1Fl, we see the better convergence of the former
+  for ell>8, as expected, and did not try to explain why L1F1 is slightly better at very low ell.
 

### 2017-07-10 limber2.tex
small motifs
Added Ludo's App C on d_mn^ell computation

@@
   i.e.~for all pre-2014 CFHTLenS results and DLS
-  \citep{jee/etal:2016} analyses, this was the approximation of choice. Note that
+  \citep{2012arXiv1210.2732J} analyses, this was the approximation of choice. Note that
   we do not discuss the second-order Limber approximation with $p(\ell)=1$.
@@
 > 20$.
+
+\forref{We note that in all cases the second-order Limber expansion adds power
+to the first-order term. In the flat hybrid case, which over-estimates the full
+spherical solution, this results in the second-order expansion being less
+precise compared to first-order.}
 
@@
 %
-\forref{where ${\rm d}^\ell_{m\,n}$ are the reduced Wigner ${\rm D}$-matrices, see App.~\ref{app:C} for details.}
+\forref{where ${\rm d}^\ell_{m\,n}$ are the reduced Wigner ${\rm D}$-matrices, see App.~\ref{app:C} for details
+on their numerical calculation.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The shear correlation function on the sphere}
+\section{Fast evaluation of the shear correlation function on the sphere}
 \label{app:C}
@@
 
+\forref{
+The calculation of the shear correlation function on the sphere requires the
+estimation of the reduced Wigner ${\rm D}$-matrices ${\rm d}^\ell_{22}$ and
+${\rm d}^\ell_{2-2}$. The general calculation of ${\rm d}^\ell_{m\,n}$ is
+cumbersome, but there are quick and numerically stable recurrence relations if
+we are interested in only a subset of these matrices. In particular, following
+\citet{BLANCO199719} we can show that
+%
+\begin{equation}
+%
+{\rm d}^\ell_{m\,n}={\ell(2\ell-1)\over \sqrt{[\ell^2-m^2][\ell^2-n^2]}}
+%
+\left[ \left( {\rm d}^1_{00}-{mn\over \ell(\ell-1)} \right) {\rm d}^{\ell-1}_{mn}
+%
+-{\sqrt{[(\ell-1)^2-m^2][(\ell-1)^2-n^2]}\over (\ell-1)(2\ell-1)} {\rm d}^{\ell-2}_{mn}\right] ,
+%
+\end{equation}
+%
+which allows to calculate all required reduced Wigner ${\rm D}$-matrices from the first two elements.
+}
+
 \label{lastpage}

### 2017-07-17 limber2.tex
Patrick/Marika's comments; removed ref to Kitching v1 in abstract

@@
 (CFHTLenS). We find that the reported tension with Planck Cosmic Microwave
-Background (CMB) temperature anisotropy results cannot be alleviated, in
-contrast to the recent claim made by Kitching et al. (2016, version 1)
+Background (CMB) temperature anisotropy results cannot be alleviated.
+%, in
+%contrast to the recent claim made by Kitching et al. (2016, version 1)
 
@@
 Considering first the flat-sky cases, the standard first-order Limber
-approximation, (L1Fl), that was adopted for all pre-2014 CFHTLenS analyses and DLS analyses, we
-find it to be accurate to better than 10\% for $\ell>3$, converging slowly to the
-true projection with percent level precison at $\ell>100$. For the extended
-Limber approximations `hybrid' cases (ExtL1FlHyb and ExtL2FlHyb), despite
-decreased accuracy for $\ell < 8$ in comparison to the standard first-order
-Limber case, the errors with respect to the true power spectrum decrease much
-faster, as $\ell^{-2}$, such that percent-level precision is reached at
-$\ell>15$.  The first-order extended Limber approximation `hybrid' cases
-(ExtL1FlHyb) was adopted by \citet{joudaki/etal:2016}, \citet{joudaki/etal:2017}, DES-SV \citep{abbott/etal:2016} and
-\cite{KiDS-450}\footnote{We confirm that there is a typographical error in
-equation 4 of \cite{KiDS-450} and in equation 2 of \citet{abbott/etal:2016} (private communication with Joe Zuntz) 
-which should include the extra term of `+0.5' in
-$\nu(\ell)$ that was incorporated in both cosmological analyses.}.
+approximation, (L1Fl), that was adopted for all pre-2014 CFHTLenS analyses and
+DLS analyses, we find it to be accurate to better than 10\% for $\ell>3$,
+converging slowly to the true projection with percent level precison at
+$\ell>100$. For the extended Limber approximations `hybrid' cases (ExtL1FlHyb
+and ExtL2FlHyb), despite decreased accuracy for $\ell < 8$ in comparison to the
+standard first-order Limber case, the errors with respect to the true power
+spectrum decrease much faster, as $\ell^{-2}$, such that percent-level
+precision is reached at $\ell>15$.  The first-order extended Limber
+approximation `hybrid' cases (ExtL1FlHyb) was adopted by
+\citet{joudaki/etal:2016}, \citet{joudaki/etal:2017}, DES-SV
+\citep{abbott/etal:2016} and \cite{KiDS-450}\footnote{We confirm that there is
+a typographical error in equation 4 of \cite{KiDS-450} and in equation 2 of
+\citet{abbott/etal:2016} (private communication with Joe Zuntz) which should
+include the extra term of `+0.5' in $\nu(\ell)$ that was incorporated in both
+cosmological analyses.}.
 
@@
 not be used in any future studies given these results.  The poor behaviour of
-this case, in comparison with the `hybrid' case, (e.g ExtL1FlHyb) can be
+this case, in comparison with the `hybrid' case, (e.g.~ExtL1FlHyb) can be
 understood by considering Taylor expansions of the different pre-factors.  The
@@
 The calculation of the shear correlation function on the sphere requires the
-estimation of the reduced Wigner ${\rm D}$-matrices ${\rm d}^\ell_{22}$ and
-${\rm d}^\ell_{2-2}$. The general calculation of ${\rm d}^\ell_{m\,n}$ is
+estimation of the reduced Wigner ${\rm D}$-matrices ${\rm d}^\ell_{2\,2}$ and
+${\rm d}^\ell_{2\,-2}$. The general calculation of ${\rm d}^\ell_{m\,n}$ is
 cumbersome, but there are quick and numerically stable recurrence relations if
@@
 %
-\left[ \left( {\rm d}^1_{00}-{mn\over \ell(\ell-1)} \right) {\rm d}^{\ell-1}_{mn}
-%
--{\sqrt{[(\ell-1)^2-m^2][(\ell-1)^2-n^2]}\over (\ell-1)(2\ell-1)} {\rm d}^{\ell-2}_{mn}\right] ,
+\left[ \left( {\rm d}^1_{0\,0}-{m\,n\over \ell(\ell-1)} \right) {\rm d}^{\ell-1}_{m\,n}
+%
+-{\sqrt{[(\ell-1)^2-m^2][(\ell-1)^2-n^2]}\over (\ell-1)(2\ell-1)} {\rm d}^{\ell-2}_{m\,n}\right] ,
 %

### 2017-07-18 answer_to_referee.txt
Added Ludo's App C on d_mn^ell computation

@@
 We would like to thank the referee for their positive report and useful comments and suggestions.
-Please fine below our replies to the referee's points. All modifications to the draft are highlighted
+Please find below our replies to the referee's points. All modifications to the draft are highlighted
 in red.
@@
   We had indeed used a transformation (with the Legendre polynomial) that is incorrect for spin-2 correlations.
-  We have replaced this with the correct transformations using the reduced Wigner D-matrices. We state their
-  form in a new Appendix C. Figures 2 and 3, involving the shear correlation functions, have been updated
+  We have replaced this with the correct transformations using the reduced Wigner D-matrices. We added a short
+  Appendix C for details on their computation. Figures 2 and 3, involving the shear correlation functions, have been updated
   accordingly, as well as some of the explanatory text.
@@
 Minor points:
+
+- abstract: Removed comment on Kitching et al. (2016, version 1), since their version 2 did not retain
+  the incorrect calculations and claims from v1.
 

### 2018-01-17 authors.tex
Removed marked comments according to ref report

@@
 Hendrik Hildebrandt$^6$,
-Fabian K\"ohlinger$^7$,
-Konrad Kuijken$^8$, and
-Massimo Viola$^8$
+Fabian K\"ohlinger$^8$,
+Konrad Kuijken$^9$, and
+Massimo Viola$^9$
 \\
@@
 $^7$Department of Physics and Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC V6T 1Z1, Canada\\
-$^7$Kavli Institute for the Physics and Mathematics of the Universe (WPI), The University of Tokyo Institutes for Advanced Study, \\
+$^8$Kavli Institute for the Physics and Mathematics of the Universe (WPI), The University of Tokyo Institutes for Advanced Study, \\
 \phantom{$^7$}The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
-$^8$Leiden Observatory, Leiden University, Niels Bohrweg 2, 2333 CA Leiden, the Netherlands
+$^9$Leiden Observatory, Leiden University, Niels Bohrweg 2, 2333 CA Leiden, the Netherlands
 }

### 2018-01-17 cfhtlens.tex
Removed marked comments according to ref report

--- 2017-04-20 cfhtlens.tex
@@
 amplitude that is well within the Monte-Carlo sampling noise. The largest
-difference is measured with the \forref{depreciated} case ExtL1Fl, for which the
+difference is measured with the deprecated case ExtL1Fl, for which the
 recovered amplitude is larger by $16\%$ of the statistical error. These
@@
 \cite{2003MNRAS.341.1311S}, there is a decrease of $0.6 \sigma$ with $\sigma_8
-(\Omega_{\rm m}/0.27)^{0.6} = 0.768^{+0.029}_{-0.031}$\forref{, using L1Fl}.
+(\Omega_{\rm m}/0.27)^{0.6} = 0.768^{+0.029}_{-0.031}$, using L1Fl.
 
@@
 
-  \caption{\label{tab:CFHTLenS_Sigma8}Mean and 68\% confidence interval for 
+  \caption{\label{tab:CFHTLenS_Sigma8}Mean and 68\% credible interval for 
   $\sigma_8 (\Omega_{\rm m}/0.27)^{0.6}$ and $\sigma_8 (\Omega_{\rm m}/0.3)^{0.6}$
@@
   ExtL2FlHyb & $0.788^{+0.031}_{-0.033}$ & $0.740^{+0.029}_{-0.031}$ \\
-  ExtL2Sph   & $0.789^{+0.031}_{-0.032}$ & $0.740^{+0.029}_{-0.030}$ \\ \hline
+  ExtL2Sph(Hankel) & $0.789^{+0.031}_{-0.032}$ & $0.740^{+0.029}_{-0.030}$ \\ \hline
   \end{tabular}

### 2018-01-17 limber2.tex
eq 1 round brackets
Removed marked comments according to ref report

@@
 
-\title[Precision calculations of the cosmic shear projection]{Precision calculations of the cosmic shear power spectrum projection}
+\title[Precision cosmic-shear projection]{Precision calculations of the cosmic shear power spectrum projection}
 
@@
 second-order Limber equations for the projection. We find that the impact of
-adopting these approximations \forref{is} negligible when constraining cosmological
+adopting these approximations is negligible when constraining cosmological
 parameters from current weak lensing surveys.
@@
 Background (CMB) temperature anisotropy results cannot be alleviated.
-%, in
-%contrast to the recent claim made by Kitching et al. (2016, version 1)
-
-%\citet{2016arXiv161104954K}.
-
+%
 For future large-scale surveys with unprecedented precision, we show that the
@@
 We consider spherical coordinates and the flat-sky approximation, and compute
-the full projection \forref{of the lensing power spectrum}. The first-order
+the full projection of the lensing power spectrum. The first-order
 extended Limber approximation provides sub-percent accuracy for $\ell > 10$ and
@@
 power spectra for the flat-sky and spherical cases, following the seminal work
-\forref{by} \citet{2000PhRvD..62d3007H} \cite[see also][]{2005PhRvD..72b3516C}. In
+by \citet{2000PhRvD..62d3007H} \cite[see also][]{2005PhRvD..72b3516C}. In
 section~\ref{sec:L2} we derive weak-lensing observables using a second-order
@@
 lensing studies, namely \citet{2008PhRvD..78d3002S,2012PhRvD..86b3001B,
-2012MNRAS.422.2854G, 2016arXiv161104954K}\forref{, see also
-\cite{2017arXiv170401054L} for a more recent work.} We present a discussion and
+2012MNRAS.422.2854G, 2016arXiv161104954K}, see also
+\cite{2017arXiv170401054L} for a more recent work. We present a discussion and
 comparison of our results to these papers in Appendix~\ref{app:B}.
@@
     %\Phi[\chi, f_K(\chi) \theta, f_K(\chi) \varphi; \chi] \, q(\chi),
-    \Phi[\chi, \chi \theta, \chi \varphi; \chi] \, q(\chi),
+    \Phi(\chi, \chi \theta, \chi \varphi; \chi) \, q(\chi),
   \label{eq:psi}
@@
   q(\chi) = \int\limits_\chi^{\chi_{\rm h}} {\rm d} \chi^\prime \, n(\chi^\prime)
-    %\frac{f_K(\chi^\prime - \chi)}{f_K(\chi^\prime)},
     \frac{\chi^\prime - \chi}{\chi^\prime},
@@
     = & (2\pi)^3 \delta_{\rm D}(\vec k - \vec k^\prime) P_\Phi(k; \chi, \chi^\prime).
-    %\nonumber \\
-    %= & (2\pi)^3 \delta_{\rm D}(\vec k - \vec k^\prime) \pref^2 k^{-4} a^{-1}(\chi) a^{-1}(\chi^\prime)
-      %P_{\rm m}(k; \chi, \chi^\prime).
   \label{eq:p_phi}
@@
 degrees. To account for the sky curvature of the observed data, the shear
-correlation functions from observed galaxy ellipticities \forref{are} now routinely
+correlation functions from observed galaxy ellipticities are now routinely
 computed using spherical coordinates, since projecting to a Cartesian plane has
@@
 %
-by performing a Taylor expansion of an arbitrary \forref{differentiable} function
+by performing a Taylor expansion of an arbitrary differentiable function
 $f$ around $x = k \chi = \nu = \ell + 1/2$, where the Bessel function has its
@@
 \begin{equation}
- P_{\rm m}(k, \chi) =: D^2_+(\chi) \tilde P_{\rm m}(k, \chi) \forref{\approx D^2_+(\chi) \tilde P_{\rm m}(k)}.
+ P_{\rm m}(k, \chi) =: D^2_+(\chi) \tilde P_{\rm m}(k, \chi) \approx D^2_+(\chi) \tilde P_{\rm m}(k).
   \label{eq:P_k_chi_sep_s}
@@
 
-\forref{We note that in all cases the second-order Limber expansion adds power
+We note that in all cases the second-order Limber expansion adds power
 to the first-order term. In the flat hybrid case, which over-estimates the full
 spherical solution, this results in the second-order expansion being less
-precise compared to first-order.}
+precise compared to first-order.
 
@@
     used in the text and figures.
-    \forref{The sixth (seventh) column indicates the mode $\ell_x$ such that for $\ell \leq \ell_x$, the approximated
-    power spectrum is more accurate than $x$, with $x=0.1$ ($0.01$).}
+    The sixth (seventh) column indicates the mode $\ell_x$ such that for $\ell \leq \ell_x$, the approximated
+    power spectrum is more accurate than $x$, with $x=0.1$ ($0.01$).
     } 
@@
   \hline
-  Case & ID & equation & $p(\ell)$ & $\nu(\ell)$ & \forref{$\ell_{0.1}$} & \forref{$\ell_{0.01}$} & Comment \\ \hline
+  Case & ID & equation & $p(\ell)$ & $\nu(\ell)$ & $\ell_{0.1}$ & $\ell_{0.01}$ & Comment \\ \hline
   %  black
@@
 galaxy shape catalogue. The baseline quantity is the two-point correlation
-function \citep{1991ApJ...370....1M, 1992ApJ...388..272K, BS01}, given \forref{in the flat-sky approximation} by
+function \citep{1991ApJ...370....1M, 1992ApJ...388..272K, BS01}, given in the flat-sky approximation by
 %
@@
   % &
-  = \forref{\left\langle \gamma \gamma^\ast \right\rangle(\theta) =} \frac 1 {2\pi} \int {\rm d} \ell \, \ell \, {\rm J}_0(\ell
+  = \left\langle \gamma \gamma^\ast \right\rangle(\theta) = \frac 1 {2\pi} \int {\rm d} \ell \, \ell \, {\rm J}_0(\ell
    \theta)
@@
   %&
-  = \forref{\left\langle \gamma \gamma \right\rangle(\theta) =} \frac 1 {2\pi} \int
+  = \left\langle \gamma \gamma \right\rangle(\theta) = \frac 1 {2\pi} \int
    {\rm d} \ell \, \ell \, {\rm J}_4(\ell \theta)
@@
 replaced by the spherical transform
-\forref{\citep{1999IJMPD...8...61N,2004MNRAS.350..914C}}
-%
-\forref{
+\citep{1999IJMPD...8...61N,2004MNRAS.350..914C}
+%
 \begin{equation}
@@
   =  \frac 1{4\pi} \sum\limits_{\ell=2}^\infty (2 \ell + 1) C^\gamma(\ell) {\rm d}^\ell_{2\,2}(\theta); \quad 
- \xi_0(\theta) 
+ \xi_-(\theta) 
   =  \frac 1{4\pi} \sum\limits_{\ell=2}^\infty (2 \ell + 1) C^\gamma(\ell) {\rm d}^\ell_{2\,-2}(\theta)
@@
 \end{equation}
-}
-%
-\forref{where ${\rm d}^\ell_{m\,n}$ are the reduced Wigner ${\rm D}$-matrices, see App.~\ref{app:C} for details
-on their numerical calculation.}
+%
+where ${\rm d}^\ell_{m\,n}$ are the reduced Wigner ${\rm D}$-matrices, see App.~\ref{app:C} for details
+on their numerical calculation.
 
@@
 %
-We find that the Hankel transform (equation~\ref{eqn:xiGG}) is accurate to better than \forref{$5$ ($0.2$) percent
-for $\xi_+$ ($\xi_-$)}.
+We find that the Hankel transform (equation~\ref{eqn:xiGG}) is accurate to better than $5$ ($0.2$) percent
+for $\xi_+$ ($\xi_-$).
 %
 The difference between the second-order Limber and full projection solution using the
-spherical transform (equation~\ref{eq:xi_wigner}) is well below one \forref{($0.03$) percent
-on scales of $\vartheta < 300$ arcminutes for $\xi_+$ ($\xi_-$)}.
+spherical transform (equation~\ref{eq:xi_wigner}) is well below one ($0.03$) percent
+on scales of $\vartheta < 300$ arcminutes for $\xi_+$ ($\xi_-$).
 The red lines in Fig.~\ref{fig:xi_p_wigner} present the limit of
 precision that we can achieve with the current fast Hankel transform implementation
-for the correlation function. The green \forref{lines show} the limit of the
+for the correlation function. The green lines show the limit of the
 second-order Limber approximation on the correlation function.
@@
   \caption{%
-    \forref{The difference of the two-point shear correlation functions $\xi_+$ (\emph{left}) and $\xi_-$ (\emph{right})
+    The difference of the two-point shear correlation functions $\xi_+$ (\emph{left}) and $\xi_-$ (\emph{right})
     of the ExtL2Sph projection relative to the full spherical case (FullSph). Two cases of the shear correlation function transformation for
     ExtL2Spha are shown,
-    the full spherical case (eq.~\ref{eq:xi_wigner}, green solid lines), and the flat-sky Hankel transform (eq.~\ref{eqn:xiGG}, red dashed curves).}
+    the full spherical case (eq.~\ref{eq:xi_wigner}, green solid lines), and the flat-sky Hankel transform (eq.~\ref{eqn:xiGG}, red dashed curves).
   }
@@
   \caption{The two-point shear correlation functions $\xi_+$ (\emph{left}) and $\xi_-$ (\emph{right}).
-  In the spherical cases (ExtL1Sph, ExtL2Sph, FullSph), \forref{$\xi_+$ and $\xi_-$ have} been computed using the spherical
-  transform (equation~\ref{eq:xi_wigner}). \forref{For the flat cases the Hankel transform
-  in equation~(\ref{eqn:xiGG}) was used.}
+  In the spherical cases (ExtL1Sph, ExtL2Sph, FullSph), $\xi_+$ and $\xi_-$ have been computed using the spherical
+  transform (equation~\ref{eq:xi_wigner}). For the flat cases the Hankel transform
+  in equation~(\ref{eqn:xiGG}) was used.
   The upper panels
@@
 
-\forref{
 The calculation of the shear correlation function on the sphere requires the
@@
 which allows to calculate all required reduced Wigner ${\rm D}$-matrices from the first two elements.
-}
 
